### 2013-07-09 summary.tex
Add rough notes
These are my rough notes from ages ago.

\documentclass{robinminion}

\usepackage[round]{natbib}
\bibliographystyle{plainnat}

\usepackage{rotating, amsthm}

\author{Willem Heijltjes and Robin Houston}
\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.2}

\def\mkspin#1#2{\smash{%
  \rotatebox[origin=c]{180}{\mathsurround=0pt$#1#2$}}}
\def\spin{\mathpalette\mkspin}
\def\parr{\mathbin{\spin{\&}}}
\let\tn\otimes

\newtheorem{lemma}{Lemma}

\begin{document}

\maketitle

\linespread{1.1}\selectfont
\noindent\emph{\textsc{mll} proof equivalence} is the problem of deciding whether one proof may be turned into another by a series of commuting conversions. Thanks to many years of work on proof nets \citep{Girard87, DR89, TrimbleThesis, BCST, HughesFreeStar} we know this is equivalent to a reasonably simple rewiring problem on graphs.

On the other side of the fence, thanks to many years of work on combinatorial games and complexity theory \citep{RushHour, HearnDemaineTCS, GamesPuzzlesAndComputation, TheConnectivityOfBooleanSatisfiability, ReconfigurationProblems} we know many examples of rewiring problems on graphs that are \textsc{pspace}-complete. So in a sense it is not a great surprise to find that \textsc{mll} proof equivalence is \textsc{pspace}-complete as well. On the other hand, I think this is the first time these different ideas have been brought together. We will give a reduction from the configuration-to-configuration problem for Nondeterministic Constraint Logic \citep{HearnDemaineTCS, GamesPuzzlesAndComputation}.

\section*{Nondeterministic Constraint Logic}

A \emph{constraint graph} is an undirected graph with an assignment of a natural number \emph{weight} to each edge and a natural number \emph{minimum in-flow constraint} to each vertex. A \emph{configuration} of the constraint graph is an orientation (direction) of the edges such that the sum of incoming edge weights at each vertex is at least the minimum in-flow constraint of that vertex. A \emph{move} from one configuration to another configuration consists of reversing the direction of a single edge such that the minimum in-flow constraints remain satisfied. The \emph{configuration-to-configuration problem} is: given a constraint graph and two configurations $s$ and $t$, is there a sequence of moves from $s$ that results in $t$ (or vice versa, since moves are reversible). This problem is \textsc{pspace}-complete. \citep{HearnDemaineTCS, GamesPuzzlesAndComputation}

For present purposes, we need to introduce a slightly different notion of configuration. A \emph{progressive configuration} assigns to each edge not only a direction but also an \emph{orientation value}, which is a natural number at most the weight of the edge. The configuration is valid when the sum of the incoming orientation values at each vertex is precisely the minimum in-flow constraint of that vertex. A move consists of:
\begin{itemize}
    \item either reversing the direction of an edge that has zero orientation value
    \item or taking a pair of edges oriented towards the same node, and incrementing the orientation value of one while decrementing the orientation value of the other.
\end{itemize}

Each progressive configuration determines a configuration in the Hearn-Demaine sense, and an edge of a progressive configuration may be reversed just when the edge of the corresponding Hearn-Demaine configuration may be. In this sense the notions are equivalent. We'll sometimes write \textsc{pncl} to mean \textsc{ncl} with progressive configurations.

\section*{Hughes-style proof nets}

We shall work in the unit-only fragment of \textsc{mll}, where our formulas are built from the constants $\bot$ and $1$ with the operations $\tn$ and $\parr$, and we'll work with one-sided sequents and modulo associativity of $\tn$ and $\parr$.

In this setting, a Hughes-style proof net for a given sequent is simply a function from the occurences of $\bot$ to the occurences of $1$ such that the usual proof net criterion is satisfied. A rewiring step consists of moving a single $\bot$-link to a different occurence of $1$.

\section*{Notation}

We'll use a diagrammatic notation for sequents and proof nets. The atoms $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively. Then we build up larger expressions in the following way.
%
Suppose $A$ is represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
and $B$ is represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}};
%
then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
%
Tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
%
Boxes play the role of parentheses, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}

\noindent So, for example, this sequent
\[ \vdash \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, 1, \{[(1\parr 1\parr 1)\tn(1\parr 1\parr 1)]\parr 1\parr (\bot\tn\bot\tn\bot)\parr 1\}\tn\bot \]
could be drawn like this:
\begin{center}\includegraphics[scale=0.75]{example-sequent.pdf}\end{center}

\noindent We represent a proof net by drawing an arrow from each $\bullet$ to some $\circ$. For example, one proof net on the above sequent is
\begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}

\noindent It will be useful to have an abbreviated notation for expressions of the form $\bot\tn\cdots\tn\bot$ and $1\parr\cdots\parr 1$. We shall write a larger disc with the number $i$ inside for the tensor of $i+1$ occurences of $\bot$, and a larger circle with $j$ inside for the par of $j+1$ occurences of $1$, like so:
\begin{center}\includegraphics[scale=0.75]{abbreviated-notation.pdf}\end{center}

\noindent We also use fat arrows to represent a series of arrows in a proof net, like so:
\begin{center}\includegraphics[scale=0.75]{fat-arrow-example.pdf}\end{center}

\noindent This is the reason for the `$+1$' in the definition: it means that a valid proof net is formed by a collection of fat arrows with a common target just when the numbers written on the sources add up to the number written on the target. The price we pay for this convenience is a less obvious arithmetic of decomposition:
\begin{center}
    \includegraphics[scale=0.75]{decomposed-circles.pdf}\\[1em]
    \includegraphics[scale=0.75]{decomposed-discs.pdf}
\end{center}

\section*{Reduction}

The idea is to encode a constraint graph as a sequent, in such a way that proof nets over the sequent correspond to progressive configurations of the constraint graph, and each \textsc{pncl} move corresponds to a sequence of rewiring steps in the proof net. First we number the nodes from $0$ to $n$, and let $k$ be the number of edges. Then we represent node $i$ with minimum inflow constraint $c$ by the following gadget:
\begin{center}\includegraphics[scale=0.75]{node-gadget.pdf}\end{center}

\noindent and an edge of weight $w$ connecting nodes $i < j$ by the following:
\begin{center}\includegraphics[scale=0.75]{edge-gadget.pdf}\end{center}

\noindent The other gadget we need is the ``edge absorber'':
\begin{center}\includegraphics[scale=0.75]{edge-absorber-gadget.pdf}\end{center}

\noindent
The key property of this encoding is that a row of an edge gadget may be attached completely to a row of a node gadget just when the edge is attached to that node in the constraint graph, as follows:
\begin{center}
    \includegraphics[scale=0.75]{attached-gadgets-i.pdf}\hskip2em
    \includegraphics[scale=0.75]{attached-gadgets-j.pdf}
\end{center}
\noindent Similarly, a row of any edge gadget may be attached completely to an edge absorber:
\begin{center}\includegraphics[scale=0.75]{attached-edge-absorber.pdf}\end{center}

\noindent Let $d$ be the difference between the sum of the edge weights and the sum of the minimum inflow constraints.
Our sequent consists of:
\begin{itemize}
    \item All the edge gadgets (as separate entries),
    \item The tensor of all the node gadgets (a single entry),
    \item $k\times d$ edge absorbers (as separate entries).
\end{itemize}

\noindent Now, every progressive configuration of the constraint graph may be represented by a proof net over this sequent, in the following way:
\begin{itemize}
    \item Each edge is attached to the the node it is oriented towards, by attaching the small $\bullet$ at the bottom of the edge gadget to the small $\circ$ at the bottom of the node gadget. We'll call this the \emph{index link}.
    \item $kv$ rows of the edge gadget are attached to $kv$ rows of the node gadget as described above, where $v$ is the edge's orientation value.
    \item The remaining edge weight is assigned to edge absorbers, one row of the edge gadget to a single edge absorber. In total an edge of weight $w$ and orientation value $v$ uses $k(w-v)$ edge absorbers.
\end{itemize}

\noindent Of course there are many proof nets over our sequent that are not precisely of this form. We shall try to establish xxxx things:
\begin{itemize}
	\item Every proof net over this sequent corresponds (in a sense we shall define precisely) to a slightly generalised form of progressive configuration;
	\item xxxx
	\item Every move in the \textsc{pncl} game may be simulated by some sequence of proof net rewirings.
	\item If we start with a proof net that represents a configuration $x$, then perform a sequence of rewirings and end up with another proof net that represents a different configuration $y$, then there is a sequence of \textsc{pncl} moves from $x$ to $y$.
\end{itemize}

However the converse is false: in general it is possible to simulate certain invalid moves as well. The next section describes how this can happen, and how to fix it.

\subsection*{Naughty proof nets}

\noindent Although it is clear that a row of the node gadget may be filled by an edge gadget only when the edge is attached to that node, it is possible for several edge gadgets to join forces and fill part of a node gadget illegitimately. For example, suppose we have the following constraint graph with four nodes
\begin{center}\includegraphics[scale=0.75]{naughty-constraint-graph.pdf}\end{center}
Then it is possible for the two edges to fill the gadget representing node 3 and one edge absorber. The relevant gadgets are these:
\begin{center}\includegraphics[scale=0.5]{naughty-gadgets.pdf}\end{center}
and one illegitimate wiring looks like this:
\begin{center}\includegraphics[scale=0.5]{naughty-proofnet.pdf}\end{center}
We have decomposed the edge absorber into 13 individual $\circ$ nodes that are scattered around the diagram, and decomposed some of the other nodes into parts, to make the diagram more legible.

The trick we use to overcome this problem is to multiply all the edge weights and minimum inflow constraints by a constant factor that is large enough to make it impossible for an edge to be freed illegitimately using a naughty wiring. The point here is that as $w$ and $c$ become larger, these naughty wirings use the edges more and more inefficiently. To make this precise, we'll use a little combinatorial lemma:

\begin{lemma}
    A non-empty bipartite forest whose leaves are all in the same part has more vertices in the part that contains the leaves than in the part that doesn't.
\end{lemma}
\begin{proof}
Here a forest is an acyclic graph, a leaf is a vertex that has fewer than two neighbours, and bipartite means the nodes are coloured red and blue in such a way that every arc connects a red and a blue node. Without loss of generality, by symmetry, we assume the leaves are red; we want to show there are more red vertices than blue ones.

It suffices to show this for trees, i.e.\ connected acyclic graphs, since a forest is a union of trees. So take a tree: either all its nodes are red, in which case we are done, or it has some blue non-leaf nodes, in which case pick one to be the root and direct all the edges towards it. Every vertex has a unique successor (or parent) under this orientation, and since the leaves are red and the colours alternate along each path this successor relation determines a surjection from the red nodes onto the blue ones. Since the root has more than one predecessor by hypothesis, this surjection cannot be a bijection, so there must be strictly more red vertices than blue ones.
\end{proof}

Now, a wiring of our gadgets determines a bipartite graph of this sort, in the following way. The blue vertices are going to be the rows of node gadgets, specifically the rows that are linked to more than one edge gadget. (Our aim is to find an upper bound on the number of such rows.) The red vertices are going to be the \emph{columns} of the edge gadgets.

When a row of a node gadget is filled by more than one edge gadget, there must in any case be some pair of edge gadgets that touch opposite sides of the tensor in the node gadget. For each such row, choose some such pair, and add a pair of corresponding arcs to the graph.

This graph must be acyclic by the proof net criterion. So the number of naughtily-filled rows is less than the total number of edge gadget columns, which is three times the number of edges in the constraint graph. It follows that, when constructing a sequent from a constraint graph, we may multiply all our $w$ and $c$ values by a factor $m$ equal to thrice the number of edges. Since we know that fewer than $m$ rows of any node gadget may be filled in a naughty way, and since each edge gadget has a number of rows that is a multiple of $m$, it can never now happen that an edge is released from a node when it ought not to have been.

[TODO: Explain how edge absorbers can be moved about when an edge gadget moves to a different node, so that it doesn't matter how the edge absorbers are attached to the edges in the two proof nets.]

\section*{Remarks}
It is \textsc{pspace}-complete to decide, for a proof net, whether a particular link may be moved. This follows from the \textsc{pspace}-completeness of the configuration-to-edge problem for \textsc{ncl}.

I believe proof equivalence is decidable in linear time for the intuitionistic fragment of \textsc{mll}, which is an interesting (and surprising?) contrast to the classical case. Dominic Hughes and I have an old unfinished draft showing this -- it is basically all Dominic's work, to be honest -- and I think the argument there is sound. There's an attempt at it in Audrey Tan's thesis, which unfortunately contains serious errors. Our draft is an attempt at a correct proof based on Tan's ideas. Does it follow from any correct existing work?

There is an unresolved question about depth-limited formulas, where by depth I mean how deeply nested the boxes are in the diagram. At depth zero -- where no boxes are used, and so every entry in the sequent is a tensor of atoms -- there is a straightforward (but not entirely trivial) linear-time algorithm. The reduction above shows that depth two is \textsc{pspace}-complete. So what happens at depth one? This is an open question.

\bibliography{refs}
\end{document}

### 2013-07-15 notes/ssr.tex
Subset sum reconfiguration
Add a one-page document summarising everything I know about subset
sum reconfiguration.

\documentclass{robinminion}

% \usepackage[round]{natbib}
% \bibliographystyle{plainnat}

\usepackage{amsthm}

\author{Robin Houston}
\title{Everything I know about Subset Sum Reconfiguration}

\newtheorem{prop}{Proposition}
\newtheorem{eg}[prop]{Example}
\newtheorem{rem}[prop]{Remark}

\begin{document}
\maketitle
\linespread{1.1}\selectfont

\noindent This is a brief summary of everything I know about the subset sum reconfiguration problem as of four o'clock in the afternoon of Monday the 15th of July. It is brief by necessity, because I know so little.

\begin{prop}
    Subset sum reconfiguration is weakly NP-hard. \textup(Demaine--Ito\textup)
\end{prop}
\begin{proof}
    The ordinary subset sum problem may be reduced to subset sum reconfiguration. Given elements
    $a_1, \dots, a_m$ with target sum $t$, build an SSR instance with elements $a_1, \dots, a_m$,
    $t_1$ and $t_2$, threshold values $k=t$ and $c=2t$, starting configuration $t_1$ and ending configuration
    $t_2$. At some point element $t_1$ must move from inside to outside: the first time it does, the
    inside set during the move must consist of some collection of $a$ elements that sum to $t$.
\end{proof}

\begin{prop}\label{prop-diameter}
    For all $n>1$, there is an $n$-element SSR instance whose configuration graph has diameter $2n-2$.
\end{prop}
\begin{proof}
    We exhibit in terms of a parameter $m$:
    \begin{itemize}
        \item an instance with $2m+2$ elements and a shortest solution with $4m+2$ steps;
        \item if $m>0$, an instance with $2m+1$ elements and a shortest solution with $4m+1$ steps.
    \end{itemize}
    The instance with $2m+2$ elements has elements $a_1, \dots, a_m$, $b_1, \dots, b_m$, $x$ and $y$.
    For the weights, let $w(a_i)=m+1$ and $w(b_i)=m+2$ for all $i$. Let $w(x)=w(y)=m(m+2)$. The
    starting configuration is $a_1, \dots, a_m, x$ and the target configuration is $a_1, \dots, a_m, y$.
    For threshold values let $k=m(m+2)$ and $c=2m(m+2)$.

    The first time $x$ moves, the weights of the remaining elements inside must sum to $m(m+2)$.
    In particular, these weights must sum to $m$ modulo $m+1$, hence the inside elements at this
    point must include all the $b$'s. Since the weight of $x$ plus the $b$'s equals the capacity $c$,
    the elements inside at this point must therefore be precisely all the $b$'s.
    %
    So all the $a$'s and $b$'s have to move twice, and $x$ and $y$ once each, for a total of
    $4m+2$ moves.

    To obtain the instance with $2m+1$ elements, remove the element $a_1$.
\end{proof}

\begin{rem}
    The lower bound exhibited in Proposition~\ref{prop-diameter} is optimal for $n<8$. I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
\end{rem}

\begin{prop}
    For all $m>1$, there is a $(5m+3)$-element SSR instance that has an element that must move at least $m$ times in any solution sequence.
\end{prop}
\begin{proof}
    The elements are $x_1, \dots, x_{2m+1}$ of weight $3$, $a_1, \dots, a_{3m+1}$ of weight $2$, and $b$ of weight $1$.
    Let $k=6m$ and $c=6m+3$. The starting configuration is $x_1, \dots, x_{2m+1}$, and the target is $a_1, \dots, a_{3m+1}, b$. For $i=0, 1, \dots, 2m$, consider the first move after which there are precisely $2m-i$ of the $a$ elements inside. That means the $a$'s and possibly $b$ inside at this point must sum to $3i$. If $i$ is odd then, since $b$ is the only element with odd weight, $b$ must be inside at this point; similarly if $i$ is even then $b$ must be outside. So element $b$ moves at least $m$ times.
\end{proof}
\end{document}

### 2013-07-15 notes/ssr_graphs.py

@@ -1,0 +1,213 @@
+#!/usr/bin/python
+
+"""Compute the maximal diameter of a subset sum reconfiguration
+graph with n elements.
+
+The algorithm is naivety itself: enumerate all possible such
+graphs and compute all-pairs shortest paths for each.
+
+(In fact our enumeration method may also produce some unrealisable
+graphs: I am not certain that it does, but have no good reason
+to think it does not. But we are searching for upper bounds on
+the diameter, so this is harmless.)
+"""
+
+import re, sys
+
+def each_subset(xs):
+    if not xs:
+        yield frozenset()
+        return
+    
+    xs_copy = { x for x in xs }
+    x = xs_copy.pop()
+    for ys in each_subset(xs_copy):
+        yield ys
+        yield ys | {x}
+
+debug_indent = ""
+def debug_enter(fmt, *args):
+    debug_print(fmt, *args)
+    global debug_indent
+    debug_indent += "  "
+
+def debug_print(fmt, *args):
+    formatted = fmt % args
+    #print debug_indent + re.sub(r"frozenset\(\[([^\]]*)\]\)", lambda mo: "{"+mo.group(1)+"}", formatted)
+
+def debug_leave(fn):
+    global debug_indent
+    debug_indent = debug_indent[:-2]
+    debug_print("/" + fn)
+
+def each_ordering(n):
+    debug_enter("each_ordering(%d)", n)
+    if n == 0:
+        yield (frozenset(),)
+        debug_leave("each_ordering")
+        return
+    for prev in each_ordering(n-1):
+        for ordering in each_merge(prev, n):
+            yield ordering
+    debug_leave("each_ordering")
+
+def each_merge(prev, n):
+    elements = prev[-1] # The last element is always the whole set
+    other = tuple( s|{n} for s in prev )
+    debug_enter("each_merge(%r, %r)", prev, other)
+    
+    def each_partial_merge(comp, i, j, partial):
+        debug_enter("each_partial_merge(%d, %d, %r)", i, j, partial)
+        if i == len(prev):
+            yield partial + other[j:]
+            debug_leave("each_partial_merge")
+            return
+        if j == len(prev):
+            yield partial + prev[i:]
+            debug_leave("each_partial_merge")
+            return
+        
+        pair = (prev[i], other[j])
+        if pair in comp:
+            new_i, new_j, new_partial = i, j, partial
+            debug_print("[%d, %d] %r in comp", i, j, pair)
[…]

### 2013-07-15 notes/ssr.tex
Tighten bound
Actually the element `b' in Proposition 4 moves 2m+1 times.

@@
 \begin{prop}
-    For all $m>1$, there is a $(5m+3)$-element SSR instance that has an element that must move at least $m$ times in any solution sequence.
+    For all $m>1$, there is a $(5m+3)$-element SSR instance that has an element that must move at least $2m+1$ times in any solution sequence.
 \end{prop}
@@
 If $i$ is odd then, since $b$ is the only element with odd weight, $b$ must be inside at this point; similarly if $i$ is even then $b$ must be outside.
-So element $b$ moves at least $m$ times.
+So element $b$ moves at least $2m$ times.
+Since it must end up inside, it must move an odd number of times altogether, so at least $2m+1$ times.
 \end{proof}

### 2013-07-16 notes/ssr.tex
Quadratic lower bound for SSR

@@
 It is brief by necessity, because I know so little.
+%
+\textbf{Update on Tuesday}: I found out another thing.
 
@@
 
-\begin{prop}\label{prop-diameter}
+\begin{prop}\label{prop:diameter}
     For all $n>1$, there is an $n$-element SSR instance whose configuration graph has diameter $2n-2$.
@@
 \begin{rem}
-    The lower bound exhibited in Proposition~\ref{prop-diameter} is optimal for $n<8$. I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
+    The lower bound exhibited in Proposition~\ref{prop:diameter} is optimal for $n<8$. I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
 \end{rem}
 
-\begin{prop}
-    For all $m>1$, there is a $(5m+3)$-element SSR instance that has an element that must move at least $2m+1$ times in any solution sequence.
+\begin{prop}\label{prop:element-moves-a-lot}
+    For all $m$, there is a $(5m+3)$-element SSR instance that has an element that must move at least $2m+1$ times in any solution sequence.
 \end{prop}
@@
 The starting configuration is $x_1, \dots, x_{2m+1}$, and the target is $a_1, \dots, a_{3m+1}, b$.
-For $i=0, 1, \dots, 2m$, consider the first move after which there are precisely $2m-i$ of the $a$ elements inside.
+For $i=0, 1, \dots, 2m$, consider the first move after which there are precisely $2m-i$ of the $x$ elements inside.
 That means the $a$'s and possibly $b$ inside at this point must sum to $3i$.
@@
 \end{proof}
+
+\section*{New finding}
+\noindent The construction of Proposition~\ref{prop:element-moves-a-lot} can be modified to give a quadratic lower bound for the diameter of the reconfiguration graph.
+\begin{prop}
+    For all $m$, there is a $(6m+2)$-element SSR instance that requires $2m^2+6m+2$ moves.
+\end{prop}
+\begin{proof}
+    The elements are
+    $x_1, \dots, x_{2m+1}$ of weight $3m$,
+    $a_1, \dots, a_{3m+1}$ of weight $2m$,
+    and $b_1, \dots, b_m$ of weight $1$.
+    %
+    Let $k=6m^2$ and $c=6m^2+3m$.
+    %
+    The starting configuration is $x_1, \dots, x_{2m+1}$,
+    and the target is $a_1, \dots, a_{3m+1}, b_1, \dots, b_m$.
+    %
+    For $i=0, 1, \dots, 2m$, consider the first move after which there are precisely $2m-i$ of the $x$ elements inside.
+That means the $a$'s and $b$'s inside at this point must sum to $3im$.
+If $i$ is odd then, since the $a$'s all weigh $2m$, all the $b$'s must be inside at this point; similarly if $i$ is even then the $b$'s must all be outside.
+So the $b$ elements each move at least $2m$ times, and in fact $2m+1$ times since they move.
+    %
+    Therefore the total number of moves must be at least $(2m+1) + (3m+1) + (2m+1)m$, which is equal to $2m^2+6m+2$ as required.
+\end{proof}
 \end{document}

### 2013-07-16 notes/ssr.tex
Improve wording slightly

@@
     The ordinary subset sum problem may be reduced to subset sum reconfiguration. Given elements
-    $a_1, \dots, a_m$ with target sum $t$, build an SSR instance with elements $a_1, \dots, a_m$,
-    $t_1$ and $t_2$, threshold values $k=t$ and $c=2t$, starting configuration $t_1$ and ending configuration
+    $a_1, \dots, a_m$ with target sum $t$, build an SSR instance with elements $a_1, \dots, a_m$ having the corresponding weights,
+    $t_1$ and $t_2$ having weight $t$, threshold values $k=t$ and $c=2t$, starting configuration $t_1$ and ending configuration
     $t_2$. At some point element $t_1$ must move from inside to outside: the first time it does, the
@@
 That means the $a$'s and possibly $b$ inside at this point must sum to $3i$.
-If $i$ is odd then, since $b$ is the only element with odd weight, $b$ must be inside at this point; similarly if $i$ is even then $b$ must be outside.
-So element $b$ moves at least $2m$ times.
-Since it must end up inside, it must move an odd number of times altogether, so at least $2m+1$ times.
+If $i$ is odd then, since the $a$'s all have even weight, $b$ must be inside at this point; similarly if $i$ is even then $b$ must be outside.
+So element $b$ moves at least $2m+1$ times.
 \end{proof}
@@
 If $i$ is odd then, since the $a$'s all weigh $2m$, all the $b$'s must be inside at this point; similarly if $i$ is even then the $b$'s must all be outside.
-So the $b$ elements each move at least $2m$ times, and in fact $2m+1$ times since they move.
+So the $b$ elements each move at least $2m+1$ times.
     %

### 2013-07-18 notes/ssr.tex
Completely reducible sequences

@@
 \newtheorem{prop}{Proposition}
+\newtheorem{lemma}[prop]{Lemma}
 \newtheorem{eg}[prop]{Example}
 \newtheorem{rem}[prop]{Remark}
+
+\let\union\cup
+\let\intersection\cap
 
@@
 
-\noindent This is a brief summary of everything I know about the subset sum reconfiguration problem as of four o'clock in the afternoon of Monday the 15th of July.
-It is brief by necessity, because I know so little.
-%
-\textbf{Update on Tuesday}: I found out another thing.
+\noindent This is a brief summary of everything I know about the subset sum reconfiguration problem as of the evening of Thursday the 18th of July.
 
@@
 
-\section*{New finding}
 \noindent The construction of Proposition~\ref{prop:element-moves-a-lot} can be modified to give a quadratic lower bound for the diameter of the reconfiguration graph.
-\begin{prop}
+\begin{prop}\label{prop:quadratic-bound}
     For all $m$, there is a $(6m+2)$-element SSR instance that requires $2m^2+6m+2$ moves.
@@
 \end{proof}
+
+\noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable -- in linear time, if we assume the elements are already sorted by weight, or $O(n \log n)$ time if we have to sort them -- without the need to construct an actual solution.
+\begin{lemma}\label{lemma:reduction}
+    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$.
+By abuse of notation we shall also refer to the whole instance as $E$.
+Let $a$ and $z$ be elements of minimal and maximal weight respectively.
+If $w(z) > c-k$ or $w(a) < c-k-w(z) + 2$ then either $E$ is trivially unsolvable or else there is an element $e\in E$ and a (smaller) instance with element set $E' = E-\{e\}$ that is equivalent to the original in the sense that $E'$ is solvable iff $E$ is.
+\end{lemma}
+\begin{proof}
+    Let $e$ be any element that has weight $z$.
+
+    If $w(z) > c - k$ then our element $z$ cannot move.
+If $z$ moves between the start and target packings, then $E$ is trivially unsolvable.
+Otherwise we let $E' = E-\{z\}$.
+If $z$ is inside in both the start and target packing, let the threshold and capacity of our new instance be $k' = k-w(z)$ and $c' = c-w(z)$, and remove $z$ from the start and target configurations.
+If $z$ is outside in both the start and target, let $k'=k$ and $c'=c$.
+Every solution of $E'$ is a solution of $E$, and vice versa -- by adding $z$ to all packings in the solution sequence in the former case, or by literally using the same solution sequence in the latter.
+
+    If $w(a) < c-k-w(z) + 2$ then let $E' = E-\{a\}$.
+Look at whether or not $a$ belongs to the start configuration: if it does, let $k'=k-w(a)$ and $c'=c$; if not, let $k'=k$ and $c'=c+w(a)$.
+In both cases we have $c'-k' = c-k+w(a)$.
+Any solution of $E$ can be converted to a solution of $E'$ just by removing element $a$ from all packings in the sequence and eliminating adjacent duplicates.
+The interesting part is the converse, converting a solution of $E'$ into a solution of $E$.
+Let $A_0', \dots, A_m'$ be a sequence of packings that solves $E'$.
+We shall show how to insert element $a$, with some additional moves of $a$, to obtain a solution of $E$.
+
+    Let us say that a packing $A'$ of $E'$ \textit{requires $a$} if $w(A') < k' + w(a)$, and that it \textit{rejects $a$} if $w(A') > c' - w(a)$.
+Now we want to argue that in a solution sequence of $E'$ there are never two adjacent packings such that one requires $a$ and the other rejects it.
+The gap between the bound for rejecting $a$ and the bound for accepting it is $c' - w(a) - (k' + w(a)) = c'-k'-2w(a) = c-k-w(a)$, so it is not possible to cross this gap without the weight changing by at least $c-k-w(a)+2$.
+Two adjacent packings differ in weight by at most $w(z)$, and since we are supposing that $w(a) < c-k-w(z) + 2$ it follows that they differ by less than $c-k-w(a)+2$, as required.
+
+    Finally we can construct a solution sequence for $E$ by inserting $a$ where it is required and removing it where it is rejected.
+We describe an algorithm that reads $A_0', \dots A_m'$ in order and outputs a solution of $E$.
+The algorithm keeps track of whether $a$ is currently inside or outside the packing as it goes along.
+If $a$ belongs to the start packing then initially $a$ is inside, otherwise initially $a$ is outside.
+Then for each $i$ from $0$ to $m$:
+    \begin{itemize}
+        \item if $a$ is currently inside and $A_i'$ rejects $a$, output $A_{i-1}'$ followed by $A_i'$. (Note this case cannot occur when $i=0$.) Let $a$ be outside.
+        \item if $a$ is currently outside and $A_i'$ requires $a$, output $A_{i-1}'\union\{a\}$ followed by $A_i'\union\{a\}$. (This case cannot occur when $i=0$ either.) Let $a$ be inside.
+        \item otherwise, output $A_i'$ if $a$ is outside, and output $A_i'\union\{a\}$ if $a$ is inside.
+    \end{itemize}
+\end{proof}
+
+\noindent In some cases we can iterate Lemma~\ref{lemma:reduction} to reduce the instance to the trivial one-element case.
+\begin{prop}\label{prop:iterated-reduction}
+    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$.
+Suppose further that no element weighs more than $c-k$.
+Let $E = {e_0, \dots, e_n}$ in nondecreasing order by weight.
+If
+    \[
+        w(e_i) < c - k + \sum_{j<i}w(e_j) - w(e_n) + 2
+    \]
+    for all $i$ then the instance is solvable.
+Note that this condition does not mention the start or target packings, so in fact such instances have the property that any valid packing is reachable from any other.
+\end{prop}
+\begin{rem}
+    Let us say that an instance satisfying the property of Proposition~\ref{prop:iterated-reduction} is \textit{completely reducible}.
+The instances exhibited in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} are completely reducible.
+\end{rem}
 \end{document}

### 2013-07-18 notes/ssr.tex
Correction

@@
 
-\noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable -- in linear time, if we assume the elements are already sorted by weight, or $O(n \log n)$ time if we have to sort them -- without the need to construct an actual solution.
+\noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable without the need to construct an actual solution.
 \begin{lemma}\label{lemma:reduction}
@@
     Let us say that an instance satisfying the property of Proposition~\ref{prop:iterated-reduction} is \textit{completely reducible}.
-The instances exhibited in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} are completely reducible.
+The instances exhibited in Proposition~\ref{prop:element-moves-a-lot} are completely reducible.
+The instances exhibited in Proposition~\ref{prop:quadratic-bound} are not completely reducible, but can be reduced to a form that has a linear bound on the length of the solution sequence.
 \end{rem}

### 2013-07-18 notes/ssr.tex
Add a little more explanation

@@
 The instances exhibited in Proposition~\ref{prop:element-moves-a-lot} are completely reducible.
-The instances exhibited in Proposition~\ref{prop:quadratic-bound} are not completely reducible, but can be reduced to a form that has a linear bound on the length of the solution sequence.
+The instances exhibited in Proposition~\ref{prop:quadratic-bound} are not completely reducible, but can be reduced to a form that has a linear bound on the length of the solution sequence by eliminating the elements that have weight $1$.
 \end{rem}

### 2013-07-19 notes/ssr.tex
Add an explicit mention of one area of uncertainty
Mark the other place the same issue arises

@@
 \noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable without the need to construct an actual solution.
+(The details need some work here, but I think the basic idea is okay.)
 \begin{lemma}\label{lemma:reduction}
@@
 Otherwise we let $E' = E-\{z\}$.
-If $z$ is inside in both the start and target packing, let the threshold and capacity of our new instance be $k' = k-w(z)$ and $c' = c-w(z)$, and remove $z$ from the start and target configurations.
+If $z$ is inside in both the start and target packing, let the threshold and capacity of our new instance be $k' = k-w(z)$ [TODO: what if $k-w(z) < 0$?] and $c' = c-w(z)$, and remove $z$ from the start and target configurations.
 If $z$ is outside in both the start and target, let $k'=k$ and $c'=c$.
@@
 Look at whether or not $a$ belongs to the start configuration: if it does, let $k'=k-w(a)$ and $c'=c$; if not, let $k'=k$ and $c'=c+w(a)$.
-In both cases we have $c'-k' = c-k+w(a)$.
+[TODO: What if $k-w(a) < 0$?
+This case needs to be considered.] In both cases we have $c'-k' = c-k+w(a)$.
 Any solution of $E$ can be converted to a solution of $E'$ just by removing element $a$ from all packings in the sequence and eliminating adjacent duplicates.

### 2013-07-19 main/mllequiv.tex
made a start

\documentclass{robinminion}

\usepackage{amsthm}
\usepackage[round]{natbib}
\usepackage{mllequiv,willemtools}

\makeTheoremDefs

\author{Willem Heijltjes and Robin Houston}
\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3}

\begin{document}

\maketitle

\begin{abstract}
MLL proof equivalence is the problem of deciding whether two proofs are related by a series of rule permutations.
%
Previous work has shown the problem to be equivalent to a rewiring problem on proof nets, which are not canonical for full MLL due to the presence of the two units.
%
Drawing from recent work on reconfiguration problems, in this paper it is shown that MLL proof equivalence is PSPACE-complete, using a reduction from Nondeterministic Constraint Logic.
\end{abstract}

%\include{s_intro}
\include{s_background}
% etc...

\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}

### 2013-07-19 main/s_background.tex
made a start

\section{MLL}

\begin{figure}
\[
\begin{array}{llll}
	\MLLrule b
 &	\MLLrule 1
 &	\MLLrule p
 &	\MLLrule t
\end{array}
\]
\caption{Inference rules for unit-only \MLL}
\label{fig:MLL}
\end{figure}

\begin{figure}
\[
	\vc{\MLLperm{bb1}} \perm \vc{\MLLperm{bb2}}
\qquad
	\vc{\MLLperm{bp1}} \perm \vc{\MLLperm{bp2}}
\]
\[
	\vc{\MLLperm{bt1}} \perm \vc{\MLLperm{bt2}} \perm \vc{\MLLperm{bt3}}
\]
\[
	\vc{\MLLperm{pp1}} \perm \vc{\MLLperm{pp2}}
\]
\[
	\vc{\MLLperm{pt1}} \perm \vc{\MLLperm{pt2}}
\]
\[
	\vc{\MLLperm{tt1}} \perm \vc{\MLLperm{tt2}}
\]
\caption{Permutations}
\label{fig:permutations}
\end{figure}

The formulae of unit-only multiplicative linear logic are given by the following grammar.
%
\[
	A,B,C \coloneq \bot \mid 1 \mid A\parr B \mid A\tn B
\]
%
The connectives $\tn$ and $\parr$ will be considered up to associativity, and \emph{duality} $\dual A$ is via DeMorgan.
%
A \emph{sequent} $\Gamma,\Delta$ will be a multiset of formulae.
%
Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names $N$, e.g.\
$\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot$.
%
This allows to 1) avoid using the notion of \emph{occurrence}, and instead refer to subformulae by the name of their root connective, as e.g.\ $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
%
Names will mostly be left implicit.

Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}.
%
The names of connectives are preserved through inferences.
%
Only cut-free proofs are considered, and no cut-rule is added.
%
\emph{Permutations} of inference rules are displayed in Figure~\ref{fig:permutations}; the symmetric variants of the last two permutations, \emph{par-tensor} and \emph{tensor-tensor}, have been omitted.

\begin{definition}
\label{def:equivalence}
%
\emph{Equivalence} of proofs in (cut-free, unit-only) multiplicative linear logic $(\perm)$ is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
%
\emph{\MLL\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
%
\end{definition}

The motivation to consider proofs up to equivalence is three-fold.
%
Firstly, there is the strong intuition that the order of permutable inferences does not contribute to the essential content of the proof.
%
Secondly, a technical motivation is that cut-elimination in \MLL\ incorporates permutation steps, and composition via cut-elimination is only associative up to permutations.
%
Thirdly, equivalent proofs are identified in natural models of multiplicative linear logic such as coherence spaces, and in the categorical semantics of \MLL, $\star$-autonomous categories.

In one of several possible definitions, a \emph{$\star$-autonomous category} \citep{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
%
\begin{itemize}

	\item
	a \emph{duality}, a contravariant functor $\dual-$ such that $A\cong\dual*A$, and

	\item
	\emph{closure}, an adjunction $-\tn B \dashv \dual{(B\tn\dual-)}$ for any object $B$,

\end{itemize}
%
satisfying natural coherence conditions.
%
The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
Modulo the \emph{strictness} induced by the use of DeMorgan duality and one-sided sequents, e.g.\ $A=\dual*A$ rather than $A\cong\dual*A$, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
\MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.

%The \emph{free $\star$-autonomous completion} $\star$-\textsc a$(\mathcal C)$ of a category $\mathcal C$ is characterised by a functor $i\colon\mathcal C\to\star$-\textsc a$(\mathcal C)$ such that any functor $\mathcal C\to \mathcal D$ into a $\star$-autonomous cateogry $\D$ factors uniquely (up to canonical isomorphism) as the composition of $i$ with a functor $\star$-\textsc a$(\mathcal C)\to\D$ preserving $\star$-autonomous structure.
%%
%\[
%\begin{tikzpicture}[auto]
%	\node (C) at (0,0) {$\mathcal C$};
%	\node (*AC) at (2,0) {$\star$-\textsc a$(\mathcal C)$};
%	\node (D) at (1,1) {$\mathcal D$};
%	\draw [->] (C) -- node {$i$} (*AC);
%	\draw [->] (C) -- (D);
%	\draw [->,dashed] (*AC) -- node {$!$} (D);
%\end{tikzpicture}
%\]
%%

\subsection{Proof nets}

A partial solution to the \MLL\ proof equivalence problem is provided by proof nets.

\begin{definition}
\label{def:proof nets}
%
For a sequent $\Gamma$,
\begin{itemize}

	\item
	a \emph{linking} $\links$ is a function from the names of $\bot$-subformulae to the names of $1$-subformulae,

	\item
	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$, with for every subformula $\named aA\named c\tn\named bB$ the edges $a-c$ and $b-c$, for every subformula $\named aA\named c\parr\named bB$ either the edge $a-c$ or the edge $b-c$, and for every subformula $\named a\bot$ the edge $a-\links(a)$,

 	\item
	a \emph{proof net} $\links$ or $(\Gamma,\links)$ is a linking $\links$ such that every switching graph is acyclic and connected.

\end{itemize}
\end{definition}

\noindent
An edge $a-\links(a)$ in a proof net or switching graph is a \emph{link} or \emph{jump}.

\begin{definition}
\label{def:proof net equivalence}
%
A \emph{permutation} between proof nets is the redirection of exactly one link.
%
\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the congruence generated by permutations.
%
\end{definition}

\noindent
There is no canonical interpretation of a proof as a proof net, since the introduction rule for $\bot$ in proofs joins a $\bot$ to a sequent, rather than a formula.

\begin{definition}
\label{def:proofs to nets}
%
The relation $(\toNet)$ interprets a proof by a linking $\links$ as follows:
% 
for each $\named a\bot$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Gamma$.
\[
	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
\]
%
\end{definition}

\begin{proposition}[\citeauthor{DR89}, \citeyear{DR89}]
\label{prop:correctness and sequentialisation}
%
For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
%
For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
%
\end{proposition}

\noindent
Proof nets are canonical representations of proofs in the absence of units: they factor out the permutations among tensor- and par-inferences, which are the last three permutations in Figure~\ref{fig:permutations}.
%
Equivalence of proof nets is generated by the remaining equations, the permutations on $\bot$-introduction.

\begin{proposition}[{\cite{HughesMLLProofNets}}]
\label{prop:proof nets work}
%
For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$ such that $\Pi\toNet\links$ and $\Pi'\toNet\links'$, $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
%
\end{proposition}

\noindent
\MLL\ proof equivalence is the problem of deciding equivalence of proof nets.

### 2013-07-20 notes/ssr.tex
Remove bogus "proof"

@@
 \end{prop}
-\begin{proof}
-    The ordinary subset sum problem may be reduced to subset sum reconfiguration. Given elements
-    $a_1, \dots, a_m$ with target sum $t$, build an SSR instance with elements $a_1, \dots, a_m$ having the corresponding weights,
-    $t_1$ and $t_2$ having weight $t$, threshold values $k=t$ and $c=2t$, starting configuration $t_1$ and ending configuration
-    $t_2$. At some point element $t_1$ must move from inside to outside: the first time it does, the
-    inside set during the move must consist of some collection of $a$ elements that sum to $t$.
-\end{proof}
 

### 2013-07-20 notes/ssr.tex
Remove lie

@@
 \newtheorem{lemma}[prop]{Lemma}
+\newtheorem{conjecture}[prop]{Conjecture}
 \newtheorem{eg}[prop]{Example}
@@
 
-\begin{prop}\label{prop:diameter}
+\begin{conjecture}\label{conjecture:diameter}
     For all $n>1$, there is an $n$-element SSR instance whose configuration graph has diameter $2n-2$.
-\end{prop}
-\begin{proof}
-    We exhibit in terms of a parameter $m$:
-    \begin{itemize}
-        \item an instance with $2m+2$ elements and a shortest solution with $4m+2$ steps;
-        \item if $m>0$, an instance with $2m+1$ elements and a shortest solution with $4m+1$ steps.
-    \end{itemize}
-    The instance with $2m+2$ elements has elements $a_1, \dots, a_m$, $b_1, \dots, b_m$, $x$ and $y$.
-    For the weights, let $w(a_i)=m+1$ and $w(b_i)=m+2$ for all $i$. Let $w(x)=w(y)=m(m+2)$. The
-    starting configuration is $a_1, \dots, a_m, x$ and the target configuration is $a_1, \dots, a_m, y$.
-    For threshold values let $k=m(m+2)$ and $c=2m(m+2)$.
-
-    The first time $x$ moves, the weights of the remaining elements inside must sum to $m(m+2)$.
-    In particular, these weights must sum to $m$ modulo $m+1$, hence the inside elements at this
-    point must include all the $b$'s. Since the weight of $x$ plus the $b$'s equals the capacity $c$,
-    the elements inside at this point must therefore be precisely all the $b$'s.
-    %
-    So all the $a$'s and $b$'s have to move twice, and $x$ and $y$ once each, for a total of
-    $4m+2$ moves.
-
-    To obtain the instance with $2m+1$ elements, remove the element $a_1$.
-\end{proof}
+\end{conjecture}
 
 \begin{rem}
-    The lower bound exhibited in Proposition~\ref{prop:diameter} is optimal for $n<8$. I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
+    The lower bound conjectured in Conjecture~\ref{prop:diameter} is optimal for $n<8$.
+I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
+An earlier version of these notes had a construction that purported to exhibit this bound, but there is an error and it does not work.
 \end{rem}

### 2013-07-20 notes/ssr.tex
Correct label
Minor wording changes

@@
 
-\noindent This is a brief summary of everything I know about the subset sum reconfiguration problem as of the evening of Thursday the 18th of July.
+\noindent This is a brief summary of some of the things I know or conjecture about the subset sum reconfiguration problem.
+These are rough notes, which are likely to contain errors large and small, intended to record ideas rather than to be a polished account.
 
@@
 \begin{rem}
-    The lower bound conjectured in Conjecture~\ref{prop:diameter} is optimal for $n<8$.
+    The lower bound conjectured by Conjecture~\ref{conjecture:diameter} exists and is optimal for $n<8$.
 I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
-An earlier version of these notes had a construction that purported to exhibit this bound, but there is an error and it does not work.
+An earlier version of these notes had a construction that purported to exhibit this bound, but there is an error in that construction.
 \end{rem}

### 2013-07-25 main/s_background.tex
fix makefile; add section "Level 0" file; change wording on strictness

@@
 %
-Modulo the \emph{strictness} induced by the use of DeMorgan duality and one-sided sequents, e.g.\ $A=\dual*A$ rather than $A\cong\dual*A$, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
+The formulation used induces various forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, one-sided sequents mean the closure adjunction is an equivalence of categories, and the associativities are identities by decree.
 %
-\MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.
+Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
+%
+This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.
 

### 2013-07-25 main/s_level_0.tex
fix makefile; add section "Level 0" file; change wording on strictness

\section{Equivalence in the absence of $\parr$}

### 2013-08-09 main/s_background.tex
made a start with section "level 0"

@@
 \noindent
-There is no canonical interpretation of a proof as a proof net, since the introduction rule for $\bot$ in proofs joins a $\bot$ to a sequent, rather than a formula.
+There is no canonical interpretation of a proof as a proof net, since the introduction rule for $\bot$ in proofs joins a $\bot$-formula to a sequent, rather than a formula.
 
@@
 
-\begin{proposition}[{\cite{HughesMLLProofNets}}]
+\begin{proposition}[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
 \label{prop:proof nets work}

### 2013-08-09 main/s_level_0.tex
made a start with section "level 0"

@@
-\section{Equivalence in the absence of $\parr$}
+\newcommand\1{1}
+\newcommand\prm[1][\links]{\mathit p_{#1}}
+
+%NOTE: need 'octopus' terminology here
+
+%NOTE: will we need to count arms often enough to make it worthwile to write $|\Gamma|_\bot$ for the number of $\bot$-occurrences in a sequent $\Gamma$?
+
+\section{Equivalence in the absence of $~\protect\parr$}
+
+Let a \emph{1-alternation} sequent be one over formulae of the form $1$ or $\bot\tn\ldots\tn\bot$, where the number of $\bot$-subformulae is at least 2.
+%
+Such a sequent is inhabited exactly when the number of formulae in the sequent is one greater than the total number of $\bot$-subformulae it contains.
+%
+An inhabited 1-alternation sequent with only one tensor-formula, i.e.\ a sequent of the form $\1,\ldots,\1,\bot\tn\ldots\tn\bot$ with $n$ $\bot$-subformulae and $n$ $1$-subformulae, will admit $n!$ different proof nets, each with $n$ links.
+%
+Since no link can re-attach, its equivalence classes are singletons.
+
+\begin{proposition}
+\label{lem:level0 max binary}
+%
+For a 1-alternation sequent with at least two tensor-formulae there are at most two equivalence classes of proof nets.
+%
+\end{proposition}
+
+\begin{proof}
+%
+It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
+%
+For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
+\[
+	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
+\]
+It has two equivalence classes of 12 proof nets each.
+
+For the inductive step, let $\Gamma$ be the following sequent.
+\[
+	\Delta,A\tn\named a\bot,\named x\1
+\]
+There are two cases: 1) where $A$ is a tensor-formula, and 2) where $A$ is $\bot$ and where, for the induction hypothesis to apply, $\Delta$ contains at least two tensor-formulae.
+%
+For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named x1$, and is the only link to do so.
+%
+This reduces equivalence on $\Gamma$ to equivalence on $\Delta,A$ in case 1, and on $\Delta$ in case 2, so that the induction hypothesis applies.
+
+Let $\named a\bot$ connect to $\named y\1$ in $\Delta$, and let $\named c\bot$ be a subformula of $A$, which means that for case 2, $A=\named c\bot$.
+%
+Then $\links'$ is obtained by adjusting $\links$ as follows.
+\begin{itemize}
+
+	\item
+Let $c-z$, i.e.\ $\named z\1$ is the target of the jump from $\named c\bot$.	
+%
+Ensure that $\named z\1$ is the only target shared between jumps in $A$ and in $\Delta$, by moving any other such jump from $\Delta$ to $\named z\1$.
+
+	\item
+If there are multiple links connecting to $\named x\1$, select one $b-x$ for some $\named b\bot$ in a tensor-formula $B$.
+%
+Re-attach the others to the target of another jump out of $B$, of which there must be at least one.
+
+	\item
+Since $A$ is only connected via $\named z\1$, there is a jump $d-z$ connecting $B$ to $A$ (though $\named d\bot$ is not necessarily a subformula of $B$).
+%
+Re-attach $\named d\bot$ to $\named y\1$, then $\named a\bot$ to $\named x\1$, and $\named b\bot$ to $\named z\1$.
+
+\end{itemize}
+
+\end{proof}
+
+Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
+%
+\begin{itemize}
+
+	\item
+The first $\bot$ in each $A_i$ is named $b(i)$, while the remaining $\bot$-subformulae in $\Gamma$ are named $b(n+1),\dotsc,b(m)$.
+
+	\item
+The first $\1$ in $\Gamma$ is named by the set $A=\{1,\dotsc,n\}$, the remaining ones are named $n+1,\dotsc,m$.
+
+\end{itemize}
+%
+The naming scheme suggests a linking for $\Gamma$, where the first $\bot$-subformula of each tensor-formula connects to $\named A\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae; i.e.\ $b(i)-A$ when $i\leq n$ and $b(i)-i$ otherwise.
+%
+A net for $\Gamma$ can be interpreted as a permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
+%
+\begin{definition}
+To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
+\[
+	\prm(i) = 
+	\begin{cases}
+		j 				& \text{ if $b(i)$ may connect to $A$ and $\named{b(i)}\bot$ is a subformula of $t(j)$}
+	\\	\links(b(i))	& \text{ otherwise.}
+	\end{cases}
+\]
+The \emph{parity} of $\links$ is the parity of its permutation.
+\end{definition}
+
+\begin{proposition}
+\label{lem:level0 min binary}
+Re-attaching a jump in a net $\links$ preserves its parity. 
+\end{proposition}
+
+\begin{proof}
+TO DO
+\end{proof}

### 2013-08-18 main/s_level_0.tex
finished proofs in Level 0

@@
-\newcommand\1{1}
-\newcommand\prm[1][\links]{\mathit p_{#1}}
-
 %NOTE: need 'octopus' terminology here
@@
 \begin{proposition}
-\label{lem:level0 max binary}
+\label{prop:level0 max binary}
 %
@@
 	\item
-Let $c-z$, i.e.\ $\named z\1$ is the target of the jump from $\named c\bot$.	
+Let $\edge cz$, i.e.\ $\named z\1$ is the target of the jump from $\named c\bot$.	
 %
@@
 	\item
-Since $A$ is only connected via $\named z\1$, there is a jump $d-z$ connecting $B$ to $A$ (though $\named d\bot$ is not necessarily a subformula of $B$).
+Since $A$ is only connected via $\named z\1$, there is a link $\edge dz$ connecting $B$ to $A$ (though $\named d\bot$ is not necessarily a subformula of $B$).
 %
@@
 
+\begin{proposition}
+\label{prop:level0 may-connect path}
+%
+In a proof net for a 1-alternation sequent a link $\edge{\named a\bot}{\named b\1}$ can be permuted to $\edge{\named a\bot}{\named c\1}$ if and only if there is a path in the net from $b$ to $c$ not passing through $a$.
+%
+\end{proposition}
+
+If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
+%
+By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
+
 Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
@@
 	\item
-The first $\bot$ in each $A_i$ is named $b(i)$, while the remaining $\bot$-subformulae in $\Gamma$ are named $b(n+1),\dotsc,b(m)$.
+The first $\1$ in $\Gamma$ is named $N$, the remaining ones are named with the numbers $n+1,\dotsc,m$.
 
 	\item
-The first $\1$ in $\Gamma$ is named by the set $A=\{1,\dotsc,n\}$, the remaining ones are named $n+1,\dotsc,m$.
+A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=N$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
 
@@
 %
-The naming scheme suggests a linking for $\Gamma$, where the first $\bot$-subformula of each tensor-formula connects to $\named A\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae; i.e.\ $b(i)-A$ when $i\leq n$ and $b(i)-i$ otherwise.
-%
-A net for $\Gamma$ can be interpreted as a permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
+The naming scheme suggests a linking for $\Gamma$, where $\edge{(i,k)}{k}$ for each $\bot$-formula; i.e\ the first $\bot$-subformula of each tensor-formula connects to $\named N\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
+
+A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
 %
@@
 \[
-	\prm(i) = 
+	\prm(k) = 
 	\begin{cases}
-		j 				& \text{ if $b(i)$ may connect to $A$ and $\named{b(i)}\bot$ is a subformula of $t(j)$}
-	\\	\links(b(i))	& \text{ otherwise.}
+		i				& \text{ if $(i,k)$ may connect to $N$; otherwise,}
+	\\	j				& \text{ where $\edge{(i,k)}j$.}
 	\end{cases}
@@
 \end{definition}
+
+To see that $\prm$ is injective, consider the following.
+\begin{itemize}
+	\item The domains of $i$ and $j$ are $1,\dotsc,n$ and $n+1,\dotsc,m$ respectively, and hence disjoint.
+	\item Exactly one $\bot$-formula in each $A_i$ may connect to $N$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $N$ it has a path to $N$ (Proposition~\ref{prop:level0 may-connect path}).
+	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $N$ via the other tensor-formula, which must have a path to $N$ by the above.
+\end{itemize}
 
@@
 \begin{proof}
-TO DO
+Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
+%
+There are two cases, depending on whether $(i,k)$ may connect to $N$.
+%
+If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $N$, since for any path to $N$ via $\edge{(i,k)}x$ in $\links$ there is a path to $N$ via $\edge{(i,k)}y$.
+%
+Then the permutation of $\links'$ is that of $\links$.
+
+If $(i,k)$ may not connect to $N$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
+\[
+	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
+\]
+Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $N$.
+%
+On the relevant domain, this gives the following permutation for $\links$.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
+	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
+\end{array}\right)
+\]
+In $\links$, where $(i,k)$ connects to $y$, the $\bot$-formulae $(i_a,k_a)$ may connect to $N$, giving the following permutation.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+The parity of both permutations is the same if and only if the relative permutation, below, is even.
+\[
+\left(\begin{array}{ccccccc}
+	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
+
 \end{proof}

### 2013-09-12 main/s_background.tex
notation, some pictures, wording

@@
 %
-The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
+%The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
 %
-The formulation used induces various forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, one-sided sequents mean the closure adjunction is an equivalence of categories, and the associativities are identities by decree.
+The category with as objects unit-only \MLL-formulae and as morphisms $A\to B$ the equivalence classes of proofs of $\dual A\parr B$, denoted $\textsc{mll}(\emptyset)$, is a $\star$-autonomous category.
+%
+The present formulation of formulae induces two forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, while
+%, one-sided sequents mean the closure adjunction is an equivalence of categories, 
+associativity is an identity by decree.
 %
@@
 %
-The relation $(\toNet)$ interprets a proof by a linking $\links$ as follows:
+The relation $(\toNet)$ interprets a proof $\Pi$ for a sequent $\Gamma$ by a linking $\links$ as follows:
 % 
-for each $\named a\bot$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Gamma$.
+$\Pi\toNet\links$ if for each $\named a\bot$ in $\Gamma$, if $\Delta$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Delta$.
 \[
-	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
+	\infer[\MLLlabel b]{\Delta,\named a\bot}{\Delta}
 \]
@@
 \MLL\ proof equivalence is the problem of deciding equivalence of proof nets.
+
+\subsection{Notation}
+
+We will use a concise diagrammatic notation for sequents and proof nets.
+%
+The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
+%
+A tensor is represented by a line connecting both subformulae, and a par by juxtaposition: if $A$ and $B$ are represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
+and \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}},
+%
+then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
+and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
+%
+A tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
+\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
+%
+Boxes play the role of parentheses around par-formulae, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}
+
+\noindent For example, this sequent
+\[ \vdash \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, 1, \{[(1\parr 1\parr 1)\tn(1\parr 1\parr 1)]\parr 1\parr (\bot\tn\bot\tn\bot)\parr 1\}\tn\bot \]
+could be drawn like this:
+\begin{center}\includegraphics[scale=0.75]{example-sequent.pdf}\end{center}
+
+\noindent We represent a proof net by drawing an arrow from each $\bullet$ to some $\circ$. For example, one proof net on the above sequent is
+\begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}

### 2013-09-12 main/s_level_0.tex
notation, some pictures, wording

@@
 
+\begin{figure}[p]
+\[
+\begin{array}{ccc}
+	\basenet 1213 & \perm & \basenet 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 1223 &		  & \basenet 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 1323 &		  & \basenet 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 1321 &		  & \basenet 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 2321 &		  & \basenet 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 2331 & \perm & \basenet 2131
+\end{array}
+\qquad
+\begin{array}{ccc}
+	\basenet 1312 & \perm & \basenet 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 2312 &		  & \basenet 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 2313 &		  & \basenet 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 2113 &		  & \basenet 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 2123 &		  & \basenet 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+	\basenet 3123 & \perm & \basenet 3121
+\end{array}
+\]
+\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
+\label{fig:2x12 nets}
+\end{figure}
+
 \begin{proof}
@@
 \]
-It has two equivalence classes of 12 proof nets each.
+It has two equivalence classes of 12 proof nets each, displayed in Figure~\ref{fig:2x12 nets}.
 
@@
 
-Let $\named a\bot$ connect to $\named y\1$ in $\Delta$, and let $\named c\bot$ be a subformula of $A$, which means that for case 2, $A=\named c\bot$.
+Let $\named a\bot$ connect to $\named y\1$ in $\Delta$.
+%
+For case 1, let $A$ be $A'\tn\named c\bot$; for case 2, let $A=\named c\bot$.
 %

### 2013-09-13 main/s_level_0.tex
Fixes, additions, and pictures for Level-0

--- 2013-08-18 main/s_level_0.tex
@@
 
+%
+%\begin{figure}[p]
+%\[
+%\begin{array}{ccc}
+%	\netA 1213 & \perm	& \netA 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 1223 &		& \netA 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 1323 &		& \netA 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 1321 &		& \netA 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2321 &		& \netA 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2331 & \perm	& \netA 2131
+%\end{array}
+%\qquad
+%\begin{array}{ccc}
+%	\netA 1312 & \perm	& \netA 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2312 &		& \netA 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2313 &		& \netA 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2113 &		& \netA 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2123 &		& \netA 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 3123 & \perm	& \netA 3121
+%\end{array}
+%\]
+%\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
+%\label{fig:2x12 nets}
+%\end{figure}
+
 \begin{proof}
@@
 \]
-It has two equivalence classes of 12 proof nets each.
+It has two equivalence classes, of 12 proof nets each.
+%
+Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.
+
+%, displayed in Figure~\ref{fig:2x12 nets}.
 
@@
 \[
-	\Delta,A\tn\named a\bot,\named x\1
+	\Delta,A\tn\named a\bot,\named z\1
 \]
@@
 %
-For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named x1$, and is the only link to do so.
+For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named z1$, and is the only link to do so.
 %
@@
 
-Let $\named a\bot$ connect to $\named y\1$ in $\Delta$, and let $\named c\bot$ be a subformula of $A$, which means that for case 2, $A=\named c\bot$.
+In constructing $\links'$, since the proof net must be connected, there is a path from $a$ to $z$.
 %
-Then $\links'$ is obtained by adjusting $\links$ as follows.
-\begin{itemize}
+We will consider only the jumps on this path, not any other edges.
+%
+There are four cases.
+
+\begin{enumerate}[label=\roman*.]
+	\item
+The path consists of exactly the jump $\edge az$.
+%
+Let $\edge by$ be a jump from a $\named b\bot$ in $A$; then $\links'$ is obtained from $\links$ by changing: $\links'(e)=y$  for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$.
 
 	\item
-Let $\edge cz$, i.e.\ $\named z\1$ is the target of the jump from $\named c\bot$.	
+The path starts with the jump $\edge ax$ (and $x\neq z$).
 %
-Ensure that $\named z\1$ is the only target shared between jumps in $A$ and in $\Delta$, by moving any other such jump from $\Delta$ to $\named z\1$.
+Let $\edge by$ be a jump from a $\named b\bot$ in $A$, and let the path end with the jumps $\edge wc$ and $\edge dz$, where $\named c\bot$ and $\named d\bot$ are in the same tensor-formula $B$.
+%
+Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$, including $d$.
+%
+These changes are illustrated as permutations below.
+%
+\[
+	\netB xywz \perm \netB zywz \perm \netB zywy
+\]
 
 	\item
-If there are multiple links connecting to $\named x\1$, select one $b-x$ for some $\named b\bot$ in a tensor-formula $B$.
+The path consists of exactly one jump $\edge bz$ from a $\named b\bot$ in $A$ (and $b\neq a$).
 %
-Re-attach the others to the target of another jump out of $B$, of which there must be at least one.
+Let $\links(a)=y$.
+%
+Choose a jump $\edge cw$ from $\named c\bot$ in $A$ such that there is another $\edge dw$ from $\named d\bot$ in a formula $B$ (not excluding the possibilities $c=b$ and $c=a$).
+%
+Let $\edge ex$ be a further jump from $\named e\bot$ in $B$.
+%
+Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, $\links'(d)=x$, $\links'(e)=y$, and $\links'(f)=x$ for each $f$ (including $b$) such that $\links(f)=z$ and $f\neq a$.
+%
+These changes are exhibited as a series of permutations below, from top left to bottom left (note that the jump from $d$ moves twice).
+%
+\[
+\begin{array}{ccccc}
+	\netC yzwx & \perm & \netC yzzx & \perm & \netC yxzx
+	\\ &&&& \vperm \\
+	\netC zxxy & \perm & \netC zxzy & \perm & \netC yxzy
+\end{array}
+\]
 
 	\item
-Since $A$ is only connected via $\named z\1$, there is a link $\edge dz$ connecting $B$ to $A$ (though $\named d\bot$ is not necessarily a subformula of $B$).
+The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
 %
-Re-attach $\named d\bot$ to $\named y\1$, then $\named a\bot$ to $\named x\1$, and $\named b\bot$ to $\named z\1$.
-
-\end{itemize}
-
+Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
+%
+Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
+%
+This is illustrated below.
+\end{enumerate}
+%
+\[
+	\kern-1pt \netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw \kern-1pt 
+\]
+%
 \end{proof}
@@
 %
-In a proof net for a 1-alternation sequent a link $\edge{\named a\bot}{\named b\1}$ can be permuted to $\edge{\named a\bot}{\named c\1}$ if and only if there is a path in the net from $b$ to $c$ not passing through $a$.
+For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
 %
+\begin{itemize}
+	\item
+The edge $\edge ab$ can be permuted to $\edge ac$.
+	\item
+There is a path from $b$ to $c$ not passing through $a$.
+	\item
+The path from $a$ to $c$ starts with the jump $a-b$.
+\end{itemize} 
 \end{proposition}
@@
 	\item
-The first $\1$ in $\Gamma$ is named $N$, the remaining ones are named with the numbers $n+1,\dotsc,m$.
+One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.
 
 	\item
-A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=N$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
+A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=*$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
 
@@
 %
-The naming scheme suggests a linking for $\Gamma$, where $\edge{(i,k)}{k}$ for each $\bot$-formula; i.e\ the first $\bot$-subformula of each tensor-formula connects to $\named N\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
+The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,k)=k$; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
 
@@
 \begin{definition}
+\label{def:combinatorial permutation}
 To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
@@
 	\begin{cases}
-		i				& \text{ if $(i,k)$ may connect to $N$; otherwise,}
-	\\	j				& \text{ where $\edge{(i,k)}j$.}
+		i				& \text{ if $(i,k)$ may connect to $*$; and}
+	\\	\links(i,k)		& \text{ otherwise.}
 	\end{cases}
@@
 \begin{itemize}
-	\item The domains of $i$ and $j$ are $1,\dotsc,n$ and $n+1,\dotsc,m$ respectively, and hence disjoint.
-	\item Exactly one $\bot$-formula in each $A_i$ may connect to $N$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $N$ it has a path to $N$ (Proposition~\ref{prop:level0 may-connect path}).
-	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $N$ via the other tensor-formula, which must have a path to $N$ by the above.
+	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
+	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Proposition~\ref{prop:level0 may-connect path}).
+	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
 \end{itemize}
@@
 \begin{proposition}
-\label{lem:level0 min binary}
-Re-attaching a jump in a net $\links$ preserves its parity. 
+\label{prop:level0 min binary}
+A permutation on a net $\links$ preserves its parity. 
 \end{proposition}
@@
 %
-There are two cases, depending on whether $(i,k)$ may connect to $N$.
+There are two cases, depending on whether $(i,k)$ may connect to $*$.
 %
-If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $N$, since for any path to $N$ via $\edge{(i,k)}x$ in $\links$ there is a path to $N$ via $\edge{(i,k)}y$.
+If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
 %
@@
 
-If $(i,k)$ may not connect to $N$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
+If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
 \[
@@
 \]
-Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $N$.
+Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
 %
@@
 \]
-In $\links$, where $(i,k)$ connects to $y$, the $\bot$-formulae $(i_a,k_a)$ may connect to $N$, giving the following permutation.
+In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
+%
+The permutation $\prm[\links']$ is the following.
 \[
@@
 This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
+%
+\end{proof}
 
+\begin{theorem}
+\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
+\end{theorem}
+
+\begin{proof}
+For a sequent with 1 tensor-formula, the problem is syntactic equality.
+%
+For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:level0 max binary} and~\ref{prop:level0 min binary} the equivalence of two nets is determined by their relative parity.
+%
+Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
+%
+This yields a linear-time algorithm.
+%
 \end{proof}

### 2013-09-13 main/scratch.tex
Fixes, additions, and pictures for Level-0

--- 2013-07-19 main/mllequiv.tex
@@
-\documentclass{robinminion}
+\documentclass{article}
 
@@
 
+\graphicspath{{../notes/}}
+
 \makeTheoremDefs
-
-\author{Willem Heijltjes and Robin Houston}
-\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3}
 
@@
 
-\maketitle
-
-\begin{abstract}
-MLL proof equivalence is the problem of deciding whether two proofs are related by a series of rule permutations.
-%
-Previous work has shown the problem to be equivalent to a rewiring problem on proof nets, which are not canonical for full MLL due to the presence of the two units.
-%
-Drawing from recent work on reconfiguration problems, in this paper it is shown that MLL proof equivalence is PSPACE-complete, using a reduction from Nondeterministic Constraint Logic.
-\end{abstract}
-
-%\include{s_intro}
-\include{s_background}
-% etc...
-
-\bibliographystyle{plainnat}
-\bibliography{refs}
-
 \end{document}

### 2013-09-23 LIX colloquium/Extended abstract.tex
abstract for LIX colloquium

\documentclass{robinminion}

\usepackage{amsthm}
\usepackage{enumitem}
\usepackage[round]{natbib}
\usepackage{EA,willemtools}

\graphicspath{{../notes/}}

\makeTheoremDefs

\author{Willem Heijltjes and Robin Houston}
\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete\\[4pt]\large Abstract}

\begin{document}

\maketitle

\linespread{1.1}\selectfont
\noindent\emph{\MLL\ proof equivalence} is the problem of deciding whether one proof in multiplicative linear logic may be turned into another by a series of commuting conversions. It is also the \emph{word problem} for $\star$-autonomous categories \citep{Barr-1991}: the problem of deciding whether two term representations denote the same morphism in any $\star$-autonomous category. In \MLL$^{-}$, without the two units, proof equivalence corresponds to syntactic equality on \emph{proof nets} \citep{Girard87, DR89}, and is linear-time decidable. For full \MLL, thanks to many years of work on proof nets \citep{TrimbleThesis, BCST, HughesFreeStar} we know that the proof equivalence problem corresponds to a reasonably simple graph-rewiring problem.

On the other side of the fence, thanks to many years of work on combinatorial games and complexity theory \citep{RushHour, HearnDemaineTCS, GamesPuzzlesAndComputation, TheConnectivityOfBooleanSatisfiability, ReconfigurationProblems} we know many examples of rewiring problems on graphs that are \textsc{pspace}-complete. We will give a reduction from the configuration-to-configuration problem for \emph{Nondeterministic Constraint Logic} \citep{HearnDemaineTCS, GamesPuzzlesAndComputation}, a graphical formalism specifically designed for easy problem reduction.

The \textsc{pspace}-completeness result rules out a satisfactory notion of proof net for \MLL\ with units, and in particular for this reason it may come as a surprise. However, \textsc{pspace}-completeness is not unusual for graph rewiring problems,  nor for \emph{reconfiguration} problems \citep{ReconfigurationProblems} of the kind to which \MLL\ proof equivalence belongs. A reconfiguration problem is the problem of finding a path across related solutions to given a decision problem---in this case \MLL\ proof search. Reconfiguration problems whose associated decision problem is \textsc{np}-complete, as is \MLL\ proof search, frequently are \textsc{pspace}-complete; an important example, \emph{satisfiability-reconfiguration} \citep{TheConnectivityOfBooleanSatisfiability} is the problem of finding a path across satisfying assignments to a boolean formula by changing the value of one atom at a time.

\small
\bibliographystyle{plainnat}
\bibliography{../refs}

\end{document}

### 2013-09-30 LIX colloquium/Extended abstract.tex
Add reference to extended abstract

@@
 In \MLL$^{-}$, without the two units, proof equivalence corresponds to syntactic equality on \emph{proof nets} \citep{Girard87, DR89}, and is linear-time decidable.
-For full \MLL, thanks to many years of work on proof nets \citep{TrimbleThesis, BCST, HughesFreeStar} we know that the proof equivalence problem corresponds to a reasonably simple graph-rewiring problem.
+For full \MLL, thanks to many years of work on proof nets \citep{TrimbleThesis, BCST, Strassburger-Lamarche-2004, HughesFreeStar} we know that the proof equivalence problem corresponds to a reasonably simple graph-rewiring problem.
 

### 2014-01-02 main/s_background.tex
started Sections 3 and 4 - main definitions, lemmas, and proof ideas

@@
 %
-\emph{Equivalence} of proofs in (cut-free, unit-only) multiplicative linear logic $(\perm)$ is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
+\emph{Equivalence} of proofs $(\perm)$ in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
 %
@@
 %
-This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.
+This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two term representations denote the same morphism.
 

### 2014-01-02 main/s_level_1.tex
started Sections 3 and 4 - main definitions, lemmas, and proof ideas

\section{Par}

\begin{definition}
A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
\end{definition}

\begin{definition}
A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
\end{definition}

The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
%
A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
%
In a proof net, the \emph{kingdom} and the \emph{empire} of a par are respectively its smallest and largest scope.

The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
%
In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$ and re-attaching all arcs connecting to removed vertices to $v$.
%

[[ ADD ILLUSTRATED EXAMPLE ]]

%
The contraction of scopes may replace the switching condition as a correctness criterion.
%
The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.

\begin{proposition}
\label{prop:scoping correctness}
A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:

\begin{enumerate}
	\item
sub-sequents are strictly nested: if $\named w\parr$ occurs in $s(v)$ then $s(w)<s(v)$; and
	\item
for each $\named v\parr$, the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents $s(w)$ are contracted.
\end{enumerate}

\end{proposition}

\begin{proof}
For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
%
For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, the sub-sequent of each $s(v)$ is the conclusion $\Delta, A\named v\parr B$ of its introduction rule.
\[
	\infer{\Delta,A\named v\parr B}{\Delta,A,B}
\]
\end{proof}

[[ IDEA: the following could help simplify octopus-arithmetic ]]

\begin{definition}
The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
%
A sequent is \emph{balanced} if its balance is zero.
\end{definition}

An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.

An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]

### 2014-01-02 main/s_level_2.tex
started Sections 3 and 4 - main definitions, lemmas, and proof ideas

\section{Proof nets and constraint graphs}

\newcommand\itn[1]{\llbracket#1\rrbracket}
\newcommand\coitn[1]{\llparenthesis#1\rrparenthesis}

\begin{definition}
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,w)$ consists of a set of vertices $V$ with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set of undirected edges $E\subseteq V\times V$ with \emph{weight} $w\colon E\to N$.

A \emph{configuration} of an \textsc{ncg} is a function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$ connecting vertices $v$ and $w$, $\gamma(e)\in\{v,w\}$, and
	\item
for every vertex $v$, the sum of its inflow weights $\sum\{w(e)\mid \gamma(e)=v\}$ is equal to or greater than its inflow constraint $c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for a \textsc{ncg} $G$ that differ in the assignment $\gamma(e)$ of exactly one edge.

\end{definition}

[[ NOTE: decide on notation for steps and paths in permutation relations ]]

For a graph $G=(V,E,c,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints, $\sum_{v\in V}c(v)$, and the sum of all edge weights, $\sum_{e\in E}w(e)$.

Let $A^n$ denote the sequent of $n$ copies of a formula $A$, and for a sequent $\Gamma=A_1,\dotsc,A_n$ let $\bigotimes\Gamma=A_1\tn\dotso\tn A_n$ and $\bigparr\Gamma=A_1\parr\dotso\parr A_n$.

\begin{definition}
The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,w)$ is a sequent constructed as follows.
%
Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_k\}$ where $|V|=n$ and $|E|=k$.

The interpretation of a vertex $v_i$ is the formula
\[
	\itn{v_i} = \bigparr\big(C^{k\times c(v_i)} \big)\parr 1
\]
where each \emph{constraint element} $C$ is the formula
\[
	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)
\]

The interpretation of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
\[
	\itn{e} = \bigotimes\big(W^{k\times w(e)}\big)\tn\bot
\]
where each \emph{weight element} $W$ is the formula
\[
	W = \bigotimes\big(\bot^{3i+2}\big)\parr\bigotimes\big(\bot^{3(j-i)+1}\big)\parr\bigotimes\big(\bot^{3(n-j)+3}\big)
\]

The interpretation of the graph $G$ is the sequent
\[
	\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
\]
where $m=k\times(|w|-|c|)\times(3n+4)$.

\end{definition}

\begin{definition}
The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
\end{definition}

\begin{lemma}
In a proof net for $\itn G$, an edge-gadget $\itn e$ belongs to the empire of at most one vertex-gadget $\itn v$.
\end{lemma}

\begin{proof}
Since vertex-gadgets are joined by a tensor, the lemma is immediate from \cite[Proposition 1]{Bellin-vandeWiele-1995}.
\end{proof}

By the above, a proof net $\links$ for $\itn G$ gives a partial function $\coitn\links\colon E\rightharpoonup V$.

\begin{lemma}
If $\links\sim\links'$ is the re-attachment of one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
\end{lemma}

\begin{proof}
TO DO
\end{proof}

In a proof net for the interpretation of a graph $\itn G$, call an edge-gadget $\itn e$ with $e=(u,w)$ \emph{appropriate} for a vertex-gadget $\itn v$ if $v\in\{u,w\}$, and \emph{inappropriate} otherwise.

\begin{lemma}
In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the

\end{lemma}

\begin{proof}[Proof sketch]
There are not enough edges to fill a unit of weight inappropriately in $\itn v$.
\end{proof}

### 2014-01-02 main/s_level_2.tex
fixes to proof ideas

@@
 \begin{definition}
-A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,w)$ consists of a set of vertices $V$ with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set of undirected edges $E\subseteq V\times V$ with \emph{weight} $w\colon E\to N$.
+A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set $E$ of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
 
@@
 	\item
-for every edge $e$ connecting vertices $v$ and $w$, $\gamma(e)\in\{v,w\}$, and
+$\gamma(e)\in v(e)$ for every edge $e$, and
 	\item
@@
 \[
-	\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
+	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
+	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
 \]
@@
 
-\end{definition}
-
-\begin{definition}
-The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
 \end{definition}
@@
 
-By the above, a proof net $\links$ for $\itn G$ gives a partial function $\coitn\links\colon E\rightharpoonup V$.
+%\begin{lemma}
+%If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
+%\end{lemma}
+
+% THIS IS FALSE : OTHER EDGES MAY BE CONNECTED *VIA* THE ONE THAT IS MOVED
+
+By the above, a proof net for $\itn G$ gives a partial function from edges to vertices.
+
+\begin{definition}
+	For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links\colon E\rightharpoonup V$ be the partial function where $\coitn\links(e)$ is $v$ if $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
+\end{definition}
+
+In an \textsc{ncg} $G$, an edge $e$ will be called \emph{appropriate} for a vertex $v$ if $v\in v(e)$, and \emph{inappropriate} otherwise.
+%
+This notion is extended to edge-gadgets $\itn e$ and vertex-gadgets $\itn v$ in $\int G$.
 
 \begin{lemma}
-If $\links\sim\links'$ is the re-attachment of one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
+If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then from $\coitn\links$ to $\coitn{\links'}$ at most one edge is taken from one appropriate vertex to another.
 \end{lemma}
 
-\begin{proof}
-TO DO
+\begin{proof}[Proof sketch]
+At most, a link can re-connect from vertex-gadget $v$ to vertex-gadget $w$, moving a number of chained edge-gadgets from $v$ to $w$.
+%
+But at most one edge is appropriate for both $v$ and $w$.
 \end{proof}
 
-In a proof net for the interpretation of a graph $\itn G$, call an edge-gadget $\itn e$ with $e=(u,w)$ \emph{appropriate} for a vertex-gadget $\itn v$ if $v\in\{u,w\}$, and \emph{inappropriate} otherwise.
-
 \begin{lemma}
-In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the
-
+In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
 \end{lemma}
@@
 \end{proof}
+
+\begin{definition}
+The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
+\end{definition}

### 2014-01-03 main/s_level_2.tex
tinkering with proofs and defs.

@@
 
-A \emph{configuration} of an \textsc{ncg} is a function $\gamma\colon E\to V$ such that
+A \emph{configuration} of an \textsc{ncg} is a partial function $\gamma\colon E\rightharpoonup V$ such that
 \begin{itemize}
 	\item
-$\gamma(e)\in v(e)$ for every edge $e$, and
+for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$, and
 	\item
-for every vertex $v$, the sum of its inflow weights $\sum\{w(e)\mid \gamma(e)=v\}$ is equal to or greater than its inflow constraint $c(v)$.
+for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
 \end{itemize}
 
-A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for a \textsc{ncg} $G$ that differ in the assignment $\gamma(e)$ of exactly one edge.
+A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for an \textsc{ncg} $G$ that differ in the assignment $\gamma(e)$ of exactly one edge.
 
@@
 
-%\begin{lemma}
-%If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
-%\end{lemma}
-
-% THIS IS FALSE : OTHER EDGES MAY BE CONNECTED *VIA* THE ONE THAT IS MOVED
-
-By the above, a proof net for $\itn G$ gives a partial function from edges to vertices.
-
-\begin{definition}
-	For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links\colon E\rightharpoonup V$ be the partial function where $\coitn\links(e)$ is $v$ if $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
-\end{definition}
-
 In an \textsc{ncg} $G$, an edge $e$ will be called \emph{appropriate} for a vertex $v$ if $v\in v(e)$, and \emph{inappropriate} otherwise.
@@
 \begin{lemma}
-If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then from $\coitn\links$ to $\coitn{\links'}$ at most one edge is taken from one appropriate vertex to another.
-\end{lemma}
-
-\begin{proof}[Proof sketch]
-At most, a link can re-connect from vertex-gadget $v$ to vertex-gadget $w$, moving a number of chained edge-gadgets from $v$ to $w$.
-%
-But at most one edge is appropriate for both $v$ and $w$.
-\end{proof}
-
-\begin{lemma}
+\label{lem:appropriate edge weights}
 In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
@@
 
+Then using the above, a proof net for $\itn G$ may be interpreted as a configuration for $G$.
+
 \begin{definition}
-The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
+	For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
 \end{definition}
+
+\begin{lemma}
+If $\links\sim\links'$ are proof nets for $\itn G$ then $\coitn\links\sim\coitn{\links'}$.
+\end{lemma}
+
+\begin{proof}
+A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.
+%
+Then in both $\coitn\links$ and $\coitn{\links'}$ the edges $e_1$ through $e_n$ are mobile, since by Lemma~\ref{lem:appropriate edge weights} the empires of the vertex-gadgets $\itn v$ (in cases 1 and 3) and $\itn w$ (in cases 2 and 3) contain appropriate edge-gadgets other than $\itn{e_1}$ through $\itn{e_n}$ of sufficient combined weight.
+%
+It follows that in the graph $G$ the edges $e_1$ through $e_n$ can be moved away from $v$ and/or onto $w$ one at a time.
+
+\end{proof}
+
+%
+%
+%
+%\begin{definition}
+%The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
+%\end{definition}

### 2014-01-05 main/s_level_2.tex
wrote a proof

@@
 
-\begin{proof}[Proof sketch]
-There are not enough edges to fill a unit of weight inappropriately in $\itn v$.
+\begin{proof}
+Let $|V|=n$ and $|E|=k$, and consider the vertex $v_i$ and an edge $e$ connecting vertices $v_a$ and $v_b$ where $i\neq a,b$.
+%
+Each constraint element in $\itn{v_i}$ is an instance of the formula
+\[
+	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)~.
+\]
+The two $\parr$-subformulae have a balance of $-3i-1$ and $-3(n-i)-2$ respectively.
+%
+Each weight element in $\itn{e}$ is an instance of 
+\[
+	W = \bigotimes\big(\bot^{3a+2}\big)\parr\bigotimes\big(\bot^{3(b-a)+1}\big)\parr\bigotimes\big(\bot^{3(n-b)+3}\big)~.
+\]
+The three $\tn$-subformulae have a net balance of $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
+%
+In pairs, they have a net balance of $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
+%
+Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$, it follows that $W$ can balance the scope of at most one of both subformulae of $C$.
+
+The vertex-gadget $\itn{v_i}$ is the formula
+\[
+	\itn{v_i} = \bigparr\big(C^{k\times c(v_i)} \big)\parr 1~.
+\]
+It will be shown that $k$ inappropriate edge-gadgets may balance at most $k-1$ constraint elements $C$.
+
+Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq k\times c(v_i)$. 
+%
+If the scopes $s(x_j)$ and $s(y_m)$ of any $x_j$ and $y_m$ are balanced by weight elements $W$ and $W'$ of the same edge-gadget $\itn e$, then since $W$ and $W'$ are connected by a tensor, there are switchings of $W$, $W'$, $s(x_j)$, and $s(y_m)$ such that $x_j$ and $y_m$ are connected in the proof net for $\itn G$.
+%
+Then the first constraint element of $\itn{v_i}$ requires 2 edge-gadgets to balance, and each successive element requires one additional edge-gadget.
 \end{proof}
 
-Then using the above, a proof net for $\itn G$ may be interpreted as a configuration for $G$.
+Using the above, a proof net for $\itn G$ may be interpreted as a configuration for $G$.
 

### 2014-01-06 main/s_level_0.tex
started Sections 3 and 4 - main definitions, lemmas, and proof ideas
completed definition and proofs for interpretation of configurations

@@
 %
-Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.
+(Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.)
 
@@
 \begin{proof}
-For a sequent with 1 tensor-formula, the problem is syntactic equality.
+For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
 %

### 2014-01-06 main/s_level_1.tex
fixes to proof ideas
completed definition and proofs for interpretation of configurations

@@
 %
-For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, the sub-sequent of each $s(v)$ is the conclusion $\Delta, A\named v\parr B$ of its introduction rule.
+For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
 \[

### 2014-01-06 main/s_level_2.tex
completed definition and proofs for interpretation of configurations

@@
 
-\newcommand\itn[1]{\llbracket#1\rrbracket}
-\newcommand\coitn[1]{\llparenthesis#1\rrparenthesis}
+% TO DO: I think we can move away from partial configurations - this requires to show that edge-gadgets always belong to the kingdom of at least one vertex-gadget
 
@@
 
-A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for an \textsc{ncg} $G$ that differ in the assignment $\gamma(e)$ of exactly one edge.
+A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.
 
@@
 
-For a graph $G=(V,E,c,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints, $\sum_{v\in V}c(v)$, and the sum of all edge weights, $\sum_{e\in E}w(e)$.
+For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints, $\sum_{v\in V}c(v)$, and the sum of all edge weights, $\sum_{e\in E}w(e)$.
 
@@
 \begin{definition}
-The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,w)$ is a sequent constructed as follows.
+\label{def:graph interpretation}
+The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
 %
-Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_k\}$ where $|V|=n$ and $|E|=k$.
+Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
 
-The interpretation of a vertex $v_i$ is the formula
+The interpretation of a vertex $v_k$ is the formula
 \[
-	\itn{v_i} = \bigparr\big(C^{k\times c(v_i)} \big)\parr 1
+	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
 \]
@@
 \[
-	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)
+	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
 \]
@@
 \[
-	\itn{e} = \bigotimes\big(W^{k\times w(e)}\big)\tn\bot
+	\itn{e} = \bigotimes\big(W^{m\times w(e)}\big)\tn\bot
 \]
@@
 	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
-	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
+	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
 \]
-where $m=k\times(|w|-|c|)\times(3n+4)$.
+where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.
 
 \end{definition}
+
+In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
+%
+This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\int G$.
+
+For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
+\[
+	W =  \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big)
+	\parr\big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
+	\parr\big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
+\]
+and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
+\[
+	C = \big(\named{    \dagger'}1\parr\named{   1'}1\parr\dotso\parr\named{3k+1'}1\big)
+	\tn \big(\named{\downdagger'}1\parr\named{3k+2'}1\parr\dotso\parr\named{3n+3'}1\big)~.
+\]
+There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
+\[
+	\links(x) = x' \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
+\]
+\[
+	\links(\ddagger)=
+	\begin{cases}
+			\dagger' & \text{if }k=i \\
+		\downdagger' & \text{if }k=j~.
+	\end{cases}
+\]
+There is also a natural linking for the sequent $W,\named\star 1,\named{1'}1,\dotsc,\named{3n+3'}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
+\[
+	\links(x)=
+	\begin{cases}
+		\star & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
+		   x' & \text{otherwise }.
+	\end{cases}
+\]
+
+\begin{proposition}
+\label{prop:element linkings}
+\begin{enumerate}
+	\item
+Given a vertex $v$ and an appropriate edge $e$, for a constraint element $C$ in $\itn v$ and a weight element $W$ in $\itn e$ the natural linking for the sequent $W,C$ is a proof net.
+	\item
+Given a weight element $W$ for a graph with $|V|=n$, the natural linking for the sequent $W,1^{3n+4}$ is a proof net.
+\end{enumerate}
+\end{proposition}
+
+The interpretation $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
+%
+Let the rightmost $1$-occurrence of each vertex-gadget $\itn v$ be named $v$, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$ named $e$:
+\[	
+	\itn v = C\parr\dotso\parr C\parr \named v1 \qquad \itn e= W\tn\dotso\tn W\tn\named e\bot~.
+\]
+To define $\itn\gamma=\links$, firstly let
+\[
+	\links(e)=\gamma(e)~.
+\]
+Then successively for each edge $e$ and each weight element $W$ in $e$, if $\gamma(e)$ has a first free constraint element $C$, extend $\links$ to include the natural linking on $W,C$; otherwise, extend $\links$ by the natural linking on $W$ plus the first $3n+4$ free edge absorbers.
+
+\begin{proposition}
+If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
+\end{proposition}
+
+\begin{proof}
+Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
+%
+The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its natural linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
+%
+The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the edge-absorbers within scopes of weight elements inside $\itn e$.
+%
+Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
+%
+After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the special $\named v1$ of $\itn v$, thus forming a tree.
+\end{proof}
+
+%------------------------------------------------------------------------------------------------
+
+\subsection{Completeness}
+
+\begin{lemma}
+If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then $\itn\gamma\sim\itn\delta$.
+\end{lemma}
+
+%------------------------------------------------------------------------------------------------
+
+\subsection{Soundness}
 
@@
 \end{proof}
-
-In an \textsc{ncg} $G$, an edge $e$ will be called \emph{appropriate} for a vertex $v$ if $v\in v(e)$, and \emph{inappropriate} otherwise.
-%
-This notion is extended to edge-gadgets $\itn e$ and vertex-gadgets $\itn v$ in $\int G$.
 
@@
 
-%
-%
-%
 %\begin{definition}

### 2014-01-06 main/s_level_2.tex
minor edits

@@
 \begin{proof}
-Let $|V|=n$ and $|E|=k$, and consider the vertex $v_i$ and an edge $e$ connecting vertices $v_a$ and $v_b$ where $i\neq a,b$.
+Let $|V|=n$ and $|E|=m$, and consider the vertex $v_i$ and an edge $e$ connecting vertices $v_a$ and $v_b$ where $i\neq a,b$.
 %
@@
 \[
-	\itn{v_i} = \bigparr\big(C^{k\times c(v_i)} \big)\parr 1~.
+	\itn{v_i} = \bigparr\big(C^{m\times c(v_i)} \big)\parr 1~.
 \]
-It will be shown that $k$ inappropriate edge-gadgets may balance at most $k-1$ constraint elements $C$.
+It will be shown that $m$ inappropriate edge-gadgets may balance at most $m-1$ constraint elements $C$.
 
-Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq k\times c(v_i)$. 
+Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq m\times c(v_i)$. 
 %

### 2014-01-08 main/s_level_2.tex
included partial / total distinction in NCG def

@@
 
-% TO DO: I think we can move away from partial configurations - this requires to show that edge-gadgets always belong to the kingdom of at least one vertex-gadget
+\newcommand\alt{\underline}
+
+[[ NOTE: we should decide on notation for steps versus paths in permutation relations ]]
 
@@
 
-A \emph{configuration} of an \textsc{ncg} is a partial function $\gamma\colon E\rightharpoonup V$ such that
+A (partial) \emph{configuration} of an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
 \begin{itemize}
 	\item
-for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$, and
+for every edge $e$, $\gamma(e)\in v(e)$ or (in the partial case) $\gamma(e)$ is undefined, and
 	\item
@@
 
-A \emph{reconfiguration step} $\gamma\sim\delta$ connects two configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.
+A \emph{reconfiguration step} $\gamma\sim\delta$ connects two (partial) configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.
 
@@
 
-[[ NOTE: decide on notation for steps and paths in permutation relations ]]
+The \emph{(partial) \textsc{ncg}-reconfiguration problem} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
+
+\begin{theorem}[\cite{demaine}]
+\textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+\end{theorem}
+
+\begin{proposition}
+Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+\end{proposition}
+
+\begin{proof}
+There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
+%
+Firstly, if $\gamma\sim\delta$ are partial configurations, they may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$.
+%
+Secondly, if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by re-assigning the values where they disagree.
+%
+\end{proof}
 
@@
 %
-This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\int G$.
+This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$.
 
@@
 \[
-	C = \big(\named{    \dagger'}1\parr\named{   1'}1\parr\dotso\parr\named{3k+1'}1\big)
-	\tn \big(\named{\downdagger'}1\parr\named{3k+2'}1\parr\dotso\parr\named{3n+3'}1\big)~.
+	C = \big(\named{\alt    \dagger}1\parr\named{\alt{   1}}1\parr\dotso\parr\named{\alt{3k+1}}1\big)
+	\tn \big(\named{\alt\downdagger}1\parr\named{\alt{3k+2}}1\parr\dotso\parr\named{\alt{3n+3}}1\big)~.
 \]
@@
 \[
-	\links(x) = x' \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
+	\links(x) = \alt x \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
 \]
@@
 	\begin{cases}
-			\dagger' & \text{if }k=i \\
-		\downdagger' & \text{if }k=j~.
+		\alt	\dagger & \text{if }k=i \\
+		\alt\downdagger & \text{if }k=j~.
 	\end{cases}
 \]
-There is also a natural linking for the sequent $W,\named\star 1,\named{1'}1,\dotsc,\named{3n+3'}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
+There is also a natural linking for the sequent $W,\named\star 1,\named{\alt 1}1,\dotsc,\named{\alt {3n+3}}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
 \[
@@
 		\star  & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
-		   x' & \text{otherwise }.
+		\alt x & \text{otherwise }.
 	\end{cases}
@@
 %
-Let the rightmost $1$-occurrence of each vertex-gadget $\itn v$ be named $v$, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$ named $e$:
+Let the rightmost $1$-occurrence of each vertex-gadget $\itn v$ be named $\alt v$, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$ named $\alt e$:
 \[	
-	\itn v = C\parr\dotso\parr C\parr \named v1 \qquad \itn e= W\tn\dotso\tn W\tn\named e\bot~.
+	\itn v = C\parr\dotso\parr C\parr \named{\alt v}1 \qquad \itn e= W\tn\dotso\tn W\tn\named{\alt e}\bot~.
 \]
-To define $\itn\gamma=\links$, firstly let
-\[
-	\links(e)=\gamma(e)~.
-\]
-Then successively for each edge $e$ and each weight element $W$ in $e$, if $\gamma(e)$ has a first free constraint element $C$, extend $\links$ to include the natural linking on $W,C$; otherwise, extend $\links$ by the natural linking on $W$ plus the first $3n+4$ free edge absorbers.
+To define $\itn\gamma$, firstly let $\itn\gamma(e)=\alt v$ where $\gamma(e)=v$.
+%
+Then successively for each edge $e$ and each weight element $W$ in $e$, if $\gamma(e)$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
 
@@
 \begin{definition}
-For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
+For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
 \end{definition}
@@
 \end{proof}
-
-%\begin{definition}
-%The interpretation $\itn\gamma$ of a configuration $\gamma$ for a graph $G$ is the set of proof nets for $\itn G$ satisfying the following constraint: if $\gamma(e)=v$ then $\itn e$ belongs to the empire of $\itn v$
-%\end{definition}

### 2014-01-10 main/s_level_0.tex
drawing the octopus roll

@@
 	\item
-A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=*$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
+A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
 
@@
 %
-The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,k)=k$; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
+The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
 

### 2014-01-10 main/scratch.tex
started Sections 3 and 4 - main definitions, lemmas, and proof ideas
drawing the octopus roll

@@
-\documentclass{article}
+\documentclass{robinminion}
 
@@
 
+\usepackage{pgffor}
+
 \graphicspath{{../notes/}}
 
-\makeTheoremDefs
+%\makeTheoremDefs
 
@@
 
+\tikzstyle{big1} = [draw,circle,minimum size=16pt,inner sep=0pt,font=\scriptsize]
+\tikzstyle{big_} = [big1,text=white,fill=black]
+\tikzstyle{big>} = [line width=3pt]
+
+\newcommand\octorollA{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big1] (a) at (0,0) {};
+	\node[big_] (d1) at (-8.5,4) {};
+	\node[big_] (d2) at (-6  ,4) {};
+	\node[big_] (d3) at (-3.5,4) {};
+	\draw[rounded corners] (-10,3) rectangle (-2,5);
+	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+	\node[big_] (e1) at ( 3.5,4) {};
+	\node[big_] (e2) at ( 6  ,4) {};
+	\node[big_] (e3) at ( 8.5,4) {};
+	\draw[rounded corners] (10,3) rectangle (2,5);
+	\draw (2,4)--(1,4) node[bullet] (e) {};
+	\node[big1] (v1) at (-2,8) {};
+	\node[big1] (v2) at ( 2,8) {};
+	\draw[rounded corners] (-3.5,7) rectangle (-0.5,9);
+	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+	\draw (-0.5,8)--(0.5,8);
+	\node[circ] (v) at (0,6) {};
+	%
+	\begin{scope}[thepink,->]
+		\draw (e)--(v);\draw (d)--(v);
+		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
+		\draw[big>,bend right=10] (e1) to (a);  \draw[big>,bend right=20] (e2) to (a);  \draw[big>, bend right=30] (e3) to (a);
+	\end{scope}
+  \end{tikzpicture}
+}
+\newcommand\octorollB[1]{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[circ] (a1a) at (0,2) {}; \node[big1] (a1) at (-2.5,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2.5,0) {};
+	\node[big_] (d1) at (-8.5,4) {};
+	\node[big_] (d2) at (-6  ,4) {};
+	\node[big_] (d3) at (-3.5,4) {};
+	\draw[rounded corners] (-10,3) rectangle (-2,5);
+	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
+	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
+	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
+	\draw[rounded corners] (10,3) rectangle (2,5);
+	\draw (2,4)--(1,4) node[bullet] (e) {};
+	\node[big1] (v1) at (-2,8) {};
+	\node[big1] (v2) at ( 2,8) {};
+	\draw[rounded corners] (-3.5,7) rectangle (-0.5,9);
+	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+	\draw (-0.5,8)--(0.5,8);
+	\node[circ] (v) at (0,6) {};
+	%
+	\begin{scope}[thepink,->]
+		\draw (e)--(v);
+	\SWITCH{#1}{1}{\draw (d)--(v);}\DEFAULT{\draw (d)--(a1a);}
+		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
+	\SWITCH{#1}
+	{3}{
+		\draw[bend left=15] (e1a) to (v1); \draw[bend left=15] (e2a) to (v2); \draw[bend left=15] (e3a) to (v2);
+		}
+	\DEFAULT{
+		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
+		}
+		\draw[big>,bend right=15] (e1) to (a1);  \draw[big>,bend right=15] (e2) to (a2);  \draw[big>, bend right=15] (e3) to (a3);
+	\end{scope}
+  \end{tikzpicture}
+}
+\newcommand\octorollC{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[circ] (a1a) at (0,2) {}; \node[big1] (a1) at (-2.5,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2.5,0) {};
+	\node[big_] (d1) at (-9,4) {};
+	\draw (-7.25,4) node[big_] (d2) {} -- (-6.25,4) node[bullet] (d2a) {};
+	\draw (-5,4) node[big_] (d3) {} -- (-3.5,4) node[big_] (d3a) {} -- (-2.5,4) node[bullet] (d3b) {};
+	\draw[rounded corners] (-10,3) rectangle (-2,5);
+	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+	\node[big_] (e1) at ( 3.5,4) {};
+	\node[big_] (e2) at ( 6  ,4) {};
+	\node[big_] (e3) at ( 8.5,4) {};
+	\draw[rounded corners] (10,3) rectangle (2,5);
+	\draw (2,4)--(1,4) node[bullet] (e) {};
+	\node[big1] (v1) at (-2,8) {};
+	\node[big1] (v2) at ( 2,8) {};
+	\draw[rounded corners] (-3.5,7) rectangle (-0.5,9);
+	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+	\draw (-0.5,8)--(0.5,8);
+	\node[circ] (v) at (0,6) {};
+	%
+	\begin{scope}[thepink,->]
+		\draw (e)--(v); \draw (d)--(a1a);
+		\draw[bend right=15] (d2a) to (v1); \draw[bend right=15] (d3b) to (v2);
+		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2) to (a1);
+		\draw[big>,bend left=20] (d3) to (a2); \draw[big>,bend left=20] (d3a) to (a3);
+		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v1);  \draw[big>, bend left=15] (e3) to (v2);
+	\end{scope}
+  \end{tikzpicture}
+}
+\newcommand\octorollD{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big1] (a1) at (0,0) {}; \node[circ] (a1a) at (0,2) {};
+	\node[big_] (d1) at (-8.5,4) {};
+	\node[big_] (d2) at (-6.25,4) {};
+	\draw (-4,4) node[big_] (d3a) {} -- (-3,4) node[bullet] (d3b) {};
+	\draw[rounded corners] (-10,3) rectangle (-2,5);
+	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+	\node[big_] (e1) at ( 3.5,4) {};
+	\node[big_] (e2) at ( 6  ,4) {};
+	\node[big_] (e3) at ( 8.5,4) {};
+	\draw[rounded corners] (10,3) rectangle (2,5);
+	\draw (2,4)--(1,4) node[bullet] (e) {};
+	\node[big1] (v1) at (-2,8) {};
+	\node[big1] (v2) at ( 2,8) {};
+	\draw[rounded corners] (-3.5,7) rectangle (-0.5,9);
+	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+	\draw (-0.5,8)--(0.5,8);
+	\node[circ] (v) at (0,6) {};
+	%
+	\begin{scope}[thepink,->]
+		\draw (e)--(v); \draw (d)--(a1a);
+		\draw[bend right=15] (d3b) to (v2);
+		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2) to (a1);
+		\draw[big>,bend left=20] (d3a) to (a1);
+		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v1);  \draw[big>, bend left=15] (e3) to (v2);
+	\end{scope}
+  \end{tikzpicture}
+}
+%
+%\octorollA
+%
+%\vskip80pt
+%
+%\octorollB1
+%
+%\vskip80pt
+%
+%\octorollB2
+%
+%\vskip80pt
+%
+%\octorollB3
+%
+%\vskip80pt
+
+\octorollC
+
+\vskip80pt
+
+\octorollD
+
+\vskip80pt
+
+%\octorollE
+
 \end{document}
+
+%\newcommand\octorollC{
+%  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+%	\node[circ] (a1a) at (0,1.5) {}; \node[big1] (a1) at (-2,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2,0) {};
+%	\draw (-9  ,4) node[bullet] (d1a) {} -- (-8  ,4) node[big_] (d1) {};
+%	\draw (-6.5,4) node[bullet] (d2a) {} -- (-5.5,4) node[big_] (d2) {};
+%	\draw (-4  ,4) node[bullet] (d3a) {} -- (-3  ,4) node[big_] (d3) {};
+%	\draw[rounded corners] (-10,3) rectangle (-2,5);
+%	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+%	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
+%	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
+%	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
+%	\draw[rounded corners] (10,3) rectangle (2,5);
+%	\draw (2,4)--(1,4) node[bullet] (e) {};
+%	\node[circ] (v1a) at (-4,8); \node[big1] (v1b) at (-3,8) {}; \node[big1] (v1c) at (-1.5,8) {};
+%	\node[big1] (v2) at  ( 2.5,8) {}; \node[big1] (v2) at ( 2.5,8) {};
+%	\draw[rounded corners] (-4.5,7) rectangle (-0.5,9);
+%	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+%	\draw (-0.5,8)--(0.5,8);
+%	\node[circ] (v) at (0,6) {};
+%	%
+%	\begin{scope}[thepink,->]
+%		\draw (e)--(v);\draw (d)--(v);
+%		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
+%		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
+%		\draw[big>,bend right=20] (e1) to (a1);  \draw[big>,bend right=20] (e2) to (a2);  \draw[big>, bend right=20] (e3) to (a3);
+%	\end{scope}
+%  \end{tikzpicture}
+%}
+
+\[
+	\big(\bigparr_{k\times c(v_i)}\big(\bigparr_{3i+2}1 \tn \bigparr_{3(n-i)+3}1\big) \big)\parr 1
+\]
+\[
+	\big(\bigotimes_{k\times w(e)}\big(\bigotimes_{3i+2}\bot\parr\bigotimes_{3(j-i)+1}\bot\parr\bigotimes_{3(n-j)+3}\bot\big)\big)\tn\bot
+\]
+
+\[
+	C = \bigparr(1^{3i+2}) \tn \bigparr(1^{3(n-i)+3})
+\]
+
+\[
+	\big(\bigparr C^{k\times c(v_i)} \big)\parr 1
+\]
+
+\[
+	W = \bigotimes(\bot^{3i+2})\parr\bigotimes(\bot^{3(j-i)+1})\parr\bigotimes(\bot^{3(n-j)+3}
+\]
+
+\[
+	\big(\bigotimes W^{k\times w(e)}\big)\tn\bot
+\]

### 2014-01-11 main/scratch.tex
more octopus roll diagrams

@@
-\documentclass{robinminion}
+\documentclass{beamer}
 
@@
 
-\newcommand\octorollA{
+\newcommand\octorollA[1]{
   \begin{tikzpicture}[x=5mm,y=-5mm,octo]
@@
 	\begin{scope}[thepink,->]
-		\draw (e)--(v);\draw (d)--(v);
-		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
-		\draw[big>,bend right=10] (e1) to (a);  \draw[big>,bend right=20] (e2) to (a);  \draw[big>, bend right=30] (e3) to (a);
+		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
+	\SWITCH{#1}
+	{1}{\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
+		\draw[big>,bend right=10] (e1) to (a);  \draw[big>,bend right=20] (e2) to (a);  \draw[big>, bend right=30] (e3) to (a);}
+	{2}{\draw[big>,bend left] (d1) to (a); \draw[big>,bend left=20] (d2) to (a); \draw[big>, bend left=20] (d3) to (a);
+		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);}
+	\DEFAULT{}
 	\end{scope}
@@
 	\begin{scope}[thepink,->]
-		\draw (e)--(v);
-	\SWITCH{#1}{1}{\draw (d)--(v);}\DEFAULT{\draw (d)--(a1a);}
+		\draw[bend left=15] (e) to (v);
+	\SWITCH{#1}{1}{\draw[bend right=15] (d) to (v);}\DEFAULT{\draw[bend left=15] (d) to (a1a);}
 		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
@@
 	\begin{scope}[thepink,->]
-		\draw (e)--(v); \draw (d)--(a1a);
+		\draw[bend left=15] (e) to (v); \draw[bend left=15] (d) to (a1a);
 		\draw[bend right=15] (d2a) to (v1); \draw[bend right=15] (d3b) to (v2);
@@
 		\draw[big>,bend left=20] (d3) to (a2); \draw[big>,bend left=20] (d3a) to (a3);
-		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v1);  \draw[big>, bend left=15] (e3) to (v2);
+		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);
 	\end{scope}
@@
 	\node[big_] (d1) at (-8.5,4) {};
-	\node[big_] (d2) at (-6.25,4) {};
-	\draw (-4,4) node[big_] (d3a) {} -- (-3,4) node[bullet] (d3b) {};
+	\draw (-6,4) node[big_] (d2a) {} -- (-5,4) node[bullet] (d2b) {};
+	\node[big_] (d3) at (-3.5,4) {};
 	\draw[rounded corners] (-10,3) rectangle (-2,5);
@@
 	\begin{scope}[thepink,->]
-		\draw (e)--(v); \draw (d)--(a1a);
-		\draw[bend right=15] (d3b) to (v2);
-		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2) to (a1);
-		\draw[big>,bend left=20] (d3a) to (a1);
-		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v1);  \draw[big>, bend left=15] (e3) to (v2);
+		\draw[bend left=15] (e) to (v); \draw[bend left=15] (d) to (a1a);
+		\draw[bend right=15] (d2b) to (v1);
+		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2a) to (a1); \draw[big>,bend left=20] (d3) to (a1);
+		\draw[big>,bend left=15] (e1) to (v1);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);
 	\end{scope}
@@
 }
+
+\newcommand\octorollE[1]{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big1] (a1) at (0,0) {}; \node[circ] (a1a) at (0,2) {};
+	\node[big_] (d1) at (-8.5,4) {};
+	\draw (-6,4) node[big_] (d2a) {} -- (-5,4) node[bullet] (d2b) {};
+	\node[big_] (d3) at (-3.5,4) {};
+	\draw[rounded corners] (-10,3) rectangle (-2,5);
+	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+	\draw (2.75,4) node[bullet] (e1a) {} -- (3.5,4) node[bullet] (e1b) {} -- (4.5,4) node[big_] (e1c) {};
+	\node[big_] (e2) at ( 6.5,4) {};
+	\node[big_] (e3) at ( 8.5,4) {};
+	\draw[rounded corners] (10,3) rectangle (2,5);
+	\draw (2,4)--(1,4) node[bullet] (e) {};
+	\node[circ] (v1a) at (-3.25,8) {}; \node[circ] (v1b) at (-2.5,8) {}; \node[big1] (v1c) at (-1.5,8) {};
+	\node[big1] (v2) at ( 2,8) {};
+	\draw[rounded corners] (-4,7) rectangle (-0.5,9);
+	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+	\draw (-0.5,8)--(0.5,8);
+	\node[circ] (v) at (0,6) {};
 	%
-%\octorollA
-%
-%\vskip80pt
-%
-%\octorollB1
-%
-%\vskip80pt
-%
-%\octorollB2
-%
-%\vskip80pt
-%
-%\octorollB3
-%
-%\vskip80pt
+	\begin{scope}[thepink,->]
+		\draw[bend left=15] (e) to (v);
+	\SWITCH{#1}
+	{1}{
+		\draw[bend left=15] (d) to (a1a);
+		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (v1a); \draw[bend left=10] (e1b) to (v1b);
+		}
+	{2}{
+		\draw[bend left=15] (d) to (a1a);
+		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend left=10] (e1b) to (v1b);
+		}
+	{3}{
+		\draw[bend right=15] (d) to (v1b);
+		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend left=10] (e1b) to (v1b);
+		}
+	{4}{
+		\draw[bend right=15] (d) to (v1b);
+		\draw[bend right=15] (d2b) to (v1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e1b) to (v1a);
+		}
+	{5}{
+		\draw[bend right=15] (d) to (v1b);
+		\draw[bend left=25] (d2b) to (a1a); \draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e1b) to (v1a);
+		}
+	{6}{
+		\draw[bend right=15] (d) to (v1b);
+		\draw[bend left=25] (d2b) to (a1a); \draw[bend left=15] (e1a) to (v1b); \draw[bend right=15] (e1b) to (v1a);
+		}
+	{7}{
+		\draw[bend right=15] (d) to (v);
+		\draw[bend left=25] (d2b) to (a1a); \draw[bend left=15] (e1a) to (v1b); \draw[bend right=15] (e1b) to (v1a);
+		}
+	\DEFAULT{}
+		\draw[big>,bend left] (d1) to (a1); \draw[big>,bend left=20] (d2a) to (a1); \draw[big>,bend left=20] (d3) to (a1);
+		\draw[big>,bend left=15] (e1c) to (v1c);  \draw[big>,bend left=15] (e2) to (v2);  \draw[big>, bend left=15] (e3) to (v2);
+	\end{scope}
+  \end{tikzpicture}
+}
 
+\begin{frame}
+	\octorollA1
+\end{frame}
+
+\begin{frame}
+	\octorollB1
+\end{frame}
+
+\begin{frame}
+	\octorollB2
+\end{frame}
+
+\begin{frame}
+	\octorollB3
+\end{frame}
+
+\begin{frame}
 	\octorollC
+\end{frame}
 
-\vskip80pt
+\begin{frame}
+	\octorollD
+\end{frame}
 
-\octorollD
+\begin{frame}
+	\octorollE1
+\end{frame}
 
-\vskip80pt
+\begin{frame}
+	\octorollE2
+\end{frame}
 
-%\octorollE
+\begin{frame}
+	\octorollE3
+\end{frame}
+
+\begin{frame}
+	\octorollE4
+\end{frame}
+
+\begin{frame}
+	\octorollE5
+\end{frame}
+
+\begin{frame}
+	\octorollE6
+\end{frame}
+
+\begin{frame}
+	\octorollE7
+\end{frame}
+
+\begin{frame}
+	\octorollA2
+\end{frame}
 
@@
 %	\begin{scope}[thepink,->]
-%		\draw (e)--(v);\draw (d)--(v);
+%		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
 %		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);

### 2014-01-12 main/s_level_0.tex
added octopus roll lemma

@@
 
+\begin{proposition}
+\label{prop:parity determines equivalence}
+Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+\end{proposition}
+
 \begin{theorem}
@@
 %
-For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:level0 max binary} and~\ref{prop:level0 min binary} the equivalence of two nets is determined by their relative parity.
+For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
 %
@@
 \end{proof}
+
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net where $\links(a)=(u)$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $b-v$ and $x-c$.
+%
+Then $\links\sim\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{proof}
+\[
+	\vc{\doubleExchange uvxy}
+	\sim
+	\vc{\doubleExchange uyxy}
+	\sim
+	\vc{\doubleExchange uyxu}
+	\sim
+	\vc{\doubleExchange vyxu}
+	\sim
+	\vc{\doubleExchange vyyu}
+	\sim
+	\vc{\doubleExchange vuyu}
+	\sim
+	\vc{\doubleExchange vuyx}
+\]
+\end{proof}

### 2014-01-12 main/s_level_2.tex
added octopus roll lemma

@@
 
-The interpretation $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
-%
-Let the rightmost $1$-occurrence of each vertex-gadget $\itn v$ be named $\alt v$, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$ named $\alt e$:
+The rightmost $1$-occurrence of each vertex-gadget $\itn v$, named $\alt v$ below, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$, named $\alt e$, will be called the \emph{indicator vertices} of $\itn v$ and $\itn e$.
 \[	
@@
 \]
-To define $\itn\gamma$, firstly let $\itn\gamma(e)=\alt v$ where $\gamma(e)=v$.
+
+\begin{definition}
+\label{def:configuration interpretation}
+The \emph{interpretation} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
 %
-Then successively for each edge $e$ and each weight element $W$ in $e$, if $\gamma(e)$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
+Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
+%
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
+\end{definition}
 
@@
 \subsection{Completeness}
+
+In a proof net for $\itn G$, an edge-gadget $\itn e$ that is in the empire of an appropriate vertex-gadget $\itn v$ is \emph{naturally linked} if the indicator of $\itn e$ connects to the indicator of $\itn v$, and each weight element $W$ of $\itn e$ is either naturally linked to a constraint element $C$ in $\itn v$ or linked only to edge-absorbers.
+
+\begin{lemma}
+\label{lem:octopus roll}
+In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is naturally linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to edge-absorbers $\bot^n$, then there is a net $\links'\sim\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
+\end{lemma}
+
+\begin{proof}
+Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
+%
+We will illustrate the path of permutations for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
+%
+\begin{enumerate}
+	\item
+The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
+\[
+	\octorollA1
+\]
+	\item
+The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
+\[
+	\octorollB2
+\]
+	\item
+Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
+\[
+	\octorollB3
+\]
+	\item\label{item:exchange added}
+There are subnets over the sub-sequents $A,B,X,D,\bot^m$ and $C,Y,E,F,\bot^k$.
+%
+These subnets may be rewired so that $D\parr E\parr F$ is naturally linked to $X\tn Y$: by Proposition~\ref{prop:parity determines equivalence}, the resulting subnets are equivalent as long as their parity is preserved.
+%
+Two links from $C$ to $X$ should remain exchanged, compared to the natural linking, for step \ref{item:exchange needed} below.
+%
+The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+\[
+	\octorollC
+\]
+	\item
+The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
+\[
+	\octorollD1
+\]
+	\item\label{item:exchange needed}
+The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
+%
+Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
+\[
+	\octorollD2
+\]
+	\item
+The link from $i$ may be re-attached to $v$ to yield the final configuration.
+\[
+	\octorollA2
+\]
+\end{enumerate}
+\end{proof}
 

### 2014-01-13 main/s_level_2.tex
final lemma completing the puzzle

@@
 
+An edge-gadget $\itn e$ is \emph{free} if each of its weight elements is linked only to edge-absorbers.
+
+\begin{lemma}
+If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
+\end{lemma}
+
+\begin{proof}
+Let $e_0$ be the indicator vertex of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
+%
+Let $e_1$ and $e_2$ be arbitrary other $\bot$-occurrences in $\itn e$.
+
+\begin{enumerate}
+
+	\item
+To permute two edge-absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.
+
+	\item
+To reinstate $e_0$ as the connection between $\itn e$ and the remainder of the proof net, either perform another permutation as above, or permute $v$ and $w$ twice again, once exchanging the targets of $e_1$ and $e_2$, and once exchanging the targets of $e_2$ and $e_0$.
+
+	\item
+To exchange an edge-absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, and attach $e_0$ to $w$, attach $d$ to $v$.
+%
+At this point, $e_1$ forms the only connect between $\itn e$ and the remainder of the proof net; to reinstate $e_0$ in this role, do as above, producing a net effect of cycling the targets of $e_1$, $e_2$, and $d$.
+
+	\item
+Finally, to permutate edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
+%
+Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to permute $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
+%
+Perform a second permutation to return $d_0$ and $d_1$ their proper edge-absorbers.
+
+\end{enumerate}
+
+In each case, if one of the edge-absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
+
+\end{proof}
+
 \begin{lemma}

### 2014-01-14 main/LICS.tex
made one file for LICS

\documentclass[conference]{IEEEtran}

\usepackage{amssymb,amsthm,amsmath}
\usepackage{microtype}
%\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[round]{natbib}
\usepackage{mllequiv,willemtools}

\graphicspath{{../notes/}}

\makeTheoremDefs

\author{
  \IEEEauthorblockN{Willem Heijltjes}
  \IEEEauthorblockA{
  		University of Bath \\
		Claverton Down \\
		Bath BA2~7AY\\
		w.b.heijltjes@bath.ac.uk
	}
\and
  \IEEEauthorblockN{Robin Houston}
  \IEEEauthorblockA{Kiln Enterprises}
}

\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete}

\begin{document}

\maketitle

\begin{abstract}
MLL proof equivalence is the problem of deciding whether two proofs in multiplicative linear logic are related by a series of inference permutations.
%
It is also known as the word problem for $*$-autonomous categories.
%
Previous work has shown the problem to be equivalent to a rewiring problem on proof nets, which are not canonical for full MLL due to the presence of the two units.
%
Drawing from recent work on reconfiguration problems, in this paper it is shown that MLL proof equivalence is PSPACE-complete, using a reduction from Nondeterministic Constraint Logic.
%
The result rules out the existence of a satisfactory notion of proof nets for MLL with units (under current complexity assumptions).
\end{abstract}

\section{MLL}

\begin{figure}
%%\noindent
%\fbox{\MLLrule b}
%\hfill\fbox{\MLLrule 1}
%\hfill\fbox{\MLLrule p}
%\hfill\fbox{\MLLrule t}
%\hfil
\[
\begin{array}{llll}
	\MLLrule b
 &	\MLLrule 1
 &	\MLLrule p
 &	\MLLrule t
\end{array}
\]
\caption{Inference rules for unit-only \MLL}
\label{fig:MLL}
\end{figure}

\begin{figure}
\[
	\vc{\MLLperm{bb1}} \perm \vc{\MLLperm{bb2}}
\qquad
	\vc{\MLLperm{bp1}} \perm \vc{\MLLperm{bp2}}
\]
\[
	\vc{\MLLperm{bt1}} \perm \vc{\MLLperm{bt2}} \perm \vc{\MLLperm{bt3}}
\]
\[
	\vc{\MLLperm{pp1}} \perm \vc{\MLLperm{pp2}}
\]
\[
	\vc{\MLLperm{pt1}} \perm \vc{\MLLperm{pt2}}
\]
\[
	\vc{\MLLperm{tt1}} \perm \vc{\MLLperm{tt2}}
\]
\caption{Permutations}
\label{fig:permutations}
\end{figure}

The formulae of unit-only multiplicative linear logic are given by the following grammar.
%
\[
	A,B,C \coloneq \bot \mid 1 \mid A\parr B \mid A\tn B
\]
%
The connectives $\tn$ and $\parr$ will be considered up to associativity, and \emph{duality} $\dual A$ is via DeMorgan.
%
A \emph{sequent} $\Gamma,\Delta$ will be a multiset of formulae.
%
Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names $N$, e.g.\
$\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot$.
%
This allows to 1) avoid using the notion of \emph{occurrence}, and instead refer to subformulae by the name of their root connective, as e.g.\ $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
%
Names will mostly be left implicit.

Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}.
%
The names of connectives are preserved through inferences.
%
Only cut-free proofs are considered, and no cut-rule is added.
%
\emph{Permutations} of inference rules are displayed in Figure~\ref{fig:permutations}; the symmetric variants of the last two permutations, \emph{par-tensor} and \emph{tensor-tensor}, have been omitted.

\begin{definition}
\label{def:equivalence}
%
\emph{Equivalence} of proofs $(\perm)$ in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
%
\emph{\MLL\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
%
\end{definition}

The motivation to consider proofs up to equivalence is three-fold.
%
Firstly, there is the strong intuition that the order of permutable inferences does not contribute to the essential content of the proof.
%
Secondly, a technical motivation is that cut-elimination in \MLL\ incorporates permutation steps, and composition via cut-elimination is only associative up to permutations.
%
Thirdly, equivalent proofs are identified in natural models of multiplicative linear logic such as coherence spaces, and in the categorical semantics of \MLL, $\star$-autonomous categories.

In one of several possible definitions, a \emph{$\star$-autonomous category} \citep{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
%
\begin{itemize}

	\item
	a \emph{duality}, a contravariant functor $\dual-$ such that $A\cong\dual*A$, and

	\item
	\emph{closure}, an adjunction $-\tn B \dashv \dual{(B\tn\dual-)}$ for any object $B$,

\end{itemize}
%
satisfying natural coherence conditions.
%
%The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
The category with as objects unit-only \MLL-formulae and as morphisms $A\to B$ the equivalence classes of proofs of $\dual A\parr B$, denoted $\textsc{mll}(\emptyset)$, is a $\star$-autonomous category.
%
The present formulation of formulae induces two forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, while
%, one-sided sequents mean the closure adjunction is an equivalence of categories, 
associativity is an identity by decree.
%
Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two term representations denote the same morphism.

%The \emph{free $\star$-autonomous completion} $\star$-\textsc a$(\mathcal C)$ of a category $\mathcal C$ is characterised by a functor $i\colon\mathcal C\to\star$-\textsc a$(\mathcal C)$ such that any functor $\mathcal C\to \mathcal D$ into a $\star$-autonomous cateogry $\D$ factors uniquely (up to canonical isomorphism) as the composition of $i$ with a functor $\star$-\textsc a$(\mathcal C)\to\D$ preserving $\star$-autonomous structure.
%%
%\[
%\begin{tikzpicture}[auto]
%	\node (C) at (0,0) {$\mathcal C$};
%	\node (*AC) at (2,0) {$\star$-\textsc a$(\mathcal C)$};
%	\node (D) at (1,1) {$\mathcal D$};
%	\draw [->] (C) -- node {$i$} (*AC);
%	\draw [->] (C) -- (D);
%	\draw [->,dashed] (*AC) -- node {$!$} (D);
%\end{tikzpicture}
%\]
%%

\subsection{Proof nets}

A partial solution to the \MLL\ proof equivalence problem is provided by proof nets.

\begin{definition}
\label{def:proof nets}
%
For a sequent $\Gamma$,
\begin{itemize}

	\item
	a \emph{linking} $\links$ is a function from the names of $\bot$-subformulae to the names of $1$-subformulae,

	\item
	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$, with for every subformula $\named aA\named c\tn\named bB$ the edges $a-c$ and $b-c$, for every subformula $\named aA\named c\parr\named bB$ either the edge $a-c$ or the edge $b-c$, and for every subformula $\named a\bot$ the edge $a-\links(a)$,

 	\item
	a \emph{proof net} $\links$ or $(\Gamma,\links)$ is a linking $\links$ such that every switching graph is acyclic and connected.

\end{itemize}
\end{definition}

\noindent
An edge $a-\links(a)$ in a proof net or switching graph is a \emph{link} or \emph{jump}.

\begin{definition}
\label{def:proof net equivalence}
%
A \emph{permutation} between proof nets is the redirection of exactly one link.
%
\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the congruence generated by permutations.
%
\end{definition}

\noindent
There is no canonical interpretation of a proof as a proof net, since the introduction rule for $\bot$ in proofs joins a $\bot$-formula to a sequent, rather than a formula.

\begin{definition}
\label{def:proofs to nets}
%
The relation $(\toNet)$ interprets a proof $\Pi$ for a sequent $\Gamma$ by a linking $\links$ as follows:
% 
$\Pi\toNet\links$ if for each $\named a\bot$ in $\Gamma$, if $\Delta$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Delta$.
\[
	\infer[\MLLlabel b]{\Delta,\named a\bot}{\Delta}
\]
%
\end{definition}

\begin{proposition}[\citeauthor{DR89}, \citeyear{DR89}]
\label{prop:correctness and sequentialisation}
%
For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
%
For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
%
\end{proposition}

\noindent
Proof nets are canonical representations of proofs in the absence of units: they factor out the permutations among tensor- and par-inferences, which are the last three permutations in Figure~\ref{fig:permutations}.
%
Equivalence of proof nets is generated by the remaining equations, the permutations on $\bot$-introduction.

\begin{proposition}[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
\label{prop:proof nets work}
%
For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$ such that $\Pi\toNet\links$ and $\Pi'\toNet\links'$, $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
%
\end{proposition}

\noindent
\MLL\ proof equivalence is the problem of deciding equivalence of proof nets.

\subsection{Notation}

We will use a concise diagrammatic notation for sequents and proof nets.
%
The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
%
A tensor is represented by a line connecting both subformulae, and a par by juxtaposition: if $A$ and $B$ are represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
and \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}},
%
then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
%
A tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
%
Boxes play the role of parentheses around par-formulae, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}

\noindent For example, this sequent
\[ \vdash \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, 1, \{[(1\parr 1\parr 1)\tn(1\parr 1\parr 1)]\parr 1\parr (\bot\tn\bot\tn\bot)\parr 1\}\tn\bot \]
could be drawn like this:
\begin{center}\includegraphics[scale=0.75]{example-sequent.pdf}\end{center}

\noindent We represent a proof net by drawing an arrow from each $\bullet$ to some $\circ$. For example, one proof net on the above sequent is
\begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}

%NOTE: need 'octopus' terminology here

%NOTE: will we need to count arms often enough to make it worthwile to write $|\Gamma|_\bot$ for the number of $\bot$-occurrences in a sequent $\Gamma$?

\section{Equivalence in the absence of $~\protect\parr$}

Let a \emph{1-alternation} sequent be one over formulae of the form $1$ or $\bot\tn\ldots\tn\bot$, where the number of $\bot$-subformulae is at least 2.
%
Such a sequent is inhabited exactly when the number of formulae in the sequent is one greater than the total number of $\bot$-subformulae it contains.
%
An inhabited 1-alternation sequent with only one tensor-formula, i.e.\ a sequent of the form $\1,\ldots,\1,\bot\tn\ldots\tn\bot$ with $n$ $\bot$-subformulae and $n$ $1$-subformulae, will admit $n!$ different proof nets, each with $n$ links.
%
Since no link can re-attach, its equivalence classes are singletons.

\begin{proposition}
\label{prop:level0 max binary}
%
For a 1-alternation sequent with at least two tensor-formulae there are at most two equivalence classes of proof nets.
%
\end{proposition}

%
%\begin{figure}[p]
%\[
%\begin{array}{ccc}
%	\netA 1213 & \perm	& \netA 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 1223 &		& \netA 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 1323 &		& \netA 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 1321 &		& \netA 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 2321 &		& \netA 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 2331 & \perm	& \netA 2131
%\end{array}
%\qquad
%\begin{array}{ccc}
%	\netA 1312 & \perm	& \netA 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 2312 &		& \netA 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 2313 &		& \netA 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 2113 &		& \netA 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 2123 &		& \netA 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
%	\netA 3123 & \perm	& \netA 3121
%\end{array}
%\]
%\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
%\label{fig:2x12 nets}
%\end{figure}

\begin{IEEEproof}
%
It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
%
For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
\[
	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
\]
It has two equivalence classes, of 12 proof nets each.
%
(Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.)

%, displayed in Figure~\ref{fig:2x12 nets}.

For the inductive step, let $\Gamma$ be the following sequent.
\[
	\Delta,A\tn\named a\bot,\named z\1
\]
There are two cases: 1) where $A$ is a tensor-formula, and 2) where $A$ is $\bot$ and where, for the induction hypothesis to apply, $\Delta$ contains at least two tensor-formulae.
%
For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named z1$, and is the only link to do so.
%
This reduces equivalence on $\Gamma$ to equivalence on $\Delta,A$ in case 1, and on $\Delta$ in case 2, so that the induction hypothesis applies.

In constructing $\links'$, since the proof net must be connected, there is a path from $a$ to $z$.
%
We will consider only the jumps on this path, not any other edges.
%
There are four cases.

\begin{enumerate}
	\item
The path consists of exactly the jump $\edge az$.
%
Let $\edge by$ be a jump from a $\named b\bot$ in $A$; then $\links'$ is obtained from $\links$ by changing: $\links'(e)=y$  for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$.

	\item
The path starts with the jump $\edge ax$ (and $x\neq z$).
%
Let $\edge by$ be a jump from a $\named b\bot$ in $A$, and let the path end with the jumps $\edge wc$ and $\edge dz$, where $\named c\bot$ and $\named d\bot$ are in the same tensor-formula $B$.
%
Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$, including $d$.
%
These changes are illustrated as permutations below.
%
\[
	\netB xywz \perm \netB zywz \perm \netB zywy
\]

	\item
The path consists of exactly one jump $\edge bz$ from a $\named b\bot$ in $A$ (and $b\neq a$).
%
Let $\links(a)=y$.
%
Choose a jump $\edge cw$ from $\named c\bot$ in $A$ such that there is another $\edge dw$ from $\named d\bot$ in a formula $B$ (not excluding the possibilities $c=b$ and $c=a$).
%
Let $\edge ex$ be a further jump from $\named e\bot$ in $B$.
%
Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, $\links'(d)=x$, $\links'(e)=y$, and $\links'(f)=x$ for each $f$ (including $b$) such that $\links(f)=z$ and $f\neq a$.
%
These changes are exhibited as a series of permutations below, from top left to bottom left (note that the jump from $d$ moves twice).
%
\[
\begin{array}{ccccc}
	\netC yzwx & \perm & \netC yzzx & \perm & \netC yxzx
	\\ &&&& \vperm \\
	\netC zxxy & \perm & \netC zxzy & \perm & \netC yxzy
\end{array}
\]

	\item
The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
%
Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
%
Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
%
This is illustrated below.
\end{enumerate}
%
\[
	\kern-1pt \netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw \kern-1pt 
\]
%
\end{IEEEproof}

\begin{proposition}
\label{prop:level0 may-connect path}
%
For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
%
\begin{itemize}
	\item
The edge $\edge ab$ can be permuted to $\edge ac$.
	\item
There is a path from $b$ to $c$ not passing through $a$.
	\item
The path from $a$ to $c$ starts with the jump $a-b$.
\end{itemize} 
\end{proposition}

If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
%
By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.

Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
%
\begin{itemize}

	\item
One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.

	\item
A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.

\end{itemize}
%
The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.

A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
%
\begin{definition}
\label{def:combinatorial permutation}
To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
\[
	\prm(k) = 
	\begin{cases}
		i				& \text{ if $(i,k)$ may connect to $*$; and}
	\\	\links(i,k)		& \text{ otherwise.}
	\end{cases}
\]
The \emph{parity} of $\links$ is the parity of its permutation.
\end{definition}

To see that $\prm$ is injective, consider the following.
\begin{itemize}
	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Proposition~\ref{prop:level0 may-connect path}).
	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
\end{itemize}

\begin{proposition}
\label{prop:level0 min binary}
A permutation on a net $\links$ preserves its parity. 
\end{proposition}

\begin{IEEEproof}
Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
%
There are two cases, depending on whether $(i,k)$ may connect to $*$.
%
If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
%
Then the permutation of $\links'$ is that of $\links$.

If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
\[
	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
\]
Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
%
On the relevant domain, this gives the following permutation for $\links$.
\[
\left(\begin{array}{ccccccc}
	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
\end{array}\right)
\]
In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
%
The permutation $\prm[\links']$ is the following.
\[
\left(\begin{array}{ccccccc}
	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
\end{array}\right)
\]
The parity of both permutations is the same if and only if the relative permutation, below, is even.
\[
\left(\begin{array}{ccccccc}
	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
\end{array}\right)
\]
This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
%
\end{IEEEproof}

\begin{proposition}
\label{prop:parity determines equivalence}
Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
\end{proposition}

\begin{theorem}
\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
\end{theorem}

\begin{IEEEproof}
For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
%
For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
%
Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
%
This yields a linear-time algorithm.
%
\end{IEEEproof}

\begin{lemma}
\label{lem:double exchange}
Let $\links$ be a proof net where $\links(a)=(u)$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $b-v$ and $x-c$.
%
Then $\links\sim\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
\end{lemma}

\begin{IEEEproof}
\[
	\vc{\doubleExchange uvxy}
	\sim
	\vc{\doubleExchange uyxy}
	\sim
	\vc{\doubleExchange uyxu}
	\sim
	\vc{\doubleExchange vyxu}
	\sim
	\vc{\doubleExchange vyyu}
	\sim
	\vc{\doubleExchange vuyu}
	\sim
	\vc{\doubleExchange vuyx}
\]
\end{IEEEproof}

\section{Par}

\begin{definition}
A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
\end{definition}

\begin{definition}
A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
\end{definition}

The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
%
A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
%
In a proof net, the \emph{kingdom} and the \emph{empire} of a par are respectively its smallest and largest scope.

The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
%
In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$ and re-attaching all arcs connecting to removed vertices to $v$.
%

[[ ADD ILLUSTRATED EXAMPLE ]]

%
The contraction of scopes may replace the switching condition as a correctness criterion.
%
The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.

\begin{proposition}
\label{prop:scoping correctness}
A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:

\begin{enumerate}
	\item
sub-sequents are strictly nested: if $\named w\parr$ occurs in $s(v)$ then $s(w)<s(v)$; and
	\item
for each $\named v\parr$, the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents $s(w)$ are contracted.
\end{enumerate}

\end{proposition}

\begin{IEEEproof}
For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
%
For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
\[
	\infer{\Delta,A\named v\parr B}{\Delta,A,B}
\]
\end{IEEEproof}

[[ IDEA: the following could help simplify octopus-arithmetic ]]

\begin{definition}
The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
%
A sequent is \emph{balanced} if its balance is zero.
\end{definition}

An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.

An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]

\section{Proof nets and constraint graphs}

[[ NOTE: we should decide on notation for steps versus paths in permutation relations ]]

\begin{definition} 
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set $E$ of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.

A (partial) \emph{configuration} of an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$, $\gamma(e)\in v(e)$ or (in the partial case) $\gamma(e)$ is undefined, and
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

A \emph{reconfiguration step} $\gamma\sim\delta$ connects two (partial) configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.

\end{definition}

The \emph{(partial) \textsc{ncg}-reconfiguration problem} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

\begin{theorem}[\cite{demaine}]
\textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
\end{theorem}

\begin{proposition}
Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
\end{proposition}

\begin{IEEEproof}
There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
Firstly, if $\gamma\sim\delta$ are partial configurations, they may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$.
%
Secondly, if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by re-assigning the values where they disagree.
%
\end{IEEEproof}

For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints, $\sum_{v\in V}c(v)$, and the sum of all edge weights, $\sum_{e\in E}w(e)$.

Let $A^n$ denote the sequent of $n$ copies of a formula $A$, and for a sequent $\Gamma=A_1,\dotsc,A_n$ let $\bigotimes\Gamma=A_1\tn\dotso\tn A_n$ and $\bigparr\Gamma=A_1\parr\dotso\parr A_n$.

\begin{definition}
\label{def:graph interpretation}
The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
%
Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.

The interpretation of a vertex $v_k$ is the formula
\[
	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
\]
where each \emph{constraint element} $C$ is the formula
\[
	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
\]

The interpretation of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
\[
	\itn{e} = \bigotimes\big(W^{m\times w(e)}\big)\tn\bot
\]
where each \emph{weight element} $W$ is the formula
\[
	W = \bigotimes\big(\bot^{3i+2}\big)\parr\bigotimes\big(\bot^{3(j-i)+1}\big)\parr\bigotimes\big(\bot^{3(n-j)+3}\big)
\]

The interpretation of the graph $G$ is the sequent
\[
	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
\]
where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.

\end{definition}

In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
%
This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$.

For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
\[
	W =  \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big)
	\parr\big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
	\parr\big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
\]
and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
\[
	C = \big(\named{\alt    \dagger}1\parr\named{\alt{   1}}1\parr\dotso\parr\named{\alt{3k+1}}1\big)
	\tn \big(\named{\alt\downdagger}1\parr\named{\alt{3k+2}}1\parr\dotso\parr\named{\alt{3n+3}}1\big)~.
\]
There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
\[
	\links(x) = \alt x \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
\]
\[
	\links(\ddagger)=
	\begin{cases}
		\alt	\dagger & \text{if }k=i \\
		\alt\downdagger & \text{if }k=j~.
	\end{cases}
\]
There is also a natural linking for the sequent $W,\named\star 1,\named{\alt 1}1,\dotsc,\named{\alt {3n+3}}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
\[
	\links(x)=
	\begin{cases}
		\star  & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
		\alt x & \text{otherwise }.
	\end{cases}
\]

\begin{proposition}
\label{prop:element linkings}
\begin{enumerate}
	\item
Given a vertex $v$ and an appropriate edge $e$, for a constraint element $C$ in $\itn v$ and a weight element $W$ in $\itn e$ the natural linking for the sequent $W,C$ is a proof net.
	\item
Given a weight element $W$ for a graph with $|V|=n$, the natural linking for the sequent $W,1^{3n+4}$ is a proof net.
\end{enumerate}
\end{proposition}

The rightmost $1$-occurrence of each vertex-gadget $\itn v$, named $\alt v$ below, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$, named $\alt e$, will be called the \emph{indicator vertices} of $\itn v$ and $\itn e$.
\[	
	\itn v = C\parr\dotso\parr C\parr \named{\alt v}1 \qquad \itn e= W\tn\dotso\tn W\tn\named{\alt e}\bot~.
\]

\begin{definition}
\label{def:configuration interpretation}
The \emph{interpretation} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
%
Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
%
Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
\end{definition}

\begin{proposition}
If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
\end{proposition}

\begin{IEEEproof}
Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
%
The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its natural linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
%
The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the edge-absorbers within scopes of weight elements inside $\itn e$.
%
Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
%
After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the special $\named v1$ of $\itn v$, thus forming a tree.
\end{IEEEproof}

%------------------------------------------------------------------------------------------------

\subsection{Completeness}

In a proof net for $\itn G$, an edge-gadget $\itn e$ that is in the empire of an appropriate vertex-gadget $\itn v$ is \emph{naturally linked} if the indicator of $\itn e$ connects to the indicator of $\itn v$, and each weight element $W$ of $\itn e$ is either naturally linked to a constraint element $C$ in $\itn v$ or linked only to edge-absorbers.

\begin{lemma}
\label{lem:octopus roll}
In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is naturally linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to edge-absorbers $\bot^n$, then there is a net $\links'\sim\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
\end{lemma}

\begin{IEEEproof}
Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
%
We will illustrate the path of permutations for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
%
\begin{enumerate}
	\item
The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
\[
	\octorollA1
\]
	\item
The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
\[
	\octorollB2
\]
	\item
Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
\[
	\octorollB3
\]
	\item\label{item:exchange added}
There are subnets over the sub-sequents $A,B,X,D,\bot^m$ and $C,Y,E,F,\bot^k$.
%
These subnets may be rewired so that $D\parr E\parr F$ is naturally linked to $X\tn Y$: by Proposition~\ref{prop:parity determines equivalence}, the resulting subnets are equivalent as long as their parity is preserved.
%
Two links from $C$ to $X$ should remain exchanged, compared to the natural linking, for step \ref{item:exchange needed} below.
%
The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
\[
	\octorollC
\]
	\item
The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
\[
	\octorollD1
\]
	\item\label{item:exchange needed}
The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
%
Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
\[
	\octorollD2
\]
	\item
The link from $i$ may be re-attached to $v$ to yield the final configuration.
\[
	\octorollA2
\]
\end{enumerate}
\end{IEEEproof}

An edge-gadget $\itn e$ is \emph{free} if each of its weight elements is linked only to edge-absorbers.

\begin{lemma}
\label{lem:permute edge-absorbers}
If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
\end{lemma}

\begin{IEEEproof}
Let $e_0$ be the indicator vertex of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
%
Let $e_1$ and $e_2$ be arbitrary other $\bot$-occurrences in $\itn e$.

\begin{enumerate}

	\item
To permute two edge-absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.

	\item
To reinstate $e_0$ as the connection between $\itn e$ and the remainder of the proof net, either perform another permutation as above, or permute $v$ and $w$ twice again, once exchanging the targets of $e_1$ and $e_2$, and once exchanging the targets of $e_2$ and $e_0$.

	\item
To exchange an edge-absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, and attach $e_0$ to $w$, attach $d$ to $v$.
%
At this point, $e_1$ forms the only connect between $\itn e$ and the remainder of the proof net; to reinstate $e_0$ in this role, do as above, producing a net effect of cycling the targets of $e_1$, $e_2$, and $d$.

	\item
Finally, to permute edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
%
Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to permute $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
%
A second such exchange is needed to re-attach $d_0$ and $d_1$ to their original targets.

\end{enumerate}

In each case, if one of the edge-absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.

\end{IEEEproof}

Let $\itn\gamma'$ be $\itn\gamma$ where the first two edge-absorbers are exchanged.

\begin{lemma}
If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\sim\itn\delta$ or $\itn\gamma\sim\itn\delta'$.
\end{lemma}

\begin{IEEEproof}
We will prove the case where $\gamma\sim\delta$ is a single reconfiguration step; the general case follows because the proof goes through also when $\itn\gamma'$ replaces $\itn\gamma$ in the statement of the lemma.
%
Let $\gamma$ and $\delta$ agree on every edge except $e$, where $\gamma(e)=v$ and $\delta(e)=w$.
%
Firstly, using Lemma~\ref{lem:octopus roll}, for the edges $d$ other than $e$ such that $\gamma(d)=v$, the weight elements of the edge-gadgets $\itn d$ may be linked to the constraint elements of $\itn v$, in accordance with the target configuration $\itn\delta$.
%
Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is free.
%
Next, the indicator vertex of $\itn e$, which links to the indicator of $\itn v$, is re-attached to the indicator of $\itn w$.
%
Again using Lemma~\ref{lem:octopus roll}, the weight elements of edge-gadgets connected to $\itn w$, including $\itn e$, may be linked in accordance with $\itn\delta$.
%
The resulting proof net is $\itn\delta$ modulo a permutation of edge-absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute edge-absorbers}.
\end{IEEEproof}

%------------------------------------------------------------------------------------------------

\subsection{Soundness}

\begin{lemma}
In a proof net for $\itn G$, an edge-gadget $\itn e$ belongs to the empire of at most one vertex-gadget $\itn v$.
\end{lemma}

\begin{IEEEproof}
Since vertex-gadgets are joined by a tensor, the lemma is immediate from \cite[Proposition 1]{Bellin-vandeWiele-1995}.
\end{IEEEproof}

\begin{lemma}
\label{lem:appropriate edge weights}
In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
\end{lemma}

\begin{IEEEproof}
Let $|V|=n$ and $|E|=m$, and consider the vertex $v_i$ and an edge $e$ connecting vertices $v_a$ and $v_b$ where $i\neq a,b$.
%
Each constraint element in $\itn{v_i}$ is an instance of the formula
\[
	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)~.
\]
The two $\parr$-subformulae have a balance of $-3i-1$ and $-3(n-i)-2$ respectively.
%
Each weight element in $\itn{e}$ is an instance of 
\[
	W = \bigotimes\big(\bot^{3a+2}\big)\parr\bigotimes\big(\bot^{3(b-a)+1}\big)\parr\bigotimes\big(\bot^{3(n-b)+3}\big)~.
\]
The three $\tn$-subformulae have a net balance of $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
%
In pairs, they have a net balance of $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
%
Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$, it follows that $W$ can balance the scope of at most one of both subformulae of $C$.

The vertex-gadget $\itn{v_i}$ is the formula
\[
	\itn{v_i} = \bigparr\big(C^{m\times c(v_i)} \big)\parr 1~.
\]
It will be shown that $m$ inappropriate edge-gadgets may balance at most $m-1$ constraint elements $C$.

Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq m\times c(v_i)$. 
%
If the scopes $s(x_j)$ and $s(y_m)$ of any $x_j$ and $y_m$ are balanced by weight elements $W$ and $W'$ of the same edge-gadget $\itn e$, then since $W$ and $W'$ are connected by a tensor, there are switchings of $W$, $W'$, $s(x_j)$, and $s(y_m)$ such that $x_j$ and $y_m$ are connected in the proof net for $\itn G$.
%
Then the first constraint element of $\itn{v_i}$ requires 2 edge-gadgets to balance, and each successive element requires one additional edge-gadget.
\end{IEEEproof}

Using the above, a proof net for $\itn G$ may be interpreted as a configuration for $G$.

\begin{definition}
For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

\begin{lemma}
If $\links\sim\links'$ are proof nets for $\itn G$ then $\coitn\links\sim\coitn{\links'}$.
\end{lemma}

\begin{IEEEproof}
A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.
%
Then in both $\coitn\links$ and $\coitn{\links'}$ the edges $e_1$ through $e_n$ are mobile, since by Lemma~\ref{lem:appropriate edge weights} the empires of the vertex-gadgets $\itn v$ (in cases 1 and 3) and $\itn w$ (in cases 2 and 3) contain appropriate edge-gadgets other than $\itn{e_1}$ through $\itn{e_n}$ of sufficient combined weight.
%
It follows that in the graph $G$ the edges $e_1$ through $e_n$ can be moved away from $v$ and/or onto $w$ one at a time.

\end{IEEEproof}

\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}

### 2014-01-14 main/s_level_2.tex
made one file for LICS

@@
 \section{Proof nets and constraint graphs}
-
-\newcommand\alt{\underline}
 
@@
 \begin{lemma}
+\label{lem:permute edge-absorbers}
 If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
@@
 	\item
-Finally, to permutate edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
+Finally, to permute edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
 %
@@
 %
-Perform a second permutation to return $d_0$ and $d_1$ their proper edge-absorbers.
+A second such exchange is needed to re-attach $d_0$ and $d_1$ to their original targets.
 
@@
 
+Let $\itn\gamma'$ be $\itn\gamma$ where the first two edge-absorbers are exchanged.
+
 \begin{lemma}
-If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then $\itn\gamma\sim\itn\delta$.
+If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\sim\itn\delta$ or $\itn\gamma\sim\itn\delta'$.
 \end{lemma}
+
+\begin{proof}
+We will prove the case where $\gamma\sim\delta$ is a single reconfiguration step; the general case follows because the proof goes through also when $\itn\gamma'$ replaces $\itn\gamma$ in the statement of the lemma.
+%
+Let $\gamma$ and $\delta$ agree on every edge except $e$, where $\gamma(e)=v$ and $\delta(e)=w$.
+%
+Firstly, using Lemma~\ref{lem:octopus roll}, for the edges $d$ other than $e$ such that $\gamma(d)=v$, the weight elements of the edge-gadgets $\itn d$ may be linked to the constraint elements of $\itn v$, in accordance with the target configuration $\itn\delta$.
+%
+Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is free.
+%
+Next, the indicator vertex of $\itn e$, which links to the indicator of $\itn v$, is re-attached to the indicator of $\itn w$.
+%
+Again using Lemma~\ref{lem:octopus roll}, the weight elements of edge-gadgets connected to $\itn w$, including $\itn e$, may be linked in accordance with $\itn\delta$.
+%
+The resulting proof net is $\itn\delta$ modulo a permutation of edge-absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute edge-absorbers}.
+\end{proof}
 

### 2014-01-14 main/LICS.tex
first stab at intro

@@
 \usepackage{mathtools}
-\usepackage[round]{natbib}
+
+% Sorts citations; e.g. [1], [2], [5]--[7]
+%\usepackage{cite}
+
+% More reference handling options
+%\usepackage{natbib}\renewcommand\bibfont{\footnotesize}
+
 \usepackage{mllequiv,willemtools}
@@
 
+\shortJournalNames
 \makeTheoremDefs
@@
   \IEEEauthorblockA{
-  		University of Bath \\
-		Claverton Down \\
-		Bath BA2~7AY\\
-		w.b.heijltjes@bath.ac.uk
+  		University of Bath
+	\\	Claverton Down
+	\\	Bath BA2~7AY
+	\\	w.b.heijltjes@bath.ac.uk
 	}
@@
   \IEEEauthorblockN{Robin Houston}
-  \IEEEauthorblockA{Kiln Enterprises}
+  \IEEEauthorblockA{
+		Kiln Enterprises
+	\\	robin.houston@gmail.com	
+	}
 }
 
-\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete}
+%\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete}
+
+%\title{Proof equivalence in MLL is \textsc{pspace}-complete}
+
+\title{No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete}
+
+%============================================================
 
@@
 %
-The result rules out the existence of a satisfactory notion of proof nets for MLL with units (under current complexity assumptions).
+An important consequence of the result is that the existence of a satisfactory notion of proof nets for MLL with units is ruled out (under current complexity assumptions).
 \end{abstract}
+
+%------------------------------------------------------------
+
+\section{Introduction}
+
+An important element of the theory of linear logic \cite{Girard-1987} is the idea that proofs should be considered modulo the permutation of inferences.
+%; that the chosen order of permutable inferences is inessential, or `bureaucracy'.
+%contributes no essential proof content, and should be considered `bureaucracy'.
+%
+%The idea is supported by the categorical semantics of linear logic, in which proofs up to permutations denote the same morphism. 
+%
+\emph{Proof equivalence} is the problem of deciding whether two proofs are equal modulo permutations.
+
+The proof equivalence problem is closely related to the notion of \emph{proof nets}.
+%
+These are canonical, geometric representations of proof that factor out permutations, so that proofs are equivalent if and only if they have the same underlying proof net.
+%
+Canonical proof nets have been found for several fragments of linear logic: the multipicative fragment without units \cite{Girard-1987,Danos-Regnier-1989}, the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
+%
+For the full multiplicative fragment, with units, several notions of proof net have been proposed \cite{BCST,Strassburger-lamarche-2004,HughesFreeStar}.
+%
+However, none is canonical, and whether a satisfactory notion of proof net can be found has remained an open question.
+
+In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \textsc{pspace}-complete.
+%
+As a main corrolary, this effectively rules out the possibility of finding a satisfactory notion of proof net for this fragment.
+
+%------------------------------------------------------------
 
@@
 
-\begin{figure}
-%%\noindent
-%\fbox{\MLLrule b}
-%\hfill\fbox{\MLLrule 1}
-%\hfill\fbox{\MLLrule p}
-%\hfill\fbox{\MLLrule t}
-%\hfil
-\[
-\begin{array}{llll}
-	\MLLrule b
- &	\MLLrule 1
- &	\MLLrule p
- &	\MLLrule t
-\end{array}
-\]
+\begin{figure}[!b]
+\quad\MLLrule b
+\hfill\MLLrule 1
+\hfill\MLLrule p
+\hfill\MLLrule t
+\quad
 \caption{Inference rules for unit-only \MLL}
@@
 
-\begin{figure}
+\begin{figure}[!tb]
+\renewcommand\scalefactor{0.88}
 \[
-	\vc{\MLLperm{bb1}} \perm \vc{\MLLperm{bb2}}
-\qquad
-	\vc{\MLLperm{bp1}} \perm \vc{\MLLperm{bp2}}
-\]
-\[
-	\vc{\MLLperm{bt1}} \perm \vc{\MLLperm{bt2}} \perm \vc{\MLLperm{bt3}}
-\]
-\[
-	\vc{\MLLperm{pp1}} \perm \vc{\MLLperm{pp2}}
-\]
-\[
-	\vc{\MLLperm{pt1}} \perm \vc{\MLLperm{pt2}}
-\]
-\[
-	\vc{\MLLperm{tt1}} \perm \vc{\MLLperm{tt2}}
+\begin{array}{@{}rcl@{}}
+	\multicolumn{3}{@{}c@{}}{
+		\vc{\scale{\MLLperm{bb1}}} ~\perm~ \vc{\scale{\MLLperm{bb2}}}
+		\hfill
+		\vc{\scale{\MLLperm{bp1}}} ~\perm~ \vc{\scale{\MLLperm{bp2}}}
+	}
+\\ \\[6pt]
+	\multicolumn{3}{@{}c@{}}{
+		\vc{\scale{\MLLperm{bt2}}} ~\perm~ \vc{\scale{\MLLperm{bt1}}} ~\perm~ \vc{\scale{\MLLperm{bt3}}}
+	}
+\\ \\[6pt]
+	\vc{\scale{\MLLperm{pp1}}} &\perm& \vc{\scale{\MLLperm{pp2}}}
+\\ \\[6pt]
+	\vc{\scale{\MLLperm{pt1}}} &\perm& \vc{\scale{\MLLperm{pt2}}}
+\\ \\[6pt]
+	\vc{\scale{\MLLperm{tt1}}} &\perm& \vc{\scale{\MLLperm{tt2}}}
+\end{array}
 \]
@@
 \end{figure}
+
+%===========================
+\bibliographystyle{plain}
+\bibliography{../refs}
+\end{document}
+%===========================
 
@@
 %NOTE: will we need to count arms often enough to make it worthwile to write $|\Gamma|_\bot$ for the number of $\bot$-occurrences in a sequent $\Gamma$?
+
+%------------------------------------------------------------
 
@@
 
+%------------------------------------------------------------
+
 \section{Par}
@@
 An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
+
+%------------------------------------------------------------
 
@@
 
-%------------------------------------------------------------------------------------------------
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 
@@
 
-\bibliographystyle{plainnat}
-\bibliography{refs}
+%------------------------------------------------------------
+
+\section{Conclusions}
 

### 2014-01-15 notes/ssr.tex
Lots of changes to SSR; so far uncommitted

--- 2013-07-20 notes/ssr.tex
@@
 \author{Robin Houston}
-\title{Everything I know about Subset Sum Reconfiguration}
+\title{Notes on Subset Sum Reconfiguration}
 
@@
 \newtheorem{rem}[prop]{Remark}
+\newtheorem*{definition}{Definition}
 
@@
 
-\noindent This is a brief summary of everything I know about the subset sum reconfiguration problem as of the evening of Thursday the 18th of July.
+\noindent Some elementary observations about the subset sum reconfiguration problem
 
-\begin{prop}
-    Subset sum reconfiguration is weakly NP-hard. \textup(Demaine--Ito\textup)
-\end{prop}
+\section*{Examples}
 
-\begin{conjecture}\label{conjecture:diameter}
-    For all $n>1$, there is an $n$-element SSR instance whose configuration graph has diameter $2n-2$.
-\end{conjecture}
-
-\begin{rem}
-    The lower bound conjectured in Conjecture~\ref{prop:diameter} is optimal for $n<8$.
-I have verified this by exhaustive enumeration using the program \texttt{ssr\_graphs.py}.
-An earlier version of these notes had a construction that purported to exhibit this bound, but there is an error and it does not work.
-\end{rem}
-
-\begin{prop}\label{prop:element-moves-a-lot}
-    For all $m$, there is a $(5m+3)$-element SSR instance that has an element that must move at least $2m+1$ times in any solution sequence.
-\end{prop}
+\noindent The first example shows that some elements must sometimes move many times
+\begin{eg}\label{eg:element-moves-a-lot}
+    For all natural numbers $m$, there is a $(5m+3)$-element instance that has an element that must move at least $2m+1$ times in any solution sequence.
+\end{eg}
 \begin{proof}
-    The elements are $x_1, \dots, x_{2m+1}$ of weight $3$, $a_1, \dots, a_{3m+1}$ of weight $2$, and $b$ of weight $1$.
+    The elements are
+    $x_1, \dots, x_{2m+1}$ of weight $3$,
+    $a_1, \dots, a_{3m+1}$ of weight $2$,
+    and $b$ of weight $1$.
+    %
     Let $k=6m$ and $c=6m+3$.
-The starting configuration is $x_1, \dots, x_{2m+1}$, and the target is $a_1, \dots, a_{3m+1}, b$.
-For $i=0, 1, \dots, 2m$, consider the first move after which there are precisely $2m-i$ of the $x$ elements inside.
-That means the $a$'s and possibly $b$ inside at this point must sum to $3i$.
+    %
+    The initial packing is $x_1, \dots, x_{2m+1}$,
+    and the target is $a_1, \dots, a_{3m+1}, b$.
+    %
+    %
+    At each packing in the sequence, count the number of $x$ elements it contains.
+The initial packing has $2m+1$ of them, and the target packing has none: therefore there must be packings in the sequence, in order, that contain $2m, 2m-1, \dots, 0$ of the $x$ elements.
+For $i=0, 1, \dots, 2m$, consider the first packing that contains precisely $2m-i$ of the $x$ elements.
+This packing must differ from its predecessor by the removal of some $x$ element, and so its total weight is forced to be $6m$.
+Hence the weights of the other elements in this packing -- $a$'s and possibly $b$ -- must sum to $3i$.
 If $i$ is odd then, since the $a$'s all have even weight, $b$ must be inside at this point; similarly if $i$ is even then $b$ must be outside.
@@
 
-\noindent The construction of Proposition~\ref{prop:element-moves-a-lot} can be modified to give a quadratic lower bound for the diameter of the reconfiguration graph.
-\begin{prop}\label{prop:quadratic-bound}
-    For all $m$, there is a $(6m+2)$-element SSR instance that requires $2m^2+6m+2$ moves.
-\end{prop}
+\noindent The second example is similar, and establishes a quadratic lower bound for the diameter of the configuration graph.
+\begin{eg}\label{eg:quadratic-bound}
+    For all $m$, there is a $(6m+2)$-element instance that requires $2m^2+6m+2$ moves.
+\end{eg}
 \begin{proof}
-    The elements are
+    This example is similar to the previous one, except that all the weights are multiplied by $m$ and
+    then the element $b$ is decomposed into $m$ elements of weight $1$. So the elements are
     $x_1, \dots, x_{2m+1}$ of weight $3m$,
@@
     %
-    The starting configuration is $x_1, \dots, x_{2m+1}$,
+    The initial packing is $x_1, \dots, x_{2m+1}$,
     and the target is $a_1, \dots, a_{3m+1}, b_1, \dots, b_m$.
     %
-    For $i=0, 1, \dots, 2m$, consider the first move after which there are precisely $2m-i$ of the $x$ elements inside.
-That means the $a$'s and $b$'s inside at this point must sum to $3im$.
-If $i$ is odd then, since the $a$'s all weigh $2m$, all the $b$'s must be inside at this point; similarly if $i$ is even then the $b$'s must all be outside.
+    The argument is as before: for $i=0, 1, \dots, 2m$, consider the first packing that contains precisely $2m-i$ of the $x$ elements.
+The total weight of the non-$x$ elements in this packing must equal $3im$.
+If $i$ is odd then, since the $a$'s all weigh $2m$, all the $b$'s must be inside this packing; similarly if $i$ is even then the $b$'s must all be outside it.
 So the $b$ elements each move at least $2m+1$ times.
@@
 
-\noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable without the need to construct an actual solution.
-(The details need some work here, but I think the basic idea is okay.)
-\begin{lemma}\label{lemma:reduction}
-    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$.
-By abuse of notation we shall also refer to the whole instance as $E$.
-Let $a$ and $z$ be elements of minimal and maximal weight respectively.
-If $w(z) > c-k$ or $w(a) < c-k-w(z) + 2$ then either $E$ is trivially unsolvable or else there is an element $e\in E$ and a (smaller) instance with element set $E' = E-\{e\}$ that is equivalent to the original in the sense that $E'$ is solvable iff $E$ is.
-\end{lemma}
-\begin{proof}
-    Let $e$ be any element that has weight $z$.
+\section*{Eliminating redundant elements}
 
-    If $w(z) > c - k$ then our element $z$ cannot move.
-If $z$ moves between the start and target packings, then $E$ is trivially unsolvable.
-Otherwise we let $E' = E-\{z\}$.
-If $z$ is inside in both the start and target packing, let the threshold and capacity of our new instance be $k' = k-w(z)$ [TODO: what if $k-w(z) < 0$?] and $c' = c-w(z)$, and remove $z$ from the start and target configurations.
-If $z$ is outside in both the start and target, let $k'=k$ and $c'=c$.
-Every solution of $E'$ is a solution of $E$, and vice versa -- by adding $z$ to all packings in the solution sequence in the former case, or by literally using the same solution sequence in the latter.
+\noindent Elements that are `large enough' or `small enough' in weight may be eliminated, in the sense that we
+can construct an equi-solvable instance by removing them and adjusting the threshold and capacity appropriately.
+For example, the $b$ elements of Example~\ref{eg:quadratic-bound} are small enough to be eliminated -- and, once
+they are eliminated, these instances admit linear-length solutions.
 
-    If $w(a) < c-k-w(z) + 2$ then let $E' = E-\{a\}$.
-Look at whether or not $a$ belongs to the start configuration: if it does, let $k'=k-w(a)$ and $c'=c$; if not, let $k'=k$ and $c'=c+w(a)$.
-[TODO: What if $k-w(a) < 0$?
-This case needs to be considered.] In both cases we have $c'-k' = c-k+w(a)$.
-Any solution of $E$ can be converted to a solution of $E'$ just by removing element $a$ from all packings in the sequence and eliminating adjacent duplicates.
-The interesting part is the converse, converting a solution of $E'$ into a solution of $E$.
-Let $A_0', \dots, A_m'$ be a sequence of packings that solves $E'$.
-We shall show how to insert element $a$, with some additional moves of $a$, to obtain a solution of $E$.
+\subsection*{Eliminating large elements}
 
-    Let us say that a packing $A'$ of $E'$ \textit{requires $a$} if $w(A') < k' + w(a)$, and that it \textit{rejects $a$} if $w(A') > c' - w(a)$.
-Now we want to argue that in a solution sequence of $E'$ there are never two adjacent packings such that one requires $a$ and the other rejects it.
-The gap between the bound for rejecting $a$ and the bound for accepting it is $c' - w(a) - (k' + w(a)) = c'-k'-2w(a) = c-k-w(a)$, so it is not possible to cross this gap without the weight changing by at least $c-k-w(a)+2$.
-Two adjacent packings differ in weight by at most $w(z)$, and since we are supposing that $w(a) < c-k-w(z) + 2$ it follows that they differ by less than $c-k-w(a)+2$, as required.
+\noindent This part is really trivial. An element whose weight exceeds $c-k$ is too large to be moved in or out
+of the packing, so it can take no part in any solution. Let us call such an element \emph{large}. If the instance
+requires a large element to move, because it is contained in the initial packing but not the target or vice versa,
+then it is clearly unsolvable. Otherwise there are two cases:
+\begin{enumerate}
+    \item The large element $x$ belongs to the initial and target packings. Remove $x$ from the set of elements and
+    from the initial and target packings. If $w(x) <= k$ then reduce both $k$ and $c$ by $w(x)$. If $w(x) > k$ then
+    let $k=0$ and reduce $c$ by $w(x)$.
+    \item The large element $x$ belongs to neither the initial nor the target packing. Simple remove $x$ from the set of elements.
+\end{enumerate}
 
-    Finally we can construct a solution sequence for $E$ by inserting $a$ where it is required and removing it where it is rejected.
-We describe an algorithm that reads $A_0', \dots A_m'$ in order and outputs a solution of $E$.
-The algorithm keeps track of whether $a$ is currently inside or outside the packing as it goes along.
-If $a$ belongs to the start packing then initially $a$ is inside, otherwise initially $a$ is outside.
-Then for each $i$ from $0$ to $m$:
-    \begin{itemize}
-        \item if $a$ is currently inside and $A_i'$ rejects $a$, output $A_{i-1}'$ followed by $A_i'$. (Note this case cannot occur when $i=0$.) Let $a$ be outside.
-        \item if $a$ is currently outside and $A_i'$ requires $a$, output $A_{i-1}'\union\{a\}$ followed by $A_i'\union\{a\}$. (This case cannot occur when $i=0$ either.) Let $a$ be inside.
-        \item otherwise, output $A_i'$ if $a$ is outside, and output $A_i'\union\{a\}$ if $a$ is inside.
-    \end{itemize}
-\end{proof}
+\subsection*{Eliminating small elements}
 
-\noindent In some cases we can iterate Lemma~\ref{lemma:reduction} to reduce the instance to the trivial one-element case.
-\begin{prop}\label{prop:iterated-reduction}
-    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$.
-Suppose further that no element weighs more than $c-k$.
-Let $E = {e_0, \dots, e_n}$ in nondecreasing order by weight.
-If
-    \[
-        w(e_i) < c - k + \sum_{j<i}w(e_j) - w(e_n) + 2
-    \]
-    for all $i$ then the instance is solvable.
-Note that this condition does not mention the start or target packings, so in fact such instances have the property that any valid packing is reachable from any other.
-\end{prop}
+\noindent The situation with small elements is rather the opposite. Of course small elements are able to move:
+they have so much freedom of movement that they may be moved whenever necessary, so it is not necessary to
+record them. In this section we assume that large elements have already been eliminated.
+
+\begin{definition}\label{def:small}
+    An element $x$ is \emph{small} if $w(x) < c-k-w_{\mathrm{max}} + 2$, where $w_{\mathrm{max}}$ is the
+    maximum weight over all elements in the instance. In particular an element of weight $1$ is always small.
+\end{definition}
+
+\noindent To eliminate a small element, remove it from the set of elements and from the initial and target packings,
+and adjust the threshold and capacity as follows:
+\begin{enumerate}
+    \item If $a$ belongs to the initial packing, leave $k$ unchanged and increase $c$ by $w(a)$.
+    \item If $a$ does not belong to the initial packing and $k \geq w(a)$, leave $c$ unchanged and
+            reduce $k$ by $w(a)$.
+    \item If $a$ does not belong to the initial packing and $k < w(a)$, leave $c$ unchanged and set $k$ to zero.
+\end{enumerate}
+
 \begin{rem}
-    Let us say that an instance satisfying the property of Proposition~\ref{prop:iterated-reduction} is \textit{completely reducible}.
-The instances exhibited in Proposition~\ref{prop:element-moves-a-lot} are completely reducible.
-The instances exhibited in Proposition~\ref{prop:quadratic-bound} are not completely reducible, but can be reduced to a form that has a linear bound on the length of the solution sequence by eliminating the elements that have weight $1$.
+    This process increases $c-k$, which means that elements may be small in the reduced
+    instance that were not small in the original. Therefore in some cases the construction may be iterated.
+    For example we may eliminate an element of weight $1$, which then makes it possible to eliminate an
+    element of weight $2$, etc.
 \end{rem}
+
 \end{document}

### 2014-01-15 main/LICS.tex
finished draft intro

@@
 As a main corrolary, this effectively rules out the possibility of finding a satisfactory notion of proof net for this fragment.
+
+\subsection*{Constraint logic and reconfiguration problems}
+
+The proof of the \textsc{pspace}-completeness result relies on a polynomial reduction from %the configuration--to--configuration problem in
+\emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
+%
+It consists of a simple graph rewriting mechanism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied, and asks whether two graphs are related in a series of valid rewriting steps.
+
+Constraint logic belongs to a class of problems called \emph{reconfiguration problems} \cite{ReconfigurationProblems}: can one solution to a given problem be transformed into another by a series of elementary changes, while remaining valid throughout?
+%
+For example, for boolean satisfyability (SAT) the reconfiguration problem asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
+%
+It is not uncommon for an \textsc{np}-complete problem to have an associated reconfiguration problem that is \textsc{pspace}-complete \cite{ReconfigurationProblems}; one example is SAT-reconfiguration, which is \textsc{pspace}-complete.
+
+MLL proof equivalence may be usefully classified as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Lincoln-1994}.
 
@@
 
-%===========================
-\bibliographystyle{plain}
-\bibliography{../refs}
-\end{document}
-%===========================
-
 The formulae of unit-only multiplicative linear logic are given by the following grammar.
@@
 
-In one of several possible definitions, a \emph{$\star$-autonomous category} \citep{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
+In one of several possible definitions, a \emph{$\star$-autonomous category} \cite{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
 %
@@
 
-\subsection{Proof nets}
+\subsection*{Proof nets}
 
@@
 
-\begin{proposition}[\citeauthor{DR89}, \citeyear{DR89}]
+\begin{proposition}[\cite{DR89}]
 \label{prop:correctness and sequentialisation}
@@
 
-\begin{proposition}[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
+\begin{proposition}[\cite{HughesMLLProofNets}] %[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
 \label{prop:proof nets work}
@@
 
-\subsection{Notation}
+\subsection*{Notation}
 
@@
 \begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}
+
+%===========================
+\bibliographystyle{plain}
+\bibliography{../refs}
+\end{document}
+%===========================
 
@@
 
-\subsection{Completeness}
+\subsection*{Completeness}
 
@@
 
-\subsection{Soundness}
+\subsection*{Soundness}
 

### 2014-01-15 main/LICS.tex

@@
 
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
 \subsection*{Constraint logic and reconfiguration problems}
@@
 
-MLL proof equivalence may be usefully classified as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Lincoln-1994}.
+MLL proof equivalence may be usefully classified as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Kanovich-1992}.
 
@@
 	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\MLLperm{bt2}}} ~\perm~ \vc{\scale{\MLLperm{bt1}}} ~\perm~ \vc{\scale{\MLLperm{bt3}}}
+		\vc{\scale{\MLLperm{bt2}}} ~\perm~ \vc{\scale{\MLLperm{bt1}}}
+								   ~\perm~ \vc{\scale{\MLLperm{bt3}}}
 	}
@@
 %
-\[
-	A,B,C \coloneq \bot \mid 1 \mid A\parr B \mid A\tn B
+\setMidspace{5pt}
+\[
+	A,B,C \Coloneq \bot \Mid 1 \Mid A\parr B \Mid A\tn B
 \]
@@
 %
-Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names $N$, e.g.\
+Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names, e.g.\
 $\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot$.
 %
-This allows to 1) avoid using the notion of \emph{occurrence}, and instead refer to subformulae by the name of their root connective, as e.g.\ $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
+This allows to 1) identify \emph{occurrences} of subformulae uniquely by the name of their root connective, e.g.\ as $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
 %
@@
 
-Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}.
-%
-The names of connectives are preserved through inferences.
+Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}, where the names of units and connectives are preserved through inferences.
 %
@@
 
-The motivation to consider proofs up to equivalence is three-fold.
-%
-Firstly, there is the strong intuition that the order of permutable inferences does not contribute to the essential content of the proof.
-%
-Secondly, a technical motivation is that cut-elimination in \MLL\ incorporates permutation steps, and composition via cut-elimination is only associative up to permutations.
-%
-Thirdly, equivalent proofs are identified in natural models of multiplicative linear logic such as coherence spaces, and in the categorical semantics of \MLL, $\star$-autonomous categories.
-
-In one of several possible definitions, a \emph{$\star$-autonomous category} \cite{Barr-1979} is a symmetric monoidal category $(\mathcal C,\tn,1)$ with:
-%
-\begin{itemize}
-
-	\item
-	a \emph{duality}, a contravariant functor $\dual-$ such that $A\cong\dual*A$, and
-
-	\item
-	\emph{closure}, an adjunction $-\tn B \dashv \dual{(B\tn\dual-)}$ for any object $B$,
-
-\end{itemize}
-%
-satisfying natural coherence conditions.
-%
-%The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
-%
-The category with as objects unit-only \MLL-formulae and as morphisms $A\to B$ the equivalence classes of proofs of $\dual A\parr B$, denoted $\textsc{mll}(\emptyset)$, is a $\star$-autonomous category.
-%
-The present formulation of formulae induces two forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, while
-%, one-sided sequents mean the closure adjunction is an equivalence of categories, 
-associativity is an identity by decree.
-%
-Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
-%
-This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two term representations denote the same morphism.
-
-%The \emph{free $\star$-autonomous completion} $\star$-\textsc a$(\mathcal C)$ of a category $\mathcal C$ is characterised by a functor $i\colon\mathcal C\to\star$-\textsc a$(\mathcal C)$ such that any functor $\mathcal C\to \mathcal D$ into a $\star$-autonomous cateogry $\D$ factors uniquely (up to canonical isomorphism) as the composition of $i$ with a functor $\star$-\textsc a$(\mathcal C)\to\D$ preserving $\star$-autonomous structure.
-%%
-%\[
-%\begin{tikzpicture}[auto]
-%	\node (C) at (0,0) {$\mathcal C$};
-%	\node (*AC) at (2,0) {$\star$-\textsc a$(\mathcal C)$};
-%	\node (D) at (1,1) {$\mathcal D$};
-%	\draw [->] (C) -- node {$i$} (*AC);
-%	\draw [->] (C) -- (D);
-%	\draw [->,dashed] (*AC) -- node {$!$} (D);
-%\end{tikzpicture}
-%\]
-%%
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 
@@
 
-A partial solution to the \MLL\ proof equivalence problem is provided by proof nets.
+Proof nets provide a solution to proof equivalence for MLL$^-$ (MLL without units).
+%
+For full MLL, they reduce the proof equivalence problem to a simple rewiring relation \cite{HughesMLLProofNets}.
 
@@
 	\item
-	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$, with for every subformula $\named aA\named c\tn\named bB$ the edges $a-c$ and $b-c$, for every subformula $\named aA\named c\parr\named bB$ either the edge $a-c$ or the edge $b-c$, and for every subformula $\named a\bot$ the edge $a-\links(a)$,
+	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$, with for every subformula $\named aA\named c\tn\named bB$ the edges $\edge ac$ and $\edge bc$, for every subformula $\named aA\named c\parr\named bB$ either the edge $\edge ac$ or the edge $\edge bc$, and for every subformula $\named a\bot$ the edge $\edge a{\links(a)}$,
 
@@
 \noindent
-An edge $a-\links(a)$ in a proof net or switching graph is a \emph{link} or \emph{jump}.
+An edge $\edge a{\links(a)}$ in a proof net or switching graph is called a \emph{link} or a \emph{jump}.
 
@@
 %
-A \emph{permutation} between proof nets is the redirection of exactly one link.
-%
-\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the congruence generated by permutations.
+A \emph{permutation} $(\perm*)$ between proof nets is the redirection of exactly one link.
+%
+\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by permutations.
 %
@@
 \noindent
-There is no canonical interpretation of a proof as a proof net, since the introduction rule for $\bot$ in proofs joins a $\bot$-formula to a sequent, rather than a formula.
+In the sequent calculus, the introduction rule for $\bot$ joins a $\bot$-formula to a sequent $\Gamma$, rather than an occurrence of $\1$.
+%
+The interpretation of a proof as a proof net may attach the corresponding link to an arbitrary $\1$ in $\Gamma$.
 
@@
 %
-The relation $(\toNet)$ interprets a proof $\Pi$ for a sequent $\Gamma$ by a linking $\links$ as follows:
-% 
-$\Pi\toNet\links$ if for each $\named a\bot$ in $\Gamma$, if $\Delta$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Delta$.
-\[
-	\infer[\MLLlabel b]{\Delta,\named a\bot}{\Delta}
+The relation $(\toNet)$ interprets a proof $\Pi$ for a sequent $\Delta$ by a linking $\links$ as follows:
+% 
+$\Pi\toNet\links$ if for each $\named a\bot$ in $\Delta$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Gamma$.
+\[
+	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
 \]
@@
 %
-Equivalence of proof nets is generated by the remaining equations, the permutations on $\bot$-introduction.
+Equivalence of proof nets is generated by the four remaining permutations, on $\bot$-introduction.
 
@@
 \noindent
-\MLL\ proof equivalence is the problem of deciding equivalence of proof nets.
+The above proposition means that \MLL\ proof equivalence is the problem of deciding equivalence of proof nets.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 

### 2014-01-16 main/LICS.tex
hacks & fixes
rummaging around

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[conference,onecolumn]{IEEEtran}
 
@@
 \graphicspath{{../notes/}}
+
+\let\alt=\underline
 
@@
 \section{Introduction}
+
+%% STILL TO ADD:
+%% - MLL proof equivalence is the word problem for *-autonomous categories
+%% - IMLL proof equivalence is polynomial-time
 
@@
 The above proposition means that \MLL\ proof equivalence is the problem of deciding equivalence of proof nets.
+%
+% We will use proof net equivalence to encode constraint logic.
 
@@
 The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
+%
+%
+%% NEW
+%
+Formulae related by a tensor will be connected by edges, while formulae related by a par will be collected in a box, omitting an outer box for the complete sequent.
+%
+For example:
+\[
+	\bot\tn\bot,\bot\tn\bot,\1,(\1\parr\1\parr\1)\tn\bot
+\]
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (2,0) node[bullet] (c) {} -- (3,0) node[bullet] (d) {};
+	\node[circ] (1) at (4,0) {};
+	\node[circ] (2) at (5.5,0) {}; \node[circ] (3) at (6.5,0) {}; \node[circ] (4) at (7.5,0) {};
+	\draw[rounded corners] (5,-1) rectangle (8,1);
+	\draw (8,0) -- (9,0) node[bullet] (e) {};
+\end{tikzpicture}
+\]
+
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[circ] (1) at (6,0) {};
+	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (3,0) node[bullet] (c) {} -- (4,0) node[bullet] (d) {};
+	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
+	\draw[rounded corners] (0,2) rectangle (4,4);
+	\draw (4,3) -- (5,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (a) to (2);
+			\draw[bend right=10] (b) to (3);
+			\draw[bend left=10] (c) to (3);
+			\draw[bend left=10] (d) to (4);
+			\draw[bend right=10] (e) to (1);
+	\end{scope}
+\end{tikzpicture}
+\]
+
+%% OLD
+
 %
@@
 \begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}
-
-%===========================
-\bibliographystyle{plain}
-\bibliography{../refs}
-\end{document}
-%===========================
 
@@
 
+%===========================
+\bibliographystyle{plain}
+\bibliography{../refs}
 \end{document}
+%===========================
+
+\end{document}

### 2014-01-16 main/LICS.tex
Update Robin’s email address
typo
changed first example diagrams

@@
 %
-For example:
+For example, the following denote the same sequent:
 \[
@@
 	\node[circ] (1) at (4,0) {};
-	\node[circ] (2) at (5.5,0) {}; \node[circ] (3) at (6.5,0) {}; \node[circ] (4) at (7.5,0) {};
-	\draw[rounded corners] (5,-1) rectangle (8,1);
-	\draw (8,0) -- (9,0) node[bullet] (e) {};
+	\node[circ] (2) at (5.25,0) {}; \node[circ] (3) at (6.25,0) {}; \node[circ] (4) at (7.25,0) {};
+	\draw[rounded corners] (4.75,-1) rectangle (7.75,1);
+	\draw (7.75,0) -- (8.75,0) node[bullet] (e) {};
 \end{tikzpicture}
 \]
-
+The links of a proof net are added to the sequent as colored arrows.
+%
+The following example is a proof net for the above sequent.
 \[
@@
 \]
+
+%===========================
+\bibliographystyle{plain}
+\bibliography{../refs}
+\end{document}
+%===========================
 
@@
 
-%===========================
-\bibliographystyle{plain}
-\bibliography{../refs}
 \end{document}
-%===========================
-
-\end{document}

### 2014-01-16 main/LICS.tex
slowly adding to "notation"

@@
 %
-Formulae related by a tensor will be connected by edges, while formulae related by a par will be collected in a box, omitting an outer box for the complete sequent.
+Formulae related by a tensor will be connected by edges.
+%
+Formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
 %
@@
 	\begin{scope}[thepink,->]
-			\draw[bend right=10] (a) to (2);
-			\draw[bend right=10] (b) to (3);
-			\draw[bend left=10] (c) to (3);
-			\draw[bend left=10] (d) to (4);
-			\draw[bend right=10] (e) to (1);
+			\draw[bend right=10] (a) to (2.center);
+			\draw[bend right=10] (b) to (3.center);
+			\draw[bend left=10]  (c) to (3.center);
+			\draw[bend left=10]  (d) to (4.center);
+			\draw[bend right=10] (e) to (1.center);
+	\end{scope}
+\end{tikzpicture}
+\]
+
+We will denote by $A^n$ the sequent consisting of $n$ copies of a formula $A$, and given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigotimes\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
+%
+In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigotimes(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
+%
+A linking between $\bigotimes(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (-1,2) {};
+	\node[big1] (!) at (-1,0) {};
+	\node at (.5,1) {$\coloneq$};
+	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
+	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
+	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
+	\begin{scope}[thepink,->]
+			\draw[big>] (A) to (!.center);
+			\draw[bend right=10] (a) to (1.center);
+			\draw[bend right=10] (b) to (2.center);
+			\draw[bend right=10] (c) to (3.center);
 	\end{scope}
@@
 
-Let $A^n$ denote the sequent of $n$ copies of a formula $A$, and for a sequent $\Gamma=A_1,\dotsc,A_n$ let $\bigotimes\Gamma=A_1\tn\dotso\tn A_n$ and $\bigparr\Gamma=A_1\parr\dotso\parr A_n$.
-
 \begin{definition}

### 2014-01-16 main/LICS.tex
Let’s be bold!
No commented-out alternatives.
added more notation

@@
-\documentclass[conference,onecolumn]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 
@@
 
-\begin{proposition}[\cite{DR89}]
+\begin{proposition}[\cite{Danos-Regnier-1989}]
 \label{prop:correctness and sequentialisation}
@@
 
-We will denote by $A^n$ the sequent consisting of $n$ copies of a formula $A$, and given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigotimes\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
+We will denote by $A^n$ the sequent consisting of $n$ occurrences of a formula $A$.
+%
+Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigotimes\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
 %
@@
 
-%===========================
-\bibliographystyle{plain}
-\bibliography{../refs}
-\end{document}
-%===========================
-
-%% OLD
-
-%
-A tensor is represented by a line connecting both subformulae, and a par by juxtaposition: if $A$ and $B$ are represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
-and \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}},
-%
-then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
-and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
-%
-A tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
-\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
-%
-Boxes play the role of parentheses around par-formulae, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}
-
-\noindent For example, this sequent
-\[ \vdash \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, 1, \{[(1\parr 1\parr 1)\tn(1\parr 1\parr 1)]\parr 1\parr (\bot\tn\bot\tn\bot)\parr 1\}\tn\bot \]
-could be drawn like this:
-\begin{center}\includegraphics[scale=0.75]{example-sequent.pdf}\end{center}
-
-\noindent We represent a proof net by drawing an arrow from each $\bullet$ to some $\circ$. For example, one proof net on the above sequent is
-\begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}
-
-%NOTE: need 'octopus' terminology here
-
-%NOTE: will we need to count arms often enough to make it worthwile to write $|\Gamma|_\bot$ for the number of $\bot$-occurrences in a sequent $\Gamma$?
+That two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge or a dashed arrow, as illustrated below.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[bullet] (a) at (0,0) {}; \node[bullet] (b) at (2,0) {}; \draw[dashed] (a)--(b);
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (3,0) {};
+	\coordinate (a') at ($(a) + (.6,0)$); \coordinate (b') at ($(b) + (-.6,0)$);
+	\draw[thepink,dashed] (a')--(b'); \draw[thepink,->] (a')--(a.center); \draw[thepink,->] (b')--(b.center);
+\end{tikzpicture}
+\]
 

### 2014-01-16 main/LICS.tex
squeezing in diagrams, correcting references

@@
 \let\alt=\underline
+
+\newcommand\NoIndent[1]{%
+  \par\vbox{\parbox[t]{\linewidth}{#1}}%
+}
 
@@
 
-That two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge or a dashed arrow, as illustrated below.
+That two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
 \[
@@
 \begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (3,0) {};
-	\coordinate (a') at ($(a) + (.6,0)$); \coordinate (b') at ($(b) + (-.6,0)$);
-	\draw[thepink,dashed] (a')--(b'); \draw[thepink,->] (a')--(a.center); \draw[thepink,->] (b')--(b.center);
+	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
+	%\coordinate (a') at ($(a) + (.6,0)$); \coordinate (b') at ($(b) + (-.6,0)$);
+	%\draw[thepink,dashed] (a')--(b'); \draw[thepink,->] (a')--(a.center); \draw[thepink,->] (b')--(b.center);
 \end{tikzpicture}
@@
 \[
-\begin{array}{ccccc}
+\kern-3pt
+\begin{array}{@{}c@{~}c@{~}c@{~}c@{~}c@{}}
 	\netC yzwx & \perm & \netC yzzx & \perm & \netC yxzx
@@
 \[
+\begin{array}{@{}ccccc@{}}
 	\vc{\doubleExchange uvxy}
-	\sim
+	&\perm&
 	\vc{\doubleExchange uyxy}
-	\sim
+	&\perm&
 	\vc{\doubleExchange uyxu}
-	\sim
+	\\
+	\\
+	\vc{\doubleExchange vuyx}
+	&\perm&
+	\vc{\doubleExchange vuyu}
+	&\perm&
+	\vc{\doubleExchange vyyu}
+\end{array}
+\begin{array}{@{~}c@{~}c@{}}
+	\indirection{ul}{\perm} \\ \\[20pt]
+	\indirection{dl}{\perm}
+\end{array}
 \vc{\doubleExchange vyxu}
-	\sim
-	\vc{\doubleExchange vyyu}
-	\sim
-	\vc{\doubleExchange vuyu}
-	\sim
-	\vc{\doubleExchange vuyx}
 \]
@@
 
-\begin{theorem}[\cite{demaine}]
+\begin{theorem}[\cite{Hearn-Demaine-2005}]
 \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
@@
 
-For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints, $\sum_{v\in V}c(v)$, and the sum of all edge weights, $\sum_{e\in E}w(e)$.
+For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+\[
+	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
+\]
 
@@
 \[
-	W =  \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big)
-	\parr\big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
-	\parr\big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
+	W = \begin{array}[t]{l}
+				 \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big) 
+	~\parr\\[5pt] \big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
+	~\parr\\[5pt] \big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
+	\end{array}
 \]
@@
 The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
+\NoIndent{
 \[
@@
 \]
+}
 	\item
 The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
+\NoIndent{
 \[
@@
 \]
+}
 	\item
 Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
+\NoIndent{
 \[
@@
 \]
+}
 	\item\label{item:exchange added}
@@
 The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+\NoIndent{
 \[
@@
 \]
+}
 	\item
 The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
+\NoIndent{
 \[
@@
 \]
+}
 	\item\label{item:exchange needed}
@@
 Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
+\NoIndent{
 \[
@@
 \]
+}
 	\item
 The link from $i$ may be re-attached to $v$ to yield the final configuration.
+\NoIndent{
 \[
@@
 \]
+}
 \end{enumerate}

### 2014-01-17 main/LICS.tex
started prose for Section 5

@@
 \[
-	\kern-1pt \netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw \kern-1pt 
+	\netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw
 \]
@@
 
-\section{Proof nets and constraint graphs}
-
-[[ NOTE: we should decide on notation for steps versus paths in permutation relations ]]
+\section{Encoding constraint graphs}
+
+\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Hearn-Demaine-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
+%
+A rewriting step is the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex, preserving the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
+%
+The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
+
+We will introduce minor adaptations to this formalism to suit our reduction to MLL proof equivalence.
+%
+Mainly, a constraint graph here will have \emph{undirected} edges, and a separate notion of \emph{configuration} imposes a direction on edges.
+%
+A constraint graph will then be encoded as a sequent, while a configuration corresponds to a linking.
+%
+In addition, a configuration will be allowed to be \emph{partial}, leaving some edges undirected, as long as the directed edges suffice to satisfy the inflow constraints.
 

### 2014-01-17 main/LICS.tex
minor edits

@@
 
-\section{Encoding constraint graphs}
-
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Hearn-Demaine-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
-%
-A rewriting step is the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex, preserving the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
+\section{Encoding constraint logic}
+
+\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
+%
+A rewrite step consists of the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex.
+%
+Rewrite steps must preserve the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
 %
@@
 %
-In addition, a configuration will be allowed to be \emph{partial}, leaving some edges undirected, as long as the directed edges suffice to satisfy the inflow constraints.
-
-\begin{definition} 
-A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set $E$ of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
-
-A (partial) \emph{configuration} of an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
+In addition, we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
+
+\begin{definition} 
+A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges, between vertices $v(e)=\{v_1,v_2\}\subseteq V$ and with \emph{weight} $w\colon E\to\mathbb N$.
+%of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
+
+\smallskip
+
+A \emph{(partial) configuration} for an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
 \begin{itemize}
 	\item
-for every edge $e$, $\gamma(e)\in v(e)$ or (in the partial case) $\gamma(e)$ is undefined, and
+for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
 	\item
@@
 
-A \emph{reconfiguration step} $\gamma\sim\delta$ connects two (partial) configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.
-
-\end{definition}
-
-The \emph{(partial) \textsc{ncg}-reconfiguration problem} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
+\smallskip
+A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \textsc{ncg} $G$ that differ in value (or definedness) on exactly one edge.
+%
+\end{definition}
+
+\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
 
@@
 \begin{IEEEproof}
-There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
-%
-Firstly, if $\gamma\sim\delta$ are partial configurations, they may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$.
-%
-Secondly, if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by re-assigning the values where they disagree.
-%
-\end{IEEEproof}
-
-For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+Partial \textsc{ncg}-reconfiguration simulates \textsc{ncg}-reconfiguration:
+%
+%There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
+%
+firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$; secondly,
+%
+if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by reversing the edges on which they disagree.
+%
+\end{IEEEproof}
+
+\subsection*{Encoding constraint graphs}
+
+For a constraint graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
 \[

### 2014-01-17 main/LICS.tex
more minor edits

@@
 \begin{definition} 
-A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges, between vertices $v(e)=\{v_1,v_2\}\subseteq V$ and with \emph{weight} $w\colon E\to\mathbb N$.
+A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting vertices $v(e)=\{v_1,v_2\}\subseteq V$.
 %of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
@@
 
-A \emph{(partial) configuration} for an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
+A \emph{(partial) configuration} for a constraint graph is a (partial) function $\gamma\colon E\to V$ such that
 \begin{itemize}
@@
 
-\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding when two configurations for a constraint graph are connected in the graph of total configurations and reconfiguration steps.
+%
+\emph{Partial \textsc{ncg}-reconfiguration} is the same problem for partial configurations.
+
+%\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
 
@@
 %
-firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$; secondly,
+firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; secondly,
 %
@@
 \begin{definition}
-\label{def:graph interpretation}
-The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
+\label{def:graph encoding}
+The \emph{encoding} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
 %
@@
 
-The interpretation of a vertex $v_k$ is the formula
+The encoding of a vertex $v_k$ is the formula
 \[
@@
 
-The interpretation of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
+The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
 \[
@@
 
-The interpretation of the graph $G$ is the sequent
+The encoding of the graph $G$ is the sequent
 \[
@@
 \begin{definition}
-\label{def:configuration interpretation}
-The \emph{interpretation} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
+\label{def:configuration encoding}
+The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
 %
@@
 \begin{definition}
-For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
+For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
 \end{definition}

### 2014-01-17 main/LICS.tex
explaining weight and constraint elements

@@
 \let\alt=\underline
+\let\bigtn=\bigotimes
 
@@
 %
-Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigotimes\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
-%
-In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigotimes(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
-%
-A linking between $\bigotimes(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
+Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
+%
+In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
+%
+A linking between $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
 \[
@@
 %
-Mainly, a constraint graph here will have \emph{undirected} edges, and a separate notion of \emph{configuration} imposes a direction on edges.
-%
-A constraint graph will then be encoded as a sequent, while a configuration corresponds to a linking.
+Mainly, a constraint graph itself will have \emph{undirected} edges, while a separate notion of \emph{configuration} imposes a direction on them.
+%
+A constraint graph may then be encoded as a sequent, and a configuration as a proof net.
 %
@@
 
-\subsection*{Encoding constraint graphs}
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{The encoding}
+
+The basis of the encoding of constraint graphs in MLL is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
+%
+The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
+%
+Below left is a constraint element, below right a weight element.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big1] (1) at (0,0) {$m'$}; 
+	\node[big1] (2) at (3,0) {$n'$};
+	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
+	\draw (1,0)--(2,0);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {$i'$}; 
+	\node[big_] (B) at (2,0) {$j'$};
+	\node[big_] (C) at (4,0) {$k'$};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+\end{tikzpicture}
+\]
+Throughout an encoding, the sum $i+j+k=m+n$ will be constant---this way, a priori any weight element may connect to any constraint element.
+%
+The value of $m$ (and thus $n$) will differ for each vertex.
+%
+The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
+\[
+	\connectingElements 1 \qquad \connectingElements 2
+\]
+To ensure that no other connections can be made, values are chosen such that $m\mod3=1$ and $n\mod3=2$, and correspondingly $i\mod3=1$, $j\mod3=0$, and $k\mod3=2$.
+
+In a constraint graph, the sum of weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
+%
+An encoding will therefore have weight elements not connected to constraint elements.
+%
+These will instead connect to additional $\1$-formulae, referred to as edge-absorbers, as follows.
 
@@
 \[
-	\itn{e} = \bigotimes\big(W^{m\times w(e)}\big)\tn\bot
+	\itn{e} = \bigtn\big(W^{m\times w(e)}\big)\tn\bot
 \]
@@
 \[
-	W = \bigotimes\big(\bot^{3i+2}\big)\parr\bigotimes\big(\bot^{3(j-i)+1}\big)\parr\bigotimes\big(\bot^{3(n-j)+3}\big)
+	W = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
 \]
@@
 \[
-	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
+	%\itn G = \bigtn_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
 	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
@@
 \[
-	W = \bigotimes\big(\bot^{3a+2}\big)\parr\bigotimes\big(\bot^{3(b-a)+1}\big)\parr\bigotimes\big(\bot^{3(n-b)+3}\big)~.
+	W = \bigtn\big(\bot^{3a+2}\big)\parr\bigtn\big(\bot^{3(b-a)+1}\big)\parr\bigtn\big(\bot^{3(n-b)+3}\big)~.
 \]

### 2014-01-18 main/LICS.tex
finished informal description of encoding

@@
 	\item
-for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
+for every vertex $v$, the total weight of its incoming edges is at least its inflow constraint, 
+%$\sum\{\kern1pt w(e)\kern1pt|\kern1pt\gamma(e)=v\kern1pt\}\geq c(v)$.
+$\sum\{w(e)\mid\gamma(e)=v\}\geq c(v)$.
 \end{itemize}
@@
 %
-Below left is a constraint element, below right a weight element.
-\[
+Below left is a weight element, below right a constraint element.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {$i'$}; 
+	\node[big_] (B) at (2,0) {$j'$};
+	\node[big_] (C) at (4,0) {$k'$};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+\end{tikzpicture}
+\qquad\qquad
 \begin{tikzpicture}[x=5mm,y=5mm,octo]
@@
 \end{tikzpicture}
-\qquad\qquad
+\]
+Throughout an encoding, the sum $i+j+k=m+n$ will be constant---this way, a priori any weight element may connect to any constraint element.
+%
+The value of $m$ (and thus $n$) will differ for each vertex.
+%
+The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
+\[
+	\connectingElements 1 \qquad \connectingElements 2
+\]
+To ensure that no other connections can be made, values are chosen such that $m\bmod3=1$ and $n\bmod3=2$, and accordingly $i\bmod3=1$, $j\bmod3=0$, and $k\bmod3=2$.
+
+In a constraint graph, the sum of weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
+%
+An encoding will therefore have weight elements not connected to constraint elements.
+%
+These will instead connect to additional, separate $\1$-formulae, referred to as \emph{edge-absorbers}, as follows.
+%
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {}; 
+	\node[big_] (B) at (2,0) {};
+	\node[big_] (C) at (4,0) {};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+	\node[big1] (1) at (7.5,0) {};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend left=30] (A) to (1);
+		\draw[bend right=30] (B) to (1);
+		\draw (C) to (1);
+	\end{scope}
+\end{tikzpicture}
+\]
+%
+An edge will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements plus a single \emph{indicator} vertex.
+%
+Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
+%
+\[
 \begin{tikzpicture}[x=5mm,y=5mm,octo]
@@
 	\draw[rounded corners] (-1,-1) rectangle (5,1);
+	\node[big_] (D) at (0,4) {$i'$}; 
+	\node[big_] (E) at (2,4) {$j'$};
+	\node[big_] (F) at (4,4) {$k'$};
+	\draw[rounded corners] (-1,3) rectangle (5,5);
+	\draw (2,1)--(2,1.5) (2,2.5)--(2,3);
+	\draw[dotted] (2,1.5)--(2,2.5);
+	\draw (2,-1)--(2,-2) node[bullet] {};
+	\path (0,-2.5)--(1,-2.5);
 \end{tikzpicture}
-\]
-Throughout an encoding, the sum $i+j+k=m+n$ will be constant---this way, a priori any weight element may connect to any constraint element.
-%
-The value of $m$ (and thus $n$) will differ for each vertex.
-%
-The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
-\[
-	\connectingElements 1 \qquad \connectingElements 2
-\]
-To ensure that no other connections can be made, values are chosen such that $m\mod3=1$ and $n\mod3=2$, and correspondingly $i\mod3=1$, $j\mod3=0$, and $k\mod3=2$.
-
-In a constraint graph, the sum of weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
-%
-An encoding will therefore have weight elements not connected to constraint elements.
-%
-These will instead connect to additional $\1$-formulae, referred to as edge-absorbers, as follows.
-
-For a constraint graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big1] (1) at (0,0) {$m'$}; 
+	\node[big1] (2) at (3,0) {$n'$};
+	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
+	\draw (1,0)--(2,0);
+	\node[big1] (3) at (0,4) {$m'$};
+	\node[big1] (4) at (3,4) {$n'$};
+	\draw[rounded corners] (-1,3) rectangle (1,5) (2,3) rectangle (4,5);
+	\draw (1,4)--(2,4);
+	\draw[dotted] (1.5,1.5)--(1.5,2.6);
+	\node[circ] at (1.5,-2) {};
+	\draw[rounded corners] (-1.5,-2.5) rectangle (4.5,5.5);
+\end{tikzpicture}
+\]
+%
+It would be natural to encode an edge of weight $n$ by an edge-gadget with $n$ weight elements.
+%
+However, there is a minor issue that prevents this straightforward approach.
+%
+Where one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
+%
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big_] (A) at (-1,0) {}; 
+	\draw (.75,0) node[big_] (B1) {} -- (2.25,0) node[big_] (B2) {};
+	\node[big_] (C) at (4,0) {};
+	\draw[rounded corners] (-2,-1) rectangle (5,1);
+	\draw (7,0) node[big_] (D1) {} -- (8.5,0) node[big_] (D2) {}; 
+	\node[big_] (E) at (10.25,0) {};
+	\node[big_] (F) at (12,0) {};
+	\draw[rounded corners] (6,-1) rectangle (13,1);
+	\node[big1] (1) at (1,4) {};
+	\node[big1] (2) at (4,4) {}; 
+	\node[big1] (3) at (7,4) {};
+	\node[big1] (4) at (10,4) {};
+	\draw[rounded corners] (3,3) rectangle (5,5) (6,3) rectangle (8,5);
+	\draw (5,4)--(6,4);
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=25] (A)  to (1);
+		\draw[bend right=15] (B1) to (1);
+		\draw[bend right=25] (B2) to (2);
+		\draw[bend right=15] (C)  to (2);
+		\draw[bend left=15] (D1) to (3);
+		\draw[bend right=15] (D2) to (4);
+		\draw[bend left=20] (E)  to (4);
+		\draw[bend left=20] (F)  to (4);
+	\end{scope}
+\end{tikzpicture}
+\]
+%
+In such an inappropriate linking, since both halves of the constraint element are connected, both weight elements may not be---otherwise, the linking would violate the switching condition.
+%
+That means the weight elements must belong to different edges; and moreover, for the same reason these two edges cannot fill another constraint element together.
+%
+To fill $n$ constraint elements inappropriately therefore requires $n+1$ edges.
+%
+It thus suffices to multiply the number of constraint elements by the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
+
+The complete encoding of a constraint graph will be a sequent consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of edge-absorbers ($\1$-formulae).
+%
+For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
 \[
@@
 The rightmost $1$-occurrence of each vertex-gadget $\itn v$, named $\alt v$ below, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$, named $\alt e$, will be called the \emph{indicator vertices} of $\itn v$ and $\itn e$.
+%
+% NOW: /indicator/ for edges and /indicator target/ for vertices
+%
 \[	

### 2014-01-18 main/LICS.tex
re-wrote defn. "standard linking" (was: "natural linking")

@@
 %
+The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
+%
 \end{definition}
 
+\begin{proposition}
+\label{prop:partial simulates total reconfiguration}
+For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
+\end{proposition}
+
+\begin{IEEEproof}
+By the following two observations: firstly, 
+%
+if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
+%
+if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
+%
+\end{IEEEproof}
+
+%
 \emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding when two configurations for a constraint graph are connected in the graph of total configurations and reconfiguration steps.
@@
 \emph{Partial \textsc{ncg}-reconfiguration} is the same problem for partial configurations.
-
-%\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
 
@@
 
+By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
+
 \begin{proposition}
 Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+%\textsc{pncg}-reconfiguration is \textsc{pspace}-complete.
 \end{proposition}
 
-\begin{IEEEproof}
-Partial \textsc{ncg}-reconfiguration simulates \textsc{ncg}-reconfiguration:
-%
-%There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
-%
-firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; secondly,
-%
-if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by reversing the edges on which they disagree.
-%
-\end{IEEEproof}
+We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL.
 
@@
 \]
-Throughout an encoding, the sum $i+j+k=m+n$ will be constant---this way, a priori any weight element may connect to any constraint element.
+For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
 %
@@
 \label{def:graph encoding}
-The \emph{encoding} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
+The \emph{encoding} $\itn G$ of a constraint graph $G=(V,E,c,v,w)$ is a sequent constructed as follows.
 %
@@
 
+\noindent
 The encoding of a vertex $v_k$ is the formula
 \[
-	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
-\]
-where each \emph{constraint element} $C$ is the formula
-\[
-	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
-\]
-
+	\itn{v_k} = \bigparr\big(C_n(k)^{m\times c(v_k)} \big)\parr\1
+\]
+where each \emph{constraint element} $C_n(k)$ is the formula
+\[
+	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
+\]
+
+\noindent
 The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
 \[
-	\itn{e} = \bigtn\big(W^{m\times w(e)}\big)\tn\bot
-\]
-where each \emph{weight element} $W$ is the formula
-\[
-	W = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
-\]
-
+	\itn{e} = \bigtn\big(W_n(i,j)^{m\times w(e)}\big)\tn\bot
+\]
+where each \emph{weight element} $W_n(i,j)$ is the formula
+\[
+	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
+\]
+
+\noindent
 The encoding of the graph $G$ is the sequent
 \[
-	%\itn G = \bigtn_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
 	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
 \]
-where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.
+where $p=m\times(|w|-|c|)\times(3n+4)$.
 
@@
 
-In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
-%
-This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$.
-
-For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
-\[
-	W = \begin{array}[t]{l}
-				 \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big) 
-	~\parr\\[5pt] \big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
-	~\parr\\[5pt] \big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
-	\end{array}
-\]
-and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
-\[
-	C = \big(\named{\alt    \dagger}1\parr\named{\alt{   1}}1\parr\dotso\parr\named{\alt{3k+1}}1\big)
-	\tn \big(\named{\alt\downdagger}1\parr\named{\alt{3k+2}}1\parr\dotso\parr\named{\alt{3n+3}}1\big)~.
-\]
-There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
-\[
-	\links(x) = \alt x \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
-\]
-\[
-	\links(\ddagger)=
-	\begin{cases}
-		\alt	\dagger & \text{if }k=i \\
-		\alt\downdagger & \text{if }k=j~.
-	\end{cases}
-\]
-There is also a natural linking for the sequent $W,\named\star 1,\named{\alt 1}1,\dotsc,\named{\alt {3n+3}}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
-\[
-	\links(x)=
-	\begin{cases}
-		\star  & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
-		\alt x & \text{otherwise }.
-	\end{cases}
-\]
+In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{edge-absorbers}.
+%
+In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
+%
+This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.
+
+A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
+%
+Firstly we will define a standard way of linking a weight element to a constraint element.
+
+\begin{definition}
+\label{def:standard linkings}
+For a weight element $W=W_n(i,j)=A\parr B\parr C$,
+\begin{enumerate}
+	\item
+for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and the remaining $\bot$-occurrences in $A,B,C$ to the remaining $\1$-occurrences in $X,Y$;
+	\item
+for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
+	\item
+the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ each to the first $\1$, and the remaining $\bot$-occurrences to the remaining $\1$-occurrences.
+\end{enumerate}
+\end{definition}
+
+The standard linkings defined in the first and third case of the above definition are illustrated below.
+
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (1) at (-.25,0) {};
+	\node[big1] (2) at (1,0) {};
+	\node[big1] (3) at (2.5,0) {};
+	\node[big1] (4) at (5.5,0) {};
+	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
+	\draw (3.5,0)--(4.5,0);
+	%
+	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
+	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
+	\node[big_] (C) at (5.5,4) {};
+	\draw[rounded corners] (-1,3) rectangle (6.5,5);
+	%
+	\begin{scope}[thepink,->]
+		\draw[bend right=5] (a) to (1);
+		\draw[bend right=10] (b) to (1);
+		\draw[big>,bend left=25] (A) to (2);
+		\draw[big>,bend left=20] (B) to (3);
+		\draw[big>,bend left=15] (C) to (4);
+	\end{scope}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (1) at (.75,0) {};
+	\node[big1] (2) at (2,0) {};
+	\node[big1] (3) at (3.5,0) {};
+	\node[big1] (4) at (5,0) {};
+	%
+	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
+	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
+	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
+	\draw[rounded corners] (-.5,3) rectangle (7,5);
+	\path (0,-1) -- (1,-1);
+	%
+	\begin{scope}[thepink,->]
+		\draw[bend right=5] (a) to (1);
+		\draw[bend right=10] (b) to (1);
+		\draw[bend right=15] (c) to (1);
+		\draw[big>,bend left=25] (A) to (2);
+		\draw[big>,bend left=20] (B) to (3);
+		\draw[big>,bend left=15] (C) to (4);
+	\end{scope}
+\end{tikzpicture}
 
@@
 \label{prop:element linkings}
-\begin{enumerate}
-	\item
-Given a vertex $v$ and an appropriate edge $e$, for a constraint element $C$ in $\itn v$ and a weight element $W$ in $\itn e$ the natural linking for the sequent $W,C$ is a proof net.
-	\item
-Given a weight element $W$ for a graph with $|V|=n$, the natural linking for the sequent $W,1^{3n+4}$ is a proof net.
-\end{enumerate}
+The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
 \end{proposition}
 
-The rightmost $1$-occurrence of each vertex-gadget $\itn v$, named $\alt v$ below, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$, named $\alt e$, will be called the \emph{indicator vertices} of $\itn v$ and $\itn e$.
-%
-% NOW: /indicator/ for edges and /indicator target/ for vertices
-%
-\[	
-	\itn v = C\parr\dotso\parr C\parr \named{\alt v}1 \qquad \itn e= W\tn\dotso\tn W\tn\named{\alt e}\bot~.
-\]
+The encoding of a configuration is then as follows.
 
@@
 \label{def:configuration encoding}
-The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
-%
-Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
-%
-Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
+The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
+%
+Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
+%
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
 \end{definition}
@@
 %
-The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its natural linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
+The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
 %
@@
 %
-Two links from $C$ to $X$ should remain exchanged, compared to the natural linking, for step \ref{item:exchange needed} below.
+Two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step \ref{item:exchange needed} below.
 %

### 2014-01-18 main/LICS.tex
re-ordered sections

@@
 
-%------------------------------------------------------------
-
-\section{Equivalence in the absence of $~\protect\parr$}
-
-Let a \emph{1-alternation} sequent be one over formulae of the form $1$ or $\bot\tn\ldots\tn\bot$, where the number of $\bot$-subformulae is at least 2.
-%
-Such a sequent is inhabited exactly when the number of formulae in the sequent is one greater than the total number of $\bot$-subformulae it contains.
-%
-An inhabited 1-alternation sequent with only one tensor-formula, i.e.\ a sequent of the form $\1,\ldots,\1,\bot\tn\ldots\tn\bot$ with $n$ $\bot$-subformulae and $n$ $1$-subformulae, will admit $n!$ different proof nets, each with $n$ links.
-%
-Since no link can re-attach, its equivalence classes are singletons.
-
-\begin{proposition}
-\label{prop:level0 max binary}
-%
-For a 1-alternation sequent with at least two tensor-formulae there are at most two equivalence classes of proof nets.
-%
-\end{proposition}
-
-%
-%\begin{figure}[p]
-%\[
-%\begin{array}{ccc}
-%	\netA 1213 & \perm	& \netA 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 1223 &		& \netA 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 1323 &		& \netA 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 1321 &		& \netA 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2321 &		& \netA 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2331 & \perm	& \netA 2131
-%\end{array}
-%\qquad
-%\begin{array}{ccc}
-%	\netA 1312 & \perm	& \netA 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2312 &		& \netA 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2313 &		& \netA 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2113 &		& \netA 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2123 &		& \netA 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 3123 & \perm	& \netA 3121
-%\end{array}
-%\]
-%\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
-%\label{fig:2x12 nets}
-%\end{figure}
-
-\begin{IEEEproof}
-%
-It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
-%
-For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
-\[
-	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
-\]
-It has two equivalence classes, of 12 proof nets each.
-%
-(Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.)
-
-%, displayed in Figure~\ref{fig:2x12 nets}.
-
-For the inductive step, let $\Gamma$ be the following sequent.
-\[
-	\Delta,A\tn\named a\bot,\named z\1
-\]
-There are two cases: 1) where $A$ is a tensor-formula, and 2) where $A$ is $\bot$ and where, for the induction hypothesis to apply, $\Delta$ contains at least two tensor-formulae.
-%
-For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named z1$, and is the only link to do so.
-%
-This reduces equivalence on $\Gamma$ to equivalence on $\Delta,A$ in case 1, and on $\Delta$ in case 2, so that the induction hypothesis applies.
-
-In constructing $\links'$, since the proof net must be connected, there is a path from $a$ to $z$.
-%
-We will consider only the jumps on this path, not any other edges.
-%
-There are four cases.
-
-\begin{enumerate}
-	\item
-The path consists of exactly the jump $\edge az$.
-%
-Let $\edge by$ be a jump from a $\named b\bot$ in $A$; then $\links'$ is obtained from $\links$ by changing: $\links'(e)=y$  for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$.
-
-	\item
-The path starts with the jump $\edge ax$ (and $x\neq z$).
-%
-Let $\edge by$ be a jump from a $\named b\bot$ in $A$, and let the path end with the jumps $\edge wc$ and $\edge dz$, where $\named c\bot$ and $\named d\bot$ are in the same tensor-formula $B$.
-%
-Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$, including $d$.
-%
-These changes are illustrated as permutations below.
-%
-\[
-	\netB xywz \perm \netB zywz \perm \netB zywy
-\]
-
-	\item
-The path consists of exactly one jump $\edge bz$ from a $\named b\bot$ in $A$ (and $b\neq a$).
-%
-Let $\links(a)=y$.
-%
-Choose a jump $\edge cw$ from $\named c\bot$ in $A$ such that there is another $\edge dw$ from $\named d\bot$ in a formula $B$ (not excluding the possibilities $c=b$ and $c=a$).
-%
-Let $\edge ex$ be a further jump from $\named e\bot$ in $B$.
-%
-Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, $\links'(d)=x$, $\links'(e)=y$, and $\links'(f)=x$ for each $f$ (including $b$) such that $\links(f)=z$ and $f\neq a$.
-%
-These changes are exhibited as a series of permutations below, from top left to bottom left (note that the jump from $d$ moves twice).
-%
-\[
-\kern-3pt
-\begin{array}{@{}c@{~}c@{~}c@{~}c@{~}c@{}}
-	\netC yzwx & \perm & \netC yzzx & \perm & \netC yxzx
-	\\ &&&& \vperm \\
-	\netC zxxy & \perm & \netC zxzy & \perm & \netC yxzy
-\end{array}
-\]
-
-	\item
-The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
-%
-Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
-%
-Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
-%
-This is illustrated below.
-\end{enumerate}
-%
-\[
-	\netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw
-\]
-%
-\end{IEEEproof}
-
-\begin{proposition}
-\label{prop:level0 may-connect path}
-%
-For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
-%
-\begin{itemize}
-	\item
-The edge $\edge ab$ can be permuted to $\edge ac$.
-	\item
-There is a path from $b$ to $c$ not passing through $a$.
-	\item
-The path from $a$ to $c$ starts with the jump $a-b$.
-\end{itemize} 
-\end{proposition}
-
-If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
-%
-By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
-
-Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
-%
-\begin{itemize}
-
-	\item
-One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.
-
-	\item
-A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
-
-\end{itemize}
-%
-The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
-
-A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
-%
-\begin{definition}
-\label{def:combinatorial permutation}
-To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
-\[
-	\prm(k) = 
-	\begin{cases}
-		i				& \text{ if $(i,k)$ may connect to $*$; and}
-	\\	\links(i,k)		& \text{ otherwise.}
-	\end{cases}
-\]
-The \emph{parity} of $\links$ is the parity of its permutation.
-\end{definition}
-
-To see that $\prm$ is injective, consider the following.
-\begin{itemize}
-	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
-	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Proposition~\ref{prop:level0 may-connect path}).
-	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
-\end{itemize}
-
-\begin{proposition}
-\label{prop:level0 min binary}
-A permutation on a net $\links$ preserves its parity. 
-\end{proposition}
-
-\begin{IEEEproof}
-Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
-%
-There are two cases, depending on whether $(i,k)$ may connect to $*$.
-%
-If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
-%
-Then the permutation of $\links'$ is that of $\links$.
-
-If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
-\[
-	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
-\]
-Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
-%
-On the relevant domain, this gives the following permutation for $\links$.
-\[
-\left(\begin{array}{ccccccc}
-	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
-	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
-\end{array}\right)
-\]
-In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
-%
-The permutation $\prm[\links']$ is the following.
-\[
-\left(\begin{array}{ccccccc}
-	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
-	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
-\end{array}\right)
-\]
-The parity of both permutations is the same if and only if the relative permutation, below, is even.
-\[
-\left(\begin{array}{ccccccc}
-	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
-	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
-\end{array}\right)
-\]
-This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
-%
-\end{IEEEproof}
-
-\begin{proposition}
-\label{prop:parity determines equivalence}
-Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
-\end{proposition}
-
-\begin{theorem}
-\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
-\end{theorem}
-
-\begin{IEEEproof}
-For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
-%
-For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
-%
-Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
-%
-This yields a linear-time algorithm.
-%
-\end{IEEEproof}
-
-\begin{lemma}
-\label{lem:double exchange}
-Let $\links$ be a proof net where $\links(a)=(u)$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $b-v$ and $x-c$.
-%
-Then $\links\sim\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
-\end{lemma}
-
-\begin{IEEEproof}
-\[
-\begin{array}{@{}ccccc@{}}
-	\vc{\doubleExchange uvxy}
-	&\perm&
-	\vc{\doubleExchange uyxy}
-	&\perm&
-	\vc{\doubleExchange uyxu}
-	\\
-	\\
-	\vc{\doubleExchange vuyx}
-	&\perm&
-	\vc{\doubleExchange vuyu}
-	&\perm&
-	\vc{\doubleExchange vyyu}
-\end{array}
-\begin{array}{@{~}c@{~}c@{}}
-	\indirection{ul}{\perm} \\ \\[20pt]
-	\indirection{dl}{\perm}
-\end{array}
-\vc{\doubleExchange vyxu}
-\]
-\end{IEEEproof}
-
-%------------------------------------------------------------
-
-\section{Par}
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Subnets}
 
@@
 %
-After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the special $\named v1$ of $\itn v$, thus forming a tree.
+After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
+\end{IEEEproof}
+
+%------------------------------------------------------------
+
+\section{Equivalence in the absence of $~\protect\parr$}
+
+Let a \emph{1-alternation} sequent be one over formulae of the form $1$ or $\bot\tn\ldots\tn\bot$, where the number of $\bot$-subformulae is at least 2.
+%
+Such a sequent is inhabited exactly when the number of formulae in the sequent is one greater than the total number of $\bot$-subformulae it contains.
+%
+An inhabited 1-alternation sequent with only one tensor-formula, i.e.\ a sequent of the form $\1,\ldots,\1,\bot\tn\ldots\tn\bot$ with $n$ $\bot$-subformulae and $n$ $1$-subformulae, will admit $n!$ different proof nets, each with $n$ links.
+%
+Since no link can re-attach, its equivalence classes are singletons.
+
+\begin{proposition}
+\label{prop:level0 max binary}
+%
+For a 1-alternation sequent with at least two tensor-formulae there are at most two equivalence classes of proof nets.
+%
+\end{proposition}
+
+%
+%\begin{figure}[p]
+%\[
+%\begin{array}{ccc}
+%	\netA 1213 & \perm	& \netA 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 1223 &		& \netA 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 1323 &		& \netA 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 1321 &		& \netA 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2321 &		& \netA 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2331 & \perm	& \netA 2131
+%\end{array}
+%\qquad
+%\begin{array}{ccc}
+%	\netA 1312 & \perm	& \netA 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2312 &		& \netA 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2313 &		& \netA 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2113 &		& \netA 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 2123 &		& \netA 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
+%	\netA 3123 & \perm	& \netA 3121
+%\end{array}
+%\]
+%\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
+%\label{fig:2x12 nets}
+%\end{figure}
+
+\begin{IEEEproof}
+%
+It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
+%
+For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
+\[
+	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
+\]
+It has two equivalence classes, of 12 proof nets each.
+%
+(Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.)
+
+%, displayed in Figure~\ref{fig:2x12 nets}.
+
+For the inductive step, let $\Gamma$ be the following sequent.
+\[
+	\Delta,A\tn\named a\bot,\named z\1
+\]
+There are two cases: 1) where $A$ is a tensor-formula, and 2) where $A$ is $\bot$ and where, for the induction hypothesis to apply, $\Delta$ contains at least two tensor-formulae.
+%
+For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named z1$, and is the only link to do so.
+%
+This reduces equivalence on $\Gamma$ to equivalence on $\Delta,A$ in case 1, and on $\Delta$ in case 2, so that the induction hypothesis applies.
+
+In constructing $\links'$, since the proof net must be connected, there is a path from $a$ to $z$.
+%
+We will consider only the jumps on this path, not any other edges.
+%
+There are four cases.
+
+\begin{enumerate}
+	\item
+The path consists of exactly the jump $\edge az$.
+%
+Let $\edge by$ be a jump from a $\named b\bot$ in $A$; then $\links'$ is obtained from $\links$ by changing: $\links'(e)=y$  for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$.
+
+	\item
+The path starts with the jump $\edge ax$ (and $x\neq z$).
+%
+Let $\edge by$ be a jump from a $\named b\bot$ in $A$, and let the path end with the jumps $\edge wc$ and $\edge dz$, where $\named c\bot$ and $\named d\bot$ are in the same tensor-formula $B$.
+%
+Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$, including $d$.
+%
+These changes are illustrated as permutations below.
+%
+\[
+	\netB xywz \perm \netB zywz \perm \netB zywy
+\]
+
+	\item
+The path consists of exactly one jump $\edge bz$ from a $\named b\bot$ in $A$ (and $b\neq a$).
+%
+Let $\links(a)=y$.
+%
+Choose a jump $\edge cw$ from $\named c\bot$ in $A$ such that there is another $\edge dw$ from $\named d\bot$ in a formula $B$ (not excluding the possibilities $c=b$ and $c=a$).
+%
+Let $\edge ex$ be a further jump from $\named e\bot$ in $B$.
+%
+Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, $\links'(d)=x$, $\links'(e)=y$, and $\links'(f)=x$ for each $f$ (including $b$) such that $\links(f)=z$ and $f\neq a$.
+%
+These changes are exhibited as a series of permutations below, from top left to bottom left (note that the jump from $d$ moves twice).
+%
+\[
+\kern-3pt
+\begin{array}{@{}c@{~}c@{~}c@{~}c@{~}c@{}}
+	\netC yzwx & \perm & \netC yzzx & \perm & \netC yxzx
+	\\ &&&& \vperm \\
+	\netC zxxy & \perm & \netC zxzy & \perm & \netC yxzy
+\end{array}
+\]
+
+	\item
+The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
+%
+Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
+%
+Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
+%
+This is illustrated below.
+\end{enumerate}
+%
+\[
+	\netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw
+\]
+%
+\end{IEEEproof}
+
+\begin{proposition}
+\label{prop:level0 may-connect path}
+%
+For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
+%
+\begin{itemize}
+	\item
+The edge $\edge ab$ can be permuted to $\edge ac$.
+	\item
+There is a path from $b$ to $c$ not passing through $a$.
+	\item
+The path from $a$ to $c$ starts with the jump $a-b$.
+\end{itemize} 
+\end{proposition}
+
+If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
+%
+By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
+
+Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
+%
+\begin{itemize}
+
+	\item
+One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.
+
+	\item
+A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
+
+\end{itemize}
+%
+The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
+
+A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
+%
+\begin{definition}
+\label{def:combinatorial permutation}
+To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
+\[
+	\prm(k) = 
+	\begin{cases}
+		i				& \text{ if $(i,k)$ may connect to $*$; and}
+	\\	\links(i,k)		& \text{ otherwise.}
+	\end{cases}
+\]
+The \emph{parity} of $\links$ is the parity of its permutation.
+\end{definition}
+
+To see that $\prm$ is injective, consider the following.
+\begin{itemize}
+	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
+	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Proposition~\ref{prop:level0 may-connect path}).
+	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
+\end{itemize}
+
+\begin{proposition}
+\label{prop:level0 min binary}
+A permutation on a net $\links$ preserves its parity. 
+\end{proposition}
+
+\begin{IEEEproof}
+Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
+%
+There are two cases, depending on whether $(i,k)$ may connect to $*$.
+%
+If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
+%
+Then the permutation of $\links'$ is that of $\links$.
+
+If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
+\[
+	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
+\]
+Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
+%
+On the relevant domain, this gives the following permutation for $\links$.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
+	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
+\end{array}\right)
+\]
+In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
+%
+The permutation $\prm[\links']$ is the following.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+The parity of both permutations is the same if and only if the relative permutation, below, is even.
+\[
+\left(\begin{array}{ccccccc}
+	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
+%
+\end{IEEEproof}
+
+\begin{proposition}
+\label{prop:parity determines equivalence}
+Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+\end{proposition}
+
+\begin{theorem}
+\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
+\end{theorem}
+
+\begin{IEEEproof}
+For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
+%
+For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
+%
+Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
+%
+This yields a linear-time algorithm.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net where $\links(a)=(u)$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $b-v$ and $x-c$.
+%
+Then $\links\sim\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{IEEEproof}
+\[
+\begin{array}{@{}ccccc@{}}
+	\vc{\doubleExchange uvxy}
+	&\perm&
+	\vc{\doubleExchange uyxy}
+	&\perm&
+	\vc{\doubleExchange uyxu}
+	\\
+	\\
+	\vc{\doubleExchange vuyx}
+	&\perm&
+	\vc{\doubleExchange vuyu}
+	&\perm&
+	\vc{\doubleExchange vyyu}
+\end{array}
+\begin{array}{@{~}c@{~}c@{}}
+	\indirection{ul}{\perm} \\ \\[20pt]
+	\indirection{dl}{\perm}
+\end{array}
+\vc{\doubleExchange vyxu}
+\]
 \end{IEEEproof}

### 2014-01-18 main/LICS.tex
added octopus arithmetic to "notation"

@@
 %
-The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
-%
-%
-%% NEW
-%
-Formulae related by a tensor will be connected by edges.
-%
-Formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
+The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively;
+%
+formulae related by a tensor will be connected by edges; 
+and
+formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
 %
@@
 \[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
+\begin{tikzpicture}[x=-5mm,y=5mm,octo]
 	\node[big_] (A) at (-1,2) {};
 	\node[big1] (!) at (-1,0) {};
-	\node at (.5,1) {$\coloneq$};
+	\node at (.5,1) {$\Rightarrow$};
 	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
@@
 \]
-
-That two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
+Two formulae $\bigtn(\bot^{i+1})$ and $\bigtn(\bot^{j+1})$ may together connect to a formula $\bigparr(\1^{i+j+1})$, as illustrated below for $i=2$ and $j=3$.
+%
+Nodes will be labelled $i'$ for $i+1$, so that both the abbreviated formulae and the arithmetic of connecting them remain intuitive.
+%
+\[
+\vc{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (0,0) node[bullet] (a) {}--
+		  (1,0) node[bullet] (b) {}--
+		  (2,0) node[bullet] (c) {};
+	\draw (4,0) node[bullet] (d) {}--
+		  (5,0) node[bullet] (e) {}--
+		  (6,0) node[bullet] (f) {}--
+		  (7,0) node[bullet] (g) {};
+	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (a) to (1);
+			\draw[bend right=10] (b) to (2);
+			\draw[bend right=10] (c) to (3);
+			\draw[bend left=10]  (d) to (3);
+			\draw[bend left=10]  (e) to (4);
+			\draw[bend left=10]  (f) to (5);
+			\draw[bend left=10]  (g) to (6);
+	\end{scope}
+  \end{tikzpicture}
+}
+\quad\Rightarrow\quad
+\vc{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big_] (A) at (-1,0) {$2'$};
+	\node[big_] (B) at ( 1,0) {$3'$};
+	\node[big1] (!) at ( 0,3) {$5'$};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=15] (A) to (!);
+		\draw[bend left=15]  (B) to (!);
+	\end{scope}
+  \end{tikzpicture}
+}
+\]
+
+Finally, that two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
 \[
@@
 
+To conclude this section we will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets.
+
 \begin{definition}
@@
 %
-In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$ and re-attaching all arcs connecting to removed vertices to $v$.
-%
-
-[[ ADD ILLUSTRATED EXAMPLE ]]
-
+In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
+%
+In the example below, the kingdom of a (ternary) par is indicated (left) and contracted (right).
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
+		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
+		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
+	\node[circ] (0) at (5.75,0) {};
+	\node[circ] (1) at (-1,3) {};
+	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
+	\draw[rounded corners] (0,2) rectangle (4,4);
+	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (x) to (1);
+			\draw[bend right=20] (y) to (2);
+			\draw[bend right=10] (a) to (2);
+			\draw[bend right=10] (b) to (3);
+			\draw[bend left=10]  (c) to (3);
+			\draw[bend left=10]  (d) to (4);
+			\draw[bend right=10] (e) to (0);
+	\end{scope}
+	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
+	\node[circ] (0) at (3,0) {};
+	\node[circ] (1) at (-1,3) {};
+	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
+	\draw (box)--(3,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (x) to (1);
+			\draw[bend right=20] (y) to (box);
+			\draw[bend right=10] (e) to (0);
+	\end{scope}
+	\path (0,4.25)--(1,4.25);
+\end{tikzpicture}
+\]
 %
@@
 
-[[ IDEA: the following could help simplify octopus-arithmetic ]]
+Finally, the standard notion of \emph{balance} is useful in constructing proof nets without $\parr$-connectives
 
@@
 An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
-
-An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
+%
+%An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
+%
 
@@
 
-We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL.
+We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL proof nets.
 
@@
 	\item
-for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and the remaining $\bot$-occurrences in $A,B,C$ to the remaining $\1$-occurrences in $X,Y$;
+for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
 	\item
@@
 	\item
-the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ each to the first $\1$, and the remaining $\bot$-occurrences to the remaining $\1$-occurrences.
+the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
 \end{enumerate}
@@
 
+\[
 \begin{tikzpicture}[x=5mm,y=5mm,octo]
@@
 \end{tikzpicture}
+\]
 

### 2014-01-18 main/scratch.tex
added octopus roll lemma
hacks & fixes
explaining weight and constraint elements
finished informal description of encoding
re-wrote defn. "standard linking" (was: "natural linking")
added octopus arithmetic to "notation"

--- 2013-09-13 main/scratch.tex
@@
-\documentclass{article}
+\documentclass[conference]{IEEEtran}
 
-\usepackage{amsthm}
-\usepackage[round]{natbib}
+\usepackage{amsmath,amsthm}
 \usepackage{mllequiv,willemtools}
+
+\usepackage{pgffor}
 
@@
 
-\makeTheoremDefs
+%\makeTheoremDefs
 
@@
 
+\[
+\begin{tikzpicture}[x=-5mm,y=5mm,octo]
+	\node[big_] (A) at (-1,2) {};
+	\node[big1] (!) at (-1,0) {};
+	\node at (.5,1) {$\Rightarrow$};
+	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
+	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
+	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
+	\begin{scope}[thepink,->]
+			\draw[big>] (A) to (!.center);
+			\draw[bend right=10] (a) to (1.center);
+			\draw[bend right=10] (b) to (2.center);
+			\draw[bend right=10] (c) to (3.center);
+	\end{scope}
+\end{tikzpicture}
+\]
+
+\[
+\vc{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (0,0) node[bullet] (a) {}--
+		  (1,0) node[bullet] (b) {}--
+		  (2,0) node[bullet] (c) {};
+	\draw (4,0) node[bullet] (d) {}--
+		  (5,0) node[bullet] (e) {}--
+		  (6,0) node[bullet] (f) {}--
+		  (7,0) node[bullet] (g) {};
+	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (a) to (1);
+			\draw[bend right=10] (b) to (2);
+			\draw[bend right=10] (c) to (3);
+			\draw[bend left=10]  (d) to (3);
+			\draw[bend left=10]  (e) to (4);
+			\draw[bend left=10]  (f) to (5);
+			\draw[bend left=10]  (g) to (6);
+	\end{scope}
+  \end{tikzpicture}
+}
+\quad\Rightarrow\quad
+\vc{
+  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big_] (A) at (-1,0) {$2'$};
+	\node[big_] (B) at ( 1,0) {$3'$};
+	\node[big1] (!) at ( 0,3) {$5'$};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=15] (A) to (!);
+		\draw[bend left=15]  (B) to (!);
+	\end{scope}
+  \end{tikzpicture}
+}
+\]
+
+%
+%\[
+%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+%	\draw (-1.75,0) node[bullet] (x) {} -- (-.75,0) node[bullet] (y) {}
+%		  (  .75,0) node[bullet] (a) {} -- (1.75,0) node[bullet] (b) {}
+%		  ( 3.25,0) node[bullet] (c) {} -- (4.25,0) node[bullet] (d) {};
+%	\node[circ] (0) at (5.75,0) {};
+%	\node[circ] (1) at (-1,3) {};
+%	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
+%	\draw[rounded corners] (0,2) rectangle (4,4);
+%	\draw (4,3) -- (5,3) node[bullet] (e) {};
+%	\begin{scope}[thepink,->]
+%			\draw[bend right=10] (x) to (1.center);
+%			\draw[bend right=20] (y) to (2.center);
+%			\draw[bend right=10] (a) to (2.center);
+%			\draw[bend right=10] (b) to (3.center);
+%			\draw[bend left=10]  (c) to (3.center);
+%			\draw[bend left=10]  (d) to (4.center);
+%			\draw[bend right=10] (e) to (0.center);
+%	\end{scope}
+%\end{tikzpicture}
+%\]
+
 \end{document}
+
+\begin{frame}
+	\octorollA1
+\end{frame}
+
+\begin{frame}
+	\octorollB1
+\end{frame}
+
+\begin{frame}
+	\octorollB2
+\end{frame}
+
+\begin{frame}
+	\octorollB3
+\end{frame}
+
+\begin{frame}
+	\octorollC
+\end{frame}
+
+\begin{frame}
+	\octorollD1
+\end{frame}
+%
+%\begin{frame}
+%	\octorollE1
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollE2
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollE3
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollE4
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollE5
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollE6
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollE7
+%\end{frame}
+
+\begin{frame}
+	\octorollD2
+\end{frame}
+
+\begin{frame}
+	\octorollA2
+\end{frame}
+
+\end{document}
+
+%\newcommand\octorollC{
+%  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
+%	\node[circ] (a1a) at (0,1.5) {}; \node[big1] (a1) at (-2,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2,0) {};
+%	\draw (-9  ,4) node[bullet] (d1a) {} -- (-8  ,4) node[big_] (d1) {};
+%	\draw (-6.5,4) node[bullet] (d2a) {} -- (-5.5,4) node[big_] (d2) {};
+%	\draw (-4  ,4) node[bullet] (d3a) {} -- (-3  ,4) node[big_] (d3) {};
+%	\draw[rounded corners] (-10,3) rectangle (-2,5);
+%	\draw (-2,4)--(-1,4) node[bullet] (d) {};
+%	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
+%	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
+%	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
+%	\draw[rounded corners] (10,3) rectangle (2,5);
+%	\draw (2,4)--(1,4) node[bullet] (e) {};
+%	\node[circ] (v1a) at (-4,8); \node[big1] (v1b) at (-3,8) {}; \node[big1] (v1c) at (-1.5,8) {};
+%	\node[big1] (v2) at  ( 2.5,8) {}; \node[big1] (v2) at ( 2.5,8) {};
+%	\draw[rounded corners] (-4.5,7) rectangle (-0.5,9);
+%	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
+%	\draw (-0.5,8)--(0.5,8);
+%	\node[circ] (v) at (0,6) {};
+%	%
+%	\begin{scope}[thepink,->]
+%		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
+%		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
+%		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
+%		\draw[big>,bend right=20] (e1) to (a1);  \draw[big>,bend right=20] (e2) to (a2);  \draw[big>, bend right=20] (e3) to (a3);
+%	\end{scope}
+%  \end{tikzpicture}
+%}
+
+\[
+	\big(\bigparr_{k\times c(v_i)}\big(\bigparr_{3i+2}1 \tn \bigparr_{3(n-i)+3}1\big) \big)\parr 1
+\]
+\[
+	\big(\bigotimes_{k\times w(e)}\big(\bigotimes_{3i+2}\bot\parr\bigotimes_{3(j-i)+1}\bot\parr\bigotimes_{3(n-j)+3}\bot\big)\big)\tn\bot
+\]
+
+\[
+	C = \bigparr(1^{3i+2}) \tn \bigparr(1^{3(n-i)+3})
+\]
+
+\[
+	\big(\bigparr C^{k\times c(v_i)} \big)\parr 1
+\]
+
+\[
+	W = \bigotimes(\bot^{3i+2})\parr\bigotimes(\bot^{3(j-i)+1})\parr\bigotimes(\bot^{3(n-j)+3}
+\]
+
+\[
+	\big(\bigotimes W^{k\times w(e)}\big)\tn\bot
+\]

### 2014-01-19 main/LICS.tex
working on "completeness"

@@
 \graphicspath{{../notes/}}
-
-\let\alt=\underline
-\let\bigtn=\bigotimes
-
-\newcommand\NoIndent[1]{%
-  \par\vbox{\parbox[t]{\linewidth}{#1}}%
-}
 
@@
 To conclude this section we will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets.
+%
+Firstly we will look at subnets---see also \cite{Bellin-vandeWiele-1995}.
 
@@
 	\item
-for each $\named v\parr$, the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents $s(w)$ are contracted.
+for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents are contracted.
 \end{enumerate}
@@
 %
-These will instead connect to additional, separate $\1$-formulae, referred to as \emph{edge-absorbers}, as follows.
+These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as follows.
 %
@@
 %
-In such an inappropriate linking, since both halves of the constraint element are connected, both weight elements may not be---otherwise, the linking would violate the switching condition.
-%
-That means the weight elements must belong to different edges; and moreover, for the same reason these two edges cannot fill another constraint element together.
+In such an inappropriate linking, since both halves of the constraint element are connected, both weight elements must be disconnected---otherwise, the linking would violate the switching condition.
+%
+That means the weight elements must belong to different edges.
+%
+For the same reason, to fill the next weight element, one half may be filled by a weight element from a previous edge, but to fill the other half requires an additional edge to be involved.
 %
@@
 
-The complete encoding of a constraint graph will be a sequent consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of edge-absorbers ($\1$-formulae).
+The complete encoding of a constraint graph will be a sequent consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
 %
@@
 
-In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{edge-absorbers}.
+In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{weight absorbers}.
 %
@@
 %
-Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
 \end{definition}
@@
 %
-The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the edge-absorbers within scopes of weight elements inside $\itn e$.
+The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the weight absorbers within scopes of weight elements inside $\itn e$.
 %
@@
 
+\begin{figure*}
+\[
+	\vc{\doubleExchange uvxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyx}
+\]
+\caption{Double exchange of links}
+\label{fig:double exchange}
+\end{figure*}
+
 %------------------------------------------------------------
 
-\section{Equivalence in the absence of $~\protect\parr$}
+\section{Rewiring proof nets}
+
+In this section we will explore the global rewiring behaviour of proof nets.
+%
+In particular, we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+%
+Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
+
+Before turning to this fragment there is the following lemma for full MLL, which states that (under the given connectedness conditions) equivalence is preserved by a double exchange of links.
+
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $\edge bv$ and $\edge xc$.
+%
+Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{IEEEproof}
+By the rewiring path shown in Figure~\ref{fig:double exchange}.
+\end{IEEEproof}
 
@@
 
-\begin{lemma}
-\label{lem:double exchange}
-Let $\links$ be a proof net where $\links(a)=(u)$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $b-v$ and $x-c$.
-%
-Then $\links\sim\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
-\end{lemma}
-
-\begin{IEEEproof}
-\[
-\begin{array}{@{}ccccc@{}}
-	\vc{\doubleExchange uvxy}
-	&\perm&
-	\vc{\doubleExchange uyxy}
-	&\perm&
-	\vc{\doubleExchange uyxu}
-	\\
-	\\
-	\vc{\doubleExchange vuyx}
-	&\perm&
-	\vc{\doubleExchange vuyu}
-	&\perm&
-	\vc{\doubleExchange vyyu}
-\end{array}
-\begin{array}{@{~}c@{~}c@{}}
-	\indirection{ul}{\perm} \\ \\[20pt]
-	\indirection{dl}{\perm}
-\end{array}
-\vc{\doubleExchange vyxu}
-\]
-\end{IEEEproof}
+%------------------------------------------------------------
+
+\section{Correctness of the encoding}
+
+In this section we will establish that in our encoding of constraint graphs %partial \textsc{ncg}-reconfiguration 
+in MLL, reconfiguration on graphs is captured by proof equivalence in MLL.
+%
+Up to minor technical details, it will be shown that $\itn\gamma\perm\itn\delta$ if and only if $\gamma\perm\delta$, in two parts: completeness ($\Leftarrow$) and soundness ($\Rightarrow$).
 
@@
 
-In a proof net for $\itn G$, an edge-gadget $\itn e$ that is in the empire of an appropriate vertex-gadget $\itn v$ is \emph{naturally linked} if the indicator of $\itn e$ connects to the indicator of $\itn v$, and each weight element $W$ of $\itn e$ is either naturally linked to a constraint element $C$ in $\itn v$ or linked only to edge-absorbers.
+Given a reconfiguration path $\gamma\perm\delta$ over total configurations, we will demonstrate a rewiring sequence between $\itn\gamma$ and $\itn\delta$ up to, possibly, a single exchange of two links in $\itn\delta$.
+%
+The central part of the argument will be to show how the weight element linking to a constraint element may be exchanged for another.
+%
+Once the weight elements of an edge-gadget are no longer connected to any constraint elements, the edge-gadget may straightforwardly be moved from one vertex-gadget to another by re-attaching its indicator link.
+%
+Throughout the rewiring process, weight elements and constraint elements will be kept in a standard linking, and according to the connectivity specified by the target configuration $\itn\delta$.
+%
+Linkings between weight elements and weight absorbers will remain arbitrary, and will be re-adjusted to match $\itn\delta$ at the end of the process.
+
+In a proof net for $\itn G$, an edge-gadget $\itn e$ is \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or linked only to weight absorbers.
+%
+A well-linked edge-gadget is \emph{free} if all its weight elements connect to weight absorbers.
+%
+In the following main lemma we will exchange the weight element linking to a constraint element.
+%
+The lemma considers a sequent consisting of just a vertex-gadget, some appropriate edge-gadgets, and sufficiently many weight absorbers.
 
@@
 \label{lem:octopus roll}
-In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is naturally linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to edge-absorbers $\bot^n$, then there is a net $\links'\sim\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
+In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $\bot^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}
+
+\renewcommand\scalefactor{0.88}
+
+\newcommand\displayOcto[1]{%
+ \NoIndent{%
+   \smallskip%
+   \centerline{%
+	 \scale{#1}%
+  }}%
+  \bigskip%
+}
 
@@
 %
-We will illustrate the path of permutations for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
+The path of permutations will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
 %
@@
 	\item
-The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
-\NoIndent{
-\[
-	\octorollA1
-\]
-}
-	\item
-The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
-\NoIndent{
-\[
-	\octorollB2
-\]
-}
-	\item
-Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
-\NoIndent{
-\[
-	\octorollB3
-\]
-}
+The initial configuration is illustrated below. 
+%
+Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
+%
+The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.
+%
+\displayOcto{\octorollA1}
+
+	\item
+The link $i-v$ is re-attached to connect to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
+%
+\displayOcto{\octorollB2}
+
+	\item
+Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.
+%
+\displayOcto{\octorollB3}
+
 	\item\label{item:exchange added}
-There are subnets over the sub-sequents $A,B,X,D,\bot^m$ and $C,Y,E,F,\bot^k$.
-%
-These subnets may be rewired so that $D\parr E\parr F$ is naturally linked to $X\tn Y$: by Proposition~\ref{prop:parity determines equivalence}, the resulting subnets are equivalent as long as their parity is preserved.
-%
-Two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step \ref{item:exchange needed} below.
-%
-The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
-\NoIndent{
-\[
-	\octorollC
-\]
-}
-	\item
-The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
-\NoIndent{
-\[
-	\octorollD1
-\]
-}
+In the present configuration, the links from the weight elements form two subnets: one over the sub-sequents $A,B,X,D,\bot^m$, and one over the sub-sequent $C,Y,E,F,\bot^k$, for some $m$ and $k$.
+%
+By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
+%
+It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step \ref{item:exchange needed} below.
+%
+The links of $A,B,C$ link to the weight absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+%
+\displayOcto{\octorollC}
+
+	\item
+The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
+%
+\displayOcto{\octorollD1}
+
 	\item\label{item:exchange needed}
@@
 Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
-\NoIndent{
-\[
-	\octorollD2
-\]
-}
-	\item
-The link from $i$ may be re-attached to $v$ to yield the final configuration.
-\NoIndent{
-\[
-	\octorollA2
-\]
-}
+%
+\displayOcto{\octorollD2}
+
+	\item
+The link from $i$ is re-attached to $v$ to yield the final configuration.
+%
+\displayOcto{\octorollA2}
+
 \end{enumerate}
@@
 
-An edge-gadget $\itn e$ is \emph{free} if each of its weight elements is linked only to edge-absorbers.
+In the exchange of weight elements in the above lemma, weight elements link to weight absorbers in arbitrary fashion.
+%
+The next lemma will demonstrate how weight absorbers can be exchanged freely, but only with two exchanges at once.
+
+%% WORKING HERE
 
 \begin{lemma}
-\label{lem:permute edge-absorbers}
-If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
+\label{lem:permute weight absorbers}
+If $\links$ is a well linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of weight absorbers, then $\links\perm\links'$.
 \end{lemma}
@@
 \begin{IEEEproof}
-Let $e_0$ be the indicator vertex of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
+Let $e_0$ be the indicator of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
 %
@@
 	\item
-To permute two edge-absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.
+To permute two weight absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.
 
@@
 	\item
-To exchange an edge-absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, and attach $e_0$ to $w$, attach $d$ to $v$.
+To exchange a weight absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, and attach $e_0$ to $w$, attach $d$ to $v$.
 %
@@
 	\item
-Finally, to permute edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
+Finally, to permute weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
 %
@@
 
-In each case, if one of the edge-absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
+In each case, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
 
@@
 
-Let $\itn\gamma'$ be $\itn\gamma$ where the first two edge-absorbers are exchanged.
+Let $\itn\gamma'$ be $\itn\gamma$ where the first two weight absorbers are exchanged.
 
@@
 %
-The resulting proof net is $\itn\delta$ modulo a permutation of edge-absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute edge-absorbers}.
+The resulting proof net is $\itn\delta$ modulo a permutation of weight absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute weight absorbers}.
 \end{IEEEproof}

### 2014-01-19 main/scratch.tex
working on "completeness"

@@
 
-%\makeTheoremDefs
+\makeTheoremDefs
 
@@
 
-\[
-\begin{tikzpicture}[x=-5mm,y=5mm,octo]
-	\node[big_] (A) at (-1,2) {};
-	\node[big1] (!) at (-1,0) {};
-	\node at (.5,1) {$\Rightarrow$};
-	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
-	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
-	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
-	\begin{scope}[thepink,->]
-			\draw[big>] (A) to (!.center);
-			\draw[bend right=10] (a) to (1.center);
-			\draw[bend right=10] (b) to (2.center);
-			\draw[bend right=10] (c) to (3.center);
-	\end{scope}
-\end{tikzpicture}
-\]
-
-\[
-\vc{
-  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (0,0) node[bullet] (a) {}--
-		  (1,0) node[bullet] (b) {}--
-		  (2,0) node[bullet] (c) {};
-	\draw (4,0) node[bullet] (d) {}--
-		  (5,0) node[bullet] (e) {}--
-		  (6,0) node[bullet] (f) {}--
-		  (7,0) node[bullet] (g) {};
-	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
-	\begin{scope}[thepink,->]
-			\draw[bend right=10] (a) to (1);
-			\draw[bend right=10] (b) to (2);
-			\draw[bend right=10] (c) to (3);
-			\draw[bend left=10]  (d) to (3);
-			\draw[bend left=10]  (e) to (4);
-			\draw[bend left=10]  (f) to (5);
-			\draw[bend left=10]  (g) to (6);
-	\end{scope}
-  \end{tikzpicture}
-}
-\quad\Rightarrow\quad
-\vc{
-  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-1,0) {$2'$};
-	\node[big_] (B) at ( 1,0) {$3'$};
-	\node[big1] (!) at ( 0,3) {$5'$};
-	\begin{scope}[thepink,->,big>]
-		\draw[bend right=15] (A) to (!);
-		\draw[bend left=15]  (B) to (!);
-	\end{scope}
-  \end{tikzpicture}
-}
-\]
-
+\end{document}
 %
-%\[
-%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-%	\draw (-1.75,0) node[bullet] (x) {} -- (-.75,0) node[bullet] (y) {}
-%		  (  .75,0) node[bullet] (a) {} -- (1.75,0) node[bullet] (b) {}
-%		  ( 3.25,0) node[bullet] (c) {} -- (4.25,0) node[bullet] (d) {};
-%	\node[circ] (0) at (5.75,0) {};
-%	\node[circ] (1) at (-1,3) {};
-%	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
-%	\draw[rounded corners] (0,2) rectangle (4,4);
-%	\draw (4,3) -- (5,3) node[bullet] (e) {};
-%	\begin{scope}[thepink,->]
-%			\draw[bend right=10] (x) to (1.center);
-%			\draw[bend right=20] (y) to (2.center);
-%			\draw[bend right=10] (a) to (2.center);
-%			\draw[bend right=10] (b) to (3.center);
-%			\draw[bend left=10]  (c) to (3.center);
-%			\draw[bend left=10]  (d) to (4.center);
-%			\draw[bend right=10] (e) to (0.center);
-%	\end{scope}
-%\end{tikzpicture}
-%\]
-
-\end{document}
-
-\begin{frame}
-	\octorollA1
-\end{frame}
-
-\begin{frame}
-	\octorollB1
-\end{frame}
-
-\begin{frame}
-	\octorollB2
-\end{frame}
-
-\begin{frame}
-	\octorollB3
-\end{frame}
-
-\begin{frame}
-	\octorollC
-\end{frame}
-
-\begin{frame}
-	\octorollD1
-\end{frame}
+%
+%\begin{frame}
+%	\octorollA1
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollB1
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollB2
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollB3
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollC
+%\end{frame}
+%
+%\begin{frame}
+%	\octorollD1
+%\end{frame}
 %

### 2014-01-19 main/LICS.tex
working on "soundness"

@@
 	\item
-sub-sequents are strictly nested: if $\named w\parr$ occurs in $s(v)$ then $s(w)<s(v)$; and
+sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
 	\item
@@
 
-Finally, the standard notion of \emph{balance} is useful in constructing proof nets without $\parr$-connectives
+Finally, the standard notion of \emph{balance} provides an easy way of identifying some unprovable sequents.
 
@@
 
-An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
+\begin{proposition}
+\label{prop:unbalanced then uninhabited}
+An unbalanced sequent is uninhabited.
+\end{proposition}
+
+%A positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
 %
@@
 
-%
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding when two configurations for a constraint graph are connected in the graph of total configurations and reconfiguration steps.
-%
-\emph{Partial \textsc{ncg}-reconfiguration} is the same problem for partial configurations.
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding whether two total configurations for a constraint graph are connected by a sequence of reconfiguration steps.
+%
+%By the above proposition, \textsc{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
 
@@
 
-By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
-
-\begin{proposition}
-Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
-%\textsc{pncg}-reconfiguration is \textsc{pspace}-complete.
-\end{proposition}
-
-We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL proof nets.
+%By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
+%
+%\begin{proposition}
+%Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+%%\textsc{pncg}-reconfiguration is \textsc{pspace}-complete.
+%\end{proposition}
+
+We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of \textsc{ncg}-reconfiguration in MLL proof nets.
 
@@
 \label{def:graph encoding}
-The \emph{encoding} $\itn G$ of a constraint graph $G=(V,E,c,v,w)$ is a sequent constructed as follows.
-%
-Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
+The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows.
+%
+Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
 
@@
 
-%% WORKING HERE
-
 \begin{lemma}
@@
 	\item
-To exchange a weight absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, and attach $e_0$ to $w$, attach $d$ to $v$.
+To exchange a weight absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, first attach $e_0$ to $w$, then re-attach $d$ to $v$.
 %
@@
 	\item
-Finally, to permute weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
+Finally, to permute weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator target of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator $d_0$ and an arbitrary other $\bot$-occurrence $d_1$.
 %
@@
 
-Let $\itn\gamma'$ be $\itn\gamma$ where the first two weight absorbers are exchanged.
+For any configuration $\gamma$ let $\itn\gamma'$ denote $\itn\gamma$ where the first two weight absorbers are exchanged.
 
 \begin{lemma}
-If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\sim\itn\delta$ or $\itn\gamma\sim\itn\delta'$.
+\label{lem:completeness}
+If $\gamma\perm\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\perm\itn\delta$ or $\itn\gamma\perm\itn\delta'$.
 \end{lemma}
@@
 \begin{IEEEproof}
-We will prove the case where $\gamma\sim\delta$ is a single reconfiguration step; the general case follows because the proof goes through also when $\itn\gamma'$ replaces $\itn\gamma$ in the statement of the lemma.
-%
+By Proposition~\ref{prop:partial simulates total reconfiguration} we may assume that $\gamma\perm\delta$ by a sequence of reconfiguration steps over total configurations.
+%
+We will prove that if $\gamma\perm*\delta$ then $\itn\gamma\perm\itn\delta$ or $\itn\gamma\perm\itn\delta'$.
+%
+The same proof will show the corresponding case for $\itn\gamma'$ instead of $\itn\gamma$, so that the general case for $\gamma\perm\delta$ follows by transitivity.
+
 Let $\gamma$ and $\delta$ agree on every edge except $e$, where $\gamma(e)=v$ and $\delta(e)=w$.
@@
 %
-Next, the indicator vertex of $\itn e$, which links to the indicator of $\itn v$, is re-attached to the indicator of $\itn w$.
+Next, the indicator vertex of $\itn e$, which links to the indicator target of $\itn v$, is re-attached to the indicator target of $\itn w$.
 %
@@
 \subsection*{Soundness}
+
+It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta$ is sound for \textsc{ncg}-reconfiguration, $\gamma\perm\delta$.
+%
+To each proof net $\links$ for an encoded constraint graph $\itn G$ we will associate a partial configuration $\gamma=\coitn\links$, such that 1) a rewiring step $\links\perm*\links$ corresponds to a reconfiguration path $\coitn\links\perm\coitn{\links'}$, and 2) it is a retraction of the encoding of configurations, $\coitn{\itn\gamma}=\gamma$.
+
+The configuration $\coitn\links$ will assign an edge $e$ to a vertex $v$ when, in the proof net $(\links,\itn G)$, the edge-gadget $\itn e$ is in the empire of the vertex-gadget $\itn v$.
+%
+Firstly, it will be shown that $\coitn\links$ is a partial function.
+
+\begin{proposition}[{\cite[Proposition 1.i]{Bellin-vandeWiele-1995}}]
+\label{prop:tensor has disjoint subnets}
+In a proof net, if vertices $v$ and $w$ are joined by a tensor, then any two subnets of which they are respective ports are disjoint.
+\end{proposition}
 
@@
 \begin{IEEEproof}
-Since vertex-gadgets are joined by a tensor, the lemma is immediate from \cite[Proposition 1]{Bellin-vandeWiele-1995}.
+Since vertex-gadgets are joined by a tensor, the lemma is immediate from Proposition~\ref{prop:tensor has disjoint subnets}.
 \end{IEEEproof}
+
+Next, it will be shown that the appropriate edge-gadgets in the empire of a vertex-gadget $\itn v$ contain sufficient weight elements to fill the constraint elements of $\itn v$.
 
@@
 \label{lem:appropriate edge weights}
-In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
+In a proof net for $\itn G$, for each node $v$ in $G$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
 \end{lemma}
@@
 \]
-The two $\parr$-subformulae have a balance of $-3i-1$ and $-3(n-i)-2$ respectively.
+The two $\parr$-subformulae have a balance of $-3i-1$ and respectively $-3(n-i)-2$.
 %
@@
 \]
-The three $\tn$-subformulae have a net balance of $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
-%
-In pairs, they have a net balance of $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
-%
-Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$, it follows that $W$ can balance the scope of at most one of both subformulae of $C$.
+For each of the three $\tn$-subformulae, adding it to the scope of a $\parr$ will change its balance by $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
+%
+In pairs, they add to the balance of a scope by $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
+%
+Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$ (by Proposition~\ref{prop:tensor has disjoint subnets}), it follows that $W$ can balance the scope of at most one of both $\parr$-subformulae of $C$.
 
@@
 
+%% WORKING HERE
+
 \begin{lemma}
-If $\links\sim\links'$ are proof nets for $\itn G$ then $\coitn\links\sim\coitn{\links'}$.
+If $\links\perm\links'$ are proof nets for $\itn G$ then $\coitn\links\perm\coitn{\links'}$.
 \end{lemma}
@@
 \begin{IEEEproof}
+The proof will consider the case where $\links\perm*\links'$; the general case follows by transitivity.
+%
 A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.

### 2014-01-19 main/LICS.tex
completed soundness proof

@@
 
-%% WORKING HERE
+To show that rewiring corresponds to reconfiguration under $\coitn-$, we will use the following lemmata.
 
 \begin{lemma}
+\label{lem:rewiring within empire}
+For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
+%
+\begin{enumerate}
+	\item
+$\links\perm*\links'$ where $\links'(a)=w$;
+	\item
+$w$ is in the empire of $a$; and
+	\item
+in any switching graph for $(\Gamma,\links)$, the path from $v$ to $w$ does not pass through $a$.
+\end{enumerate}
+\end{lemma}
+
+\begin{IEEEproof}
+By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.
+
+Next, the empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
+%
+By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net $\sigma$, $a$ may link anywhere in $\sigma$.
+%
+Then 2 implies 1.
+
+Finally, if $\links'$ is a net, and for some switching of $\links$ the path from $v$ to $w$ passes through $a$, then in $\links'$ there is no path between $a$ and $v$ (and two paths between $a$ and $w$) for that switching; then 1 implies 3.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:rewiring preserves empire}
+Let $\links\perm*\links'$ by $\links(a)\neq\links'(a)$, and denote the empire of $a$ in $\links$ and $\links'$ by $\sigma$ and $\sigma'$ respectively; then $\sigma\perm*\sigma'$.
+\end{lemma}
+
+\begin{IEEEproof}
+By Lemma~\ref{lem:rewiring empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae.
+%
+That they must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:rewiring affects empires}
+For proof nets $\links\perm*\links'$, let the empire of a given vertex $v$ in $\links$ be a net for the sequent $\Delta$, and in $\links'$, for $\Delta'$; then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
+\end{lemma}
+
+\begin{IEEEproof}
+By \cite[Proposition 2.b]{Bellin-vandeWiele-1995} the empire of $v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) down from one subformula into a tensor; 4) down from all subformulae into a par; 5) but never down from $v$.
+%
+Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
+%
+There are four cases.
+%
+\begin{enumerate}
+	\item
+If the empire of $v$ is propagated from $a$ to $w$ in $\links$, it includes the empire of $a$.
+%
+Then by Lemma~\ref{lem:rewiring preserves empire} $\Delta=\Delta'$.
+
+	\item
+If the empire of $v$ includes $w$ but not $w'$, then it is propagated through $a$ in $\links$ but not in $\links'$, so that $\Delta\geq\Delta'$.
+
+	\item
+If the empire of $v$ includes $w'$ but not $w$, then $\Delta\leq\Delta'$.
+
+	\item
+Otherwise, $\Delta=\Delta'$.
+\end{enumerate}
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:soundness}
 If $\links\perm\links'$ are proof nets for $\itn G$ then $\coitn\links\perm\coitn{\links'}$.
@@
 %
-A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.
-%
-Then in both $\coitn\links$ and $\coitn{\links'}$ the edges $e_1$ through $e_n$ are mobile, since by Lemma~\ref{lem:appropriate edge weights} the empires of the vertex-gadgets $\itn v$ (in cases 1 and 3) and $\itn w$ (in cases 2 and 3) contain appropriate edge-gadgets other than $\itn{e_1}$ through $\itn{e_n}$ of sufficient combined weight.
-%
-It follows that in the graph $G$ the edges $e_1$ through $e_n$ can be moved away from $v$ and/or onto $w$ one at a time.
-
+By Lemma~\ref{lem:rewiring affects empires}, the empire of each vertex-gadget $\itn v$ contains either a subset of, a superset of, or exactly the same edge-gadgets in $\links'$ as it does in $\links$.
+%
+Let $\itn e_1$ through $\itn e_n$ be the edge-gadgets moving in or out of the empire of $\itn v$.
+%
+By Lemma~\ref{lem:appropriate edge weights} other edge-gadgets must fill the constraint elements of $\itn v$.
+%
+Then the corresponding edges $e_1$ through $e_n$ are mobile in $\coitn\links$ and it follows that $\coitn\links\perm\coitn{\links'}$ by moving each $e_i$ in turn, and repeating the same for other vertices.
+%
 \end{IEEEproof}
@@
 
-\section{Conclusions}
+\section{MLL proof equivalence is \textsc{pspace}-complete}
 

### 2014-01-19 main/scratch.tex
completed soundness proof

@@
 
-\usepackage{amsmath,amsthm}
+\usepackage{amsmath,amssymb,amsthm}
 \usepackage{mllequiv,willemtools}
@@
 \begin{document}
+
+\[
+	\lesssim \gtrsim
+\[
+
+\end{document}
+
+\begin{lemma}
+For a proof net $(\Gamma,\links)$, if the linking $\links'$ agrees with $\links$ on all values except $\links'(a)=v$, then $\links'$ is a proof net if and only if $v$ is in the empire of $a$ in $(\Gamma,\links)$.
+%
+%If $\links\perm*\links'$ by rewiring the link $\links(a)=v$ to $\links'(a)=w$, then $w$ is in the empire of $a$ in the proof net $\links$.
+\end{lemma}
+
+\begin{proof}
+The empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
+%
+In one direction, by Definition~\ref{def:proofs to nets} $a$ may link anywhere in a translation of $\Sigma$ to a net; if $\named v\1$ is in $\Sigma$, then $\links'$ is a net.
+%
+In the other direction, if $\links\perm*\links'$, then for any switching of $(\Gamma,\links')$ there is a path from $\links(a)=w$ to
+
+%%Let $\sigma$ be the empire of $a$ in $(\Gamma,\links)$.
+%%
+%In one direction, if $v$ is in $\sigma$, then since $\sigma$ is a subnet, for any switching of $\sigma$ there is a path from $\links(a)$ to $v$ not passing through $a$.
+%%
+%Then if $\sigma'\perm*\sigma$ by 
+%
+% $\sigma$ minus the link $\edge a{\links(a)}$ is a subnet, 
+%
+%By definition, $\sigma$ is the largest subnet with $a$ as a port.
+%%
+%Then there is a proof $\Sigma\tonet\sigma$ with as conclusion the introduction rule for $\named a\bot$, which 1) is a subproof of some sequent proof $\Pi\tonet\links$, and 2) is the largest subproof of $\named a\bot$ among all $\Pi\tonet\links$.
+%
+%
+%In one direction, if $\links'$ is a proof net, then $\links\perm*\links'$, and there is a $\Pi'\tonet\links'$ such that $\Pi\perm\Pi'$ by permuting the introduction rule for $\named a\bot$.
+%%
+%But since permuting this rule in $\Pi$ cannot give it a larger subnet than $\Sigma$ (by 2 above), $\named v\1$ must be in $\Sigma$, and $v$ in $\sigma$.
+%
+%By Definition~\ref{def:proofs to nets}
+
+\end{proof}
 

### 2014-01-19 main/LICS.tex
added main theorem

@@
 \end{enumerate}
+\vskip-12pt
 \end{IEEEproof}
@@
 \section{MLL proof equivalence is \textsc{pspace}-complete}
+
+We are now ready to state our main theorem.
+
+\begin{theorem}
+MLL proof equivalence is \textsc{pspace}-complete.
+\end{theorem}
+
+\begin{IEEEproof}
+MLL proof equivalence has at most non-deterministic polynomial space complexity: a proof net may be represented in linear space (with respect to a proof); a single rewiring step is performed without requiring additional space; and a non-deterministic algorithm may guess the correct rewiring sequence.
+%
+Then by Savitch's Theorem \cite{Savitch-1970} MLL proof equivalence is in \textsc{pspace}.
+
+\textsc{pspace}-hardness follows by the encoding of \textsc{ncg}-reconfiguration, which in its completed form is stated:
+\[
+	\gamma\perm\delta \qquad\iff\qquad \itn\gamma\perm\itn\delta \text{ or } \itn\gamma\perm\itn\delta'~.
+\]
+%
+The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and the observation that $\coitn{\itn\gamma}=\coitn{\itn\gamma'}=\gamma$.
+%
+\end{IEEEproof}
 

### 2014-01-20 main/LICS.tex
Minor tweaks to intro

--- 2014-01-19 main/LICS.tex
@@
 \graphicspath{{../notes/}}
+
+\let\alt=\underline
+
+\newcommand\NoIndent[1]{%
+  \par\vbox{\parbox[t]{\linewidth}{#1}}%
+}
 
@@
 		Kiln Enterprises
-	\\	robin.houston@gmail.com	
-	}
-}
-
-%\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete}
-
-%\title{Proof equivalence in MLL is \textsc{pspace}-complete}
+	\\	robin@kiln.it
+	}
+}
 
@@
 %
-As a main corrolary, this effectively rules out the possibility of finding a satisfactory notion of proof net for this fragment.
+As a main corollary, this effectively rules out the possibility of finding a satisfactory notion of proof net for this fragment.
 
@@
 
-The proof of the \textsc{pspace}-completeness result relies on a polynomial reduction from %the configuration--to--configuration problem in
+The proof of \textsc{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in
 \emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
 %
-It consists of a simple graph rewriting mechanism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied, and asks whether two graphs are related in a series of valid rewriting steps.
+Constraint logic is a simple graph rewriting mechanism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied; the configuration-to-configuration question is whether two graphs are related by a sequence of valid rewriting steps.
 
@@
 %
-For example, for boolean satisfyability (SAT) the reconfiguration problem asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
+For example, for boolean satisfiability (SAT) the reconfiguration problem asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
 %
@@
 %
-The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively;
-%
-formulae related by a tensor will be connected by edges; 
-and
-formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
+The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
+%
+%
+%% NEW
+%
+Formulae related by a tensor will be connected by edges.
+%
+Formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
 %
@@
 %
-Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
-%
-In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
-%
-A linking between $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
-\[
-\begin{tikzpicture}[x=-5mm,y=5mm,octo]
+Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigotimes\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
+%
+In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigotimes(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
+%
+A linking between $\bigotimes(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
 	\node[big_] (A) at (-1,2) {};
 	\node[big1] (!) at (-1,0) {};
-	\node at (.5,1) {$\Rightarrow$};
+	\node at (.5,1) {$\coloneq$};
 	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
@@
 \]
-Two formulae $\bigtn(\bot^{i+1})$ and $\bigtn(\bot^{j+1})$ may together connect to a formula $\bigparr(\1^{i+j+1})$, as illustrated below for $i=2$ and $j=3$.
-%
-Nodes will be labelled $i'$ for $i+1$, so that both the abbreviated formulae and the arithmetic of connecting them remain intuitive.
-%
-\[
-\vc{
-  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (0,0) node[bullet] (a) {}--
-		  (1,0) node[bullet] (b) {}--
-		  (2,0) node[bullet] (c) {};
-	\draw (4,0) node[bullet] (d) {}--
-		  (5,0) node[bullet] (e) {}--
-		  (6,0) node[bullet] (f) {}--
-		  (7,0) node[bullet] (g) {};
-	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
-	\begin{scope}[thepink,->]
-			\draw[bend right=10] (a) to (1);
-			\draw[bend right=10] (b) to (2);
-			\draw[bend right=10] (c) to (3);
-			\draw[bend left=10]  (d) to (3);
-			\draw[bend left=10]  (e) to (4);
-			\draw[bend left=10]  (f) to (5);
-			\draw[bend left=10]  (g) to (6);
-	\end{scope}
-  \end{tikzpicture}
-}
-\quad\Rightarrow\quad
-\vc{
-  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-1,0) {$2'$};
-	\node[big_] (B) at ( 1,0) {$3'$};
-	\node[big1] (!) at ( 0,3) {$5'$};
-	\begin{scope}[thepink,->,big>]
-		\draw[bend right=15] (A) to (!);
-		\draw[bend left=15]  (B) to (!);
-	\end{scope}
-  \end{tikzpicture}
-}
-\]
-
-Finally, that two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
+
+That two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
 \[
@@
 
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{Subnets}
-
-To conclude this section we will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets.
-%
-Firstly we will look at subnets---see also \cite{Bellin-vandeWiele-1995}.
-
-\begin{definition}
-A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
-\end{definition}
-
-\begin{definition}
-A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
-\end{definition}
-
-The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
-%
-A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
-%
-In a proof net, the \emph{kingdom} and the \emph{empire} of a par are respectively its smallest and largest scope.
-
-The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
-%
-In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
-%
-In the example below, the kingdom of a (ternary) par is indicated (left) and contracted (right).
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
-		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
-		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
-	\node[circ] (0) at (5.75,0) {};
-	\node[circ] (1) at (-1,3) {};
-	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
-	\draw[rounded corners] (0,2) rectangle (4,4);
-	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
-	\begin{scope}[thepink,->]
-			\draw[bend right=10] (x) to (1);
-			\draw[bend right=20] (y) to (2);
-			\draw[bend right=10] (a) to (2);
-			\draw[bend right=10] (b) to (3);
-			\draw[bend left=10]  (c) to (3);
-			\draw[bend left=10]  (d) to (4);
-			\draw[bend right=10] (e) to (0);
-	\end{scope}
-	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
-	\node[circ] (0) at (3,0) {};
-	\node[circ] (1) at (-1,3) {};
-	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
-	\draw (box)--(3,3) node[bullet] (e) {};
-	\begin{scope}[thepink,->]
-			\draw[bend right=10] (x) to (1);
-			\draw[bend right=20] (y) to (box);
-			\draw[bend right=10] (e) to (0);
-	\end{scope}
-	\path (0,4.25)--(1,4.25);
-\end{tikzpicture}
-\]
-%
-The contraction of scopes may replace the switching condition as a correctness criterion.
-%
-The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
-
-\begin{proposition}
-\label{prop:scoping correctness}
-A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
-
-\begin{enumerate}
-	\item
-sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
-	\item
-for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents are contracted.
-\end{enumerate}
-
-\end{proposition}
-
-\begin{IEEEproof}
-For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
-%
-For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
-\[
-	\infer{\Delta,A\named v\parr B}{\Delta,A,B}
-\]
-\end{IEEEproof}
-
-Finally, the standard notion of \emph{balance} provides an easy way of identifying some unprovable sequents.
-
-\begin{definition}
-The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
-%
-A sequent is \emph{balanced} if its balance is zero.
-\end{definition}
-
-\begin{proposition}
-\label{prop:unbalanced then uninhabited}
-An unbalanced sequent is uninhabited.
-\end{proposition}
-
-%A positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
-%
-%An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
-%
-
 %------------------------------------------------------------
 
-\section{Encoding constraint logic}
-
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
-%
-A rewrite step consists of the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex.
-%
-Rewrite steps must preserve the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
-%
-The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-
-We will introduce minor adaptations to this formalism to suit our reduction to MLL proof equivalence.
-%
-Mainly, a constraint graph itself will have \emph{undirected} edges, while a separate notion of \emph{configuration} imposes a direction on them.
-%
-A constraint graph may then be encoded as a sequent, and a configuration as a proof net.
-%
-In addition, we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
-
-\begin{definition} 
-A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting vertices $v(e)=\{v_1,v_2\}\subseteq V$.
-%of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
-
-\smallskip
-
-A \emph{(partial) configuration} for a constraint graph is a (partial) function $\gamma\colon E\to V$ such that
-\begin{itemize}
-	\item
-for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
-	\item
-for every vertex $v$, the total weight of its incoming edges is at least its inflow constraint, 
-%$\sum\{\kern1pt w(e)\kern1pt|\kern1pt\gamma(e)=v\kern1pt\}\geq c(v)$.
-$\sum\{w(e)\mid\gamma(e)=v\}\geq c(v)$.
-\end{itemize}
-
-\smallskip
-A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \textsc{ncg} $G$ that differ in value (or definedness) on exactly one edge.
-%
-The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
-%
-\end{definition}
-
-\begin{proposition}
-\label{prop:partial simulates total reconfiguration}
-For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
-\end{proposition}
-
-\begin{IEEEproof}
-By the following two observations: firstly, 
-%
-if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
-%
-if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
-%
-\end{IEEEproof}
-
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding whether two total configurations for a constraint graph are connected by a sequence of reconfiguration steps.
-%
-%By the above proposition, \textsc{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
-
-\begin{theorem}[\cite{Hearn-Demaine-2005}]
-\textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
-\end{theorem}
-
-%By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
-%
-%\begin{proposition}
-%Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
-%%\textsc{pncg}-reconfiguration is \textsc{pspace}-complete.
-%\end{proposition}
-
-We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of \textsc{ncg}-reconfiguration in MLL proof nets.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{The encoding}
-
-The basis of the encoding of constraint graphs in MLL is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
-%
-The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
-%
-Below left is a weight element, below right a constraint element.
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {$i'$}; 
-	\node[big_] (B) at (2,0) {$j'$};
-	\node[big_] (C) at (4,0) {$k'$};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big1] (1) at (0,0) {$m'$}; 
-	\node[big1] (2) at (3,0) {$n'$};
-	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
-	\draw (1,0)--(2,0);
-\end{tikzpicture}
-\]
-For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
-%
-The value of $m$ (and thus $n$) will differ for each vertex.
-%
-The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
-\[
-	\connectingElements 1 \qquad \connectingElements 2
-\]
-To ensure that no other connections can be made, values are chosen such that $m\bmod3=1$ and $n\bmod3=2$, and accordingly $i\bmod3=1$, $j\bmod3=0$, and $k\bmod3=2$.
-
-In a constraint graph, the sum of weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
-%
-An encoding will therefore have weight elements not connected to constraint elements.
-%
-These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as follows.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {}; 
-	\node[big_] (B) at (2,0) {};
-	\node[big_] (C) at (4,0) {};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-	\node[big1] (1) at (7.5,0) {};
-	\begin{scope}[thepink,->,big>]
-		\draw[bend left=30] (A) to (1);
-		\draw[bend right=30] (B) to (1);
-		\draw (C) to (1);
-	\end{scope}
-\end{tikzpicture}
-\]
-%
-An edge will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements plus a single \emph{indicator} vertex.
-%
-Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {$i'$}; 
-	\node[big_] (B) at (2,0) {$j'$};
-	\node[big_] (C) at (4,0) {$k'$};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-	\node[big_] (D) at (0,4) {$i'$}; 
-	\node[big_] (E) at (2,4) {$j'$};
-	\node[big_] (F) at (4,4) {$k'$};
-	\draw[rounded corners] (-1,3) rectangle (5,5);
-	\draw (2,1)--(2,1.5) (2,2.5)--(2,3);
-	\draw[dotted] (2,1.5)--(2,2.5);
-	\draw (2,-1)--(2,-2) node[bullet] {};
-	\path (0,-2.5)--(1,-2.5);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big1] (1) at (0,0) {$m'$}; 
-	\node[big1] (2) at (3,0) {$n'$};
-	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
-	\draw (1,0)--(2,0);
-	\node[big1] (3) at (0,4) {$m'$};
-	\node[big1] (4) at (3,4) {$n'$};
-	\draw[rounded corners] (-1,3) rectangle (1,5) (2,3) rectangle (4,5);
-	\draw (1,4)--(2,4);
-	\draw[dotted] (1.5,1.5)--(1.5,2.6);
-	\node[circ] at (1.5,-2) {};
-	\draw[rounded corners] (-1.5,-2.5) rectangle (4.5,5.5);
-\end{tikzpicture}
-\]
-%
-It would be natural to encode an edge of weight $n$ by an edge-gadget with $n$ weight elements.
-%
-However, there is a minor issue that prevents this straightforward approach.
-%
-Where one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-1,0) {}; 
-	\draw (.75,0) node[big_] (B1) {} -- (2.25,0) node[big_] (B2) {};
-	\node[big_] (C) at (4,0) {};
-	\draw[rounded corners] (-2,-1) rectangle (5,1);
-	\draw (7,0) node[big_] (D1) {} -- (8.5,0) node[big_] (D2) {}; 
-	\node[big_] (E) at (10.25,0) {};
-	\node[big_] (F) at (12,0) {};
-	\draw[rounded corners] (6,-1) rectangle (13,1);
-	\node[big1] (1) at (1,4) {};
-	\node[big1] (2) at (4,4) {}; 
-	\node[big1] (3) at (7,4) {};
-	\node[big1] (4) at (10,4) {};
-	\draw[rounded corners] (3,3) rectangle (5,5) (6,3) rectangle (8,5);
-	\draw (5,4)--(6,4);
-	\begin{scope}[thepink,->,big>]
-		\draw[bend right=25] (A)  to (1);
-		\draw[bend right=15] (B1) to (1);
-		\draw[bend right=25] (B2) to (2);
-		\draw[bend right=15] (C)  to (2);
-		\draw[bend left=15] (D1) to (3);
-		\draw[bend right=15] (D2) to (4);
-		\draw[bend left=20] (E)  to (4);
-		\draw[bend left=20] (F)  to (4);
-	\end{scope}
-\end{tikzpicture}
-\]
-%
-In such an inappropriate linking, since both halves of the constraint element are connected, both weight elements must be disconnected---otherwise, the linking would violate the switching condition.
-%
-That means the weight elements must belong to different edges.
-%
-For the same reason, to fill the next weight element, one half may be filled by a weight element from a previous edge, but to fill the other half requires an additional edge to be involved.
-%
-To fill $n$ constraint elements inappropriately therefore requires $n+1$ edges.
-%
-It thus suffices to multiply the number of constraint elements by the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
-
-The complete encoding of a constraint graph will be a sequent consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
-%
-For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
-\[
-	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
-\]
-
-\begin{definition}
-\label{def:graph encoding}
-The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows.
-%
-Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
-
-\noindent
-The encoding of a vertex $v_k$ is the formula
-\[
-	\itn{v_k} = \bigparr\big(C_n(k)^{m\times c(v_k)} \big)\parr\1
-\]
-where each \emph{constraint element} $C_n(k)$ is the formula
-\[
-	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
-\]
-
-\noindent
-The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
-\[
-	\itn{e} = \bigtn\big(W_n(i,j)^{m\times w(e)}\big)\tn\bot
-\]
-where each \emph{weight element} $W_n(i,j)$ is the formula
-\[
-	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
-\]
-
-\noindent
-The encoding of the graph $G$ is the sequent
-\[
-	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
-\]
-where $p=m\times(|w|-|c|)\times(3n+4)$.
-
-\end{definition}
-
-In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{weight absorbers}.
-%
-In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
-%
-This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.
-
-A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
-%
-Firstly we will define a standard way of linking a weight element to a constraint element.
-
-\begin{definition}
-\label{def:standard linkings}
-For a weight element $W=W_n(i,j)=A\parr B\parr C$,
-\begin{enumerate}
-	\item
-for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
-	\item
-for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
-	\item
-the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
-\end{enumerate}
-\end{definition}
-
-The standard linkings defined in the first and third case of the above definition are illustrated below.
-
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (1) at (-.25,0) {};
-	\node[big1] (2) at (1,0) {};
-	\node[big1] (3) at (2.5,0) {};
-	\node[big1] (4) at (5.5,0) {};
-	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
-	\draw (3.5,0)--(4.5,0);
-	%
-	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
-	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
-	\node[big_] (C) at (5.5,4) {};
-	\draw[rounded corners] (-1,3) rectangle (6.5,5);
-	%
-	\begin{scope}[thepink,->]
-		\draw[bend right=5] (a) to (1);
-		\draw[bend right=10] (b) to (1);
-		\draw[big>,bend left=25] (A) to (2);
-		\draw[big>,bend left=20] (B) to (3);
-		\draw[big>,bend left=15] (C) to (4);
-	\end{scope}
-\end{tikzpicture}
-\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (1) at (.75,0) {};
-	\node[big1] (2) at (2,0) {};
-	\node[big1] (3) at (3.5,0) {};
-	\node[big1] (4) at (5,0) {};
-	%
-	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
-	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
-	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
-	\draw[rounded corners] (-.5,3) rectangle (7,5);
-	\path (0,-1) -- (1,-1);
-	%
-	\begin{scope}[thepink,->]
-		\draw[bend right=5] (a) to (1);
-		\draw[bend right=10] (b) to (1);
-		\draw[bend right=15] (c) to (1);
-		\draw[big>,bend left=25] (A) to (2);
-		\draw[big>,bend left=20] (B) to (3);
-		\draw[big>,bend left=15] (C) to (4);
-	\end{scope}
-\end{tikzpicture}
-\]
-
-\begin{proposition}
-\label{prop:element linkings}
-The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
-\end{proposition}
-
-The encoding of a configuration is then as follows.
-
-\begin{definition}
-\label{def:configuration encoding}
-The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
-%
-Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
-%
-Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
-\end{definition}
-
-\begin{proposition}
-If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
-\end{proposition}
-
-\begin{IEEEproof}
-Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
-%
-The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
-%
-The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the weight absorbers within scopes of weight elements inside $\itn e$.
-%
-Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
-%
-After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
-\end{IEEEproof}
-
-\begin{figure*}
-\[
-	\vc{\doubleExchange uvxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyx}
-\]
-\caption{Double exchange of links}
-\label{fig:double exchange}
-\end{figure*}
-
-%------------------------------------------------------------
-
-\section{Rewiring proof nets}
-
-In this section we will explore the global rewiring behaviour of proof nets.
-%
-In particular, we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
-%
-Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
-
-Before turning to this fragment there is the following lemma for full MLL, which states that (under the given connectedness conditions) equivalence is preserved by a double exchange of links.
-
-\begin{lemma}
-\label{lem:double exchange}
-Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $\edge bv$ and $\edge xc$.
-%
-Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
-\end{lemma}
-
-\begin{IEEEproof}
-By the rewiring path shown in Figure~\ref{fig:double exchange}.
-\end{IEEEproof}
+\section{Equivalence in the absence of $~\protect\parr$}
 
@@
 \[
-	\netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw
+	\kern-1pt \netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw \kern-1pt 
 \]
@@
 
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net where $\links(a)=(u)$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $b-v$ and $x-c$.
+%
+Then $\links\sim\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{IEEEproof}
+\[
+\begin{array}{@{}ccccc@{}}
+	\vc{\doubleExchange uvxy}
+	&\perm&
+	\vc{\doubleExchange uyxy}
+	&\perm&
+	\vc{\doubleExchange uyxu}
+	\\
+	\\
+	\vc{\doubleExchange vuyx}
+	&\perm&
+	\vc{\doubleExchange vuyu}
+	&\perm&
+	\vc{\doubleExchange vyyu}
+\end{array}
+\begin{array}{@{~}c@{~}c@{}}
+	\indirection{ul}{\perm} \\ \\[20pt]
+	\indirection{dl}{\perm}
+\end{array}
+\vc{\doubleExchange vyxu}
+\]
+\end{IEEEproof}
+
 %------------------------------------------------------------
 
-\section{Correctness of the encoding}
-
-In this section we will establish that in our encoding of constraint graphs %partial \textsc{ncg}-reconfiguration 
-in MLL, reconfiguration on graphs is captured by proof equivalence in MLL.
-%
-Up to minor technical details, it will be shown that $\itn\gamma\perm\itn\delta$ if and only if $\gamma\perm\delta$, in two parts: completeness ($\Leftarrow$) and soundness ($\Rightarrow$).
+\section{Par}
+
+\begin{definition}
+A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
+\end{definition}
+
+\begin{definition}
+A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
+\end{definition}
+
+The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
+%
+A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
+%
+In a proof net, the \emph{kingdom} and the \emph{empire} of a par are respectively its smallest and largest scope.
+
+The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
+%
+In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$ and re-attaching all arcs connecting to removed vertices to $v$.
+%
+
+[[ ADD ILLUSTRATED EXAMPLE ]]
+
+%
+The contraction of scopes may replace the switching condition as a correctness criterion.
+%
+The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
+
+\begin{proposition}
+\label{prop:scoping correctness}
+A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
+
+\begin{enumerate}
+	\item
+sub-sequents are strictly nested: if $\named w\parr$ occurs in $s(v)$ then $s(w)<s(v)$; and
+	\item
+for each $\named v\parr$, the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents $s(w)$ are contracted.
+\end{enumerate}
+
+\end{proposition}
+
+\begin{IEEEproof}
+For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
+%
+For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
+\[
+	\infer{\Delta,A\named v\parr B}{\Delta,A,B}
+\]
+\end{IEEEproof}
+
+[[ IDEA: the following could help simplify octopus-arithmetic ]]
+
+\begin{definition}
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
+%
+A sequent is \emph{balanced} if its balance is zero.
+\end{definition}
+
+An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
+
+An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
+
+%------------------------------------------------------------
+
+\section{Proof nets and constraint graphs}
+
+[[ NOTE: we should decide on notation for steps versus paths in permutation relations ]]
+
+\begin{definition} 
+A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set $E$ of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
+
+A (partial) \emph{configuration} of an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
+\begin{itemize}
+	\item
+for every edge $e$, $\gamma(e)\in v(e)$ or (in the partial case) $\gamma(e)$ is undefined, and
+	\item
+for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
+\end{itemize}
+
+A \emph{reconfiguration step} $\gamma\sim\delta$ connects two (partial) configurations for an \textsc{ncg} $G$ that differ in the assignment of exactly one edge.
+
+\end{definition}
+
+The \emph{(partial) \textsc{ncg}-reconfiguration problem} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.
+
+\begin{theorem}[\cite{Hearn-Demaine-2005}]
+\textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+\end{theorem}
+
+\begin{proposition}
+Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+\end{proposition}
+
+\begin{IEEEproof}
+There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
+%
+Firstly, if $\gamma\sim\delta$ are partial configurations, they may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$.
+%
+Secondly, if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by re-assigning the values where they disagree.
+%
+\end{IEEEproof}
+
+For a graph $G=(V,E,c,v,w)$ let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+\[
+	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
+\]
+
+\begin{definition}
+\label{def:graph interpretation}
+The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
+%
+Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
+
+The interpretation of a vertex $v_k$ is the formula
+\[
+	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
+\]
+where each \emph{constraint element} $C$ is the formula
+\[
+	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
+\]
+
+The interpretation of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
+\[
+	\itn{e} = \bigotimes\big(W^{m\times w(e)}\big)\tn\bot
+\]
+where each \emph{weight element} $W$ is the formula
+\[
+	W = \bigotimes\big(\bot^{3i+2}\big)\parr\bigotimes\big(\bot^{3(j-i)+1}\big)\parr\bigotimes\big(\bot^{3(n-j)+3}\big)
+\]
+
+The interpretation of the graph $G$ is the sequent
+\[
+	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
+	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
+\]
+where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.
+
+\end{definition}
+
+In an \textsc{ncg} $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
+%
+This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$.
+
+For a weight element $W$ of an edge connecting $v_i$ and $v_j$, let the $\bot$-occurrences be named as follows,
+\[
+	W = \begin{array}[t]{l}
+				 \big(\named{    \dagger}\bot\tn\named{   1}\bot\tn\dotsc\tn\named{3i+1}\bot\big) 
+	~\parr\\[5pt] \big(\named{   \ddagger}\bot\tn\named{3i+2}\bot\tn\dotsc\tn\named{3j+1}\bot\big)
+	~\parr\\[5pt] \big(\named{\downdagger}\bot\tn\named{3j+2}\bot\tn\dotsc\tn\named{3n+3}\bot\big)
+	\end{array}
+\]
+and the $1$-occurrences of a constraint element $C$ in $\itn{v_k}$,
+\[
+	C = \big(\named{\alt    \dagger}1\parr\named{\alt{   1}}1\parr\dotso\parr\named{\alt{3k+1}}1\big)
+	\tn \big(\named{\alt\downdagger}1\parr\named{\alt{3k+2}}1\parr\dotso\parr\named{\alt{3n+3}}1\big)~.
+\]
+There is a \emph{natural linking} for the sequent $W,C$ if $e$ is appropriate for $v_k$, i.e.\ if $k=i$ or $k=j$, as follows:
+\[
+	\links(x) = \alt x \qquad \text{for }x\in\{\dagger,\downdagger\}\cup\mathbb N
+\]
+\[
+	\links(\ddagger)=
+	\begin{cases}
+		\alt	\dagger & \text{if }k=i \\
+		\alt\downdagger & \text{if }k=j~.
+	\end{cases}
+\]
+There is also a natural linking for the sequent $W,\named\star 1,\named{\alt 1}1,\dotsc,\named{\alt {3n+3}}1$ consisting of the weight element $W$ and $3n+4$ edge-absorbers:
+\[
+	\links(x)=
+	\begin{cases}
+		\star  & \text{if }x\in\{\dagger,\ddagger,\downdagger\} \\
+		\alt x & \text{otherwise }.
+	\end{cases}
+\]
+
+\begin{proposition}
+\label{prop:element linkings}
+\begin{enumerate}
+	\item
+Given a vertex $v$ and an appropriate edge $e$, for a constraint element $C$ in $\itn v$ and a weight element $W$ in $\itn e$ the natural linking for the sequent $W,C$ is a proof net.
+	\item
+Given a weight element $W$ for a graph with $|V|=n$, the natural linking for the sequent $W,1^{3n+4}$ is a proof net.
+\end{enumerate}
+\end{proposition}
+
+The rightmost $1$-occurrence of each vertex-gadget $\itn v$, named $\alt v$ below, and the rightmost $\bot$-occurrence of each edge-gadget $\itn e$, named $\alt e$, will be called the \emph{indicator vertices} of $\itn v$ and $\itn e$.
+\[	
+	\itn v = C\parr\dotso\parr C\parr \named{\alt v}1 \qquad \itn e= W\tn\dotso\tn W\tn\named{\alt e}\bot~.
+\]
+
+\begin{definition}
+\label{def:configuration interpretation}
+The \emph{interpretation} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
+%
+Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
+%
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
+\end{definition}
+
+\begin{proposition}
+If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
+\end{proposition}
+
+\begin{IEEEproof}
+Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
+%
+The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its natural linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
+%
+The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the edge-absorbers within scopes of weight elements inside $\itn e$.
+%
+Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
+%
+After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the special $\named v1$ of $\itn v$, thus forming a tree.
+\end{IEEEproof}
 
@@
 
-Given a reconfiguration path $\gamma\perm\delta$ over total configurations, we will demonstrate a rewiring sequence between $\itn\gamma$ and $\itn\delta$ up to, possibly, a single exchange of two links in $\itn\delta$.
-%
-The central part of the argument will be to show how the weight element linking to a constraint element may be exchanged for another.
-%
-Once the weight elements of an edge-gadget are no longer connected to any constraint elements, the edge-gadget may straightforwardly be moved from one vertex-gadget to another by re-attaching its indicator link.
-%
-Throughout the rewiring process, weight elements and constraint elements will be kept in a standard linking, and according to the connectivity specified by the target configuration $\itn\delta$.
-%
-Linkings between weight elements and weight absorbers will remain arbitrary, and will be re-adjusted to match $\itn\delta$ at the end of the process.
-
-In a proof net for $\itn G$, an edge-gadget $\itn e$ is \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or linked only to weight absorbers.
-%
-A well-linked edge-gadget is \emph{free} if all its weight elements connect to weight absorbers.
-%
-In the following main lemma we will exchange the weight element linking to a constraint element.
-%
-The lemma considers a sequent consisting of just a vertex-gadget, some appropriate edge-gadgets, and sufficiently many weight absorbers.
+In a proof net for $\itn G$, an edge-gadget $\itn e$ that is in the empire of an appropriate vertex-gadget $\itn v$ is \emph{naturally linked} if the indicator of $\itn e$ connects to the indicator of $\itn v$, and each weight element $W$ of $\itn e$ is either naturally linked to a constraint element $C$ in $\itn v$ or linked only to edge-absorbers.
 
@@
 \label{lem:octopus roll}
-In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $\bot^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
+In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is naturally linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to edge-absorbers $\bot^n$, then there is a net $\links'\sim\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}
 
-\renewcommand\scalefactor{0.88}
-
-\newcommand\displayOcto[1]{%
- \NoIndent{%
-   \smallskip%
-   \centerline{%
-	 \scale{#1}%
-  }}%
-  \bigskip%
-}
-
 \begin{IEEEproof}
@@
 %
-The path of permutations will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
+We will illustrate the path of permutations for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
 %
@@
 	\item
-The initial configuration is illustrated below. 
-%
-Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
-%
-The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.
-%
-\displayOcto{\octorollA1}
-
-	\item
-The link $i-v$ is re-attached to connect to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
-%
-\displayOcto{\octorollB2}
-
-	\item
-Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.
-%
-\displayOcto{\octorollB3}
-
+The initial configuration is illustrated below; other weight and constraint elements are omitted, and $v$, $i$, and $j$ are the indicator vertices of $\itn v$, $\itn{e_i}$, and $\itn{e_j}$ respectively.
+\NoIndent{
+\[
+	\octorollA1
+\]
+}
+	\item
+The link $i-v$ is re-attached to connect to an edge-absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
+\NoIndent{
+\[
+	\octorollB2
+\]
+}
+	\item
+Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those of $E$ and $F$ are moved to $Y$.
+\NoIndent{
+\[
+	\octorollB3
+\]
+}
 	\item\label{item:exchange added}
-In the present configuration, the links from the weight elements form two subnets: one over the sub-sequents $A,B,X,D,\bot^m$, and one over the sub-sequent $C,Y,E,F,\bot^k$, for some $m$ and $k$.
-%
-By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
-%
-It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step \ref{item:exchange needed} below.
-%
-The links of $A,B,C$ link to the weight absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
-%
-\displayOcto{\octorollC}
-
-	\item
-The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
-%
-\displayOcto{\octorollD1}
-
+There are subnets over the sub-sequents $A,B,X,D,\bot^m$ and $C,Y,E,F,\bot^k$.
+%
+These subnets may be rewired so that $D\parr E\parr F$ is naturally linked to $X\tn Y$: by Proposition~\ref{prop:parity determines equivalence}, the resulting subnets are equivalent as long as their parity is preserved.
+%
+Two links from $C$ to $X$ should remain exchanged, compared to the natural linking, for step \ref{item:exchange needed} below.
+%
+The links of $A,B,C$ connect to the edge-absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+\NoIndent{
+\[
+	\octorollC
+\]
+}
+	\item
+The link from $C$ to $Y$ is moved towards an edge-absorber connected to $A,B$.
+\NoIndent{
+\[
+	\octorollD1
+\]
+}
 	\item\label{item:exchange needed}
@@
 Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
-%
-\displayOcto{\octorollD2}
-
-	\item
-The link from $i$ is re-attached to $v$ to yield the final configuration.
-%
-\displayOcto{\octorollA2}
-
+\NoIndent{
+\[
+	\octorollD2
+\]
+}
+	\item
+The link from $i$ may be re-attached to $v$ to yield the final configuration.
+\NoIndent{
+\[
+	\octorollA2
+\]
+}
 \end{enumerate}
@@
 
-In the exchange of weight elements in the above lemma, weight elements link to weight absorbers in arbitrary fashion.
-%
-The next lemma will demonstrate how weight absorbers can be exchanged freely, but only with two exchanges at once.
+An edge-gadget $\itn e$ is \emph{free} if each of its weight elements is linked only to edge-absorbers.
 
 \begin{lemma}
-\label{lem:permute weight absorbers}
-If $\links$ is a well linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of weight absorbers, then $\links\perm\links'$.
+\label{lem:permute edge-absorbers}
+If $\links$ is a naturally linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of edge-absorbers, then $\links\sim\links'$.
 \end{lemma}
@@
 \begin{IEEEproof}
-Let $e_0$ be the indicator of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
+Let $e_0$ be the indicator vertex of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
 %
@@
 	\item
-To permute two weight absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.
+To permute two edge-absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.
 
@@
 	\item
-To exchange a weight absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, first attach $e_0$ to $w$, then re-attach $d$ to $v$.
+To exchange an edge-absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, and attach $e_0$ to $w$, attach $d$ to $v$.
 %
@@
 	\item
-Finally, to permute weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator target of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator $d_0$ and an arbitrary other $\bot$-occurrence $d_1$.
+Finally, to permute edge-absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator vertex $d_0$ and an arbitrary other vertex $d_1$.
 %
@@
 
-In each case, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
-
-\end{IEEEproof}
-
-For any configuration $\gamma$ let $\itn\gamma'$ denote $\itn\gamma$ where the first two weight absorbers are exchanged.
+In each case, if one of the edge-absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
+
+\end{IEEEproof}
+
+Let $\itn\gamma'$ be $\itn\gamma$ where the first two edge-absorbers are exchanged.
 
 \begin{lemma}
-\label{lem:completeness}
-If $\gamma\perm\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\perm\itn\delta$ or $\itn\gamma\perm\itn\delta'$.
+If $\gamma\sim\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\sim\itn\delta$ or $\itn\gamma\sim\itn\delta'$.
 \end{lemma}
@@
 \begin{IEEEproof}
-By Proposition~\ref{prop:partial simulates total reconfiguration} we may assume that $\gamma\perm\delta$ by a sequence of reconfiguration steps over total configurations.
-%
-We will prove that if $\gamma\perm*\delta$ then $\itn\gamma\perm\itn\delta$ or $\itn\gamma\perm\itn\delta'$.
-%
-The same proof will show the corresponding case for $\itn\gamma'$ instead of $\itn\gamma$, so that the general case for $\gamma\perm\delta$ follows by transitivity.
-
+We will prove the case where $\gamma\sim\delta$ is a single reconfiguration step; the general case follows because the proof goes through also when $\itn\gamma'$ replaces $\itn\gamma$ in the statement of the lemma.
+%
 Let $\gamma$ and $\delta$ agree on every edge except $e$, where $\gamma(e)=v$ and $\delta(e)=w$.
@@
 %
-Next, the indicator vertex of $\itn e$, which links to the indicator target of $\itn v$, is re-attached to the indicator target of $\itn w$.
+Next, the indicator vertex of $\itn e$, which links to the indicator of $\itn v$, is re-attached to the indicator of $\itn w$.
 %
@@
 %
-The resulting proof net is $\itn\delta$ modulo a permutation of weight absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute weight absorbers}.
+The resulting proof net is $\itn\delta$ modulo a permutation of edge-absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute edge-absorbers}.
 \end{IEEEproof}
@@
 \subsection*{Soundness}
-
-It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta$ is sound for \textsc{ncg}-reconfiguration, $\gamma\perm\delta$.
-%
-To each proof net $\links$ for an encoded constraint graph $\itn G$ we will associate a partial configuration $\gamma=\coitn\links$, such that 1) a rewiring step $\links\perm*\links$ corresponds to a reconfiguration path $\coitn\links\perm\coitn{\links'}$, and 2) it is a retraction of the encoding of configurations, $\coitn{\itn\gamma}=\gamma$.
-
-The configuration $\coitn\links$ will assign an edge $e$ to a vertex $v$ when, in the proof net $(\links,\itn G)$, the edge-gadget $\itn e$ is in the empire of the vertex-gadget $\itn v$.
-%
-Firstly, it will be shown that $\coitn\links$ is a partial function.
-
-\begin{proposition}[{\cite[Proposition 1.i]{Bellin-vandeWiele-1995}}]
-\label{prop:tensor has disjoint subnets}
-In a proof net, if vertices $v$ and $w$ are joined by a tensor, then any two subnets of which they are respective ports are disjoint.
-\end{proposition}
 
@@
 \begin{IEEEproof}
-Since vertex-gadgets are joined by a tensor, the lemma is immediate from Proposition~\ref{prop:tensor has disjoint subnets}.
-\end{IEEEproof}
-
-Next, it will be shown that the appropriate edge-gadgets in the empire of a vertex-gadget $\itn v$ contain sufficient weight elements to fill the constraint elements of $\itn v$.
+Since vertex-gadgets are joined by a tensor, the lemma is immediate from \cite[Proposition 1]{Bellin-vandeWiele-1995}.
+\end{IEEEproof}
 
@@
 \label{lem:appropriate edge weights}
-In a proof net for $\itn G$, for each node $v$ in $G$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
+In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
 \end{lemma}
@@
 \]
-The two $\parr$-subformulae have a balance of $-3i-1$ and respectively $-3(n-i)-2$.
+The two $\parr$-subformulae have a balance of $-3i-1$ and $-3(n-i)-2$ respectively.
 %
@@
 \[
-	W = \bigtn\big(\bot^{3a+2}\big)\parr\bigtn\big(\bot^{3(b-a)+1}\big)\parr\bigtn\big(\bot^{3(n-b)+3}\big)~.
-\]
-For each of the three $\tn$-subformulae, adding it to the scope of a $\parr$ will change its balance by $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
-%
-In pairs, they add to the balance of a scope by $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
-%
-Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$ (by Proposition~\ref{prop:tensor has disjoint subnets}), it follows that $W$ can balance the scope of at most one of both $\parr$-subformulae of $C$.
+	W = \bigotimes\big(\bot^{3a+2}\big)\parr\bigotimes\big(\bot^{3(b-a)+1}\big)\parr\bigotimes\big(\bot^{3(n-b)+3}\big)~.
+\]
+The three $\tn$-subformulae have a net balance of $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
+%
+In pairs, they have a net balance of $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
+%
+Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$, it follows that $W$ can balance the scope of at most one of both subformulae of $C$.
 
@@
 \begin{definition}
-For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
-\end{definition}
-
-%% WORKING HERE
+For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
+\end{definition}
 
 \begin{lemma}
-If $\links\perm\links'$ are proof nets for $\itn G$ then $\coitn\links\perm\coitn{\links'}$.
+If $\links\sim\links'$ are proof nets for $\itn G$ then $\coitn\links\sim\coitn{\links'}$.
 \end{lemma}
@@
 \begin{IEEEproof}
-The proof will consider the case where $\links\perm*\links'$; the general case follows by transitivity.
-%
 A single permutation $\links\sim\links'$ on proof nets may move a number of edge-gadgets $\itn{e_1},\dotso,\itn{e_n}$ in three ways: 1) out of the empire of a vertex-gadget $\int v$, 2) into the empire of a vertex-gadget $\int w$, or 3) both.

### 2014-01-20 main/LICS.tex

--- 2014-01-19 main/LICS.tex
@@
 		Kiln Enterprises
-	\\	robin.houston@gmail.com	
+	\\	robin@kiln.it
 	}
 }
-
-%\title{The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete}
-
-%\title{Proof equivalence in MLL is \textsc{pspace}-complete}
 

### 2014-01-20 main/LICS.tex
fixing the lemma-spaghetti

--- 2014-01-19 main/LICS.tex
@@
 An edge $\edge a{\links(a)}$ in a proof net or switching graph is called a \emph{link} or a \emph{jump}.
+%
+% MAYBE SAY: The restriction that links must target $\1$-occurrences (rather than any connective) can be circumvented by replacing a subformula $A$ by the equivalent $A\tn\1$.
 
@@
 %
-In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
+In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par (or a sequent) over only $1$-formulae, $\bigparr(\1^n)$.
 %
@@
 \]
-
-Finally, that two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
+%
+A dashed edge will indicate that two vertices are connected, in a proof net or a switching graph, as illustrated below.
 \[
@@
 \]
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{Subnets}
-
-To conclude this section we will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets.
-%
-Firstly we will look at subnets---see also \cite{Bellin-vandeWiele-1995}.
-
-\begin{definition}
-A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
-\end{definition}
-
-\begin{definition}
-A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
-\end{definition}
-
-The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
-%
-A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
-%
-In a proof net, the \emph{kingdom} and the \emph{empire} of a par are respectively its smallest and largest scope.
-
-The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
-%
-In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
-%
-In the example below, the kingdom of a (ternary) par is indicated (left) and contracted (right).
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
-		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
-		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
-	\node[circ] (0) at (5.75,0) {};
-	\node[circ] (1) at (-1,3) {};
-	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
-	\draw[rounded corners] (0,2) rectangle (4,4);
-	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
-	\begin{scope}[thepink,->]
-			\draw[bend right=10] (x) to (1);
-			\draw[bend right=20] (y) to (2);
-			\draw[bend right=10] (a) to (2);
-			\draw[bend right=10] (b) to (3);
-			\draw[bend left=10]  (c) to (3);
-			\draw[bend left=10]  (d) to (4);
-			\draw[bend right=10] (e) to (0);
-	\end{scope}
-	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
-	\node[circ] (0) at (3,0) {};
-	\node[circ] (1) at (-1,3) {};
-	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
-	\draw (box)--(3,3) node[bullet] (e) {};
-	\begin{scope}[thepink,->]
-			\draw[bend right=10] (x) to (1);
-			\draw[bend right=20] (y) to (box);
-			\draw[bend right=10] (e) to (0);
-	\end{scope}
-	\path (0,4.25)--(1,4.25);
-\end{tikzpicture}
-\]
-%
-The contraction of scopes may replace the switching condition as a correctness criterion.
-%
-The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
-
-\begin{proposition}
-\label{prop:scoping correctness}
-A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
-
-\begin{enumerate}
-	\item
-sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
-	\item
-for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents are contracted.
-\end{enumerate}
-
-\end{proposition}
-
-\begin{IEEEproof}
-For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
-%
-For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
-\[
-	\infer{\Delta,A\named v\parr B}{\Delta,A,B}
-\]
-\end{IEEEproof}
-
-Finally, the standard notion of \emph{balance} provides an easy way of identifying some unprovable sequents.
-
-\begin{definition}
-The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
-%
-A sequent is \emph{balanced} if its balance is zero.
-\end{definition}
-
-\begin{proposition}
-\label{prop:unbalanced then uninhabited}
-An unbalanced sequent is uninhabited.
-\end{proposition}
 
@@
 
-\begin{figure*}
-\[
-	\vc{\doubleExchange uvxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyx}
-\]
-\caption{Double exchange of links}
-\label{fig:double exchange}
-\end{figure*}
-
 %------------------------------------------------------------
-
-\section{Rewiring proof nets}
-
-In this section we will explore the global rewiring behaviour of proof nets.
-%
-In particular, we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
-%
-Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
-
-Before turning to this fragment there is the following lemma for full MLL, which states that (under the given connectedness conditions) equivalence is preserved by a double exchange of links.
-
-\begin{lemma}
-\label{lem:double exchange}
-Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $\edge bv$ and $\edge xc$.
-%
-Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
-\end{lemma}
-
-\begin{IEEEproof}
-By the rewiring path shown in Figure~\ref{fig:double exchange}.
-\end{IEEEproof}
-
-Let a \emph{1-alternation} sequent be one over formulae of the form $1$ or $\bot\tn\ldots\tn\bot$, where the number of $\bot$-subformulae is at least 2.
-%
-Such a sequent is inhabited exactly when the number of formulae in the sequent is one greater than the total number of $\bot$-subformulae it contains.
-%
-An inhabited 1-alternation sequent with only one tensor-formula, i.e.\ a sequent of the form $\1,\ldots,\1,\bot\tn\ldots\tn\bot$ with $n$ $\bot$-subformulae and $n$ $1$-subformulae, will admit $n!$ different proof nets, each with $n$ links.
-%
-Since no link can re-attach, its equivalence classes are singletons.
-
-\begin{proposition}
-\label{prop:level0 max binary}
-%
-For a 1-alternation sequent with at least two tensor-formulae there are at most two equivalence classes of proof nets.
-%
-\end{proposition}
-
-%
-%\begin{figure}[p]
-%\[
-%\begin{array}{ccc}
-%	\netA 1213 & \perm	& \netA 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 1223 &		& \netA 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 1323 &		& \netA 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 1321 &		& \netA 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2321 &		& \netA 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2331 & \perm	& \netA 2131
-%\end{array}
-%\qquad
-%\begin{array}{ccc}
-%	\netA 1312 & \perm	& \netA 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2312 &		& \netA 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2313 &		& \netA 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2113 &		& \netA 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 2123 &		& \netA 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
-%	\netA 3123 & \perm	& \netA 3121
-%\end{array}
-%\]
-%\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
-%\label{fig:2x12 nets}
-%\end{figure}
-
-\begin{IEEEproof}
-%
-It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
-%
-For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
-\[
-	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
-\]
-It has two equivalence classes, of 12 proof nets each.
-%
-(Apart from listing these exhaustively, this can also be shown by using the proof of the inductive step, below, to reduce the base case to that of the sequent $\1,\1,\bot\tn\bot$, which has two singleton equivalence classes.)
-
-%, displayed in Figure~\ref{fig:2x12 nets}.
-
-For the inductive step, let $\Gamma$ be the following sequent.
-\[
-	\Delta,A\tn\named a\bot,\named z\1
-\]
-There are two cases: 1) where $A$ is a tensor-formula, and 2) where $A$ is $\bot$ and where, for the induction hypothesis to apply, $\Delta$ contains at least two tensor-formulae.
-%
-For both cases, it will be shown that any net $\links$ for $\Gamma$ is equivalent to a net $\links'$ where $\named a\bot$ connects to $\named z1$, and is the only link to do so.
-%
-This reduces equivalence on $\Gamma$ to equivalence on $\Delta,A$ in case 1, and on $\Delta$ in case 2, so that the induction hypothesis applies.
-
-In constructing $\links'$, since the proof net must be connected, there is a path from $a$ to $z$.
-%
-We will consider only the jumps on this path, not any other edges.
-%
-There are four cases.
-
-\begin{enumerate}
-	\item
-The path consists of exactly the jump $\edge az$.
-%
-Let $\edge by$ be a jump from a $\named b\bot$ in $A$; then $\links'$ is obtained from $\links$ by changing: $\links'(e)=y$  for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$.
-
-	\item
-The path starts with the jump $\edge ax$ (and $x\neq z$).
-%
-Let $\edge by$ be a jump from a $\named b\bot$ in $A$, and let the path end with the jumps $\edge wc$ and $\edge dz$, where $\named c\bot$ and $\named d\bot$ are in the same tensor-formula $B$.
-%
-Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $\links(e)=z$ and $e\neq a$, including $d$.
-%
-These changes are illustrated as permutations below.
-%
-\[
-	\netB xywz \perm \netB zywz \perm \netB zywy
-\]
-
-	\item
-The path consists of exactly one jump $\edge bz$ from a $\named b\bot$ in $A$ (and $b\neq a$).
-%
-Let $\links(a)=y$.
-%
-Choose a jump $\edge cw$ from $\named c\bot$ in $A$ such that there is another $\edge dw$ from $\named d\bot$ in a formula $B$ (not excluding the possibilities $c=b$ and $c=a$).
-%
-Let $\edge ex$ be a further jump from $\named e\bot$ in $B$.
-%
-Then $\links'$ is obtained from $\links$ by changing: $\links'(a)=z$, $\links'(d)=x$, $\links'(e)=y$, and $\links'(f)=x$ for each $f$ (including $b$) such that $\links(f)=z$ and $f\neq a$.
-%
-These changes are exhibited as a series of permutations below, from top left to bottom left (note that the jump from $d$ moves twice).
-%
-\[
-\kern-3pt
-\begin{array}{@{}c@{~}c@{~}c@{~}c@{~}c@{}}
-	\netC yzwx & \perm & \netC yzzx & \perm & \netC yxzx
-	\\ &&&& \vperm \\
-	\netC zxxy & \perm & \netC zxzy & \perm & \netC yxzy
-\end{array}
-\]
-
-	\item
-The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
-%
-Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
-%
-Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
-%
-This is illustrated below.
-\end{enumerate}
-%
-\[
-	\netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw
-\]
-%
-\end{IEEEproof}
-
-\begin{proposition}
-\label{prop:level0 may-connect path}
-%
-For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
-%
-\begin{itemize}
-	\item
-The edge $\edge ab$ can be permuted to $\edge ac$.
-	\item
-There is a path from $b$ to $c$ not passing through $a$.
-	\item
-The path from $a$ to $c$ starts with the jump $a-b$.
-\end{itemize} 
-\end{proposition}
-
-If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
-%
-By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
-
-Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
-%
-\begin{itemize}
-
-	\item
-One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.
-
-	\item
-A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
-
-\end{itemize}
-%
-The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
-
-A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
-%
-\begin{definition}
-\label{def:combinatorial permutation}
-To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
-\[
-	\prm(k) = 
-	\begin{cases}
-		i				& \text{ if $(i,k)$ may connect to $*$; and}
-	\\	\links(i,k)		& \text{ otherwise.}
-	\end{cases}
-\]
-The \emph{parity} of $\links$ is the parity of its permutation.
-\end{definition}
-
-To see that $\prm$ is injective, consider the following.
-\begin{itemize}
-	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
-	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Proposition~\ref{prop:level0 may-connect path}).
-	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
-\end{itemize}
-
-\begin{proposition}
-\label{prop:level0 min binary}
-A permutation on a net $\links$ preserves its parity. 
-\end{proposition}
-
-\begin{IEEEproof}
-Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
-%
-There are two cases, depending on whether $(i,k)$ may connect to $*$.
-%
-If so, using Proposition~\ref{prop:level0 may-connect path}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
-%
-Then the permutation of $\links'$ is that of $\links$.
-
-If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
-\[
-	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
-\]
-Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
-%
-On the relevant domain, this gives the following permutation for $\links$.
-\[
-\left(\begin{array}{ccccccc}
-	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
-	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
-\end{array}\right)
-\]
-In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
-%
-The permutation $\prm[\links']$ is the following.
-\[
-\left(\begin{array}{ccccccc}
-	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
-	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
-\end{array}\right)
-\]
-The parity of both permutations is the same if and only if the relative permutation, below, is even.
-\[
-\left(\begin{array}{ccccccc}
-	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
-	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
-\end{array}\right)
-\]
-This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
-%
-\end{IEEEproof}
-
-\begin{proposition}
-\label{prop:parity determines equivalence}
-Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
-\end{proposition}
-
-\begin{theorem}
-\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
-\end{theorem}
-
-\begin{IEEEproof}
-For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
-%
-For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
-%
-Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
-%
-This yields a linear-time algorithm.
-%
-\end{IEEEproof}
 
@@
 In each case, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
-
+%
 \end{IEEEproof}
@@
 
-To show that rewiring corresponds to reconfiguration under $\coitn-$, we will use the following lemmata.
-
-\begin{lemma}
-\label{lem:rewiring within empire}
-For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
-%
-\begin{enumerate}
-	\item
-$\links\perm*\links'$ where $\links'(a)=w$;
-	\item
-$w$ is in the empire of $a$; and
-	\item
-in any switching graph for $(\Gamma,\links)$, the path from $v$ to $w$ does not pass through $a$.
-\end{enumerate}
-\end{lemma}
-
-\begin{IEEEproof}
-By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.
-
-Next, the empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
-%
-By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net $\sigma$, $a$ may link anywhere in $\sigma$.
-%
-Then 2 implies 1.
-
-Finally, if $\links'$ is a net, and for some switching of $\links$ the path from $v$ to $w$ passes through $a$, then in $\links'$ there is no path between $a$ and $v$ (and two paths between $a$ and $w$) for that switching; then 1 implies 3.
-%
-\end{IEEEproof}
-
-\begin{lemma}
-\label{lem:rewiring preserves empire}
-Let $\links\perm*\links'$ by $\links(a)\neq\links'(a)$, and denote the empire of $a$ in $\links$ and $\links'$ by $\sigma$ and $\sigma'$ respectively; then $\sigma\perm*\sigma'$.
-\end{lemma}
-
-\begin{IEEEproof}
-By Lemma~\ref{lem:rewiring empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae.
-%
-That they must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$.
-%
-\end{IEEEproof}
-
-\begin{lemma}
-\label{lem:rewiring affects empires}
-For proof nets $\links\perm*\links'$, let the empire of a given vertex $v$ in $\links$ be a net for the sequent $\Delta$, and in $\links'$, for $\Delta'$; then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
-\end{lemma}
-
-\begin{IEEEproof}
-By \cite[Proposition 2.b]{Bellin-vandeWiele-1995} the empire of $v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) down from one subformula into a tensor; 4) down from all subformulae into a par; 5) but never down from $v$.
-%
-Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
-%
-There are four cases.
-%
-\begin{enumerate}
-	\item
-If the empire of $v$ is propagated from $a$ to $w$ in $\links$, it includes the empire of $a$.
-%
-Then by Lemma~\ref{lem:rewiring preserves empire} $\Delta=\Delta'$.
-
-	\item
-If the empire of $v$ includes $w$ but not $w'$, then it is propagated through $a$ in $\links$ but not in $\links'$, so that $\Delta\geq\Delta'$.
-
-	\item
-If the empire of $v$ includes $w'$ but not $w$, then $\Delta\leq\Delta'$.
-
-	\item
-Otherwise, $\Delta=\Delta'$.
-\end{enumerate}
-\vskip-12pt
-\end{IEEEproof}
+The following lemma then shows that rewiring corresponds to reconfiguration under $\coitn-$.
 
@@
 %
-Then the corresponding edges $e_1$ through $e_n$ are mobile in $\coitn\links$ and it follows that $\coitn\links\perm\coitn{\links'}$ by moving each $e_i$ in turn, and repeating the same for other vertices.
+Then the corresponding edges $e_1$ through $e_n$ are mobile in $\coitn\links$.
+%
+It follows that $\coitn\links\perm\coitn{\links'}$ by moving each $e_i$ in turn, and repeating the process for other vertices.
 %

### 2014-01-20 main/scratch.tex
fixing the lemma-spaghetti

@@
 
+\newcommand\empire{\varepsilon}
+
 \begin{document}
 
+\section{Rewiring proof nets}
+
+In this section we will explore the global rewiring behaviour of proof nets.
+%
+In particular, we will look at notions of subnets, and we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Subnets}
+
+We will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets, and relate them to rewiring.
+%
+Firstly we will look at subnets---see also \cite{Bellin-vandeWiele-1995}.
+
+\begin{definition}
+A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
+\end{definition}
+
+\begin{definition}
+A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
+\end{definition}
+
+The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
+%
+A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
+
+The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
+%
+In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
+%
+In the example below, a scope of a (ternary) par is indicated (left) and contracted (right).
 \[
-	\lesssim \gtrsim
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
+		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
+		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
+	\node[circ] (0) at (5.75,0) {};
+	\node[circ] (1) at (-1,3) {};
+	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
+	\draw[rounded corners] (0,2) rectangle (4,4);
+	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (x) to (1);
+			\draw[bend right=20] (y) to (2);
+			\draw[bend right=10] (a) to (2);
+			\draw[bend right=10] (b) to (3);
+			\draw[bend left=10]  (c) to (3);
+			\draw[bend left=10]  (d) to (4);
+			\draw[bend right=10] (e) to (0);
+	\end{scope}
+	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
+	\node[circ] (0) at (3,0) {};
+	\node[circ] (1) at (-1,3) {};
+	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
+	\draw (box)--(3,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (x) to (1);
+			\draw[bend right=20] (y) to (box);
+			\draw[bend right=10] (e) to (0);
+	\end{scope}
+	\path (0,4.25)--(1,4.25);
+\end{tikzpicture}
+\]
+%
+The contraction of scopes may replace the switching condition as a correctness criterion.
+%
+The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
+
+\begin{proposition}
+\label{prop:scoping correctness}
+A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
+
+\begin{enumerate}
+	\item
+sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
+	\item
+for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents are contracted.
+\end{enumerate}
+%
+\end{proposition}
+
+\begin{IEEEproof}
+For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
+%
+For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
 \[
+	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
+\]
+\vskip-12pt
+\end{IEEEproof}
+
+In a proof net, the \emph{kingdom} and the \emph{empire} of a vertex $v$ are respectively the smallest and largest subnet that have $v$ as a port.
+%
+In working with the rewiring relation, the notion of empire can be particularly useful.
+%
+Firstly, we repeat the following proposition.
+
+\begin{proposition}[{\cite[Proposition 2.b]{Bellin-vandeWiele-1995}}]
+\label{prop:empire propagation}
+The empire $\sigma$ of $v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\sigma$; 4) into a par if all its subformulae are in $\sigma$; 5) except never into a par or tensor if $v$ is a subformula.
+\end{proposition}
+
+Empires are connected to rewiring in the following ways.
+
+\begin{lemma}
+\label{lem:rewiring within empire}
+For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
+%
+\begin{enumerate}
+	\item
+$\links\perm*\links'$ where $\links'(a)=w$;
+	\item
+$w$ is in the empire of $a$; and
+	\item
+in any switching graph for $(\Gamma,\links)$, the path from $v$ to $w$ does not pass through $a$.
+\end{enumerate}
+\end{lemma}
+
+\begin{IEEEproof}
+By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.
+
+Next, the empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
+%
+By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net $\sigma$, $a$ may link anywhere in $\sigma$.
+%
+Then 2 implies 1.
+
+Finally, if for some switching of $\links$ the path from $v$ to $w$ passes through $a$, then in $\links'$ there is no path between $a$ and $v$ (and two paths between $a$ and $w$) for that switching, so $\links'$ is not a net; then by contraposition 1 implies 3.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:rewiring preserves empire}
+Let $\links\perm*\links'$ by $\links(v)\neq\links'(v)$, and denote the empire of $v$ in $\links$ and $\links'$ by $\sigma$ and $\sigma'$ respectively; then $\sigma\perm*\sigma'$.
+\end{lemma}
+
+\begin{IEEEproof}
+By Lemma~\ref{lem:rewiring empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
+%
+That $\sigma$ and $\sigma'$ must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:rewiring affects empires}
+For proof nets $\links\perm*\links'$, let the empire of a given vertex $v$ in $\links$ be a net for the sequent $\Delta$, and in $\links'$, for $\Delta'$; then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
+\end{lemma}
+
+\begin{IEEEproof}
+Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
+%
+Using Proposition~\ref{prop:empire propagation}, there are four cases.
+%
+\begin{enumerate}
+	\item
+If the empire of $v$ is propagated from $a$ to $w$ in $\links$, it includes the empire of $a$.
+%
+Then by Lemma~\ref{lem:rewiring preserves empire} $\Delta=\Delta'$.
+
+	\item
+If the empire of $v$ includes $w$ but not $w'$, then it is propagated through $a$ in $\links$ but not in $\links'$, so that $\Delta\geq\Delta'$.
+
+	\item
+If the empire of $v$ includes $w'$ but not $w$, then $\Delta\leq\Delta'$.
+
+	\item
+Otherwise, $\Delta=\Delta'$.
+\end{enumerate}
+\vskip-12pt
+\end{IEEEproof}
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Equivalence without $\parr$}
+
+A basic observation on MLL is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
+%
+This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
+%
+However, a double such exchange commonly does give an equivalent net.
+
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $\edge bv$ and $\edge xc$.
+%
+Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{IEEEproof}
+By the rewiring path shown in Figure~\ref{fig:double exchange}.
+\end{IEEEproof}
+
+\begin{figure*}
+\[
+	\vc{\doubleExchange uvxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyx}
+\]
+\caption{Double exchange of links}
+\label{fig:double exchange}
+\end{figure*}
+
+This dynamic completely characterises rewiring in the fragment of MLL that omits the par.
+%
+The following standard notion of \emph{balance} characterises provability for it.
+
+\begin{definition}
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
+%
+A sequent is \emph{balanced} if its balance is zero.
+\end{definition}
+
+\begin{proposition}
+\label{prop:unbalanced then uninhabited}
+An unbalanced sequent is uninhabited.
+\end{proposition}
+
+Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
+%
+After removing $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
+
+\begin{proposition}
+A basic sequent is inhabited if and only if it is balanced.
+\end{proposition}
+
+\begin{proposition}
+A basic sequent $\bigtn(\bot^n),\1^n$ is inhabited by exactly $n!$ inequivalent proof nets.
+\end{proposition}
+
+\begin{proposition}
+\label{prop:level0 max binary}
+%
+A basic sequent with at least two tensor-formulae has at most two equivalence classes of proof nets.
+%
+\end{proposition}
+
+\begin{IEEEproof}
+By induction on the size of a sequent $\Gamma$.
+%
+The base case is the sequent $\1,\1,\bot\tn\bot$, which has two inequivalent proof nets.
+%
+For the inductive step, let $A\tn\named a\bot$ be a largest $\tn$-formula in $\Gamma$, and pick an occurence $\named z\1$.
+%
+It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, for the sequent $\Gamma$ with $\named z\1$ removed and $A\tn\named a\bot$ replaced by $A$, the subnet for $\links'$ belongs to one of two equivalence classes.
+
+To find $\links'$, if $\links(a)=z$ we are done.
+%
+Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by rewiring only $\links'(a)=z$.
+%
+Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
+%
+Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
+%
+Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
+
+Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
+%
+Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
+\end{IEEEproof}
+
+%
+%\begin{proposition}
+%\label{prop:level0 may-connect path}
+%%
+%For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
+%%
+%\begin{itemize}
+%	\item
+%The edge $\edge ab$ can be permuted to $\edge ac$.
+%	\item
+%There is a path from $b$ to $c$ not passing through $a$.
+%	\item
+%The path from $a$ to $c$ starts with the jump $a-b$.
+%\end{itemize} 
+%\end{proposition}
+
+If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
+%
+By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
+
+Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
+%
+\begin{itemize}
+
+	\item
+One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.
+
+	\item
+A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
+
+\end{itemize}
+%
+The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
+
+A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
+%
+\begin{definition}
+\label{def:combinatorial permutation}
+To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
+\[
+	\prm(k) = 
+	\begin{cases}
+		i				& \text{ if $(i,k)$ may connect to $*$; and}
+	\\	\links(i,k)		& \text{ otherwise.}
+	\end{cases}
+\]
+The \emph{parity} of $\links$ is the parity of its permutation.
+\end{definition}
+
+To see that $\prm$ is injective, consider the following.
+\begin{itemize}
+	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
+	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Lemma~\ref{lem:rewiring within empire}).
+	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
+\end{itemize}
+
+\begin{proposition}
+\label{prop:level0 min binary}
+A permutation on a net $\links$ preserves its parity. 
+\end{proposition}
+
+\begin{IEEEproof}
+Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
+%
+There are two cases, depending on whether $(i,k)$ may connect to $*$.
+%
+If so, using Lemma~\ref{lem:rewiring within empire}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
+%
+Then the permutation of $\links'$ is that of $\links$.
+
+If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
+\[
+	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
+\]
+Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
+%
+On the relevant domain, this gives the following permutation for $\links$.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
+	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
+\end{array}\right)
+\]
+In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
+%
+The permutation $\prm[\links']$ is the following.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+The parity of both permutations is the same if and only if the relative permutation, below, is even.
+\[
+\left(\begin{array}{ccccccc}
+	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
+%
+\end{IEEEproof}
+
+\begin{proposition}
+\label{prop:parity determines equivalence}
+Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+\end{proposition}
+
+\begin{theorem}
+\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
+\end{theorem}
+
+\begin{IEEEproof}
+For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
+%
+For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
+%
+Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
+%
+This yields a linear-time algorithm.
+%
+\end{IEEEproof}
+
+Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
+
+These characteristics carry over to the full fragment, including the par.
+%
+They hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
+%
+Firstly, making proof nets equivalent is generally easier than preventing them from being equivalent, and in particular changing a formula $A$ to $A\tn\bot$ dramatically increases its rewiring potential.
+%
+The focus of our encoding will therefore be on preventing undesired linkings from being proof nets at all, rather than being unreachable by rewiring.
+%
+Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and should be no more than a technical distraction.
 
@@
 
-\begin{lemma}
-For a proof net $(\Gamma,\links)$, if the linking $\links'$ agrees with $\links$ on all values except $\links'(a)=v$, then $\links'$ is a proof net if and only if $v$ is in the empire of $a$ in $(\Gamma,\links)$.
 %
-%If $\links\perm*\links'$ by rewiring the link $\links(a)=v$ to $\links'(a)=w$, then $w$ is in the empire of $a$ in the proof net $\links$.
-\end{lemma}
-
-\begin{proof}
-The empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
 %
-In one direction, by Definition~\ref{def:proofs to nets} $a$ may link anywhere in a translation of $\Sigma$ to a net; if $\named v\1$ is in $\Sigma$, then $\links'$ is a net.
 %
-In the other direction, if $\links\perm*\links'$, then for any switching of $(\Gamma,\links')$ there is a path from $\links(a)=w$ to
-
+%\begin{lemma}
+%For a proof net $(\Gamma,\links)$, if the linking $\links'$ agrees with $\links$ on all values except $\links'(a)=v$, then $\links'$ is a proof net if and only if $v$ is in the empire of $a$ in $(\Gamma,\links)$.
+%%
+%%If $\links\perm*\links'$ by rewiring the link $\links(a)=v$ to $\links'(a)=w$, then $w$ is in the empire of $a$ in the proof net $\links$.
+%\end{lemma}
+%
+%\begin{proof}
+%The empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
+%%
+%In one direction, by Definition~\ref{def:proofs to nets} $a$ may link anywhere in a translation of $\Sigma$ to a net; if $\named v\1$ is in $\Sigma$, then $\links'$ is a net.
+%%
+%In the other direction, if $\links\perm*\links'$, then for any switching of $(\Gamma,\links')$ there is a path from $\links(a)=w$ to 
+%
 %%Let $\sigma$ be the empire of $a$ in $(\Gamma,\links)$.

### 2014-01-20 main/LICS.tex
complete modulo permutations & parity

@@
 
+\section{Rewiring proof nets}
+
+In this section we will explore the global rewiring behaviour of proof nets.
+%
+In particular, we will look at notions of subnets, and we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Subnets}
+
+We will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets, and relate them to rewiring.
+%
+Firstly we will look at subnets---see also \cite{Bellin-vandeWiele-1995}.
+
+\begin{definition}
+A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
+\end{definition}
+
+\begin{definition}
+A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
+\end{definition}
+
+The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
+%
+A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
+
+The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
+%
+In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
+%
+In the example below, a scope of a (ternary) par is indicated (left) and contracted (right).
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
+		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
+		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
+	\node[circ] (0) at (5.75,0) {};
+	\node[circ] (1) at (-1,3) {};
+	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
+	\draw[rounded corners] (0,2) rectangle (4,4);
+	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (x) to (1);
+			\draw[bend right=20] (y) to (2);
+			\draw[bend right=10] (a) to (2);
+			\draw[bend right=10] (b) to (3);
+			\draw[bend left=10]  (c) to (3);
+			\draw[bend left=10]  (d) to (4);
+			\draw[bend right=10] (e) to (0);
+	\end{scope}
+	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
+	\node[circ] (0) at (3,0) {};
+	\node[circ] (1) at (-1,3) {};
+	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
+	\draw (box)--(3,3) node[bullet] (e) {};
+	\begin{scope}[thepink,->]
+			\draw[bend right=10] (x) to (1);
+			\draw[bend right=20] (y) to (box);
+			\draw[bend right=10] (e) to (0);
+	\end{scope}
+	\path (0,4.25)--(1,4.25);
+\end{tikzpicture}
+\]
+%
+The contraction of scopes may replace the switching condition as a correctness criterion.
+%
+The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
+
+\begin{proposition}
+\label{prop:scoping correctness}
+A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
+
+\begin{enumerate}
+	\item
+sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
+	\item
+for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents are contracted.
+\end{enumerate}
+%
+\end{proposition}
+
+\begin{IEEEproof}
+For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
+%
+For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
+\[
+	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
+\]
+\vskip-12pt
+\end{IEEEproof}
+
+In a proof net, the \emph{kingdom} and the \emph{empire} of a vertex $v$ are respectively the smallest and largest subnet that have $v$ as a port.
+%
+In working with the rewiring relation, the notion of empire can be particularly useful.
+%
+Firstly, we repeat the following proposition.
+
+\begin{proposition}[{\cite[Proposition 2.b]{Bellin-vandeWiele-1995}}]
+\label{prop:empire propagation}
+The empire $\sigma$ of $v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\sigma$; 4) into a par if all its subformulae are in $\sigma$; 5) except never into a par or tensor if $v$ is a subformula.
+\end{proposition}
+
+Empires are connected to rewiring in the following ways.
+
+\begin{lemma}
+\label{lem:rewiring within empire}
+For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
+%
+\begin{enumerate}
+	\item
+$\links\perm*\links'$ where $\links'(a)=w$;
+	\item
+$w$ is in the empire of $a$; and
+	\item
+in any switching graph for $(\Gamma,\links)$, the path from $v$ to $w$ does not pass through $a$.
+\end{enumerate}
+\end{lemma}
+
+\begin{IEEEproof}
+By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.
+
+Next, the empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
+%
+By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net $\sigma$, $a$ may link anywhere in $\sigma$.
+%
+Then 2 implies 1.
+
+Finally, if for some switching of $\links$ the path from $v$ to $w$ passes through $a$, then in $\links'$ there is no path between $a$ and $v$ (and two paths between $a$ and $w$) for that switching, so $\links'$ is not a net; then by contraposition 1 implies 3.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:rewiring preserves empire}
+Let $\links\perm*\links'$ by $\links(v)\neq\links'(v)$, and denote the empire of $v$ in $\links$ and $\links'$ by $\sigma$ and $\sigma'$ respectively; then $\sigma\perm*\sigma'$.
+\end{lemma}
+
+\begin{IEEEproof}
+By Lemma~\ref{lem:rewiring empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
+%
+That $\sigma$ and $\sigma'$ must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is.
+%
+\end{IEEEproof}
+
+\begin{lemma}
+\label{lem:rewiring affects empires}
+For proof nets $\links\perm*\links'$, let the empire of a given vertex $v$ in $\links$ be a net for the sequent $\Delta$, and in $\links'$, for $\Delta'$; then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
+\end{lemma}
+
+\begin{IEEEproof}
+Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
+%
+Using Proposition~\ref{prop:empire propagation}, there are four cases.
+%
+\begin{enumerate}
+	\item
+If the empire of $v$ is propagated from $a$ to $w$ in $\links$, it includes the empire of $a$.
+%
+Then by Lemma~\ref{lem:rewiring preserves empire} $\Delta=\Delta'$.
+
+	\item
+If the empire of $v$ includes $w$ but not $w'$, then it is propagated through $a$ in $\links$ but not in $\links'$, so that $\Delta\geq\Delta'$.
+
+	\item
+If the empire of $v$ includes $w'$ but not $w$, then $\Delta\leq\Delta'$.
+
+	\item
+Otherwise, $\Delta=\Delta'$.
+\end{enumerate}
+\vskip-12pt
+\end{IEEEproof}
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Equivalence without $\parr$}
+
+A basic observation on MLL is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
+%
+This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
+%
+However, a double such exchange commonly does give an equivalent net.
+
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $\edge bv$ and $\edge xc$.
+%
+Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{IEEEproof}
+By the rewiring path shown in Figure~\ref{fig:double exchange}.
+\end{IEEEproof}
+
+\begin{figure*}
+\[
+	\vc{\doubleExchange uvxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyx}
+\]
+\caption{Double exchange of links}
+\label{fig:double exchange}
+\end{figure*}
+
+This dynamic completely characterises rewiring in the fragment of MLL that omits the par.
+%
+The following standard notion of \emph{balance} characterises provability for it.
+
+\begin{definition}
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
+%
+A sequent is \emph{balanced} if its balance is zero.
+\end{definition}
+
+\begin{proposition}
+\label{prop:unbalanced then uninhabited}
+An unbalanced sequent is uninhabited.
+\end{proposition}
+
+Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
+%
+After removing $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
+
+\begin{proposition}
+A basic sequent is inhabited if and only if it is balanced.
+\end{proposition}
+
+\begin{proposition}
+A basic sequent $\bigtn(\bot^n),\1^n$ is inhabited by exactly $n!$ inequivalent proof nets.
+\end{proposition}
+
+\begin{proposition}
+\label{prop:level0 max binary}
+%
+A basic sequent with at least two tensor-formulae has at most two equivalence classes of proof nets.
+%
+\end{proposition}
+
+\begin{IEEEproof}
+By induction on the size of a sequent $\Gamma$.
+%
+The base case is the sequent $\1,\1,\bot\tn\bot$, which has two inequivalent proof nets.
+%
+For the inductive step, let $A\tn\named a\bot$ be a largest $\tn$-formula in $\Gamma$, and pick an occurence $\named z\1$.
+%
+It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, for the sequent $\Gamma$ with $\named z\1$ removed and $A\tn\named a\bot$ replaced by $A$, the subnet for $\links'$ belongs to one of two equivalence classes.
+
+To find $\links'$, if $\links(a)=z$ we are done.
+%
+Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by rewiring only $\links'(a)=z$.
+%
+Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
+%
+Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
+%
+Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
+
+Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
+%
+Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
+\end{IEEEproof}
+
+Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
+
+These characteristics carry over to the full fragment, including the par.
+%
+They hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
+%
+Firstly, making proof nets equivalent is generally easier than preventing them from being equivalent, and in particular changing a formula $A$ to $A\tn\bot$ dramatically increases its rewiring potential.
+%
+The focus of our encoding will therefore be on preventing undesired linkings from being proof nets at all, rather than being unreachable by rewiring.
+%
+Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and should be no more than a technical distraction.
+
 %------------------------------------------------------------
@@
 \section{Encoding constraint logic}
+\label{sec:encoding}
 

### 2014-01-20 main/scratch.tex
complete modulo permutations & parity

--- 2014-01-19 main/scratch.tex
@@
 
+%
+%\begin{proposition}
+%\label{prop:level0 may-connect path}
+%%
+%For a proof net for a 1-alternation sequent containing a link $\edge{\named a\bot}{\named b\1}$ and a formula $\named c\1$, the following are equivalent.
+%%
+%\begin{itemize}
+%	\item
+%The edge $\edge ab$ can be permuted to $\edge ac$.
+%	\item
+%There is a path from $b$ to $c$ not passing through $a$.
+%	\item
+%The path from $a$ to $c$ starts with the jump $a-b$.
+%\end{itemize} 
+%\end{proposition}
+
+If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$. 
+%
+By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
+
+Consider the following naming scheme for the units in a 1-alternation sequent $\Gamma$ with tensor-formulae $A_1,\dotsc,A_n$.
+%
+\begin{itemize}
+
+	\item
+One $\1$ in $\Gamma$ is named $*$, and the remaining ones with the numbers $n+1,\dotsc,m$.
+
+	\item
+A $\bot$-formula in $A_i$ is named by a pair $(i,k)$, where $k=i$ for the first $\bot$-formula in each $A_i$, and for the remaining $\bot$-formulae in all $A_i$, each $k$ is a distinct number in $n+1,\dotsc,m$.
+
+\end{itemize}
+%
+The naming scheme suggests a linking for $\Gamma$, defined by $\links(i,i)=\star$ and $\links(i,k)=k$ otherwise; i.e\ the first $\bot$ in each tensor-formula connects to $\named *\1$, while other $\bot$-subformulae connect uniquely to the remaining $\1$-subformulae.
+
+A net for $\Gamma$ is interpreted as a combinatorial permutation (an automorphism on $\{1,\dotsc,m\}$) as follows.
+%
+\begin{definition}
+\label{def:combinatorial permutation}
+To a proof net $\links$ for a 1-alternation sequent $\Gamma$ named as above, associate the \emph{permutation} $\prm:\{1,\dotsc,m\}\to\{1,\dotsc,m\}$ given by:
 \[
-	\lesssim \gtrsim
+	\prm(k) = 
+	\begin{cases}
+		i				& \text{ if $(i,k)$ may connect to $*$; and}
+	\\	\links(i,k)		& \text{ otherwise.}
+	\end{cases}
+\]
+The \emph{parity} of $\links$ is the parity of its permutation.
+\end{definition}
+
+To see that $\prm$ is injective, consider the following.
+\begin{itemize}
+	\item The domains of $i$ and $\links(i,k)$, respectively $1,\dotsc,n$ and $n+1,\dotsc,m$, are disjoint.
+	\item Exactly one $\bot$-formula in each $A_i$ may connect to $*$ because of connectedness and acyclicity, since if a $\bot$-formula may connect to $*$ it has a path to $*$ (Lemma~\ref{lem:rewiring within empire}).
+	\item If two $\bot$-formulae have the same target, which means they are in different tensor-formulae, at least one may connect to $*$ via the other tensor-formula, which must have a path to $*$ by the above.
+\end{itemize}
+
+\begin{proposition}
+\label{prop:level0 min binary}
+A permutation on a net $\links$ preserves its parity. 
+\end{proposition}
+
+\begin{IEEEproof}
+Let $\links$ be a net for $\Gamma$, with $\Gamma$ named as above, and let the link $\edge{(i,k)}x$ in $\links$ re-attach as $\edge{(i,k)}y$, forming $\links'$.
+%
+There are two cases, depending on whether $(i,k)$ may connect to $*$.
+%
+If so, using Lemma~\ref{lem:rewiring within empire}, the re-wiring preserves which $\bot$-formulae may connect to $*$, since for any path to $*$ via $\edge{(i,k)}x$ in $\links$ there is a path to $*$ via $\edge{(i,k)}y$.
+%
+Then the permutation of $\links'$ is that of $\links$.
+
+If $(i,k)$ may not connect to $*$, let the path from $x$ to $y$ run via the following $\bot$- and $\1$-vertices.
 \[
+	x=x_1, (i_1,j_1), (i_1,k_1), x_2, (i_2,j_2), \dotsc, (i_n,k_n), x_{n+1}=y 	
+\]
+Note that the $\bot$-formulae $(i_a,j_a)$ may connect to $*$.
+%
+On the relevant domain, this gives the following permutation for $\links$.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &  k  & k_1 & \dotso & k_n \\
+	i_1 & \dotso & i_n & x_1 & x_2 & \dotso & x_{n+1}
+\end{array}\right)
+\]
+In $\links'$, since $\links'(i,k)=y$, the $\bot$-formulae that may connect to $*$ are the $(i_a,k_a)$.
+%
+The permutation $\prm[\links']$ is the following.
+\[
+\left(\begin{array}{ccccccc}
+	j_1 & \dotso & j_n &    k    & k_1 & \dotso & k_n \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+The parity of both permutations is the same if and only if the relative permutation, below, is even.
+\[
+\left(\begin{array}{ccccccc}
+	i_1 & \dotso & i_n & x_1     & x_2 & \dotso & x_{n+1} \\
+	x_1 & \dotso & x_n & x_{n+1} & i_1 & \dotso & i_n
+\end{array}\right)
+\]
+This is the case, as it is obtained by the exchange of $x_a$ and $i_a$ for each $a\leq n$, and subsequently the exchange of $x_{n+1}$ and each $i_a$ in turn.
+%
+\end{IEEEproof}
+
+\begin{proposition}
+\label{prop:parity determines equivalence}
+Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+\end{proposition}
+
+\begin{theorem}
+\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
+\end{theorem}
+
+\begin{IEEEproof}
+For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
+%
+For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
+%
+Following Definition~\ref{def:combinatorial permutation} the parity of a net can be read off in a single traversal of the net.
+%
+This yields a linear-time algorithm.
+%
+\end{IEEEproof}
 

### 2014-01-20 main/LICS.tex
typo

@@
 \begin{definition}
-The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and comma's.
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and commas.
 %

### 2014-01-20 main/LICS.tex
Updated intro

@@
 
-%% STILL TO ADD:
-%% - MLL proof equivalence is the word problem for *-autonomous categories
-%% - IMLL proof equivalence is polynomial-time
-
-An important element of the theory of linear logic \cite{Girard-1987} is the idea that proofs should be considered modulo the permutation of inferences.
-%; that the chosen order of permutable inferences is inessential, or `bureaucracy'.
-%contributes no essential proof content, and should be considered `bureaucracy'.
-%
-%The idea is supported by the categorical semantics of linear logic, in which proofs up to permutations denote the same morphism. 
-%
-\emph{Proof equivalence} is the problem of deciding whether two proofs are equal modulo permutations.
-
-The proof equivalence problem is closely related to the notion of \emph{proof nets}.
-%
-These are canonical, geometric representations of proof that factor out permutations, so that proofs are equivalent if and only if they have the same underlying proof net.
-%
-Canonical proof nets have been found for several fragments of linear logic: the multipicative fragment without units \cite{Girard-1987,Danos-Regnier-1989}, the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
-%
-For the full multiplicative fragment, with units, several notions of proof net have been proposed \cite{BCST,Strassburger-lamarche-2004,HughesFreeStar}.
-%
-However, none is canonical, and whether a satisfactory notion of proof net can be found has remained an open question.
+\noindent The question of equivalence of proofs goes back to Lambek \cite{Lambek-1968}, who realised that the then-new tool of category-theoretic logic gave a notion of proof equivalence that was coarser and better-behaved than syntactic equality.
+
+A striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of \textsc{mll} -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
+This naturally raises the question whether proof nets can be extended to work in the presence of units.
+There is a line of work in this direction, beginning with \cite{TrimbleThesis,BCST} and perhaps culminating with \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+
+So the question remains whether there exist fully canonical proof nets for full \textsc{mll}.
+Canonical proof nets have been found for several other fragments of linear logic: the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
 
 In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \textsc{pspace}-complete.
-%
-As a main corollary, this effectively rules out the possibility of finding a satisfactory notion of proof net for this fragment.
+It follows that there can be no satisfactory canonical notion of proof net.
 

### 2014-01-20 main/LICS.tex
Define MLL the first time it’s used

@@
 
-A striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of \textsc{mll} -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
+A striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic (\textsc{mll}) -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
 This naturally raises the question whether proof nets can be extended to work in the presence of units.

### 2014-01-20 main/LICS.tex
Cite Lamarche/Straßburger

@@
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
-There is a line of work in this direction, beginning with \cite{TrimbleThesis,BCST} and perhaps culminating with \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+There is a line of work in this direction, beginning with \cite{TrimbleThesis,BCST} via \cite{Strassburger-Lamarche-2004} and perhaps culminating with \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
 

### 2014-01-20 main/LICS.tex
Lose the ambiguous parenthetical

@@
 %
-Drawing from recent work on reconfiguration problems, in this paper it is shown that MLL proof equivalence is PSPACE-complete, using a reduction from Nondeterministic Constraint Logic.
+Drawing from recent work on reconfiguration problems, in this paper it is shown that \textsc{mll} proof equivalence is \textsc{pspace}-complete, using a reduction from Nondeterministic Constraint Logic.
 %
@@
 
-A striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic (\textsc{mll}) -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
+A striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
 This naturally raises the question whether proof nets can be extended to work in the presence of units.

### 2014-01-20 main/LICS.tex
Constraint logic wording

@@
 
-The proof of \textsc{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in
+The proof of \textsc{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in nondeterministic
 \emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
@@
 
-Constraint logic belongs to a class of problems called \emph{reconfiguration problems} \cite{ReconfigurationProblems}: can one solution to a given problem be transformed into another by a series of elementary changes, while remaining valid throughout?
-%
-For example, for boolean satisfiability (SAT) the reconfiguration problem asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
+This is one of a class of problems called \emph{reconfiguration problems} \cite{ReconfigurationProblems}: can one solution to a given problem be transformed into another by a series of elementary changes, while remaining valid throughout?
+%
+For example, the reconfiguration problem for boolean satisfiability (SAT) asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
 %
@@
 
-MLL proof equivalence may be usefully classified as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Kanovich-1992}.
+MLL proof equivalence may be regarded as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
 

### 2014-01-20 main/scratch.tex
Rewrite for general case

--- 2014-01-19 main/scratch.tex
@@
 
-\usepackage{pgffor}
-
-\graphicspath{{../notes/}}
-
 \makeTheoremDefs
@@
 
-\[
-	\lesssim \gtrsim
-\[
+If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$.
+%
+By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
+
+We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
+We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a 1-alternation sequent.
+
+In this section we shall assume that the connectives $\tn$ and $\parr$ are n-ary, and that every argument of a $\tn$ is a $\parr$ and vice versa.
+Assume also that $\Gamma$ consists of a single formula, if necessary by introducing a $\parr$ at the root.
+Now fix an arbitrary switching of $\Gamma$; this switching together with a linking $\links$ defines a tree whose vertices are the subformulae of $\Gamma$ and whose edges are the edges of the chosen switching together with the links of $\links$.
+Take the root of the formula $\Gamma$ to be the root of this tree.
+Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
+This therefore establishes a bijection between the edges of the tree and the non-root vertices.
+%
+A second linking $\links'$ similarly establishes such a bijection.
+Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
+Finally the parity of the pair of linkings is taken to be the parity of this permutation.
+
+\begin{lemma}
+	The parity is well-defined, in the sense that it does not depend on the choice of switching.
+\end{lemma}
+\begin{IEEEproof}
+	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
+	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
+	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
+	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
+	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
+	permutation of an odd number of elements is an even permutation.
+\end{IEEEproof}
+
+Essentially the same argument also establishes that:
+\begin{lemma}
+	If two linkings are equivalent, their parity is even.
+\end{lemma}
+
+\begin{proposition}
+\label{prop:parity determines equivalence}
+Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+\end{proposition}
+
+\begin{theorem}
+\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
+\end{theorem}
+
+\begin{IEEEproof}
+For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
+%
+For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
+%
+The parity of a net can be read off in a single traversal of the net.
+%
+This yields a linear-time algorithm.
+\end{IEEEproof}
 
 \end{document}
-
-\begin{lemma}
-For a proof net $(\Gamma,\links)$, if the linking $\links'$ agrees with $\links$ on all values except $\links'(a)=v$, then $\links'$ is a proof net if and only if $v$ is in the empire of $a$ in $(\Gamma,\links)$.
-%
-%If $\links\perm*\links'$ by rewiring the link $\links(a)=v$ to $\links'(a)=w$, then $w$ is in the empire of $a$ in the proof net $\links$.
-\end{lemma}
-
-\begin{proof}
-The empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
-%
-In one direction, by Definition~\ref{def:proofs to nets} $a$ may link anywhere in a translation of $\Sigma$ to a net; if $\named v\1$ is in $\Sigma$, then $\links'$ is a net.
-%
-In the other direction, if $\links\perm*\links'$, then for any switching of $(\Gamma,\links')$ there is a path from $\links(a)=w$ to
-
-%%Let $\sigma$ be the empire of $a$ in $(\Gamma,\links)$.
-%%
-%In one direction, if $v$ is in $\sigma$, then since $\sigma$ is a subnet, for any switching of $\sigma$ there is a path from $\links(a)$ to $v$ not passing through $a$.
-%%
-%Then if $\sigma'\perm*\sigma$ by 
-%
-% $\sigma$ minus the link $\edge a{\links(a)}$ is a subnet, 
-%
-%By definition, $\sigma$ is the largest subnet with $a$ as a port.
-%%
-%Then there is a proof $\Sigma\tonet\sigma$ with as conclusion the introduction rule for $\named a\bot$, which 1) is a subproof of some sequent proof $\Pi\tonet\links$, and 2) is the largest subproof of $\named a\bot$ among all $\Pi\tonet\links$.
-%
-%
-%In one direction, if $\links'$ is a proof net, then $\links\perm*\links'$, and there is a $\Pi'\tonet\links'$ such that $\Pi\perm\Pi'$ by permuting the introduction rule for $\named a\bot$.
-%%
-%But since permuting this rule in $\Pi$ cannot give it a larger subnet than $\Sigma$ (by 2 above), $\named v\1$ must be in $\Sigma$, and $v$ in $\sigma$.
-%
-%By Definition~\ref{def:proofs to nets}
-
-\end{proof}
-
-\end{document}
-%
-%
-%\begin{frame}
-%	\octorollA1
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollB1
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollB2
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollB3
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollC
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollD1
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE1
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE2
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE3
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE4
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE5
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE6
-%\end{frame}
-%
-%\begin{frame}
-%	\octorollE7
-%\end{frame}
-
-\begin{frame}
-	\octorollD2
-\end{frame}
-
-\begin{frame}
-	\octorollA2
-\end{frame}
-
-\end{document}
-
-%\newcommand\octorollC{
-%  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-%	\node[circ] (a1a) at (0,1.5) {}; \node[big1] (a1) at (-2,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2,0) {};
-%	\draw (-9  ,4) node[bullet] (d1a) {} -- (-8  ,4) node[big_] (d1) {};
-%	\draw (-6.5,4) node[bullet] (d2a) {} -- (-5.5,4) node[big_] (d2) {};
-%	\draw (-4  ,4) node[bullet] (d3a) {} -- (-3  ,4) node[big_] (d3) {};
-%	\draw[rounded corners] (-10,3) rectangle (-2,5);
-%	\draw (-2,4)--(-1,4) node[bullet] (d) {};
-%	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
-%	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
-%	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
-%	\draw[rounded corners] (10,3) rectangle (2,5);
-%	\draw (2,4)--(1,4) node[bullet] (e) {};
-%	\node[circ] (v1a) at (-4,8); \node[big1] (v1b) at (-3,8) {}; \node[big1] (v1c) at (-1.5,8) {};
-%	\node[big1] (v2) at  ( 2.5,8) {}; \node[big1] (v2) at ( 2.5,8) {};
-%	\draw[rounded corners] (-4.5,7) rectangle (-0.5,9);
-%	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
-%	\draw (-0.5,8)--(0.5,8);
-%	\node[circ] (v) at (0,6) {};
-%	%
-%	\begin{scope}[thepink,->]
-%		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
-%		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
-%		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
-%		\draw[big>,bend right=20] (e1) to (a1);  \draw[big>,bend right=20] (e2) to (a2);  \draw[big>, bend right=20] (e3) to (a3);
-%	\end{scope}
-%  \end{tikzpicture}
-%}
-
-\[
-	\big(\bigparr_{k\times c(v_i)}\big(\bigparr_{3i+2}1 \tn \bigparr_{3(n-i)+3}1\big) \big)\parr 1
-\]
-\[
-	\big(\bigotimes_{k\times w(e)}\big(\bigotimes_{3i+2}\bot\parr\bigotimes_{3(j-i)+1}\bot\parr\bigotimes_{3(n-j)+3}\bot\big)\big)\tn\bot
-\]
-
-\[
-	C = \bigparr(1^{3i+2}) \tn \bigparr(1^{3(n-i)+3})
-\]
-
-\[
-	\big(\bigparr C^{k\times c(v_i)} \big)\parr 1
-\]
-
-\[
-	W = \bigotimes(\bot^{3i+2})\parr\bigotimes(\bot^{3(j-i)+1})\parr\bigotimes(\bot^{3(n-j)+3}
-\]
-
-\[
-	\big(\bigotimes W^{k\times w(e)}\big)\tn\bot
-\]

### 2014-01-20 main/LICS.tex
the phenomenal parity proof included

@@
 
-Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
-
-These characteristics carry over to the full fragment, including the par.
-%
-They hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
+\subsection*{Parity}
+
+We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
+We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a 1-alternation sequent.
+
+For this argument we shall assume that the connectives $\tn$ and $\parr$ are n-ary, and that every argument of a $\tn$ is a $\parr$ and vice versa.
+Assume also that $\Gamma$ consists of a single formula, if necessary by introducing a $\parr$ at the root.
+Now fix an arbitrary switching of $\Gamma$; this switching together with a linking $\links$ defines a tree whose vertices are the subformulae of $\Gamma$ and whose edges are the edges of the chosen switching together with the links of $\links$.
+Take the root of the formula $\Gamma$ to be the root of this tree.
+Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
+This therefore establishes a bijection between the edges of the tree and the non-root vertices.
+%
+A second linking $\links'$ similarly establishes such a bijection.
+Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
+Finally the parity of the pair of linkings is taken to be the parity of this permutation.
+
+\begin{lemma}
+	The parity is well-defined, in the sense that it does not depend on the choice of switching.
+\end{lemma}
+\begin{IEEEproof}
+	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
+	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
+	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
+	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
+	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
+	permutation of an odd number of elements is an even permutation.
+\end{IEEEproof}
+
+Essentially the same argument also establishes that:
+\begin{lemma}
+	If two linkings are equivalent, their parity is even.
+\end{lemma}
+
+\begin{proposition}
+\label{prop:parity determines equivalence}
+Two proof nets for a basic sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+\end{proposition}
+
+\begin{IEEEproof}
+By Proposition~\ref{prop:level0 max binary} the sequent has at most 2 equivalence classes.
+%
+Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
+\end{IEEEproof}
+
+The previous illustrates that equivalence in the fragment without $\parr$ is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
+
+These characteristics hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
 %
@@
 %
-Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and should be no more than a technical distraction.
+Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and shall mean no more than a technical distraction.
 
@@
 
+%% WORKING HERE
+
+%We shall translate a pair of
+
 For any configuration $\gamma$ let $\itn\gamma'$ denote $\itn\gamma$ where the first two weight absorbers are exchanged.

### 2014-01-20 main/scratch.tex
the phenomenal parity proof included

@@
 
-We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
-We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a 1-alternation sequent.
-
-In this section we shall assume that the connectives $\tn$ and $\parr$ are n-ary, and that every argument of a $\tn$ is a $\parr$ and vice versa.
-Assume also that $\Gamma$ consists of a single formula, if necessary by introducing a $\parr$ at the root.
-Now fix an arbitrary switching of $\Gamma$; this switching together with a linking $\links$ defines a tree whose vertices are the subformulae of $\Gamma$ and whose edges are the edges of the chosen switching together with the links of $\links$.
-Take the root of the formula $\Gamma$ to be the root of this tree.
-Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
-This therefore establishes a bijection between the edges of the tree and the non-root vertices.
-%
-A second linking $\links'$ similarly establishes such a bijection.
-Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
-Finally the parity of the pair of linkings is taken to be the parity of this permutation.
-
-\begin{lemma}
-	The parity is well-defined, in the sense that it does not depend on the choice of switching.
-\end{lemma}
-\begin{IEEEproof}
-	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
-	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
-	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
-	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
-	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
-	permutation of an odd number of elements is an even permutation.
-\end{IEEEproof}
-
-Essentially the same argument also establishes that:
-\begin{lemma}
-	If two linkings are equivalent, their parity is even.
-\end{lemma}
-
-\begin{proposition}
-\label{prop:parity determines equivalence}
-Two proof nets for a 1-alternation sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
-\end{proposition}
-
-\begin{theorem}
-\MLL\ proof equivalence in the absence of ~$\parr$ is linear-time decidable.
-\end{theorem}
-
-\begin{IEEEproof}
-For a sequent with 1 tensor-formula, the problem is reduced to syntactic equality.
-%
-For a sequent with 2 or more tensor-formulae, by Propositions~\ref{prop:parity determines equivalence} the equivalence of two nets is determined by their parity.
-%
-The parity of a net can be read off in a single traversal of the net.
-%
-This yields a linear-time algorithm.
-\end{IEEEproof}
-
 \end{document}

### 2014-01-20 main/LICS.tex
1-alternation sequents are now basic
polishing and fixing references

@@
 \makeTheoremDefs
+
+\let\beforesection=\medskip
+\let\aftersection=\noindent
 
@@
 %------------------------------------------------------------
+\beforesection
 
@@
 
-\noindent The question of equivalence of proofs goes back to Lambek \cite{Lambek-1968}, who realised that the then-new tool of category-theoretic logic gave a notion of proof equivalence that was coarser and better-behaved than syntactic equality.
+\aftersection
+%
+The question of equivalence of proofs goes back to Lambek \cite{Lambek-1968}, who realised that the then-new tool of category-theoretic logic gave a notion of proof equivalence that was coarser and better-behaved than syntactic equality.
 
@@
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
-There is a line of work in this direction, beginning with \cite{TrimbleThesis,BCST} via \cite{Strassburger-Lamarche-2004} and perhaps culminating with \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+There is a line of work in this direction, beginning with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \cite{Strassburger-Lamarche-2004} and perhaps culminating with \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
 
@@
 %------------------------------------------------------------
-
-\section{MLL}
 
@@
 
+\beforesection
+
+\section{MLL}
+
+\aftersection
+%
 The formulae of unit-only multiplicative linear logic are given by the following grammar.
@@
 
-%A positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
-%
-%An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
-%
+%------------------------------------------------------------
+
+\beforesection
 
@@
 
+\aftersection
+%
 In this section we will explore the global rewiring behaviour of proof nets.
@@
 In particular, we will look at notions of subnets, and we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+
+\begin{figure*}
+\[
+	\vc{\doubleExchange uvxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyx}
+\]
+\caption{Double exchange of links (Lemma~\ref{lem:double exchange})}
+\label{fig:double exchange}
+\end{figure*}
 
@@
 \begin{IEEEproof}
-By Lemma~\ref{lem:rewiring empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
+By Lemma~\ref{lem:rewiring within empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
 %
@@
 
-\begin{figure*}
-\[
-	\vc{\doubleExchange uvxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyx}
-\]
-\caption{Double exchange of links}
-\label{fig:double exchange}
-\end{figure*}
-
 This dynamic completely characterises rewiring in the fragment of MLL that omits the par.
@@
 We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
-We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a 1-alternation sequent.
+We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a basic sequent.
 
@@
 
+\beforesection
+
 \section{Encoding constraint logic}
@@
 
+\aftersection
+%
 \emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
@@
 
-%------------------------------------------------------------
+\beforesection
 
@@
 
+\aftersection
+%
 In this section we will establish that in our encoding of constraint graphs %partial \textsc{ncg}-reconfiguration 
@@
 
-%% WORKING HERE
-
-%We shall translate a pair of
-
-For any configuration $\gamma$ let $\itn\gamma'$ denote $\itn\gamma$ where the first two weight absorbers are exchanged.
+If two connected configurations $\gamma\perm\delta$ are encoded individually as $\itn\gamma$ and $\itn\delta$, these may not be equivalent simply because their parity happens to be odd.
+%
+For that reason we shall adjust the encoding of the second to guarantee an even parity between them.
+
+\begin{definition}
+%
+Let $\itn\delta'$ be $\itn\delta$ with the first two weight absorbers exchanged.
+%
+For configurations $\gamma$ and $\delta$ for $G$, let $\itn\delta_\gamma$ be $\itn\delta$ if it has even parity with $\itn\gamma$, and $\itn\delta'$ otherwise.
+%
+\end{definition}
 
@@
 \label{lem:completeness}
-If $\gamma\perm\delta$ for total configurations $\gamma$ and $\delta$, then either $\itn\gamma\perm\itn\delta$ or $\itn\gamma\perm\itn\delta'$.
+If $\gamma\perm\delta$ for total configurations $\gamma$ and $\delta$, then $\itn\gamma\perm\itn\delta_\gamma$.
 \end{lemma}
@@
 
+\beforesection
+
 \section{MLL proof equivalence is \textsc{pspace}-complete}
 
+\aftersection
+%
 We are now ready to state our main theorem.
@@
 \[
-	\gamma\perm\delta \qquad\iff\qquad \itn\gamma\perm\itn\delta \text{ or } \itn\gamma\perm\itn\delta'~.
-\]
-%
-The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and the observation that $\coitn{\itn\gamma}=\coitn{\itn\gamma'}=\gamma$.
+	\gamma\perm\delta \qquad\iff\qquad \itn\gamma\perm\itn\delta_\gamma~.
+\]
+%
+The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and the observation that $\coitn{\itn\gamma}=\gamma$ and $\coitn{\itn\delta_\gamma}=\delta$.
 %

### 2014-01-20 main/LICS.tex
Minor corrections

@@
 \let\aftersection=\noindent
+
+\let\capsabbrev=\uppercase
 
@@
 
-\title{No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete}
+\title{No proof nets for \capsabbrev{mll} with units\\[5pt]\Large Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}
 
@@
 \begin{abstract}
-MLL proof equivalence is the problem of deciding whether two proofs in multiplicative linear logic are related by a series of inference permutations.
+\capsabbrev{mll} proof equivalence is the problem of deciding whether two proofs in multiplicative linear logic are related by a series of inference permutations.
 %
@@
 %
-Previous work has shown the problem to be equivalent to a rewiring problem on proof nets, which are not canonical for full MLL due to the presence of the two units.
-%
-Drawing from recent work on reconfiguration problems, in this paper it is shown that \textsc{mll} proof equivalence is \textsc{pspace}-complete, using a reduction from Nondeterministic Constraint Logic.
-%
-An important consequence of the result is that the existence of a satisfactory notion of proof nets for MLL with units is ruled out (under current complexity assumptions).
+Previous work has shown the problem to be equivalent to a rewiring problem on proof nets, which are not canonical for full \capsabbrev{mll} due to the presence of the two units.
+%
+Drawing from recent work on reconfiguration problems, in this paper it is shown that \capsabbrev{mll} proof equivalence is \capsabbrev{pspace}-complete, using a reduction from Nondeterministic Constraint Logic.
+%
+An important consequence of the result is that the existence of a satisfactory notion of proof nets for \capsabbrev{mll} with units is ruled out (under current complexity assumptions).
 \end{abstract}
@@
 %
-The question of equivalence of proofs goes back to Lambek \cite{Lambek-1968}, who realised that the then-new tool of category-theoretic logic gave a notion of proof equivalence that was coarser and better-behaved than syntactic equality.
-
-A striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
+The question of equivalence of proofs goes back to Lambek \cite{Lambek-1968}, who realised that the new tool of category-theoretic logic gave a notion of proof equivalence that was coarser and better-behaved than syntactic equality.
+
+Later, a striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
-There is a line of work in this direction, beginning with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \cite{Strassburger-Lamarche-2004} and perhaps culminating with \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
-
-So the question remains whether there exist fully canonical proof nets for full \textsc{mll}.
+The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \cite{Strassburger-Lamarche-2004} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+
+So the question remains whether there exist fully canonical proof nets for full \capsabbrev{mll}.
 Canonical proof nets have been found for several other fragments of linear logic: the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
 
-In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \textsc{pspace}-complete.
+In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \capsabbrev{pspace}-complete.
 It follows that there can be no satisfactory canonical notion of proof net.
@@
 
-The proof of \textsc{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in nondeterministic
+\aftersection The proof of \capsabbrev{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in nondeterministic
 \emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
 %
-Constraint logic is a simple graph rewriting mechanism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied; the configuration-to-configuration question is whether two graphs are related by a sequence of valid rewriting steps.
+Constraint logic is a simple graph rewriting formalism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied; the configuration-to-configuration question is whether two graphs are related by a sequence of valid rewriting steps.
 
@@
 %
-It is not uncommon for an \textsc{np}-complete problem to have an associated reconfiguration problem that is \textsc{pspace}-complete \cite{ReconfigurationProblems}; one example is SAT-reconfiguration, which is \textsc{pspace}-complete.
-
-MLL proof equivalence may be regarded as the reconfiguration problem associated with MLL proof search, which is \textsc{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
+It is not uncommon for an \capsabbrev{np}-complete problem to have an associated reconfiguration problem that is \capsabbrev{pspace}-complete \cite{ReconfigurationProblems}; one example is SAT-reconfiguration, which is \capsabbrev{pspace}-complete.
+\capsabbrev{mll} proof equivalence may be regarded as the reconfiguration problem associated with \capsabbrev{mll} proof search, which is \capsabbrev{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
 
@@
 \begin{figure}[!b]
-\quad\MLLrule b
-\hfill\MLLrule 1
-\hfill\MLLrule p
-\hfill\MLLrule t
+\quad\capsabbrev{mll}rule b
+\hfill\capsabbrev{mll}rule 1
+\hfill\capsabbrev{mll}rule p
+\hfill\capsabbrev{mll}rule t
 \quad
-\caption{Inference rules for unit-only \MLL}
+\caption{Inference rules for unit-only \capsabbrev{mll}}
 \label{fig:MLL}
@@
 	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\MLLperm{bb1}}} ~\perm~ \vc{\scale{\MLLperm{bb2}}}
+		\vc{\scale{\capsabbrev{mll}perm{bb1}}} ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bb2}}}
 		\hfill
-		\vc{\scale{\MLLperm{bp1}}} ~\perm~ \vc{\scale{\MLLperm{bp2}}}
+		\vc{\scale{\capsabbrev{mll}perm{bp1}}} ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bp2}}}
 	}
@@
 	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\MLLperm{bt2}}} ~\perm~ \vc{\scale{\MLLperm{bt1}}}
-								   ~\perm~ \vc{\scale{\MLLperm{bt3}}}
+		\vc{\scale{\capsabbrev{mll}perm{bt2}}} ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bt1}}}
+								   ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bt3}}}
 	}
 \\ \\[6pt]
-	\vc{\scale{\MLLperm{pp1}}} &\perm& \vc{\scale{\MLLperm{pp2}}}
+	\vc{\scale{\capsabbrev{mll}perm{pp1}}} &\perm& \vc{\scale{\capsabbrev{mll}perm{pp2}}}
 \\ \\[6pt]
-	\vc{\scale{\MLLperm{pt1}}} &\perm& \vc{\scale{\MLLperm{pt2}}}
+	\vc{\scale{\capsabbrev{mll}perm{pt1}}} &\perm& \vc{\scale{\capsabbrev{mll}perm{pt2}}}
 \\ \\[6pt]
-	\vc{\scale{\MLLperm{tt1}}} &\perm& \vc{\scale{\MLLperm{tt2}}}
+	\vc{\scale{\capsabbrev{mll}perm{tt1}}} &\perm& \vc{\scale{\capsabbrev{mll}perm{tt2}}}
 \end{array}
@@
 
-\section{MLL}
+\section{\capsabbrev{mll}}
 
@@
 %
-\emph{\MLL\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
+\emph{\capsabbrev{mll}\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
 %
@@
 
-Proof nets provide a solution to proof equivalence for MLL$^-$ (MLL without units).
-%
-For full MLL, they reduce the proof equivalence problem to a simple rewiring relation \cite{HughesMLLProofNets}.
+Proof nets provide a solution to proof equivalence for \capsabbrev{mll} without units.
+%
+For full \capsabbrev{mll}, they reduce the proof equivalence problem to a simple rewiring relation \cite{HughesMLLProofNets}.
 
@@
 %
-A \emph{permutation} $(\perm*)$ between proof nets is the redirection of exactly one link.
-%
-\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by permutations.
+A \emph{rewiring} $(\perm*)$ between proof nets is the redirection of exactly one link.
+%
+\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by rewirings.
 %
@@
 \[
-	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
+	\infer[\capsabbrev{mll}label b]{\Gamma,\named a\bot}{\Gamma}
 \]
@@
 \noindent
-The above proposition means that \MLL\ proof equivalence is the problem of deciding equivalence of proof nets.
+The above proposition means that \capsabbrev{mll}\ proof equivalence is the problem of deciding equivalence of proof nets.
 %
@@
 \]
-The links of a proof net are added to the sequent as colored arrows.
+The links of a proof net are added to the sequent as coloured arrows.
 %
@@
 %
-In particular, we will look at notions of subnets, and we will give a simple account of equivalence for the fragment of MLL that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+In particular, we will look at notions of subnets, and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
 
@@
 
-We will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets, and relate them to rewiring.
+We will discuss (and adapt) some convenient standard notions for \capsabbrev{mll} proofs and proof nets, and relate them to rewiring.
 %
@@
 \[
-	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
+	\infer[\capsabbrev{mll}label p]{\Delta,A\named v\parr B}{\Delta,A,B}
 \]
@@
 
-A basic observation on MLL is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
+A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
 %
@@
 
-This dynamic completely characterises rewiring in the fragment of MLL that omits the par.
+This dynamic completely characterises rewiring in the fragment of \capsabbrev{mll} that omits the par.
 %
@@
 %
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
+\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \capsabbrev{pspace}-hardness reductions.
 %
@@
 
-We will introduce minor adaptations to this formalism to suit our reduction to MLL proof equivalence.
+We will introduce minor adaptations to this formalism to suit our reduction to \capsabbrev{mll} proof equivalence.
 %
@@
 \smallskip
-A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \textsc{ncg} $G$ that differ in value (or definedness) on exactly one edge.
+A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \capsabbrev{ncg} $G$ that differ in value (or definedness) on exactly one edge.
 %
@@
 
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding whether two total configurations for a constraint graph are connected by a sequence of reconfiguration steps.
-%
-%By the above proposition, \textsc{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations for a constraint graph are connected by a sequence of reconfiguration steps.
+%
+%By the above proposition, \capsabbrev{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
 
 \begin{theorem}[\cite{Hearn-Demaine-2005}]
-\textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
+\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
 \end{theorem}
@@
 %\begin{proposition}
-%Partial \textsc{ncg}-reconfiguration is \textsc{pspace}-complete.
-%%\textsc{pncg}-reconfiguration is \textsc{pspace}-complete.
+%Partial \capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
+%%\capsabbrev{pncg}-reconfiguration is \capsabbrev{pspace}-complete.
 %\end{proposition}
 
-We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of \textsc{ncg}-reconfiguration in MLL proof nets.
+We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
 
@@
 
-The basis of the encoding of constraint graphs in MLL is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
+The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
 %
@@
 \]
-For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
+For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same -- this way, a priori any weight element may connect to any constraint element.
 %
@@
 \]
-To ensure that no other connections can be made, values are chosen such that $m\bmod3=1$ and $n\bmod3=2$, and accordingly $i\bmod3=1$, $j\bmod3=0$, and $k\bmod3=2$.
+To ensure that no other connections can be made, values are chosen such that $m\equiv1$ and $n\equiv2$ $(\bmod3)$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2$ $(\bmod3)$.
 
@@
 %
-Where one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
+Although one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
 %
@@
 %
-In this section we will establish that in our encoding of constraint graphs %partial \textsc{ncg}-reconfiguration 
-in MLL, reconfiguration on graphs is captured by proof equivalence in MLL.
+In this section we will establish that in our encoding of constraint graphs %partial \capsabbrev{ncg}-reconfiguration 
+in \capsabbrev{mll}, reconfiguration on graphs is captured by proof equivalence in \capsabbrev{mll}.
 %
@@
 
-In each case, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be termporarily attached elsewhere.
+In each case, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be temporarily attached elsewhere.
 %
@@
 
-It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta$ is sound for \textsc{ncg}-reconfiguration, $\gamma\perm\delta$.
+It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta$ is sound for \capsabbrev{ncg}-reconfiguration, $\gamma\perm\delta$.
 %
@@
 
-\section{MLL proof equivalence is \textsc{pspace}-complete}
+\section{\capsabbrev{mll} proof equivalence is \capsabbrev{pspace}-complete}
 
@@
 \begin{theorem}
-MLL proof equivalence is \textsc{pspace}-complete.
+\capsabbrev{mll} proof equivalence is \capsabbrev{pspace}-complete.
 \end{theorem}
@@
 \begin{IEEEproof}
-MLL proof equivalence has at most non-deterministic polynomial space complexity: a proof net may be represented in linear space (with respect to a proof); a single rewiring step is performed without requiring additional space; and a non-deterministic algorithm may guess the correct rewiring sequence.
-%
-Then by Savitch's Theorem \cite{Savitch-1970} MLL proof equivalence is in \textsc{pspace}.
-
-\textsc{pspace}-hardness follows by the encoding of \textsc{ncg}-reconfiguration, which in its completed form is stated:
+\capsabbrev{mll} proof equivalence has at most non-deterministic polynomial space complexity: a proof net may be represented in linear space (with respect to a proof); a single rewiring step is performed without requiring additional space; and a non-deterministic algorithm may guess the correct rewiring sequence.
+%
+Then by Savitch's Theorem \cite{Savitch-1970} \capsabbrev{mll} proof equivalence is in \capsabbrev{pspace}.
+
+\capsabbrev{pspace}-hardness follows by the encoding of \capsabbrev{ncg}-reconfiguration, which in its completed form is stated:
 \[

### 2014-01-20 main/LICS.tex
minor edits

@@
 %
-The path of permutations will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
+The path of rewirings will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
 %
@@
 	\item
-To permute two weight absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, also exchanging the targets of $e_0$ and $e_1$.
-
-	\item
-To reinstate $e_0$ as the connection between $\itn e$ and the remainder of the proof net, either perform another permutation as above, or permute $v$ and $w$ twice again, once exchanging the targets of $e_1$ and $e_2$, and once exchanging the targets of $e_2$ and $e_0$.
+To exchange two weight absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$ while also exchanging the targets of $e_0$ and $e_1$.
+
+	\item
+To reinstate $e_0$ as the connection between $\itn e$ and the remainder of the proof net, either perform another exchange as above, or exchange $v$ and $w$ twice again, once exchanging also the targets of $e_1$ and $e_2$, and once exchanging also the targets of $e_2$ and $e_0$.
 
@@
 	\item
-Finally, to permute weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator target of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator $d_0$ and an arbitrary other $\bot$-occurrence $d_1$.
-%
-Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to permute $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
+Finally, to exchange weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator target of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator $d_0$ and an arbitrary other $\bot$-occurrence $d_1$.
+%
+Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
 %

### 2014-01-20 main/LICS.tex
Revert overenthusiastic search/replace
synchronous fixing - hopefully GIT understands...

@@
 \begin{figure}[!b]
-\quad\capsabbrev{mll}rule b
-\hfill\capsabbrev{mll}rule 1
-\hfill\capsabbrev{mll}rule p
-\hfill\capsabbrev{mll}rule t
+\quad\MLLrule b
+\hfill\MLLrule 1
+\hfill\MLLrule p
+\hfill\MLLrule t
 \quad
@@
 	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\capsabbrev{mll}perm{bb1}}} ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bb2}}}
+		\vc{\scale{\MLLperm{bb1}}} ~\perm~ \vc{\scale{\MLLperm{bb2}}}
 		\hfill
-		\vc{\scale{\capsabbrev{mll}perm{bp1}}} ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bp2}}}
+		\vc{\scale{\MLLperm{bp1}}} ~\perm~ \vc{\scale{\MLLperm{bp2}}}
 	}
@@
 	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\capsabbrev{mll}perm{bt2}}} ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bt1}}}
-								   ~\perm~ \vc{\scale{\capsabbrev{mll}perm{bt3}}}
+		\vc{\scale{\MLLperm{bt2}}} ~\perm~ \vc{\scale{\MLLperm{bt1}}}
+								   ~\perm~ \vc{\scale{\MLLperm{bt3}}}
 	}
 \\ \\[6pt]
-	\vc{\scale{\capsabbrev{mll}perm{pp1}}} &\perm& \vc{\scale{\capsabbrev{mll}perm{pp2}}}
+	\vc{\scale{\MLLperm{pp1}}} &\perm& \vc{\scale{\MLLperm{pp2}}}
 \\ \\[6pt]
-	\vc{\scale{\capsabbrev{mll}perm{pt1}}} &\perm& \vc{\scale{\capsabbrev{mll}perm{pt2}}}
+	\vc{\scale{\MLLperm{pt1}}} &\perm& \vc{\scale{\MLLperm{pt2}}}
 \\ \\[6pt]
-	\vc{\scale{\capsabbrev{mll}perm{tt1}}} &\perm& \vc{\scale{\capsabbrev{mll}perm{tt2}}}
+	\vc{\scale{\MLLperm{tt1}}} &\perm& \vc{\scale{\MLLperm{tt2}}}
 \end{array}
@@
 \[
-	\infer[\capsabbrev{mll}label b]{\Gamma,\named a\bot}{\Gamma}
+	\infer[MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
 \]
@@
 \[
-	\infer[\capsabbrev{mll}label p]{\Delta,A\named v\parr B}{\Delta,A,B}
+	\infer[MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
 \]

### 2014-01-20 main/LICS.tex
Revert overenthusiastic search/replace
Trivial wording tweaks

@@
 \[
-	\infer[MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
+	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
 \]
@@
 \[
-	\infer[MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
+	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
 \]
@@
 
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations for a constraint graph are connected by a sequence of reconfiguration steps.
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
 %
@@
 %
-In such an inappropriate linking, since both halves of the constraint element are connected, both weight elements must be disconnected---otherwise, the linking would violate the switching condition.
+In such an inappropriate linking, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the linking would violate the switching condition.
 %

### 2014-01-20 main/LICS.tex
Fix orphaned QED symbol
Upgrade IEEEtran.cls to the latest version, which supports manual
placement of the QED symbol.
re-wording for better spacing
star-autonomous blablabla

@@
 
+The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008} for \capsabbrev{mll} without units).
+%
+Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two representations denote the same morphism in any star-autonomous category.
+
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 %
-For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
+%
+If $\Pi\toNet\links$ and $\Pi$ has conclusion $\Gamma$, then $\links$ is a proof net for $\Gamma$.
+%For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
 %
@@
 %
-\displayOcto{\octorollA2}
-
+\displayOcto{\octorollA2\IEEEQEDhere}
 \end{enumerate}

### 2014-01-20 main/LICS.tex
\aftersubsection

@@
 \let\aftersection=\noindent
+\let\aftersubsection=\noindent
 
@@
 
-\aftersection The proof of \capsabbrev{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in nondeterministic
+\aftersubsection
+The proof of \capsabbrev{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in nondeterministic
 \emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
@@
 
+\aftersubsection
 Proof nets provide a solution to proof equivalence for \capsabbrev{mll} without units.
@@
 
+\aftersubsection
 We will use a concise diagrammatic notation for sequents and proof nets.
@@
 
+\aftersubsection
 We will discuss (and adapt) some convenient standard notions for \capsabbrev{mll} proofs and proof nets, and relate them to rewiring.
@@
 
+\aftersubsection
 A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
@@
 
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
 \subsection*{Parity}
 
+\aftersubsection
 We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
@@
 
+\aftersubsection
 The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
@@
 
+\aftersubsection
 Given a reconfiguration path $\gamma\perm\delta$ over total configurations, we will demonstrate a rewiring sequence between $\itn\gamma$ and $\itn\delta$ up to, possibly, a single exchange of two links in $\itn\delta$.
@@
 
+\aftersubsection
 It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta$ is sound for \capsabbrev{ncg}-reconfiguration, $\gamma\perm\delta$.

### 2014-01-21 main/LICS.tex
fixed: need 3x edges

@@
 %
-In particular, we will look at notions of subnets, and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par, i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+We will look at notions of subnets, and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par.
+%
+Furthermore, we will  \emph{parity},
+
+%i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
+
+% TODO: mention the parity problem
 
@@
 
-This dynamic completely characterises rewiring in the fragment of \capsabbrev{mll} that omits the par.
+This dynamic will be used to characterise rewiring in the fragment of \capsabbrev{mll} that omits the par.
 %
@@
 %
-Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by rewiring only $\links'(a)=z$.
+Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
 %
@@
 
-These characteristics hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
+These characteristics hold the following lessons on rewiring for the design of our encoding, in Section~\ref{sec:encoding}. 
 %
@@
 
-We will introduce minor adaptations to this formalism to suit our reduction to \capsabbrev{mll} proof equivalence.
-%
-Mainly, a constraint graph itself will have \emph{undirected} edges, while a separate notion of \emph{configuration} imposes a direction on them.
+We shall choose a variant of this formalism to suit our reduction to \capsabbrev{mll} proof equivalence.
+%
+A constraint graph itself will have \emph{undirected} edges, while a separate notion of \emph{configuration} imposes a direction on them.
 %
@@
 %
-In addition, we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
+As a minor adaptation, we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
 
@@
 That means the weight elements must belong to different edges.
-%
-For the same reason, to fill the next weight element, one half may be filled by a weight element from a previous edge, but to fill the other half requires an additional edge to be involved.
-%
-To fill $n$ constraint elements inappropriately therefore requires $n+1$ edges.
-%
-It thus suffices to multiply the number of constraint elements by the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
+
+As the linkings above illustrate, it may occur that one subformula of a weight element $A\parr B\parr C$ fills one half of a constraint element.
+%
+Consequently, a weight element can fill three halves, but only of different constraint elements.
+%
+The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
+%
+To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
+%
+To fill $3n$ constraint elements inappropriately therefore requires $n+1$ edges.
+%
+It thus suffices to multiply the number of constraint elements by three times the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times3\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
 
@@
 \[
-	\itn{v_k} = \bigparr\big(C_n(k)^{m\times c(v_k)} \big)\parr\1
+	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\parr\1
 \]
@@
 \[
-	\itn{e} = \bigtn\big(W_n(i,j)^{m\times w(e)}\big)\tn\bot
+	\itn{e} = \bigtn\big(W_n(i,j)^{3m\times w(e)}\big)\tn\bot
 \]
@@
 \]
-where $p=m\times(|w|-|c|)\times(3n+4)$.
+where $p=3m\times(|w|-|c|)\times(3n+4)$.
 
@@
 
+% TODO: mention the parity problem
+
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 \[
-	\itn{v_i} = \bigparr\big(C^{m\times c(v_i)} \big)\parr 1~.
-\]
-It will be shown that $m$ inappropriate edge-gadgets may balance at most $m-1$ constraint elements $C$.
-
-Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq m\times c(v_i)$. 
-%
-If the scopes $s(x_j)$ and $s(y_m)$ of any $x_j$ and $y_m$ are balanced by weight elements $W$ and $W'$ of the same edge-gadget $\itn e$, then since $W$ and $W'$ are connected by a tensor, there are switchings of $W$, $W'$, $s(x_j)$, and $s(y_m)$ such that $x_j$ and $y_m$ are connected in the proof net for $\itn G$.
-%
-Then the first constraint element of $\itn{v_i}$ requires 2 edge-gadgets to balance, and each successive element requires one additional edge-gadget.
+	\itn{v_i} = \bigparr\big(C^{3m\times c(v_i)} \big)\parr 1~.
+\]
+It will be shown that $m$ inappropriate edge-gadgets may balance at most $3(m-1)$ constraint elements $C$.
+
+Two edge-gadgets may balance at most three constraint elements: one weight element $W$ has three subformulae, which may each balance at most one half of a constraint element; the other halves may be balanced by different weight elements of the second edge-gadget.
+%
+In the same way, adding one further edge-gadget allows at most three further constraint elements to be filled, since previous edges may connect to only one half of each constraint element.
+%
+Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
+%
+%
+%Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq 3m\times c(v_i)$. 
+%%
+%If the scopes $s(x_j)$ and $s(y_m)$ of any $x_j$ and $y_m$ are balanced by weight elements $W$ and $W'$ of the same edge-gadget $\itn e$, then since $W$ and $W'$ are connected by a tensor, there are switchings of $W$, $W'$, $s(x_j)$, and $s(y_m)$ such that $x_j$ and $y_m$ are connected in the proof net for $\itn G$.
+%%
+%Then the first constraint element of $\itn{v_i}$ requires 2 edge-gadgets to balance, and each successive element requires one additional edge-gadget.
 \end{IEEEproof}

### 2014-01-21 main/LICS.tex
terminology: free (edge-gadget) => mobile

@@
 \section{Rewiring proof nets}
+\label{sec:rewiring}
 
@@
 %
-Furthermore, we will  \emph{parity},
+Furthermore, we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence.
 
 %i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
-
-% TODO: mention the parity problem
 
@@
 Take the root of the formula $\Gamma$ to be the root of this tree.
-Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
+%
+Now consider the bijection between non-root vertices and edges that associates each vertex with the edge towards its parent. 
+%
+A second linking $\links'$ similarly establishes such a bijection.
+Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the non-root vertices in $\Gamma$.
+Finally the parity of the pair of linkings is taken to be the parity of this permutation.
+%
+% Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
 This therefore establishes a bijection between the edges of the tree and the non-root vertices.
 %
-A second linking $\links'$ similarly establishes such a bijection.
+%A second linking $\links'$ similarly establishes such a bijection.
 Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
@@
 %
-Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and shall mean no more than a technical distraction.
+Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding.
+%
+It will prove a minor technical distraction, that we will call the `parity problem'.
 
@@
 \smallskip
-A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for an \capsabbrev{ncg} $G$ that differ in value (or definedness) on exactly one edge.
+A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for $G$ that differ in value (or definedness) on exactly one edge; this edge is then called \emph{mobile} in $\gamma$ and $\delta$.
 %
@@
 %
-Up to minor technical details, it will be shown that $\itn\gamma\perm\itn\delta$ if and only if $\gamma\perm\delta$, in two parts: completeness ($\Leftarrow$) and soundness ($\Rightarrow$).
-
-% TODO: mention the parity problem
+It will be shown that $\gamma\perm\delta$ if and only if $\itn\gamma\perm\itn\delta$ (modulo the parity problem---see Section~\ref{sec:rewiring}).
+%
+This will be separated into two parts: completeness ($\Rightarrow$) and soundness ($\Leftarrow$) .
 
@@
 %
-A well-linked edge-gadget is \emph{free} if all its weight elements connect to weight absorbers.
+A well-linked edge-gadget is \emph{mobile} if all its weight elements connect to weight absorbers.
 %
@@
 \label{lem:permute weight absorbers}
-If $\links$ is a well linked proof net for $\itn G$ with a free edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of weight absorbers, then $\links\perm\links'$.
+If $\links$ is a well linked proof net for $\itn G$ with a mobile edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of weight absorbers, then $\links\perm\links'$.
 \end{lemma}
@@
 \begin{IEEEproof}
-Let $e_0$ be the indicator of $\itn e$; since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
+Let $e_0$ be the indicator of $\itn e$; since $\itn e$ is mobile, $e_0$ may re-attach anywhere within the proof net.
 %
@@
 %
-Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is free.
+Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is mobile.
 %

### 2014-01-21 main/LICS.tex
Tweaks to the constraint graph stuff

@@
 %
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \capsabbrev{pspace}-hardness reductions.
-%
-A rewrite step consists of the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex.
-%
-Rewrite steps must preserve the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
-%
+\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reductions.
+%
+A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint} -- a natural number that may be taken to be always $2$ -- on each vertex.
+A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
+A rewrite step consists of the reversal of a single edge in a configuration:
+rewrite steps must preserve the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
+
 The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-
-We shall choose a variant of this formalism to suit our reduction to \capsabbrev{mll} proof equivalence.
-%
-A constraint graph itself will have \emph{undirected} edges, while a separate notion of \emph{configuration} imposes a direction on them.
-%
-A constraint graph may then be encoded as a sequent, and a configuration as a proof net.
-%
-As a minor adaptation, we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
+%
+A constraint graph may be encoded as a sequent, and a configuration as a proof net.
+%
+It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
 
@@
 A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting vertices $v(e)=\{v_1,v_2\}\subseteq V$.
-%of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.
 
@@
 
-\begin{theorem}[\cite{Hearn-Demaine-2005}]
+\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
 \capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.

### 2014-02-20 main/scratch.tex
\aftersubsection
Pictures for parity proof

@@
 
+\newcommand\parityNetA{
+  \begin{tikzpicture}[x=6mm,y=-7mm]
+	\node[pn] (a) at (-2,2) {$\nx a\1$};
+	\node[pn] (b) at (-1,2) {$\nx b\1$};
+	\node[pn] (c) at (1,2) {$\nx c\tn$};
+	\node[pn] (d) at (0,1) {$\nx d\bot$};
+	\node[pn] (e) at (1,1) {$\nx e\bot$};
+	\node[pn] (f) at (2,1) {$\nx f\bot$};
+	\node[pn] (g) at (4,2) {$\nx g\tn$};
+	\node[pn] (h) at (3,1) {$\nx h\bot$};
+	\node[pn] (i) at (5,1) {$\nx i\pr$};
+	\node[pn] (j) at (4,0) {$\nx j\1$};
+	\node[pn] (k) at (6,0) {$\nx k\1$};
+	%
+	\draw (c)--(d) (c)--(e) (c)--(f) (g)--(h) (g)--(i);
+	\draw[thick,dash pattern=on 3pt off 2pt] (i)--(j) (i)--(k);
+	%
+	\draw[octar,bend right=45] (d) to (b);
+	\draw[octar,bend left=60]  (e) to (k);
+	\draw[octar,bend left=45]  (f) to (j);
+	\draw[octar,bend right=60] (h) to (a);
+  \end{tikzpicture}
+}
+
+\newcommand\parityNetB{
+  \begin{tikzpicture}[x=6mm,y=-4mm]
+	\node[pn] (a) at (-1,3) {$\nx a\1$};
+	\node[pn] (b) at (0,10) {$\nx b\1$};
+	\node[pn] (c) at (1,7) {$\nx c\tn$};
+	\node[pn] (d) at (0,8) {$\nx d\bot$};
+	\node[pn] (e) at (2,8) {$\nx e\bot$};
+	\node[pn] (f) at (1,5) {$\nx f\bot$};
+	\node[pn] (g) at (0,0) {$\nx g\tn$};
+	\node[pn] (h) at (-1,1) {$\nx h\bot$};
+	\node[pn] (i) at (1,1) {$\nx i\pr$};
+	\node[pn] (j) at (1,3) {$\nx j\1$};
+	\node[pn] (k) at (2,10) {$\nx k\1$};
+	%
+	\draw (c)--(d) (c)--(f) (g)--(h);
+	\draw ($(g)!0.45!(i)$) -- (i);
+	\draw ($(c)!0.4!(e)$) -- (e);
+	\draw[thick,dash pattern=on 2pt off 2pt] (i)--(j);
+	%
+	\draw[octar,bend right=45] (d) to (b);
+	\draw[octar,bend right=45]  (e) to (k);
+	\draw[octar,bend left=45]  (f) to (j);
+	\draw[octar,bend right=45] (h) to (a);
+  \end{tikzpicture}
+}
+
+\newcommand\parityNetC[1]{
+	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+	  \node[pn] (1) at (-1,2) {$\nx a\1$};
+	  \node[pn] (2) at ( 1,2) {$\nx b\1$};
+	  \node[pn] (a) at ( 0,5) {$\bot$};
+	  %
+	  \draw (-.5,2) -- (2) -- (0,0) -- (1);
+	  \draw (a) -- (1,7) -- (-1,7) -- (a);
+	  %
+	  \SWITCH{#1}
+	    {1}{\draw[thepink,->,bend right=25] (a) to ($(1)+(.5,.5)$);}
+	    {2}{\draw[thepink,->,bend left]  (a) to (2);}
+	  \DEFAULT{}
+	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
+	\end{tikzpicture}
+}
+
+\newcommand\parityNetD[1]{
+  \SWITCH{#1}
+  {3}{\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+	  \node[pn] (a) at (0,2) {$\bot$};
+	  \node[pn] (2) at (1,7) {$\nx b\1$};
+	  \node[pn] (1) at (0,9) {$\nx a\1$};
+	  %
+	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
+	  \draw (1) -- (2) -- (2,9) -- (1);
+	  %
+	  \draw[thepink,->,bend left] (a) to (2);
+	\end{tikzpicture}
+  }
+  \DEFAULT{
+	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+	  \node[pn] (a) at (0,2) {$\bot$};
+	  \node[pn] (1) at (0,5) {$\nx a\1$};
+	  \node[pn] (2) at (1,7) {$\nx b\1$};
+	  %
+	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
+	  \draw (1) -- (2) -- (-1,7) -- (1);
+	  %
+	  \SWITCH{#1}
+	    {1}{\draw[thepink,->,bend left]  (a) to (1);}
+	    {2}{\draw[thepink,->,bend left] (a) to (2);}
+	  \DEFAULT{}
+	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
+	\end{tikzpicture}
+  }
+}
+\newcommand\parityNetE{
+  \begin{tikzpicture}[x=1mm,y=-7mm]
+	\node[pn] (a1) at ( 0,0) {$a$};
+	\node[pn] (a2) at (10,0) {$v_0$};
+	\node[pn] (a3) at (20,0) {$v_1$};
+	\node[pn] (an) at (40,0) {$v_{2n}$};
+	\node[pn] (b) at (50,0) {$b$};
+	\node at (30,.5) {$\dots$};
+	%
+	\draw ($(a1)+(2,0)$)--(a2)--(a3)--($(a3)+(4,0)$) ($(an)+(-5,0)$)--(an)--(b);
+	%
+	\foreach \a in {a1,a2,a3,an,b} {
+	  \draw (\a)--+(4,1)--+(-4,1)--(\a);
+	}
+  \end{tikzpicture}
+}
+
 \makeTheoremDefs
@@
 
-If a link $\edge ab$ may be reconnected as $\edge ac$ it is said that $a$ \emph{may connect to} $c$.
+\tikzstyle{octar}=[thepink,->,octo]
+\tikzstyle{pn}=[inner sep=1pt]
+\newcommand\nx[2]{#2_{\smash{\makebox[0pt][l]{\ensuremath{\scriptstyle{#1}}}}}}
+
+Given a named sequent $\Gamma$, we can identify edges across all switching graphs for all proof nets for $\Gamma$ by their parent connective: a tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges $v(1),\dotsc,v(n)$; a par $\named v\pr$ has one switched edge $v(1)$; and $\named v\bot$ has the jump $v(1)$.
 %
-By the above proposition, it is immediate that if $a$ and $b$ may both connect to $c$, then after actually reconnecting $\edge ac$, still $b$ may connect to $c$.
+For a switching graph, selecting a vertex as the root establishes a bijection between edges and the remaining nodes, which associates each edge with its target.
+%
+The example below displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $\named i\pr$, with chosen root $g$.
+\[
+	\vc{\parityNetA} \qquad \vc{\parityNetB}
+\]
+The tree above right associates, for example, the edge $c(3)$ with the vertex $c$, and $i(1)$ with $j$.
+%
+Two proof nets for the same sequent establish two such bijections, composing which gives a permutation on the (non-root) vertices.
+%
+If the nets are equivalent, the parity of this permutation is even.
+%
+This follows from what will be established next: a single rewiring connects switching graphs with even parity, and so does switching a single par.
+%
+The case for rewiring is illustrated; that for switching is similar.
+%
+For rewiring a jump $\edge va$ to $\edge vb$ (named $v(1)$ in the above scheme) there are two possibilities.
+%
+If the jump is directed towards the root, illustrated below left, then each node is connected to the root via the same edge, and the permutation is the identity.
+%
+If the jump is directed downward, the subtree of $a$ will get the new root node $b$, as illustrated below right.
+%
+\[
+	\vc{\parityNetC1} \perm \vc{\parityNetC2}
+\quad \vc{\rule{.5pt}{4cm}} \quad
+	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
+\]
+%
+The vertices that are assigned a new edge are exactly those on the path from $a$ to $b$ in the switching graph, illustrated below.
+%
+\[
+	\parityNetE
+\]
+%
+Since proof nets were assumed to be strictly alternating---each even $v_i$ is a $\bot$ or $\pr$, each odd $v_j$ a $\1$ or $\tn$---there are an odd number of vertices on this path, $2n+3$.
+%
+The permutation it induces is a cyclic one, matching each $v_i$ with $v_{i+1}$, $v_{2n}$ with $b$, $b$ with $a$, and $a$ with $v_0$.
+%
+A cyclic permutation of odd length is an odd permutation.
 
 \end{document}
+
+\newcommand\parityNetC[1]{
+	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+	  \node[circ,  outer sep=2pt] (1) at (-1,2) {};
+	  \node[circ,  outer sep=2pt] (2) at ( 1,2) {};
+	  \node[bullet,outer sep=2pt] (a) at ( 0,5) {};
+	  %
+	  \node[anchor=north east] at (1) {$a\vphantom b$};
+	  \node[anchor=north west] at (2) {$b$};
+	  %
+	  \draw (0,0) -- (1) -- (2) -- (0,0);
+	  \draw (a) -- (1,7) -- (-1,7) -- (a);
+	  %
+	  \SWITCH{#1}
+	    {1}{\draw[thepink,->,bend right] (a) to (1);}
+	    {2}{\draw[thepink,->,bend left]  (a) to (2);}
+	  \DEFAULT{}
+	\end{tikzpicture}
+}
+
+\newcommand\parityNetD[1]{
+  \SWITCH{#1}
+  {3}{\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+	  \node[bullet,outer sep=2pt] (a) at (0,2) {};
+	  \node[circ,  outer sep=2pt] (2) at (1,7) {};
+	  \node[circ,  outer sep=2pt] (1) at (0,9) {};
+	  %
+	  \node[anchor=south east] at (1) {$a$};
+	  \node[anchor=south east] at (2) {$b$};
+	  %
+	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
+	  \draw (1) -- (2) -- (2,9) -- (1);
+	  %
+	  \draw[thepink,->,bend left] (a) to (2);
+	\end{tikzpicture}
+  }
+  \DEFAULT{
+	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+	  \node[bullet,outer sep=2pt] (a) at (0,2) {};
+	  \node[circ,  outer sep=2pt] (1) at (0,5) {};
+	  \node[circ,  outer sep=2pt] (2) at (1,7) {};
+	  %
+	  \node[anchor=south east] at (1) {$a$};
+	  \node[anchor=north west] at (2) {$b$};
+	  %
+	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
+	  \draw (1) -- (2) -- (-1,7) -- (1);
+	  %
+	  \SWITCH{#1}
+	    {1}{\draw[thepink,->,bend left]  (a) to (1);}
+	    {2}{\draw[thepink,->,bend left] (a) to (2);}
+	  \DEFAULT{}
+	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
+	\end{tikzpicture}
+  }
+}

### 2014-04-03 main/LICS.tex
balanced header by removing address
added reviews, started making changes

@@
   		University of Bath
-	\\	Claverton Down
-	\\	Bath BA2~7AY
+	%\\	Claverton Down
+	%\\	Bath BA2~7AY
 	\\	w.b.heijltjes@bath.ac.uk
@@
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
-The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \cite{Strassburger-Lamarche-2004} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \color{red}\cite{Lamarche-Strassburger-2006}\color{black} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
 
@@
 In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \capsabbrev{pspace}-complete.
-It follows that there can be no satisfactory canonical notion of proof net.
+It follows that there can be no satisfactory canonical notion of proof net:
+\color{red}
+it is reasonable to ask that both the translation from proofs to nets and equality of proof nets are polynomial-time computable---but this would imply \capsabbrev{p}\,=\,\capsabbrev{pspace}.
+\color{black}
 
@@
 
-\begin{proposition}[\cite{Danos-Regnier-1989}]
+\begin{proposition}[\cite{Danos-Regnier-1989}, \color{red}\cite{Lamarche-Strassburger-2006}\color{black}]
 \label{prop:correctness and sequentialisation}
@@
 %
-A dashed edge will indicate that two vertices are connected, in a proof net or a switching graph, as illustrated below.
+\color{red}
+A path in a proof net or switching graph is indicated $\path ab$, and illustrated as below.
+\color{black}
+%
+%A dashed edge will indicate that two vertices are connected, in a proof net or a switching graph, as illustrated below.
 \[
@@
 %
-In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
-%
-In the example below, a scope of a (ternary) par is indicated (left) and contracted (right).
+\color{red}
+In the graph of a proof net, the scope of a par can be made explicit as a \emph{box}, as illustrated below left.
+%
+Boxes may replace the switching condition as a correctness criterion: in the example, both the outside and the inside of the box form a tree.
+%
+To make this precise, we will consider the action of \emph{closing} a box, which will mean we consider it as a single vertex in the graph.
+
 \[
@@
 \]
-%
-The contraction of scopes may replace the switching condition as a correctness criterion.
-%
-The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
+
+\begin{definition}
+A \emph{boxing} $s$ for a linking $\links$ for $\Gamma$ assigns a sub-sequent $s(v)\leq\Gamma$ to each par-vertex $\named v\parr$ such that 1) $v$ is a port of $s(v)$ and 2) boxes are either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$.
+\end{definition}
+
+\noindent
+In the graph for $\links$ and $\Gamma$, a box $s(v)$ may be \emph{closed} by replacing the subgraph over $s(v)$ by the single vertex $v$, and replacing every arc into $s(v)$ by one onto $v$.
+%
+For each box $s(v)$ we define the \emph{local graph} to be that formed by the subgraph over $s(v)$ where each immediately smaller box $s(w)<s(v)$ is closed.
+%
+The following is then a variation on the local retraction algorithm by Danos \cite{Danos-1990}.
 
@@
 \label{prop:scoping correctness}
-A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
-
-\begin{enumerate}
-	\item
-sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
-	\item
-for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all immediate sub-sequents are contracted.
-\end{enumerate}
-%
+A linking $\links$ for $\Gamma$ is a proof net if and only if it has a boxing $s$ such that each local graph is a tree.
 \end{proposition}
 
-\begin{IEEEproof}
-For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
-%
-For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
+\begin{proof}
+Given a boxing $s$, it follows by induction on the nesting of boxes that the graph over each $s(v)$ satisfies the switching condition.
+%
+In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
 \[
@@
 \vskip-12pt
-\end{IEEEproof}
+\end{proof}
+
+\color{black}
+
+%
+%In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
+%%
+%In the example below, a scope of a (ternary) par is indicated (left) and contracted (right).
+%\[
+%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+%	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
+%		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
+%		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
+%	\node[circ] (0) at (5.75,0) {};
+%	\node[circ] (1) at (-1,3) {};
+%	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
+%	\draw[rounded corners] (0,2) rectangle (4,4);
+%	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
+%	\begin{scope}[thepink,->]
+%			\draw[bend right=10] (x) to (1);
+%			\draw[bend right=20] (y) to (2);
+%			\draw[bend right=10] (a) to (2);
+%			\draw[bend right=10] (b) to (3);
+%			\draw[bend left=10]  (c) to (3);
+%			\draw[bend left=10]  (d) to (4);
+%			\draw[bend right=10] (e) to (0);
+%	\end{scope}
+%	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
+%\end{tikzpicture}
+%\qquad\qquad
+%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+%	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
+%	\node[circ] (0) at (3,0) {};
+%	\node[circ] (1) at (-1,3) {};
+%	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
+%	\draw (box)--(3,3) node[bullet] (e) {};
+%	\begin{scope}[thepink,->]
+%			\draw[bend right=10] (x) to (1);
+%			\draw[bend right=20] (y) to (box);
+%			\draw[bend right=10] (e) to (0);
+%	\end{scope}
+%	\path (0,4.25)--(1,4.25);
+%\end{tikzpicture}
+%\]
+%%
+%The contraction of a scope corresponds to the use of a box,  may replace the switching condition as a correctness criterion:
+%%
+%The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
+
+%
+%\begin{proposition}
+%\label{prop:scoping correctness}
+%A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
+%
+%\begin{enumerate}
+%	\item
+%sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
+%	\item
+%for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all \color{red} (immediate) sub-sequents $s(w)<s(v)$ are contracted.
+%\end{enumerate}
+%%
+%\end{proposition}
+%
+%
+%\begin{IEEEproof}
+%For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
+%%
+%For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
+%\[
+%	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
+%\]
+%\vskip-12pt
+%\end{IEEEproof}
 
@@
 %
-Firstly, we repeat the following proposition.
+\color{red} 
+We will denote the empire of $v$ in $\links$ by $\emp v$.
+\color{black}
 
@@
 \label{prop:empire propagation}
-The empire $\sigma$ of $v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\sigma$; 4) into a par if all its subformulae are in $\sigma$; 5) except never into a par or tensor if $v$ is a subformula.
+The empire $\emp v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v$; 4) into a par if all its subformulae are in $\emp v$; 5) except never into a par or tensor if $v$ is a subformula.
 \end{proposition}
@@
 	\item
-$w$ is in the empire of $a$; and
-	\item
-in any switching graph for $(\Gamma,\links)$, the path from $v$ to $w$ does not pass through $a$.
+$w$ is in the empire $\emp a$; and
+	\item
+in any switching graph for $(\Gamma,\links)$, the path $\path vw$ does not pass through $a$.
 \end{enumerate}
@@
 
-Next, the empire of $a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
-%
-By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net $\sigma$, $a$ may link anywhere in $\sigma$.
-%
-Then 2 implies 1.
-
-Finally, if for some switching of $\links$ the path from $v$ to $w$ passes through $a$, then in $\links'$ there is no path between $a$ and $v$ (and two paths between $a$ and $w$) for that switching, so $\links'$ is not a net; then by contraposition 1 implies 3.
+Next, it is shown that 2 implies 1.
+%
+The empire $\emp a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
+%
+By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net, $a$ may link to any $1$-occurrence, including to $w$.
+
+Finally, it is shown that 1 implies 3, by contraposition.
+%
+If for some switching of $\links$ the path $\path vw$ passes through $a$, then in $\links'$ there is no path $\path av$ (and two paths $\path aw$) for that switching, so $\links'$ is not a net.
 %
@@
 \label{lem:rewiring preserves empire}
-Let $\links\perm*\links'$ by $\links(v)\neq\links'(v)$, and denote the empire of $v$ in $\links$ and $\links'$ by $\sigma$ and $\sigma'$ respectively; then $\sigma\perm*\sigma'$.
+If $\links\perm*\links'$ by $\links(v)\neq\links'(v)$ then $\emp v\perm*\emp*v$.
 \end{lemma}
@@
 \begin{IEEEproof}
-By Lemma~\ref{lem:rewiring within empire} the empires $\sigma$ and $\sigma'$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
-%
-That $\sigma$ and $\sigma'$ must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is.
+By Lemma~\ref{lem:rewiring within empire} the empires $\emp v$ and $\emp*v$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
+%
+That $\emp v$ and $\emp*v$ must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is.
 %
@@
 \label{lem:rewiring affects empires}
-For proof nets $\links\perm*\links'$, let the empire of a given vertex $v$ in $\links$ be a net for the sequent $\Delta$, and in $\links'$, for $\Delta'$; then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
+If $\links\perm*\links'$ where $\emp v$ is a net for the sequent $\Delta$, and $\emp*v$ a net for $\Delta'$, then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
 \end{lemma}
@@
 \label{lem:double exchange}
-Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path from $u$ to $y$ passes through the links $\edge bv$ and $\edge xc$.
-%
-Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+Let $\links$ be a proof net with for every switching a path
+$\links(a){\xedge}a{\xpath}b{\xedge}\links(b){\xpath}\links(c){\xedge}c{\xpath}d{\xedge}\links(d)$.
+%
+Then $\links\perm\links'$ where $\links'(a)=\links(b)$ and $\links'(b)=\links(a)$, $\links'(c)=\links(d)$, and $\links'(d)=\links(c)$, and $\links'(z)=\links(z)$ otherwise.
+%
+%Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path $\path uy$ passes through $\edge bv$ and $\edge xc$.
+%
+%Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
 \end{lemma}
@@
 %
-For the inductive step, let $A\tn\named a\bot$ be a largest $\tn$-formula in $\Gamma$, and pick an occurence $\named z\1$.
-%
-It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, for the sequent $\Gamma$ with $\named z\1$ removed and $A\tn\named a\bot$ replaced by $A$, the subnet for $\links'$ belongs to one of two equivalence classes.
-
-To find $\links'$, if $\links(a)=z$ we are done.
-%
-Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
-%
-Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
-%
-Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
-%
-Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
-
-Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
-%
-Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
+For the inductive step,
+%
+\color{red}
+let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.
+%
+It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, the subnet $\links'$ restricted to $\Gamma',A$ belongs to one of two equivalence classes.
+%
+To find $\links'$, there are two cases.
+
+1) The path $\path az$ is via $\links(a)$.
+%
+If $\links(a)=z$, we are done. Otherwise, by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
+
+2) The path $\path az$ is via some $\named b\bot$ in $A$.
+%
+Firstly, if $\links(b)\neq z$, use Lemma~\ref{lem:rewiring within empire} to re-attach $b$ to $z$.
+%
+Next, let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
+%
+Then $\links'$ is obtained by linking $c$ to $b$, and applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as those of $c$ and $d$.
+%
 \end{IEEEproof}
+\color{black}
+
+%
+%To find $\links'$, if $\links(a)=z$ we are done.
+%%
+%Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
+%%
+%Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
+%%
+%Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
+%%
+%Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
+%
+%
+%Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
+%%
+%Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
 
@@
 %
-Now consider the bijection between non-root vertices and edges that associates each vertex with the edge towards its parent. 
-%
-A second linking $\links'$ similarly establishes such a bijection.
+
+\color{red}
+Given a named sequent $\Gamma$, we can identify edges across all switching graphs for all proof nets for $\Gamma$ by their parent connective: a tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges $v(1),\dotsc,v(n)$; a par $\named v\pr$ has one switched edge $v(1)$; and $\named v\bot$ has the jump $v(1)$.
+%
+For a switching graph, selecting a vertex as the root establishes a bijection between edges and the remaining nodes, which associates each edge with its target.
+%
+The example below displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $\named i\pr$, with chosen root $g$.
+\[
+	\vc{\parityNetA} \qquad \vc{\parityNetB}
+\]
+The tree above right associates, for example, the edge $c(3)$ with the vertex $c$, and $i(1)$ with $j$.
+%
+Two proof nets for the same sequent establish two such bijections, composing which gives a permutation on the (non-root) vertices.
+%
+If the nets are equivalent, the parity of this permutation is even.
+%
+This follows from what will be established next: a single rewiring connects switching graphs with even parity, and so does switching a single par.
+%
+The case for rewiring is illustrated; that for switching is similar.
+%
+For rewiring a jump $\edge va$ to $\edge vb$ (named $v(1)$ in the above scheme) there are two possibilities.
+%
+If the jump is directed towards the root, illustrated below left, then each node is connected to the root via the same edge, and the permutation is the identity.
+%
+If the jump is directed downward, the subtree of $a$ will get the new root node $b$, as illustrated below right.
+%
+\[
+	\vc{\parityNetC1} \perm \vc{\parityNetC2}
+\quad \vc{\rule{.5pt}{4cm}} \quad
+	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
+\]
+%
+The vertices that are assigned a new edge are exactly those on the path from $a$ to $b$ in the switching graph, illustrated below.
+%
+\[
+	\parityNetE
+\]
+%
+Since proof nets were assumed to be strictly alternating---each even $v_i$ is a $\bot$ or $\pr$, each odd $v_j$ a $\1$ or $\tn$---there are an odd number of vertices on this path, $2n+3$.
+%
+The permutation it induces is a cyclic one, matching each $v_i$ with $v_{i+1}$, $v_{2n}$ with $b$, $b$ with $a$, and $a$ with $v_0$.
+%
+A cyclic permutation of odd length is an even permutation.
+
+\color{black}
+
+%Now consider the bijection between non-root vertices and edges that associates each vertex with the edge towards its parent. 
+%
+%A second linking $\links'$ similarly establishes such a bijection.
 Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the non-root vertices in $\Gamma$.
@@
 %
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reductions.
+\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reduction.
 %
@@
 
-The standard linkings defined in the first and third case of the above definition are illustrated below.
+The standard linkings defined in the \color{red} second \color{black} and third case of the above definition are illustrated below.
 
@@
 \label{lem:octopus roll}
-In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},\bot^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $\bot^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $\bot^n$, and $\links'$ agrees with $\links$ otherwise.
+In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}
@@
 	\item\label{item:exchange added}
-In the present configuration, the links from the weight elements form two subnets: one over the sub-sequents $A,B,X,D,\bot^m$, and one over the sub-sequent $C,Y,E,F,\bot^k$, for some $m$ and $k$.
+In the present configuration, the links from the weight elements form two subnets: one over the sub-sequents $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
 %
@@
 %
-The links of $A,B,C$ link to the weight absorbers $\bot^m$ and $\bot^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+The links of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
 %

### 2014-04-03 main/scratch.tex
added reviews, started making changes

@@
 \documentclass[conference]{IEEEtran}
+
+\usepackage[default]{frcursive}
+\usepackage[T1]{fontenc}
 
@@
 
-\newcommand\parityNetA{
-  \begin{tikzpicture}[x=6mm,y=-7mm]
-	\node[pn] (a) at (-2,2) {$\nx a\1$};
-	\node[pn] (b) at (-1,2) {$\nx b\1$};
-	\node[pn] (c) at (1,2) {$\nx c\tn$};
-	\node[pn] (d) at (0,1) {$\nx d\bot$};
-	\node[pn] (e) at (1,1) {$\nx e\bot$};
-	\node[pn] (f) at (2,1) {$\nx f\bot$};
-	\node[pn] (g) at (4,2) {$\nx g\tn$};
-	\node[pn] (h) at (3,1) {$\nx h\bot$};
-	\node[pn] (i) at (5,1) {$\nx i\pr$};
-	\node[pn] (j) at (4,0) {$\nx j\1$};
-	\node[pn] (k) at (6,0) {$\nx k\1$};
-	%
-	\draw (c)--(d) (c)--(e) (c)--(f) (g)--(h) (g)--(i);
-	\draw[thick,dash pattern=on 3pt off 2pt] (i)--(j) (i)--(k);
-	%
-	\draw[octar,bend right=45] (d) to (b);
-	\draw[octar,bend left=60]  (e) to (k);
-	\draw[octar,bend left=45]  (f) to (j);
-	\draw[octar,bend right=60] (h) to (a);
-  \end{tikzpicture}
-}
+\DeclareRobustCommand{\frcshape}{\fontfamily{frc}\selectfont}
+\DeclareTextFontCommand{\textfrc}{\frcshape}
 
-\newcommand\parityNetB{
-  \begin{tikzpicture}[x=6mm,y=-4mm]
-	\node[pn] (a) at (-1,3) {$\nx a\1$};
-	\node[pn] (b) at (0,10) {$\nx b\1$};
-	\node[pn] (c) at (1,7) {$\nx c\tn$};
-	\node[pn] (d) at (0,8) {$\nx d\bot$};
-	\node[pn] (e) at (2,8) {$\nx e\bot$};
-	\node[pn] (f) at (1,5) {$\nx f\bot$};
-	\node[pn] (g) at (0,0) {$\nx g\tn$};
-	\node[pn] (h) at (-1,1) {$\nx h\bot$};
-	\node[pn] (i) at (1,1) {$\nx i\pr$};
-	\node[pn] (j) at (1,3) {$\nx j\1$};
-	\node[pn] (k) at (2,10) {$\nx k\1$};
-	%
-	\draw (c)--(d) (c)--(f) (g)--(h);
-	\draw ($(g)!0.45!(i)$) -- (i);
-	\draw ($(c)!0.4!(e)$) -- (e);
-	\draw[thick,dash pattern=on 2pt off 2pt] (i)--(j);
-	%
-	\draw[octar,bend right=45] (d) to (b);
-	\draw[octar,bend right=45]  (e) to (k);
-	\draw[octar,bend left=45]  (f) to (j);
-	\draw[octar,bend right=45] (h) to (a);
-  \end{tikzpicture}
-}
-
-\newcommand\parityNetC[1]{
-	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
-	  \node[pn] (1) at (-1,2) {$\nx a\1$};
-	  \node[pn] (2) at ( 1,2) {$\nx b\1$};
-	  \node[pn] (a) at ( 0,5) {$\bot$};
-	  %
-	  \draw (-.5,2) -- (2) -- (0,0) -- (1);
-	  \draw (a) -- (1,7) -- (-1,7) -- (a);
-	  %
-	  \SWITCH{#1}
-	    {1}{\draw[thepink,->,bend right=25] (a) to ($(1)+(.5,.5)$);}
-	    {2}{\draw[thepink,->,bend left]  (a) to (2);}
-	  \DEFAULT{}
-	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
-	\end{tikzpicture}
-}
-
-\newcommand\parityNetD[1]{
-  \SWITCH{#1}
-  {3}{\begin{tikzpicture}[x=5mm,y=-4mm,octo]
-	  \node[pn] (a) at (0,2) {$\bot$};
-	  \node[pn] (2) at (1,7) {$\nx b\1$};
-	  \node[pn] (1) at (0,9) {$\nx a\1$};
-	  %
-	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
-	  \draw (1) -- (2) -- (2,9) -- (1);
-	  %
-	  \draw[thepink,->,bend left] (a) to (2);
-	\end{tikzpicture}
-  }
-  \DEFAULT{
-	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
-	  \node[pn] (a) at (0,2) {$\bot$};
-	  \node[pn] (1) at (0,5) {$\nx a\1$};
-	  \node[pn] (2) at (1,7) {$\nx b\1$};
-	  %
-	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
-	  \draw (1) -- (2) -- (-1,7) -- (1);
-	  %
-	  \SWITCH{#1}
-	    {1}{\draw[thepink,->,bend left]  (a) to (1);}
-	    {2}{\draw[thepink,->,bend left] (a) to (2);}
-	  \DEFAULT{}
-	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
-	\end{tikzpicture}
-  }
-}
-\newcommand\parityNetE{
-  \begin{tikzpicture}[x=1mm,y=-7mm]
-	\node[pn] (a1) at ( 0,0) {$a$};
-	\node[pn] (a2) at (10,0) {$v_0$};
-	\node[pn] (a3) at (20,0) {$v_1$};
-	\node[pn] (an) at (40,0) {$v_{2n}$};
-	\node[pn] (b) at (50,0) {$b$};
-	\node at (30,.5) {$\dots$};
-	%
-	\draw ($(a1)+(2,0)$)--(a2)--(a3)--($(a3)+(4,0)$) ($(an)+(-5,0)$)--(an)--(b);
-	%
-	\foreach \a in {a1,a2,a3,an,b} {
-	  \draw (\a)--+(4,1)--+(-4,1)--(\a);
-	}
-  \end{tikzpicture}
-}
+%\newenvironment{frcseries}{\fontfamily{frc}\selectfont}{}
+%\newcommand{\textfrc}[1]{{\frcseries#1}}
 
@@
 \begin{document}
+
+\textfrc{l ~ k}
+
+\[
+\links ~ \textfrc{l ~ k}
+\]
+
+\end{document}
 
@@
 %
-A cyclic permutation of odd length is an odd permutation.
+A cyclic permutation of odd length is an even permutation.
 
 \end{document}
+
+%
+%\newcommand\parityNetA{
+%  \begin{tikzpicture}[x=6mm,y=-7mm]
+%	\node[pn] (a) at (-2,2) {$\nx a\1$};
+%	\node[pn] (b) at (-1,2) {$\nx b\1$};
+%	\node[pn] (c) at (1,2) {$\nx c\tn$};
+%	\node[pn] (d) at (0,1) {$\nx d\bot$};
+%	\node[pn] (e) at (1,1) {$\nx e\bot$};
+%	\node[pn] (f) at (2,1) {$\nx f\bot$};
+%	\node[pn] (g) at (4,2) {$\nx g\tn$};
+%	\node[pn] (h) at (3,1) {$\nx h\bot$};
+%	\node[pn] (i) at (5,1) {$\nx i\pr$};
+%	\node[pn] (j) at (4,0) {$\nx j\1$};
+%	\node[pn] (k) at (6,0) {$\nx k\1$};
+%	%
+%	\draw (c)--(d) (c)--(e) (c)--(f) (g)--(h) (g)--(i);
+%	\draw[thick,dash pattern=on 3pt off 2pt] (i)--(j) (i)--(k);
+%	%
+%	\draw[octar,bend right=45] (d) to (b);
+%	\draw[octar,bend left=60]  (e) to (k);
+%	\draw[octar,bend left=45]  (f) to (j);
+%	\draw[octar,bend right=60] (h) to (a);
+%  \end{tikzpicture}
+%}
+%
+%\newcommand\parityNetB{
+%  \begin{tikzpicture}[x=6mm,y=-4mm]
+%	\node[pn] (a) at (-1,3) {$\nx a\1$};
+%	\node[pn] (b) at (0,10) {$\nx b\1$};
+%	\node[pn] (c) at (1,7) {$\nx c\tn$};
+%	\node[pn] (d) at (0,8) {$\nx d\bot$};
+%	\node[pn] (e) at (2,8) {$\nx e\bot$};
+%	\node[pn] (f) at (1,5) {$\nx f\bot$};
+%	\node[pn] (g) at (0,0) {$\nx g\tn$};
+%	\node[pn] (h) at (-1,1) {$\nx h\bot$};
+%	\node[pn] (i) at (1,1) {$\nx i\pr$};
+%	\node[pn] (j) at (1,3) {$\nx j\1$};
+%	\node[pn] (k) at (2,10) {$\nx k\1$};
+%	%
+%	\draw (c)--(d) (c)--(f) (g)--(h);
+%	\draw ($(g)!0.45!(i)$) -- (i);
+%	\draw ($(c)!0.4!(e)$) -- (e);
+%	\draw[thick,dash pattern=on 2pt off 2pt] (i)--(j);
+%	%
+%	\draw[octar,bend right=45] (d) to (b);
+%	\draw[octar,bend right=45]  (e) to (k);
+%	\draw[octar,bend left=45]  (f) to (j);
+%	\draw[octar,bend right=45] (h) to (a);
+%  \end{tikzpicture}
+%}
+%
+%\newcommand\parityNetC[1]{
+%	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+%	  \node[pn] (1) at (-1,2) {$\nx a\1$};
+%	  \node[pn] (2) at ( 1,2) {$\nx b\1$};
+%	  \node[pn] (a) at ( 0,5) {$\bot$};
+%	  %
+%	  \draw (-.5,2) -- (2) -- (0,0) -- (1);
+%	  \draw (a) -- (1,7) -- (-1,7) -- (a);
+%	  %
+%	  \SWITCH{#1}
+%	    {1}{\draw[thepink,->,bend right=25] (a) to ($(1)+(.5,.5)$);}
+%	    {2}{\draw[thepink,->,bend left]  (a) to (2);}
+%	  \DEFAULT{}
+%	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
+%	\end{tikzpicture}
+%}
+%
+%\newcommand\parityNetD[1]{
+%  \SWITCH{#1}
+%  {3}{\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+%	  \node[pn] (a) at (0,2) {$\bot$};
+%	  \node[pn] (2) at (1,7) {$\nx b\1$};
+%	  \node[pn] (1) at (0,9) {$\nx a\1$};
+%	  %
+%	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
+%	  \draw (1) -- (2) -- (2,9) -- (1);
+%	  %
+%	  \draw[thepink,->,bend left] (a) to (2);
+%	\end{tikzpicture}
+%  }
+%  \DEFAULT{
+%	\begin{tikzpicture}[x=5mm,y=-4mm,octo]
+%	  \node[pn] (a) at (0,2) {$\bot$};
+%	  \node[pn] (1) at (0,5) {$\nx a\1$};
+%	  \node[pn] (2) at (1,7) {$\nx b\1$};
+%	  %
+%	  \draw (0,0) -- (1,2) -- (a) -- (-1,2) -- (0,0);
+%	  \draw (1) -- (2) -- (-1,7) -- (1);
+%	  %
+%	  \SWITCH{#1}
+%	    {1}{\draw[thepink,->,bend left]  (a) to (1);}
+%	    {2}{\draw[thepink,->,bend left] (a) to (2);}
+%	  \DEFAULT{}
+%	  \node[circ,outer sep=2pt,draw opacity=0] at (0,9) {};
+%	\end{tikzpicture}
+%  }
+%}
+%\newcommand\parityNetE{
+%  \begin{tikzpicture}[x=1mm,y=-7mm]
+%	\node[pn] (a1) at ( 0,0) {$a$};
+%	\node[pn] (a2) at (10,0) {$v_0$};
+%	\node[pn] (a3) at (20,0) {$v_1$};
+%	\node[pn] (an) at (40,0) {$v_{2n}$};
+%	\node[pn] (b) at (50,0) {$b$};
+%	\node at (30,.5) {$\dots$};
+%	%
+%	\draw ($(a1)+(2,0)$)--(a2)--(a3)--($(a3)+(4,0)$) ($(an)+(-5,0)$)--(an)--(b);
+%	%
+%	\foreach \a in {a1,a2,a3,an,b} {
+%	  \draw (\a)--+(4,1)--+(-4,1)--(\a);
+%	}
+%  \end{tikzpicture}
+%}
 

### 2014-04-03 main/LICS.tex
added figure, minor edits

@@
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
-The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \color{red}\cite{Lamarche-Strassburger-2006}\color{black} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \color{red}\cite{Lamarche-Strassburger-2006} \color{black} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
 
@@
 
-The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008} for \capsabbrev{mll} without units).
+The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
 %
@@
 and
-formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
+formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula \color{red}(or for illustrative purposes)\color{black}.
 %
@@
 \color{red} 
-We will denote the empire of $v$ in $\links$ by $\emp v$.
+We will denote the empire of $v$ in $\links$ by $\emp v$ (used both as a graph and a set of vertices).
 \color{black}
@@
 \label{prop:empire propagation}
-The empire $\emp v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v$; 4) into a par if all its subformulae are in $\emp v$; 5) except never into a par or tensor if $v$ is a subformula.
+The empire $\emp v$ is determined by propagation from $v$: 1) through links;\\ \color{red} 2) up towards subformulae;\\ 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$;\\ 4) into a par if all its subformulae are in $\emp v-\{v\}$.%;\\ 5) except never into a par or tensor if $v$ is a subformula.
 \end{proposition}
@@
 %
-After removing $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
+After removing \color{red}dangling \color{black} $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
 
@@
 %
-A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint} -- a natural number that may be taken to be always $2$ -- on each vertex.
+A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint}---a natural number that may be taken to be always $2$---on each vertex.
 A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
@@
 rewrite steps must preserve the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
+
+\color{red}
+Figure~\ref{fig:NCL example} shows an example rewrite sequence in a constraint graph.
+%
+The central node has inflow constraint 2, the thick blue (dark grey) edge has weight 2, and the thinner red (light grey) edges have weight 1.
+\color{black}
+
+\begin{figure}\color{red}
+$
+\quad
+\vc{\begin{tikzpicture}[x=3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,->-] (3,0) -- (5,2);
+	\draw[ncl1,->-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\,\perm*\hfill
+\vc{\begin{tikzpicture}[x=3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,->-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\,\perm*\hfill
+\vc{\begin{tikzpicture}[x=3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,-<-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\,\perm*\hfill
+\vc{\begin{tikzpicture}[x=3mm,y=3mm]
+	\draw[ncl2,-<-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,-<-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\quad
+$
+
+\smallskip
+\caption{A series of reconfiguration steps in a constraint graph}
+\label{fig:NCL example}
+\end{figure}
 
@@
 \label{def:standard linkings}
-For a weight element $W=W_n(i,j)=A\parr B\parr C$,
+For $W=W_n(i,j)=A\parr B\parr C$ a weight element,
 \begin{enumerate}

### 2014-04-08 main/LICS.tex
migrated to sigplanconf class

@@
-\documentclass[conference]{IEEEtran}
+\documentclass{sigplanconf-modified}
+
+% NOTE: sigplanconf.cls modified to remove DOI line.
 
@@
 
-\author{
-  \IEEEauthorblockN{Willem Heijltjes}
-  \IEEEauthorblockA{
-  		University of Bath
-	%\\	Claverton Down
-	%\\	Bath BA2~7AY
-	\\	w.b.heijltjes@bath.ac.uk
-	}
-\and
-  \IEEEauthorblockN{Robin Houston}
-  \IEEEauthorblockA{
-		Kiln Enterprises
-	\\	robin@kiln.it
-	}
-}
-
-\title{No proof nets for \capsabbrev{mll} with units\\[5pt]\Large Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}
+\title{No proof nets for \capsabbrev{mll} with units}
+\subtitle{Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}
+
+\authorinfo
+ {Willem Heijltjes}
+ {University of Bath}
+ {w.b.heijltjes@bath.ac.uk}
+\authorinfo
+ {Robin Houston}
+ {Kiln Enterprises}
+ {robin@kiln.it}
+
+\conferenceinfo{CSL-LICS'14}{July 14--18, 2014, Vienna, Austria} 
+\copyrightyear{2014} 
+%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
+%\doi{}
 
@@
 \maketitle
+
+% ACM classifications:
+% F.2.2 - Nonnumerical Algorithms and Problems (Complexity of proof procedures)
+% F.4.1 - Mathematical logic (Proof theory)
+
+\category{F.4.1}{Mathematical logic and formal languages}{Mathematical logic}[Proof theory]
+\category{F.2.2}{Analysis of algorithms and problem complexity}{Nonnumerical algorithms and problems}[Complexity of proof procedures]
 
@@
 %
-%\begin{IEEEproof}
+%\begin{proof}
 %For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
@@
 %\vskip-12pt
-%\end{IEEEproof}
+%\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.
@@
 %
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By Lemma~\ref{lem:rewiring within empire} the empires $\emp v$ and $\emp*v$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
@@
 
-\begin{IEEEproof}
+\begin{proof}
 Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
@@
 \vskip-12pt
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By the rewiring path shown in Figure~\ref{fig:double exchange}.
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By induction on the size of a sequent $\Gamma$.
@@
 %
-\end{IEEEproof}
+\end{proof}
 \color{black}
@@
 \end{lemma}
-\begin{IEEEproof}
+\begin{proof}
 	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
@@
 	permutation of an odd number of elements is an even permutation.
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By Proposition~\ref{prop:level0 max binary} the sequent has at most 2 equivalence classes.
@@
 Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By the following two observations: firstly, 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
@@
 After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
-\end{IEEEproof}
+\end{proof}
 
@@
 \label{lem:octopus roll}
-In a proof net $\links$ for a sequent $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
+In a proof net $\links$ for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}
@@
 
-\begin{IEEEproof}
+\begin{proof}
 Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
@@
 %
-\displayOcto{\octorollA2\IEEEQEDhere}
+\displayOcto{\octorollA2}%\QEDhere}
 \end{enumerate}
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 Let $e_0$ be the indicator of $\itn e$; since $\itn e$ is mobile, $e_0$ may re-attach anywhere within the proof net.
@@
 
-\begin{IEEEproof}
+\begin{proof}
 By Proposition~\ref{prop:partial simulates total reconfiguration} we may assume that $\gamma\perm\delta$ by a sequence of reconfiguration steps over total configurations.
@@
 The resulting proof net is $\itn\delta$ modulo a permutation of weight absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute weight absorbers}.
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 Since vertex-gadgets are joined by a tensor, the lemma is immediate from Proposition~\ref{prop:tensor has disjoint subnets}.
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 Let $|V|=n$ and $|E|=m$, and consider the vertex $v_i$ and an edge $e$ connecting vertices $v_a$ and $v_b$ where $i\neq a,b$.
@@
 %Then the first constraint element of $\itn{v_i}$ requires 2 edge-gadgets to balance, and each successive element requires one additional edge-gadget.
-\end{IEEEproof}
+\end{proof}
 
@@
 
-\begin{IEEEproof}
+\begin{proof}
 The proof will consider the case where $\links\perm*\links'$; the general case follows by transitivity.
@@
 
-\begin{IEEEproof}
+\begin{proof}
 \capsabbrev{mll} proof equivalence has at most non-deterministic polynomial space complexity: a proof net may be represented in linear space (with respect to a proof); a single rewiring step is performed without requiring additional space; and a non-deterministic algorithm may guess the correct rewiring sequence.

### 2014-04-17 main/LICS.tex
new drawings
added new drawings to main file
re-ordered sections

@@
-\documentclass{sigplanconf-modified}
-
-% NOTE: sigplanconf.cls modified to remove DOI line.
+\documentclass{sigplanconf}
 
@@
 
-\conferenceinfo{CSL-LICS'14}{July 14--18, 2014, Vienna, Austria} 
+\conferenceinfo{CSL-LICS 2014}{July 14--18, 2014, Vienna, Austria} 
 \copyrightyear{2014} 
-%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
-%\doi{}
+\copyrightdata{978-1-4503-2886-9}
+\doi{nnnnnnn.nnnnnnn}
 
@@
 
-Later, a striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic -- two proofs are equivalent if and only if they have the same proof net -- so proof nets offer a simple decision procedure for proofs in this fragment.
+Later, a striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic---two proofs are equivalent if and only if they have the same proof net---so proof nets offer a simple decision procedure for proofs in this fragment.
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
@@
 \color{red}
-it is reasonable to ask that both the translation from proofs to nets and equality of proof nets are polynomial-time computable---but this would imply \capsabbrev{p}\,=\,\capsabbrev{pspace}.
+if a notion of proof net existed where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
 \color{black}
@@
 \aftersubsection
-The proof of \capsabbrev{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in nondeterministic
+The proof of \capsabbrev{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in non-deterministic
 \emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
 %
-Constraint logic is a simple graph rewriting formalism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied; the configuration-to-configuration question is whether two graphs are related by a sequence of valid rewriting steps.
+Constraint logic is a simple graph rewriting formalism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied; the configuration-to-configuration problem asks whether two graphs are related by a sequence of rewriting steps.
 
@@
 Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names, e.g.\
-$\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot$.
+\[
+	\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot~.
+\]
 %
@@
 %
-\emph{Equivalence} of proofs $(\perm)$ in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
+\emph{Equivalence} $(\perm)$ of proofs in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
 %
@@
 %
-% MAYBE SAY: The restriction that links must target $\1$-occurrences (rather than any connective) can be circumvented by replacing a subformula $A$ by the equivalent $A\tn\1$.
+\color{red}
+The restriction that jumps must target $\1$-occurrences (rather than any connective) is a convenience---it can be circumvented by replacing a subformula $A$ by the equivalent $A\tn\1$.
+\color{black}
+
+\begin{figure}
+\color{red}
+\[
+	\netA 1223 ~\perm*~
+	\netA 1323 ~\perm*~
+	\netA 1321 ~\perm*~
+	\netA 2321
+\]
+\caption{A rewiring sequence on proof nets}
+\label{fig:net rewiring}
+\end{figure}
 
@@
 %
-\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by rewirings.
+\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by rewiring.
 %
@@
 \noindent
-In the sequent calculus, the introduction rule for $\bot$ joins a $\bot$-formula to a sequent $\Gamma$, rather than an occurrence of $\1$.
-%
-The interpretation of a proof as a proof net may attach the corresponding link to an arbitrary $\1$ in $\Gamma$.
+\color{red}
+An example rewiring sequence is given in Figure~\ref{fig:net rewiring}, using the notation for proof nets introduced below.
+\color{black}
+
+To translate a sequent proof to a proof net requires to find a target for each jump from a $\bot$-formula.
+%
+The inference rule for $\bot$ introduces it into a sequent $\Gamma$; in the corresponding proof net, any occurrence of $\1$ in $\Gamma$ may serve as the target of the jump.
+
+%The translation from sequent proofs to proof nets is as follows.
+
+%In the sequent calculus, the rule for $\bot$ introduces a $\bot$-formula into a sequent $\Gamma$, rather than an occurrence of $\1$, as in proof nets.
+%
+%The interpretation of a proof as a proof net may attach the corresponding link to an arbitrary $\1$ in $\Gamma$.
 
@@
 \noindent
-Proof nets are canonical representations of proofs in the absence of units: they factor out the permutations among tensor- and par-inferences, which are the last three permutations in Figure~\ref{fig:permutations}.
+Proof nets are a canonical representation of proofs in the absence of the units: they factor out the permutations among tensor- and par-inferences, which are the last three permutations in Figure~\ref{fig:permutations}.
 %
@@
 %
-The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively;
+The units $1$ and $\bot$ are represented by a circle~($\circ$) and a disc~($\bullet$) respectively;
 %
 formulae related by a tensor will be connected by edges; 
-and
-formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula \color{red}(or for illustrative purposes)\color{black}.
+formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula \color{red}(and also for illustrative purposes)\color{black}.
 %
@@
 
+\section{Encoding constraint logic}
+\label{sec:encoding}
+
+\aftersection
+%
+\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reduction.
+%
+A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint}---a natural number that may be taken to be always $2$---on each vertex.
+A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
+A rewrite step consists of the reversal of a single edge in a configuration:
+rewrite steps must preserve the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
+
+\color{red}
+Figure~\ref{fig:NCL example} shows an example rewrite sequence in a constraint graph.
+%
+The central node has inflow constraint 2, the thick blue edge has weight 2, and the thinner red edges have weight 1.
+\color{black}
+
+The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
+%
+A constraint graph may be encoded as a sequent, and a configuration as a proof net.
+%
+It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
+
+\begin{definition} 
+A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting the two vertices $v(e)=\{v_1,v_2\}\subseteq V$.
+
+\smallskip
+
+A \emph{(partial) configuration} for a constraint graph is a (partial) function $\gamma\colon E\to V$ such that
+\begin{itemize}
+	\item
+for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
+	\item
+for every vertex $v$, the total weight of its incoming edges is at least its inflow constraint, 
+%$\sum\{\kern1pt w(e)\kern1pt|\kern1pt\gamma(e)=v\kern1pt\}\geq c(v)$.
+$\sum\{w(e)\mid\gamma(e)=v\}\geq c(v)$.
+\end{itemize}
+
+\smallskip
+A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for $G$ that differ in value (or definedness) on exactly one edge; this edge is then called \emph{mobile} in $\gamma$ and $\delta$.
+%
+The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
+%
+\end{definition}
+
+\begin{proposition}
+\label{prop:partial simulates total reconfiguration}
+For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
+\end{proposition}
+
+\begin{proof}
+By the following two observations: firstly, 
+%
+if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
+%
+if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
+%
+\end{proof}
+
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
+%
+%By the above proposition, \capsabbrev{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
+
+\begin{figure}\color{red}
+$
+~
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,->-] (3,0) -- (5,2);
+	\draw[ncl1,->-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\hfill\perm*\,
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,->-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\hfill\perm*\,
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,-<-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\hfill\perm*\,
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,-<-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,-<-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+~
+$
+
+\smallskip
+\caption{A series of reconfiguration steps in a constraint graph}
+\label{fig:NCL example}
+\end{figure}
+
+\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
+\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
+\end{theorem}
+
+%By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
+%
+%\begin{proposition}
+%Partial \capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
+%%\capsabbrev{pncg}-reconfiguration is \capsabbrev{pspace}-complete.
+%\end{proposition}
+
+We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\begin{figure*}
+\color{red}
+\[
+\vc{\scalebox{0.36}{\BIGexample 3}}
+\quad\perm\quad
+\vc{\scalebox{0.36}{\BIGexample 2}}
+\quad\perm\quad
+\vc{\scalebox{0.36}{\BIGexample 1}}
+\]
+\caption{Rewiring three edge-gadgets connected to a single vertex-gadget}
+\label{fig:encoding example}
+\end{figure*}
+
+\subsection*{The encoding}
+
+\aftersubsection
+The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
+%
+The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
+%
+Below left is a weight element, below right a constraint element.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {$i'$}; 
+	\node[big_] (B) at (2,0) {$j'$};
+	\node[big_] (C) at (4,0) {$k'$};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big1] (1) at (0,0) {$m'$}; 
+	\node[big1] (2) at (3,0) {$n'$};
+	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
+	\draw (1,0)--(2,0);
+\end{tikzpicture}
+\]
+For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same -- this way, a priori any weight element may connect to any constraint element.
+%
+The value of $m$ (and thus $n$) will differ for each vertex.
+%
+The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
+\[
+	\connectingElements 1 \qquad \connectingElements 2
+\]
+To ensure that no other connections can be made, values are chosen such that $m\equiv1$ and $n\equiv2 \pmod 3$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2\pmod 3$.
+
+In a constraint graph, the sum of all weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
+%
+An encoding will therefore have weight elements not connected to constraint elements.
+%
+These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as follows.
+%
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {}; 
+	\node[big_] (B) at (2,0) {};
+	\node[big_] (C) at (4,0) {};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+	\node[big1] (1) at (7.5,0) {};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend left=30] (A) to (1);
+		\draw[bend right=30] (B) to (1);
+		\draw (C) to (1);
+	\end{scope}
+\end{tikzpicture}
+\]
+%
+An edge will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements plus a single \emph{indicator} vertex.
+%
+Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
+%
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {$i'$}; 
+	\node[big_] (B) at (2,0) {$j'$};
+	\node[big_] (C) at (4,0) {$k'$};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+	\node[big_] (D) at (0,4) {$i'$}; 
+	\node[big_] (E) at (2,4) {$j'$};
+	\node[big_] (F) at (4,4) {$k'$};
+	\draw[rounded corners] (-1,3) rectangle (5,5);
+	\draw (2,1)--(2,1.5) (2,2.5)--(2,3);
+	\draw[dotted] (2,1.5)--(2,2.5);
+	\draw (2,-1)--(2,-2) node[bullet] {};
+	\path (0,-2.5)--(1,-2.5);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big1] (1) at (0,0) {$m'$}; 
+	\node[big1] (2) at (3,0) {$n'$};
+	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
+	\draw (1,0)--(2,0);
+	\node[big1] (3) at (0,4) {$m'$};
+	\node[big1] (4) at (3,4) {$n'$};
+	\draw[rounded corners] (-1,3) rectangle (1,5) (2,3) rectangle (4,5);
+	\draw (1,4)--(2,4);
+	\draw[dotted] (1.5,1.5)--(1.5,2.6);
+	\node[circ] at (1.5,-2) {};
+	\draw[rounded corners] (-1.5,-2.5) rectangle (4.5,5.5);
+\end{tikzpicture}
+\]
+%
+It would be natural to encode an edge of weight $n$ by an edge-gadget with $n$ weight elements.
+%
+However, there is a minor issue that prevents this straightforward approach.
+%
+Although one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
+%
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big_] (A) at (-1,0) {}; 
+	\draw (.75,0) node[big_] (B1) {} -- (2.25,0) node[big_] (B2) {};
+	\node[big_] (C) at (4,0) {};
+	\draw[rounded corners] (-2,-1) rectangle (5,1);
+	\draw (7,0) node[big_] (D1) {} -- (8.5,0) node[big_] (D2) {}; 
+	\node[big_] (E) at (10.25,0) {};
+	\node[big_] (F) at (12,0) {};
+	\draw[rounded corners] (6,-1) rectangle (13,1);
+	\node[big1] (1) at (1,4) {};
+	\node[big1] (2) at (4,4) {}; 
+	\node[big1] (3) at (7,4) {};
+	\node[big1] (4) at (10,4) {};
+	\draw[rounded corners] (3,3) rectangle (5,5) (6,3) rectangle (8,5);
+	\draw (5,4)--(6,4);
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=25] (A)  to (1);
+		\draw[bend right=15] (B1) to (1);
+		\draw[bend right=25] (B2) to (2);
+		\draw[bend right=15] (C)  to (2);
+		\draw[bend left=15] (D1) to (3);
+		\draw[bend right=15] (D2) to (4);
+		\draw[bend left=20] (E)  to (4);
+		\draw[bend left=20] (F)  to (4);
+	\end{scope}
+\end{tikzpicture}
+\]
+%
+In such an inappropriate linking, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the linking would violate the switching condition.
+%
+That means the weight elements must belong to different edges.
+
+As the linkings above illustrate, it may occur that one subformula of a weight element $A\parr B\parr C$ fills one half of a constraint element.
+%
+Consequently, a weight element can fill three halves, but only of different constraint elements.
+%
+The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
+%
+To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
+%
+To fill $3n$ constraint elements inappropriately therefore requires $n+1$ edges.
+%
+It thus suffices to multiply the number of constraint elements by three times the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times3\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
+
+\color{red}
+The complete encoding of a constraint graph $G$ will be a sequent $\Gamma=\itn G$ consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
+%
+A configuration for $G$ will be encoded as a proof net for $\Gamma$, and conversely each proof net for $\Gamma$ may be interpreted as a (partial) configuration for $G$.
+
+Figure~\ref{fig:encoding example} displays an encoding of the constraint graph of Figure~\ref{fig:NCL example}, where two edge-gadgets of weight 1, and one of weight 2, connect to a central vertex-gadget with inflow constraint 2.
+%
+The jumps from the three indicator vertices, at the bottom, indicate which vertex an edge is directed at.
+%
+Indicator jumps can only be rewired (between vertices) when the edge-gadget is connected only to weight absorbers---in the first net of Figure~\ref{fig:encoding example}, the two leftmost edges are mobile, and in the third, the rightmost edge is mobile.
+%
+All three nets in Figure~\ref{fig:encoding example} then correspond to the third graph in Figure~\ref{fig:NCL example}, but the first net allows rewiring to the second and first graph, and the third net allows rewiring to the fourth graph.
+%
+\color{black}
+
+%
+For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+\[
+	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
+\]
+
+\begin{definition}
+\label{def:graph encoding}
+The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows.
+%
+Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
+
+\noindent
+The encoding of a vertex $v_k$ is the formula
+\[
+	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\parr\1
+\]
+where each \emph{constraint element} $C_n(k)$ is the formula
+\[
+	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
+\]
+
+\noindent
+The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
+\[
+	\itn{e} = \bigtn\big(W_n(i,j)^{3m\times w(e)}\big)\tn\bot
+\]
+where each \emph{weight element} $W_n(i,j)$ is the formula
+\[
+	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
+\]
+
+\noindent
+The encoding of the graph $G$ is the sequent
+\[
+	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
+\]
+where $p=3m\times(|w|-|c|)\times(3n+4)$.
+
+\end{definition}
+
+In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{weight absorbers}.
+%
+In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
+%
+This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.
+
+A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
+%
+Firstly we will define a standard way of linking a weight element to a constraint element.
+
+\begin{definition}
+\label{def:standard linkings}
+For $W=W_n(i,j)=A\parr B\parr C$ a weight element,
+\begin{enumerate}
+	\item
+for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
+	\item
+for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
+	\item
+the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
+\end{enumerate}
+\end{definition}
+
+The standard linkings defined in the \color{red} second \color{black} and third case of the above definition are illustrated below.
+
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (1) at (-.25,0) {};
+	\node[big1] (2) at (1,0) {};
+	\node[big1] (3) at (2.5,0) {};
+	\node[big1] (4) at (5.5,0) {};
+	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
+	\draw (3.5,0)--(4.5,0);
+	%
+	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
+	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
+	\node[big_] (C) at (5.5,4) {};
+	\draw[rounded corners] (-1,3) rectangle (6.5,5);
+	%
+	\begin{scope}[thepink,->]
+		\draw[bend right=5] (a) to (1);
+		\draw[bend right=10] (b) to (1);
+		\draw[big>,bend left=25] (A) to (2);
+		\draw[big>,bend left=20] (B) to (3);
+		\draw[big>,bend left=15] (C) to (4);
+	\end{scope}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (1) at (.75,0) {};
+	\node[big1] (2) at (2,0) {};
+	\node[big1] (3) at (3.5,0) {};
+	\node[big1] (4) at (5,0) {};
+	%
+	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
+	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
+	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
+	\draw[rounded corners] (-.5,3) rectangle (7,5);
+	\path (0,-1) -- (1,-1);
+	%
+	\begin{scope}[thepink,->]
+		\draw[bend right=5] (a) to (1);
+		\draw[bend right=10] (b) to (1);
+		\draw[bend right=15] (c) to (1);
+		\draw[big>,bend left=25] (A) to (2);
+		\draw[big>,bend left=20] (B) to (3);
+		\draw[big>,bend left=15] (C) to (4);
+	\end{scope}
+\end{tikzpicture}
+\]
+
+\begin{proposition}
+\label{prop:element linkings}
+The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
+\end{proposition}
+
+The encoding of a configuration is then as follows.
+
+\begin{definition}
+\label{def:configuration encoding}
+The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
+%
+Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
+%
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
+\end{definition}
+
+\begin{proposition}
+If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
+\end{proposition}
+
+\begin{proof}
+Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
+%
+The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
+%
+The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the weight absorbers within scopes of weight elements inside $\itn e$.
+%
+Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
+%
+After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
+\end{proof}
+
+%------------------------------------------------------------
+
+\beforesection
+
 \section{Rewiring proof nets}
@@
 
-The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
+%\noindent
+The \emph{ports} of a sub-sequent $\Gamma'$ or subnet $(\Gamma',\links')$ are the root vertices of $\Gamma'$.
+%
+%The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
 %
@@
 \color{red}
-In the graph of a proof net, the scope of a par can be made explicit as a \emph{box}, as illustrated below left.
+In the graph of a proof net, a chosen scope of a par can be made explicit as a \emph{box}, as illustrated below left.
 %
@@
 %
-To make this precise, we will consider the action of \emph{closing} a box, which will mean we consider it as a single vertex in the graph.
+To make this precise, we will consider the action of \emph{closing} a box, which means it is regarded as a single vertex in the graph, as illustrated below right.
 
@@
 \label{prop:empire propagation}
-The empire $\emp v$ is determined by propagation from $v$: 1) through links;\\ \color{red} 2) up towards subformulae;\\ 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$;\\ 4) into a par if all its subformulae are in $\emp v-\{v\}$.%;\\ 5) except never into a par or tensor if $v$ is a subformula.
+The empire $\emp v$ is determined by propagation from $v$: 1) through links; \color{red} 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.%;\\ 5) except never into a par or tensor if $v$ is a subformula.
 \end{proposition}
@@
 
-\section{Encoding constraint logic}
-\label{sec:encoding}
-
-\aftersection
-%
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reduction.
-%
-A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint}---a natural number that may be taken to be always $2$---on each vertex.
-A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
-A rewrite step consists of the reversal of a single edge in a configuration:
-rewrite steps must preserve the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
-
-\color{red}
-Figure~\ref{fig:NCL example} shows an example rewrite sequence in a constraint graph.
-%
-The central node has inflow constraint 2, the thick blue (dark grey) edge has weight 2, and the thinner red (light grey) edges have weight 1.
-\color{black}
-
-\begin{figure}\color{red}
-$
-\quad
-\vc{\begin{tikzpicture}[x=3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,->-] (3,0) -- (5,2);
-	\draw[ncl1,->-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\,\perm*\hfill
-\vc{\begin{tikzpicture}[x=3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,->-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\,\perm*\hfill
-\vc{\begin{tikzpicture}[x=3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,-<-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\,\perm*\hfill
-\vc{\begin{tikzpicture}[x=3mm,y=3mm]
-	\draw[ncl2,-<-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,-<-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\quad
-$
-
-\smallskip
-\caption{A series of reconfiguration steps in a constraint graph}
-\label{fig:NCL example}
-\end{figure}
-
-The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-%
-A constraint graph may be encoded as a sequent, and a configuration as a proof net.
-%
-It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
-
-\begin{definition} 
-A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting vertices $v(e)=\{v_1,v_2\}\subseteq V$.
-
-\smallskip
-
-A \emph{(partial) configuration} for a constraint graph is a (partial) function $\gamma\colon E\to V$ such that
-\begin{itemize}
-	\item
-for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
-	\item
-for every vertex $v$, the total weight of its incoming edges is at least its inflow constraint, 
-%$\sum\{\kern1pt w(e)\kern1pt|\kern1pt\gamma(e)=v\kern1pt\}\geq c(v)$.
-$\sum\{w(e)\mid\gamma(e)=v\}\geq c(v)$.
-\end{itemize}
-
-\smallskip
-A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for $G$ that differ in value (or definedness) on exactly one edge; this edge is then called \emph{mobile} in $\gamma$ and $\delta$.
-%
-The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
-%
-\end{definition}
-
-\begin{proposition}
-\label{prop:partial simulates total reconfiguration}
-For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
-\end{proposition}
-
-\begin{proof}
-By the following two observations: firstly, 
-%
-if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
-%
-if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
-%
-\end{proof}
-
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
-%
-%By the above proposition, \capsabbrev{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
-
-\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
-\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
-\end{theorem}
-
-%By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
-%
-%\begin{proposition}
-%Partial \capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
-%%\capsabbrev{pncg}-reconfiguration is \capsabbrev{pspace}-complete.
-%\end{proposition}
-
-We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{The encoding}
-
-\aftersubsection
-The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
-%
-The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
-%
-Below left is a weight element, below right a constraint element.
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {$i'$}; 
-	\node[big_] (B) at (2,0) {$j'$};
-	\node[big_] (C) at (4,0) {$k'$};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big1] (1) at (0,0) {$m'$}; 
-	\node[big1] (2) at (3,0) {$n'$};
-	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
-	\draw (1,0)--(2,0);
-\end{tikzpicture}
-\]
-For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same -- this way, a priori any weight element may connect to any constraint element.
-%
-The value of $m$ (and thus $n$) will differ for each vertex.
-%
-The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
-\[
-	\connectingElements 1 \qquad \connectingElements 2
-\]
-To ensure that no other connections can be made, values are chosen such that $m\equiv1$ and $n\equiv2$ $(\bmod3)$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2$ $(\bmod3)$.
-
-In a constraint graph, the sum of weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
-%
-An encoding will therefore have weight elements not connected to constraint elements.
-%
-These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as follows.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {}; 
-	\node[big_] (B) at (2,0) {};
-	\node[big_] (C) at (4,0) {};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-	\node[big1] (1) at (7.5,0) {};
-	\begin{scope}[thepink,->,big>]
-		\draw[bend left=30] (A) to (1);
-		\draw[bend right=30] (B) to (1);
-		\draw (C) to (1);
-	\end{scope}
-\end{tikzpicture}
-\]
-%
-An edge will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements plus a single \emph{indicator} vertex.
-%
-Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {$i'$}; 
-	\node[big_] (B) at (2,0) {$j'$};
-	\node[big_] (C) at (4,0) {$k'$};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-	\node[big_] (D) at (0,4) {$i'$}; 
-	\node[big_] (E) at (2,4) {$j'$};
-	\node[big_] (F) at (4,4) {$k'$};
-	\draw[rounded corners] (-1,3) rectangle (5,5);
-	\draw (2,1)--(2,1.5) (2,2.5)--(2,3);
-	\draw[dotted] (2,1.5)--(2,2.5);
-	\draw (2,-1)--(2,-2) node[bullet] {};
-	\path (0,-2.5)--(1,-2.5);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big1] (1) at (0,0) {$m'$}; 
-	\node[big1] (2) at (3,0) {$n'$};
-	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
-	\draw (1,0)--(2,0);
-	\node[big1] (3) at (0,4) {$m'$};
-	\node[big1] (4) at (3,4) {$n'$};
-	\draw[rounded corners] (-1,3) rectangle (1,5) (2,3) rectangle (4,5);
-	\draw (1,4)--(2,4);
-	\draw[dotted] (1.5,1.5)--(1.5,2.6);
-	\node[circ] at (1.5,-2) {};
-	\draw[rounded corners] (-1.5,-2.5) rectangle (4.5,5.5);
-\end{tikzpicture}
-\]
-%
-It would be natural to encode an edge of weight $n$ by an edge-gadget with $n$ weight elements.
-%
-However, there is a minor issue that prevents this straightforward approach.
-%
-Although one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-1,0) {}; 
-	\draw (.75,0) node[big_] (B1) {} -- (2.25,0) node[big_] (B2) {};
-	\node[big_] (C) at (4,0) {};
-	\draw[rounded corners] (-2,-1) rectangle (5,1);
-	\draw (7,0) node[big_] (D1) {} -- (8.5,0) node[big_] (D2) {}; 
-	\node[big_] (E) at (10.25,0) {};
-	\node[big_] (F) at (12,0) {};
-	\draw[rounded corners] (6,-1) rectangle (13,1);
-	\node[big1] (1) at (1,4) {};
-	\node[big1] (2) at (4,4) {}; 
-	\node[big1] (3) at (7,4) {};
-	\node[big1] (4) at (10,4) {};
-	\draw[rounded corners] (3,3) rectangle (5,5) (6,3) rectangle (8,5);
-	\draw (5,4)--(6,4);
-	\begin{scope}[thepink,->,big>]
-		\draw[bend right=25] (A)  to (1);
-		\draw[bend right=15] (B1) to (1);
-		\draw[bend right=25] (B2) to (2);
-		\draw[bend right=15] (C)  to (2);
-		\draw[bend left=15] (D1) to (3);
-		\draw[bend right=15] (D2) to (4);
-		\draw[bend left=20] (E)  to (4);
-		\draw[bend left=20] (F)  to (4);
-	\end{scope}
-\end{tikzpicture}
-\]
-%
-In such an inappropriate linking, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the linking would violate the switching condition.
-%
-That means the weight elements must belong to different edges.
-
-As the linkings above illustrate, it may occur that one subformula of a weight element $A\parr B\parr C$ fills one half of a constraint element.
-%
-Consequently, a weight element can fill three halves, but only of different constraint elements.
-%
-The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
-%
-To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
-%
-To fill $3n$ constraint elements inappropriately therefore requires $n+1$ edges.
-%
-It thus suffices to multiply the number of constraint elements by three times the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times3\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
-
-The complete encoding of a constraint graph will be a sequent consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
-%
-For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
-\[
-	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
-\]
-
-\begin{definition}
-\label{def:graph encoding}
-The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows.
-%
-Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
-
-\noindent
-The encoding of a vertex $v_k$ is the formula
-\[
-	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\parr\1
-\]
-where each \emph{constraint element} $C_n(k)$ is the formula
-\[
-	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
-\]
-
-\noindent
-The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
-\[
-	\itn{e} = \bigtn\big(W_n(i,j)^{3m\times w(e)}\big)\tn\bot
-\]
-where each \emph{weight element} $W_n(i,j)$ is the formula
-\[
-	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
-\]
-
-\noindent
-The encoding of the graph $G$ is the sequent
-\[
-	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
-\]
-where $p=3m\times(|w|-|c|)\times(3n+4)$.
-
-\end{definition}
-
-In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{weight absorbers}.
-%
-In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
-%
-This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.
-
-A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
-%
-Firstly we will define a standard way of linking a weight element to a constraint element.
-
-\begin{definition}
-\label{def:standard linkings}
-For $W=W_n(i,j)=A\parr B\parr C$ a weight element,
-\begin{enumerate}
-	\item
-for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
-	\item
-for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
-	\item
-the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
-\end{enumerate}
-\end{definition}
-
-The standard linkings defined in the \color{red} second \color{black} and third case of the above definition are illustrated below.
-
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (1) at (-.25,0) {};
-	\node[big1] (2) at (1,0) {};
-	\node[big1] (3) at (2.5,0) {};
-	\node[big1] (4) at (5.5,0) {};
-	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
-	\draw (3.5,0)--(4.5,0);
-	%
-	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
-	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
-	\node[big_] (C) at (5.5,4) {};
-	\draw[rounded corners] (-1,3) rectangle (6.5,5);
-	%
-	\begin{scope}[thepink,->]
-		\draw[bend right=5] (a) to (1);
-		\draw[bend right=10] (b) to (1);
-		\draw[big>,bend left=25] (A) to (2);
-		\draw[big>,bend left=20] (B) to (3);
-		\draw[big>,bend left=15] (C) to (4);
-	\end{scope}
-\end{tikzpicture}
-\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (1) at (.75,0) {};
-	\node[big1] (2) at (2,0) {};
-	\node[big1] (3) at (3.5,0) {};
-	\node[big1] (4) at (5,0) {};
-	%
-	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
-	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
-	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
-	\draw[rounded corners] (-.5,3) rectangle (7,5);
-	\path (0,-1) -- (1,-1);
-	%
-	\begin{scope}[thepink,->]
-		\draw[bend right=5] (a) to (1);
-		\draw[bend right=10] (b) to (1);
-		\draw[bend right=15] (c) to (1);
-		\draw[big>,bend left=25] (A) to (2);
-		\draw[big>,bend left=20] (B) to (3);
-		\draw[big>,bend left=15] (C) to (4);
-	\end{scope}
-\end{tikzpicture}
-\]
-
-\begin{proposition}
-\label{prop:element linkings}
-The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
-\end{proposition}
-
-The encoding of a configuration is then as follows.
-
-\begin{definition}
-\label{def:configuration encoding}
-The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
-%
-Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
-%
-Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
-\end{definition}
-
-\begin{proposition}
-If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
-\end{proposition}
-
-\begin{proof}
-Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
-%
-The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
-%
-The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the weight absorbers within scopes of weight elements inside $\itn e$.
-%
-Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
-%
-After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
-\end{proof}
-
-%------------------------------------------------------------
-
-\beforesection
-
 \section{Correctness of the encoding}
@@
 %
-To each proof net $\links$ for an encoded constraint graph $\itn G$ we will associate a partial configuration $\gamma=\coitn\links$, such that 1) a rewiring step $\links\perm*\links$ corresponds to a reconfiguration path $\coitn\links\perm\coitn{\links'}$, and 2) it is a retraction of the encoding of configurations, $\coitn{\itn\gamma}=\gamma$.
+To each proof net $\links$ for an encoded constraint graph $\itn G$ we will associate a partial configuration $\gamma=\coitn\links$, such that 1) a rewiring step $\links\perm*\links$ corresponds to a reconfiguration path $\coitn\links\perm\coitn{\links'}$, and 2) the function $\coitn-$ is a retraction of the encoding of configurations, $\coitn{\itn\gamma}=\gamma$.
 
@@
 
+\acks
+
+We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees.
+
 %===========================

### 2014-04-18 main/LICS.tex
minor edits, copyright updated

@@
 
-\let\beforesection=\medskip
-\let\aftersection=\noindent
-\let\aftersubsection=\noindent
+\let\beforesection=\relax%\medskip
+\let\aftersection=\relax%\noindent
+\let\aftersubsection=\relax%\noindent
 
@@
 
+\exclusivelicense
 \conferenceinfo{CSL-LICS 2014}{July 14--18, 2014, Vienna, Austria} 
@@
 \copyrightdata{978-1-4503-2886-9}
-\doi{nnnnnnn.nnnnnnn}
+\doi{2603088.2603126}
+
+% FOR PERSONAL USE, ADD:
+
+%"© [Owner] [Year].
+This is the author's version of the work.
+It is posted here for your personal use.
+Not for redistribution.
+The definitive version was published in {Source Publication}, http://dx.doi.org/10.1145/{number}."
 
@@
 \color{red}
-if a notion of proof net existed where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
+if a notion of proof net were to exist where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
 \color{black}
@@
 
+\noindent
+%
 We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
@@
 \label{prop:element linkings}
-The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
+%The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
+Standard linkings are proof nets.
 \end{proposition}

### 2014-04-18 main/LICS.tex
re-arranging and minor edits

@@
 \color{red}
-The complete encoding of a constraint graph $G$ will be a sequent $\Gamma=\itn G$ consisting of: 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
+The complete encoding of a constraint graph $G$ will be a sequent $\Gamma$ consisting of:
+% 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
+\begin{enumerate}
+ 	\item
+all vertex-gadgets, combined in a single formula via tensors, 
+	\item
+all edge-gadgets as individual formulae, and
+	\item
+a sufficient number of weight absorbers ($\1$-formulae).
+\end{enumerate}
 %
@@
 
-Figure~\ref{fig:encoding example} displays an encoding of the constraint graph of Figure~\ref{fig:NCL example}, where two edge-gadgets of weight 1, and one of weight 2, connect to a central vertex-gadget with inflow constraint 2.
+Figure~\ref{fig:encoding example} displays an encoding of two edges of weight 1, and one of weight 2, connecting to a central vertex with inflow constraint 2, as in the example reconfiguration sequence in Figure~\ref{fig:NCL example}.
 %
@@
 %
-Indicator jumps can only be rewired (between vertices) when the edge-gadget is connected only to weight absorbers---in the first net of Figure~\ref{fig:encoding example}, the two leftmost edges are mobile, and in the third, the rightmost edge is mobile.
-%
-All three nets in Figure~\ref{fig:encoding example} then correspond to the third graph in Figure~\ref{fig:NCL example}, but the first net allows rewiring to the second and first graph, and the third net allows rewiring to the fourth graph.
-%
+Indicator jumps can only be rewired between vertices when the edge-gadget is connected only to weight absorbers---in the first net of Figure~\ref{fig:encoding example}, the two leftmost edges are mobile, and in the third, the rightmost edge is mobile.
+%
+All three nets in Figure~\ref{fig:encoding example} then correspond to the third graph in Figure~\ref{fig:NCL example}, but the first net allows rewiring according to the second and first graph, whereas the third net allows rewiring according to the fourth graph.
+
+The encoding will be made formal in Section~\ref{sec:correctness}; first we will establish some basic results for rewiring on proof nets.
+
 \color{black}
-
-%
-For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
-\[
-	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
-\]
-
-\begin{definition}
-\label{def:graph encoding}
-The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows.
-%
-Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
-
-\noindent
-The encoding of a vertex $v_k$ is the formula
-\[
-	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\parr\1
-\]
-where each \emph{constraint element} $C_n(k)$ is the formula
-\[
-	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
-\]
-
-\noindent
-The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
-\[
-	\itn{e} = \bigtn\big(W_n(i,j)^{3m\times w(e)}\big)\tn\bot
-\]
-where each \emph{weight element} $W_n(i,j)$ is the formula
-\[
-	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
-\]
-
-\noindent
-The encoding of the graph $G$ is the sequent
-\[
-	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
-\]
-where $p=3m\times(|w|-|c|)\times(3n+4)$.
-
-\end{definition}
-
-In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{weight absorbers}.
-%
-In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
-%
-This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.
-
-A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
-%
-Firstly we will define a standard way of linking a weight element to a constraint element.
-
-\begin{definition}
-\label{def:standard linkings}
-For $W=W_n(i,j)=A\parr B\parr C$ a weight element,
-\begin{enumerate}
-	\item
-for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
-	\item
-for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
-	\item
-the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
-\end{enumerate}
-\end{definition}
-
-The standard linkings defined in the \color{red} second \color{black} and third case of the above definition are illustrated below.
-
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (1) at (-.25,0) {};
-	\node[big1] (2) at (1,0) {};
-	\node[big1] (3) at (2.5,0) {};
-	\node[big1] (4) at (5.5,0) {};
-	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
-	\draw (3.5,0)--(4.5,0);
-	%
-	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
-	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
-	\node[big_] (C) at (5.5,4) {};
-	\draw[rounded corners] (-1,3) rectangle (6.5,5);
-	%
-	\begin{scope}[thepink,->]
-		\draw[bend right=5] (a) to (1);
-		\draw[bend right=10] (b) to (1);
-		\draw[big>,bend left=25] (A) to (2);
-		\draw[big>,bend left=20] (B) to (3);
-		\draw[big>,bend left=15] (C) to (4);
-	\end{scope}
-\end{tikzpicture}
-\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (1) at (.75,0) {};
-	\node[big1] (2) at (2,0) {};
-	\node[big1] (3) at (3.5,0) {};
-	\node[big1] (4) at (5,0) {};
-	%
-	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
-	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
-	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
-	\draw[rounded corners] (-.5,3) rectangle (7,5);
-	\path (0,-1) -- (1,-1);
-	%
-	\begin{scope}[thepink,->]
-		\draw[bend right=5] (a) to (1);
-		\draw[bend right=10] (b) to (1);
-		\draw[bend right=15] (c) to (1);
-		\draw[big>,bend left=25] (A) to (2);
-		\draw[big>,bend left=20] (B) to (3);
-		\draw[big>,bend left=15] (C) to (4);
-	\end{scope}
-\end{tikzpicture}
-\]
-
-\begin{proposition}
-\label{prop:element linkings}
-%The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
-Standard linkings are proof nets.
-\end{proposition}
-
-The encoding of a configuration is then as follows.
-
-\begin{definition}
-\label{def:configuration encoding}
-The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
-%
-Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
-%
-Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
-\end{definition}
-
-\begin{proposition}
-If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
-\end{proposition}
-
-\begin{proof}
-Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable scope for each $\parr$. 
-%
-The scope of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
-%
-The scope of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the weight absorbers within scopes of weight elements inside $\itn e$.
-%
-Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
-%
-After contracting the scope of each $W$, each edge-gadget in the scope of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
-\end{proof}
 
@@
 Furthermore, we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence.
-
-%i.e.\ that of sequents of formulae constructed over $\1$, $\bot$, and $\tn$.
-
-\begin{figure*}
-\[
-	\vc{\doubleExchange uvxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyx}
-\]
-\caption{Double exchange of links (Lemma~\ref{lem:double exchange})}
-\label{fig:double exchange}
-\end{figure*}
 
@@
 \begin{definition}
-A \emph{subnet} $(\Gamma',\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Gamma'\leq\Gamma$ and $\links'$ is $(\links|_{\Gamma'})$, the restriction of $\links$ to $\Gamma'$.
+A \emph{subnet} $(\Delta,\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Delta\leq\Gamma$ and $\links'$ is the restriction of $\links$ to the names in $\Delta$.
 \end{definition}
@@
 %\noindent
+\color{red}
 The \emph{ports} of a sub-sequent $\Gamma'$ or subnet $(\Gamma',\links')$ are the root vertices of $\Gamma'$.
@@
 %
-A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
-
-The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
-%
-\color{red}
-In the graph of a proof net, a chosen scope of a par can be made explicit as a \emph{box}, as illustrated below left.
+For a vertex $v$ naming a par, tensor, or bottom, the subnets of which it is a port correspond to the possible subproofs of the rule introducing $v$ in a sequentialisation (the subproof of a $\1$-subformula must always be empty).
+%
+%
+%A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
+%
+%The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
+
+In the graph of a proof net, a chosen subnet for a par can be made explicit as a \emph{box}, as illustrated below left.
 %
@@
 To make this precise, we will consider the action of \emph{closing} a box, which means it is regarded as a single vertex in the graph, as illustrated below right.
-
+%
+%
+%
 \[
@@
 \]
-
+%
+%
 \begin{definition}
@@
 %
-If for some switching of $\links$ the path $\path vw$ passes through $a$, then in $\links'$ there is no path $\path av$ (and two paths $\path aw$) for that switching, so $\links'$ is not a net.
+If for some switching of $\links$ the path $\path vw$ passes through $a$, then in $\links'$ there is no path $\path av$ (and two paths $\path aw$) for that switching, so that $\links'$ is not a net.
 %
 \end{proof}
+
+\color{red}
+Rewiring a jump from $\named v\bot$ preserves the empire of $v$, up to that rewiring, by the first lemma below.
+%
+By the second lemma, the empire of any other vertex $w$ grows or shrinks, or neither, but not both.
+\color{black}
 
@@
 \begin{proof}
-By Lemma~\ref{lem:rewiring within empire} the empires $\emp v$ and $\emp*v$ contain the same $\1$-subformulae, since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$.
-%
-That $\emp v$ and $\emp*v$ must share also any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is.
+Since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$, by Lemma~\ref{lem:rewiring within empire} the empires $\emp v$ and $\emp*v$ contain the same $\1$-subformulae.
+%
+That they also share any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is (unless $v$ names $A$, but in this case $A$ is included in both $\emp v$ and $\emp*v$).
 %
@@
 \end{proof}
+
+\begin{figure*}
+\[
+	\vc{\doubleExchange uvxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxy}
+	\quad\perm*\quad
+	\vc{\doubleExchange uyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyxu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vyyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyu}
+	\quad\perm*\quad
+	\vc{\doubleExchange vuyx}
+\]
+\caption{Double exchange of links (Lemma~\ref{lem:double exchange})}
+\label{fig:double exchange}
+\end{figure*}
 
@@
 \section{Correctness of the encoding}
+\label{sec:correctness}
 
@@
 This will be separated into two parts: completeness ($\Rightarrow$) and soundness ($\Leftarrow$) .
+
+%
+For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+\[
+	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
+\]
+
+\begin{definition}
+\label{def:graph encoding}
+The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows.
+%
+Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
+
+\noindent
+The encoding of a vertex $v_k$ is the formula
+\[
+	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\parr\1
+\]
+where each \emph{constraint element} $C_n(k)$ is the formula
+\[
+	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
+\]
+
+\noindent
+The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
+\[
+	\itn{e} = \bigtn\big(W_n(i,j)^{3m\times w(e)}\big)\tn\bot
+\]
+where each \emph{weight element} $W_n(i,j)$ is the formula
+\[
+	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
+\]
+
+\noindent
+The encoding of the graph $G$ is the sequent
+\[
+	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
+\]
+where $p=3m\times(|w|-|c|)\times(3n+4)$.
+
+\end{definition}
+
+In the above definition, the final $\1$-subformula of a vertex-gadget $\itn{v_k}$ is its \emph{indicator target}; the final $\bot$-subformula of an edge-gadget $\itn{e}$ is its \emph{indicator}; and in the completed encoding $\itn G$ the $p$ instances of $\1$ are the \emph{weight absorbers}.
+%
+In a constraint graph $G$, a vertex $v$ and an edge $e$ will be called \emph{appropriate} (for each other) if $v\in v(e)$, and \emph{inappropriate} otherwise.
+%
+This notion is extended to vertex-gadgets $\itn v$ and edge-gadgets $\itn e$ in $\itn G$, and their respective constraint elements and weight elements.
+
+A configuration $\gamma$ for a constraint graph $G$ will be encoded as a proof net for the sequent $\itn G$.
+%
+Firstly we will define a standard way of linking a weight element to a constraint element.
+
+\begin{definition}
+\label{def:standard linkings}
+For $W=W_n(i,j)=A\parr B\parr C$ a weight element,
+\begin{enumerate}
+	\item
+for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
+	\item
+for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
+	\item
+the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
+\end{enumerate}
+\end{definition}
+
+The standard linkings defined in the \color{red} second \color{black} and third case of the above definition are illustrated below.
+
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (1) at (-.25,0) {};
+	\node[big1] (2) at (1,0) {};
+	\node[big1] (3) at (2.5,0) {};
+	\node[big1] (4) at (5.5,0) {};
+	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
+	\draw (3.5,0)--(4.5,0);
+	%
+	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
+	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
+	\node[big_] (C) at (5.5,4) {};
+	\draw[rounded corners] (-1,3) rectangle (6.5,5);
+	%
+	\begin{scope}[thepink,->]
+		\draw[bend right=5] (a) to (1);
+		\draw[bend right=10] (b) to (1);
+		\draw[big>,bend left=25] (A) to (2);
+		\draw[big>,bend left=20] (B) to (3);
+		\draw[big>,bend left=15] (C) to (4);
+	\end{scope}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[circ] (1) at (.75,0) {};
+	\node[big1] (2) at (2,0) {};
+	\node[big1] (3) at (3.5,0) {};
+	\node[big1] (4) at (5,0) {};
+	%
+	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
+	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
+	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
+	\draw[rounded corners] (-.5,3) rectangle (7,5);
+	\path (0,-1) -- (1,-1);
+	%
+	\begin{scope}[thepink,->]
+		\draw[bend right=5] (a) to (1);
+		\draw[bend right=10] (b) to (1);
+		\draw[bend right=15] (c) to (1);
+		\draw[big>,bend left=25] (A) to (2);
+		\draw[big>,bend left=20] (B) to (3);
+		\draw[big>,bend left=15] (C) to (4);
+	\end{scope}
+\end{tikzpicture}
+\]
+
+\begin{proposition}
+\label{prop:element linkings}
+%The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
+Standard linkings are proof nets.
+\end{proposition}
+
+The encoding of a configuration is then as follows.
+
+\begin{definition}
+\label{def:configuration encoding}
+The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a constraint graph $G$ is a linking $\links$ for $\itn G$, constructed incrementally for each successive edge $e$ and for each successive weight element $W$ within $e$, as follows.
+%
+Let $\gamma(e)=v$; firstly, the indicator of $\itn e$ is linked to the indicator target of $\itn v$.
+%
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
+\end{definition}
+
+\begin{proposition}
+If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
+\end{proposition}
+
+\begin{proof}
+Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable box for each $\parr$. 
+%
+The box of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
+%
+The box of each vertex-gadget $\itn v$ contains the edge-gadgets $\itn e$ such that $\gamma(e)=v$, plus all the weight absorbers within boxes of weight elements inside $\itn e$.
+%
+Since the weights of the connected edges $e$ sum to more than the inflow constraint of $v$, there are no unused constraint elements remaining in $\itn v$.
+%
+After closing the box of each $W$, each edge-gadget in the box of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
+\end{proof}
 

### 2014-05-11 main/LICS.tex
forgot to sync last time - no idea what did ...

@@
 %
-We will look at notions of subnets, and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par.
-%
-Furthermore, we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence.
+We will look at notions of subnets; we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence; and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par.
+
+\color{red}
+The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{MLL} proof equivalence, as described informally in the previous section, is correct.
+\color{black}
 
@@
 \[
-	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
-\]
-\vskip-12pt
+	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B} \qedhere
+\]
 \end{proof}
@@
 \label{prop:empire propagation}
-The empire $\emp v$ is determined by propagation from $v$: 1) through links; \color{red} 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.%;\\ 5) except never into a par or tensor if $v$ is a subformula.
+The empire $\emp v$ is determined by propagation from $v$: 1) through links; \color{red} 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.
 \end{proposition}
 
-Empires are connected to rewiring in the following ways.
+\noindent
+\color{red}
+The following three lemmata show how empires are connected to rewiring.
+%
+Firstly (Lemma~\ref{lem:rewiring within empire}), a jump from $\named v\bot$ may be rewired to exactly those $\1$-occurences that are in the empire of $v$.
+%
+Secondly (Lemma~\ref{lem:rewiring preserves empire}), rewiring this jump preserves the empire of $v$, up to that rewiring.
+%
+Thirdly (Lemma~\ref{lem:rewiring affects empires}), the empire of any other vertex $w$ will grow or shrink, or neither, but not both.
+\color{black}
 
@@
 \label{lem:rewiring within empire}
-For a proof net $(\Gamma,\links)$ where $\links(a)=v$ and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
+For a proof net $(\Gamma,\links)$ where $\links(a)=v$, and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
 %
@@
 \end{proof}
-
-\color{red}
-Rewiring a jump from $\named v\bot$ preserves the empire of $v$, up to that rewiring, by the first lemma below.
-%
-By the second lemma, the empire of any other vertex $w$ grows or shrinks, or neither, but not both.
-\color{black}
 
@@
 	\item
-Otherwise, $\Delta=\Delta'$.
+Otherwise, $\Delta=\Delta'$. \hfill\qedhere
 \end{enumerate}
-\vskip-12pt
 \end{proof}
@@
 
-\subsection*{Equivalence without $\parr$}
+\subsection*{Parity}
 
@@
 This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
-%
-However, a double such exchange commonly does give an equivalent net.
-
-\begin{lemma}
-\label{lem:double exchange}
-Let $\links$ be a proof net with for every switching a path
-$\links(a){\xedge}a{\xpath}b{\xedge}\links(b){\xpath}\links(c){\xedge}c{\xpath}d{\xedge}\links(d)$.
-%
-Then $\links\perm\links'$ where $\links'(a)=\links(b)$ and $\links'(b)=\links(a)$, $\links'(c)=\links(d)$, and $\links'(d)=\links(c)$, and $\links'(z)=\links(z)$ otherwise.
-%
-%Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path $\path uy$ passes through $\edge bv$ and $\edge xc$.
-%
-%Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
-\end{lemma}
-
-\begin{proof}
-By the rewiring path shown in Figure~\ref{fig:double exchange}.
-\end{proof}
-
-This dynamic will be used to characterise rewiring in the fragment of \capsabbrev{mll} that omits the par.
-%
-The following standard notion of \emph{balance} characterises provability for it.
-
-\begin{definition}
-The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and commas.
-%
-A sequent is \emph{balanced} if its balance is zero.
-\end{definition}
-
-\begin{proposition}
-\label{prop:unbalanced then uninhabited}
-An unbalanced sequent is uninhabited.
-\end{proposition}
-
-Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
-%
-After removing \color{red}dangling \color{black} $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
-
-\begin{proposition}
-A basic sequent is inhabited if and only if it is balanced.
-\end{proposition}
-
-\begin{proposition}
-A basic sequent $\bigtn(\bot^n),\1^n$ is inhabited by exactly $n!$ inequivalent proof nets.
-\end{proposition}
-
-\begin{proposition}
-\label{prop:level0 max binary}
-%
-A basic sequent with at least two tensor-formulae has at most two equivalence classes of proof nets.
-%
-\end{proposition}
-
-\begin{proof}
-By induction on the size of a sequent $\Gamma$.
-%
-The base case is the sequent $\1,\1,\bot\tn\bot$, which has two inequivalent proof nets.
-%
-For the inductive step,
-%
-\color{red}
-let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.
-%
-It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, the subnet $\links'$ restricted to $\Gamma',A$ belongs to one of two equivalence classes.
-%
-To find $\links'$, there are two cases.
-
-1) The path $\path az$ is via $\links(a)$.
-%
-If $\links(a)=z$, we are done. Otherwise, by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
-
-2) The path $\path az$ is via some $\named b\bot$ in $A$.
-%
-Firstly, if $\links(b)\neq z$, use Lemma~\ref{lem:rewiring within empire} to re-attach $b$ to $z$.
-%
-Next, let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
-%
-Then $\links'$ is obtained by linking $c$ to $b$, and applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as those of $c$ and $d$.
-%
-\end{proof}
-\color{black}
-
-%
-%To find $\links'$, if $\links(a)=z$ we are done.
-%%
-%Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
-%%
-%Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
-%%
-%Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
-%%
-%Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
-%
-%
-%Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
-%%
-%Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{Parity}
-
-\aftersubsection
+
 We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
@@
 
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Equivalence without $\parr$}
+
+\aftersubsection
+
+A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
+%
+This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
+%
+However, a double such exchange commonly does give an equivalent net.
+
+\begin{lemma}
+\label{lem:double exchange}
+Let $\links$ be a proof net with for every switching a path
+$\links(a){\xedge}a{\xpath}b{\xedge}\links(b){\xpath}\links(c){\xedge}c{\xpath}d{\xedge}\links(d)$.
+%
+Then $\links\perm\links'$ where $\links'(a)=\links(b)$ and $\links'(b)=\links(a)$, $\links'(c)=\links(d)$, and $\links'(d)=\links(c)$, and $\links'(z)=\links(z)$ otherwise.
+%
+%Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path $\path uy$ passes through $\edge bv$ and $\edge xc$.
+%
+%Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
+\end{lemma}
+
+\begin{proof}
+By the rewiring path shown in Figure~\ref{fig:double exchange}.
+\end{proof}
+
+This dynamic will be used to characterise rewiring in the fragment of \capsabbrev{mll} that omits the par.
+%
+%The following standard notion of \emph{balance} characterises provability for it.
+
+\begin{definition}
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and commas.
+%
+A sequent is \emph{balanced} if its balance is zero.
+\end{definition}
+
+\begin{proposition}
+\label{prop:unbalanced then uninhabited}
+An unbalanced sequent is uninhabited.
+\end{proposition}
+
+Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
+%
+After removing \color{red}dangling \color{black} $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
+
+\begin{proposition}
+A basic sequent is inhabited if and only if it is balanced.
+\end{proposition}
+
+\begin{proposition}
+A basic sequent $\bigtn(\bot^n),\1^n$ is inhabited by exactly $n!$ inequivalent proof nets.
+\end{proposition}
+
+\begin{proposition}
+\label{prop:level0 max binary}
+%
+A basic sequent with at least two tensor-formulae has at most two equivalence classes of proof nets.
+%
+\end{proposition}
+
+\begin{proof}
+By induction on the size of a sequent $\Gamma$.
+%
+The base case is the sequent $\1,\1,\bot\tn\bot$, which has two inequivalent proof nets.
+%
+For the inductive step,
+%
+\color{red}
+let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.
+%
+It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, the subnet $\links'$ restricted to $\Gamma',A$ belongs to one of two equivalence classes.
+%
+To find $\links'$, there are two cases.
+
+1) The path $\path az$ is via $\links(a)$.
+%
+If $\links(a)=z$, we are done. Otherwise, by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
+
+2) The path $\path az$ is via some $\named b\bot$ in $A$.
+%
+Firstly, if $\links(b)\neq z$, use Lemma~\ref{lem:rewiring within empire} to re-attach $b$ to $z$.
+%
+Next, let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
+%
+Then $\links'$ is obtained by linking $c$ to $b$, and applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as those of $c$ and $d$.
+%
+\end{proof}
+\color{black}
+
+%
+%To find $\links'$, if $\links(a)=z$ we are done.
+%%
+%Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
+%%
+%Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
+%%
+%Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
+%%
+%Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
+%
+%
+%Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
+%%
+%Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
+
 %------------------------------------------------------------
@@
 
-\section{Correctness of the encoding}
+\section{Formalising the encoding}
 \label{sec:correctness}
@@
 %
-\displayOcto{\octorollA2}%\QEDhere}
+\displayOcto{\octorollA2}\qedhere
 \end{enumerate}

### 2014-05-11 main/LICS.tex
working on subsection "Completeness"

@@
 
+Finally, if two connected configurations $\gamma\perm\delta$ are encoded individually as $\itn\gamma$ and $\itn\delta$, these may not be equivalent simply because their parity happens to be odd.
+%
+For that reason we shall adjust the encoding of the second to guarantee an even parity between them.
+
+\begin{definition}
+%
+Let $\itn\delta'$ be $\itn\delta$ with the first two weight absorbers exchanged.
+%
+For configurations $\gamma$ and $\delta$ for $G$, let $\itn\delta_\gamma$ be $\itn\delta$ if it has even parity with $\itn\gamma$, and $\itn\delta'$ otherwise.
+%
+\end{definition}
+
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 \aftersubsection
-Given a reconfiguration path $\gamma\perm\delta$ over total configurations, we will demonstrate a rewiring sequence between $\itn\gamma$ and $\itn\delta$ up to, possibly, a single exchange of two links in $\itn\delta$.
-%
-The central part of the argument will be to show how the weight element linking to a constraint element may be exchanged for another.
-%
-Once the weight elements of an edge-gadget are no longer connected to any constraint elements, the edge-gadget may straightforwardly be moved from one vertex-gadget to another by re-attaching its indicator link.
-%
-Throughout the rewiring process, weight elements and constraint elements will be kept in a standard linking, and according to the connectivity specified by the target configuration $\itn\delta$.
+Given a reconfiguration path $\gamma\perm\delta$ over total configurations, we will demonstrate a rewiring sequence between $\itn\gamma$ and $\itn\delta_\gamma$.
+%
+The central part of the argument will be to show how the weight element linking to a constraint element may be exchanged for another (Lemma~\ref{lem:octopus roll}).
+%
+Before and after the exchange, the constraint element and the weight element connecting to it will be in a standard linking.
+%
+
+Once the weight elements of an edge-gadget are no longer connected to any constraint elements, the edge-gadget becomes mobile, and may straightforwardly be moved from one vertex-gadget to another by re-attaching its indicator link.
 %
@@
 %
-The next lemma will demonstrate how weight absorbers can be exchanged freely, but only with two exchanges at once.
+\color{red}
+To be able to correct for this, the next lemma will demonstrate that, modulo parity, weight absorbers can be re-arranged at will.
 
@@
 \label{lem:permute weight absorbers}
-If $\links$ is a well linked proof net for $\itn G$ with a mobile edge-gadget $\itn e$, and $\links'$ agrees with $\links$ up to an even permutation of weight absorbers, then $\links\perm\links'$.
+If $\links$ and $\links'$ are well-linked proof nets for $\itn G$ that are equal up to an even permutation of weight absorbers, then $\links\perm\links'$ if $\links$ and $\links'$ have at least one mobile edge-gadget $\itn e$.
 \end{lemma}
@@
 \begin{proof}
-Let $e_0$ be the indicator of $\itn e$; since $\itn e$ is mobile, $e_0$ may re-attach anywhere within the proof net.
-%
-Let $e_1$ and $e_2$ be arbitrary other $\bot$-occurrences in $\itn e$.
-
-\begin{enumerate}
-
-	\item
-To exchange two weight absorbers $v$ and $w$ linked to by other edge-gadgets than $\itn e$, attach $e_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$ while also exchanging the targets of $e_0$ and $e_1$.
-
-	\item
-To reinstate $e_0$ as the connection between $\itn e$ and the remainder of the proof net, either perform another exchange as above, or exchange $v$ and $w$ twice again, once exchanging also the targets of $e_1$ and $e_2$, and once exchanging also the targets of $e_2$ and $e_0$.
-
-	\item
-To exchange a weight absorber $w$ linked from a $\named d\bot$ outside $\itn e$ for the target $v$ of $e_1$, first attach $e_0$ to $w$, then re-attach $d$ to $v$.
-%
-At this point, $e_1$ forms the only connect between $\itn e$ and the remainder of the proof net; to reinstate $e_0$ in this role, do as above, producing a net effect of cycling the targets of $e_1$, $e_2$, and $d$.
-
-	\item
-Finally, to exchange weight absorbers $v$ and $w$ linked by $\itn e$, attach $e_0$ to the indicator target of a vertex-gadget where also another edge-gadget $\itn d$ is connected, with indicator $d_0$ and an arbitrary other $\bot$-occurrence $d_1$.
-%
-Connect $d_0$ to $v$, and apply Lemma~\ref{lem:double exchange} to exchange $v$ and $w$, as well as exchanging the targets of $d_0$ and $d_1$.
-%
-A second such exchange is needed to re-attach $d_0$ and $d_1$ to their original targets.
-
-\end{enumerate}
-
-In each case, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be temporarily attached elsewhere.
+To reconfigure $\links'$ into $\links$, we will use the double exchange operation of Lemma~\ref{lem:double exchange} to exchange two arbitrary weight absorbers at a time, as well as two chosen jumps in the mobile edge-gadget $\itn e$.
+%
+Firstly, let $e_0$ be the indicator of $\itn e$.
+%
+Note that since $\itn e$ is mobile, $e_0$ may re-attach anywhere within the proof net.
+
+We will need two basic operations: 1) to exchange two arbitrary weight absorbers $v$ and $w$ linked from outside $\itn e$; and 2) to exchange an arbitrary weight absorber linked from inside $\itn e$ with one linked from outside $\itn e$.
+%
+Since we are using double exchanges, each operation will also exchange two arbitrary jumps from $\itn e$ (but not that from $e_0$).
+%
+By using operation 1) twice, we obtain a third, where four arbitrary weight absorbers linked from inside $\itn e$ are pairwise exchanged.
+%
+Since $\links'$ and $\links$ differ by an even permutation of weight absorbers, these three operations together give $\links'\sim\links$.
+
+To perform operation 1), exchanging $v$ and $w$ as well as the jumps from $e_1$ and $e_2$ in $\itn e$, first connect $e_0$ to $v$.
+%
+Then apply Lemma~\ref{lem:double exchange} three times: exchanging $v$ and $w$, and the targets of $e_0$ and $e_1$; exchanging $w$ and $v$, and the targets of $e_1$ and $e_2$; and exchanging $v$ and $w$, and the targets of $e_2$ and $e_0$.
+%
+The result is a net exchange of $v$ and $w$, and the targets of $e_1$ and $e_2$.
+
+Operation 2) is performed similarly.
+%
+In both cases, if one of the weight absorbers exchanged is linked to by multiple $\bot$-occurrences within the same weight element, these may be temporarily attached elsewhere.
 %
 \end{proof}
-
-If two connected configurations $\gamma\perm\delta$ are encoded individually as $\itn\gamma$ and $\itn\delta$, these may not be equivalent simply because their parity happens to be odd.
-%
-For that reason we shall adjust the encoding of the second to guarantee an even parity between them.
-
-\begin{definition}
-%
-Let $\itn\delta'$ be $\itn\delta$ with the first two weight absorbers exchanged.
-%
-For configurations $\gamma$ and $\delta$ for $G$, let $\itn\delta_\gamma$ be $\itn\delta$ if it has even parity with $\itn\gamma$, and $\itn\delta'$ otherwise.
-%
-\end{definition}
+\color{black}
 

### 2014-05-12 main/LICS.tex
subsection "completeness"

@@
 
+\color{red}
+
 \aftersubsection
@@
 %
-
-Once the weight elements of an edge-gadget are no longer connected to any constraint elements, the edge-gadget becomes mobile, and may straightforwardly be moved from one vertex-gadget to another by re-attaching its indicator link.
-%
-Linkings between weight elements and weight absorbers will remain arbitrary, and will be re-adjusted to match $\itn\delta$ at the end of the process.
-
-In a proof net for $\itn G$, an edge-gadget $\itn e$ is \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or linked only to weight absorbers.
-%
-A well-linked edge-gadget is \emph{mobile} if all its weight elements connect to weight absorbers.
+The linking between weight elements and weight absorbers need not be standard: it will be shown that weight absorbers may be freely rearranged, as long as parity remains even (Lemma~\ref{lem:permute weight absorbers}).
+
+For a reconfiguration step $\gamma\perm*\delta$ where the edge $e$ changes direction from $v$ to $w$, the rewiring sequence $\itn\gamma\perm\itn\delta_\gamma$ will be as follows.
+%
+First, the weight elements of edge-gadgets connecting to $\itn v$ are rearranged to match their target configuration, in $\itn\delta_\gamma$, which means the weight elements of $\itn e$ connect only to weight absorbers.
+%
+Then $\itn e$ is moved from $\itn v$ to $\itn w$ by rewiring its indicator link, from the indicator of $\itn v$ to that of $\itn w$.
+%
+Next, the weight elements connecting to $\itn w$ are rewired to match $\itn\delta_\gamma$, and finally, weight absorbers are rearranged to match $\itn\delta_\gamma$ as well.
+
+To describe the intermediate stages of such a rewiring sequence, call an edge-gadget $\itn e$ \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or linked only to weight absorbers (in arbitrary fashion).
+%
+\color{black}
+%
+A well-linked edge-gadget is \emph{mobile} if all its weight elements connect only to weight absorbers.
 %
@@
 	\item\label{item:exchange added}
-In the present configuration, the links from the weight elements form two subnets: one over the sub-sequents $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
+In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
 %

### 2014-05-15 main/LICS.tex
revised "parity" and "equivalence without par"

@@
 
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\color{red}
+
+\subsection*{Parity}
+
+\aftersubsection
+The linearity of \capsabbrev{mll} means that in a proof or proof net, there is always a certain balance to the number of $\bot$- and $\parr$-occurrences. 
+%
+This observation gives a well-known necessary condition for the provability of a sequent.
+
+\begin{definition}
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and commas.
+%
+A sequent is \emph{balanced} if its balance is zero.
+\end{definition}
+
+\begin{proposition}
+\label{prop:unbalanced then uninhabited}
+An unbalanced sequent is uninhabited.
+\end{proposition}
+
+Here, we will introduce a similar necessary condition for the equivalence of two proof nets.
+%
+We shall associate a \emph{parity} with any pair of linkings $\links$ and $\links'$ over the same sequent $\Gamma$, and we shall find that the parity of equivalent linkings is always even.
+
+For this argument we will work with formulae over alternating $n$-ary connectives $\tn$ and $\parr$; i.e.\ every argument of a $\tn$ is a $\parr$ and vice versa.
+%
+The units are then given by the $0$-ary case; moreover, we need not rule out $1$-ary connectives.
+%
+We will consider a given named sequent $\Gamma$, but will assume that it consists of a single formula, if necessary by introducing a $\parr$ at the root.
+
+To be able to compare arbitrary proof nets over $\Gamma$, we will use the following naming scheme for the edges of a switching graph, for any proof net over $\Gamma$.
+%
+A tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges, which we shall name $v(1),\dotsc,v(n)$; a par $\named v\pr$ has one switched edge named $v(1)$; and $\named v\bot$ has the jump named $v(1)$.
+%
+The naming scheme identifies edges across all switching graphs of all proof nets for $\Gamma$.
+
+Taking a different perspective, we may consider a switching graph as a directed tree, rooted in the root connective of $\Gamma$.
+%
+This establishes a bijection between the edges and the non-root vertices, which associates each edge with its target vertex.
+
+\begin{figure}
+\[
+	\vc{\parityNetA} \qquad \vc{\parityNetB}
+\]
+\caption{A switching graph of a proof net as a directed tree}
+\label{fig:directed switching graph}
+\end{figure}
+
+The example in Figure~\ref{fig:directed switching graph} displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $i$, and the edge $\edge rg$ for the root par $r$.
+%
+The induced bijection associates for example the edge named $r(1)$ with the vertex $g$, the edge $g(1)$ with $h$, and the edge $h(1)$ with $a$, and it associates $f(1)$ with $f$ and $c(3)$ with $c$.
+
+Given two proof nets $\links$ and $\links'$ for $\Gamma$, and a switching graph for each (not necessarily given by the same switching of $\Gamma$), we obtain two bijections between edges and (non-root) vertices.
+%
+Composing these gives a permutation on the non-root vertices.
+%
+\begin{definition}
+The \emph{parity} of two switching graphs for proof nets $\links$ and $\links'$ for a sequent $\Gamma$ is the parity of their induced permutation.
+\end{definition}
+%
+We will show that both 1) rewiring and 2) choosing a different switching induce even parity.
+%
+By 2) we may define the parity of two proof nets $\links$ and $\links'$ to be that over arbitrary switching graphs; then by 1) it follows that proof nets with odd parity are inequivalent.
+
+\begin{figure}
+\[
+	\vc{\parityNetC1} \perm \vc{\parityNetC2}
+\quad \vc{\rule{.5pt}{4cm}} \quad
+	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
+\]
+\caption{Rewiring on a switching graph as a directed tree}
+\label{fig:rewiring directed switching graph}
+\end{figure}
+
+We will demonstrate 1), while 2) is similar.
+%
+Let $\links\perm*\links'$ by rewiring a jump from $\edge va$ to $\edge vb$.
+%
+By fixing a switching for $\Gamma$, we obtain a switching graph for each of the two nets; note that the jump is named $v(1)$ in each.
+%
+There are two possibilities, illustrated in Figure~\ref{fig:rewiring directed switching graph}.
+%
+On the left, if the jump $v(1)$ is directed upward, then the target of each edge in the directed switching graphs remains the same---in particular $v(1)$ has target $v$---and the induced permutation is the identity.
+
+On the right, in Figure~\ref{fig:rewiring directed switching graph}, if the jump from $v$ is directed downward, the subtree of $a$ will get the new root node $b$.
+%
+Then the vertices that are associated with a new edge are exactly those on the path $\path ab$ in the switching graph, as illustrated below.
+%
+\[
+	\parityNetE
+\]
+%
+Since the connectives in $\Gamma$ were assumed to be strictly alternating, there are an odd number of vertices on this path, $2n+3$: each even $v_i$ must be a $\bot$ or $\pr$, while each odd $v_j$ must be a $\1$ or $\tn$.
+%
+The permutation induced is then as follows.
+%
+Since $v$ has target $a$ in the first switching graph, and target $b$ in the second, it takes $a$ to $b$.
+%
+Further, since an edge connecting $v_i$ and $v_{i+1}$ has target $v_{i+1}$ in the first, but target $v_i$ in the second graph, the permutation takes $v_{i+1}$ to $v_i$.
+%
+The complete permutation is then a cyclic one taking each vertex on the path $\path ab$ to the previous, and the first to the last.
+%
+A cyclic permutation of odd length has even parity.
+
+The above argument gives us 1), that rewiring has even parity.
+%
+To see that the same argument also gives 2), it is sufficient to consider that choosing a different switching for a single par is essentially the same operation as rewiring, if the par is considered a $\bot$ and the switched edge a jump.
+%
+We may thus conclude that:
+
+\begin{proposition}
+Two equivalent proof nets have even parity.
+\end{proposition}
+
+%Now consider the bijection between non-root vertices and edges that associates each vertex with the edge towards its parent. 
+%
+%A second linking $\links'$ similarly establishes such a bijection.
+Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the non-root vertices in $\Gamma$.
+Finally the parity of the pair of linkings is taken to be the parity of this permutation.
+%
+% Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
+This therefore establishes a bijection between the edges of the tree and the non-root vertices.
+%
+%A second linking $\links'$ similarly establishes such a bijection.
+Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
+Finally the parity of the pair of linkings is taken to be the parity of this permutation.
+%
+%\begin{lemma}
+%	The parity is well-defined, in the sense that it does not depend on the choice of switching.
+%\end{lemma}
+%\begin{proof}
+%	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
+%	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
+%	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
+%	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
+%	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
+%	permutation of an odd number of elements is an even permutation.
+%\end{proof}
+%
+%Essentially the same argument also establishes that:
+%\begin{lemma}
+%	If two linkings are equivalent, their parity is even.
+%\end{lemma}
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
 \begin{figure*}
@@
 
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{Parity}
+\subsection*{Equivalence without $\parr$}
 
 \aftersubsection
-A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
-%
-This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
-
-We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$.
-We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a basic sequent.
-
-For this argument we shall assume that the connectives $\tn$ and $\parr$ are n-ary, and that every argument of a $\tn$ is a $\parr$ and vice versa.
-Assume also that $\Gamma$ consists of a single formula, if necessary by introducing a $\parr$ at the root.
-Now fix an arbitrary switching of $\Gamma$; this switching together with a linking $\links$ defines a tree whose vertices are the subformulae of $\Gamma$ and whose edges are the edges of the chosen switching together with the links of $\links$.
-Take the root of the formula $\Gamma$ to be the root of this tree.
-%
-
-\color{red}
-Given a named sequent $\Gamma$, we can identify edges across all switching graphs for all proof nets for $\Gamma$ by their parent connective: a tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges $v(1),\dotsc,v(n)$; a par $\named v\pr$ has one switched edge $v(1)$; and $\named v\bot$ has the jump $v(1)$.
-%
-For a switching graph, selecting a vertex as the root establishes a bijection between edges and the remaining nodes, which associates each edge with its target.
-%
-The example below displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $\named i\pr$, with chosen root $g$.
-\[
-	\vc{\parityNetA} \qquad \vc{\parityNetB}
-\]
-The tree above right associates, for example, the edge $c(3)$ with the vertex $c$, and $i(1)$ with $j$.
-%
-Two proof nets for the same sequent establish two such bijections, composing which gives a permutation on the (non-root) vertices.
-%
-If the nets are equivalent, the parity of this permutation is even.
-%
-This follows from what will be established next: a single rewiring connects switching graphs with even parity, and so does switching a single par.
-%
-The case for rewiring is illustrated; that for switching is similar.
-%
-For rewiring a jump $\edge va$ to $\edge vb$ (named $v(1)$ in the above scheme) there are two possibilities.
-%
-If the jump is directed towards the root, illustrated below left, then each node is connected to the root via the same edge, and the permutation is the identity.
-%
-If the jump is directed downward, the subtree of $a$ will get the new root node $b$, as illustrated below right.
-%
-\[
-	\vc{\parityNetC1} \perm \vc{\parityNetC2}
-\quad \vc{\rule{.5pt}{4cm}} \quad
-	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
-\]
-%
-The vertices that are assigned a new edge are exactly those on the path from $a$ to $b$ in the switching graph, illustrated below.
-%
-\[
-	\parityNetE
-\]
-%
-Since proof nets were assumed to be strictly alternating---each even $v_i$ is a $\bot$ or $\pr$, each odd $v_j$ a $\1$ or $\tn$---there are an odd number of vertices on this path, $2n+3$.
-%
-The permutation it induces is a cyclic one, matching each $v_i$ with $v_{i+1}$, $v_{2n}$ with $b$, $b$ with $a$, and $a$ with $v_0$.
-%
-A cyclic permutation of odd length is an even permutation.
-
-\color{black}
-
-%Now consider the bijection between non-root vertices and edges that associates each vertex with the edge towards its parent. 
-%
-%A second linking $\links'$ similarly establishes such a bijection.
-Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the non-root vertices in $\Gamma$.
-Finally the parity of the pair of linkings is taken to be the parity of this permutation.
-%
-% Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
-This therefore establishes a bijection between the edges of the tree and the non-root vertices.
-%
-%A second linking $\links'$ similarly establishes such a bijection.
-Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
-Finally the parity of the pair of linkings is taken to be the parity of this permutation.
-
-\begin{lemma}
-	The parity is well-defined, in the sense that it does not depend on the choice of switching.
-\end{lemma}
-\begin{proof}
-	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
-	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
-	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
-	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
-	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
-	permutation of an odd number of elements is an even permutation.
-\end{proof}
-
-Essentially the same argument also establishes that:
-\begin{lemma}
-	If two linkings are equivalent, their parity is even.
-\end{lemma}
+Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
+%
+After removing dangling $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
+
+Provability for basic sequents is entirely determined by balance:
 
 \begin{proposition}
-\label{prop:parity determines equivalence}
-Two proof nets for a basic sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
+A balanced basic sequent is inhabited.
 \end{proposition}
 
-\begin{proof}
-By Proposition~\ref{prop:level0 max binary} the sequent has at most 2 equivalence classes.
-%
-Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
-\end{proof}
-
-The previous illustrates that equivalence in the fragment without $\parr$ is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.
-
-These characteristics hold the following lessons on rewiring for the design of our encoding, in Section~\ref{sec:encoding}. 
-%
-Firstly, making proof nets equivalent is generally easier than preventing them from being equivalent, and in particular changing a formula $A$ to $A\tn\bot$ dramatically increases its rewiring potential.
-%
-The focus of our encoding will therefore be on preventing undesired linkings from being proof nets at all, rather than being unreachable by rewiring.
-%
-Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding.
-%
-It will prove a minor technical distraction, that we will call the `parity problem'.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{Equivalence without $\parr$}
-
-\aftersubsection
-
-A basic observation on \capsabbrev{mll} is that the identity proof for $\bot\tn\bot,\1\parr\1$ is not equivalent to the `symmetry' or `twist' proof for the same sequent.
-%
-This will hold in general: exchanging the targets of two links generally results in an inequivalent net, in particular when the $\bot$-instances are connected by a tensor.
-%
-However, a double such exchange commonly does give an equivalent net.
+We will show that, similarly, equivalence for basic sequents is determined by parity.
+%
+An immediate observation is that a proof net for a basic sequent with only one tensor-formula, every $\1$ is linked to by exactly one jump---which means that no rewiring is possible.
+
+\begin{proposition}
+A basic sequent $\1^n,\bigtn(\bot^n)$ is inhabited by exactly $n!$ inequivalent proof nets.
+\end{proposition}
+
+In the following we will characterise equivalence for basic sequents with two or more tensor-formulae.
 
@@
 %
-%Let $\links$ be a proof net where $\links(a)=u$, $\links(b)=v$, $\links(c)=x$, and $\links(d)=y$, and for any switching the path $\path uy$ passes through $\edge bv$ and $\edge xc$.
-%
-%Then $\links\perm\links'$ where $\links'(a)=v$, $\links'(b)=u$, $\links'(c)=y$, and $\links'(d)=x$, and $\links'(z)=\links(z)$ otherwise.
 \end{lemma}
@@
 
-This dynamic will be used to characterise rewiring in the fragment of \capsabbrev{mll} that omits the par.
-%
-%The following standard notion of \emph{balance} characterises provability for it.
-
-\begin{definition}
-The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and commas.
-%
-A sequent is \emph{balanced} if its balance is zero.
-\end{definition}
-
-\begin{proposition}
-\label{prop:unbalanced then uninhabited}
-An unbalanced sequent is uninhabited.
-\end{proposition}
-
-Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
-%
-After removing \color{red}dangling \color{black} $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
-
-\begin{proposition}
-A basic sequent is inhabited if and only if it is balanced.
-\end{proposition}
-
-\begin{proposition}
-A basic sequent $\bigtn(\bot^n),\1^n$ is inhabited by exactly $n!$ inequivalent proof nets.
-\end{proposition}
-
-\begin{proposition}
-\label{prop:level0 max binary}
+\begin{lemma}
+\label{lem:level0 max binary}
 %
@@
 %
-\end{proposition}
+\end{lemma}
 
@@
 
-%
-%To find $\links'$, if $\links(a)=z$ we are done.
-%%
-%Next, if the path from $\links(a)$ to $z$ does not pass through $a$, then by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
-%%
-%Thirdly, let $\links(b)=z$ for a $\named b\bot$ in $A$.
-%%
-%Let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
-%%
-%Then $\links'$ is obtained by first linking $c$ to $b$, and then applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as the targets of $c$ and $d$.
-%
-%
-%Finally, let the path from $a$ to $z$ pass $\named b\bot$ in $A$.
-%%
-%Then using Lemma~\ref{lem:rewiring within empire} re-attach $b$ to $z$, and repeat as above.
+\begin{proposition}
+\label{prop:parity determines equivalence}
+For a basic sequent with at least two tensor-formulae, two proof nets with even parity are equivalent.
+\end{proposition}
+
+\begin{proof}
+By Lemma~\ref{lem:level0 max binary} the sequent has at most 2 equivalence classes.
+%
+Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
+\end{proof}
 

### 2014-05-16 main/LICS.tex
final version

@@
 
+\keywords{linear logic, proof equivalence, proof nets, constraint logic, \capsabbrev{pspace}-completeness}
+
 \begin{abstract}
@@
 This naturally raises the question whether proof nets can be extended to work in the presence of units.
-The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \color{red}\cite{Lamarche-Strassburger-2006} \color{black} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
+The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \cite{Lamarche-Strassburger-2006} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
 
@@
 In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \capsabbrev{pspace}-complete. 
-It follows that there can be no satisfactory canonical notion of proof net:
-\color{red}
-if a notion of proof net were to exist where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
-\color{black}
+%
+This effectively rules out the existence of a satisfactory notion of proof net for \capsabbrev{mll} with units---one that reduces proof equivalence to syntactic equality, and where the translation from proofs to proof nets and equality of proof nets are both tractable.
+
+%It follows that there can be no satisfactory canonical notion of proof net: if a notion of proof net were to exist where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
 
@@
 %
-It is not uncommon for an \capsabbrev{np}-complete problem to have an associated reconfiguration problem that is \capsabbrev{pspace}-complete \cite{ReconfigurationProblems}; one example is SAT-reconfiguration, which is \capsabbrev{pspace}-complete.
+It is not uncommon for an \capsabbrev{np}-complete problem to have an associated reconfiguration problem that is \capsabbrev{pspace}-complete \cite{ReconfigurationProblems}; an example of this is SAT-reconfiguration.
 \capsabbrev{mll} proof equivalence may be regarded as the reconfiguration problem associated with \capsabbrev{mll} proof search, which is \capsabbrev{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
@@
 %------------------------------------------------------------
-
-\begin{figure}[!b]
+\beforesection
+
+\section{\capsabbrev{mll}}
+
+\aftersection
+%
+The formulae of unit-only multiplicative linear logic are given by the following grammar.
+%
+\setMidspace{5pt}
+\[
+	A,B,C \Coloneq \bot \Mid 1 \Mid A\parr B \Mid A\tn B
+\]
+%
+The connectives $\tn$ and $\parr$ will be considered up to associativity, and \emph{duality} $\dual A$ is via DeMorgan.
+%
+A \emph{sequent} $\Gamma,\Delta$ will be a multiset of formulae.
+%
+Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names, e.g.\
+\[
+	\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot~.
+\]
+%
+This allows to 1) identify \emph{occurrences} of subformulae uniquely by the name of their root connective, e.g.\ as $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
+%
+Names will often be left implicit.
+
+Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}, where the names of units and connectives are preserved through inferences.
+%
+Only cut-free proofs are considered, and no cut-rule is added.
+%
+\emph{Permutations} of inference rules are displayed in Figure~\ref{fig:permutations}; the symmetric variants of the last two permutations, \emph{par-tensor} and \emph{tensor-tensor}, have been omitted.
+
+\begin{definition}
+\label{def:equivalence}
+%
+\emph{Equivalence} $(\perm)$ of proofs in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
+%
+\emph{\capsabbrev{mll}\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
+%
+\end{definition}
+
+The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
+%
+Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
+
+\begin{figure}
 \quad\MLLrule b
@@
 
-\beforesection
-
-\section{\capsabbrev{mll}}
-
-\aftersection
-%
-The formulae of unit-only multiplicative linear logic are given by the following grammar.
-%
-\setMidspace{5pt}
-\[
-	A,B,C \Coloneq \bot \Mid 1 \Mid A\parr B \Mid A\tn B
-\]
-%
-The connectives $\tn$ and $\parr$ will be considered up to associativity, and \emph{duality} $\dual A$ is via DeMorgan.
-%
-A \emph{sequent} $\Gamma,\Delta$ will be a multiset of formulae.
-%
-Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names, e.g.\
-\[
-	\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot~.
-\]
-%
-This allows to 1) identify \emph{occurrences} of subformulae uniquely by the name of their root connective, e.g.\ as $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
-%
-Names will mostly be left implicit.
-
-Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}, where the names of units and connectives are preserved through inferences.
-%
-Only cut-free proofs are considered, and no cut-rule is added.
-%
-\emph{Permutations} of inference rules are displayed in Figure~\ref{fig:permutations}; the symmetric variants of the last two permutations, \emph{par-tensor} and \emph{tensor-tensor}, have been omitted.
-
-\begin{definition}
-\label{def:equivalence}
-%
-\emph{Equivalence} $(\perm)$ of proofs in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
-%
-\emph{\capsabbrev{mll}\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
-%
-\end{definition}
-
-The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
-%
-Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two representations denote the same morphism in any star-autonomous category.
-
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 %
-\color{red}
 The restriction that jumps must target $\1$-occurrences (rather than any connective) is a convenience---it can be circumvented by replacing a subformula $A$ by the equivalent $A\tn\1$.
-\color{black}
 
 \begin{figure}
-\color{red}
 \[
@@
 \noindent
-\color{red}
 An example rewiring sequence is given in Figure~\ref{fig:net rewiring}, using the notation for proof nets introduced below.
-\color{black}
 
@@
 
-\begin{proposition}[\cite{Danos-Regnier-1989}, \color{red}\cite{Lamarche-Strassburger-2006}\color{black}]
+\begin{proposition}[\cite{Danos-Regnier-1989}, \cite{Lamarche-Strassburger-2006}]
 \label{prop:correctness and sequentialisation}
@@
 %
-For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$ such that $\Pi\toNet\links$ and $\Pi'\toNet\links'$, $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
+%If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
+For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$, if $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
 %
@@
 formulae related by a tensor will be connected by edges; 
-formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula \color{red}(and also for illustrative purposes)\color{black}.
+formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula (and also for illustrative purposes).
 %
@@
 %
-Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
+Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\parr\cdots\parr\! A_n$.
 %
@@
 %
-\color{red}
 A path in a proof net or switching graph is indicated $\path ab$, and illustrated as below.
-\color{black}
-%
-%A dashed edge will indicate that two vertices are connected, in a proof net or a switching graph, as illustrated below.
+%
 \[
@@
 	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
-	%\coordinate (a') at ($(a) + (.6,0)$); \coordinate (b') at ($(b) + (-.6,0)$);
-	%\draw[thepink,dashed] (a')--(b'); \draw[thepink,->] (a')--(a.center); \draw[thepink,->] (b')--(b.center);
 \end{tikzpicture}
@@
 A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
-A rewrite step consists of the reversal of a single edge in a configuration:
-rewrite steps must preserve the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
-
-\color{red}
-Figure~\ref{fig:NCL example} shows an example rewrite sequence in a constraint graph.
+A rewrite step consists of the reversal of a single edge in a configuration, while preserving the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
+
+Figure~\ref{fig:NCL example} shows an example rewrite sequence in a part of a constraint graph.
 %
 The central node has inflow constraint 2, the thick blue edge has weight 2, and the thinner red edges have weight 1.
-\color{black}
 
@@
 
-\begin{figure}\color{red}
+\begin{figure}
 $
@@
 \begin{figure*}
-\color{red}
 \[
@@
 
-\color{red}
-The complete encoding of a constraint graph $G$ will be a sequent $\Gamma$ consisting of:
+The complete encoding of a constraint graph $G$ will then be a sequent $\Gamma$ consisting of:
 % 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
@@
 
-\color{black}
-
 %------------------------------------------------------------
@@
 
-\color{red}
 The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{MLL} proof equivalence, as described informally in the previous section, is correct.
-\color{black}
 
@@
 
-%\noindent
-\color{red}
 The \emph{ports} of a sub-sequent $\Gamma'$ or subnet $(\Gamma',\links')$ are the root vertices of $\Gamma'$.
 %
-%The root vertices of $\Gamma'$ are the \emph{ports} of the sub-sequent $\Gamma'$ and of the subnet $(\Gamma',\links')$.
-%
 For a vertex $v$ naming a par, tensor, or bottom, the subnets of which it is a port correspond to the possible subproofs of the rule introducing $v$ in a sequentialisation (the subproof of a $\1$-subformula must always be empty).
-%
-%
-%A \emph{scope} of a par $\named v\parr$ is a subnet that has $v$ as a port.
-%
-%The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
 
@@
 
-\color{black}
-
-%
-%In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
-%%
-%In the example below, a scope of a (ternary) par is indicated (left) and contracted (right).
-%\[
-%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-%	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
-%		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
-%		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
-%	\node[circ] (0) at (5.75,0) {};
-%	\node[circ] (1) at (-1,3) {};
-%	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
-%	\draw[rounded corners] (0,2) rectangle (4,4);
-%	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
-%	\begin{scope}[thepink,->]
-%			\draw[bend right=10] (x) to (1);
-%			\draw[bend right=20] (y) to (2);
-%			\draw[bend right=10] (a) to (2);
-%			\draw[bend right=10] (b) to (3);
-%			\draw[bend left=10]  (c) to (3);
-%			\draw[bend left=10]  (d) to (4);
-%			\draw[bend right=10] (e) to (0);
-%	\end{scope}
-%	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
-%\end{tikzpicture}
-%\qquad\qquad
-%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-%	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
-%	\node[circ] (0) at (3,0) {};
-%	\node[circ] (1) at (-1,3) {};
-%	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
-%	\draw (box)--(3,3) node[bullet] (e) {};
-%	\begin{scope}[thepink,->]
-%			\draw[bend right=10] (x) to (1);
-%			\draw[bend right=20] (y) to (box);
-%			\draw[bend right=10] (e) to (0);
-%	\end{scope}
-%	\path (0,4.25)--(1,4.25);
-%\end{tikzpicture}
-%\]
-%%
-%The contraction of a scope corresponds to the use of a box,  may replace the switching condition as a correctness criterion:
-%%
-%The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.
-
-%
-%\begin{proposition}
-%\label{prop:scoping correctness}
-%A linking $\links$ for a sequent $\Gamma$ is a proof net if and only if each $\named v\parr$ is a port of a sub-sequent $s(v)\leq\Gamma$ such that:
-%
-%\begin{enumerate}
-%	\item
-%sub-sequents either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$; and
-%	\item
-%for each $\named v\parr$ the graph $\sigma(v)=(s(v),\links|_{s(v)})$ becomes a tree when all \color{red} (immediate) sub-sequents $s(w)<s(v)$ are contracted.
-%\end{enumerate}
-%%
-%\end{proposition}
-%
-%
-%\begin{proof}
-%For the `if' direction, it follows by induction on the nesting of sub-sequents that each graph $\sigma(v)$ satisfies the switching condition.
-%%
-%For the `only if' direction, given a sequentialisation of $(\Gamma,\links)$, a sub-sequent $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
-%\[
-%	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
-%\]
-%\vskip-12pt
-%\end{proof}
-
 In a proof net, the \emph{kingdom} and the \emph{empire} of a vertex $v$ are respectively the smallest and largest subnet that have $v$ as a port.
@@
 %
-\color{red} 
 We will denote the empire of $v$ in $\links$ by $\emp v$ (used both as a graph and a set of vertices).
-\color{black}
 
@@
 \label{prop:empire propagation}
-The empire $\emp v$ is determined by propagation from $v$: 1) through links; \color{red} 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.
+The empire $\emp v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.
 \end{proposition}
@@
 \noindent
-\color{red}
 The following three lemmata show how empires are connected to rewiring.
 %
-Firstly (Lemma~\ref{lem:rewiring within empire}), a jump from $\named v\bot$ may be rewired to exactly those $\1$-occurences that are in the empire of $v$.
-%
-Secondly (Lemma~\ref{lem:rewiring preserves empire}), rewiring this jump preserves the empire of $v$, up to that rewiring.
-%
-Thirdly (Lemma~\ref{lem:rewiring affects empires}), the empire of any other vertex $w$ will grow or shrink, or neither, but not both.
-\color{black}
+Firstly, a jump from $\named v\bot$ may be rewired to exactly those $\1$-occurences that are in the empire of $v$ (Lemma~\ref{lem:rewiring within empire}).
+%
+Secondly, rewiring this jump preserves the empire of $v$, up to that rewiring (Lemma~\ref{lem:rewiring preserves empire}).
+%
+Thirdly, the empire of any other vertex $w$ will grow or shrink, or neither, but not both (Lemma~\ref{lem:rewiring affects empires}).
 
@@
 
-\color{red}
-
 \subsection*{Parity}
@@
 
-For this argument we will work with formulae over alternating $n$-ary connectives $\tn$ and $\parr$; i.e.\ every argument of a $\tn$ is a $\parr$ and vice versa.
-%
-The units are then given by the $0$-ary case; moreover, we need not rule out $1$-ary connectives.
+For this argument we will work with $n$-ary connectives $\tn$ and $\parr$, and alternating formulae, i.e.\ every argument of a $\tn$ is a $\parr$ and vice versa.
+%
+The units are given by the $0$-ary connectives, and we need not rule out unary ones.
 %
@@
 %
-A tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges, which we shall name $v(1),\dotsc,v(n)$; a par $\named v\pr$ has one switched edge named $v(1)$; and $\named v\bot$ has the jump named $v(1)$.
+A tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges, which we shall name $v(1)$ through $v(n)$; a par $\named v\pr$ has one switched edge, to be named $v(1)$; and $\named v\bot$ has the jump named $v(1)$.
 %
@@
 This establishes a bijection between the edges and the non-root vertices, which associates each edge with its target vertex.
+
+The example in Figure~\ref{fig:directed switching graph} displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $i$, and the edge $\edge rg$ for the root par $r$.
+%
+The induced bijection associates for example the edge named $r(1)$ with the vertex $g$, the edge $g(1)$ with $h$, and the edge $h(1)$ with $a$; it further associates $f(1)$ with $f$ and $c(3)$ with $c$.
+
+Given two proof nets $\links$ and $\links'$ for $\Gamma$, and a switching graph for each (not necessarily given by the same switching of $\Gamma$), we obtain two bijections between edges and (non-root) vertices.
+%
+Composing these gives a permutation on the non-root vertices.
+%
+\begin{definition}
+The \emph{parity} of two switching graphs for proof nets $\links$ and $\links'$ for a sequent $\Gamma$ is the parity of their induced permutation.
+\end{definition}
+%
+We will show that both 1) rewiring and 2) choosing a different switching induce even parity.
+%
+By 2) we may define the parity of two proof nets $\links$ and $\links'$ to be that over arbitrary switching graphs; then by 1) it follows that proof nets with odd parity are inequivalent.
+
+We will demonstrate 1), while 2) is similar.
+%
+Let $\links\perm*\links'$ by rewiring a jump from $\edge va$ to $\edge vb$.
+%
+By fixing a switching for $\Gamma$, we obtain a switching graph for each of the two nets, where the jump is named $v(1)$ in each.
+%
+There are two possibilities, illustrated in Figure~\ref{fig:rewiring directed switching graph}.
+%
+On the left, if the jump $v(1)$ is directed upward, then the target of each edge in the directed switching graphs remains the same---in particular $v(1)$ has target $v$---and the induced permutation is the identity.
+
+On the right, in Figure~\ref{fig:rewiring directed switching graph}, if the jump from $v$ is directed downward, the subtree of $a$ will get the new root node $b$.
+%
+Then the vertices that are associated with a new edge are exactly those on the path $\path ab$ in the switching graph, as illustrated below.
+%
+\[
+	\parityNetE
+\]
+%
+Since the connectives in $\Gamma$ were assumed to be strictly alternating, there are an odd number of vertices on this path, $2n+3$: each even $v_i$ must be a $\bot$ or $\pr$, while each odd $v_j$ must be a $\1$ or $\tn$.
+%
+The permutation induced is then as follows.
+%
+Since $v$ has target $a$ in the first switching graph, and target $b$ in the second, it takes $a$ to $b$.
+%
+Further, since an edge connecting $v_i$ and $v_{i+1}$ has target $v_{i+1}$ in the first, but target $v_i$ in the second graph, the permutation takes $v_{i+1}$ to $v_i$.
+%
+The complete permutation is then a cyclic one taking each vertex on the path $\path ab$ to the previous, and the first to the last.
+%
+A cyclic permutation of odd length has even parity.
+
+The above argument gives us 1), that rewiring has even parity.
+%
+To see that the same argument also gives 2), it is sufficient to consider that choosing a different switching for a single par is essentially the same operation as rewiring, if the par is considered a $\bot$ and the switched edge a jump.
+%
+We may thus conclude that:
+
+\begin{proposition}
+Two equivalent proof nets have even parity.
+\end{proposition}
 
@@
 
-The example in Figure~\ref{fig:directed switching graph} displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $i$, and the edge $\edge rg$ for the root par $r$.
-%
-The induced bijection associates for example the edge named $r(1)$ with the vertex $g$, the edge $g(1)$ with $h$, and the edge $h(1)$ with $a$, and it associates $f(1)$ with $f$ and $c(3)$ with $c$.
-
-Given two proof nets $\links$ and $\links'$ for $\Gamma$, and a switching graph for each (not necessarily given by the same switching of $\Gamma$), we obtain two bijections between edges and (non-root) vertices.
-%
-Composing these gives a permutation on the non-root vertices.
-%
-\begin{definition}
-The \emph{parity} of two switching graphs for proof nets $\links$ and $\links'$ for a sequent $\Gamma$ is the parity of their induced permutation.
-\end{definition}
-%
-We will show that both 1) rewiring and 2) choosing a different switching induce even parity.
-%
-By 2) we may define the parity of two proof nets $\links$ and $\links'$ to be that over arbitrary switching graphs; then by 1) it follows that proof nets with odd parity are inequivalent.
-
 \begin{figure}
@@
 \]
-\caption{Rewiring on a switching graph as a directed tree}
+\caption{Rewiring on the directed tree of a switching graph}
 \label{fig:rewiring directed switching graph}
 \end{figure}
-
-We will demonstrate 1), while 2) is similar.
-%
-Let $\links\perm*\links'$ by rewiring a jump from $\edge va$ to $\edge vb$.
-%
-By fixing a switching for $\Gamma$, we obtain a switching graph for each of the two nets; note that the jump is named $v(1)$ in each.
-%
-There are two possibilities, illustrated in Figure~\ref{fig:rewiring directed switching graph}.
-%
-On the left, if the jump $v(1)$ is directed upward, then the target of each edge in the directed switching graphs remains the same---in particular $v(1)$ has target $v$---and the induced permutation is the identity.
-
-On the right, in Figure~\ref{fig:rewiring directed switching graph}, if the jump from $v$ is directed downward, the subtree of $a$ will get the new root node $b$.
-%
-Then the vertices that are associated with a new edge are exactly those on the path $\path ab$ in the switching graph, as illustrated below.
-%
-\[
-	\parityNetE
-\]
-%
-Since the connectives in $\Gamma$ were assumed to be strictly alternating, there are an odd number of vertices on this path, $2n+3$: each even $v_i$ must be a $\bot$ or $\pr$, while each odd $v_j$ must be a $\1$ or $\tn$.
-%
-The permutation induced is then as follows.
-%
-Since $v$ has target $a$ in the first switching graph, and target $b$ in the second, it takes $a$ to $b$.
-%
-Further, since an edge connecting $v_i$ and $v_{i+1}$ has target $v_{i+1}$ in the first, but target $v_i$ in the second graph, the permutation takes $v_{i+1}$ to $v_i$.
-%
-The complete permutation is then a cyclic one taking each vertex on the path $\path ab$ to the previous, and the first to the last.
-%
-A cyclic permutation of odd length has even parity.
-
-The above argument gives us 1), that rewiring has even parity.
-%
-To see that the same argument also gives 2), it is sufficient to consider that choosing a different switching for a single par is essentially the same operation as rewiring, if the par is considered a $\bot$ and the switched edge a jump.
-%
-We may thus conclude that:
-
-\begin{proposition}
-Two equivalent proof nets have even parity.
-\end{proposition}
 
@@
 %
-\color{red}
 let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.
@@
 \end{proof}
-\color{black}
 
@@
 %
-In this section we will establish that in our encoding of constraint graphs %partial \capsabbrev{ncg}-reconfiguration 
-in \capsabbrev{mll}, reconfiguration on graphs is captured by proof equivalence in \capsabbrev{mll}.
-%
-It will be shown that $\gamma\perm\delta$ if and only if $\itn\gamma\perm\itn\delta$ (modulo the parity problem---see Section~\ref{sec:rewiring}).
-%
-This will be separated into two parts: completeness ($\Rightarrow$) and soundness ($\Leftarrow$) .
-
-%
-For the formal definition, let $|V|$ and $|E|$ denote the number of vertices and edges, respectively, in a constraint graph $G=(V,E,c,v,w)$, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights respectively:
+We will formalise the encoding of \capsabbrev{ncg}-reconfiguration into \capsabbrev{mll} proof equivalence that was informally introduced in Section~\ref{sec:encoding}.
+%
+A constraint graph $G$ will be encoded as a sequent $\itn G$, and a configuration $\gamma$ for $G$ will be encoded as a proof net $\itn\gamma$ for $\itn G$.
+%
+We will show that $\gamma\perm\delta$ if and only if $\itn\gamma\perm\itn\delta$ (modulo a small adjustment to ensure even parity between $\itn\gamma$ and $\itn\delta$).
+
+For a constraint graph $G=(V,E,c,v,w)$, let $|V|$ and $|E|$ denote the number of vertices and edges, and let $|c|$ and $|w|$ denote the sum of all inflow constraints and the sum of all weights, respectively:
 \[
@@
 %
-Let $G=(V,E,c,v,w)$, and let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.
+Let $G=(V,E,c,v,w)$ with $|V|=n$, $|E|=m$, $V=\{v_1,\dotsc,v_n\}$, and $E=\{e_1,\dotsc,e_m\}$.
 
@@
 
-The standard linkings defined in the \color{red} second \color{black} and third case of the above definition are illustrated below.
+The standard linkings defined in the second and third case of the above definition are illustrated below.
 
@@
 %
-For that reason we shall adjust the encoding of the second to guarantee an even parity between them.
+For that reason we shall adjust the encoding of the second to guarantee an even parity.
 
@@
 
+In the remainder, we will show that our encoding is correct, i.e.\ that $\gamma\perm\delta$ if and only if $\itn\gamma\perm\itn\delta_\gamma$.
+%
+This will be separated into two parts: completeness ($\Rightarrow$) and soundness ($\Leftarrow$) .
+
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 \subsection*{Completeness}
-
-\color{red}
 
@@
 To describe the intermediate stages of such a rewiring sequence, call an edge-gadget $\itn e$ \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or linked only to weight absorbers (in arbitrary fashion).
-%
-\color{black}
 %
@@
 
-\renewcommand\scalefactor{0.88}
+\renewcommand\scalefactor{0.80}
 
 \newcommand\displayOcto[1]{%
- \NoIndent{%
-   \smallskip%
+% \NoIndent{%
+   \medskip%
    \centerline{%
 	 \scale{#1}%
-  }}%
-  \bigskip%
+  }%
+  \medskip%
 }
@@
 %
-The path of rewirings will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
-%
-\begin{enumerate}
-	\item
-The initial configuration is illustrated below. 
+The rewiring path will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
+
+\displayOcto{\octorollA1}
+
+\noindent
+1.\quad The initial configuration is illustrated above. 
 %
@@
 The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.
-%
-\displayOcto{\octorollA1}
-
-	\item
-The link $i-v$ is re-attached to connect to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
-%
+
 \displayOcto{\octorollB2}
 
-	\item
-Secondly, the link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.
-%
+\noindent
+2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$. 
+%
+
 \displayOcto{\octorollB3}
 
-	\item\label{item:exchange added}
+\noindent
+3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.
+%
+
+\displayOcto{\octorollC}
+
+\noindent
+4.\quad %\label{item:exchange added}
 In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
@@
 %
-It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step \ref{item:exchange needed} below.
+It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step 6 %\ref{item:exchange needed}
+below.
 %
@@
 %
-\displayOcto{\octorollC}
-
-	\item
-The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
-%
+
 \displayOcto{\octorollD1}
 
-	\item\label{item:exchange needed}
+\noindent
+5.\quad The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
+%
+
+\displayOcto{\octorollD2}
+
+\noindent
+6.\quad %\label{item:exchange needed}
 The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
 %
-Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step \ref{item:exchange added} above.
-%
-\displayOcto{\octorollD2}
-
-	\item
-The link from $i$ is re-attached to $v$ to yield the final configuration.
-%
-\displayOcto{\octorollA2}\qedhere
-\end{enumerate}
+Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step 4 %\ref{item:exchange added}
+above.
+%
+
+\displayOcto{\octorollA2}
+
+\noindent
+7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration.
+%\qedhere
+%\end{enumerate}
 \end{proof}
@@
 %
-\color{red}
 To be able to correct for this, the next lemma will demonstrate that, modulo parity, weight absorbers can be re-arranged at will.
@@
 \aftersubsection
-It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta$ is sound for \capsabbrev{ncg}-reconfiguration, $\gamma\perm\delta$.
-%
-To each proof net $\links$ for an encoded constraint graph $\itn G$ we will associate a partial configuration $\gamma=\coitn\links$, such that 1) a rewiring step $\links\perm*\links$ corresponds to a reconfiguration path $\coitn\links\perm\coitn{\links'}$, and 2) the function $\coitn-$ is a retraction of the encoding of configurations, $\coitn{\itn\gamma}=\gamma$.
+It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta_\gamma$ is sound for \capsabbrev{ncg}-reconfiguration, $\gamma\perm\delta$.
+%
+To each proof net $\links$ for an encoded constraint graph $\itn G$ we will associate a partial configuration $\gamma=\coitn\links$, such that 1) a rewiring step between $\links$ and $\links'$ corresponds to a reconfiguration path $\coitn\links\perm\coitn{\links'}$, and 2) the function $\coitn-$ is a retraction of the encoding of configurations, $\coitn{\itn\gamma}=\gamma$.
 
@@
 \begin{proof}
-Let $|V|=n$ and $|E|=m$, and consider the vertex $v_i$ and an edge $e$ connecting vertices $v_a$ and $v_b$ where $i\neq a,b$.
-%
-Each constraint element in $\itn{v_i}$ is an instance of the formula
-\[
-	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)~.
-\]
-The two $\parr$-subformulae have a balance of $-3i-1$ and respectively $-3(n-i)-2$.
-%
-Each weight element in $\itn{e}$ is an instance of 
-\[
-	W = \bigtn\big(\bot^{3a+2}\big)\parr\bigtn\big(\bot^{3(b-a)+1}\big)\parr\bigtn\big(\bot^{3(n-b)+3}\big)~.
-\]
-For each of the three $\tn$-subformulae, adding it to the scope of a $\parr$ will change its balance by $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
-%
-In pairs, they add to the balance of a scope by $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
-%
-Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$ (by Proposition~\ref{prop:tensor has disjoint subnets}), it follows that $W$ can balance the scope of at most one of both $\parr$-subformulae of $C$.
-
-The vertex-gadget $\itn{v_i}$ is the formula
-\[
-	\itn{v_i} = \bigparr\big(C^{3m\times c(v_i)} \big)\parr 1~.
-\]
-It will be shown that $m$ inappropriate edge-gadgets may balance at most $3(m-1)$ constraint elements $C$.
-
+%
+Let $|E|=m$.
+%
+We will show that the inappropriate edge-gadgets in $G$ are insufficient to fill $3m$ weight elements in $\itn v$.
+%
+Since weight elements come in multiples of $3m$, it follows that to fill the $3m\times c(v)$ constraint elements of $v$, there must be at least as many appropriate weight elements available.
+
+Let $e$ be inappropriate for $v$; let $C=A\tn B$ be a constraint element in $\itn v$, and $W=X\parr Y\parr Z$ weight element  in $\itn e$.
+%
+To find a proof net for the sequent $W,C$ requires to assign balanced boxes to the par-formulae $A$ and $B$.
+%
+Since $e$ is inappropriate, the sequents $A,X$ and $A,X,Y$ are not balanced, while the balance of each of the other sequents of $A$ with one or more of $X,Y,Z$ is always $1$ or $2$ $\pmod 3$.
+%
+It follows that there is no proof net for $W,C$.
+
+Next, it will be shown that to balance $3m$ constraint elements requires at least $m+1$ inappropriate edge-gadgets.
+%
 Two edge-gadgets may balance at most three constraint elements: one weight element $W$ has three subformulae, which may each balance at most one half of a constraint element; the other halves may be balanced by different weight elements of the second edge-gadget.
@@
 %
-%
-%Let the root nodes of the two $\parr$-subformulae of each instance of $C$ be labelled $x_j$ and $y_j$, for $1\leq j\leq 3m\times c(v_i)$. 
-%%
-%If the scopes $s(x_j)$ and $s(y_m)$ of any $x_j$ and $y_m$ are balanced by weight elements $W$ and $W'$ of the same edge-gadget $\itn e$, then since $W$ and $W'$ are connected by a tensor, there are switchings of $W$, $W'$, $s(x_j)$, and $s(y_m)$ such that $x_j$ and $y_m$ are connected in the proof net for $\itn G$.
-%%
-%Then the first constraint element of $\itn{v_i}$ requires 2 edge-gadgets to balance, and each successive element requires one additional edge-gadget.
 \end{proof}
@@
 \begin{definition}
-For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
+For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if both $e$ is appropriate for $v$ and $\itn e$ belongs to the empire of $\itn v$, and  undefined otherwise.
 \end{definition}
@@
 %
-Let $\itn e_1$ through $\itn e_n$ be the edge-gadgets moving in or out of the empire of $\itn v$.
+Let $\itn e_1$ through $\itn e_n$ be the edge-gadgets moving into or out of the empire of $\itn v$.
 %
@@
 
-\capsabbrev{pspace}-hardness follows by the encoding of \capsabbrev{ncg}-reconfiguration, which in its completed form is stated:
+\capsabbrev{pspace}-hardness is by the encoding of \capsabbrev{ncg}-reconfiguration, which in its completed form is stated:
 \[
@@
 
+\newpage
+
 \acks
 
-We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees.
+We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees for their constructive observations.
 
@@
 \end{document}
+
+%
+%Write $b(A)$ for the balance of a formula (or sequent) $A$.
+%%
+%Each constraint element in $\itn v$ is an instance of the formula $C=A\tn B$, where $b(A)\equiv 2$ and $b(B)\equiv 1\pmod 3$.
+%%
+%For $e$ inappropriate for $v$, a weight element $W=X\pr Y\pr Z$ in $\itn e$ satisfies $b(X)\equiv 2$, $b(Y)\equiv 1$, and $b(Z)\equiv 0\pmod 3$. 
+%%
+%To find a proof net for $W,C$ we need to assign balanced boxes to the par-formulae $A$ and $B$.
+%%
+%Since $e$ is inappropriate, the sequents $A,X$ and $A,X,Y$ are not balanced, while the balance $b(A,Y)\equiv 2$, $b(A,Z)\equiv
+
+%Each constraint element in $\itn{v_i}$ is an instance of the formula
+%\[
+%	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)~.
+%\]
+%The two $\parr$-subformulae have a balance of $-3i-1$ and respectively $-3(n-i)-2$.
+%%
+%Each weight element in $\itn{e}$ is an instance of 
+%\[
+%	W = \bigtn\big(\bot^{3a+2}\big)\parr\bigtn\big(\bot^{3(b-a)+1}\big)\parr\bigtn\big(\bot^{3(n-b)+3}\big)~.
+%\]
+%We will show that within the sequent $C,W$, it is not possible to assign a balanced box to both $\parr$-subformulae of $C$.
+%%
+%For each of the three $\tn$-subformulae, adding it to the box of a $\parr$ will change its balance by $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
+%%
+%In pairs, they add to the balance of a box by $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
+%%
+%Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$ (by Proposition~\ref{prop:tensor has disjoint subnets}), it follows that $W$ can balance the box of at most one of both $\parr$-subformulae of $C$.
+%
+%
+%Next, the vertex-gadget $\itn{v_i}$ is the formula
+%\[
+%	\itn{v_i} = \bigparr\big(C^{3m\times c(v_i)} \big)\parr 1~.
+%\]
+%It will be shown that $m$ inappropriate edge-gadgets may balance at most $3(m-1)$ constraint elements $C$.
+%
+%
+%Two edge-gadgets may balance at most three constraint elements: one weight element $W$ has three subformulae, which may each balance at most one half of a constraint element; the other halves may be balanced by different weight elements of the second edge-gadget.
+%%
+%In the same way, adding one further edge-gadget allows at most three further constraint elements to be filled, since previous edges may connect to only one half of each constraint element.
+%%
+%Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
+%%

### 2014-05-16 main/LICS.tex
very minor fixes
author version; removed garbage

@@
 
+\authorversion
+  {2014}
+  {CSL-LICS}
+  {2014}
+  {2603088.2603126}
+
 % FOR PERSONAL USE, ADD:
@@
 This effectively rules out the existence of a satisfactory notion of proof net for \capsabbrev{mll} with units---one that reduces proof equivalence to syntactic equality, and where the translation from proofs to proof nets and equality of proof nets are both tractable.
-
-%It follows that there can be no satisfactory canonical notion of proof net: if a notion of proof net were to exist where both the translation from proofs to nets and equality of proof nets are polynomial-time computable, this would imply that \capsabbrev{p}\,=\,\capsabbrev{pspace}.
 
@@
 
-%The translation from sequent proofs to proof nets is as follows.
-
-%In the sequent calculus, the rule for $\bot$ introduces a $\bot$-formula into a sequent $\Gamma$, rather than an occurrence of $\1$, as in proof nets.
-%
-%The interpretation of a proof as a proof net may attach the corresponding link to an arbitrary $\1$ in $\Gamma$.
-
 \begin{definition}
@@
 If $\Pi\toNet\links$ and $\Pi$ has conclusion $\Gamma$, then $\links$ is a proof net for $\Gamma$.
-%For a proof $\Pi$ with conclusion $\Gamma$, if $\Pi\toNet\links$ then $\links$ is a proof net for $\Gamma$.
 %
@@
 
-\begin{proposition}[\cite{HughesMLLProofNets}] %[\citeauthor{HughesMLLProofNets}, \citeyear{HughesMLLProofNets}]
+\begin{proposition}[\cite{HughesMLLProofNets}]
 \label{prop:proof nets work}
 %
-%If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
 For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$, if $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
@@
 The above proposition means that \capsabbrev{mll}\ proof equivalence is the problem of deciding equivalence of proof nets.
-%
-% We will use proof net equivalence to encode constraint logic.
 
@@
 for every vertex $v$, the total weight of its incoming edges is at least its inflow constraint, 
-%$\sum\{\kern1pt w(e)\kern1pt|\kern1pt\gamma(e)=v\kern1pt\}\geq c(v)$.
 $\sum\{w(e)\mid\gamma(e)=v\}\geq c(v)$.
@@
 \emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
-%
-%By the above proposition, \capsabbrev{ncg}-reconfiguration is unaffected by inclusion or exclusion of partial configurations.
 
@@
 
-%By Proposition~\ref{prop:partial simulates total reconfiguration} the following is then immediate.
-%
-%\begin{proposition}
-%Partial \capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
-%%\capsabbrev{pncg}-reconfiguration is \capsabbrev{pspace}-complete.
-%\end{proposition}
-
 \noindent
@@
 The complete encoding of a constraint graph $G$ will then be a sequent $\Gamma$ consisting of:
-% 1) all vertex-gadgets combined in a single formula via tensors, 2) all edge-gadgets as individual formulae, 3) a sufficient number of weight absorbers ($\1$-formulae).
+%
 \begin{enumerate}
@@
 
-%Now consider the bijection between non-root vertices and edges that associates each vertex with the edge towards its parent. 
-%
-%A second linking $\links'$ similarly establishes such a bijection.
-Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the non-root vertices in $\Gamma$.
-Finally the parity of the pair of linkings is taken to be the parity of this permutation.
-%
-% Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$.
-This therefore establishes a bijection between the edges of the tree and the non-root vertices.
-%
-%A second linking $\links'$ similarly establishes such a bijection.
-Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$.
-Finally the parity of the pair of linkings is taken to be the parity of this permutation.
-%
-%\begin{lemma}
-%	The parity is well-defined, in the sense that it does not depend on the choice of switching.
-%\end{lemma}
-%\begin{proof}
-%	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
-%	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
-%	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
-%	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
-%	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
-%	permutation of an odd number of elements is an even permutation.
-%\end{proof}
-%
-%Essentially the same argument also establishes that:
-%\begin{lemma}
-%	If two linkings are equivalent, their parity is even.
-%\end{lemma}
-
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 \[
-	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
+	C_n(k) = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)~.
 \]
@@
 \[
-	W_n(i,j) = \bigtn\big(\bot^{3i+2}\big)\parr\bigtn\big(\bot^{3(j-i)+1}\big)\parr\bigtn\big(\bot^{3(n-j)+3}\big)
+	W_n(i,j) = \bigtn\big(\bot\!^{3i+2}\big)\parr\bigtn\big(\bot\!^{3(j-i)+1}\big)\parr\bigtn\big(\bot\!^{3(n-j)+3}\big)\,.
 \]
@@
 \label{prop:element linkings}
-%The standard linkings of Definition~\ref{def:standard linkings} are proof nets.
 Standard linkings are proof nets.
@@
 \newcommand\displayOcto[1]{%
-% \NoIndent{%
    \medskip%
@@
 2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$.
-%
 
@@
 3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.
-%
 
@@
 \noindent
-4.\quad %\label{item:exchange added}
-In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
+4.\quad In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
 %
@@
 %
-It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step 6 %\ref{item:exchange needed}
-below.
+It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
 %
 The links of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
-%
 
@@
 5.\quad The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
-%
 
@@
 \noindent
-6.\quad %\label{item:exchange needed}
-The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
-%
-Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step 4 %\ref{item:exchange added}
-above.
-%
+6.\quad The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
+%
+Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step 4 above.
 
@@
 7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration.
-%\qedhere
-%\end{enumerate}
+%
 \end{proof}
@@
 %
-Let $\itn e_1$ through $\itn e_n$ be the edge-gadgets moving into or out of the empire of $\itn v$.
+Let $\itn {e_1}$ through $\itn {e_n}$ be the edge-gadgets moving into or out of the empire of $\itn v$.
 %
@@
 \end{document}
-
-%
-%Write $b(A)$ for the balance of a formula (or sequent) $A$.
-%%
-%Each constraint element in $\itn v$ is an instance of the formula $C=A\tn B$, where $b(A)\equiv 2$ and $b(B)\equiv 1\pmod 3$.
-%%
-%For $e$ inappropriate for $v$, a weight element $W=X\pr Y\pr Z$ in $\itn e$ satisfies $b(X)\equiv 2$, $b(Y)\equiv 1$, and $b(Z)\equiv 0\pmod 3$. 
-%%
-%To find a proof net for $W,C$ we need to assign balanced boxes to the par-formulae $A$ and $B$.
-%%
-%Since $e$ is inappropriate, the sequents $A,X$ and $A,X,Y$ are not balanced, while the balance $b(A,Y)\equiv 2$, $b(A,Z)\equiv
-
-%Each constraint element in $\itn{v_i}$ is an instance of the formula
-%\[
-%	C = \bigparr\big(1^{3i+2}\big) \tn \bigparr\big(1^{3(n-i)+3}\big)~.
-%\]
-%The two $\parr$-subformulae have a balance of $-3i-1$ and respectively $-3(n-i)-2$.
-%%
-%Each weight element in $\itn{e}$ is an instance of 
-%\[
-%	W = \bigtn\big(\bot^{3a+2}\big)\parr\bigtn\big(\bot^{3(b-a)+1}\big)\parr\bigtn\big(\bot^{3(n-b)+3}\big)~.
-%\]
-%We will show that within the sequent $C,W$, it is not possible to assign a balanced box to both $\parr$-subformulae of $C$.
-%%
-%For each of the three $\tn$-subformulae, adding it to the box of a $\parr$ will change its balance by $3a+1$, $3(b-a)$, and $3(n-b)+2$ respectively.
-%%
-%In pairs, they add to the balance of a box by $3b+1$ (1st and 2nd subformula), $3(a+n-b)+3$ (1st and 3rd), and $3(n-a)+2$ (2nd and 3rd).
-%%
-%Since $i\neq a,b$, and since no $\tn$-subformula of $W$ can connect to more than one $\parr$-subformula of $C$ (by Proposition~\ref{prop:tensor has disjoint subnets}), it follows that $W$ can balance the box of at most one of both $\parr$-subformulae of $C$.
-%
-%
-%Next, the vertex-gadget $\itn{v_i}$ is the formula
-%\[
-%	\itn{v_i} = \bigparr\big(C^{3m\times c(v_i)} \big)\parr 1~.
-%\]
-%It will be shown that $m$ inappropriate edge-gadgets may balance at most $3(m-1)$ constraint elements $C$.
-%
-%
-%Two edge-gadgets may balance at most three constraint elements: one weight element $W$ has three subformulae, which may each balance at most one half of a constraint element; the other halves may be balanced by different weight elements of the second edge-gadget.
-%%
-%In the same way, adding one further edge-gadget allows at most three further constraint elements to be filled, since previous edges may connect to only one half of each constraint element.
-%%
-%Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
-%%

### 2014-05-20 main/LICS.tex
fixed C/D typo

@@
 \usepackage{microtype}
-%\usepackage{enumitem}
 \usepackage[T1]{fontenc}
@@
 \usepackage{mathtools}
-
-% Sorts citations; e.g. [1], [2], [5]--[7]
-%\usepackage{cite}
-
-% More reference handling options
-%\usepackage{natbib}\renewcommand\bibfont{\footnotesize}
 
@@
 %
-It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $C$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
+It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
 %
@@
 %
-Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $C$ to $X$ added in step 4 above.
+Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $D$ to $X$ added in step 4 above.
 

### 2014-05-26 main/LICS.tex
Change variable names to avoid clash
The variable names in the statement of the octopus roll lemma
overlap with names used (for a different purpose) in the proof,
which is confusing.

@@
 \label{lem:octopus roll}
-In a proof net $\links$ for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $C$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $C$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
+In a proof net $\links$ for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $V$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $V$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}

### 2014-05-26 main/LICS.tex
Reverse text/diagram ordering in octopus roll lemma
I find it easier to follow the proof if the text precedes the
associated diagram.

@@
 \begin{proof}
-Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $C=X\tn Y$.
+Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $V=X\tn Y$.
 %
@@
 
+\noindent
+1.\quad The initial configuration is illustrated below.
+%
+Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
+%
+The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.
+
 \displayOcto{\octorollA1}
@@
 \noindent
-1.\quad The initial configuration is illustrated above. 
-%
-Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
-%
-The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.
+2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$:
 
@@
 \noindent
-2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$.
+3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$:
 
@@
 \noindent
-3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$.
+4.\quad In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
+%
+By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
+%
+It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
+%
+The links of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
 
@@
 \noindent
-4.\quad In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
-%
-By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
-%
-It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
-%
-The links of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+5.\quad The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
 
@@
 \noindent
-5.\quad The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
+6.\quad The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
+%
+Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $D$ to $X$ added in step 4 above.
 
@@
 \noindent
-6.\quad The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
-%
-Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $D$ to $X$ added in step 4 above.
+7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration:
 
 \displayOcto{\octorollA2}
-
-\noindent
-7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration.
 %

### 2014-12-01 main/LMCS.tex
Duplicate the LICS version to form the basis of the journal version

--- 2014-05-26 main/LICS.tex
@@
-\documentclass{sigplanconf}
+\documentclass{lmcs}
 
@@
 
-\let\beforesection=\relax%\medskip
-\let\aftersection=\relax%\noindent
-\let\aftersubsection=\relax%\noindent
-
 \let\capsabbrev=\uppercase
 
-\title{No proof nets for \capsabbrev{mll} with units}
-\subtitle{Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}
-
-\authorinfo
- {Willem Heijltjes}
- {University of Bath}
- {w.b.heijltjes@bath.ac.uk}
-\authorinfo
- {Robin Houston}
- {Kiln Enterprises}
- {robin@kiln.it}
-
-\exclusivelicense
-\conferenceinfo{CSL-LICS 2014}{July 14--18, 2014, Vienna, Austria} 
-\copyrightyear{2014} 
-\copyrightdata{978-1-4503-2886-9}
-\doi{2603088.2603126}
-
-\authorversion
-  {2014}
-  {CSL-LICS}
-  {2014}
-  {2603088.2603126}
-
-% FOR PERSONAL USE, ADD:
-
-%"© [Owner] [Year].
-This is the author's version of the work.
-It is posted here for your personal use.
-Not for redistribution.
-The definitive version was published in {Source Publication}, http://dx.doi.org/10.1145/{number}."
+\title{Proof equivalence in MLL is PSPACE-complete}
+
+\author{Willem Heijltjes and Robin Houston}
 
@@
 
-\category{F.4.1}{Mathematical logic and formal languages}{Mathematical logic}[Proof theory]
-\category{F.2.2}{Analysis of algorithms and problem complexity}{Nonnumerical algorithms and problems}[Complexity of proof procedures]
-
-\keywords{linear logic, proof equivalence, proof nets, constraint logic, \capsabbrev{pspace}-completeness}
+%\category{F.4.1}{Mathematical logic and formal languages}{Mathematical logic}[Proof theory]
+%\category{F.2.2}{Analysis of algorithms and problem complexity}{Nonnumerical algorithms and problems}[Complexity of proof procedures]
+
+%\keywords{linear logic, proof equivalence, proof nets, constraint logic, \capsabbrev{pspace}-completeness}
 
@@
 %------------------------------------------------------------
-\beforesection
 
@@
 
-\aftersection
-%
-The question of equivalence of proofs goes back to Lambek \cite{Lambek-1968}, who realised that the new tool of category-theoretic logic gave a notion of proof equivalence that was coarser and better-behaved than syntactic equality.
-
-Later, a striking technical innovation of linear logic was the introduction of proof nets \cite{Girard-1987,Danos-Regnier-1989}, which define a canonical form for proofs in the unitless fragment of multiplicative linear logic---two proofs are equivalent if and only if they have the same proof net---so proof nets offer a simple decision procedure for proofs in this fragment.
-This naturally raises the question whether proof nets can be extended to work in the presence of units.
-The work in this direction begins with \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996} via \cite{Lamarche-Strassburger-2006} and perhaps culminates in \cite{HughesFreeStar,HughesMLLProofNets}; but these proof nets are not canonical and must be identified up to a rewiring equivalence.
-
-So the question remains whether there exist fully canonical proof nets for full \capsabbrev{mll}.
-Canonical proof nets have been found for several other fragments of linear logic: the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
-
-In this paper we establish that the proof equivalence problem for multiplicative linear logic with units is \capsabbrev{pspace}-complete. 
-%
-This effectively rules out the existence of a satisfactory notion of proof net for \capsabbrev{mll} with units---one that reduces proof equivalence to syntactic equality, and where the translation from proofs to proof nets and equality of proof nets are both tractable.
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-\subsection*{Constraint logic and reconfiguration problems}
-
-\aftersubsection
-The proof of \capsabbrev{pspace}-completeness relies on a polynomial reduction from the configuration-to-configuration problem in non-deterministic
-\emph{constraint logic}, a graphical formalism recently introduced as a uniform tool for use in complexity reductions \cite{Demaine-Hearn-2008}.
-%
-Constraint logic is a simple graph rewriting formalism, where weighted edges may be reversed as long as the given in-flow constraint for each vertex is satisfied; the configuration-to-configuration problem asks whether two graphs are related by a sequence of rewriting steps.
-
-This is one of a class of problems called \emph{reconfiguration problems} \cite{ReconfigurationProblems}: can one solution to a given problem be transformed into another by a series of elementary changes, while remaining valid throughout?
-%
-For example, the reconfiguration problem for boolean satisfiability (SAT) asks whether one satisfying assignment can be transformed into another by changing the value of one atomic formula at a time, without passing via a non-satisfying assignment.
-%
-It is not uncommon for an \capsabbrev{np}-complete problem to have an associated reconfiguration problem that is \capsabbrev{pspace}-complete \cite{ReconfigurationProblems}; an example of this is SAT-reconfiguration.
-\capsabbrev{mll} proof equivalence may be regarded as the reconfiguration problem associated with \capsabbrev{mll} proof search, which is \capsabbrev{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
+%
+
+\cite{Lambek-1968}
+
+\cite{Girard-1987,Danos-Regnier-1989}
+\cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}
+\cite{Lamarche-Strassburger-2006}
+\cite{HughesFreeStar,HughesMLLProofNets}
+
+\cite{Hughes-vanGlabbeek-2005}
+\cite{Heijltjes-2011}
+
+\cite{Demaine-Hearn-2008}
+
+\cite{ReconfigurationProblems}
+\cite{Kanovich-1992,Lincoln-Winkler-1994}.
 
 %------------------------------------------------------------
-\beforesection
 
@@
 
-\aftersection
-%
+% TODO
+%   remove naming - work with occurrences instead
+%   explain cut-elimination
+%   define *-autonomous categories
+
+%   separate section for proof nets
+%   discuss both small-step and big-step equivalence
+%      connect jumps anywhere / to positive leaves (1,a) only
+%   example translation: proof => net
+
 The formulae of unit-only multiplicative linear logic are given by the following grammar.
@@
 
-\aftersubsection
 Proof nets provide a solution to proof equivalence for \capsabbrev{mll} without units.
@@
 
-\aftersubsection
 We will use a concise diagrammatic notation for sequents and proof nets.
@@
 
-\beforesection
+% TO DO
+%   add 3-partition example
+%
+
+% TO DO
+%	add separate section for constraint logic
+%
 
@@
 
-\aftersection
 %
@@
 
-\aftersubsection
 The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
@@
 
-\beforesection
-
 \section{Rewiring proof nets}
@@
 
-\aftersubsection
 We will discuss (and adapt) some convenient standard notions for \capsabbrev{mll} proofs and proof nets, and relate them to rewiring.
@@
 \[
-	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B} \qedhere
+	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
 \]
@@
 
-\aftersubsection
 The linearity of \capsabbrev{mll} means that in a proof or proof net, there is always a certain balance to the number of $\bot$- and $\parr$-occurrences. 
@@
 
-\aftersubsection
 Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
@@
 
-\beforesection
-
 \section{Formalising the encoding}
@@
 
-\aftersubsection
 Given a reconfiguration path $\gamma\perm\delta$ over total configurations, we will demonstrate a rewiring sequence between $\itn\gamma$ and $\itn\delta_\gamma$.
@@
 
+\pagebreak
 \noindent
@@
 
+\newpage
 \noindent
@@
 
-\aftersubsection
 It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta_\gamma$ is sound for \capsabbrev{ncg}-reconfiguration, $\gamma\perm\delta$.
@@
 
-\beforesection
-
 \section{\capsabbrev{mll} proof equivalence is \capsabbrev{pspace}-complete}
 
-\aftersection
 %
@@
 
-\acks
+%\acks
 

### 2014-12-01 main/LMCS.tex
Terminology correction

@@
 \label{lem:octopus roll}
-In a proof net $\links$ for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $V$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is naturally linked to $V$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
+In a proof net $\links$ for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $V$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is well linked to $V$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}

### 2014-12-03 main/LMCS.tex
more TODOs
Tiny addition to TODO list
Make a separate section introducing NCL
Re-did section MLL (minus *-autonomous categories)

@@
 
+% MLL
+%   remove naming - work with occurrences instead ??
+%   explain cut-elimination
+%   define *-autonomous categories
+
+% PROOF NETS
+%   separate section for proof nets
+%   discuss both small-step and big-step equivalence
+%      connect jumps anywhere / to positive leaves (1,a) only
+%   example translation: proof => net
+% 
+%   add 3-partition example
+%
+
+% CONSTRAINT LOGIC
+%	add separate section for constraint logic
+%
+
+% PARITY
+%   stress alternation over n-arity
+%   explain n-arity is safe
+%   mention alternatives ??
+%   clear up argument where possible
+
+% CONSTRUCTION
+%   clarify where possible
+
 \title{Proof equivalence in MLL is PSPACE-complete}
@@
 \begin{document}
-
-\maketitle
 
@@
 \end{abstract}
+
+\maketitle
 
@@
 
+% It should be stressed that to consider MLL proofs modulo equivalence is a choice---one that is well motivated by semantics, but a choice nonetheless.
+Interesting alternatives are available, such as polarised linear logic, tensorial logic, multi-focussing, ...
+
 %------------------------------------------------------------
@@
 
-% TODO
-%   remove naming - work with occurrences instead
-%   explain cut-elimination
-%   define *-autonomous categories
-
-%   separate section for proof nets
-%   discuss both small-step and big-step equivalence
-%      connect jumps anywhere / to positive leaves (1,a) only
-%   example translation: proof => net
-
-The formulae of unit-only multiplicative linear logic are given by the following grammar.
-%
-\setMidspace{5pt}
+In this section, we will give a brief introduction to multiplicative linear logic (MLL).
+For simplicity of exposition, we will work in the unit-only fragment of MLL.
+The formulae of this fragment are given by the following grammar.
+%
+\setMidspace{8pt}
 \[
@@
 %
-The connectives $\tn$ and $\parr$ will be considered up to associativity, and \emph{duality} $\dual A$ is via DeMorgan.
-%
-A \emph{sequent} $\Gamma,\Delta$ will be a multiset of formulae.
-%
-Within a sequent, connectives and units will be \emph{named} with distinct elements from an arbitrary set of names, e.g.\
-\[
-	\named a1\named b\parr\named c1,\named d\bot\named e\tn\named f\bot~.
-\]
-%
-This allows to 1) identify \emph{occurrences} of subformulae uniquely by the name of their root connective, e.g.\ as $\named bA$, 2) distinguish the two proofs of the above sequent while using standard multiset sequents, and 3) easily extract proof nets, as graphs using the names of connectives as vertices.
-%
-Names will often be left implicit.
-
-Proofs are constructed from the inference rules in Figure~\ref{fig:MLL}, where the names of units and connectives are preserved through inferences.
-%
-Only cut-free proofs are considered, and no cut-rule is added.
-%
-\emph{Permutations} of inference rules are displayed in Figure~\ref{fig:permutations}; the symmetric variants of the last two permutations, \emph{par-tensor} and \emph{tensor-tensor}, have been omitted.
-
-\begin{definition}
-\label{def:equivalence}
-%
-\emph{Equivalence} $(\perm)$ of proofs in (cut-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
-%
-\emph{\capsabbrev{mll}\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
-%
-\end{definition}
-
-The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
-%
-Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
+The connectives tensor ($\tn$) and par ($\parr$) will be considered up to associativity, and \emph{duality}, indicated $\dual A$, is via DeMorgan.
+%
+A \emph{sequent} $\Gamma, \Delta,\Lambda$ will be a multiset of formulae.
+%
+To distinguish different occurrences of a formula within a sequent, the connectives and units in a sequent will be \emph{named} with distinct elements from an arbitrary set of names, e.g.:\
+\[
+	\named a1\named b\parr\named c1~,~\named d\bot\named e\tn\named f\bot~.
+\]
+%
+This simple technical device is introduced for a dual purpose.
+Firstly, it distinguishes proofs that are equal up to a symmetric exchange of formulae, such as the \emph{identity} and the \emph{twist} proof of the above sequent, while the sequent rules can be given using standard multiset sequents, i.e.\ without the need for explicit \emph{exchange} rules.
+Secondly, it creates an easy way to extract proof nets, as graphs that use the names of connectives and units as vertices.
+
+Within a proof, the names of units and connectives are preserved through inferences. Where convenient, we may leave names implicit.
 
 \begin{figure}
-\quad\MLLrule b
-\hfill\MLLrule 1
-\hfill\MLLrule p
-\hfill\MLLrule t
-\quad
+\[
+		\MLLrule b
+\qquad	\MLLrule 1
+\qquad	\MLLrule p
+\qquad	\MLLrule t
+\qquad \vc{\rule{.5pt}{30pt}}
+\qquad	\MLLrule a
+\qquad	\MLLrule c
+\]
 \caption{Inference rules for unit-only \capsabbrev{mll}}
@@
 
-\begin{figure}[!tb]
-\renewcommand\scalefactor{0.88}
-\[
-\begin{array}{@{}rcl@{}}
-	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\MLLperm{bb1}}} ~\perm~ \vc{\scale{\MLLperm{bb2}}}
-		\hfill
-		\vc{\scale{\MLLperm{bp1}}} ~\perm~ \vc{\scale{\MLLperm{bp2}}}
-	}
-\\ \\[6pt]
-	\multicolumn{3}{@{}c@{}}{
-		\vc{\scale{\MLLperm{bt2}}} ~\perm~ \vc{\scale{\MLLperm{bt1}}}
-								   ~\perm~ \vc{\scale{\MLLperm{bt3}}}
-	}
-\\ \\[6pt]
-	\vc{\scale{\MLLperm{pp1}}} &\perm& \vc{\scale{\MLLperm{pp2}}}
-\\ \\[6pt]
-	\vc{\scale{\MLLperm{pt1}}} &\perm& \vc{\scale{\MLLperm{pt2}}}
-\\ \\[6pt]
-	\vc{\scale{\MLLperm{tt1}}} &\perm& \vc{\scale{\MLLperm{tt2}}}
+A one-sided sequent calculus for unit-only \capsabbrev{MLL} is given in Figure~\ref{fig:MLL}.
+The rules for identity ($\mathsf{ax}$) and cut ($\mathsf{cut}$) are admissible, and are eliminated via the identity-elimination and cut-elimination transformations displayed in Figure~\ref{fig:id-elim} and Figure~\ref{fig:cut-elim} respectively.
+The cut-elimination process in addition makes essential use of \emph{permutations} of inference rules, displayed in Figure~\ref{fig:permutations}, to match up a cut-rule with the two inferences that introduce both cut-formulae.
+Note that the symmetric variants of various transformations have been omitted from the figures, as well as permutations involving the cut-rule, which are similar to those of the tensor rule.
+
+The proof system we shall be working with is that consisting of just the introduction rules for the two units and the two connectives, the four rules $(\bot)$, $(\1)$, $(\parr)$, and $(\tn)$ of Figure~\ref{fig:MLL}.
+The problem we consider is the following.
+
+\begin{definition}
+\label{def:equivalence}
+\emph{Equivalence} $(\perm)$ of proofs in (cut-free, identity-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
+\emph{\capsabbrev{mll}\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
+\end{definition}
+
+\begin{figure}
+\[
+	\MLLelim{a0}\quad\rightsquigarrow\quad\MLLelim{a1}
+\qquad\qquad\qquad
+	\MLLelim{a2}\quad\rightsquigarrow\quad\MLLelim{a3}
+\]
+\caption{Identity-elimination transformations}
+\label{fig:id-elim}
+\end{figure}
+
+\begin{figure}
+\[
+\begin{array}{rcl}
+	\MLLelim{c0} & \rightsquigarrow & \Gamma \\ \\[5pt]
+	\MLLelim{c1} & \rightsquigarrow & \MLLelim{c2}
+\end{array}
+\]
+\caption{Cut-elimination transformations}
+\label{fig:cut-elim}
+\end{figure}
+
+\begin{figure}
+\[
+\begin{array}{c}
+	\MLLperm{bb1}\quad\sim\quad\MLLperm{bb2}
+	\qquad\qquad
+	\MLLperm{bp1}\quad\sim\quad\MLLperm{bp2}
+\\ \\[5pt]
+	\MLLperm{bt2}\quad\sim\quad\MLLperm{bt1}\quad\sim\quad\MLLperm{bt3}
+\\ \\[5pt]
+  \begin{array}{rcl}
+	\MLLperm{pp1} & \sim & \MLLperm{pp2}
+  \\ \\[5pt]
+	\MLLperm{pt1} & \sim & \MLLperm{pt2}
+  \\ \\[5pt]
+	\MLLperm{tt1} & \sim & \MLLperm{tt2}
+  \end{array}
 \end{array}
@@
 
-\subsection*{Proof nets}
+\subsection*{Star-autonomous categories}
+
+The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
+%
+Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\section*{Proof nets}
 
@@
 
-% TO DO
-%   add 3-partition example
-%
-
-% TO DO
-%	add separate section for constraint logic
-%
-
-\section{Encoding constraint logic}
-\label{sec:encoding}
+\section{Constraint logic}
+\label{sec:ncl}
 
@@
 
+\section{Encoding constraint logic}
+\label{sec:encoding}
 \noindent

### 2014-12-05 main/LMCS.tex
re-worked section "Proof Nets" (minus "notation")

@@
 \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}
+\cite{Koh-Ong-1999}
 \cite{Lamarche-Strassburger-2006}
-\cite{HughesFreeStar,HughesMLLProofNets}
+\cite{Hughes-2012-categories,Hughes-2012-nets}
 
@@
 \[
-	A,B,C \Coloneq \bot \Mid 1 \Mid A\parr B \Mid A\tn B
-\]
-%
-The connectives tensor ($\tn$) and par ($\parr$) will be considered up to associativity, and \emph{duality}, indicated $\dual A$, is via DeMorgan.
+	A,B,C \Coloneq \bot \Mid 1 \Mid A\pr B \Mid A\tn B
+\]
+%
+The connectives tensor ($\tn$) and par ($\pr$) will be considered up to associativity, and \emph{duality}, indicated $\dual A$, is via DeMorgan.
 %
@@
 \[
-	\named a1\named b\parr\named c1~,~\named d\bot\named e\tn\named f\bot~.
+	\named a1\named b\pr\named c1~,~\named d\bot\named e\tn\named f\bot~.
 \]
@@
 
-The proof system we shall be working with is that consisting of just the introduction rules for the two units and the two connectives, the four rules $(\bot)$, $(\1)$, $(\parr)$, and $(\tn)$ of Figure~\ref{fig:MLL}.
+The proof system we shall be working with is that consisting of just the introduction rules for the two units and the two connectives, the four rules $(\bot)$, $(\1)$, $(\pr)$, and $(\tn)$ of Figure~\ref{fig:MLL}.
 The problem we consider is the following.
 
-\begin{definition}
+\begin{definition}[MLL proof equivalence]
 \label{def:equivalence}
@@
 The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
-%
 Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
 
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+%------------------------------------------------------------
 
@@
 
-Proof nets provide a solution to proof equivalence for \capsabbrev{mll} without units.
-%
-For full \capsabbrev{mll}, they reduce the proof equivalence problem to a simple rewiring relation \cite{HughesMLLProofNets}.
-
-\begin{definition}
+For \capsabbrev{mll} without units, Girard's original proof nets \cite{Girard-1987} are canonical: two proofs translate into the same proof net if and only if they are equivalent.
+Since the translation from proofs to proof nets and the syntactic comparison of proof nets are both effectively computable (linear-time), proof nets provide an effective solution to the proof equivalence problem for \capsabbrev{mll} without units.
+
+There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for MLL.
+We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our PSPACE-hardness reduction.
+In this section we will discuss how this notion of proof net arises from the sequent calculus, and introduce a compact notation for it.
+
+\begin{definition}[Proof nets]
 \label{def:proof nets}
@@
 	\item
-	a \emph{linking} $\links$ is a function from the names of $\bot$-subformulae to the names of $1$-subformulae,
-
-	\item
-	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$, with for every subformula $\named aA\named c\tn\named bB$ the edges $\edge ac$ and $\edge bc$, for every subformula $\named aA\named c\parr\named bB$ either the edge $\edge ac$ or the edge $\edge bc$, and for every subformula $\named a\bot$ the edge $\edge a{\links(a)}$,
-
- 	\item
-	a \emph{proof net} $\links$ or $(\Gamma,\links)$ is a linking $\links$ such that every switching graph is acyclic and connected.
+	a \emph{linking} $\links$ is a function from the names of $\bot$-subformulae in $\Gamma$ to the names of $\Gamma$;
+
+	\item
+	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$ with:
+	\begin{itemize}
+		\item for every subformula $\named aA\named c\tn\named bB$ the edges $\edge ca$ and $\edge cb$,
+		\item for every subformula $\named aA\named c\pr\named bB$ either the edge $\edge ca$ or the edge $\edge cb$, and
+		\item for every subformula $\named a\bot$ the edge $\edge a{\links(a)}$;
+	\end{itemize}
+
+	\item
+	a linking $\links$ is \emph{correct} if every switching graph is acyclic and connected;
+
+ 	\item
+	a \emph{proof net} $(\Gamma,\links)$ consists of the sequent $\Gamma$ and a correct linking $\links$ for $\Gamma$.
 
@@
 
-\noindent
-An edge $\edge a{\links(a)}$ in a proof net or switching graph is called a \emph{link} or a \emph{jump}.
-%
-The restriction that jumps must target $\1$-occurrences (rather than any connective) is a convenience---it can be circumvented by replacing a subformula $A$ by the equivalent $A\tn\1$.
+An example proof net is given in Figure~\ref{fig:example net}.
+The edges from a $\pr$-node, which are subject to being switched, are drawn as dashed lines, while edges from a $\tn$-node are solid lines.
+An edge $\edge a{\links(a)}$ in a proof net or switching graph is called a \emph{link} or a \emph{jump}, and may also be indicated $\jump a{\links(a)}$, to match the illustrations.
+Note that unlike the axiom links of proof nets without units, a jump may connect to any connective or unit, and multiple jumps may point to the same position.
+
+\begin{figure}
+\[
+	\examplenet
+\]
+\caption{An example proof net}
+\label{fig:example net}
+\end{figure}
+
+The present notion of proof net can be seen as a direct interpretation of the sequent calculus, in the following way.
+As there are inequivalent proofs of the sequent $\bot\tn\bot,1\pr1$, some way of attaching the $\bot$-formulae to the remainder of the proof net appears necessary.
+The introduction rule for $\bot$, in Figure~\ref{fig:MLL}, attaches a $\bot$-formula to a sequent---but sequents are not explicit in proof nets.
+The notion of a jump, which attaches the $\bot$ to an arbitrary point in the sequent $\Gamma$, is then a natural generalisation of the axiom links of unit-free MLL proof nets.
+This gives the following translation from proofs to proof nets.
+
+\begin{definition}
+\label{def:proofs to nets}
+The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is a name in $\Gamma$.
+\[
+	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
+\]
+\end{definition}
+
+\begin{proposition}[\cite{Danos-Regnier-1989,Lamarche-Strassburger-2006}]
+\label{prop:correctness and sequentialisation}
+If $\Pi\toNet\links$ and $\Pi$ has conclusion $\Gamma$, then $(\Gamma,\links)$ is a proof net.
+For any proof net $(\Gamma,\links)$ there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (sequentialisation).
+\end{proposition}
+
+\begin{remark}
+A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae.
+This formulation allows an easy inclusion of cuts, which are not present in our proof nets.
+That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, may seem curious at first, but it is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
+\end{remark}
+
+\subsection*{Rewiring}
+
+The use of proof nets factors out the bottom three permutations in Figure~\ref{fig:permutations}, $(\pr-\pr$), $(\tn-\pr)$, and $(\tn-\tn)$.
+The remaining permutations, involving the $\bot$-introduction rule, impose an equivalence on proof nets, consisting of the \emph{rewiring} of jumps from one target to another.
+This is defined as follows.
+
+\begin{definition}
+\label{def:proof net equivalence}
+A \emph{rewiring} $(\perm*)$ between proof nets changes the target of exactly one jump.
+\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by rewiring.
+\end{definition}
+
+Figure~\ref{fig:rewiring} illustrates the rewiring relation in local steps.
+In the top row, a jump can be rewired across another jump and across a tensor without breaking correctness; these rewiring steps can be seen to correspond to $\bot-\bot$ and $\tn-\bot$ permutations.
+In the bottom row, rewiring a jump into the par, from $a$ or $b$, only preserves correctness if the jump can be rewired between $a$ and $b$ independently of the par.
+Intuitively, this corresponds to the $\pr-\bot$ permutation in the following way: the positions that a jump may rewire to correspond to the context of the rule introducing the $\bot$; then to have the premise of the $\pr$-introduction as its context, the jump should be able to rewire to both $a$ and $b$.
+
+\begin{figure}
+\[
+\begin{array}{cccrccc}
+	\PN b1 & \sim & \PN b2 &                          \PN t1 \quad \sim  & \PN t2 & \sim & \PN t3
+\\ \\ \\
+	\PN p1 & \sim & \PN p2 & \sim \quad \PN p3 \qquad\text{only if}\quad & \PN q1 & \sim & \PN q2
+\end{array}
+\]
+\caption{Rewiring steps}
+\label{fig:rewiring}
+\end{figure}
+
+A refinement of proof nets introduced by Hughes \cite{Hughes-2012-nets}, is that jumps may be restricted to target only $1$-formulae.
+For the remainder of the paper, unless otherwise indicated, we will assume that proof nets are of this form.
+
+\begin{proposition}[\cite{Hughes-2012-nets}]
+Any proof net is equivalent to one where the codomain of $\links$ is restricted to occurrences of the formula $1$.
+\end{proposition}
+
+A main technical advantage of this restriction is that cut-elimination can be performed in a one-shot operation, by path composition over jumps.
+Without the need to define cut-elimination by local transformations, cuts may then be omitted from proof nets altogether, which justifies the present definition.
+
+Finally, the following proposition states that equivalence is preserved when translating between proofs and proof nets, which means that \capsabbrev{mll}\ proof equivalence is equivalent to the problem of deciding equivalence of proof nets.
+
+\begin{proposition}[\cite{Blute-Cockett-Seely-Trimple-1994,Hughes-2012-nets}]
+\label{prop:proof nets work}
+%
+If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
+%
+\end{proposition}
+
+\end{document}
 
@@
 
-\begin{definition}
-\label{def:proof net equivalence}
-%
-A \emph{rewiring} $(\perm*)$ between proof nets is the redirection of exactly one link.
-%
-\emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by rewiring.
-%
-\end{definition}
-
-\noindent
-An example rewiring sequence is given in Figure~\ref{fig:net rewiring}, using the notation for proof nets introduced below.
-
-To translate a sequent proof to a proof net requires to find a target for each jump from a $\bot$-formula.
-%
-The inference rule for $\bot$ introduces it into a sequent $\Gamma$; in the corresponding proof net, any occurrence of $\1$ in $\Gamma$ may serve as the target of the jump.
-
-\begin{definition}
-\label{def:proofs to nets}
-%
-The relation $(\toNet)$ interprets a proof $\Pi$ for a sequent $\Delta$ by a linking $\links$ as follows:
-% 
-$\Pi\toNet\links$ if for each $\named a\bot$ in $\Delta$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Gamma$.
-\[
-	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
-\]
-%
-\end{definition}
-
-\begin{proposition}[\cite{Danos-Regnier-1989}, \cite{Lamarche-Strassburger-2006}]
-\label{prop:correctness and sequentialisation}
-%
-%
-If $\Pi\toNet\links$ and $\Pi$ has conclusion $\Gamma$, then $\links$ is a proof net for $\Gamma$.
-%
-For a net $\links$ for $\Gamma$, there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (\emph{sequentialisation}).
-%
-\end{proposition}
-
-\noindent
-Proof nets are a canonical representation of proofs in the absence of the units: they factor out the permutations among tensor- and par-inferences, which are the last three permutations in Figure~\ref{fig:permutations}.
-%
-Equivalence of proof nets is generated by the four remaining permutations, on $\bot$-introduction.
-
-\begin{proposition}[\cite{HughesMLLProofNets}]
-\label{prop:proof nets work}
-%
-For proofs $\Pi$, $\Pi'$ and proof nets $\links$, $\links'$, if $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
-%
-\end{proposition}
-
-\noindent
-The above proposition means that \capsabbrev{mll}\ proof equivalence is the problem of deciding equivalence of proof nets.
-
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 \[
-	\bot\tn\bot,\bot\tn\bot,\1,(\1\parr\1\parr\1)\tn\bot
+	\bot\tn\bot,\bot\tn\bot,\1,(\1\pr\1\pr\1)\tn\bot
 \]
@@
 %
-Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\parr\cdots\parr\! A_n$.
+Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\pr\cdots\pr\! A_n$.
 %
@@
 
-As the linkings above illustrate, it may occur that one subformula of a weight element $A\parr B\parr C$ fills one half of a constraint element.
+As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
 %
@@
 \begin{definition}
-A \emph{boxing} $s$ for a linking $\links$ for $\Gamma$ assigns a sub-sequent $s(v)\leq\Gamma$ to each par-vertex $\named v\parr$ such that 1) $v$ is a port of $s(v)$ and 2) boxes are either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$.
+A \emph{boxing} $s$ for a linking $\links$ for $\Gamma$ assigns a sub-sequent $s(v)\leq\Gamma$ to each par-vertex $\named v\pr$ such that 1) $v$ is a port of $s(v)$ and 2) boxes are either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$.
 \end{definition}
@@
 %
-In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $s(v)\leq\Gamma$ for each $\named v\parr$ is found by taking the conclusion $\Delta, A\named v\parr B$ of its introduction rule, below.
-\[
-	\infer[\MLLlabel p]{\Delta,A\named v\parr B}{\Delta,A,B}
+In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $s(v)\leq\Gamma$ for each $\named v\pr$ is found by taking the conclusion $\Delta, A\named v\pr B$ of its introduction rule, below.
+\[
+	\infer[\MLLlabel p]{\Delta,A\named v\pr B}{\Delta,A,B}
 \]
@@
 
-The linearity of \capsabbrev{mll} means that in a proof or proof net, there is always a certain balance to the number of $\bot$- and $\parr$-occurrences. 
+The linearity of \capsabbrev{mll} means that in a proof or proof net, there is always a certain balance to the number of $\bot$- and $\pr$-occurrences. 
 %
@@
 \begin{definition}
-The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\parr$s and commas.
+The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\pr$s and commas.
 %
@@
 
-For this argument we will work with $n$-ary connectives $\tn$ and $\parr$, and alternating formulae, i.e.\ every argument of a $\tn$ is a $\parr$ and vice versa.
+For this argument we will work with $n$-ary connectives $\tn$ and $\pr$, and alternating formulae, i.e.\ every argument of a $\tn$ is a $\pr$ and vice versa.
 %
@@
 %
-We will consider a given named sequent $\Gamma$, but will assume that it consists of a single formula, if necessary by introducing a $\parr$ at the root.
+We will consider a given named sequent $\Gamma$, but will assume that it consists of a single formula, if necessary by introducing a $\pr$ at the root.
 
@@
 
-\subsection*{Equivalence without $\parr$}
+\subsection*{Equivalence without $\pr$}
 
@@
 \[
-	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\parr\1
+	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\pr\1
 \]
@@
 \[
-	W_n(i,j) = \bigtn\big(\bot\!^{3i+2}\big)\parr\bigtn\big(\bot\!^{3(j-i)+1}\big)\parr\bigtn\big(\bot\!^{3(n-j)+3}\big)\,.
+	W_n(i,j) = \bigtn\big(\bot\!^{3i+2}\big)\pr\bigtn\big(\bot\!^{3(j-i)+1}\big)\pr\bigtn\big(\bot\!^{3(n-j)+3}\big)\,.
 \]
@@
 \label{def:standard linkings}
-For $W=W_n(i,j)=A\parr B\parr C$ a weight element,
+For $W=W_n(i,j)=A\pr B\pr C$ a weight element,
 \begin{enumerate}
@@
 \begin{proof}
-Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable box for each $\parr$. 
+Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable box for each $\pr$. 
 %
@@
 \begin{proof}
-Let $W_i=A\parr B\parr C$, $W_j=D\parr E\parr F$, and $V=X\tn Y$.
+Let $W_i=A\pr B\pr C$, $W_j=D\pr E\pr F$, and $V=X\tn Y$.
 %
@@
 %
-It is then sufficient to choose linkings so that $D\parr E\parr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
+It is then sufficient to choose linkings so that $D\pr E\pr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
 %
@@
 
-Let $e$ be inappropriate for $v$; let $C=A\tn B$ be a constraint element in $\itn v$, and $W=X\parr Y\parr Z$ weight element  in $\itn e$.
+Let $e$ be inappropriate for $v$; let $C=A\tn B$ be a constraint element in $\itn v$, and $W=X\pr Y\pr Z$ weight element  in $\itn e$.
 %

### 2014-12-09 main/LMCS.tex
separated bibliography
Reference typo
Include the “boat” diagrams

@@
 Interesting alternatives are available, such as polarised linear logic, tensorial logic, multi-focussing, ...
+This gives us interesting and important references as well.
 
@@
 
-\begin{proposition}[\cite{Blute-Cockett-Seely-Trimple-1994,Hughes-2012-nets}]
+\begin{proposition}[\cite{Blute-Cockett-Seely-Trimble-1994,Hughes-2012-nets}]
 \label{prop:proof nets work}
@@
 \end{proposition}
-
-\end{document}
 
@@
 A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint}---a natural number that may be taken to be always $2$---on each vertex.
-A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
-A rewrite step consists of the reversal of a single edge in a configuration, while preserving the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
+A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph, where at each vertex the total weight of the incoming edges is at least the inflow constraint of that vertex.
+A rewrite step consists of the reversal of a single edge in a configuration, such that all the inflow constraints remain satisfied.
 
@@
 
-The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-%
-A constraint graph may be encoded as a sequent, and a configuration as a proof net.
-%
 It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
@@
 \end{theorem}
+
+This result may seem surprising at first.
+To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed.
+
+\noindent\boat{1}\hskip3em\boat{10}
+
+\noindent\boat{11}\hskip3em\boat{20}
 
@@
 
-\subsection*{Equivalence without $\pr$}
+\subsection*{Equivalence without $\protect\pr$}
 
@@
 \bibliographystyle{plain}
-\bibliography{../refs}
+\bibliography{LMCS}
 \end{document}

### 2014-12-10 main/LMCS.tex
"notation" subsection; separated macro file

--- 2014-12-05 main/LMCS.tex
@@
 
-\usepackage{mllequiv,willemtools}
+\usepackage{LMCS_macros,willemtools}
 
@@
 % MLL
-%   remove naming - work with occurrences instead ??
-%   explain cut-elimination
+%   x remove naming - work with occurrences instead ??
+%   v explain cut-elimination
 %     define *-autonomous categories
@@
 % PROOF NETS
-%   separate section for proof nets
-%   discuss both small-step and big-step equivalence
+%   v separate section for proof nets
+%   v discuss both small-step and big-step equivalence
 %      connect jumps anywhere / to positive leaves (1,a) only
@@
 
+An example is given in Figure~\ref{fig:example trans}, where a proof is interpreted as the proof net of Figure~\ref{fig:example net}, by indicating the chosen jumps in the conclusion of each $\bot$-inference.
+(In the example, to trace formulae through inferences, the five $\bot$-formulae are kept in order from left to right, while the three $1$-formulae have explicit names.)
+
+\begin{figure}
+\[
+	\exampletrans
+\]
+\caption{Interpreting a proof as the proof net of Figure~\ref{fig:example net}}
+\label{fig:example trans}
+\end{figure}
+
 \begin{proposition}[\cite{Danos-Regnier-1989,Lamarche-Strassburger-2006}]
@@
 This formulation allows an easy inclusion of cuts, which are not present in our proof nets.
-That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, may seem curious at first, but it is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
+That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
 \end{remark}
@@
 A main technical advantage of this restriction is that cut-elimination can be performed in a one-shot operation, by path composition over jumps.
-Without the need to define cut-elimination by local transformations, cuts may then be omitted from proof nets altogether, which justifies the present definition.
+Then, without the need to define cut-elimination by local transformations, cuts may be omitted from proof nets altogether, which justifies the present definition.
 
@@
 
-\end{document}
-
-\begin{figure}
-\[
-	\netA 1223 ~\perm*~
-	\netA 1323 ~\perm*~
-	\netA 1321 ~\perm*~
-	\netA 2321
-\]
-\caption{A rewiring sequence on proof nets}
-\label{fig:net rewiring}
-\end{figure}
-
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 
-\subsection*{Notation}
-
-We will use a concise diagrammatic notation for sequents and proof nets.
-%
-The units $1$ and $\bot$ are represented by a circle~($\circ$) and a disc~($\bullet$) respectively;
-%
-formulae related by a tensor will be connected by edges; 
-formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula (and also for illustrative purposes).
-%
-For example, the following denote the same sequent:
-\[
-	\bot\tn\bot,\bot\tn\bot,\1,(\1\pr\1\pr\1)\tn\bot
-\]
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+\subsection*{Diagram notation}
+
+To concisely represent larger sequents and proof nets, we will introduce a compact diagrammatic notation.
+%
+Briefly, the units $1$ and $\bot$ are represented by a circle~($\circ$) and a disc~($\bullet$) respectively, a tensor $(\tn)$ will be indicated by an edge, and a par $(\pr)$ will be indicated by a box.
+%
+For example, the sequent below left is represented as a diagram below right.
+%
+\[
+	\bot\tn\bot~,~\bot\tn\bot~,~\1~,~(\1\pr\1\pr\1)\tn\bot
+\qquad\qquad
+\vc{\begin{tikzpicture}[x=5mm,y=-5mm,octo]
 	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (2,0) node[bullet] (c) {} -- (3,0) node[bullet] (d) {};
@@
 	\draw (7.75,0) -- (8.75,0) node[bullet] (e) {};
-\end{tikzpicture}
-\]
-The links of a proof net are added to the sequent as coloured arrows.
-%
-The following example is a proof net for the above sequent.
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+\end{tikzpicture}}
+\]
+%
+The salient features of a diagram are the connectedness by $\tn$-edges and containment within a $\pr$-box; respecting these, diagrams may be laid out in the plane in any way that is convenient.
+More formally, then, sequents and formulae are interpreted as diagrams as follows.
+%
+\[
+\begin{array}{c@{~}c@{~}c}
+	\bot & \Rightarrow & \bullet \\[5pt]
+	1	 & \Rightarrow & \circ
+\end{array}
+\qquad
+\begin{array}{rcll}
+	A_1\tn A_2\tn\dotso\tn A_n 
+	& \Rightarrow &
+	  \vc{\begin{tikzpicture}[octo]
+	    \node[draw,rounded corners] (1) at (0,0) {$A_1$};
+	    \node[draw,rounded corners] (2) at (1,0) {$A_2$};
+	    \node[draw,rounded corners] (n) at (3,0) {$A_n$};
+	    \node at (2,0) {$\dots$};
+	    \draw (1)--(2)--(1.6,0) (2.4,0)--(n);
+	    \path[use as bounding box] (-.5,-.5) rectangle (3.5,.5);
+	  \end{tikzpicture}}
+	& (A_i~\text{not a $\tn$-formula})
+\\[5pt]
+	A_1\pr A_2\pr\dotso\pr A_n
+	& \Rightarrow &
+	  \vc{\begin{tikzpicture}[octo]
+	    \node[draw,rounded corners] at (0,0) {$A_1$};
+	    \node[draw,rounded corners] at (1,0) {$A_2$};
+	    \node[draw,rounded corners] at (3,0) {$A_n$};
+	    \node at (2,0) {$\dots$};
+	    \draw[rounded corners] (-.5,-.5) rectangle (3.5,.5);
+	  \end{tikzpicture}}
+	& (A_i~\text{not a $\pr$-formula})
+\\[5pt]
+	A_1, A_2,\dotsc, A_n
+	& \Rightarrow &
+	  \vc{\begin{tikzpicture}[octo]
+	    \node[draw,rounded corners] at (0,0) {$A_1$};
+	    \node[draw,rounded corners] at (1,0) {$A_2$};
+	    \node[draw,rounded corners] at (3,0) {$A_n$};
+	    \node at (2,0) {$\dots$};
+	    \path[use as bounding box] (-.5,-.5) rectangle (3.5,.5);
+	  \end{tikzpicture}}
+	& \quad \text{where }A_i~\Rightarrow~
+	  \vc{\begin{tikzpicture}[octo]
+	    \node[draw,rounded corners] {$A_i$};
+	  \end{tikzpicture}}
+\end{array}
+\]
+%
+In the diagrammatic notation, as in the regular notation before, the jumps of a proof net are added to the sequent as coloured arrows.
+Per the restriction mentioned previously, jumps always connect a $\bot$-formula to a $1$-formula.
+The example below gives a proof net for the above sequent, presented in both notational styles.
+%
+\[
+\vc{\begin{tikzpicture}[x=6mm,y=6mm,inner sep=1pt]
+	\node (a) at (0,1) {$\bot$};
+	\node (b) at (1,0) {$\tn$};
+	\node (c) at (2,1) {$\bot$};
+	\node (d) at (3,1) {$\bot$};
+	\node (e) at (4,0) {$\tn$};
+	\node (f) at (5,1) {$\bot$};
+	\node (g) at (6,0) {$1$};
+	\node (h) at (7,3) {$1$};
+	\node (i) at (8,2) {$\pr$};
+	\node (j) at (9,1) {$\pr$};
+	\node (k) at (9,3) {$1$};
+	\node (l) at (10,0) {$\tn$};
+	\node (m) at (10,2) {$1$};
+	\node (n) at (11,1) {$\bot$};
+	\node at (0,-.5) {};
+	%
+	\draw[thick] (a)--(b)--(c) (d)--(e)--(f) (j)--(l)--(n);
+	\draw[thick,dashed] (h)--(i)--(k) (i)--(j)--(m);
+	%
+	\draw[jump] (a) -- +(0,2) to[out=90,in=90] (h);
+	\draw[jump] (c) -- +(0,2) to[out=90,in=90] (k);
+	\draw[jump] (d) -- +(0,1.5) to[out=90,in=120] (k);
+	\draw[jump] (f) -- +(0,1.5) to[out=90,in=90] ($(m)+(0,0.5)$) -- (m);
+	\draw[jump] (n) -- +(0,2.5) to[out=90,in=90] ($(g)+(0,3.5)$) -- (g);
+\end{tikzpicture}}
+\qquad\qquad
+\vc{\begin{tikzpicture}[x=5mm,y=-5mm,octo]
 	\node[circ] (1) at (6,0) {};
@@
 	\end{scope}
-\end{tikzpicture}
-\]
+\end{tikzpicture}}
+\]
+%
+The above examples illustrate how the diagrammatic notation replaces the connectives by geometric features, to allow for more convenient placement in the plane.
+The diagrams preserve the connectedness of non-switched edges, while switched components are placed within a box, so that a switching graph is obtained by replacing each box by an edge to exactly one of its components.
+
+To lay out a sequent as a diagram in two dimensions may lead to ambiguity when multiple occurrences of the same formula are present, as is the case for the formula $\bot\tn\bot$ in the above examples.
+Where necessary, this will be resolved by adding the names of $\bot$-formulae and $1$-formulae to a diagram.
+When discussing different proof nets over the same sequent, the sequent will be laid out in a consistent manner.
+
+Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Lamarche-Strassburger-2005}.
+There are 24 proof nets in total, forming two equivalence classes, each consisting of a single cyclic rewiring path.
+
+\begin{figure}
+\[
+\begin{array}{@{}ccccccccccc@{}}
+	\netA 1223 &\perm*& \netA 1323 &\perm*& \netA 1321 &\perm*& \netA 2321 &\perm*& \netA 2331 &\perm*& \netA 2131 \\ \\ \perm* &&&&&&&&&& \perm* \\ \\
+	\netA 1213 &\perm*& \netA 3213 &\perm*& \netA 3212 &\perm*& \netA 3112 &\perm*& \netA 3132 &\perm*& \netA 2132 
+	\\ \\ \\ \\ \\
+	\netA 1232 &\perm*& \netA 1332 &\perm*& \netA 1312 &\perm*& \netA 2312 &\perm*& \netA 2313 &\perm*& \netA 2113 \\ \\ \perm* &&&&&&&&&& \perm* \\ \\
+	\netA 1231 &\perm*& \netA 3231 &\perm*& \netA 3221 &\perm*& \netA 3121 &\perm*& \netA 3123 &\perm*& \netA 2123
+	\\ \\
+\end{array}
+\]
+\caption{All proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$}
+\label{fig:_*_,1,1,1,_*_}
+\end{figure}
+
+\section{Proof search complexity}
+
+% TO DO:
+%	n-fold bottoms & ones (below)
+%   3-sat reduction for proof search
+
+\cite{Lincoln-Mitchell-Scedrov-Shankar-1992} % NP-completeness with weakening
+\cite{Kanovich-1992} % NP-completeness for MLL
+\cite{Lincoln-Winkler-1994} % NP-completeness for MLL without atoms
+
+\end{document}
 
@@
 \]
+
+\end{document}
 

### 2014-12-11 main/LMCS.tex
encoding 3-partition, pics for the boat

@@
 %      connect jumps anywhere / to positive leaves (1,a) only
-%     example translation: proof => net
-% 
-%     add 3-partition example
+%   v example translation: proof => net
+% 
+%   v add 3-partition example
 %
@@
 
-\section{\capsabbrev{mll}}
-
-In this section, we will give a brief introduction to multiplicative linear logic (MLL).
-For simplicity of exposition, we will work in the unit-only fragment of MLL.
+\section{\protect\capsabbrev{mll}}
+
+In this section, we will give a brief introduction to multiplicative linear logic (\capsabbrev{mll}).
+For simplicity of exposition, we will work in the unit-only fragment of \capsabbrev{mll}.
 The formulae of this fragment are given by the following grammar.
@@
 
-A one-sided sequent calculus for unit-only \capsabbrev{MLL} is given in Figure~\ref{fig:MLL}.
+A one-sided sequent calculus for unit-only \capsabbrev{mll} is given in Figure~\ref{fig:MLL}.
 The rules for identity ($\mathsf{ax}$) and cut ($\mathsf{cut}$) are admissible, and are eliminated via the identity-elimination and cut-elimination transformations displayed in Figure~\ref{fig:id-elim} and Figure~\ref{fig:cut-elim} respectively.
@@
 
-\begin{definition}[MLL proof equivalence]
+\begin{definition}[\capsabbrev{mll} proof equivalence]
 \label{def:equivalence}
@@
 
-There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for MLL.
+There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for \capsabbrev{mll}.
 We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our PSPACE-hardness reduction.
@@
 	\item
-	a \emph{switching graph} for $\links$ is an undirected graph over the names of $\Gamma$ with:
+	a \emph{switching graph} for $\Gamma$ and $\links$ is an undirected graph over the names of $\Gamma$ with:
 	\begin{itemize}
@@
 The introduction rule for $\bot$, in Figure~\ref{fig:MLL}, attaches a $\bot$-formula to a sequent---but sequents are not explicit in proof nets.
-The notion of a jump, which attaches the $\bot$ to an arbitrary point in the sequent $\Gamma$, is then a natural generalisation of the axiom links of unit-free MLL proof nets.
+The notion of a jump, which attaches the $\bot$ to an arbitrary point in the sequent $\Gamma$, is then a natural generalisation of the axiom links of unit-free \capsabbrev{mll} proof nets.
 This gives the following translation from proofs to proof nets.
@@
 %
-The above examples illustrate how the diagrammatic notation replaces the connectives by geometric features, to allow for more convenient placement in the plane.
+The above examples illustrate how the diagrammatic notation replaces the connectives by geometric features to allow for more convenient placement in the plane.
 The diagrams preserve the connectedness of non-switched edges, while switched components are placed within a box, so that a switching graph is obtained by replacing each box by an edge to exactly one of its components.
@@
 To lay out a sequent as a diagram in two dimensions may lead to ambiguity when multiple occurrences of the same formula are present, as is the case for the formula $\bot\tn\bot$ in the above examples.
-Where necessary, this will be resolved by adding the names of $\bot$-formulae and $1$-formulae to a diagram.
+Where necessary, this will be resolved by adding the names of chosen $\bot$-formulae and $1$-formulae to a diagram.
 When discussing different proof nets over the same sequent, the sequent will be laid out in a consistent manner.
@@
 
-\section{Proof search complexity}
-
-% TO DO:
-%	n-fold bottoms & ones (below)
-%   3-sat reduction for proof search
-
-\cite{Lincoln-Mitchell-Scedrov-Shankar-1992} % NP-completeness with weakening
-\cite{Kanovich-1992} % NP-completeness for MLL
-\cite{Lincoln-Winkler-1994} % NP-completeness for MLL without atoms
-
-\end{document}
-
-We will denote by $A^n$ the sequent consisting of $n$ occurrences of a formula $A$.
-%
-Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\pr\cdots\pr\! A_n$.
-%
-In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par (or a sequent) over only $1$-formulae, $\bigparr(\1^n)$.
-%
-A linking between $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
-\[
-\begin{tikzpicture}[x=-5mm,y=5mm,octo]
-	\node[big_] (A) at (-1,2) {};
-	\node[big1] (!) at (-1,0) {};
-	\node at (.5,1) {$\Rightarrow$};
-	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
-	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
-	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
-	\begin{scope}[thepink,->]
-			\draw[big>] (A) to (!.center);
-			\draw[bend right=10] (a) to (1.center);
-			\draw[bend right=10] (b) to (2.center);
-			\draw[bend right=10] (c) to (3.center);
-	\end{scope}
-\end{tikzpicture}
-\]
-Two formulae $\bigtn(\bot^{i+1})$ and $\bigtn(\bot^{j+1})$ may together connect to a formula $\bigparr(\1^{i+j+1})$, as illustrated below for $i=2$ and $j=3$.
-%
-Nodes will be labelled $i'$ for $i+1$, so that both the abbreviated formulae and the arithmetic of connecting them remain intuitive.
-%
+%------------------------------------------------------------
+
+\section{Proof complexity}
+
+The problem of deciding whether a given \capsabbrev{mll} sequent is provable is \capsabbrev{np}-complete.
+This was shown first for an extension of \capsabbrev{mll} with weakening \cite{Lincoln-Mitchell-Scedrov-Shankar-1992}, and subsequently for unit-free \capsabbrev{mll} \cite{Kanovich-1992} and for unit-only  \capsabbrev{mll} \cite{Lincoln-Winkler-1994}---note that since \capsabbrev{mll} is conservative over both its unit-only and its unit-free fragment, each of the latter two implies \capsabbrev{np}-completeness for provability in full \capsabbrev{mll}.
+
+Both Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994} use a reduction from (a variant of) the 3-Partition problem to show  \capsabbrev{np}-hardness.
+Such reductions provide a good illustration of how the linearity of \capsabbrev{mll} can be used to encode combinatoric problems.
+In this section we will discuss a similar reduction from 3-Partition.
+
+To encode simple numerical properties in \capsabbrev{mll}, our primary tools will be formulae of the form $\bot\tn\dotso\tn\bot$ and $1\pr\dotso\pr1$.
+In particular, two formulae of the former kind with $i+1$ and $j+1$ $\bot$-occurrences respectively may form a proof net with a formula $1\pr\dotso\pr1$ if and only if the latter counts $i+j+1$ occurrences of the formula $1$.
+This is illustrated below left for $i=2$ and $j=3$; in the following, we will introduce the abbreviated notation used below right.
 \[
@@
   \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\draw (0,0) node[bullet] (a) {}--
-		  (1,0) node[bullet] (b) {}--
-		  (2,0) node[bullet] (c) {};
-	\draw (4,0) node[bullet] (d) {}--
-		  (5,0) node[bullet] (e) {}--
-		  (6,0) node[bullet] (f) {}--
-		  (7,0) node[bullet] (g) {};
+	\foreach \x/\i in {0/a,1/b,2/c,4/d,5/e,6/f,7/g} {\node[bullet] (\i) at (\x,0) {};}
 	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
+	\draw (a)--(b)--(c) (d)--(e)--(f)--(g);
+	\draw[rounded corners] ($(1) + (-.8,-.8)$) rectangle ($(6) + (.8,.8)$);
 	\begin{scope}[thepink,->]
@@
 	\end{scope}
-  \end{tikzpicture}
-}
-\quad\Rightarrow\quad
-\vc{
-  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-1,0) {$2'$};
-	\node[big_] (B) at ( 1,0) {$3'$};
-	\node[big1] (!) at ( 0,3) {$5'$};
+	\node[big_] (A) at (14,0) {$2'$};
+	\node[big_] (B) at (16,0) {$3'$};
+	\node[big1] (!) at (15,3) {$5'$};
+	\draw[rounded corners] ($(!) + (-1.2,-.8)$) rectangle ($(!) + (1.2,.8)$);
 	\begin{scope}[thepink,->,big>]
@@
 \]
-%
-A path in a proof net or switching graph is indicated $\path ab$, and illustrated as below.
-%
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[bullet] (a) at (0,0) {}; \node[bullet] (b) at (2,0) {}; \draw[dashed] (a)--(b);
+By $A^n$ we will denote the sequent consisting of $n$ occurrences of a formula $A$.
+Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\pr\cdots\pr\!
+A_n$.
+In diagrammatic notation, a big disc labelled $n'$ will represent the formula $\bigtn(\bot^{n+1})$, and a big circle labelled $n'$ will represent the sequent $\1^{n+1}$.
+A formula $\bigparr(\1^{n+1})$ is represented by a disc enclosed in a box.
+
+\[
+\begin{array}{ccc}
+	\1^{n+1}			&\Rightarrow& \bignodes1 \\[5pt]
+	\bigparr(\1^{n+1})	&\Rightarrow& \bignodes2 \\[5pt]
+	\bigtn(\bot^{n+1})  &\Rightarrow& \bignodes3 \\[5pt]
+\end{array}
+\qquad\qquad\qquad
+\vc{
+\begin{tikzpicture}[x=5mm,y=8mm,octo]
+	\node[big_] (A) at (-1,2) {};
+	\node[big1] (!) at (-1,0) {};
+	\node at (.5,1) {$=$};
+	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (6,2) -- (7,2) node[bullet] (c) {}; 
+	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (7,0) {};
+	%\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
+	\node at (5,2) {$\dots$}; \node at (5,0) {$\dots$};
+	\begin{scope}[thepink,->]
+			\draw[big>] (A) to (!);
+			\draw[bend right=10] (a) to (1);
+			\draw[bend right=10] (b) to (2);
+			\draw[bend right=10] (c) to (3);
+	\end{scope}
+\end{tikzpicture}}
+\]
+A linking between formulae $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated above right.
+For the moment, we will not distinguish between the $n!$ different ways in which such a linking can be made, but when the distinction becomes relevant we will make an explicit choice.
+
+The intention behind the chosen notation is that both the abbreviated formulae and the arithmetic of connecting them remain intuitive.
+Specifically, the following is a proof net if and only if $n=i_1+\dotso+i_k$.
+\[
+  \vc{\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big_] (A) at (-2,0) {$i_1'$};
+	\node[big_] (B) at ( 2,0) {$i_k'$};
+	\node[big1] (!) at ( 0,3) {$n'$};
+	\node at (0,0) {$\dots$};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=15] (A) to (!);
+		\draw[bend left=15]  (B) to (!);
+	\end{scope}
+  \end{tikzpicture}}
+\]
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+
+\subsection*{Encoding 3-Partition}
+
+An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$, for which the decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$.
+It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, to relax the problem to ask whether there is a partitioning into \emph{subsets} with sum $k$.
+The 3-Partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.
+
+A 3-Partition instance $I$ is encoded by a sequent consisting of:
+\begin{itemize}
+	\item a formula $\bigtn(\bot^{i+1})$ for each $i\in I$, and
+	\item the formula $\bigtn(K^n)$ where $K=\bigparr(\1^{k+1})$.
+\end{itemize}
+The construction, including a proof net providing a solution, is illustrated below.
+
+\[
+\begin{tikzpicture}[x=10mm,y=8mm,octo]
+	\node[big1] (a) at (2,0) {$k'$};
+	\node[big1] (b) at (5,0) {$k'$};
+	\node[big1] (c) at (11,0) {$k'$};
+	\draw[rounded corners] (1,-.5) rectangle (3,.5);
+	\draw[rounded corners] (4,-.5) rectangle (6,.5);
+	\draw[rounded corners] (10,-.5) rectangle (12,.5);
+	\draw (3,0)--(4,0) (6,0)--(7,0) (9,0)--(10,0);
+	%\draw[dash pattern=on 1pt off 2pt] (7.5,0)--(8.5,0) (7.5,2)--(8.5,2);
+	\node at (8,0) {$\dots$}; \node at (8,2) {$\dots$};
+	%
+	\foreach \i in {1,...,6} {
+		\node[big_] (\i) at (\i,2) {$i'_{\i}$};
+	}
+	\node[big_] (7) at (10,2) {};
+	\node[big_] (8) at (11,2) {};
+	\node[big_] (9) at (12,2) {$i'_{3n}$};
+	%
+	\begin{scope}[thepink,->,big>]
+	\foreach \i/\a in {1/a,4/b,7/c} \draw (\i) to[bend right=20] (\a);
+	\foreach \i/\a in {2/a,5/b,8/c} \draw (\i) -- (\a);
+	\foreach \i/\a in {3/a,6/b,9/c} \draw (\i) to[bend left=20] (\a);
+	\end{scope}
 \end{tikzpicture}
-\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
-\end{tikzpicture}
-\]
+\]
+
+The idea behind the encoding is that in a proof net, the jumps from a formula for $i$ must connect to the same instance of $K$, since otherwise a switching graph with a cycle is created.
+The number of $\bot$-occurrences and $1$-occurrences in the sequent then requires that each formula $K$ is linked to by exactly three formulae.
+A proof net for a sequent that encodes a 3-Partition instance $I$ then directly gives a solution to $I$.
+
+\newpage
+
+\begin{figure}
+\[
+\begin{array}{ccccccccc}
+	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
+	\\ \\ &&&&&&&& \perm \\ \\
+	\boat5 &\perm& \boat6 &\perm& \boat7 &\perm& \boat8 &\perm& \boat9
+\end{array}
+\]
+\caption{The boat}
+\label{fig:boat}
+\end{figure}
+
+\begin{figure}
+\[
+	\boats
+\]
+\caption{Nested boats}
+\label{fig:boats}
+\end{figure}
 
@@
 
+% TO DO: FIND A PLACE FOR:
+%
+% A path in a proof net or switching graph will be indicated $\path ab$, and illustrated as below.
+%\[
+%\begin{tikzpicture}[x=5mm,y=5mm,octo]
+%	\node[bullet] (a) at (0,0) {}; \node[bullet] (b) at (2,0) {}; \draw[dashed] (a)--(b);
+%\end{tikzpicture}
+%\qquad
+%\begin{tikzpicture}[x=5mm,y=5mm,octo]
+%	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
+%\end{tikzpicture}
+%\]
+
 %
@@
 
-The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{MLL} proof equivalence, as described informally in the previous section, is correct.
+The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof equivalence, as described informally in the previous section, is correct.
 

### 2015-01-30 main/LMCS.tex
Correct references

@@
 \begin{remark}
-A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae.
+A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1996} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae.
 This formulation allows an easy inclusion of cuts, which are not present in our proof nets.
@@
 
-\begin{proposition}[\cite{Blute-Cockett-Seely-Trimble-1994,Hughes-2012-nets}]
+\begin{proposition}[\cite{Blute-Cockett-Seely-Trimble-1996,Hughes-2012-nets}]
 \label{prop:proof nets work}
@@
 
-Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Lamarche-Strassburger-2005}.
+Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Strassburger-Lamarche-2004}.
 There are 24 proof nets in total, forming two equivalence classes, each consisting of a single cyclic rewiring path.

### 2015-01-30 Boat/test.tex
finished 3-PART, started NCL section

\documentclass{beamer}

\usepackage{xargs}
\usepackage{tikz}

\colorlet{darkred}{red!80!black}

\tikzset{->-/.style={decoration={
  markings,
  mark=at position 1 with {\arrow{>}}},postaction={decorate}}}
\tikzset{-<-/.style={decoration={
  markings,
  mark=at position 0.2 with {\arrow{<}}},postaction={decorate}}}

\definecolor{thegrey1}{rgb}{.72,.72,.72}
\definecolor{thegrey2}{rgb}{.50,.50,.50}
\definecolor{theblue}{rgb}{0,.24,.98}

\tikzstyle{nclnode}=[draw=thegrey2,fill=thegrey1,circle,inner sep=0pt, minimum size=4pt]
\tikzstyle{ncl1}=[line cap=round,line width=1.5pt,darkred]
\tikzstyle{ncl2}=[line cap=round,line width=3pt,theblue]

\begin{document}

%--------------------------------
\begin{frame}

\[
\scalebox{1.6}{
\begin{tikzpicture}[x=6mm,y=10mm]
	\foreach \a/\p in 
		{a/{(0,2)},b/{(3,3)},c/{(3,1)},d/{(6,3)},e/{(6,1)},f/{(4,2)},1/{(3,4.5)},0/{(3,-.5)}}
		{\node[nclnode,minimum size=5pt,outer sep=2pt] (\a) at \p {};}
	%
	\begin{scope}[ncl1,->,cap = butt]
	  \draw<1-2> (a) to[out=60,in=180] (b);  \draw<3-> (b) to[out=180,in=60] (a);
	  \draw<1-8> (c) to[in=300,out=180] (a); \draw<9-> (a) to[out=300,in=180] (c);
	  \draw<1-2> (d) -- (b); \draw<3-> (b) -- (d);
	  \draw<1-8> (c) -- (e); \draw<9-> (e) -- (c);
	  \draw<1-5> (d) -- (e); \draw<6-> (e) -- (d);
	\end{scope}
	%
	\begin{scope}[ncl2,->,cap = butt]
	  \draw<1-3,8-10> (f) -- (a); \draw<4-7> (a)--(f);
	  \draw<1>   (b) -- (1); \draw<2-> (1)--(b);
	  \draw<1-9> (0) -- (c); \draw<10->(c)--(0);
	  \draw<1-6> (f) -- (d); \draw<7-> (d)--(f);
	  \draw<1-4> (e) -- (f); \draw<5-> (f)--(e);
	\end{scope}
	%
	\foreach \a/\p in 
		{a1/{(2,1.5)},b1/{(1.5,2)},c1/{(2.5,2)},d1/{(1.5,2.5)},e1/{(2.5,2.5)},f1/{(2,2.16)}}
		{\node<11>[nclnode,minimum size=3pt,outer sep=1pt] (\a) at \p {};}
	%
	\begin{scope}[ncl1,line width=.8pt,->,cap = butt]
	  \draw<11> (a1) to[out=150,in=270] (b1); 
	  \draw<11> (c1) to[in=30,out=270] (a1);
	  \draw<11> (d1) -- (b1);
	  \draw<11> (c1) -- (e1);
	  \draw<11> (d1) -- (e1);
	\end{scope}
	%
	\begin{scope}[ncl2,line width=1pt,->,cap = butt]
	  \draw<11> (f1) -- (a1);
	  \draw<11> (f1) -- (d1);
	  \draw<11> (e1) -- (f1);
	\end{scope}
	\draw<11>[ncl2,->,line width=2pt,cap = butt] (b1) -- (a);
	\draw<11>[ncl2,->,line width=2pt,cap = butt] (f) -- (c1);
	%
\end{tikzpicture}
}
\]

\end{frame}

\end{document}

### 2015-01-30 main/LMCS.tex
finished 3-PART, started NCL section

--- 2014-12-11 main/LMCS.tex
@@
 \label{def:proofs to nets}
-The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is a name in $\Gamma$.
+The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, $\links(a)$ is a name in $\Gamma$, where $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below.
 \[
@@
 \begin{remark}
-A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae.
-This formulation allows an easy inclusion of cuts, which are not present in our proof nets.
-That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
+The proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} may appear to be formulated in quite a distinct way from our presentation, in particular in that their jumps from $\bot$-vertices connect to edges, rather than vertices.
+The difference is only superficial: in their proof nets, vertices represent inferences, and edges represent formulae; in both presentations, therefore, jumps may be seen to attach to formulae.
+This way of attaching jumps (to formulae, rather than inferences) is the natural choice also in their setting, which is motivated categorically, where $\bot$-introduction corresponds to the isomorphism $A\to A\pr\bot$.
 \end{remark}
@@
 
-Figure~\ref{fig:rewiring} illustrates the rewiring relation in local steps.
-In the top row, a jump can be rewired across another jump and across a tensor without breaking correctness; these rewiring steps can be seen to correspond to $\bot-\bot$ and $\tn-\bot$ permutations.
+The above definition, which is due to Hughes~\cite{Hughes-2012-nets}, gives a ``big-step'' rewrite relation for equivalence.
+In turn, this rewiring relation is generated by smaller local steps, which correspond more closely to the permutations in the sequent calculus.
+These smaller steps are illustrated in Figure~\ref{fig:rewiring}.
+In the top row, a jump can be rewired across another jump and across a tensor without breaking correctness; these rewiring steps can be seen to correspond to $(\bot-\bot)$ and $(\tn-\bot)$ permutations.
 In the bottom row, rewiring a jump into the par, from $a$ or $b$, only preserves correctness if the jump can be rewired between $a$ and $b$ independently of the par.
-Intuitively, this corresponds to the $\pr-\bot$ permutation in the following way: the positions that a jump may rewire to correspond to the context of the rule introducing the $\bot$; then to have the premise of the $\pr$-introduction as its context, the jump should be able to rewire to both $a$ and $b$.
+Intuitively, this corresponds to the $(\pr-\bot)$ permutation in the following way: the positions that a jump may rewire to correspond to the context of the rule introducing the $\bot$; then to have the premise of the $\pr$-introduction as its context, the jump should be able to rewire to both $a$ and $b$.
+
+That the rewiring relation is generated by the small-step relation in Figure~\ref{fig:rewiring} is a main theorem in \cite{Hughes-2012-nets}.
+
+\begin{proposition}[\cite{Hughes-2012-nets}]
+Rewiring $(\perm*)$ is generated by the local steps in Figure~\ref{fig:rewiring}.
+\end{proposition}
 
@@
 
-A refinement of proof nets introduced by Hughes \cite{Hughes-2012-nets}, is that jumps may be restricted to target only $1$-formulae.
+A further refinement in the proof nets introduced by Hughes \cite{Hughes-2012-nets}, is that jumps may be restricted to target only $1$-formulae.
 For the remainder of the paper, unless otherwise indicated, we will assume that proof nets are of this form.
@@
 %
-The salient features of a diagram are the connectedness by $\tn$-edges and containment within a $\pr$-box; respecting these, diagrams may be laid out in the plane in any way that is convenient.
-More formally, then, sequents and formulae are interpreted as diagrams as follows.
-%
-\[
-\begin{array}{c@{~}c@{~}c}
-	\bot & \Rightarrow & \bullet \\[5pt]
-	1	 & \Rightarrow & \circ
-\end{array}
-\qquad
-\begin{array}{rcll}
+The salient features of a diagram are the connectedness by $\tn$-edges and containment within a $\pr$-box.
+Respecting these, we will lay out a diagram in the plane in any way that is convenient, while ensuring (of course) that the layout is kept consistent when comparing different proof nets over the same sequent.
+More formally, then, sequents and formulae are interpreted as diagrams as follows:
+%
+\[
+  1\mathrel\Rightarrow\circ, \quad  \bot\mathrel\Rightarrow\bullet, \quad \text{and if}\quad
+	A_i~\Rightarrow~
+	  \vc{\begin{tikzpicture}[octo]
+	    \node[draw,rounded corners] {$A_i$};
+	  \end{tikzpicture}}
+  \quad\text{then}
+\]
+\[
+\begin{array}{@{}rcll@{}}
 	A_1\tn A_2\tn\dotso\tn A_n 
@@
 	  \end{tikzpicture}}
-	& (A_i~\text{not a $\tn$-formula})
-\\[5pt]
+	& \text{where no $A_i$ is a $\tn$-formula}
+\\ \\ 
 	A_1\pr A_2\pr\dotso\pr A_n
@@
 	  \end{tikzpicture}}
-	& (A_i~\text{not a $\pr$-formula})
-\\[5pt]
+	& \text{where no $A_i$ is a $\pr$-formula}
+\\ \\
 	A_1, A_2,\dotsc, A_n
@@
 	  \end{tikzpicture}}
-	& \quad \text{where }A_i~\Rightarrow~
-	  \vc{\begin{tikzpicture}[octo]
-	    \node[draw,rounded corners] {$A_i$};
-	  \end{tikzpicture}}
+	& 
 \end{array}
@@
 To encode simple numerical properties in \capsabbrev{mll}, our primary tools will be formulae of the form $\bot\tn\dotso\tn\bot$ and $1\pr\dotso\pr1$.
-In particular, two formulae of the former kind with $i+1$ and $j+1$ $\bot$-occurrences respectively may form a proof net with a formula $1\pr\dotso\pr1$ if and only if the latter counts $i+j+1$ occurrences of the formula $1$.
-This is illustrated below left for $i=2$ and $j=3$; in the following, we will introduce the abbreviated notation used below right.
+In particular, two formulae $A$ and $B$ of the former kind may form a proof net with one $C$ of the latter kind if and only if the total number of $\bot$-occurrences in $A$ and $B$ exceeds the number of $1$-occurrences in $C$ by 1: each 1-occurrence must be linked to by a $\bot$, and one additional $\bot$ is needed to connect $A$ and $B$.
+We will capture this more generally by counting the number of $\bot$-occurrences in $A$ as $i+1$, so that if $j+1$ is the number of $\bot$-occurrences in $B$, the number of $1$-occurrences in $C$ must be $i+j+1$.
+Below left is an illustration for $i=2$ and $j=3$.
+In the following, we will introduce an abbreviated notation, illustrated below right.
 \[
@@
 A formula $\bigparr(\1^{n+1})$ is represented by a disc enclosed in a box.
+This extends our diagrammatic notation as follows.
 
@@
 \begin{array}{ccc}
-	\1^{n+1}			&\Rightarrow& \bignodes1 \\[5pt]
-	\bigparr(\1^{n+1})	&\Rightarrow& \bignodes2 \\[5pt]
-	\bigtn(\bot^{n+1})  &\Rightarrow& \bignodes3 \\[5pt]
+	\1^{n+1}			&\Rightarrow& \bignodes1 \\[10pt]
+	\bigparr(\1^{n+1})	&\Rightarrow& \bignodes2 \\[10pt]
+	\bigtn(\bot^{n+1})  &\Rightarrow& \bignodes3 \\[10pt]
 \end{array}
@@
 
-An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$, for which the decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$.
-It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, to relax the problem to ask whether there is a partitioning into \emph{subsets} with sum $k$.
+An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$.
+The decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$.
+It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, so that any partitioning into \emph{subsets} with sum $k$ is a solution, since each subset of sum $k$ necessarily has $3$ elements.
 The 3-Partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.
 
+We will give a simple encoding of 3-partition in MLL proof search, similar to those of Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994}.
 A 3-Partition instance $I$ is encoded by a sequent consisting of:
@@
 \end{itemize}
-The construction, including a proof net providing a solution, is illustrated below.
+A solution to the 3-partition problem is encoded as a proof net as follows.
+If the numbers $a$, $b$, and $c$ are assigned to a triple corresponding to a formula $K_j$, then the corresponding formulae have $a+1$, $b+1$, and $c+1$ occurrences of $\bot$, and $k+1=a+b+c+1$ occurrences of $\1$, respectively.
+Then as described previously, there is a proof net for these formulae, obtained by attaching each jump to a distinct $\1$, with the exception of three jumps, one each from $a$, $b$, and $c$, overlapping on exactly one intance.
+
+The construction is illustrated below, where the numbers $i$ are conveniently ordered to give the solution $(i_1,i_2,i_3)$, $(i_4,i_5,i_6)$, etc.
 
@@
 
-The idea behind the encoding is that in a proof net, the jumps from a formula for $i$ must connect to the same instance of $K$, since otherwise a switching graph with a cycle is created.
-The number of $\bot$-occurrences and $1$-occurrences in the sequent then requires that each formula $K$ is linked to by exactly three formulae.
-A proof net for a sequent that encodes a 3-Partition instance $I$ then directly gives a solution to $I$.
-
-\newpage
-
-\begin{figure}
-\[
-\begin{array}{ccccccccc}
-	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
-	\\ \\ &&&&&&&& \perm \\ \\
-	\boat5 &\perm& \boat6 &\perm& \boat7 &\perm& \boat8 &\perm& \boat9
-\end{array}
-\]
-\caption{The boat}
-\label{fig:boat}
-\end{figure}
-
-\begin{figure}
-\[
-	\boats
-\]
-\caption{Nested boats}
-\label{fig:boats}
-\end{figure}
-
-\end{document}
+The correctness condition ensures that every proof net on a sequent encoding a 3-partition problem gives a solution that problem.
+If two jumps from a formula encoding a number $i$ connect to different formulae $K_j$ and $K_m$, a cycle is created immediately.
+Thus, the jumps from each $i$ must all connect to the same $K$, and the number of occurrences of $\bot$ and $\1$ in the encoding then ensures that when the formulae for $i_a$, $i_b$, and $i_c$, connect to one formulae $K$, their values sum to $k$, $i_a+i_b+i_c=k$.
+
+The encoding of 3-partition serves to illustrate how simple numerical constraints can be encoded in proof nets: by matching up a given number of $\bot$-occurrences and $\1$-occurrences and by separating formulae of the form $\bigparr(\1^n)$ by a tensor.
+This idea will form the basis of our encoding of non-deterministic constraint logic.
+First, we will introduce the latter.
 
@@
 
-%
-\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reduction.
-%
-A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint}---a natural number that may be taken to be always $2$---on each vertex.
-A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph.
-A rewrite step consists of the reversal of a single edge in a configuration, while preserving the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.
-
-Figure~\ref{fig:NCL example} shows an example rewrite sequence in a part of a constraint graph.
-%
-The central node has inflow constraint 2, the thick blue edge has weight 2, and the thinner red edges have weight 1.
+\emph{Non-deterministic constraint logic} (NCL) \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, introduced as a convenient tool for \capsabbrev{pspace}-hardness reduction.
+It is exactly for this purpose that we shall use it.
+
+The graphs of NCL, called \emph{constraint graphs}, have directed, weighted edges, and a rewrite step (or \emph{move}) consists of reversing the direction of exactly one edge.
+Each vertex in a constraint graph has an \emph{inflow constraint}, a natural number value, and moves are required to preserve the property that the \emph{inflow} at each vertex, the sum weight of its incoming edges, never drops below the inflow constraint (i.e.\ the inflow constraint dictates a \emph{minimum} inflow).
 
 The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
+This problem is PSPACE-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.
+
+We will need no such restrictions, and will encode the general case.
+However, for simplicity of exposition, in the examples of constraint graphs in this section we will use the following conventions.
+Edges will have weight 1 or 2; those of weight 1 are drawn as thin red arrows, and those of weight 2 as thicker blue arrows.
+Vertices with inflow constraint 2 are drawn as grey circles.
+For convenience, we will assume that dangling edges are connected to vertices of weight 0, which are omitted from illustrations.
+
+An example rewrite sequence is given in Figure~\ref{fig:NCL example}.
+This particular specimen encodes a logical conjunction, and is not unlike an \textsc{and}-gate: in order to invert the weight 2 edge on the right, both weight 1 edges on the left must be inverted first.
+
+\begin{figure}
+\[
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,->-] (3,0) -- (5,2);
+	\draw[ncl1,->-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\quad\perm*\quad
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,->-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\quad\perm*\quad
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,->-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,-<-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\quad\perm*\quad
+\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
+	\draw[ncl2,-<-] (0,0) -- (3,0);
+	\draw[ncl1,-<-] (3,0) -- (5,2);
+	\draw[ncl1,-<-] (3,0) -- (5,-2);
+	\node[nclnode] at (3,0) {};
+\end{tikzpicture}}
+\]
+\caption{A series of reconfiguration steps in a constraint graph}
+\label{fig:NCL example}
+\end{figure}
+
 %
@@
 
-\begin{figure}
-$
-~
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,->-] (3,0) -- (5,2);
-	\draw[ncl1,->-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\hfill\perm*\,
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,->-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\hfill\perm*\,
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,-<-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\hfill\perm*\,
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,-<-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,-<-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-~
-$
-
-\smallskip
-\caption{A series of reconfiguration steps in a constraint graph}
-\label{fig:NCL example}
-\end{figure}
-
 \begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
@@
 We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
+
+\newpage
+
+\begin{figure}
+\[
+\begin{array}{ccccccccc}
+	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
+	\\ \\ &&&&&&&& \perm \\ \\
+	\boat5 &\perm& \boat6 &\perm& \boat7 &\perm& \boat8 &\perm& \boat9
+\end{array}
+\]
+\caption{The boat}
+\label{fig:boat}
+\end{figure}
+
+\begin{figure}
+\[
+	\boats
+\]
+\caption{Nested boats}
+\label{fig:boats}
+\end{figure}
+
+\end{document}
 

### 2015-01-30 main/LMCS.tex

@@
 %
+
 It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.

### 2015-01-30 main/LMCS.tex
section NCL

@@
 \let\capsabbrev=\uppercase
+
+\newcommand\jumpsto{\jump}
 
@@
 \end{definition}
+
+We will write $\links[\jumpsto ab]$ for the linking where $\jump ab$, and $\jump c{\links(c)}$ for any $\named c\bot$ other than $a$.
+Then in a rewiring $\links\perm*\links[\jumpsto ab]$, the jump being rewired is that from $a$.
 
@@
 This idea will form the basis of our encoding of non-deterministic constraint logic.
-First, we will introduce the latter.
 
@@
 
-%
-A constraint graph may be encoded as a sequent, and a configuration as a proof net.
-%
-
-It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.
+In the formal definition, a constraint graph is an \emph{undirected} graph, for which a \emph{configuration} assigns an orientation to each edge.
+It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where the direction of edges may be left undefined, as long as the inflow constraints are satisfied by the directed edges.
+We will use $\star$ to indicate an undefined value, to avoid overloading $\bot$.
 
 \begin{definition} 
-A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting the two vertices $v(e)=\{v_1,v_2\}\subseteq V$.
-
-\smallskip
-
-A \emph{(partial) configuration} for a constraint graph is a (partial) function $\gamma\colon E\to V$ such that
+A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of:
+\begin{itemize}
+	\item $V$ a set of vertices,
+	\item $E$ a set of edges,
+	\item $c\colon V\to\mathbb N$ an \emph{inflow constraint} on each vertes,
+	\item $v\colon E\to\mathcal P(V)$ where $|v(e)|\in\{1,2\}$ for $e\in E$, a set of 1 or 2 vertices for each edge,
+ 	\item $w\colon E\to\mathbb N$ a \emph{weight} on each edge.
+\end{itemize}
+\end{definition}
+
+\begin{definition}
+A \emph{(partial) configuration} for a constraint graph $G=(V,E,c,v,w)$ is a (partial) function $\gamma\colon E\to V$ such that
 \begin{itemize}
 	\item
-for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
+for every edge $e$, $\gamma(e)\in v(e)\cup\{\star\}$,
 	\item
-for every vertex $v$, the total weight of its incoming edges is at least its inflow constraint, 
-$\sum\{w(e)\mid\gamma(e)=v\}\geq c(v)$.
+for every vertex $v$,
+\[
+	c(v) \leq \sum\{w(e)\mid\gamma(e)=v\}~.
+\]
 \end{itemize} 
-
-\smallskip
-A \emph{reconfiguration step} $\gamma\perm*\delta$ relates two (partial) configurations for $G$ that differ in value (or definedness) on exactly one edge; this edge is then called \emph{mobile} in $\gamma$ and $\delta$.
-%
+\end{definition}
+
+In the above definition, the first condition states that the weight of an edge may be assigned only to one of its vertices, or left undefined, but not to any other vertex in the constraint graph.
+The second condition states that the total weight of its incoming edges of a vertex must be at least its inflow constraint.
+
+We will write $\gamma[e\mapsto v]$ for the partial configuration that directs $e$ to $v$, and any other edge $e'$ to $\gamma(e')$.
+An edge that may be reversed will be called \emph{mobile}.
+Formally, an edge $e$ in $\gamma$ is \emph{mobile} if $\gamma[e\mapsto\star]$ is a partial configuration.
+
+\begin{definition}
+A \emph{reconfiguration step} $(\perm*)$ relates two partial configurations for $G$ that differ in value (or definedness) on exactly one edge:
+\[
+	\gamma[e\mapsto u]~\perm*~\gamma[e\mapsto w]\qquad\text{ if }u\neq w\text{ and }u,w\in v(e)\cup\{\star\}~.
+\]
 The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
-%
 \end{definition}
+
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
+This is the problem shown to be PSPACE-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:
+
+\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
+\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
+\end{theorem}
+
+To show that this result extends to our setting, with partial configurations, we have the following proposition.
 
@@
 
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
-
-\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
-\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
-\end{theorem}
-
-This result may seem surprising at first.
+The PSPACE-completeness of NCG-reconfiguration may seem surprising at first.
 To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed.
-
-\noindent\boat{1}\hskip3em\boat{10}
-
-\noindent\boat{11}\hskip3em\boat{20}
+The existence of such rewiring sequences is an essential property for the hardness result: if reconfiguration sequences could be given a polynomial bound, they would be polynomial-time witnesses, placing the problem within NP.
+
+\newpage
+
+\begin{figure}
+\[
+\begin{array}{ccccccccc}
+	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
+	\\ \\ &&&&&&&& \perm \\ \\
+	\boat9 &\perm& \boat8 &\perm& \boat7 &\perm& \boat6 &\perm& \boat5
+\end{array}
+\]
+\caption{The boat}
+\label{fig:boat}
+\end{figure}
+
+\begin{figure}
+\[
+	\boats
+\]
+\caption{Nested boats}
+\label{fig:boats}
+\end{figure}
+
+\end{document}
+
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 
@@
 We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
-
-\newpage
-
-\begin{figure}
-\[
-\begin{array}{ccccccccc}
-	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
-	\\ \\ &&&&&&&& \perm \\ \\
-	\boat5 &\perm& \boat6 &\perm& \boat7 &\perm& \boat8 &\perm& \boat9
-\end{array}
-\]
-\caption{The boat}
-\label{fig:boat}
-\end{figure}
-
-\begin{figure}
-\[
-	\boats
-\]
-\caption{Nested boats}
-\label{fig:boats}
-\end{figure}
-
-\end{document}
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 

### 2015-01-31 main/LMCS.tex
finished section NCL

@@
 Vertices with inflow constraint 2 are drawn as grey circles.
-For convenience, we will assume that dangling edges are connected to vertices of weight 0, which are omitted from illustrations.
+For convenience, we will assume that dangling edges are connected to vertices of weight zero, which are omitted from illustrations.
+These zero-inflow vertices can be seen as ``connection points'', where the graph may be connected to a wider network of graphs.
 
@@
 
-\newpage
+The example is then as follows.
+Figure~\ref{fig:boats} gives a reconfiguration sequence, clockwise from the top left, on a constraint graph with two connection points, top and bottom.
+As such, the graph is meant to replace a single edge from top to bottom, and the reconfiguration sequence inverts the direction of this would-be edge.
+The key point is that in doing so, the central horizontal edge must be inverted \emph{twice}.
+Then by nesting the graph within itself, where one graph replaces the central edge of another, as illustrated in Figure~\ref{fig:big boat}, a graph is created with an edge that requires 4 inversions.
+Each added level of nesting doubles the number of inversions that the central edge must make, while growing the graph by only a constant factor.
+Thus, the length of a rewiring path may grow exponentially with the size of the graph.
 
@@
 \]
-\caption{The boat}
-\label{fig:boat}
+\caption{A reconfiguration path requiring two inversions of a single edge}
+\label{fig:boats}
 \end{figure}
@@
 \]
-\caption{Nested boats}
-\label{fig:boats}
+\caption{Nesting graphs to grow reconfiguration paths exponentially}
+\label{fig:big boat}
 \end{figure}

### 2015-01-31 main/LMCS.tex
pasted in Encoding + big example

@@
 \newcommand\jumpsto{\jump}
+\newcommand\Perm{\mathbf\sim}
 
@@
 \[
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,->-] (3,0) -- (5,2);
-	\draw[ncl1,->-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\quad\perm*\quad
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,->-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\quad\perm*\quad
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,->-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,-<-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
-\quad\perm*\quad
-\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
-	\draw[ncl2,-<-] (0,0) -- (3,0);
-	\draw[ncl1,-<-] (3,0) -- (5,2);
-	\draw[ncl1,-<-] (3,0) -- (5,-2);
-	\node[nclnode] at (3,0) {};
-\end{tikzpicture}}
+	\andexample 1 \quad\perm*\quad
+	\andexample 2 \quad\perm*\quad
+	\andexample 3 \quad\perm*\quad
+	\andexample 4
 \]
@@
 
-\end{document}
-
-% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+%------------------------------------------------------------
 
@@
 \label{sec:encoding}
-\noindent
-%
+
 We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
-
-\begin{figure*}
-\[
-\vc{\scalebox{0.36}{\BIGexample 3}}
-\quad\perm\quad
-\vc{\scalebox{0.36}{\BIGexample 2}}
-\quad\perm\quad
-\vc{\scalebox{0.36}{\BIGexample 1}}
-\]
-\caption{Rewiring three edge-gadgets connected to a single vertex-gadget}
-\label{fig:encoding example}
-\end{figure*}
-
-\subsection*{The encoding}
+A sequent will encode a constraint graph, and a proof net a configuration, such that rewiring  the proof net corresponds to reconfiguration.
 
@@
 
+\newcommand\ANDmark[1]{\makebox[0pt][r]{\Large{\textbf{#1}}}}
+
+\begin{figure}[p]
+\[
+\begin{array}{@{}r@{\hspace{16pt}}|@{\hspace{16pt}}l@{}}
+	\ANDexample 1 \ANDmark 1 & \ANDexample 2 \ANDmark 2 \\ \\ \hline \\
+	\ANDexample 3 \ANDmark 3 & \ANDexample 4 \ANDmark 4 \\ \\ \hline \\
+	\ANDexample 5 \ANDmark 5 & \ANDexample 6 \ANDmark 6 \\ \\ \hline
+\end{array}
+\]
+\vspace{20pt}
+\[
+\begin{array}{c@{\hspace{30pt}}c@{\hspace{30pt}}c@{\hspace{30pt}}c}
+	\andexample 1 & \andexample 2 & \andexample 3 & \andexample 4 \\
+	\textbf{1} & \textbf{2} & \textbf{3~4~5} & \textbf{6}
+\end{array}
+\]
+\caption{Encoding an \textsc{and}-gate in proof nets}
+\label{fig:big example}
+\end{figure}
+
 %------------------------------------------------------------
+
+\newpage
+
+%\acks
+
+We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction and our proofs, and Dominic Hughes for several useful suggestions on exposition.
+% and the anonymous referees for their constructive observations.
+
+%===========================
+\bibliographystyle{plain}
+\bibliography{LMCS}
+\end{document}
+%===========================
+
+\end{document}
 

### 2015-01-31 main/LMCS.tex
one para Encoding

@@
 
+The natural basis of the encoding is the use of jumps to indicate where the weight of an edge is allocated.
+The main problem then becomes, how to restrict the movement of such jumps, so that they may assign weight only to the vertices of one particular edge.
+The central design idea of the encoding is to use the combinatorics of connecting formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ to solve this problem.
+
 The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
-%
-The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
+
+To ensure that a weight element may be linked to only two vertices. The arithmetic of linking will be used
 %

### 2015-01-31 main/LMCS.tex
Correct BCST reference

--- 2015-01-31 main/LMCS.tex
@@
 \begin{remark}
-The proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} may appear to be formulated in quite a distinct way from our presentation, in particular in that their jumps from $\bot$-vertices connect to edges, rather than vertices.
+The proof nets of \cite{Blute-Cockett-Seely-Trimble-1996} may appear to be formulated in quite a distinct way from our presentation, in particular in that their jumps from $\bot$-vertices connect to edges, rather than vertices.
 The difference is only superficial: in their proof nets, vertices represent inferences, and edges represent formulae; in both presentations, therefore, jumps may be seen to attach to formulae.

### 2015-02-01 main/LMCS.tex
section Encoding complete

--- 2015-01-31 main/LMCS.tex
@@
 
-The basis of the encoding of constraint graphs in \capsabbrev{mll} is formed by \emph{weight elements}, which encode one unit of weight on an edge, and \emph{constraint elements}, that encode one unit towards the inflow constraint of a vertex.
-%
-The arithmetic of linking formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ will be used to ensure that a weight element may be linked to only two vertices.
-%
-Below left is a weight element, below right a constraint element.
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
+The natural basis of the encoding is the use of jumps to indicate where the weight of an edge is allocated.
+The main problem is then how to restrict the movement of such jumps, so that they may assign weight only to the vertices of one particular edge, and not to any other vertices.
+The central design idea of our encoding is to use the combinatorics of connecting formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ to solve this problem.
+
+The two basic components of our encoding will be \emph{weight elements}, representing the weight value of edges, and \emph{constraint elements}, which encode the inflow constraint of vertices.
+For now, we will work under the assumption that each unit of weight on an edge is encoded by exactly one weight element---later, we will amend this to use multiple weight elements for each unit of weight.
+A weight element will be a construction over a number of $\bot$-formulae, whose jumps may connect to the $\1$-formulae of a constraint element.
+
+Below top is a weight element, below bottom a constraint element.
+\[
+\begin{array}{ccc}
+	  \vc{\begin{tikzpicture}[x=5mm,y=5mm,octo]
 	 	\node[big_] (A) at (0,0) {$i'$}; 
@@
 		\draw[rounded corners] (-1,-1) rectangle (5,1);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	  \end{tikzpicture}}
+	&=&
+	  \bigtn(\bot^{i+1})~~\pr~~\bigtn(\bot^{j+1})~~\pr~~\bigtn(\bot^{k+1})
+\\ \\
+	  \vc{\begin{tikzpicture}[x=5mm,y=5mm,octo]
 		\node[big1] (1) at (0,0) {$m'$}; 
@@
 		\draw (1,0)--(2,0);
-\end{tikzpicture}
-\]
-For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same -- this way, a priori any weight element may connect to any constraint element.
-%
-The value of $m$ (and thus $n$) will differ for each vertex.
-%
-The weight element above will be able to connect naturally to those constraint elements where $m=i$ and where $m=i+j$, as illustrated below.
+	  \end{tikzpicture}}
+	&=&
+	  \bigparr(\1^{m+1})~\tn~\bigparr(\1^{n+1})
+\end{array}
+\]
+For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
+The value $m$ will be unique for each vertex, and used for all constraint elements in the encoding of that vertex.
+The weight element above is for an edge connecting the two vertices for which $m=i$ and $m=i+j$: with those constraint elements it is possible to form a proof net, as illustrated below.
 \[
@@
 \]
-To ensure that no other connections can be made, values are chosen such that $m\equiv1$ and $n\equiv2 \pmod 3$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2\pmod 3$.
-
-In a constraint graph, the sum of all weights is usually greater than the sum of all inflow constraints---otherwise, no edge can move, or no configuration exists.
-%
-An encoding will therefore have weight elements not connected to constraint elements.
-%
-These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as follows.
-%
+To ensure that a weight element may not form a proof net with a constraint element of another vertex, the values of $m$ and $n$ are chosen such that $m\equiv1$ and $n\equiv2 \pmod 3$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2\pmod 3$.
+It then becomes impossible for $m$ to equal any other sum over $i$, $j$, and $k$, so that forming a proof net requires either $m=i$ or $m=i+j$.
+
+Several further constructions are used in our encoding.
+Firstly, in a constraint graph, the sum of all weights is usually greater than the sum of all inflow constraints---otherwise, no edge can be mobile, or no configuration exists.
+Correspondingly, an encoding will have weight elements not connected to constraint elements.
+These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as shown below.
+A weight element that is connected to absorbers will be called \emph{free}.
 \[
@@
 \]
-%
-An edge will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements plus a single \emph{indicator} vertex.
-%
+
+An edge in a constraint graph will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements, plus a single $\bot$-formula which we will refer to as the \emph{indicator}.
 Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
-%
 \[
@@
 \]
-%
-It would be natural to encode an edge of weight $n$ by an edge-gadget with $n$ weight elements.
-%
+The natural way for edge-gadgets to link up with a vertex-gadget is shown in Figure~\ref{fig:connect example}: indicators connect to indicator targets, and weight elements connect to constraint elements or weight absorbers.
+The illustration depicts two equivalent proof nets, both encoding the same (fragment of a) constraint graph: a single vertex that is the target of a weight-1 edge (on the left, in red) and a weight-2 edge (on the right, in blue).
+The inflow of the vertex is 3, and its constraint is 2; then 2 weight elements are connected to the constraint elements in the vertex-gadget, while one remains free (connected to weight absorbers).
+It is essential to the functioning of the encoding that any re-distribution of weight elements gives an equivalent proof net, as illustrated by the example.
+Then in the second proof net, the single weight element of the left edge-gadget is free, which means the indicator jump can be rewired to connect to a different vertex.
+
+In the encoding, the indicator jumps determine which vertex is the target of the edge, and while they may in principle assign any vertex, the weight elements of the edge-gadget can only form proof nets with the constraint elements of the correct vertices.
+An edge-gadget will be called \emph{free} if all its weight elements are free.
+The vertex-gadgets in an encoding will all be gathered in a $\tn$-formula, which means they are connected, so that free edge-gadgets may attach their indicator to any of them.
+
+\begin{figure}
+
+\noindent$\CONexample 2{.60}\hfill\perm\hfill\CONexample 1{.60}$
+
+\caption{Two edge-gadgets connecting to one vertex-gadget}
+\label{fig:connect example}
+\end{figure}
+
+In Figure~\ref{fig:big example} we give a complete encoding of the example rewiring sequence shown in Figure~\ref{fig:NCL example}, a reconfiguration sequence for a constraint graph functioning as an \textsc{and}-gate.
+The given proof nets are all equivalent, and their corresponding constraint graphs are shown near the bottom of the figure.
+The central vertex-gadget encodes the central constraint-2 vertex in the graph, while its three implicit constraint-0 vertices, at the dangling ends of the three edges, are encoded by the three formulae connected to the central gadget.
+
+\newcommand\ANDmark[1]{\makebox[0pt][r]{\Large{\textbf{#1}}}}
+
+\begin{figure}[p]
+\[
+\begin{array}{@{}r@{\hspace{16pt}}|@{\hspace{16pt}}l@{}}
+	\ANDexample 1 \ANDmark 1 & \ANDexample 2 \ANDmark 2 \\ \\ \hline \\
+	\ANDexample 3 \ANDmark 3 & \ANDexample 4 \ANDmark 4 \\ \\ \hline \\
+	\ANDexample 5 \ANDmark 5 & \ANDexample 6 \ANDmark 6 \\ \\ \hline
+\end{array}
+\]
+\vspace{20pt}
+\[
+\begin{array}{ccccccc}
+	\andexample 1 &\perm& \andexample 2 &\perm& \andexample 3 &\perm& \andexample 4 \\
+	\textbf{1} && \textbf{2} && \textbf{3~4~5} && \textbf{6}
+\end{array}
+\]
+\caption{Encoding an \textsc{and}-gate in proof nets}
+\label{fig:big example}
+\end{figure}
+
+\subsection*{Weight adjustment}
+
+So far we have assumed that one weight element may encode one unit of weight in the constraint graph.
 However, there is a minor issue that prevents this straightforward approach.
-%
-Although one weight element cannot `fill' an inappropriate constraint element, two weight elements can, in the way illustrated below.
-%
+Although one weight element cannot `fill' an inappropriate constraint element, two weight elements \emph{can}, in the way illustrated below.
+In such a situation, the weight element that should have been linked to this constraint element becomes free, and the edge it belongs to may inappropriately become free, too.
 \[
@@
 \]
-%
-In such an inappropriate linking, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the linking would violate the switching condition.
-%
+To resolve this issue, it is sufficient to increase the number of weight elements used to encode one unit of weight. In the following, we will investigate how many are needed.
+
+In an inappropriate linking as shown above, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the switching condition would be violated.
 That means the weight elements must belong to different edges.
@@
 As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
-%
 Consequently, a weight element can fill three halves, but only of different constraint elements.
-%
 The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
-%
 To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
-%
 To fill $3n$ constraint elements inappropriately therefore requires $n+1$ edges.
-%
-It thus suffices to multiply the number of constraint elements by three times the number of edges, and encode a vertex with inflow constraint $c$ by a vertex-gadget with $c\times3\times|E|$ constraint elements (where $|E|$ denotes the number of edges in the constraint graph).
+It thus suffices to encode one unit of weight on an edge by $3\times|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly to encode one unit of inflow constraint by $3\times|E|$ constraint elements.
+
+\subsection*{The complete encoding}
 
@@
 A configuration for $G$ will be encoded as a proof net for $\Gamma$, and conversely each proof net for $\Gamma$ may be interpreted as a (partial) configuration for $G$.
-
-Figure~\ref{fig:encoding example} displays an encoding of two edges of weight 1, and one of weight 2, connecting to a central vertex with inflow constraint 2, as in the example reconfiguration sequence in Figure~\ref{fig:NCL example}.
-%
-The jumps from the three indicator vertices, at the bottom, indicate which vertex an edge is directed at.
-%
-Indicator jumps can only be rewired between vertices when the edge-gadget is connected only to weight absorbers---in the first net of Figure~\ref{fig:encoding example}, the two leftmost edges are mobile, and in the third, the rightmost edge is mobile.
-%
-All three nets in Figure~\ref{fig:encoding example} then correspond to the third graph in Figure~\ref{fig:NCL example}, but the first net allows rewiring according to the second and first graph, whereas the third net allows rewiring according to the fourth graph.
-
 The encoding will be made formal in Section~\ref{sec:correctness}; first we will establish some basic results for rewiring on proof nets.
-
-\newcommand\ANDmark[1]{\makebox[0pt][r]{\Large{\textbf{#1}}}}
-
-\begin{figure}[p]
-\[
-\begin{array}{@{}r@{\hspace{16pt}}|@{\hspace{16pt}}l@{}}
-	\ANDexample 1 \ANDmark 1 & \ANDexample 2 \ANDmark 2 \\ \\ \hline \\
-	\ANDexample 3 \ANDmark 3 & \ANDexample 4 \ANDmark 4 \\ \\ \hline \\
-	\ANDexample 5 \ANDmark 5 & \ANDexample 6 \ANDmark 6 \\ \\ \hline
-\end{array}
-\]
-\vspace{20pt}
-\[
-\begin{array}{c@{\hspace{30pt}}c@{\hspace{30pt}}c@{\hspace{30pt}}c}
-	\andexample 1 & \andexample 2 & \andexample 3 & \andexample 4 \\
-	\textbf{1} & \textbf{2} & \textbf{3~4~5} & \textbf{6}
-\end{array}
-\]
-\caption{Encoding an \textsc{and}-gate in proof nets}
-\label{fig:big example}
-\end{figure}
 

### 2015-02-01 main/LMCS.tex
First part of intro

--- 2015-01-31 main/LMCS.tex
@@
 \section{Introduction}
-
-%
+\noindent
+Sequent calculus was originally introduced by Gentzen as a way to better understand
+the properties of natural deduction -- in particular the eliminability of cut. In this
+view, a sequent calculus proof gives a recipe for the construction of a natural deduction
+proof.
+
+Linear logic was formulated as a sequent calculus system, and doesn’t have a corresponding
+natural deduction in the classical sense. The role of natural deduction is taken instead by
+proof nets. Each sequent calculus proof gives rise to a proof net. Furthermore, at least in
+the case of multiplicative linear logic without units, proof nets are canonical in the sense
+that two sequent calculus proofs give rise to the same proof net if and only if they are
+equivalent.
+
+Proof nets do not work so well when the logical units 1 and $\bot$ are included. Although
+proof nets can still be defined in this case, they are no longer canonical. It has not
 

### 2015-02-01 main/LMCS.tex
added everything

@@
 Note that unlike the axiom links of proof nets without units, a jump may connect to any connective or unit, and multiple jumps may point to the same position.
+A path between vertices $a$ and $b$ in a switching graph is indicated as $\path ab$.
 
@@
 The introduction rule for $\bot$, in Figure~\ref{fig:MLL}, attaches a $\bot$-formula to a sequent---but sequents are not explicit in proof nets.
-The notion of a jump, which attaches the $\bot$ to an arbitrary point in the sequent $\Gamma$, is then a natural generalisation of the axiom links of unit-free \capsabbrev{mll} proof nets.
+The notion of a jump, which attaches the $\bot$ to an arbitrary subformula in the sequent $\Gamma$, is then a natural generalisation of the axiom links of unit-free \capsabbrev{mll} proof nets.
 This gives the following translation from proofs to proof nets.
@@
 \end{array}
-\qquad\qquad\qquad
+\qquad\qquad
 \vc{
@@
 \end{tikzpicture}}
-\]
-A linking between formulae $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated above right.
+\qquad\quad
+\begin{array}{c}
+	\vc{\begin{tikzpicture}[x=5mm,y=5mm,octo] \node[big_] {$k'$}; \end{tikzpicture}} ~=~
+	\vc{\begin{tikzpicture}[x=5mm,y=5mm,octo] \draw (0,0) node[big_] {$i'$} -- (2,0) node[big_] {$j'$}; \end{tikzpicture}}
+	\\ \\ (k=i+j+1)
+\end{array}
+\]
+A linking between formulae $\bigtn(\bot^n)$ and a sequent $\1^n$ will be represented by a wide arrow, as illustrated above center.
 For the moment, we will not distinguish between the $n!$ different ways in which such a linking can be made, but when the distinction becomes relevant we will make an explicit choice.
-
-The intention behind the chosen notation is that both the abbreviated formulae and the arithmetic of connecting them remain intuitive.
+Above right, to link a formula $\bigtn(\bot^{k+1})$ to several other formulae, we may display the formula as two discs according to the given arithmetic, representing the formula $\bigtn(\bot^{i+1})\tn~\bigtn(\bot^{j+1})$.
+
+The primary intention behind the chosen notation is to make the arithmetic of connecting formulae $\bigtn(\bot^n)$ to formulae $\bigparr(\1^n)$ apparent in the illustrations.
 Specifically, the following is a proof net if and only if $n=i_1+\dotso+i_k$.
@@
 
-\newpage
-
-%\acks
-
-We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction and our proofs, and Dominic Hughes for several useful suggestions on exposition.
-% and the anonymous referees for their constructive observations.
-
-%===========================
-\bibliographystyle{plain}
-\bibliography{LMCS}
-\end{document}
-%===========================
-
-\end{document}
-
 \section{Rewiring proof nets}
@@
 
-% TO DO: FIND A PLACE FOR:
-%
-% A path in a proof net or switching graph will be indicated $\path ab$, and illustrated as below.
-%\[
-%\begin{tikzpicture}[x=5mm,y=5mm,octo]
-%	\node[bullet] (a) at (0,0) {}; \node[bullet] (b) at (2,0) {}; \draw[dashed] (a)--(b);
-%\end{tikzpicture}
-%\qquad
-%\begin{tikzpicture}[x=5mm,y=5mm,octo]
-%	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
-%\end{tikzpicture}
-%\]
-
-%
 In this section we will explore the global rewiring behaviour of proof nets.
-%
 We will look at notions of subnets; we will introduce a notion of relative \emph{parity} between nets, which if odd, guarantees inequivalence; and we will give a simple account of equivalence for the fragment of \capsabbrev{mll} that omits the par.
@@
 We will discuss (and adapt) some convenient standard notions for \capsabbrev{mll} proofs and proof nets, and relate them to rewiring.
-%
 Firstly we will look at subnets---see also \cite{Bellin-vandeWiele-1995}.
@@
 The \emph{ports} of a sub-sequent $\Gamma'$ or subnet $(\Gamma',\links')$ are the root vertices of $\Gamma'$.
-%
 For a vertex $v$ naming a par, tensor, or bottom, the subnets of which it is a port correspond to the possible subproofs of the rule introducing $v$ in a sequentialisation (the subproof of a $\1$-subformula must always be empty).
@@
 In the graph of a proof net, a chosen subnet for a par can be made explicit as a \emph{box}, as illustrated below left.
-%
 Boxes may replace the switching condition as a correctness criterion: in the example, both the outside and the inside of the box form a tree.
-%
 To make this precise, we will consider the action of \emph{closing} a box, which means it is regarded as a single vertex in the graph, as illustrated below right.
-%
-%
-%
 \[
@@
 \end{tikzpicture}
-\qquad\qquad
+\qquad\qquad\qquad
 \begin{tikzpicture}[x=5mm,y=-5mm,octo]
@@
 \]
-%
-%
+
+\newcommand\bx{s}
+
 \begin{definition}
-A \emph{boxing} $s$ for a linking $\links$ for $\Gamma$ assigns a sub-sequent $s(v)\leq\Gamma$ to each par-vertex $\named v\pr$ such that 1) $v$ is a port of $s(v)$ and 2) boxes are either disjoint or strictly nested: if $s(v)\cap s(w)\neq\varnothing$ then $s(w)<s(v)$ or $s(v)<s(w)$.
+A \emph{boxing} $\bx$ for a linking $\links$ for $\Gamma$ assigns a sub-sequent $\bx(v)\leq\Gamma$ to each par-vertex $\named v\pr$ such that 1) $v$ is a port of $\bx(v)$ and 2) boxes are either disjoint or strictly nested: if $\bx(v)\cap\bx(w)\neq\varnothing$ then $\bx(w)<\bx(v)$ or $\bx(v)<\bx(w)$.
 \end{definition}
@@
 \noindent
-In the graph for $\links$ and $\Gamma$, a box $s(v)$ may be \emph{closed} by replacing the subgraph over $s(v)$ by the single vertex $v$, and replacing every arc into $s(v)$ by one onto $v$.
-%
-For each box $s(v)$ we define the \emph{local graph} to be that formed by the subgraph over $s(v)$ where each immediately smaller box $s(w)<s(v)$ is closed.
-%
+In the graph for $\links$ and $\Gamma$, a box $\bx(v)$ may be \emph{closed} by replacing the subgraph over $\bx(v)$ by the single vertex $v$, and replacing every arc into $\bx(v)$ by one onto $v$.
+For each box $\bx(v)$ we define the \emph{local graph} to be that formed by the subgraph over $\bx(v)$ where each immediately smaller box $\bx(v)<\bx(v)$ is closed.
 The following is then a variation on the local retraction algorithm by Danos \cite{Danos-1990}.
@@
 \label{prop:scoping correctness}
-A linking $\links$ for $\Gamma$ is a proof net if and only if it has a boxing $s$ such that each local graph is a tree.
+A linking $\links$ for $\Gamma$ is a proof net if and only if it has a boxing $\bx$ such that each local graph is a tree.
 \end{proposition}
@@
 \begin{proof}
-Given a boxing $s$, it follows by induction on the nesting of boxes that the graph over each $s(v)$ satisfies the switching condition.
-%
-In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $s(v)\leq\Gamma$ for each $\named v\pr$ is found by taking the conclusion $\Delta, A\named v\pr B$ of its introduction rule, below.
+Given a boxing $\bx$, it follows by induction on the nesting of boxes that the graph over each $\bx(v)$ satisfies the switching condition.
+In the other direction, given a sequentialisation of $(\Gamma,\links)$, a box $\bx(v)\leq\Gamma$ for each $\named v\pr$ is found by taking the conclusion $\Delta, A\named v\pr B$ of its introduction rule, below.
 \[
@@
 In a proof net, the \emph{kingdom} and the \emph{empire} of a vertex $v$ are respectively the smallest and largest subnet that have $v$ as a port.
-%
 In working with the rewiring relation, the notion of empire can be particularly useful.
-%
-We will denote the empire of $v$ in $\links$ by $\emp v$ (used both as a graph and a set of vertices).
+
+\begin{definition}
+The \emph{empire} $\emp v$ of a vertex $v$ in $(\Gamma,\links)$ is the smallest subnet $(\Delta,\links')$ of which $v$ is a port.
+\end{definition}
 
@@
 \label{prop:empire propagation}
-The empire $\emp v$ is determined by propagation from $v$: 1) through links; 2) up towards subformulae; 3) into a tensor if one of its subformulae is in $\emp v-\{v\}$; 4) into a par if all its subformulae are in $\emp v-\{v\}$.
+The empire $\emp v$ is determined by propagation from $v$:
+\begin{enumerate}
+	\item\label{case:empire propagation 1} through links;
+	\item up towards subformulae;
+	\item into a tensor if one of its subformulae is in $\emp v-\{v\}$;
+	\item into a par if all its subformulae are in $\emp v-\{v\}$.
+\end{enumerate}
 \end{proposition}
 
-\noindent
-The following three lemmata show how empires are connected to rewiring.
-%
+It should be noted that the above characterisation of  empires relies on the restriction of jumps to target $\1$-formulae only.
+Otherwise, the first case of the definition should be specialised so that propagation does not traverse jumps into $v$.
+
+The following three lemmata will show how empires are connected to rewiring.
 Firstly, a jump from $\named v\bot$ may be rewired to exactly those $\1$-occurences that are in the empire of $v$ (Lemma~\ref{lem:rewiring within empire}).
-%
-Secondly, rewiring this jump preserves the empire of $v$, up to that rewiring (Lemma~\ref{lem:rewiring preserves empire}).
-%
-Thirdly, the empire of any other vertex $w$ will grow or shrink, or neither, but not both (Lemma~\ref{lem:rewiring affects empires}).
+Secondly, rewiring a jump from $\named v\bot$ preserves the empire of $v$, up to that rewiring (Lemma~\ref{lem:rewiring preserves empire}).
+Thirdly, rewiring the jump from $v$ may add subformulae to the empire of another vertex $w$, or remove subformulae from it, but not both (Lemma~\ref{lem:rewiring affects empires}).
 
@@
 For a proof net $(\Gamma,\links)$ where $\links(a)=v$, and $w$ names a $\1$-occurrence in $\Gamma$, the following are equivalent:
-%
 \begin{enumerate}
 	\item
-$\links\perm*\links'$ where $\links'(a)=w$;
+$\links\perm*\links[\jumpsto aw]$
 	\item
@@
 Next, it is shown that 2 implies 1.
-%
-The empire $\emp a$ corresponds to the largest subproof $\Sigma$ in any $\Pi\toNet\links$ with as conclusion the introduction rule of $\named a\bot$.
-%
+The empire $\emp a$ corresponds to the largest subproof $\Sigma$, with as conclusion the introduction rule of $\named a\bot$, in any sequentialisation $\Pi$ of $\links$.
 By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net, $a$ may link to any $1$-occurrence, including to $w$.
@@
 Finally, it is shown that 1 implies 3, by contraposition.
-%
-If for some switching of $\links$ the path $\path vw$ passes through $a$, then in $\links'$ there is no path $\path av$ (and two paths $\path aw$) for that switching, so that $\links'$ is not a net.
-%
+If for some switching of $\links$ the path $\path vw$ passes through $a$, then in $\links[\jumpsto aw]$ there is no path $\path av$ (and two paths $\path aw$) for that switching, so that $(\Gamma,\links[\jumpsto aw])$ is not a net.
 \end{proof}
@@
 \label{lem:rewiring preserves empire}
-If $\links\perm*\links'$ by $\links(v)\neq\links'(v)$ then $\emp v\perm*\emp*v$.
+If $\links\perm*\links[\jumpsto vw]=\links'$ then $\emp v\perm*\emp*v$.
 \end{lemma}
@@
 Since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$, by Lemma~\ref{lem:rewiring within empire} the empires $\emp v$ and $\emp*v$ contain the same $\1$-subformulae.
-%
 That they also share any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is (unless $v$ names $A$, but in this case $A$ is included in both $\emp v$ and $\emp*v$).
-%
 \end{proof}
@@
 \begin{proof}
-Let the link from $a$ be rewired, $\links(a)=w$ but $\links'(a)=w'$.
-%
-Using Proposition~\ref{prop:empire propagation}, there are four cases.
-%
-\begin{enumerate}
-	\item
-If the empire of $v$ is propagated from $a$ to $w$ in $\links$, it includes the empire of $a$.
-%
-Then by Lemma~\ref{lem:rewiring preserves empire} $\Delta=\Delta'$.
-
-	\item
-If the empire of $v$ includes $w$ but not $w'$, then it is propagated through $a$ in $\links$ but not in $\links'$, so that $\Delta\geq\Delta'$.
-
-	\item
-If the empire of $v$ includes $w'$ but not $w$, then $\Delta\leq\Delta'$.
-
-	\item
-Otherwise, $\Delta=\Delta'$. \hfill\qedhere
-\end{enumerate}
+Let $\links'=\links[\jumpsto aw]$, where $\links(a)=u$ and $\links'(a)=w$.
+We will distinguish five cases, depending on three factors: 1) whether $\emp v$ contains $u$; 2) if so, whether $\emp v$ is propagated from $u$ to $a$ or from $a$ to $u$ in case~\ref{case:empire propagation 1} of Proposition~\ref{prop:empire propagation}; and 3) whether $\emp v$ contains $w$.
+%
+\begin{itemize}
+	\item
+If $\emp v$ is propagated from $a$ to $u$, then it includes $\emp a$ as a subnet, because the latter is generated by propagation from $a$.
+Since $\emp a=\emp*a$ by Lemma~\ref{lem:rewiring preserves empire}, then in $\links'$ the empire of $v$ is propagated from $a$ to $w$, and includes $\emp*a$.
+It follows that $\Delta=\Delta'$.
+
+	\item
+If $\emp v$ is propagated from $u$ to $a$, and also contains $w$, then $\emp v$ has been propagated to $w$ without passing through $a$; otherwise, a switching cycle would be formed by the two propagation paths from $a$ to $w$, one generated by $\emp a$ via $u$, and one generated by $\emp v$, not via $u$.
+Then $\emp*v$ is propagated from $v$ to $w$ to $a$, and $\Delta=\Delta'$.
+
+	\item
+If $\emp v$ is propagated from $u$ to $a$, but does not contain $w$, then $\Delta\geq\Delta'$.
+
+	\item
+If $\emp v$ contains $w$ but not $u$, then $\Delta\leq\Delta'$.
+
+	\item
+If $\emp v$ contains neither $u$ nor $w$, then it also does not contain $a$. Then also $\emp*v$ contains neither $u$, $w$, nor $a$, and $\Delta=\Delta'$. \hfill\qedhere
+\end{itemize}
 \end{proof}
 
+% TO DO: 
+%  * Fix notion of empire for arbitrary jump targets
+%  * Make the above lemma obvious
+
 % - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
@@
 The linearity of \capsabbrev{mll} means that in a proof or proof net, there is always a certain balance to the number of $\bot$- and $\pr$-occurrences.
-%
 This observation gives a well-known necessary condition for the provability of a sequent.
@@
 Here, we will introduce a similar necessary condition for the equivalence of two proof nets.
-%
 We shall associate a \emph{parity} with any pair of linkings $\links$ and $\links'$ over the same sequent $\Gamma$, and we shall find that the parity of equivalent linkings is always even.
@@
 For this argument we will work with $n$-ary connectives $\tn$ and $\pr$, and alternating formulae, i.e.\ every argument of a $\tn$ is a $\pr$ and vice versa.
-%
 The units are given by the $0$-ary connectives, and we need not rule out unary ones.
-%
 We will consider a given named sequent $\Gamma$, but will assume that it consists of a single formula, if necessary by introducing a $\pr$ at the root.
@@
 To be able to compare arbitrary proof nets over $\Gamma$, we will use the following naming scheme for the edges of a switching graph, for any proof net over $\Gamma$.
-%
 A tensor $\bigtn(A_1,\dotsc,A_n)$ named $v$ has $n$ edges, which we shall name $v(1)$ through $v(n)$; a par $\named v\pr$ has one switched edge, to be named $v(1)$; and $\named v\bot$ has the jump named $v(1)$.
-%
 The naming scheme identifies edges across all switching graphs of all proof nets for $\Gamma$.
 
-Taking a different perspective, we may consider a switching graph as a directed tree, rooted in the root connective of $\Gamma$.
-%
+Taking a different perspective, we may alternatively consider a switching graph as a directed tree, rooted in the root connective of $\Gamma$.
 This establishes a bijection between the edges and the non-root vertices, which associates each edge with its target vertex.
 
+\begin{figure}
+\[
+	\vc{\parityNetA} \qquad\qquad\qquad \vc{\parityNetB}
+\]
+\caption{A switching graph of a proof net as a directed tree}
+\label{fig:directed switching graph}
+\end{figure}
+
 The example in Figure~\ref{fig:directed switching graph} displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $i$, and the edge $\edge rg$ for the root par $r$.
-%
 The induced bijection associates for example the edge named $r(1)$ with the vertex $g$, the edge $g(1)$ with $h$, and the edge $h(1)$ with $a$; it further associates $f(1)$ with $f$ and $c(3)$ with $c$.
@@
 Given two proof nets $\links$ and $\links'$ for $\Gamma$, and a switching graph for each (not necessarily given by the same switching of $\Gamma$), we obtain two bijections between edges and (non-root) vertices.
-%
 Composing these gives a permutation on the non-root vertices.
-%
+
 \begin{definition}
@@
 \end{definition}
-%
+
+\noindent
 We will show that both 1) rewiring and 2) choosing a different switching induce even parity.
-%
 By 2) we may define the parity of two proof nets $\links$ and $\links'$ to be that over arbitrary switching graphs; then by 1) it follows that proof nets with odd parity are inequivalent.
@@
 We will demonstrate 1), while 2) is similar.
-%
-Let $\links\perm*\links'$ by rewiring a jump from $\edge va$ to $\edge vb$.
-%
+Let $\links\perm*\links'$ by rewiring a jump $\jump va$ to $\jump vb$.
 By fixing a switching for $\Gamma$, we obtain a switching graph for each of the two nets, where the jump is named $v(1)$ in each.
-%
-There are two possibilities, illustrated in Figure~\ref{fig:rewiring directed switching graph}.
-%
+There are two possibilities, illustrated below.
+%in Figure~\ref{fig:rewiring directed switching graph}.
 On the left, if the jump $v(1)$ is directed upward, then the target of each edge in the directed switching graphs remains the same---in particular $v(1)$ has target $v$---and the induced permutation is the identity.
 
-On the right, in Figure~\ref{fig:rewiring directed switching graph}, if the jump from $v$ is directed downward, the subtree of $a$ will get the new root node $b$.
-%
+\[
+	\vc{\parityNetC1} \perm \vc{\parityNetC2}
+\qquad\qquad\qquad
+	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
+\]
+
+%On the right, in Figure~\ref{fig:rewiring directed switching graph},
+Above on the right, if the jump from $v$ is directed downward, the subtree of $a$ will get the new root node $b$.
 Then the vertices that are associated with a new edge are exactly those on the path $\path ab$ in the switching graph, as illustrated below.
@@
 Since the connectives in $\Gamma$ were assumed to be strictly alternating, there are an odd number of vertices on this path, $2n+3$: each even $v_i$ must be a $\bot$ or $\pr$, while each odd $v_j$ must be a $\1$ or $\tn$.
-%
 The permutation induced is then as follows.
-%
 Since $v$ has target $a$ in the first switching graph, and target $b$ in the second, it takes $a$ to $b$.
-%
 Further, since an edge connecting $v_i$ and $v_{i+1}$ has target $v_{i+1}$ in the first, but target $v_i$ in the second graph, the permutation takes $v_{i+1}$ to $v_i$.
-%
 The complete permutation is then a cyclic one taking each vertex on the path $\path ab$ to the previous, and the first to the last.
-%
 A cyclic permutation of odd length has even parity.
@@
 The above argument gives us 1), that rewiring has even parity.
-%
 To see that the same argument also gives 2), it is sufficient to consider that choosing a different switching for a single par is essentially the same operation as rewiring, if the par is considered a $\bot$ and the switched edge a jump.
-%
 We may thus conclude that:
@@
 
-\begin{figure}
-\[
-	\vc{\parityNetA} \qquad \vc{\parityNetB}
-\]
-\caption{A switching graph of a proof net as a directed tree}
-\label{fig:directed switching graph}
-\end{figure}
-
-\begin{figure}
-\[
-	\vc{\parityNetC1} \perm \vc{\parityNetC2}
-\quad \vc{\rule{.5pt}{4cm}} \quad
-	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
-\]
-\caption{Rewiring on the directed tree of a switching graph}
-\label{fig:rewiring directed switching graph}
-\end{figure}
+%\begin{figure}
+%\[
+%	\vc{\parityNetC1} \perm \vc{\parityNetC2}
+%\qquad\qquad\qquad
+%	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
+%\]
+%\caption{Rewiring on the directed tree of a switching graph}
+%\label{fig:rewiring directed switching graph}
+%\end{figure}
 
@@
 \[
-	\vc{\doubleExchange uvxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxy}
-	\quad\perm*\quad
-	\vc{\doubleExchange uyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyxu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vyyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyu}
-	\quad\perm*\quad
-	\vc{\doubleExchange vuyx}
-\]
-\caption{Double exchange of links (Lemma~\ref{lem:double exchange})}
+\begin{array}{ccccc}
+	\doubleExchange uvxy &\quad\perm*\quad&
+	\doubleExchange uyxy &\quad\perm*\quad&
+	\doubleExchange uyxu
+	\\ \\[3pt] &&&& \perm*
+	   \\[3pt] &&&& \doubleExchange vyxu
+	\\ \\[3pt] &&&& \perm*
+	   \\[3pt] 
+	\doubleExchange vuyx &\perm*&
+	\doubleExchange vuyu &\perm*&
+	\doubleExchange vyyu
+\end{array}
+\]
+\caption{Double exchange of jumps (Lemma~\ref{lem:double exchange})}
 \label{fig:double exchange}
@@
 Let a \emph{basic} sequent be one of formulae constructed only over $\1$, $\bot$, and $\tn$.
-%
 After removing dangling $\bot$-formulae and replacing subformulae $\1\tn A$ with $A$, basic sequents consist of formulae of the form $1$ or $\bigtn(\bot^n)$ with $n\geq2$.
-
 Provability for basic sequents is entirely determined by balance:
@@
 We will show that, similarly, equivalence for basic sequents is determined by parity.
-%
 An immediate observation is that a proof net for a basic sequent with only one tensor-formula, every $\1$ is linked to by exactly one jump---which means that no rewiring is possible.
@@
 Let $\links$ be a proof net with for every switching a path
-$\links(a){\xedge}a{\xpath}b{\xedge}\links(b){\xpath}\links(c){\xedge}c{\xpath}d{\xedge}\links(d)$.
-%
-Then $\links\perm\links'$ where $\links'(a)=\links(b)$ and $\links'(b)=\links(a)$, $\links'(c)=\links(d)$, and $\links'(d)=\links(c)$, and $\links'(z)=\links(z)$ otherwise.
-%
+\[
+	\links(a)\mathrel{\xpmuj}a\mathrel{\xpath}b\mathrel{\xjump}\links(b)\mathrel{\xpath}\links(c)\mathrel{\xpmuj}c\mathrel{\xpath}d\mathrel{\xjump}\links(d)~.
+\]
+Then $\links\perm\links[\jumpsto a{\links(b)}][\jumpsto b{\links(a)}][\jumpsto c{\links(d)}][\jumpsto d{\links(c)}]$.
 \end{lemma}
@@
 \label{lem:level0 max binary}
-%
 A basic sequent with at least two tensor-formulae has at most two equivalence classes of proof nets.
-%
 \end{lemma}
@@
 By induction on the size of a sequent $\Gamma$.
-%
 The base case is the sequent $\1,\1,\bot\tn\bot$, which has two inequivalent proof nets.
-%
-For the inductive step,
-%
-let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.
-%
+For the inductive step, let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.
 It will be shown that any net $\links$ is equivalent to one $\links'$ where $\links'(a)=z$; then by induction, the subnet $\links'$ restricted to $\Gamma',A$ belongs to one of two equivalence classes.
-%
 To find $\links'$, there are two cases.
 
-1) The path $\path az$ is via $\links(a)$.
-%
-If $\links(a)=z$, we are done. Otherwise, by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
+1) The path $\path az$ is via $\links(a)$. If $\links(a)=z$, we are done. Otherwise, by Lemma~\ref{lem:rewiring within empire} $\links'$ may be obtained from $\links$ by changing only $\links'(a)=z$.
 
 2) The path $\path az$ is via some $\named b\bot$ in $A$.
-%
 Firstly, if $\links(b)\neq z$, use Lemma~\ref{lem:rewiring within empire} to re-attach $b$ to $z$.
-%
 Next, let $\named c\bot$ and $\named d\bot$ be occurrences in a separate formula $B$ such that $c$ links to the same $\1$-occurrence as some $\bot$ in $A$.
-%
 Then $\links'$ is obtained by linking $c$ to $b$, and applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as those of $c$ and $d$.
-%
 \end{proof}
@@
 By Lemma~\ref{lem:level0 max binary} the sequent has at most 2 equivalence classes.
-%
 Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
@@
 
-%
 We will formalise the encoding of \capsabbrev{ncg}-reconfiguration into \capsabbrev{mll} proof equivalence that was informally introduced in Section~\ref{sec:encoding}.
-%
 A constraint graph $G$ will be encoded as a sequent $\itn G$, and a configuration $\gamma$ for $G$ will be encoded as a proof net $\itn\gamma$ for $\itn G$.
-%
 We will show that $\gamma\perm\delta$ if and only if $\itn\gamma\perm\itn\delta$ (modulo a small adjustment to ensure even parity between $\itn\gamma$ and $\itn\delta$).
@@
 \[
-	|c| = \sum_{v\in V}c(v) \qquad |w| = \sum_{e\in E}w(e)~.
+	|c| = \sum_{v\in V}c(v) \qquad\qquad |w| = \sum_{e\in E}w(e)~.
 \]
@@
 The \emph{encoding} $\itn G$ of a constraint graph $G$ is a sequent constructed as follows. 
-%
 Let $G=(V,E,c,v,w)$ with $|V|=n$, $|E|=m$, $V=\{v_1,\dotsc,v_n\}$, and $E=\{e_1,\dotsc,e_m\}$.
@@
 \[
-	\itn{v_k} = \bigparr\big(C_n(k)^{3m\times c(v_k)} \big)\pr\1
+	\itn{v_k} = \bigparr\big(C_n(k)^{3m\,\times\,c(v_k)} \big)\pr\1
 \]
@@
 \noindent
-The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
-\[
-	\itn{e} = \bigtn\big(W_n(i,j)^{3m\times w(e)}\big)\tn\bot
+The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i\leq j$ is the formula
+\[
+	\itn{e} = \bigtn\big(W_n(i,j)^{3m\,\times\,w(e)}\big)\tn\bot
 \]
@@
 \end{tikzpicture}
-\qquad
+\qquad\qquad\qquad
 \begin{tikzpicture}[x=5mm,y=5mm,octo]
@@
 
-To describe the intermediate stages of such a rewiring sequence, call an edge-gadget $\itn e$ \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or linked only to weight absorbers (in arbitrary fashion).
-%
-A well-linked edge-gadget is \emph{mobile} if all its weight elements connect only to weight absorbers.
-%
+To describe the intermediate stages of such a rewiring sequence, call an edge-gadget $\itn e$ \emph{well linked} if: 1) its indicator connects to the indicator target of an appropriate vertex-gadget $\itn v$, and 2) each weight element is either in a standard linking with a constraint element of $\itn v$, or is free (linked only to weight absorbers, in arbitrary fashion).
 In the following main lemma we will exchange the weight element linking to a constraint element.
-%
 The lemma considers a sequent consisting of just a vertex-gadget, some appropriate edge-gadgets, and sufficiently many weight absorbers.
@@
 
-\pagebreak
+\medskip
+
 \noindent
-1.\quad The initial configuration is illustrated below.
-%
+\textbf{1.}\quad The initial configuration is illustrated below.
 Other edges, other weight and constraint elements, and the outer box of the vertex-gadget, are omitted.
-%
 The vertices $i$, $j$, and  $v$ are the indicators of $\itn{e_i}$ and $\itn{e_j}$ and the indicator target of $\itn v$, respectively.
@@
 \noindent
-2.\quad The link $i-v$ is re-connected to a weight absorber together with only the links from the first $\bot$ of each of $D$, $E$, and $F$:
+\textbf{2.}\quad The jump $\jump iv$ is rewired to a weight absorber together with only the jumps from the first $\bot$ of each of $D$, $E$, and $F$:
 
@@
 \noindent
-3.\quad The link from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$:
+\textbf{3.}\quad The jump from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$:
 
@@
 \noindent
-4.\quad In the present configuration, the links from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
-%
+\textbf{4.}\quad In the present configuration, the jumps from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
 By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
-%
-It is then sufficient to choose linkings so that $D\pr E\pr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two links from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
-%
-The links of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining link from $B$ to $X$ and one from $C$ to $Y$.
+It is then sufficient to choose linkings so that $D\pr E\pr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two jumps from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
+The jumps of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining jump from $B$ to $X$ and one from $C$ to $Y$.
 
@@
 
-\newpage
 \noindent
-5.\quad The link from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
+\textbf{5.}\quad The jump from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
 
@@
 \noindent
-6.\quad The link from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
-%
-Lemma~\ref{lem:double exchange} allows to swap the targets of the link from $B$ to $X$ and the link from $i$, and simultaneously undo the exchange in the links from $D$ to $X$ added in step 4 above.
+\textbf{6.}\quad The jump from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
+Lemma~\ref{lem:double exchange} allows to swap the targets of the jump from $B$ to $X$ and the jump from $i$, and simultaneously undo the exchange in the jumps from $D$ to $X$ added in step 4 above.
 
@@
 \noindent
-7.\quad The link from $i$ is re-attached to $v$ to yield the final configuration:
+\textbf{7.}\quad The jump from $i$ is re-attached to $v$ to yield the final configuration:
 
 \displayOcto{\octorollA2}
-%
+
 \end{proof}
@@
 In the exchange of weight elements in the above lemma, weight elements link to weight absorbers in arbitrary fashion.
-%
 To be able to correct for this, the next lemma will demonstrate that, modulo parity, weight absorbers can be re-arranged at will.
@@
 \label{lem:permute weight absorbers}
-If $\links$ and $\links'$ are well-linked proof nets for $\itn G$ that are equal up to an even permutation of weight absorbers, then $\links\perm\links'$ if $\links$ and $\links'$ have at least one mobile edge-gadget $\itn e$.
+If $\links$ and $\links'$ are well-linked proof nets for $\itn G$ that are equal up to an even permutation of weight absorbers, then $\links\perm\links'$ if $\links$ and $\links'$ have at least one free edge-gadget $\itn e$.
 \end{lemma}
@@
 \begin{proof}
-To reconfigure $\links'$ into $\links$, we will use the double exchange operation of Lemma~\ref{lem:double exchange} to exchange two arbitrary weight absorbers at a time, as well as two chosen jumps in the mobile edge-gadget $\itn e$.
+To reconfigure $\links'$ into $\links$, we will use the double exchange operation of Lemma~\ref{lem:double exchange} to exchange two arbitrary weight absorbers at a time, as well as two chosen jumps in the free edge-gadget $\itn e$.
 %
@@
 %
-Note that since $\itn e$ is mobile, $e_0$ may re-attach anywhere within the proof net.
+Note that since $\itn e$ is free, $e_0$ may re-attach anywhere within the proof net.
 
@@
 
-We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees for their constructive observations.
+We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction and our proofs, and Dominic Hughes for useful suggestions on exposition.
+% and the anonymous referees for their constructive observations.
 
@@
 \end{document}
+
+\newpage
+
+%\acks
+
+We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees for their constructive observations.
+
+%===========================
+\bibliographystyle{plain}
+\bibliography{LMCS}
+\end{document}
+%===========================
+
+\end{document}

### 2015-02-01 main/LMCS.tex
intro para

@@
 This gives us interesting and important references as well.
+
+The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories.
+The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`s's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.
 
@@
 
-It should be noted that the above characterisation of  empires relies on the restriction of jumps to target $\1$-formulae only.
+\noindent
+It should be noted that the above characterisation of  empires relies on the restriction that we have imposed, that jumps target $\1$-formulae only.
 Otherwise, the first case of the definition should be specialised so that propagation does not traverse jumps into $v$.

### 2015-02-01 main/LMCS.tex
minor edits

@@
 The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories.
-The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`s's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.
+The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.
 
@@
 
-\newpage
-
-%\acks
-
-We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction and our proofs, and Dominic Hughes for useful suggestions on exposition.
+\subsection*{Acknowledgements}
+We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction, and Dominic Hughes for useful suggestions on exposition.
 % and the anonymous referees for their constructive observations.

### 2015-02-01 main/LMCS.tex
Edit final par of intro

@@
 
-The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories.
-The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.
+Since there can be no canonical representation of multiplicative linear logic proofs in accordance with the categorical semantics, it is tempting to consider other ways of defining the identity of proofs.
+The literature contains several interesting ideas in this direction, such as \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing \emph{tensorial logic} and \emph{dialogue categories} \cite{Mellies-2012}.
 

### 2015-02-02 main/LMCS.tex
Use \capsabbrev where appropriate

@@
 
-\title{Proof equivalence in MLL is PSPACE-complete}
+\title{Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}
 
@@
 There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for \capsabbrev{mll}.
-We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our PSPACE-hardness reduction.
+We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our \capsabbrev{pspace}-hardness reduction.
 In this section we will discuss how this notion of proof net arises from the sequent calculus, and introduce a compact notation for it.
@@
 The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-This problem is PSPACE-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.
+This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.
 
@@
 \emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
-This is the problem shown to be PSPACE-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:
+This is the problem shown to be \capsabbrev{pspace}-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:
 
@@
 
-The PSPACE-completeness of NCG-reconfiguration may seem surprising at first.
+The \capsabbrev{pspace}-completeness of \capsabbrev{ncg}-reconfiguration may seem surprising at first.
 To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed.

### 2015-02-02 main/LMCS.tex
Introduction

@@
 proof.
-
-Linear logic was formulated as a sequent calculus system, and doesn’t have a corresponding
+%
+Linear logic was formulated as a sequent calculus system, and doesn't have a corresponding
 natural deduction in the classical sense. The role of natural deduction is taken instead by
@@
 Proof nets do not work so well when the logical units 1 and $\bot$ are included. Although
-proof nets can still be defined in this case, they are no longer canonical. It has not
-
-\cite{Lambek-1968}
-
-\cite{Girard-1987,Danos-Regnier-1989}
-\cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}
-\cite{Koh-Ong-1999}
-\cite{Lamarche-Strassburger-2006}
-\cite{Hughes-2012-categories,Hughes-2012-nets}
-
-\cite{Hughes-vanGlabbeek-2005}
-\cite{Heijltjes-2011}
-
-\cite{Demaine-Hearn-2008}
-
-\cite{ReconfigurationProblems}
-\cite{Kanovich-1992,Lincoln-Winkler-1994}.
+proof nets can still be defined in this case, they are no longer canonical. Firstly the
+translation from proofs to proof nets is not canonical, so a proof may be translated
+to several possible proof nets with no privileged choice. Also, equivalent proofs are not
+in general translated to the same possible proof nets. So proof nets lose their principal
+advantage, compared to proofs, of being canonical, and are subject to a non-trivial
+equivalence relation.
+
+Equivalence of proofs (in the sense we are interested in here) was first considered
+by Lambek \cite{Lambek-1968}, who introduced the idea of category-theoretic logic and used
+it to define a natural notion of equivalence of proofs.
+
+Proof nets were introduced at the birth of linear logic by Girard \cite{Girard-1987}, and
+the correctness criterion was simplified by Danos and Regnier \cite{Danos-Regnier-1989}.
+These proof nets did not include the logical units, and are canonical for multiplicative linear logic.
+%
+Canonical proof nets also exist for larger fragments of linear logic, such as the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
+Canonical proof nets may also be defined for \emph{intuitionistic} multiplicative linear logic with units.
+
+Proof nets incorporating units were defined by Blute, Cockett, Seely and Trimble \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}, though these proof nets cease to be canonical.
+The `joker games' of Koh and Ong \cite{Koh-Ong-1999} have a very similar structure to proof nets, and include units.
+Another explicit treatment of proof nets for \capsabbrev{mll} with units is given by Lamarche and Stra\ss burger \cite{Lamarche-Strassburger-2006}, and later a particularly simple and elegant version by Hughes \cite{Hughes-2012-categories,Hughes-2012-nets}.
+
+The idea of the present work is to look at proof equivalence through the lens of computational
+complexity, and use this to settle the question of whether there can be canonical proof nets
+for \capsabbrev{mll} with units. The canonical proof nets for \capsabbrev{mll} without units
+give an efficient decision procedure for proof equivalence: to decide whether two such proofs
+are equivalent, it is sufficient to translate both to proof nets and compare the proof nets
+for equality.
+
+The corresponding decision procedure for \capsabbrev{mll} \emph{with} units is shown to be
+\capsabbrev{pspace}-complete, which is generally supposed to preclude the existence of a
+polynomial-time algorithm for this problem. So there can be no canonical proof nets in the
+usual sense: if the proof nets are syntactically equal just when their corresponding proofs
+are equivalent, then the translation from proofs to proof nets must be intractable.
 
@@
 The literature contains several interesting ideas in this direction, such as \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing \emph{tensorial logic} and \emph{dialogue categories} \cite{Mellies-2012}.
+
+Our proof of \capsabbrev{pspace}-completeness uses the \emph{nondeterministic constraint logic} of \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation}. This is a graph rewriting
+system introduced as a tool for use in complexity proofs, originally for games and puzzles.
+
+It is not uncommon for an \capsabbrev{np}-complete problem to have an associated reconfiguration problem that is \capsabbrev{pspace}-complete \cite{ReconfigurationProblems}; an example of this is \capsabbrev{sat}-reconfiguration.
+\capsabbrev{mll} proof equivalence may be regarded as the reconfiguration problem associated with \capsabbrev{mll} proof search, which is \capsabbrev{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
 

### 2015-06-17 main/LMCS.tex
Wording tweak
added reviews

@@
 for equality.
-
-The corresponding decision procedure for \capsabbrev{mll} \emph{with} units is shown to be
+%
+We show that the corresponding decision procedure for \capsabbrev{mll} \emph{with} units is
 \capsabbrev{pspace}-complete, which is generally supposed to preclude the existence of a
@@
 \end{document}
-
-\newpage
-
-%\acks
-
-We would like to thank Lutz Stra{\ss}burger for comments and discussion, and the anonymous referees for their constructive observations.
-
-%===========================
-\bibliographystyle{plain}
-\bibliography{LMCS}
-\end{document}
-%===========================
-
-\end{document}

### 2015-06-24 Reviews LMCS/Response.txt
many updates

We thank the referees for their careful reading of our paper, and for the detailed and helpful feedback they have provided. Here, we will discuss each review in turn, as well as the changes we have made in response. We omit comments whose

Review 1

p.1, l.-1: "Canonical proof nets may also be defined for intuitionistic MLL with units": are you referring to (some of) the same papers you cite in the next paragraphs (i.e. Blute et al., Trimble, Lamarche, etc.)?  In any case, you should add a reference here.

*** We have tried and failed to find a decent reference for the kind of proof nets we have in mind here, although private discussions have convinced us that the issue is quite widely understood. The principle is simple: re-wiring jumps towards the unique conclusion yields a canonical form. But Lamarche's "essential nets", extended with units by Murawski and Ong (both of which we have added as a reference), attach jumps to the leaves of the tree instead.

p.10, notations: why do you use a "prime" in your notation for sequents/formulas?  I mean, why n' (in a circle) instead of just n?  Since n',i',j', etc. are common notations for variables (as n,i,j...), the notation is quite misleading at first.

*** The prime is used as a notation for 'successor', to indicate that a node labelled n' has n + 1 bottoms or ones, while n' and m' connect to (n+m)'.

p.25, Definition 37: I find this definition a bit disturbing, it seems ad hoc at first and leaves one wondering whether something is wrong with your encoding. [...]

*** We agree that the purpose of Definition 37 is not well-explained. We have opted for an orthogonal solution: we now explicitly define the translation of an instance of NCL-reconfiguration (which consists of a constraint graph with two configurations).

p.30, Theorem 46: just a minor quibble: you could make explicit the reduction from NCG-reconfiguration to the proof net equivalence problem, in order for the reader to better understand the complexity of such a reduction, which must be at least polytime computable. [...]

 ??? We have also made the complexity of this translation more explicit (in Theorem 46).

Review 2

I have the impression that the authors do not realize the importance of their own result.
From the point of view of the theory of proof nets, the problem concerns how to deal with lack of connectedness. It is formulated in terms of the multiplicative units but this is just for technical convenience. The reason why the problem is relevant is the fact that the bottom unit is a variant of the weakening rule, one of the cornerstones of linear logic. The multiplicative units can indeed be easily encoded by the exponentials (fix a type A and let 1 be encoded as an axiom on A, whose conclusions are connected by a par and then wrapped in a promotion, i.e. !(A^\perp \par A), and let bottom be the weakening on the dual formula). Therefore PSPACE­-completeness of proof equivalence for MLL implies PSPACE­hardness of proof equivalence for MELL. This is the real issue, as the exponentials are the expressive core of linear logic. Essentially, the paper proves that proof nets for MELL are intractable, unless ad-­hoc notions as the mix rules are added, or intractability is encapsulated in the translation from proofs to nets. Such a consequence is not explained in the paper, while there is no doubt that it has to be mentioned as it is the main reason of interest for the result.

Another issue concerns the paragraph of the introduction that mentions the fragments of linear logic for which canonical proof nets are known. I think that the polarized case should be added. Moreover it is said that Intuitionistic MLL with units has a canonical presentation but
no citations are given. Of course, *a citation has to be given*, but that is not the point. Given the results in the paper, Intuitionistic (ME)LL is the only hope for a tractable and expressive theory of proof nets. The intuitionistic case should then be discussed precisely, explaining the differences with the classical case. The canonical presentation of the intuitionistic case that the authors have in mind probably relies on jumps, and thus rewiring and proof equivalence make sense there too. Why is that case tractable? And does tractability rely on the fact that cut­-elimination in the linear case is trivial? Would Intuitionistic MELL be tractable as well?

I also find the third paragraph of page 2 (“Since there can be no canonical representation...”) unsatisfying. It points to alternative ideas in the literature to define the identity of proofs. They have to be discussed, at least briefly. At present the alternative approaches are just cited, without giving any hint of why they would help to treat the units.
I am also surprised by the total absence of a discussion of the case of MLL with the MIX rules.
A better treatment of the context of the problem cannot be avoided, because it is the reason why the result is interesting. Moreover, it is also the reason that justifies to not take too seriously the many technicalities of the

Review 3

- p.21: the bijection associates f(1) to j and c(3) to f

*** In fact, the association f(1)-f and c(3)-c in the paper is correct: each edge from parent to child is associated with the child.

### 2015-06-30 Reviews LMCS/Response.txt
some intro changes

@@
 
-*** We agree that the purpose of Definition 37 is not well-explained.
-We have opted for an orthogonal solution: we now explicitly define the translation of an instance of NCL-reconfiguration (which consists of a constraint graph with two configurations).
+*** We agree that Definition 37 is not well-explained.
+We have opted for the following solution: we now explicitly define the translation of an instance of NCL-reconfiguration (which consists of a constraint graph with two configurations).
 
@@
 
-I have the impression that the authors do not realize the importance of their own result.
-From the point of view of the theory of proof nets, the problem concerns how to deal with lack of connectedness.
-It is formulated in terms of the multiplicative units but this is just for technical convenience.
-The reason why the problem is relevant is the fact that the bottom unit is a variant of the weakening rule, one of the cornerstones of linear logic.
-The multiplicative units can indeed be easily encoded by the exponentials (fix a type A and let 1 be encoded as an axiom on A, whose conclusions are connected by a par and then wrapped in a promotion, i.e.
-!(A^\perp \par A), and let bottom be the weakening on the dual formula).
-Therefore PSPACE­-completeness of proof equivalence for MLL implies PSPACE­hardness of proof equivalence for MELL.
-This is the real issue, as the exponentials are the expressive core of linear logic.
-Essentially, the paper proves that proof nets for MELL are intractable, unless ad-­hoc notions as the mix rules are added, or intractability is encapsulated in the translation from proofs to nets.
-Such a consequence is not explained in the paper, while there is no doubt that it has to be mentioned as it is the main reason of interest for the result.
+I have the impression that the authors do not realize the importance of their own result. [...]
 
-Another issue concerns the paragraph of the introduction that mentions the fragments of linear logic for which canonical proof nets are known.
-I think that the polarized case should be added.
-Moreover it is said that Intuitionistic MLL with units has a canonical presentation but
-no citations are given.
-Of course, *a citation has to be given*, but that is not the point.
+*** While we were aware that MELL- may encode MLL, we indeed did not realise that the consequence of our result (that MELL has no canonical normal forms) would be unexpected or considered interesting.
+And we remain cautious: surely proof equivalence for MELL is completely dominated by the complexity of cut-elimination?
+We have added a paragraph to this effect to the introduction.
+
+Another issue concerns the paragraph of the introduction that mentions the fragments of linear logic for which canonical proof nets are known. I think that the polarized case should be added.
+
+Moreover it is said that Intuitionistic MLL with units has a canonical presentation but no citations are given.
+[...] Of course, *a citation has to be given*, but that is not the point.
 Given the results in the paper, Intuitionistic (ME)LL is the only hope for a tractable and expressive theory of proof nets.
@@
 Would Intuitionistic MELL be tractable as well?
+
+*** We have expanded the explanation of IMLL proof nets that we have in mind.
+(See also above in the response to Review 1.) We view intuitionistic LL as one of several alternatives to classical LL (as remarked on in the next comment).
 
@@
 Moreover, it is also the reason that justifies to not take too seriously the many technicalities of the
+*** While in principle we agree that these alternatives could be discussed in more detail, the general picture is simply that each drops one or more of the axioms of a *-autonomous category.
+We did not want to turn this
 
@@
 
-*** In fact, the association f(1)-f and c(3)-c in the paper is correct: each edge from parent to child is associated with the child.
+*** In fact, the association f(1)-f and c(3)-c in the paper is correct: each edge from parent to child is associated with the child. We have amended the formulation of this bijection for clarity.

### 2015-06-30 main/LMCS.tex
some intro changes

@@
 
-\shortJournalNames
+\longJournalNames
 \makeTheoremDefs
@@
 \newcommand\Perm{\mathbf\sim}
+
+\newcommand\ap{'}
 
@@
 Canonical proof nets also exist for larger fragments of linear logic, such as the combined multiplicative-additive fragment without units \cite{Hughes-vanGlabbeek-2005}, and the additive fragment, including the additive units \cite{Heijltjes-2011}.
-Canonical proof nets may also be defined for \emph{intuitionistic} multiplicative linear logic with units.
+% Canonical proof nets may also be defined for \emph{intuitionistic} multiplicative linear logic with units.
 
 Proof nets incorporating units were defined by Blute, Cockett, Seely and Trimble \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}, though these proof nets cease to be canonical.
-The `joker games' of Koh and Ong \cite{Koh-Ong-1999} have a very similar structure to proof nets, and include units.
+The `joker games' of Koh and Ong \cite{Koh-Ong-1999}, for MLL and its intuitionistic variant IMLL, have a very similar structure to proof nets, and include units.
 Another explicit treatment of proof nets for \capsabbrev{mll} with units is given by Lamarche and Stra\ss burger \cite{Lamarche-Strassburger-2006}, and later a particularly simple and elegant version by Hughes \cite{Hughes-2012-categories,Hughes-2012-nets}.
+
+% NEW
+
+The difficulty with the multiplicative units is that each instance of $\bot$, the unit to the par, must be attached to the main proof structure, while there isn't always a canonical point where to attach it.
+In the sequent calculus, $\bot$-instances are introduced by a weakening rule, which permutes with many (but not all) other rules.
+In proof nets, $\bot$-instances are commonly attached by edges called jumps, which may be re-attached via local graph-rewrite rules \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}.
+For intuitionistic MLL the rewrite rules may be directed towards the unique conclusion, to yield canonical forms.\footnote{The canonical representation for IMLL described here appears to be folklore; established proof nets for intuitionistic linear logic, called essential nets \cite{Lamarche-2008,Murawsky-Ong-2003}, (non-canonically) attach jumps to the leaves of the formula tree, for easier composition.}
+For classical MLL with units however, there is not an obvious preferred point to attach jumps.
+And this problem extends to multiplicative--exponential linear logic (MELL) without units, where a formula $?A$ may be introduced via a weakening rule with similar permutability to the $\bot$-introduction rule.
+
+% OLD
 
@@
 
+% NEW
+
+The result has a similar consequence for MELL without units, which may emulate the unit $\bot$ via carefully chosen formulae $?A$: equivalence of MELL proofs in normal form is \capsabbrev{pspace}-hard.
+This is in sharp contrast with many intuitionistic calculi such as the simply typed lambda-calculus, where normal forms are unique.
+However, it does not impact the complexity of proof equivalence for MELL in general, which is dominated by cut-elimination (MELL encodes the simply-typed lambda-calculus, which is not elementary recursive \cite{Statman-1977}).
+
 % It should be stressed that to consider MLL proofs modulo equivalence is a choice---one that is well motivated by semantics, but a choice nonetheless.
@@
 
-Since there can be no canonical representation of multiplicative linear logic proofs in accordance with the categorical semantics, it is tempting to consider other ways of defining the identity of proofs.
-The literature contains several interesting ideas in this direction, such as \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing \emph{tensorial logic} and \emph{dialogue categories} \cite{Mellies-2012}.
+%Since there can be no canonical representation of multiplicative linear logic proofs in accordance with the semantics of *-autonomous categories,
+
+Given our results for classical linear logic, which effectively rule out canonical forms for MELL, it becomes tempting to consider possible alternatives.
+One is intuitionistic linear logic, mentioned above.
+Another is Melli\`es's game-semantics inspired \emph{tensorial logic} \cite{Mellies-2012}, which embeds linear logic via a double-negation translation.
+Furthermore, the \emph{polarised} fragment of linear logic has canonical proof nets \cite{Laurent-1999}.
+A different direction to the above three, aimed more at proof search than semantics of programming, is \emph{focusing}, which retains classical linear logic but weakens the notion of proof equivalence; this gives canonical representations in \emph{focused proof nets} \cite{Andreoli-Maieli-1999} and \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}.
+
+% OLD
 
@@
 \capsabbrev{mll} proof equivalence may be regarded as the reconfiguration problem associated with \capsabbrev{mll} proof search, which is \capsabbrev{np}-complete \cite{Kanovich-1992,Lincoln-Winkler-1994}.
+
+% NEW
+
+This paper is an extended version of \cite{Heijltjes-Houston-2014}.
+
+% OLD
 
@@
 An edge $\edge a{\links(a)}$ in a proof net or switching graph is called a \emph{link} or a \emph{jump}, and may also be indicated $\jump a{\links(a)}$, to match the illustrations.
-Note that unlike the axiom links of proof nets without units, a jump may connect to any connective or unit, and multiple jumps may point to the same position.
+Note that unlike the axiom links of proof nets without units, a jump may connect to any connective or unit, even another $\bot$-instance, and multiple jumps may point to the same position.
 A path between vertices $a$ and $b$ in a switching graph is indicated as $\path ab$.
@@
 
-\section{Proof complexity}
+\section{Encoding numerical constraints}
+
+In this section we will show how numerical constraints may be encoded in \capsabbrev{mll}, a necessary ingredient for our main construction.
+We will illustrate the ideas with an example: an encoding of 3-partition into the problem of \capsabbrev{mll} proof search.
 
@@
 	\end{scope}
-	\node[big_] (A) at (14,0) {$2'$};
-	\node[big_] (B) at (16,0) {$3'$};
-	\node[big1] (!) at (15,3) {$5'$};
+	\node[big_] (A) at (14,0) {$2\ap$};
+	\node[big_] (B) at (16,0) {$3\ap$};
+	\node[big1] (!) at (15,3) {$5\ap$};
 	\draw[rounded corners] ($(!) + (-1.2,-.8)$) rectangle ($(!) + (1.2,.8)$);
@@
 A_n$.
-In diagrammatic notation, a big disc labelled $n'$ will represent the formula $\bigtn(\bot^{n+1})$, and a big circle labelled $n'$ will represent the sequent $\1^{n+1}$.
+In diagrammatic notation, a big disc labelled $n\ap$ will represent the formula $\bigtn(\bot^{n+1})$, and a big circle labelled $n\ap$ will represent the sequent $\1^{n+1}$.
 A formula $\bigparr(\1^{n+1})$ is represented by a disc enclosed in a box.
@@
 \begin{array}{c}
-	\vc{\begin{tikzpicture}[x=5mm,y=5mm,octo] \node[big_] {$k'$}; \end{tikzpicture}} ~=~
-	\vc{\begin{tikzpicture}[x=5mm,y=5mm,octo] \draw (0,0) node[big_] {$i'$} -- (2,0) node[big_] {$j'$}; \end{tikzpicture}}
+	\vc{\begin{tikzpicture}[x=5mm,y=5mm,octo] \node[big_] {$k\ap$}; \end{tikzpicture}} ~=~
+	\vc{\begin{tikzpicture}[x=5mm,y=5mm,octo] \draw (0,0) node[big_] {$i\ap$} -- (2,0) node[big_] {$j\ap$}; \end{tikzpicture}}
 	\\ \\ (k=i+j+1)
@@
   \vc{\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-2,0) {$i_1'$};
-	\node[big_] (B) at ( 2,0) {$i_k'$};
-	\node[big1] (!) at ( 0,3) {$n'$};
+	\node[big_] (A) at (-2,0) {$i_1\ap$};
+	\node[big_] (B) at ( 2,0) {$i_k\ap$};
+	\node[big1] (!) at ( 0,3) {$n\ap$};
 	\node at (0,0) {$\dots$};
@@
 \begin{tikzpicture}[x=10mm,y=8mm,octo]
-	\node[big1] (a) at (2,0) {$k'$};
-	\node[big1] (b) at (5,0) {$k'$};
-	\node[big1] (c) at (11,0) {$k'$};
+	\node[big1] (a) at (2,0) {$k\ap$};
+	\node[big1] (b) at (5,0) {$k\ap$};
+	\node[big1] (c) at (11,0) {$k\ap$};
 	\draw[rounded corners] (1,-.5) rectangle (3,.5);
@@
 	\foreach \i in {1,...,6} {
-		\node[big_] (\i) at (\i,2) {$i'_{\i}$};
+		\node[big_] (\i) at (\i,2) {$i\ap_{\i}$};
 	}
@@
 	\node[big_] (8) at (11,2) {};
-	\node[big_] (9) at (12,2) {$i'_{3n}$};
+	\node[big_] (9) at (12,2) {$i\ap_{3n}$};
 	%
@@
 This idea will form the basis of our encoding of non-deterministic constraint logic.
-
-%------------------------------------------------------------
-
-\section{Constraint logic}
-\label{sec:ncl}
-
-\emph{Non-deterministic constraint logic} (NCL) \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, introduced as a convenient tool for \capsabbrev{pspace}-hardness reduction.
-It is exactly for this purpose that we shall use it.
-
-The graphs of NCL, called \emph{constraint graphs}, have directed, weighted edges, and a rewrite step (or \emph{move}) consists of reversing the direction of exactly one edge.
-Each vertex in a constraint graph has an \emph{inflow constraint}, a natural number value, and moves are required to preserve the property that the \emph{inflow} at each vertex, the sum weight of its incoming edges, never drops below the inflow constraint (i.e.\ the inflow constraint dictates a \emph{minimum} inflow).
-
-The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.
-
-We will need no such restrictions, and will encode the general case.
-However, for simplicity of exposition, in the examples of constraint graphs in this section we will use the following conventions.
-Edges will have weight 1 or 2; those of weight 1 are drawn as thin red arrows, and those of weight 2 as thicker blue arrows.
-Vertices with inflow constraint 2 are drawn as grey circles.
-For convenience, we will assume that dangling edges are connected to vertices of weight zero, which are omitted from illustrations.
-These zero-inflow vertices can be seen as ``connection points'', where the graph may be connected to a wider network of graphs.
-
-An example rewrite sequence is given in Figure~\ref{fig:NCL example}.
-This particular specimen encodes a logical conjunction, and is not unlike an \textsc{and}-gate: in order to invert the weight 2 edge on the right, both weight 1 edges on the left must be inverted first.
-
-\begin{figure}
-\[
-	\andexample 1 \quad\perm*\quad
-	\andexample 2 \quad\perm*\quad
-	\andexample 3 \quad\perm*\quad
-	\andexample 4
-\]
-\caption{A series of reconfiguration steps in a constraint graph}
-\label{fig:NCL example}
-\end{figure}
-
-In the formal definition, a constraint graph is an \emph{undirected} graph, for which a \emph{configuration} assigns an orientation to each edge.
-It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where the direction of edges may be left undefined, as long as the inflow constraints are satisfied by the directed edges.
-We will use $\star$ to indicate an undefined value, to avoid overloading $\bot$.
-
-\begin{definition} 
-A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of:
-\begin{itemize}
-	\item $V$ a set of vertices,
-	\item $E$ a set of edges,
-	\item $c\colon V\to\mathbb N$ an \emph{inflow constraint} on each vertes,
-	\item $v\colon E\to\mathcal P(V)$ where $|v(e)|\in\{1,2\}$ for $e\in E$, a set of 1 or 2 vertices for each edge,
- 	\item $w\colon E\to\mathbb N$ a \emph{weight} on each edge.
-\end{itemize}
-\end{definition}
-
-\begin{definition}
-A \emph{(partial) configuration} for a constraint graph $G=(V,E,c,v,w)$ is a (partial) function $\gamma\colon E\to V$ such that
-\begin{itemize}
-	\item
-for every edge $e$, $\gamma(e)\in v(e)\cup\{\star\}$,
-	\item
-for every vertex $v$,
-\[
-	c(v) \leq \sum\{w(e)\mid\gamma(e)=v\}~.
-\]
-\end{itemize} 
-\end{definition}
-
-In the above definition, the first condition states that the weight of an edge may be assigned only to one of its vertices, or left undefined, but not to any other vertex in the constraint graph.
-The second condition states that the total weight of its incoming edges of a vertex must be at least its inflow constraint.
-
-We will write $\gamma[e\mapsto v]$ for the partial configuration that directs $e$ to $v$, and any other edge $e'$ to $\gamma(e')$.
-An edge that may be reversed will be called \emph{mobile}.
-Formally, an edge $e$ in $\gamma$ is \emph{mobile} if $\gamma[e\mapsto\star]$ is a partial configuration.
-
-\begin{definition}
-A \emph{reconfiguration step} $(\perm*)$ relates two partial configurations for $G$ that differ in value (or definedness) on exactly one edge:
-\[
-	\gamma[e\mapsto u]~\perm*~\gamma[e\mapsto w]\qquad\text{ if }u\neq w\text{ and }u,w\in v(e)\cup\{\star\}~.
-\]
-The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
-\end{definition}
-
-\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
-This is the problem shown to be \capsabbrev{pspace}-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:
-
-\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
-\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
-\end{theorem}
-
-To show that this result extends to our setting, with partial configurations, we have the following proposition.
-
-\begin{proposition}
-\label{prop:partial simulates total reconfiguration}
-For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
-\end{proposition}
-
-\begin{proof}
-By the following two observations: firstly, 
-%
-if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
-%
-if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
-%
-\end{proof}
-
-The \capsabbrev{pspace}-completeness of \capsabbrev{ncg}-reconfiguration may seem surprising at first.
-To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed.
-The existence of such rewiring sequences is an essential property for the hardness result: if reconfiguration sequences could be given a polynomial bound, they would be polynomial-time witnesses, placing the problem within NP.
-
-The example is then as follows.
-Figure~\ref{fig:boats} gives a reconfiguration sequence, clockwise from the top left, on a constraint graph with two connection points, top and bottom.
-As such, the graph is meant to replace a single edge from top to bottom, and the reconfiguration sequence inverts the direction of this would-be edge.
-The key point is that in doing so, the central horizontal edge must be inverted \emph{twice}.
-Then by nesting the graph within itself, where one graph replaces the central edge of another, as illustrated in Figure~\ref{fig:big boat}, a graph is created with an edge that requires 4 inversions.
-Each added level of nesting doubles the number of inversions that the central edge must make, while growing the graph by only a constant factor.
-Thus, the length of a rewiring path may grow exponentially with the size of the graph.
-
-\begin{figure}
-\[
-\begin{array}{ccccccccc}
-	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
-	\\ \\ &&&&&&&& \perm \\ \\
-	\boat9 &\perm& \boat8 &\perm& \boat7 &\perm& \boat6 &\perm& \boat5
-\end{array}
-\]
-\caption{A reconfiguration path requiring two inversions of a single edge}
-\label{fig:boats}
-\end{figure}
-
-\begin{figure}
-\[
-	\boats
-\]
-\caption{Nesting graphs to grow reconfiguration paths exponentially}
-\label{fig:big boat}
-\end{figure}
-
-%------------------------------------------------------------
-
-\section{Encoding constraint logic}
-\label{sec:encoding}
-
-We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
-A sequent will encode a constraint graph, and a proof net a configuration, such that rewiring  the proof net corresponds to reconfiguration.
-
-The natural basis of the encoding is the use of jumps to indicate where the weight of an edge is allocated.
-The main problem is then how to restrict the movement of such jumps, so that they may assign weight only to the vertices of one particular edge, and not to any other vertices.
-The central design idea of our encoding is to use the combinatorics of connecting formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ to solve this problem.
-
-The two basic components of our encoding will be \emph{weight elements}, representing the weight value of edges, and \emph{constraint elements}, which encode the inflow constraint of vertices.
-For now, we will work under the assumption that each unit of weight on an edge is encoded by exactly one weight element---later, we will amend this to use multiple weight elements for each unit of weight.
-A weight element will be a construction over a number of $\bot$-formulae, whose jumps may connect to the $\1$-formulae of a constraint element.
-
-Below top is a weight element, below bottom a constraint element.
-\[
-\begin{array}{ccc}
-	  \vc{\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	 	\node[big_] (A) at (0,0) {$i'$}; 
-	 	\node[big_] (B) at (2,0) {$j'$};
-		\node[big_] (C) at (4,0) {$k'$};
-		\draw[rounded corners] (-1,-1) rectangle (5,1);
-	  \end{tikzpicture}}
-	&=&
-	  \bigtn(\bot^{i+1})~~\pr~~\bigtn(\bot^{j+1})~~\pr~~\bigtn(\bot^{k+1})
-\\ \\
-	  \vc{\begin{tikzpicture}[x=5mm,y=5mm,octo]
-		\node[big1] (1) at (0,0) {$m'$}; 
-		\node[big1] (2) at (3,0) {$n'$};
-		\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
-		\draw (1,0)--(2,0);
-	  \end{tikzpicture}}
-	&=&
-	  \bigparr(\1^{m+1})~\tn~\bigparr(\1^{n+1})
-\end{array}
-\]
-For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
-The value $m$ will be unique for each vertex, and used for all constraint elements in the encoding of that vertex.
-The weight element above is for an edge connecting the two vertices for which $m=i$ and $m=i+j$: with those constraint elements it is possible to form a proof net, as illustrated below.
-\[
-	\connectingElements 1 \qquad \connectingElements 2
-\]
-To ensure that a weight element may not form a proof net with a constraint element of another vertex, the values of $m$ and $n$ are chosen such that $m\equiv1$ and $n\equiv2 \pmod 3$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2\pmod 3$.
-It then becomes impossible for $m$ to equal any other sum over $i$, $j$, and $k$, so that forming a proof net requires either $m=i$ or $m=i+j$.
-
-Several further constructions are used in our encoding.
-Firstly, in a constraint graph, the sum of all weights is usually greater than the sum of all inflow constraints---otherwise, no edge can be mobile, or no configuration exists.
-Correspondingly, an encoding will have weight elements not connected to constraint elements.
-These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as shown below.
-A weight element that is connected to absorbers will be called \emph{free}.
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {}; 
-	\node[big_] (B) at (2,0) {};
-	\node[big_] (C) at (4,0) {};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-	\node[big1] (1) at (7.5,0) {};
-	\begin{scope}[thepink,->,big>]
-		\draw[bend left=30] (A) to (1);
-		\draw[bend right=30] (B) to (1);
-		\draw (C) to (1);
-	\end{scope}
-\end{tikzpicture}
-\]
-
-An edge in a constraint graph will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements, plus a single $\bot$-formula which we will refer to as the \emph{indicator}.
-Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
-\[
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big_] (A) at (0,0) {$i'$}; 
-	\node[big_] (B) at (2,0) {$j'$};
-	\node[big_] (C) at (4,0) {$k'$};
-	\draw[rounded corners] (-1,-1) rectangle (5,1);
-	\node[big_] (D) at (0,4) {$i'$}; 
-	\node[big_] (E) at (2,4) {$j'$};
-	\node[big_] (F) at (4,4) {$k'$};
-	\draw[rounded corners] (-1,3) rectangle (5,5);
-	\draw (2,1)--(2,1.5) (2,2.5)--(2,3);
-	\draw[dotted] (2,1.5)--(2,2.5);
-	\draw (2,-1)--(2,-2) node[bullet] {};
-	\path (0,-2.5)--(1,-2.5);
-\end{tikzpicture}
-\qquad\qquad
-\begin{tikzpicture}[x=5mm,y=5mm,octo]
-	\node[big1] (1) at (0,0) {$m'$}; 
-	\node[big1] (2) at (3,0) {$n'$};
-	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
-	\draw (1,0)--(2,0);
-	\node[big1] (3) at (0,4) {$m'$};
-	\node[big1] (4) at (3,4) {$n'$};
-	\draw[rounded corners] (-1,3) rectangle (1,5) (2,3) rectangle (4,5);
-	\draw (1,4)--(2,4);
-	\draw[dotted] (1.5,1.5)--(1.5,2.6);
-	\node[circ] at (1.5,-2) {};
-	\draw[rounded corners] (-1.5,-2.5) rectangle (4.5,5.5);
-\end{tikzpicture}
-\]
-The natural way for edge-gadgets to link up with a vertex-gadget is shown in Figure~\ref{fig:connect example}: indicators connect to indicator targets, and weight elements connect to constraint elements or weight absorbers.
-The illustration depicts two equivalent proof nets, both encoding the same (fragment of a) constraint graph: a single vertex that is the target of a weight-1 edge (on the left, in red) and a weight-2 edge (on the right, in blue).
-The inflow of the vertex is 3, and its constraint is 2; then 2 weight elements are connected to the constraint elements in the vertex-gadget, while one remains free (connected to weight absorbers).
-It is essential to the functioning of the encoding that any re-distribution of weight elements gives an equivalent proof net, as illustrated by the example.
-Then in the second proof net, the single weight element of the left edge-gadget is free, which means the indicator jump can be rewired to connect to a different vertex.
-
-In the encoding, the indicator jumps determine which vertex is the target of the edge, and while they may in principle assign any vertex, the weight elements of the edge-gadget can only form proof nets with the constraint elements of the correct vertices.
-An edge-gadget will be called \emph{free} if all its weight elements are free.
-The vertex-gadgets in an encoding will all be gathered in a $\tn$-formula, which means they are connected, so that free edge-gadgets may attach their indicator to any of them.
-
-\begin{figure}
-
-\noindent$\CONexample 2{.60}\hfill\perm\hfill\CONexample 1{.60}$
-
-\caption{Two edge-gadgets connecting to one vertex-gadget}
-\label{fig:connect example}
-\end{figure}
-
-In Figure~\ref{fig:big example} we give a complete encoding of the example rewiring sequence shown in Figure~\ref{fig:NCL example}, a reconfiguration sequence for a constraint graph functioning as an \textsc{and}-gate.
-The given proof nets are all equivalent, and their corresponding constraint graphs are shown near the bottom of the figure.
-The central vertex-gadget encodes the central constraint-2 vertex in the graph, while its three implicit constraint-0 vertices, at the dangling ends of the three edges, are encoded by the three formulae connected to the central gadget.
-
-\newcommand\ANDmark[1]{\makebox[0pt][r]{\Large{\textbf{#1}}}}
-
-\begin{figure}[p]
-\[
-\begin{array}{@{}r@{\hspace{16pt}}|@{\hspace{16pt}}l@{}}
-	\ANDexample 1 \ANDmark 1 & \ANDexample 2 \ANDmark 2 \\ \\ \hline \\
-	\ANDexample 3 \ANDmark 3 & \ANDexample 4 \ANDmark 4 \\ \\ \hline \\
-	\ANDexample 5 \ANDmark 5 & \ANDexample 6 \ANDmark 6 \\ \\ \hline
-\end{array}
-\]
-\vspace{20pt}
-\[
-\begin{array}{ccccccc}
-	\andexample 1 &\perm& \andexample 2 &\perm& \andexample 3 &\perm& \andexample 4 \\
-	\textbf{1} && \textbf{2} && \textbf{3~4~5} && \textbf{6}
-\end{array}
-\]
-\caption{Encoding an \textsc{and}-gate in proof nets}
-\label{fig:big example}
-\end{figure}
-
-\subsection*{Weight adjustment}
-
-So far we have assumed that one weight element may encode one unit of weight in the constraint graph.
-However, there is a minor issue that prevents this straightforward approach.
-Although one weight element cannot `fill' an inappropriate constraint element, two weight elements \emph{can}, in the way illustrated below.
-In such a situation, the weight element that should have been linked to this constraint element becomes free, and the edge it belongs to may inappropriately become free, too.
-\[
-\begin{tikzpicture}[x=5mm,y=-5mm,octo]
-	\node[big_] (A) at (-1,0) {}; 
-	\draw (.75,0) node[big_] (B1) {} -- (2.25,0) node[big_] (B2) {};
-	\node[big_] (C) at (4,0) {};
-	\draw[rounded corners] (-2,-1) rectangle (5,1);
-	\draw (7,0) node[big_] (D1) {} -- (8.5,0) node[big_] (D2) {}; 
-	\node[big_] (E) at (10.25,0) {};
-	\node[big_] (F) at (12,0) {};
-	\draw[rounded corners] (6,-1) rectangle (13,1);
-	\node[big1] (1) at (1,4) {};
-	\node[big1] (2) at (4,4) {}; 
-	\node[big1] (3) at (7,4) {};
-	\node[big1] (4) at (10,4) {};
-	\draw[rounded corners] (3,3) rectangle (5,5) (6,3) rectangle (8,5);
-	\draw (5,4)--(6,4);
-	\begin{scope}[thepink,->,big>]
-		\draw[bend right=25] (A)  to (1);
-		\draw[bend right=15] (B1) to (1);
-		\draw[bend right=25] (B2) to (2);
-		\draw[bend right=15] (C)  to (2);
-		\draw[bend left=15] (D1) to (3);
-		\draw[bend right=15] (D2) to (4);
-		\draw[bend left=20] (E)  to (4);
-		\draw[bend left=20] (F)  to (4);
-	\end{scope}
-\end{tikzpicture}
-\]
-To resolve this issue, it is sufficient to increase the number of weight elements used to encode one unit of weight. In the following, we will investigate how many are needed.
-
-In an inappropriate linking as shown above, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the switching condition would be violated.
-That means the weight elements must belong to different edges.
-
-As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
-Consequently, a weight element can fill three halves, but only of different constraint elements.
-The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
-To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
-To fill $3n$ constraint elements inappropriately therefore requires $n+1$ edges.
-It thus suffices to encode one unit of weight on an edge by $3\times|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly to encode one unit of inflow constraint by $3\times|E|$ constraint elements.
-
-\subsection*{The complete encoding}
-
-The complete encoding of a constraint graph $G$ will then be a sequent $\Gamma$ consisting of:
-%
-\begin{enumerate}
- 	\item
-all vertex-gadgets, combined in a single formula via tensors, 
-	\item
-all edge-gadgets as individual formulae, and
-	\item
-a sufficient number of weight absorbers ($\1$-formulae).
-\end{enumerate}
-%
-A configuration for $G$ will be encoded as a proof net for $\Gamma$, and conversely each proof net for $\Gamma$ may be interpreted as a (partial) configuration for $G$.
-The encoding will be made formal in Section~\ref{sec:correctness}; first we will establish some basic results for rewiring on proof nets.
 
@@
 In the graph for $\links$ and $\Gamma$, a box $\bx(v)$ may be \emph{closed} by replacing the subgraph over $\bx(v)$ by the single vertex $v$, and replacing every arc into $\bx(v)$ by one onto $v$.
-For each box $\bx(v)$ we define the \emph{local graph} to be that formed by the subgraph over $\bx(v)$ where each immediately smaller box $\bx(v)<\bx(v)$ is closed.
+For each box $\bx(v)$ we define the \emph{local graph} to be that formed by the subgraph over $\bx(v)$ where each immediately smaller box $\bx(w)<\bx(v)$ is closed.
 The following is then a variation on the local retraction algorithm by Danos \cite{Danos-1990}.
@@
 \begin{definition}
-The \emph{empire} $\emp v$ of a vertex $v$ in $(\Gamma,\links)$ is the smallest subnet $(\Delta,\links')$ of which $v$ is a port.
+The \emph{empire} $\emp v$ of a vertex $v$ in $(\Gamma,\links)$ is the largest subnet $(\Delta,\links')$ of which $v$ is a port.
 \end{definition}
@@
 Taking a different perspective, we may alternatively consider a switching graph as a directed tree, rooted in the root connective of $\Gamma$.
-This establishes a bijection between the edges and the non-root vertices, which associates each edge with its target vertex.
+This establishes a bijection between the non-root vertices and the edges, which associates vertex with the edge connecting it to its parent.
 
@@
 The example in Figure~\ref{fig:directed switching graph} displays a proof net on the left, and on the right the switching graph choosing the edge $\edge ij$ for the par $i$, and the edge $\edge rg$ for the root par $r$.
-The induced bijection associates for example the edge named $r(1)$ with the vertex $g$, the edge $g(1)$ with $h$, and the edge $h(1)$ with $a$; it further associates $f(1)$ with $f$ and $c(3)$ with $c$.
+The induced bijection associates for example the vertex $g$ and the edge named $r(1)$, the the vertex $h$ and the edge $g(1)$, and the vertex $a$ and the edge $h(1)$; it further associates $f$ with $f(1)$, and $c$ with $c(3)$.
 
@@
 We will show that, similarly, equivalence for basic sequents is determined by parity.
-An immediate observation is that a proof net for a basic sequent with only one tensor-formula, every $\1$ is linked to by exactly one jump---which means that no rewiring is possible.
+An immediate observation is that a proof net for a basic sequent with only one tensor-formula (a formula of the form $\bigtn(\bot^n)$ for $n\geq 2$), every $\1$ is linked to by exactly one jump, which means that no rewiring is possible.
 
@@
 
+\section{Constraint logic}
+\label{sec:ncl}
+
+\emph{Non-deterministic constraint logic} (NCL) \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, introduced as a convenient tool for \capsabbrev{pspace}-hardness reduction.
+It is exactly for this purpose that we shall use it.
+
+The graphs of NCL, called \emph{constraint graphs}, have directed, weighted edges, and a rewrite step (or \emph{move}) consists of reversing the direction of exactly one edge.
+Each vertex in a constraint graph has an \emph{inflow constraint}, a natural number value, and moves are required to preserve the property that the \emph{inflow} at each vertex, the sum weight of its incoming edges, never drops below the inflow constraint (i.e.\ the inflow constraint dictates a \emph{minimum} inflow).
+
+The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
+This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.
+
+We will need no such restrictions, and will encode the general case.
+However, for simplicity of exposition, in the examples of constraint graphs in this section we will use the following conventions.
+Edges will have weight 1 or 2; those of weight 1 are drawn as thin red arrows, and those of weight 2 as thicker blue arrows.
+Vertices with inflow constraint 2 are drawn as grey circles.
+For convenience, we will assume that dangling edges are connected to vertices of weight zero, which are omitted from illustrations.
+These zero-inflow vertices can be seen as ``connection points'', where the graph may be connected to a wider network of graphs.
+
+An example rewrite sequence is given in Figure~\ref{fig:NCL example}.
+This particular specimen encodes a logical conjunction, and is not unlike an \textsc{and}-gate: in order to invert the weight 2 edge on the right, both weight 1 edges on the left must be inverted first.
+
+\begin{figure}
+\[
+	\andexample 1 \quad\perm*\quad
+	\andexample 2 \quad\perm*\quad
+	\andexample 3 \quad\perm*\quad
+	\andexample 4
+\]
+\caption{A series of reconfiguration steps in a constraint graph}
+\label{fig:NCL example}
+\end{figure}
+
+In the formal definition, a constraint graph is an \emph{undirected} graph, for which a \emph{configuration} assigns an orientation to each edge.
+It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where the direction of edges may be left undefined, as long as the inflow constraints are satisfied by the directed edges.
+We will use $\star$ to indicate an undefined value, to avoid overloading $\bot$.
+
+\begin{definition} 
+A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of:
+\begin{itemize}
+	\item $V$ a set of vertices,
+	\item $E$ a set of edges,
+	\item $c\colon V\to\mathbb N$ an \emph{inflow constraint} on each vertes,
+	\item $v\colon E\to\mathcal P(V)$ where $|v(e)|\in\{1,2\}$ for $e\in E$, a set of 1 or 2 vertices for each edge,
+ 	\item $w\colon E\to\mathbb N$ a \emph{weight} on each edge.
+\end{itemize}
+\end{definition}
+
+\begin{definition}
+A \emph{(partial) configuration} for a constraint graph $G=(V,E,c,v,w)$ is a (partial) function $\gamma\colon E\to V$ such that
+\begin{itemize}
+	\item
+for every edge $e$, $\gamma(e)\in v(e)\cup\{\star\}$,
+	\item
+for every vertex $v$,
+\[
+	c(v) \leq \sum\{w(e)\mid\gamma(e)=v\}~.
+\]
+\end{itemize} 
+\end{definition}
+
+In the above definition, the first condition states that the weight of an edge may be assigned only to one of its vertices, or left undefined, but not to any other vertex in the constraint graph.
+The second condition states that the total weight of its incoming edges of a vertex must be at least its inflow constraint.
+
+We will write $\gamma[e\mapsto v]$ for the partial configuration that directs $e$ to $v$, and any other edge $e'$ to $\gamma(e')$.
+An edge that may be reversed will be called \emph{mobile}.
+Formally, an edge $e$ in $\gamma$ is \emph{mobile} if $\gamma[e\mapsto\star]$ is a partial configuration.
+
+\begin{definition}
+A \emph{reconfiguration step} $(\perm*)$ relates two partial configurations for $G$ that differ in value (or definedness) on exactly one edge:
+\[
+	\gamma[e\mapsto u]~\perm*~\gamma[e\mapsto w]\qquad\text{ if }u\neq w\text{ and }u,w\in v(e)\cup\{\star\}~.
+\]
+The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
+\end{definition}
+
+\emph{Non-deterministic constraint graph reconfiguration} or \emph{\capsabbrev{ncg}-reconfiguration} is the problem of deciding whether two total configurations of a constraint graph are connected by a sequence of reconfiguration steps.
+More formally, an instance of \capsabbrev{ncg}-reconfiguration is a triple $(G,\gamma,\delta)$ consisting of a constraint graph $G$ and two configurations $\gamma$ and $\delta$ for $G$.
+The decision problem then asks whether $\gamma\perm\delta$.
+
+This is the problem shown to be \capsabbrev{pspace}-complete by Hearne and Demaine \cite{GamesPuzzlesAndComputation}:
+
+\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
+\capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
+\end{theorem}
+
+To show that this result extends to our setting, with partial configurations, we have the following proposition.
+
+\begin{proposition}
+\label{prop:partial simulates total reconfiguration}
+For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
+\end{proposition}
+
+\begin{proof}
+By the following two observations: firstly, 
+%
+if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; and secondly,
+%
+if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where the latter is defined, then $\gamma'$ and $\gamma''$ are connected by reversing the edges on which they disagree one after another.
+%
+\end{proof}
+
+The \capsabbrev{pspace}-completeness of \capsabbrev{ncg}-reconfiguration may seem surprising at first.
+To give a feel for the dynamics that make this problem \capsabbrev{pspace}-hard, we shall exhibit an example where an exponentially-long reconfiguration sequence is needed.
+The existence of such rewiring sequences is an essential property for the hardness result: if reconfiguration sequences could be given a polynomial bound, they would be polynomial-time witnesses, placing the problem within NP.
+
+The example is then as follows.
+Figure~\ref{fig:boats} gives a reconfiguration sequence, clockwise from the top left, on a constraint graph with two connection points, top and bottom.
+As such, the graph is meant to replace a single edge from top to bottom, and the reconfiguration sequence inverts the direction of this would-be edge.
+The key point is that in doing so, the central horizontal edge must be inverted \emph{twice}.
+Then by nesting the graph within itself, where one graph replaces the central edge of another, as illustrated in Figure~\ref{fig:big boat}, a graph is created with an edge that requires 4 inversions.
+Each added level of nesting doubles the number of inversions that the central edge must make, while growing the graph by only a constant factor.
+Thus, the length of a rewiring path may grow exponentially with the size of the graph.
+
+\begin{figure}
+\[
+\begin{array}{ccccccccc}
+	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
+	\\ \\ &&&&&&&& \perm \\ \\
+	\boat9 &\perm& \boat8 &\perm& \boat7 &\perm& \boat6 &\perm& \boat5
+\end{array}
+\]
+\caption{A reconfiguration path requiring two inversions of a single edge}
+\label{fig:boats}
+\end{figure}
+
+\begin{figure}
+\[
+	\boats
+\]
+\caption{Nesting graphs to grow reconfiguration paths exponentially}
+\label{fig:big boat}
+\end{figure}
+
+%------------------------------------------------------------
+
+\section{Encoding constraint logic}
+\label{sec:encoding}
+
+We will demonstrate the \capsabbrev{pspace}-hardness of \capsabbrev{mll} proof equivalence by an encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof nets.
+A sequent will encode a constraint graph, and a proof net a configuration, such that rewiring  the proof net corresponds to reconfiguration.
+
+The natural basis of the encoding is the use of jumps to indicate where the weight of an edge is allocated.
+The main problem is then how to restrict the movement of such jumps, so that they may assign weight only to the vertices of one particular edge, and not to any other vertices.
+The central design idea of our encoding is to use the combinatorics of connecting formulae of the form $\bigtn(\bot^n)$ to formulae $\bigparr(1^m)$ to solve this problem.
+
+The two basic components of our encoding will be \emph{weight elements}, representing the weight value of edges, and \emph{constraint elements}, which encode the inflow constraint of vertices.
+For now, we will work under the assumption that each unit of weight on an edge is encoded by exactly one weight element---later, we will amend this to use multiple weight elements for each unit of weight.
+A weight element will be a construction over a number of $\bot$-formulae, whose jumps may connect to the $\1$-formulae of a constraint element.
+
+Below top is a weight element, below bottom a constraint element.
+\[
+\begin{array}{ccc}
+	  \vc{\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	 	\node[big_] (A) at (0,0) {$i\ap$}; 
+	 	\node[big_] (B) at (2,0) {$j\ap$};
+		\node[big_] (C) at (4,0) {$k\ap$};
+		\draw[rounded corners] (-1,-1) rectangle (5,1);
+	  \end{tikzpicture}}
+	&=&
+	  \bigtn(\bot^{i+1})~~\pr~~\bigtn(\bot^{j+1})~~\pr~~\bigtn(\bot^{k+1})
+\\ \\
+	  \vc{\begin{tikzpicture}[x=5mm,y=5mm,octo]
+		\node[big1] (1) at (0,0) {$m\ap$}; 
+		\node[big1] (2) at (3,0) {$n\ap$};
+		\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
+		\draw (1,0)--(2,0);
+	  \end{tikzpicture}}
+	&=&
+	  \bigparr(\1^{m+1})~\tn~\bigparr(\1^{n+1})
+\end{array}
+\]
+For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
+The value $m$ will be unique for each vertex, and used for all constraint elements in the encoding of that vertex.
+The weight element above is for an edge connecting the two vertices for which $m=i$ and $m=i+j$: with those constraint elements it is possible to form a proof net, as illustrated below.
+\[
+	\connectingElements 1 \qquad \connectingElements 2
+\]
+To ensure that a weight element may not form a proof net with a constraint element of another vertex, the values of $m$ and $n$ are chosen such that $m\equiv1$ and $n\equiv2 \pmod 3$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2\pmod 3$.
+It then becomes impossible for $m$ to equal any other sum over $i$, $j$, and $k$, so that forming a proof net requires either $m=i$ or $m=i+j$.
+
+Several further constructions are used in our encoding.
+Firstly, in a constraint graph, the sum of all weights is usually greater than the sum of all inflow constraints---otherwise, no edge can be mobile, or no configuration exists.
+Correspondingly, an encoding will have weight elements not connected to constraint elements.
+These will instead connect to additional, separate $\1$-formulae, referred to as \emph{weight absorbers}, as shown below.
+A weight element that is connected to absorbers will be called \emph{free}.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {}; 
+	\node[big_] (B) at (2,0) {};
+	\node[big_] (C) at (4,0) {};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+	\node[big1] (1) at (7.5,0) {};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend left=30] (A) to (1);
+		\draw[bend right=30] (B) to (1);
+		\draw (C) to (1);
+	\end{scope}
+\end{tikzpicture}
+\]
+
+An edge in a constraint graph will be encoded by an \emph{edge-gadget}, illustrated below left, constructed by stringing together a number of similar weight elements, plus a single $\bot$-formula which we will refer to as the \emph{indicator}.
+Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
+\[
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big_] (A) at (0,0) {$i\ap$}; 
+	\node[big_] (B) at (2,0) {$j\ap$};
+	\node[big_] (C) at (4,0) {$k\ap$};
+	\draw[rounded corners] (-1,-1) rectangle (5,1);
+	\node[big_] (D) at (0,4) {$i\ap$}; 
+	\node[big_] (E) at (2,4) {$j\ap$};
+	\node[big_] (F) at (4,4) {$k\ap$};
+	\draw[rounded corners] (-1,3) rectangle (5,5);
+	\draw (2,1)--(2,1.5) (2,2.5)--(2,3);
+	\draw[dotted] (2,1.5)--(2,2.5);
+	\draw (2,-1)--(2,-2) node[bullet] {};
+	\path (0,-2.5)--(1,-2.5);
+\end{tikzpicture}
+\qquad\qquad
+\begin{tikzpicture}[x=5mm,y=5mm,octo]
+	\node[big1] (1) at (0,0) {$m\ap$}; 
+	\node[big1] (2) at (3,0) {$n\ap$};
+	\draw[rounded corners] (-1,-1) rectangle (1,1) (2,-1) rectangle (4,1);
+	\draw (1,0)--(2,0);
+	\node[big1] (3) at (0,4) {$m\ap$};
+	\node[big1] (4) at (3,4) {$n\ap$};
+	\draw[rounded corners] (-1,3) rectangle (1,5) (2,3) rectangle (4,5);
+	\draw (1,4)--(2,4);
+	\draw[dotted] (1.5,1.5)--(1.5,2.6);
+	\node[circ] at (1.5,-2) {};
+	\draw[rounded corners] (-1.5,-2.5) rectangle (4.5,5.5);
+\end{tikzpicture}
+\]
+The natural way for edge-gadgets to link up with a vertex-gadget is shown in Figure~\ref{fig:connect example}: indicators connect to indicator targets, and weight elements connect to constraint elements or weight absorbers.
+The illustration depicts two equivalent proof nets, both encoding the same (fragment of a) constraint graph: a single vertex that is the target of a weight-1 edge (on the left, in red) and a weight-2 edge (on the right, in blue).
+The inflow of the vertex is 3, and its constraint is 2; then 2 weight elements are connected to the constraint elements in the vertex-gadget, while one remains free (connected to weight absorbers).
+It is essential to the functioning of the encoding that any re-distribution of weight elements gives an equivalent proof net, as illustrated by the example.
+Then in the second proof net, the single weight element of the left edge-gadget is free, which means the indicator jump can be rewired to connect to a different vertex.
+
+In the encoding, the indicator jumps determine which vertex is the target of the edge, and while they may in principle assign any vertex, the weight elements of the edge-gadget can only form proof nets with the constraint elements of the correct vertices.
+An edge-gadget will be called \emph{free} if all its weight elements are free.
+The vertex-gadgets in an encoding will all be gathered in a $\tn$-formula, which means they are connected, so that free edge-gadgets may attach their indicator to any of them.
+
+\begin{figure}
+
+\noindent$\CONexample 2{.60}\hfill\perm\hfill\CONexample 1{.60}$
+
+\caption{Two edge-gadgets connecting to one vertex-gadget}
+\label{fig:connect example}
+\end{figure}
+
+In Figure~\ref{fig:big example} we give a complete encoding of the example rewiring sequence shown in Figure~\ref{fig:NCL example}, a reconfiguration sequence for a constraint graph functioning as an \textsc{and}-gate.
+The given proof nets are all equivalent, and their corresponding constraint graphs are shown near the bottom of the figure.
+The central vertex-gadget encodes the central constraint-2 vertex in the graph, while its three implicit constraint-0 vertices, at the dangling ends of the three edges, are encoded by the three formulae connected to the central gadget.
+
+\newcommand\ANDmark[1]{\makebox[0pt][r]{\Large{\textbf{#1}}}}
+
+\begin{figure}[p]
+\[
+\begin{array}{@{}r@{\hspace{16pt}}|@{\hspace{16pt}}l@{}}
+	\ANDexample 1 \ANDmark 1 & \ANDexample 2 \ANDmark 2 \\ \\ \hline \\
+	\ANDexample 3 \ANDmark 3 & \ANDexample 4 \ANDmark 4 \\ \\ \hline \\
+	\ANDexample 5 \ANDmark 5 & \ANDexample 6 \ANDmark 6 \\ \\ \hline
+\end{array}
+\]
+\vspace{20pt}
+\[
+\begin{array}{ccccccc}
+	\andexample 1 &\perm& \andexample 2 &\perm& \andexample 3 &\perm& \andexample 4 \\
+	\textbf{1} && \textbf{2} && \textbf{3~4~5} && \textbf{6}
+\end{array}
+\]
+\caption{Encoding an \textsc{and}-gate in proof nets}
+\label{fig:big example}
+\end{figure}
+
+\subsection*{Weight adjustment}
+
+So far we have assumed that one weight element may encode one unit of weight in the constraint graph.
+However, there is a minor issue that prevents this straightforward approach.
+Although one weight element cannot `fill' an inappropriate constraint element, two weight elements \emph{can}, in the way illustrated below.
+In such a situation, the weight element that should have been linked to this constraint element becomes free, and the edge it belongs to may inappropriately become free, too.
+\[
+\begin{tikzpicture}[x=5mm,y=-5mm,octo]
+	\node[big_] (A) at (-1,0) {}; 
+	\draw (.75,0) node[big_] (B1) {} -- (2.25,0) node[big_] (B2) {};
+	\node[big_] (C) at (4,0) {};
+	\draw[rounded corners] (-2,-1) rectangle (5,1);
+	\draw (7,0) node[big_] (D1) {} -- (8.5,0) node[big_] (D2) {}; 
+	\node[big_] (E) at (10.25,0) {};
+	\node[big_] (F) at (12,0) {};
+	\draw[rounded corners] (6,-1) rectangle (13,1);
+	\node[big1] (1) at (1,4) {};
+	\node[big1] (2) at (4,4) {}; 
+	\node[big1] (3) at (7,4) {};
+	\node[big1] (4) at (10,4) {};
+	\draw[rounded corners] (3,3) rectangle (5,5) (6,3) rectangle (8,5);
+	\draw (5,4)--(6,4);
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=25] (A)  to (1);
+		\draw[bend right=15] (B1) to (1);
+		\draw[bend right=25] (B2) to (2);
+		\draw[bend right=15] (C)  to (2);
+		\draw[bend left=15] (D1) to (3);
+		\draw[bend right=15] (D2) to (4);
+		\draw[bend left=20] (E)  to (4);
+		\draw[bend left=20] (F)  to (4);
+	\end{scope}
+\end{tikzpicture}
+\]
+To resolve this issue, it is sufficient to increase the number of weight elements used to encode one unit of weight. In the following, we will investigate how many are needed.
+
+In an inappropriate linking as shown above, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the switching condition would be violated.
+That means the weight elements must belong to different edges.
+
+As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
+Consequently, a weight element can fill three halves, but only of different constraint elements.
+The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
+To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
+To fill $3n$ constraint elements inappropriately therefore requires $n+1$ edges.
+It thus suffices to encode one unit of weight on an edge by $3\times|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly to encode one unit of inflow constraint by $3\times|E|$ constraint elements.
+
+\subsection*{The complete encoding}
+
+The complete encoding of a constraint graph $G$ will then be a sequent $\Gamma$ consisting of:
+%
+\begin{enumerate}
+ 	\item
+all vertex-gadgets, combined in a single formula via tensors, 
+	\item
+all edge-gadgets as individual formulae, and
+	\item
+a sufficient number of weight absorbers ($\1$-formulae).
+\end{enumerate}
+%
+A configuration for $G$ will be encoded as a proof net for $\Gamma$, and conversely each proof net for $\Gamma$ may be interpreted as a (partial) configuration for $G$.
+The encoding will be made formal in the next section.
+%Section~\ref{sec:correctness}.
+
+%------------------------------------------------------------
+
 \section{Formalising the encoding}
@@
 
-We will formalise the encoding of \capsabbrev{ncg}-reconfiguration into \capsabbrev{mll} proof equivalence that was informally introduced in Section~\ref{sec:encoding}.
+We will formalise the encoding of \capsabbrev{ncg}-reconfiguration into \capsabbrev{mll} proof equivalence that was informally introduced in the previous section. %Section~\ref{sec:encoding}.
 A constraint graph $G$ will be encoded as a sequent $\itn G$, and a configuration $\gamma$ for $G$ will be encoded as a proof net $\itn\gamma$ for $\itn G$.
@@
 	\item
-for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
-	\item
-for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
+for a constraint element $V=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,V$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
+	\item
+for $V=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,V$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
 	\item
@@
 
-Finally, if two connected configurations $\gamma\perm\delta$ are encoded individually as $\itn\gamma$ and $\itn\delta$, these may not be equivalent simply because their parity happens to be odd.
-%
+Finally, we will encode an instance of the NCL reconfiguration problem: a pair of configurations $\gamma$ and $\delta$ for a given NCL graph $G$, for which the problem asks whether $\gamma\perm\delta$.
+Here we need to ensure that the two encodings as proof nets have even parity; otherwise, they will never be equivalent.
+We have opted for a simple and straightforward solution: first we encode both configurations as $\itn\gamma$ and $\itn\delta$; then we check their parity, and if it is odd, we adjust it by swapping two weight absorbers on $\itn\delta$.
+
+%Finally, if two connected configurations $\gamma\perm\delta$ are encoded individually as $\itn\gamma$ and $\itn\delta$, these may not be equivalent simply because their parity happens to be odd.
 For that reason we shall adjust the encoding of the second to guarantee an even parity.
@@
 %
-Let $\itn\delta'$ be $\itn\delta$ with the first two weight absorbers exchanged.
-%
+The \emph{encoding} of an instance of NCL-reconfiguration $(G,\gamma,\delta)$ is the triple $(\itn G,\itn\gamma,\itn\delta_\gamma)$ where
+\[
+	\itn\delta_\gamma=\left\{
+	 \begin{array}{ll}\itn\delta & \text{if $\itn\gamma$ and $\itn\delta$ have even parity} \\
+	 				  \itn\delta' & \text{otherwise}\end{array}\right.
+\]
+and $\itn\delta'$ is $\itn\delta$ with the first two weight absorbers exchanged.
+\end{definition}
+
+%Let $\itn\delta'$ be $\itn\delta$ with the first two weight absorbers exchanged.
 For configurations $\gamma$ and $\delta$ for $G$, let $\itn\delta_\gamma$ be $\itn\delta$ if it has even parity with $\itn\gamma$, and $\itn\delta'$ otherwise.
 %
-\end{definition}
 
@@
 \label{lem:octopus roll}
-In a proof net $\links$ for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ where each edge-gadget is well linked, if a weight element $W_i$ in $\itn{e_i}$ is linked to $V$ in $\itn v$ and $W_j$ in $\itn{e_j}$ is linked to weight absorbers $1^n$, then there is a net $\links'\perm\links$ in which $W_j$ is well linked to $V$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
+Let $\links$ be a proof net for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ such that each edge-gadget $\itn e_i$ is well linked.
+Let $W_i$ and $W_j$ be weight elements in edge-gadgets $\itn{e_i}$ and $\itn{e_j}$ respectively; let $W_i$ be linked to $V$ in $\itn v$, and let $W_j$ be linked to weight absorbers $1^n$.
+Then there is a net $\links'\perm\links$ in which $W_j$ is well linked to $V$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}
@@
 By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
-It is then sufficient to choose linkings so that $D\pr E\pr F$ is in a a standard linking with $X\tn Y$, with a minor adjustment: two jumps from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
+It is then sufficient to choose linkings so that $D\pr E\pr F$ is in a standard linking with $X\tn Y$, with a minor adjustment: two jumps from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
 The jumps of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining jump from $B$ to $X$ and one from $C$ to $Y$.
@@
 
-\capsabbrev{pspace}-hardness is by the encoding of \capsabbrev{ncg}-reconfiguration, which in its completed form is stated:
+\capsabbrev{pspace}-hardness is by the encoding of \capsabbrev{ncg}-reconfiguration.
+Recall that an instance of \capsabbrev{ncg}-reconfiguration $(G,\gamma,\delta)$ is encoded by the triple $(\itn G,\itn\gamma,\itn\gamma_\delta)$.
+Then:
 \[
@@
 The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and the observation that $\coitn{\itn\gamma}=\gamma$ and $\coitn{\itn\delta_\gamma}=\delta$.
-%
 \end{proof}
@@
 We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction, and Dominic Hughes for useful suggestions on exposition.
-% and the anonymous referees for their constructive observations.
+We would also like to thank the anonymous referees for insightful remarks, in particular regarding the consequences for MELL.
 

### 2015-07-05 Reviews LMCS/Response.txt
more fixes

@@
 
-*** We have tried and failed to find a decent reference for the kind of proof nets we have in mind here, although private discussions have convinced us that the issue is quite widely understood.
+*** We have tried and failed to find a decent reference for the kind of proof nets we have in mind here, although private discussions have convinced us that they are quite widely understood.
 The principle is simple: re-wiring jumps towards the unique conclusion yields a canonical form.
@@
 
-*** The prime is used as a notation for 'successor', to indicate that a node labelled n' has n + 1 bottoms or ones, while n' and m' connect to (n+m)'.
+*** We have removed the primes.
 
@@
 
-Moreover it is said that Intuitionistic MLL with units has a canonical presentation but no citations are given.
-[...] Of course, *a citation has to be given*, but that is not the point.
-Given the results in the paper, Intuitionistic (ME)LL is the only hope for a tractable and expressive theory of proof nets.
-The intuitionistic case should then be discussed precisely, explaining the differences with the classical case.
-The canonical presentation of the intuitionistic case that the authors have in mind probably relies on jumps, and thus rewiring and proof equivalence make sense there too.
-Why is that case tractable?
-And does tractability rely on the fact that cut­-elimination in the linear case is trivial?
-Would Intuitionistic MELL be tractable as well?
+*** We have now mentioned more explicitly that polarized proof nets are canonical, further down from that paragraph.
+
+Moreover it is said that Intuitionistic MLL with units has a canonical presentation but no citations are given. [...]
 
@@
 They have to be discussed, at least briefly.
-At present the alternative approaches are just cited, without giving any hint of why they would help to treat the units.
+[...]
+
+*** We have expanded the discussion of these alternatives, giving brief hints as to how they avoid the unit problem.
+
 I am also surprised by the total absence of a discussion of the case of MLL with the MIX rules.
-A better treatment of the context of the problem cannot be avoided, because it is the reason why the result is interesting.
-Moreover, it is also the reason that justifies to not take too seriously the many technicalities of the
-*** While in principle we agree that these alternatives could be discussed in more detail, the general picture is simply that each drops one or more of the axioms of a *-autonomous category.
-We did not want to turn this
+
+*** We opted not to discuss MIX - depending on which rules are added, either the units are equated, which is semantically equivalent to omitting them, or they are not, in which case the logic is conservative over MLL and the unit problem remains.
 

### 2015-07-05 main/LMCS.tex
more fixes

@@
 
-\newcommand\ap{'}
-
 % MLL
@@
 An important consequence of the result is that the existence of a satisfactory notion of proof nets for \capsabbrev{mll} with units is ruled out (under current complexity assumptions).
+%
+Another is that for \capsabbrev{mell}, even without units, equivalence of normal forms is \capsabbrev{pspace}-hard.
 \end{abstract}
@@
 Linear logic was formulated as a sequent calculus system, and doesn't have a corresponding
-natural deduction in the classical sense. The role of natural deduction is taken instead by
+natural deduction in the %classical
+traditional sense. The role of natural deduction is taken instead by
 proof nets. Each sequent calculus proof gives rise to a proof net. Furthermore, at least in
@@
 Proof nets incorporating units were defined by Blute, Cockett, Seely and Trimble \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}, though these proof nets cease to be canonical.
-The `joker games' of Koh and Ong \cite{Koh-Ong-1999}, for MLL and its intuitionistic variant IMLL, have a very similar structure to proof nets, and include units.
+The `joker games' of Koh and Ong \cite{Koh-Ong-1999}, for \capsabbrev{mll} and its intuitionistic variant \capsabbrev{imll}, have a very similar structure to proof nets, and include units.
 Another explicit treatment of proof nets for \capsabbrev{mll} with units is given by Lamarche and Stra\ss burger \cite{Lamarche-Strassburger-2006}, and later a particularly simple and elegant version by Hughes \cite{Hughes-2012-categories,Hughes-2012-nets}.
+However, none of these notions gives proof nets that are canonical.
 
@@
 In the sequent calculus, $\bot$-instances are introduced by a weakening rule, which permutes with many (but not all) other rules.
-In proof nets, $\bot$-instances are commonly attached by edges called jumps, which may be re-attached via local graph-rewrite rules \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}.
-For intuitionistic MLL the rewrite rules may be directed towards the unique conclusion, to yield canonical forms.\footnote{The canonical representation for IMLL described here appears to be folklore; established proof nets for intuitionistic linear logic, called essential nets \cite{Lamarche-2008,Murawsky-Ong-2003}, (non-canonically) attach jumps to the leaves of the formula tree, for easier composition.}
+In proof nets, $\bot$-instances are commonly attached by edges called jumps, which may be \emph{rewired} via local graph-rewrite rules \cite{Trimble-1994,Blute-Cockett-Seely-Trimble-1996}.
+For intuitionistic \capsabbrev{mll} rewiring may be directed towards the unique conclusion, to yield canonical forms.\footnote{The canonical nets for \capsabbrev{imll} described here appear to be folklore; established proof nets for intuitionistic linear logic, called essential nets \cite{Lamarche-2008,Murawski-Ong-2003}, (non-canonically) attach jumps to the leaves of the formula tree, for easier composition.}
 For classical MLL with units however, there is not an obvious preferred point to attach jumps.
-And this problem extends to multiplicative--exponential linear logic (MELL) without units, where a formula $?A$ may be introduced via a weakening rule with similar permutability to the $\bot$-introduction rule.
+And this problem extends to multiplicative--exponential linear logic (\capsabbrev{mell}) without units, where a formula $?A$ may be introduced via a weakening rule with similar permutability to the $\bot$-introduction rule.
 
@@
 
-The result has a similar consequence for MELL without units, which may emulate the unit $\bot$ via carefully chosen formulae $?A$: equivalence of MELL proofs in normal form is \capsabbrev{pspace}-hard.
+In \capsabbrev{mell}, even without units, the unit $\bot$ may be emulated via carefully chosen formulae $?A$.
+Consequently, our result means that equivalence of cut-free MELL proofs is \capsabbrev{pspace}-hard.
 This is in sharp contrast with many intuitionistic calculi such as the simply typed lambda-calculus, where normal forms are unique.
-However, it does not impact the complexity of proof equivalence for MELL in general, which is dominated by cut-elimination (MELL encodes the simply-typed lambda-calculus, which is not elementary recursive \cite{Statman-1977}).
+However, it does not impact the complexity of proof equivalence for \capsabbrev{mell} in general, which is dominated by cut-elimination (\capsabbrev{mell} encodes the simply-typed lambda-calculus, which is not elementary recursive \cite{Statman-1977}).
 
@@
 
-Given our results for classical linear logic, which effectively rule out canonical forms for MELL, it becomes tempting to consider possible alternatives.
+Given our results for classical linear logic, which effectively rule out canonical forms for \capsabbrev{mll} and \capsabbrev{mell}, it becomes tempting to consider possible alternatives.
 One is intuitionistic linear logic, mentioned above.
-Another is Melli\`es's game-semantics inspired \emph{tensorial logic} \cite{Mellies-2012}, which embeds linear logic via a double-negation translation.
-Furthermore, the \emph{polarised} fragment of linear logic has canonical proof nets \cite{Laurent-1999}.
-A different direction to the above three, aimed more at proof search than semantics of programming, is \emph{focusing}, which retains classical linear logic but weakens the notion of proof equivalence; this gives canonical representations in \emph{focused proof nets} \cite{Andreoli-Maieli-1999} and \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}.
+Another is Melli\`es's game-semantics inspired \emph{tensorial logic} \cite{Mellies-2012}, with a semantics in \emph{dialogue categories}.
+Tensorial logic rejects double-negation elimination, and embeds linear logic via a double-negation translation; the presence of explicit negations in formulae renders jumps immobile, so that the re-wiring problem for the unit does not occur.
+A further alternative is the \emph{polarised} fragment of linear logic, which has canonical proof nets \cite{Laurent-1999}; here, the rewiring of jumps is blocked by the presence of exponentials rather than negations.
+Finally, in a direction aimed more at proof search, \emph{focusing} retains classical linear logic but weakens the notion of proof equivalence.
+This gives canonical representations in \emph{focused proof nets} \cite{Andreoli-Maieli-1999} and \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}.
 
@@
 \label{def:equivalence}
-\emph{Equivalence} $(\perm)$ of proofs in (cut-free, identity-free, unit-only) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
-\emph{\capsabbrev{mll}\ proof equivalence} is the problem of deciding whether two given proofs are equivalent.
+\emph{Equivalence} $(\perm)$ of proofs in (unit-only, cut-free, identity-free) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
+\emph{\capsabbrev{mll} proof equivalence} is the problem of deciding whether two given proofs are equivalent.
 \end{definition}
@@
 \[
+\begin{array}{c}
+\\
 	\MLLelim{a0}\quad\rightsquigarrow\quad\MLLelim{a1}
@@
 	\MLLelim{a2}\quad\rightsquigarrow\quad\MLLelim{a3}
+\\[5pt]
+\end{array}
 \]
@@
 \begin{array}{rcl}
-	\MLLelim{c0} & \rightsquigarrow & \Gamma \\ \\[5pt]
+\\[5pt]
+	\MLLelim{c0} & \rightsquigarrow & \Gamma \\ \\[10pt]
 	\MLLelim{c1} & \rightsquigarrow & \MLLelim{c2}
+\\[5pt]
 \end{array}
@@
 \begin{array}{c}
+\\[5pt]
 	\MLLperm{bb1}\quad\sim\quad\MLLperm{bb2}
@@
 	\MLLperm{bp1}\quad\sim\quad\MLLperm{bp2}
-\\ \\[5pt]
+\\ \\[10pt]
 	\MLLperm{bt2}\quad\sim\quad\MLLperm{bt1}\quad\sim\quad\MLLperm{bt3}
-\\ \\[5pt]
+\\ \\[10pt]
   \begin{array}{rcl}
 	\MLLperm{pp1} & \sim & \MLLperm{pp2}
-  \\ \\[5pt]
+  \\ \\[10pt]
 	\MLLperm{pt1} & \sim & \MLLperm{pt2}
-  \\ \\[5pt]
+  \\ \\[10pt]
 	\MLLperm{tt1} & \sim & \MLLperm{tt2}
   \end{array}
+\\[5pt]
 \end{array}
@@
 The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
-Proof equivalence for \capsabbrev{mll} is therefore equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
+Proof equivalence for \capsabbrev{mll} is thus equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
 
@@
 There have been several proposals for (non-canonical) multiplicative proof nets with units \cite{Blute-Cockett-Seely-Trimble-1996, Koh-Ong-1999, Lamarche-Strassburger-2006, Hughes-2012-nets}, each providing a different take on the proof equivalence problem for \capsabbrev{mll}.
-We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our \capsabbrev{pspace}-hardness reduction.
+% We will use the formulation by Hughes \cite{Hughes-2012-nets}, which reduces proof equivalence to a simple rewiring relation, as the basis for our \capsabbrev{pspace}-hardness reduction.
+We will use essentially the formulation by Hughes \cite{Hughes-2012-nets}.
+A proof net is a sequent, seen as a forest of formula trees, for which a set of \emph{links} or \emph{jumps} attaches the instances of $\bot$ to other vertices (occurrences of connectives and units) in the forest.
+%
+Rewiring is the re-attachment of one jump, either as a small-step relation that moves jumps only to neighbouring vertices, or as a big-step relation that moves a jump anywhere in the forest.
+Hughes relates both flavours of rewiring, which allows us to switch between the two at will.
+In addition, we may at any point impose the restriction that jumps connect only to occurrences of the unit $1$.
+
 In this section we will discuss how this notion of proof net arises from the sequent calculus, and introduce a compact notation for it.
@@
 \label{def:proofs to nets}
-The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, $\links(a)$ is a name in $\Gamma$, where $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below.
-\[
-	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
+The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, $\links(a)$ is a name in the context $\Gamma$ of the inference introducing $\named a\bot$:
+\[
+	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}~.
 \]
@@
 
-The above definition, which is due to Hughes~\cite{Hughes-2012-nets}, gives a ``big-step'' rewrite relation for equivalence.
+The above definition, which is due to Hughes~\cite{Hughes-2012-nets}, gives the ``big-step'' rewrite relation for equivalence.
 In turn, this rewiring relation is generated by smaller local steps, which correspond more closely to the permutations in the sequent calculus.
@@
 A further refinement in the proof nets introduced by Hughes \cite{Hughes-2012-nets}, is that jumps may be restricted to target only $1$-formulae.
-For the remainder of the paper, unless otherwise indicated, we will assume that proof nets are of this form.
+This will be convenient for the compact diagrammatic notation introduced below, and unless otherwise indicated, we will assume that proof nets are of this form.
+
+%For the remainder of the paper, unless otherwise indicated, we will assume that proof nets are of this form.
 
@@
 A main technical advantage of this restriction is that cut-elimination can be performed in a one-shot operation, by path composition over jumps.
-Then, without the need to define cut-elimination by local transformations, cuts may be omitted from proof nets altogether, which justifies the present definition.
-
-Finally, the following proposition states that equivalence is preserved when translating between proofs and proof nets, which means that \capsabbrev{mll}\ proof equivalence is equivalent to the problem of deciding equivalence of proof nets.
+Then, without the need to define cut-elimination by local transformations, proof nets may omit an explicit representation of cuts, as the present definition does.
+
+Finally, the following proposition states that equivalence is preserved when translating between proofs and proof nets, which means that \capsabbrev{mll} proof equivalence is equivalent to the problem of deciding equivalence of proof nets.
 
@@
 %
-For example, the sequent below left is represented as a diagram below right.
-%
-\[
-	\bot\tn\bot~,~\bot\tn\bot~,~\1~,~(\1\pr\1\pr\1)\tn\bot
-\qquad\qquad
+For example, the diagram below left represents the sequent below right.
+%
+\[
+\begin{array}{c}
 \vc{\begin{tikzpicture}[x=5mm,y=-5mm,octo]
@@
 \end{tikzpicture}}
+\qquad\qquad
+	\bot\tn\bot~,~\bot\tn\bot~,~\1~,~(\1\pr\1\pr\1)\tn\bot
+\end{array}
 \]
@@
 Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Strassburger-Lamarche-2004}.
-There are 24 proof nets in total, forming two equivalence classes, each consisting of a single cyclic rewiring path.
+There are 24 proof nets in total (under the restriction that jumps only connect to $1$-occurrences), forming two equivalence classes, each consisting of a single cyclic rewiring path.
 
@@
 In this section we will show how numerical constraints may be encoded in \capsabbrev{mll}, a necessary ingredient for our main construction.
-We will illustrate the ideas with an example: an encoding of 3-partition into the problem of \capsabbrev{mll} proof search.
+We will illustrate the ideas with an example from the literature: an encoding of 3-partition into the problem of \capsabbrev{mll} proof search \cite{Kanovich-1992,Lincoln-Winkler-1994}.
 
@@
 If the numbers $a$, $b$, and $c$ are assigned to a triple corresponding to a formula $K_j$, then the corresponding formulae have $a+1$, $b+1$, and $c+1$ occurrences of $\bot$, and $k+1=a+b+c+1$ occurrences of $\1$, respectively.
-Then as described previously, there is a proof net for these formulae, obtained by attaching each jump to a distinct $\1$, with the exception of three jumps, one each from $a$, $b$, and $c$, overlapping on exactly one intance.
+Then as described previously, there is a proof net for these formulae, obtained by attaching each jump to a distinct $\1$, with the exception of three jumps, one each from $a$, $b$, and $c$, overlapping on exactly one instance.
 
@@
 
-The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof equivalence, as described informally in the previous section, is correct.
+The notions and results introduced in this section will be used in the main proofs of the paper, in Section~\ref{sec:correctness}, which show that the encoding of \capsabbrev{ncg}-reconfiguration in \capsabbrev{mll} proof equivalence is correct.
 

### 2015-07-07 main/LMCS.tex
intro to "parity"

@@
 \begin{document}
+
+%\end{document}
 
@@
 
+% NEW
+
 Here, we will introduce a similar necessary condition for the equivalence of two proof nets.
-We shall associate a \emph{parity} with any pair of linkings $\links$ and $\links'$ over the same sequent $\Gamma$, and we shall find that the parity of equivalent linkings is always even.
+Consider the example of the identity and twist maps on $\bot\tn\bot$, below.
+The two maps are semantically distinct; hence they are often given as a minimal example showing the necessity of having jumps in proof nets.
+\[
+	\twistid0 \qquad\qquad \twistid1
+\]
+In this case, it is easily seen that neither jump can be rewired, and that the two nets are thus inequivalent; to change from one net to the other, two jumps would need to be rewired simultaneously.
+This prompts the question of what would happen in a larger net: would a complicated series of rewirings be able to exchange two jumps configured like those of the above nets?
+Or phrased semantically: are there maps that equalise the identity and twist on $\bot\tn\bot$ in the free $*$-autonomous category?
+
+It turns out that this is not the case.
+Most provable sequents have at least two equivalence classes of proofs, such that for each proof in one class there is a corresponding proof, equal up to the exchange of two jumps, in the other.
+An example of this is Figure~\ref{fig:_*_,1,1,1,_*_}.
+
+We will capture this idea as follows: we shall associate a \emph{parity} with any pair of linkings $\links$ and $\links'$ over the same sequent $\Gamma$, which may be \emph{even} or \emph{odd}, and we shall find that the parity of equivalent linkings is always even.
+
+% OLD
 

### 2015-07-07 main/LMCS.tex
layout, spacing, "parity problem" comment

@@
 The problem we consider is the following.
-
-\begin{definition}[\capsabbrev{mll} proof equivalence]
-\label{def:equivalence}
-\emph{Equivalence} $(\perm)$ of proofs in (unit-only, cut-free, identity-free) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
-\emph{\capsabbrev{mll} proof equivalence} is the problem of deciding whether two given proofs are equivalent.
-\end{definition}
 
@@
 \end{figure}
+
+\begin{definition}[\capsabbrev{mll} proof equivalence]
+\label{def:equivalence}
+\emph{Equivalence} $(\perm)$ of proofs in (unit-only, cut-free, identity-free) multiplicative linear logic is the congruence generated by the permutations given in Figure~\ref{fig:permutations}.
+\emph{\capsabbrev{mll} proof equivalence} is the problem of deciding whether two given proofs are equivalent.
+\end{definition}
 
@@
 Taking a different perspective, we may alternatively consider a switching graph as a directed tree, rooted in the root connective of $\Gamma$.
-This establishes a bijection between the non-root vertices and the edges, which associates vertex with the edge connecting it to its parent.
+This establishes a bijection between the non-root vertices and the edges, which associates each vertex with the edge connecting it to its parent.
+
+%Next, we take a switching graph $G$ for the proof net $(\Gamma,\links)$, and  consider it as a directed tree, rooted in the root connective of $\Gamma$.
+This establishes a bijection $f_G$ between the non-root vertices and the edges, which associates each vertex with the edge connecting it to its parent: for a given vertex $v$, if $\edge v{\path wx}$ is the path in $G$ from $v$ to the root $x$, then $f_G(v)=a$ is the name of the $\edge vw$ in the above scheme, i.e.\ $a=v(i)$ or $a=w(i)$ for some index $i$.
 
@@
 There are two possibilities, illustrated below.
-%in Figure~\ref{fig:rewiring directed switching graph}.
 On the left, if the jump $v(1)$ is directed upward, then the target of each edge in the directed switching graphs remains the same---in particular $v(1)$ has target $v$---and the induced permutation is the identity.
@@
 \[
-	\vc{\parityNetC1} \perm \vc{\parityNetC2}
+	\vc{\parityNetC1} ~\perm~ \vc{\parityNetC2}
 \qquad\qquad\qquad
-	\vc{\parityNetD1} \perm \vc{\parityNetD2} \kern5pt{=}\kern-5pt \vc{\parityNetD3}
-\]
-
-%On the right, in Figure~\ref{fig:rewiring directed switching graph},
+	\vc{\parityNetD1} ~\perm~ \vc{\parityNetD2} ~\kern5pt{=}\kern-5pt~ \vc{\parityNetD3}
+\]
+
 Above on the right, if the jump from $v$ is directed downward, the subtree of $a$ will get the new root node $b$.
@@
 \end{proposition}
+
+% NEW
+
+For our encoding, in Section~\ref{sec:encoding}, this poses the following challenge (the \emph{parity problem}): when we want the encoding to produce proof nets that are equivalent, we must ensure that these do not inadvertently have odd parity.
+
+% OLD
 
@@
 \begin{proposition}
-A basic sequent $\1^n,\bigtn(\bot^n)$ is inhabited by exactly $n!$ inequivalent proof nets.
+A basic sequent $\1^n,\bigtn(\bot^n)$ is inhabited by $n!$ inequivalent proof nets.
 \end{proposition}

### 2015-07-07 Reviews LMCS/Response.txt
review response

@@
 
+1) Numerical constraints [...]
+
+***
+
+2) Parity [...]
+
+*** We have added some introductory paragraphs to the subsection on parity, and adjusted Definition 37 for clarity (see also the response to Review 1 above).
+
+3) Soundness/readback[...]
+
+***
+
+First, the authors choose to restrict jumps to target 1­formulae and to rewire jumps according to a big­step strategy, building on the work of Hughes. [...]
+
+*** We have more clearly motivated this choice: it is mostly cosmetic, as it simplifies the diagrammatic notation for proof nets - though it does impact the formulation of some lemmas in the section "Rewiring proof nets".
+
+Second, in section 4 it is said that the reconfiguration problem remains PSPACE­complete under a number of restrictions, e.g.
+fixing constraint at the value 2, but the authors choose the encode the general case, without restrictions.
+[...]
+
+***
+
 Review 3

### 2015-07-07 main/LMCS.tex
minor changes Section 5

@@
 
-We will need no such restrictions, and will encode the general case.
+We will need no such restrictions, and as they would not significantly simplify our encoding, we will work with the general case.
 However, for simplicity of exposition, in the examples of constraint graphs in this section we will use the following conventions.
@@
 An example rewrite sequence is given in Figure~\ref{fig:NCL example}.
-This particular specimen encodes a logical conjunction, and is not unlike an \textsc{and}-gate: in order to invert the weight 2 edge on the right, both weight 1 edges on the left must be inverted first.
+This particular constraint graph encodes a logical conjunction, and is not unlike an \textsc{and}-gate: in order to invert the weight 2 edge on the right, both weight 1 edges on the left must be inverted first.
 
@@
 	\item $E$ a set of edges,
-	\item $c\colon V\to\mathbb N$ an \emph{inflow constraint} on each vertes,
+	\item $c\colon V\to\mathbb N$ an \emph{inflow constraint} on each vertex,
 	\item $v\colon E\to\mathcal P(V)$ where $|v(e)|\in\{1,2\}$ for $e\in E$, a set of 1 or 2 vertices for each edge,
@@
 In the above definition, the first condition states that the weight of an edge may be assigned only to one of its vertices, or left undefined, but not to any other vertex in the constraint graph.
-The second condition states that the total weight of its incoming edges of a vertex must be at least its inflow constraint.
+The second condition states that the total weight of the incoming edges of a vertex must be at least its inflow constraint.
 
 We will write $\gamma[e\mapsto v]$ for the partial configuration that directs $e$ to $v$, and any other edge $e'$ to $\gamma(e')$.
-An edge that may be reversed will be called \emph{mobile}.
-Formally, an edge $e$ in $\gamma$ is \emph{mobile} if $\gamma[e\mapsto\star]$ is a partial configuration.
+An edge that may be reversed will be called \emph{mobile}; formally, an edge $e$ is \emph{mobile} in $\gamma$ if $\gamma[e\mapsto\star]$ is a partial configuration.
 
@@
 \[
-	\gamma[e\mapsto u]~\perm*~\gamma[e\mapsto w]\qquad\text{ if }u\neq w\text{ and }u,w\in v(e)\cup\{\star\}~.
+	\gamma~\perm*~\gamma[e\mapsto u]\qquad\text{ if }\gamma(e)\neq u\text{ and }u\in v(e)\cup\{\star\}~.
 \]
@@
 Figure~\ref{fig:boats} gives a reconfiguration sequence, clockwise from the top left, on a constraint graph with two connection points, top and bottom.
-As such, the graph is meant to replace a single edge from top to bottom, and the reconfiguration sequence inverts the direction of this would-be edge.
+As such, the graph operates as would a single edge from top to bottom, and the reconfiguration sequence inverts the direction of this would-be edge.
 The key point is that in doing so, the central horizontal edge must be inverted \emph{twice}.

### 2015-07-08 main/LMCS.tex
reduced encoding size by factor 3

@@
 
+% NEW
+
 In an inappropriate linking as shown above, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the switching condition would be violated.
 That means the weight elements must belong to different edges.
-
-As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
+Note that it is possible to use more than one weight element from the same edge to fill one half of a constraint element; or even weight elements from different edges, but we are interested here only in the \emph{minimum} number of edges needed to inappropriately fill a vertex-gadget.
+
+Since the different halves of a constraint element must be filled by different edge-gadgets, the switching condition forces inappropriately connected edge-gadgets and constraint elements to form a tree, with edge-gadgets as nodes and constraint elements as edges.
+Since in a tree the number of nodes is always one greater than the number of edges, it requires $n+1$ edge-gadgets to fill $n$ constraint elements.
+It thus suffices to multiply the number of weight elements by the number of edges: we will encode one unit of weight on an edge by $|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly encode one unit of inflow constraint by $|E|$ constraint elements.
+
+%As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
 Consequently, a weight element can fill three halves, but only of different constraint elements.
@@
 It thus suffices to encode one unit of weight on an edge by $3\times|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly to encode one unit of inflow constraint by $3\times|E|$ constraint elements.
+
+% OLD
 
@@
 \[
-	\itn{v_k} = \bigparr\big(C_n(k)^{3m\,\times\,c(v_k)} \big)\pr\1
+	\itn{v_k} = \bigparr\big(C_n(k)^{m\,\times\,c(v_k)} \big)\pr\1
 \]
@@
 \[
-	\itn{e} = \bigtn\big(W_n(i,j)^{3m\,\times\,w(e)}\big)\tn\bot
+	\itn{e} = \bigtn\big(W_n(i,j)^{m\,\times\,w(e)}\big)\tn\bot
 \]
@@
 \]
-where $p=3m\times(|w|-|c|)\times(3n+4)$.
+where $p=m\times(|w|-|c|)\times(3n+4)$.
 
@@
 %
-We will show that the inappropriate edge-gadgets in $G$ are insufficient to fill $3m$ weight elements in $\itn v$.
-%
-Since weight elements come in multiples of $3m$, it follows that to fill the $3m\times c(v)$ constraint elements of $v$, there must be at least as many appropriate weight elements available.
+We will show that the inappropriate edge-gadgets in $G$ are insufficient to fill $m$ weight elements in $\itn v$.
+%
+Since weight elements come in multiples of $m$, it follows that to fill the $m\times c(v)$ constraint elements of $v$, there must be at least as many appropriate weight elements available.
 
@@
 
-Next, it will be shown that to balance $3m$ constraint elements requires at least $m+1$ inappropriate edge-gadgets.
-%
-Two edge-gadgets may balance at most three constraint elements: one weight element $W$ has three subformulae, which may each balance at most one half of a constraint element; the other halves may be balanced by different weight elements of the second edge-gadget.
-%
-In the same way, adding one further edge-gadget allows at most three further constraint elements to be filled, since previous edges may connect to only one half of each constraint element.
-%
-Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
+{\color{red}TO DO!!!}
+
+%
+%Next, it will be shown that to balance $m$ constraint elements requires at least $m+1$ inappropriate edge-gadgets.
+%%
+%Two edge-gadgets may balance at most three constraint elements: one weight element $W$ has three subformulae, which may each balance at most one half of a constraint element; the other halves may be balanced by different weight elements of the second edge-gadget.
+%%
+%In the same way, adding one further edge-gadget allows at most three further constraint elements to be filled, since previous edges may connect to only one half of each constraint element.
+%%
+%Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
 %

### 2015-07-08 Reviews LMCS/Response.txt
minor changes Section 5
final?

--- 2015-07-05 Reviews LMCS/Response.txt
@@
 Here, we will discuss each review in turn, as well as the changes we have made in response.
-We omit comments whose
+We omit the suggested minor changes that we have implemented, but comment on those we chose not to.
 
@@
 
+1) Numerical constraints [...]
+
+*** We have added a further illustration showing where the multiplication by 3x the number of edges is needed.
+
+2) Parity [...]
+
+*** We have added some introductory paragraphs to the subsection on parity, and adjusted Definition 37 for clarity (see also the response to Review 1 above).
+
+3) Soundness/readback[...]
+
+*** We have put the read-back or decoding function in a separate proposition, with justification.
+The only concern for decoding is the following lemma: if two linkings are equivalent, there is a reconfiguration path between their decodings.
+
+First, the authors choose to restrict jumps to target 1-­formulae and to rewire jumps according to a big-­step strategy, building on the work of Hughes. [...]
+
+*** We now have more clearly motivated this choice: it is mostly cosmetic, as it simplifies the diagrammatic notation for proof nets - though it does impact the formulation of some lemmas in the section "Rewiring proof nets".
+
+Second, in Section 4 it is said that the reconfiguration problem remains PSPACE-­complete under a number of restrictions, e.g.
+fixing constraint at the value 2, but the authors choose the encode the general case, without restrictions.
+[...]
+
+*** We don't think these restrictions would actually simplify the encoding - in fact, it would be exactly the same.
+It would still be necessary, for instance, to correct for parity, and to multiply weights by 3 times the number of edges.
+
 Review 3

### 2015-07-08 main/LMCS.tex
final?

--- 2015-07-07 main/LMCS.tex
@@
 Below top is a weight element, below bottom a constraint element.
+
 \[
@@
 \]
+
+\noindent
 For all edges and vertices in the encoding of a constraint graph, the sum $i+j+k=m+n$ will be the same---this way, a priori any weight element may connect to any constraint element.
@@
 The weight element above is for an edge connecting the two vertices for which $m=i$ and $m=i+j$: with those constraint elements it is possible to form a proof net, as illustrated below.
+
 \[
@@
 \]
+
+\noindent
 To ensure that a weight element may not form a proof net with a constraint element of another vertex, the values of $m$ and $n$ are chosen such that $m\equiv1$ and $n\equiv2 \pmod 3$, and accordingly $i\equiv1$, $j\equiv0$, and $k\equiv2\pmod 3$.
@@
 Illustrated below right is a \emph{vertex-gadget} encoding a vertex, formed by a number of constraint elements plus a single \emph{indicator target}.
+
 \[
@@
 \]
+
 The natural way for edge-gadgets to link up with a vertex-gadget is shown in Figure~\ref{fig:connect example}: indicators connect to indicator targets, and weight elements connect to constraint elements or weight absorbers.
@@
 
+% NEW
+
 In an inappropriate linking as shown above, since both halves of the constraint element are connected, the weight elements must be disconnected---otherwise, the switching condition would be violated.
 That means the weight elements must belong to different edges.
+Note that it is possible to use more than one weight element from the same edge to fill one half of a constraint element; or even weight elements from different edges, but we are interested here only in the \emph{minimum} number of edges needed to inappropriately fill a vertex-gadget.
+
+%Since the different halves of a constraint element must be filled by different edge-gadgets, the switching condition forces inappropriately connected edge-gadgets and constraint elements to form a tree, with edge-gadgets as nodes and constraint elements as edges.
+Since in a tree the number of nodes is always one greater than the number of edges, it requires $n+1$ edge-gadgets to fill $n$ constraint elements.
+It thus suffices to multiply the number of weight elements by the number of edges: we will encode one unit of weight on an edge by $|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly encode one unit of inflow constraint by $|E|$ constraint elements.
 
 As the linkings above illustrate, it may occur that one subformula of a weight element $A\pr B\pr C$ fills one half of a constraint element.
-Consequently, a weight element can fill three halves, but only of different constraint elements.
-The other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
+In the pathological case for $(v_i)$ where $i$ is very small or very large, a weight element can fill three halves of different constraint elements, as illustrated in Figure~\ref{fig:pathological}.
+As in the illustration, the other three halves may be filled by weight elements of a different edge---so to fill 3 constraint elements requires 2 inappropriate edges.
 To fill the next three constraint elements, at most 1 previous inappropriate edge may be used, and one additional one is needed.
@@
 It thus suffices to encode one unit of weight on an edge by $3\times|E|$ weight elements (where $|E|$ is the number of edges in the constraint graph), and correspondingly to encode one unit of inflow constraint by $3\times|E|$ constraint elements.
+
+\begin{figure}
+\[
+\begin{tikzpicture}[x=-5mm,y=-5mm,octo]
+	\node[big1] (1) at (0,3) {};
+	\foreach \i in {0,3,6} {
+		\node[big_] (A\i) at (3.5,\i) {}; 
+		\node[big_] (B\i) at (5,  \i) {}; 
+		\node[big_] (C\i) at (7,  \i) {};
+		\node[big_] (D\i) at (9,  \i) {};
+		\draw (A\i)--(B\i);
+		\draw[rounded corners] ($(2.5,-1) + (0,\i)$) rectangle ($(10,1) + (0,\i)$);
+		%
+		\node[big1] (2\i) at (13,\i) {}; 
+		\node[big1] (3\i) at (16,\i) {};
+		\draw[rounded corners] ($(12,-1) + (0,\i)$) rectangle ($(14,1) + (0,\i)$);
+		\draw[rounded corners] ($(15,-1) + (0,\i)$) rectangle ($(17,1) + (0,\i)$);
+		\draw (14,\i)--(15,\i);
+		%
+		\begin{scope}[thepink,->,big>]
+			\draw[bend left=30] (B\i) to (2\i);
+			\draw[bend left=15]  (C\i) to (2\i);
+			\draw (D\i) to (2\i);
+		\end{scope}
+	}
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=20] (A6) to (1);
+		\draw                (A3) -- (1);
+		\draw[bend left=20]  (A0) to (1);
+	\end{scope}
+	\draw (6.25,1) -- +(0,1) (6.25,4) -- +(0,1);
+	\draw[rounded corners] (11.5,-1.5) rectangle (17.5,7.5);
+	\foreach \i in {1,3,5} {
+		\node[big_] (E\i) at (20,  \i) {};
+		\node[big_] (F\i) at (21.5,\i) {};
+		\draw (E\i)--(F\i);
+	}
+	\draw[rounded corners] (19,0) rectangle (22.5,6);
+	\node[big1] (4) at (24,3) {};
+	\begin{scope}[thepink,->,big>]
+		\draw[bend right=20] (E5) to (36);
+		\draw                (E3) -- (33);
+		\draw[bend left=20]  (E1) to (30);
+		\draw[bend left=20]  (F5) to (4);
+		\draw                (F3) -- (4);
+		\draw[bend right=20] (F1) to (4);
+	\end{scope}
+\end{tikzpicture}
+\]
+\caption{A weight element connecting to three constraint elements}
+\label{fig:pathological}
+\end{figure}
+
+% OLD
 
@@
 The encoding will be made formal in the next section.
-%Section~\ref{sec:correctness}.
 
@@
 
-We will formalise the encoding of \capsabbrev{ncg}-reconfiguration into \capsabbrev{mll} proof equivalence that was informally introduced in the previous section. %Section~\ref{sec:encoding}.
+We will formalise the encoding of \capsabbrev{ncg}-reconfiguration into \capsabbrev{mll} proof equivalence that was informally introduced in the previous section.
 A constraint graph $G$ will be encoded as a sequent $\itn G$, and a configuration $\gamma$ for $G$ will be encoded as a proof net $\itn\gamma$ for $\itn G$.
@@
 \[
-	\itn{v_k} = \bigparr\big(C_n(k)^{3m\,\times\,c(v_k)} \big)\pr\1
-\]
-where each \emph{constraint element} $C_n(k)$ is the formula
+	\itn{v_k} = \bigparr\big(C(k,n)^{3m\,\times\,c(v_k)} \big)\pr\1
+\]
+where each \emph{constraint element} $C(k,n)$ is the formula
 \[
@@
 \[
-	\itn{e} = \bigtn\big(W_n(i,j)^{3m\,\times\,w(e)}\big)\tn\bot
-\]
-where each \emph{weight element} $W_n(i,j)$ is the formula
-\[
-	W_n(i,j) = \bigtn\big(\bot\!^{3i+2}\big)\pr\bigtn\big(\bot\!^{3(j-i)+1}\big)\pr\bigtn\big(\bot\!^{3(n-j)+3}\big)\,.
+	\itn{e} = \bigtn\big(W(i,j,n)^{3m\,\times\,w(e)}\big)\tn\bot
+\]
+where each \emph{weight element} $W(i,j,n)$ is the formula
+\[
+	W(i,j,n) = \bigtn\big(\bot\!^{3i+2}\big)\pr\bigtn\big(\bot\!^{3(j-i)+1}\big)\pr\bigtn\big(\bot\!^{3(n-j)+3}\big)\,.
 \]
@@
 \label{def:standard linkings}
-For $W=W_n(i,j)=A\pr B\pr C$ a weight element,
+For $W=W(i,j,n)=X\pr Y\pr Z$ a weight element,
 \begin{enumerate}
 	\item
-for a constraint element $V=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,V$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
+for a constraint element $C=C(i,n)=A\tn B$, the \emph{standard linking} for the sequent $C,W$ links the first $\bot$ in $X$ to the first $\1$ in $A$, the first $\bot$ in $Y$ and $Z$ each to the first $\1$ in $B$, and each remaining $\bot$ in $X,Y,Z$ to a remaining $\1$ in $A,B$ in their order of occurrence;
 	\item
-for $V=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,V$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
+for $C=C(j,n)=A\tn B$, the \emph{standard linking} for $C,W$ is defined as above, except the first $\bot$ in $Y$ links to the first $\1$ in $A$;
 	\item
-the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
+the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $X$, $Y$, and $Z$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
 \end{enumerate}
@@
 %
-Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $W,C$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
+Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $C,W$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
 \end{definition}
@@
 %
-The box of each weight element $W$ is the sequent $W,C$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
+The box of each weight element $W$ is the sequent $C,W$ or $W,1^{3n+4}$ of its standard linking, which forms a proof net by Proposition~\ref{prop:element linkings}.
 %
@@
 
-Finally, we will encode an instance of the NCL reconfiguration problem: a pair of configurations $\gamma$ and $\delta$ for a given NCL graph $G$, for which the problem asks whether $\gamma\perm\delta$.
+Finally, we will encode an instance of the NCL reconfiguration problem, consisting of an NCL graph $G$ with two configurations $\gamma$ and $\delta$, for which the problem asks whether $\gamma\perm\delta$.
 Here we need to ensure that the two encodings as proof nets have even parity; otherwise, they will never be equivalent.
 We have opted for a simple and straightforward solution: first we encode both configurations as $\itn\gamma$ and $\itn\delta$; then we check their parity, and if it is odd, we adjust it by swapping two weight absorbers on $\itn\delta$.
-
-%Finally, if two connected configurations $\gamma\perm\delta$ are encoded individually as $\itn\gamma$ and $\itn\delta$, these may not be equivalent simply because their parity happens to be odd.
-For that reason we shall adjust the encoding of the second to guarantee an even parity.
 
@@
 \]
-and $\itn\delta'$ is $\itn\delta$ with the first two weight absorbers exchanged.
+and $\itn\delta'$ is $\itn\delta$ with the first two weight absorbers $a$ and $b$ exchanged: $v\mathbin{\xjump}a$ in $\itn\delta'$ if and only if $v\mathbin{\xjump}b$ in $\itn\delta$, and vice versa.
 \end{definition}
 
-%Let $\itn\delta'$ be $\itn\delta$ with the first two weight absorbers exchanged.
-For configurations $\gamma$ and $\delta$ for $G$, let $\itn\delta_\gamma$ be $\itn\delta$ if it has even parity with $\itn\gamma$, and $\itn\delta'$ otherwise.
-%
-
 In the remainder, we will show that our encoding is correct, i.e.\ that $\gamma\perm\delta$ if and only if $\itn\gamma\perm\itn\delta_\gamma$.
-%
-This will be separated into two parts: completeness ($\Rightarrow$) and soundness ($\Leftarrow$) .
+This will be separated into two parts: completeness ($\Rightarrow$) and soundness ($\Leftarrow$).
 
@@
 Let $\links$ be a proof net for $\Gamma=\itn v,\itn{e_1},\dotsc,\itn{e_m},1^p$ such that each edge-gadget $\itn e_i$ is well linked.
-Let $W_i$ and $W_j$ be weight elements in edge-gadgets $\itn{e_i}$ and $\itn{e_j}$ respectively; let $W_i$ be linked to $V$ in $\itn v$, and let $W_j$ be linked to weight absorbers $1^n$.
-Then there is a net $\links'\perm\links$ in which $W_j$ is well linked to $V$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
+Let $W_i$ and $W_j$ be weight elements in edge-gadgets $\itn{e_i}$ and $\itn{e_j}$ respectively; let $W_i$ be linked to $C$ in $\itn v$, and let $W_j$ be linked to weight absorbers $1^n$.
+Then there is a net $\links'\perm\links$ in which $W_j$ is well linked to $C$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
 \end{lemma}
@@
 \begin{proof}
-Let $W_i=A\pr B\pr C$, $W_j=D\pr E\pr F$, and $V=X\tn Y$.
-%
-The rewiring path will be illustrated for the case where $A,B,X$ and $D,X$, and thus also $C,Y$ and $E,F,Y$, are balanced sequents; other cases are similar.
+Let $W_i=X\pr Y\pr Z$, $W_j=P\pr Q\pr R$, and $C=A\tn B$.
+%
+The rewiring path will be illustrated for the case where $X,Y,A$ and $P,A$, and thus also $Z,B$ and $Q,R,B$, are balanced sequents; other cases are similar.
 
@@
 \noindent
-\textbf{2.}\quad The jump $\jump iv$ is rewired to a weight absorber together with only the jumps from the first $\bot$ of each of $D$, $E$, and $F$:
+\textbf{2.}\quad The jump $\jump iv$ is rewired to a weight absorber, together with only the jumps from the first $\bot$ of each of $P$, $Q$, and $R$:
 
@@
 \noindent
-\textbf{3.}\quad The jump from the first $\bot$ of $D$ is moved to $X$, and those from the first $\bot$ of $E$ and $F$ are moved to $Y$:
+\textbf{3.}\quad The jump from the first $\bot$ of $P$ is moved to $A$, and those from the first $\bot$ of $Q$ and $R$ are moved to $B$:
 
@@
 \noindent
-\textbf{4.}\quad In the present configuration, the jumps from the weight elements form two subnets: one over the sub-sequent $A,B,X,D,1^m$, and one over the sub-sequent $C,Y,E,F,1^k$, for some $m$ and $k$.
-By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent, as long as their parity is preserved.
-It is then sufficient to choose linkings so that $D\pr E\pr F$ is in a standard linking with $X\tn Y$, with a minor adjustment: two jumps from $D$ to $X$ should remain exchanged, compared to the standard linking, for step 6 below.
-The jumps of $A,B,C$ link to the weight absorbers $1^m$ and $1^k$, with one remaining jump from $B$ to $X$ and one from $C$ to $Y$.
+\textbf{4.}\quad In the present configuration, the jumps from the weight elements form two subnets: one over the sub-sequent $X,Y,A,P,1^m$, and one over the sub-sequent $Z,B,Q,R,1^k$, for some $m$ and $k$.
+By Proposition~\ref{prop:parity determines equivalence}, these subnets are equivalent to any other over the same sequent with which they have even parity.
+It is then sufficient to choose linkings so that $P\pr Q\pr R$ is in a standard linking with $A\tn B$, with a minor adjustment: two jumps from $P$ to $A$ should remain exchanged, compared to the standard linking, for step 6 below.
+The jumps of $X,Y,Z$ link to the weight absorbers $1^m$ and $1^k$, with one remaining jump from $Y$ to $A$ and one from $Z$ to $B$.
 
@@
 \noindent
-\textbf{5.}\quad The jump from $C$ to $Y$ is moved towards a weight absorber connected to $A,B$.
+\textbf{5.}\quad The jump from $Z$ to $B$ is moved towards a weight absorber connected to $X,Y$.
 
@@
 \noindent
-\textbf{6.}\quad The jump from $B$ to $X$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
-Lemma~\ref{lem:double exchange} allows to swap the targets of the jump from $B$ to $X$ and the jump from $i$, and simultaneously undo the exchange in the jumps from $D$ to $X$ added in step 4 above.
+\textbf{6.}\quad The jump from $Y$ to $A$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
+Lemma~\ref{lem:double exchange} allows to swap the targets of the jump from $Y$ to $A$ and the jump from $i$, and simultaneously undo the exchange in the jumps from $P$ to $A$ added in step 4 above.
 
@@
 %
-Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is mobile.
+Since $e$ is mobile in $\gamma$, the weights of the edges $d$ suffice to fill the inflow constraint of $v$, and correspondingly the weight elements of edge-gadgets $\itn d$ suffice to fill the constraint elements of $\itn v$, so that $\itn e$ is free.
 %
@@
 
-It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta_\gamma$ is sound for \capsabbrev{ncg}-reconfiguration, $\gamma\perm\delta$.
+It will be shown that proof net rewiring $\itn\gamma\perm\itn\delta_\gamma$ is sound for \capsabbrev{ncg}-reconfiguration, i.e\ that it implies $\gamma\perm\delta$.
 %
@@
 
-The configuration $\coitn\links$ will assign an edge $e$ to a vertex $v$ when, in the proof net $(\links,\itn G)$, the edge-gadget $\itn e$ is in the empire of the vertex-gadget $\itn v$.
+The configuration $\coitn\links$ will assign an edge $e$ to a vertex $v$ when, in the proof net $(\itn G,\links)$, the edge-gadget $\itn e$ is in the empire of the vertex-gadget $\itn v$.
 %
@@
 %
-We will show that the inappropriate edge-gadgets in $G$ are insufficient to fill $3m$ weight elements in $\itn v$.
-%
-Since weight elements come in multiples of $3m$, it follows that to fill the $3m\times c(v)$ constraint elements of $v$, there must be at least as many appropriate weight elements available.
-
-Let $e$ be inappropriate for $v$; let $C=A\tn B$ be a constraint element in $\itn v$, and $W=X\pr Y\pr Z$ weight element  in $\itn e$.
-%
-To find a proof net for the sequent $W,C$ requires to assign balanced boxes to the par-formulae $A$ and $B$.
-%
-Since $e$ is inappropriate, the sequents $A,X$ and $A,X,Y$ are not balanced, while the balance of each of the other sequents of $A$ with one or more of $X,Y,Z$ is always $1$ or $2$ $\pmod 3$.
-%
-It follows that there is no proof net for $W,C$.
-
-Next, it will be shown that to balance $3m$ constraint elements requires at least $m+1$ inappropriate edge-gadgets.
+We will show that the inappropriate edge-gadgets in $G$ are insufficient to fill $m$ weight elements in $\itn v$.
+%
+Since weight elements come in multiples of $m$, it follows that to fill the $m\times c(v)$ constraint elements of $v$, there must be at least as many appropriate weight elements available.
+
+Let $e$ be inappropriate for $v$; let $C=A\tn B$ be a constraint element in $\itn v$, and $W=X\pr Y\pr Z$ a weight element  in $\itn e$.
+To find a proof net for the sequent $C,W$ requires to assign balanced boxes to the par-formulae $A$ and $B$.
+Since $e$ is inappropriate, the sequents $A,X$ and $A,X,Y$ are not balanced, while the balance of each of the other sequents of $A$ with one or more of $X,Y,Z$ is always $1$ or $2\pmod 3$.
+It follows that there is no proof net for $C,W$.
+
+Next, it will be shown that to balance $m$ constraint elements requires at least $m+1$ inappropriate edge-gadgets.
 %
@@
 Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
-%
+
 \end{proof}
@@
 \begin{definition}
-For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if both $e$ is appropriate for $v$ and $\itn e$ belongs to the empire of $\itn v$, and  undefined otherwise.
+For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where
+% $\coitn\links(e)$ is $v$ if both $e$ is appropriate for $v$ and $\itn e$ belongs to the empire of $\itn v$, and  undefined otherwise.
+\[
+	\coitn\links(e)=
+	\left\{\begin{array}{ll}
+		v & \text{if $e$ is appropriate for $v$ and $\itn e$ is in the empire of $\itn v$} \\
+		\star & \text{otherwise.}
+	\end{array}\right.
+\]
 \end{definition}
+
+To observe that an encoding $\itn\gamma$ decodes back to $\gamma$, note that whenever $\gamma(e)=v$ the indicator of $\itn e$ in $\itn\gamma$ connects to the indicator target of $\itn v$; this is sufficient to place $\itn e$ in the empire of $\itn v$.
+We have the following proposition.
+
+\begin{proposition}
+\label{prop:retraction}
+$\coitn{\itn\gamma}=\gamma$ and $\coitn{\itn\gamma'}=\gamma$.
+\end{proposition}
 
@@
 \capsabbrev{pspace}-hardness is by the encoding of \capsabbrev{ncg}-reconfiguration.
-Recall that an instance of \capsabbrev{ncg}-reconfiguration $(G,\gamma,\delta)$ is encoded by the triple $(\itn G,\itn\gamma,\itn\gamma_\delta)$.
+Recall that an instance of \capsabbrev{ncg}-reconfiguration $(G,\gamma,\delta)$ is encoded by the triple $(\itn G,\itn\gamma,\itn\delta_\gamma)$.
 Then:
@@
 %
-The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and the observation that $\coitn{\itn\gamma}=\gamma$ and $\coitn{\itn\delta_\gamma}=\delta$.
+The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and Proposition \ref{prop:retraction}.
 \end{proof}
@@
 \subsection*{Acknowledgements}
-We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction, and Dominic Hughes for useful suggestions on exposition.
-We would also like to thank the anonymous referees for insightful remarks, in particular regarding the consequences for MELL.
+We would like to thank Beniamino Accattoli, Dominic Hughes, and Lutz Stra{\ss}burger for helpful discussions and comments. We would also like to thank the anonymous referees for insightful remarks.
 

### 2015-07-12 Reviews LMCS/Response.txt
more edits; final author response

@@
 We thank the referees for their careful reading of our paper, and for the detailed and helpful feedback they have provided.
-Here, we will discuss each review in turn, as well as the changes we have made in response.
-We omit the suggested minor changes that we have implemented, but comment on those we chose not to.
+Here, we will discuss each review in turn, and highlight the changes we have made in response.
+For the suggested minor changes, we have implemented most, and will comment only on those we chose not to.
 
@@
 
- ??? We have also made the complexity of this translation more explicit (in Theorem 46).
+*** We have also made this translation more explicit (in the final theorem as well as earlier in the paper).
 
@@
 
-*** While we were aware that MELL- may encode MLL, we indeed did not realise that the consequence of our result (that MELL has no canonical normal forms) would be unexpected or considered interesting.
-And we remain cautious: surely proof equivalence for MELL is completely dominated by the complexity of cut-elimination?
+*** While we were aware that MELL (without units) may encode MLL, we indeed did not realise that this consequence of our result (that MELL has no canonical normal forms) would be unexpected, or considered more interesting than the consequence for MLL.
+And we remain slightly cautious: surely proof equivalence for MELL is completely dominated by the complexity of cut-elimination?
 We have added a paragraph to this effect to the introduction.

### 2015-07-12 main/LMCS.tex
Remove dubious statement
I don’t think this really makes sense as stated, and I can’t think
of a nice way to phrase it correctly. I think it’s fine without.
more edits; final author response

@@
 %
-Another is that for \capsabbrev{mell}, even without units, equivalence of normal forms is \capsabbrev{pspace}-hard.
+The \capsabbrev{pspace}-hardness result extends to equivalence of normal forms in \capsabbrev{mell} without units, where the weakening rule for the ``why-not'' exponential induces a similar rewiring problem.
 \end{abstract}
@@
 This prompts the question of what would happen in a larger net: would a complicated series of rewirings be able to exchange two jumps configured like those of the above nets?
-Or phrased semantically: are there maps that equalise the identity and twist on $\bot\tn\bot$ in the free $*$-autonomous category?
 
@@
 The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and Proposition \ref{prop:retraction}.
+The encoding involves computing $\itn G$, $\itn\gamma$, and $\itn\delta$, then computing the parity of $\itn\gamma$ and $\itn\delta$ and adjusting $\itn\delta$ if needed; each can be done in polynomial time in the size of $(G,\gamma,\delta)$.
 \end{proof}
@@
 \subsection*{Acknowledgements}
-We would like to thank Beniamino Accattoli, Dominic Hughes, and Lutz Stra{\ss}burger for helpful discussions and comments. We would also like to thank the anonymous referees for insightful remarks.
+We would like to thank Beniamino Accattoli, Dominic Hughes, and Lutz Stra{\ss}burger for helpful discussions and comments.
+We would also like to thank the anonymous referees for their insightful remarks.
 

### 2015-07-12 Reviews LMCS/Response.txt
edits for page breaks etc.

@@
 But Lamarche's "essential nets", extended with units by Murawski and Ong (both of which we have added as a reference), attach jumps to the leaves of the tree instead.
+We have added a comment along these lines to the paper.
 
@@
 
-*** We have expanded the explanation of IMLL proof nets that we have in mind.
-(See also above in the response to Review 1.) We view intuitionistic LL as one of several alternatives to classical LL (as remarked on in the next comment).
+*** We have tried and failed to find a decent reference for the kind of proof nets we have in mind here, although private discussions have convinced us that they are quite widely understood.
+The principle is simple: re-wiring jumps towards the unique conclusion yields a canonical form.
+But Lamarche's "essential nets", extended with units by Murawski and Ong (both of which we have added as a reference), attach jumps to the leaves of the tree instead.
+We have added a comment along these lines to the paper.
+We view intuitionistic LL as one of several alternatives to classical LL (as remarked on in the next comment).
 
@@
 
-*** We have added some introductory paragraphs to the subsection on parity, and adjusted Definition 37 for clarity (see also the response to Review 1 above).
+*** We have added some introductory paragraphs to the subsection on parity.
+We agree that Definition 37 was not well-explained; we now explicitly define the translation of an instance of NCL-reconfiguration (which consists of a constraint graph with two configurations).
 

### 2015-07-12 main/LMCS.tex
edits for page breaks etc.

--- 2015-07-08 main/LMCS.tex
@@
 
-\graphicspath{{../notes/}}
-
 \longJournalNames
-\makeTheoremDefs
-
 \let\capsabbrev=\uppercase
 
-\newcommand\jumpsto{\jump}
-\newcommand\Perm{\mathbf\sim}
-
-% MLL
-%   x remove naming - work with occurrences instead ??
-%   v explain cut-elimination
-%     define *-autonomous categories
-
-% PROOF NETS
-%   v separate section for proof nets
-%   v discuss both small-step and big-step equivalence
-%      connect jumps anywhere / to positive leaves (1,a) only
-%   v example translation: proof => net
-% 
-%   v add 3-partition example
-%
-
-% CONSTRAINT LOGIC
-%	  add separate section for constraint logic
-%
-
-% PARITY
-%     stress alternation over n-arity
-%     explain n-arity is safe
-%     mention alternatives ??
-%     clear up argument where possible
-
-% CONSTRUCTION
-%     clarify where possible
-
 \title{Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete}
 
-\author{Willem Heijltjes and Robin Houston}
+\author{Willem Heijltjes}
+\address{University of Bath}
+\email{w.b.heijltjes@bath.ac.uk}
+
+\author{Robin Houston}
+\address{Kiln Enterprises}
+\email{robin@kiln.it}
 
@@
 
-%\keywords{linear logic, proof equivalence, proof nets, constraint logic, \capsabbrev{pspace}-completeness}
+\keywords{linear logic, proof equivalence, proof nets, constraint logic, \capsabbrev{pspace}-completeness}
+\subjclass{F.4.1 Mathematical logic and formal languages---Mathematical logic} %(Proof theory)
+%\subjclass{F.2.2: Analysis of algorithms and problem complexity; Nonnumerical algorithms and problems; Complexity of proof procedures}
 
@@
 %
-Another is that for \capsabbrev{mell}, even without units, equivalence of normal forms is \capsabbrev{pspace}-hard.
+The \capsabbrev{pspace}-hardness result extends to equivalence of normal forms in \capsabbrev{mell} without units, where the weakening rule for the exponentials induces a similar rewiring problem.
 \end{abstract}
@@
 
-A one-sided sequent calculus for unit-only \capsabbrev{mll} is given in Figure~\ref{fig:MLL}.
-The rules for identity ($\mathsf{ax}$) and cut ($\mathsf{cut}$) are admissible, and are eliminated via the identity-elimination and cut-elimination transformations displayed in Figure~\ref{fig:id-elim} and Figure~\ref{fig:cut-elim} respectively.
-The cut-elimination process in addition makes essential use of \emph{permutations} of inference rules, displayed in Figure~\ref{fig:permutations}, to match up a cut-rule with the two inferences that introduce both cut-formulae.
-Note that the symmetric variants of various transformations have been omitted from the figures, as well as permutations involving the cut-rule, which are similar to those of the tensor rule.
-
-The proof system we shall be working with is that consisting of just the introduction rules for the two units and the two connectives, the four rules $(\bot)$, $(\1)$, $(\pr)$, and $(\tn)$ of Figure~\ref{fig:MLL}.
-The problem we consider is the following.
-
 \begin{figure}
@@
 \label{fig:id-elim}
-\end{figure}
-
-\begin{figure}
+\bigskip
 \[
@@
 \label{fig:cut-elim}
-\end{figure}
-
-\begin{figure}
+\bigskip
 \[
@@
 
-\begin{definition}[\capsabbrev{mll} proof equivalence]
+A one-sided sequent calculus for unit-only \capsabbrev{mll} is given in Figure~\ref{fig:MLL}.
+The rules for identity ($\mathsf{ax}$) and cut ($\mathsf{cut}$) are admissible, and are eliminated via the identity-elimination and cut-elimination transformations displayed in Figure~\ref{fig:id-elim} and Figure~\ref{fig:cut-elim} respectively.
+The cut-elimination process in addition makes essential use of \emph{permutations} of inference rules, displayed in Figure~\ref{fig:permutations}, to match up a cut-rule with the two inferences that introduce both cut-formulae.
+Note that the symmetric variants of various transformations have been omitted from the figures, as well as permutations involving the cut-rule, which are similar to those of the tensor rule.
+
+The proof system we shall be working with is that consisting of just the introduction rules for the two units and the two connectives, the four rules $(\bot)$, $(\1)$, $(\pr)$, and $(\tn)$ of Figure~\ref{fig:MLL}.
+The problem we consider is the following.
+
+\begin{defi}[\capsabbrev{mll} proof equivalence]
 \label{def:equivalence}
@@
 \emph{\capsabbrev{mll} proof equivalence} is the problem of deciding whether two given proofs are equivalent.
-\end{definition}
+\end{defi}
 
@@
 The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
-Proof equivalence for \capsabbrev{mll} is thus equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
+Proof equivalence for \capsabbrev{mll} is equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
 
@@
 
-\begin{definition}[Proof nets]
+\begin{defi}[Proof nets]
 \label{def:proof nets}
@@
 \end{itemize}
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}
+\begin{defi}
 \label{def:proofs to nets}
@@
 \]
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}[\cite{Danos-Regnier-1989,Lamarche-Strassburger-2006}]
+\begin{prop}[\cite{Danos-Regnier-1989,Lamarche-Strassburger-2006}]
 \label{prop:correctness and sequentialisation}
@@
 For any proof net $(\Gamma,\links)$ there is a proof $\Pi$ of $\Gamma$ such that $\Pi\toNet\links$ (sequentialisation).
-\end{proposition}
-
-\begin{remark}
+\end{prop}
+
+\begin{rem}
 The proof nets of \cite{Blute-Cockett-Seely-Trimble-1996} may appear to be formulated in quite a distinct way from our presentation, in particular in that their jumps from $\bot$-vertices connect to edges, rather than vertices.
@@
 This way of attaching jumps (to formulae, rather than inferences) is the natural choice also in their setting, which is motivated categorically, where $\bot$-introduction corresponds to the isomorphism $A\to A\pr\bot$.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{definition}
+\begin{defi}
 \label{def:proof net equivalence}
@@
 \emph{Equivalence} $(\perm)$ of proof nets over a sequent $\Gamma$ is the equivalence generated by rewiring.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}[\cite{Hughes-2012-nets}]
+\begin{prop}[\cite{Hughes-2012-nets}]
 Rewiring $(\perm*)$ is generated by the local steps in Figure~\ref{fig:rewiring}.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}[\cite{Hughes-2012-nets}]
+\begin{prop}[\cite{Hughes-2012-nets}]
 Any proof net is equivalent to one where the codomain of $\links$ is restricted to occurrences of the formula $1$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}[\cite{Blute-Cockett-Seely-Trimble-1996,Hughes-2012-nets}]
+\begin{prop}[\cite{Blute-Cockett-Seely-Trimble-1996,Hughes-2012-nets}]
 \label{prop:proof nets work}
 %
-If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ if and only if $\links\perm\links'$.
-%
-\end{proposition}
+If $\Pi\toNet\links$ and $\Pi'\toNet\links'$, then $\Pi\perm\Pi'$ iff $\links\perm\links'$.
+%
+\end{prop}
 
@@
 
-Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$, an interesting example also highlighted in \cite{Strassburger-Lamarche-2004}.
+Figure~\ref{fig:_*_,1,1,1,_*_} uses the diagrammatic notation to display the rewiring relation over the proof nets for the sequent $\bot\tn\bot,1,1,1,\bot\tn\bot$ (an example also highlighted in \cite{Strassburger-Lamarche-2004}).
 There are 24 proof nets in total (under the restriction that jumps only connect to $1$-occurrences), forming two equivalence classes, each consisting of a single cyclic rewiring path.
@@
 
-\begin{definition}
+\begin{defi}
 A \emph{sub-sequent} $\Delta\leq\Gamma$ of a sequent $\Gamma$ is a sequent consisting of disjoint subformulae of $\Gamma$, preserving names.
-\end{definition}
-
-\begin{definition}
+\end{defi}
+
+\begin{defi}
 A \emph{subnet} $(\Delta,\links') \leq (\Gamma,\links)$ of a proof net is a net such that $\Delta\leq\Gamma$ and $\links'$ is the restriction of $\links$ to the names in $\Delta$.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}
+\begin{defi}
 A \emph{boxing} $\bx$ for a linking $\links$ for $\Gamma$ assigns a sub-sequent $\bx(v)\leq\Gamma$ to each par-vertex $\named v\pr$ such that 1) $v$ is a port of $\bx(v)$ and 2) boxes are either disjoint or strictly nested: if $\bx(v)\cap\bx(w)\neq\varnothing$ then $\bx(w)<\bx(v)$ or $\bx(v)<\bx(w)$.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}
+\begin{prop}
 \label{prop:scoping correctness}
 A linking $\links$ for $\Gamma$ is a proof net if and only if it has a boxing $\bx$ such that each local graph is a tree.
-\end{proposition}
-
-\begin{proof}
+\end{prop}
+
+\proof
 Given a boxing $\bx$, it follows by induction on the nesting of boxes that the graph over each $\bx(v)$ satisfies the switching condition.
@@
 \]
-\end{proof}
+\qed
 
@@
 
-\begin{definition}
+\begin{defi}
 The \emph{empire} $\emp v$ of a vertex $v$ in $(\Gamma,\links)$ is the largest subnet $(\Delta,\links')$ of which $v$ is a port.
-\end{definition}
-
-\begin{proposition}[{\cite[Proposition 2.b]{Bellin-vandeWiele-1995}}]
+\end{defi}
+
+\begin{prop}[{\cite[Proposition 2.b]{Bellin-vandeWiele-1995}}]
 \label{prop:empire propagation}
@@
 \end{enumerate}
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{lemma}
+\begin{lem}
 \label{lem:rewiring within empire}
@@
 \end{enumerate}
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 By \cite[Proposition 2.a]{Bellin-vandeWiele-1995} 2 and 3 are equivalent.
@@
 The empire $\emp a$ corresponds to the largest subproof $\Sigma$, with as conclusion the introduction rule of $\named a\bot$, in any sequentialisation $\Pi$ of $\links$.
-By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net, $a$ may link to any $1$-occurrence, including to $w$.
+By Definition~\ref{def:proofs to nets}, in the translation of $\Sigma$ to a net, $a$ may link to any $1$-occurrence, including $w$.
 
@@
 If for some switching of $\links$ the path $\path vw$ passes through $a$, then in $\links[\jumpsto aw]$ there is no path $\path av$ (and two paths $\path aw$) for that switching, so that $(\Gamma,\links[\jumpsto aw])$ is not a net.
-\end{proof}
-
-\begin{lemma}
+\qed
+
+\begin{lem}
 \label{lem:rewiring preserves empire}
 If $\links\perm*\links[\jumpsto vw]=\links'$ then $\emp v\perm*\emp*v$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 Since $v$ may rewire to exactly the same $\1$-occurrences in $\links$ as in $\links'$, by Lemma~\ref{lem:rewiring within empire} the empires $\emp v$ and $\emp*v$ contain the same $\1$-subformulae.
 That they also share any other subformula $A$ follows by the observation that $A\tn\1$ may replace $A$: by Proposition~\ref{prop:empire propagation} the new $\1$ is in a given empire if and only if $A$ is (unless $v$ names $A$, but in this case $A$ is included in both $\emp v$ and $\emp*v$).
-\end{proof}
-
-\begin{lemma}
+\qed
+
+\begin{lem}
 \label{lem:rewiring affects empires}
 If $\links\perm*\links'$ where $\emp v$ is a net for the sequent $\Delta$, and $\emp*v$ a net for $\Delta'$, then $\Delta\leq\Delta'$ or $\Delta\geq\Delta'$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 Let $\links'=\links[\jumpsto aw]$, where $\links(a)=u$ and $\links'(a)=w$.
@@
 	\item
-If $\emp v$ contains neither $u$ nor $w$, then it also does not contain $a$. Then also $\emp*v$ contains neither $u$, $w$, nor $a$, and $\Delta=\Delta'$. \hfill\qedhere
+If $\emp v$ contains neither $u$ nor $w$, then it also does not contain $a$. Then also $\emp*v$ contains neither $u$, $w$, nor $a$, and $\Delta=\Delta'$.\qed
 \end{itemize}
-\end{proof}
 
@@
 
-\begin{definition}
+\begin{defi}
 The \emph{balance} of a sequent is the number of $\bot$s minus the number of $\pr$s and commas.
@@
 A sequent is \emph{balanced} if its balance is zero.
-\end{definition}
-
-\begin{proposition}
+\end{defi}
+
+\begin{prop}
 \label{prop:unbalanced then uninhabited}
 An unbalanced sequent is uninhabited.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{definition}
+\begin{defi}
 The \emph{parity} of two switching graphs for proof nets $\links$ and $\links'$ for a sequent $\Gamma$ is the parity of their induced permutation.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}
+\begin{prop}
 Two equivalent proof nets have even parity.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 A balanced basic sequent is inhabited.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 A basic sequent $\1^n,\bigtn(\bot^n)$ is inhabited by $n!$ inequivalent proof nets.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{lemma}
+\begin{lem}
 \label{lem:double exchange}
@@
 Then $\links\perm\links[\jumpsto a{\links(b)}][\jumpsto b{\links(a)}][\jumpsto c{\links(d)}][\jumpsto d{\links(c)}]$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 By the rewiring path shown in Figure~\ref{fig:double exchange}.
-\end{proof}
-
-\begin{lemma}
+\qed
+
+\begin{lem}
 \label{lem:level0 max binary}
 A basic sequent with at least two tensor-formulae has at most two equivalence classes of proof nets.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 By induction on the size of a sequent $\Gamma$.
@@
 Then $\links'$ is obtained by linking $c$ to $b$, and applying Lemma~\ref{lem:double exchange} to exchange the targets of $a$ and $b$, as well as those of $c$ and $d$.
-\end{proof}
-
-\begin{proposition}
+\qed
+
+\begin{prop}
 \label{prop:parity determines equivalence}
 For a basic sequent with at least two tensor-formulae, two proof nets with even parity are equivalent.
-\end{proposition}
-
-\begin{proof}
+\end{prop}
+
+\proof
 By Lemma~\ref{lem:level0 max binary} the sequent has at most 2 equivalence classes.
 Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
-\end{proof}
+\qed
 
@@
 
-\begin{definition} 
+\begin{defi} 
 A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of:
@@
 \end{itemize}
-\end{definition}
-
-\begin{definition}
+\end{defi}
+
+\begin{defi}
 A \emph{(partial) configuration} for a constraint graph $G=(V,E,c,v,w)$ is a (partial) function $\gamma\colon E\to V$ such that
@@
 \end{itemize} 
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}
+\begin{defi}
 A \emph{reconfiguration step} $(\perm*)$ relates two partial configurations for $G$ that differ in value (or definedness) on exactly one edge:
@@
 The reflexive--transitive closure of $(\perm*)$ will be denoted $(\perm)$.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{theorem}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
+\begin{thm}[\cite{GamesPuzzlesAndComputation}, Theorem~5.15]
 \capsabbrev{ncg}-reconfiguration is \capsabbrev{pspace}-complete.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{proposition}
+\begin{prop}
 \label{prop:partial simulates total reconfiguration}
 For total configurations $\gamma$ and $\delta$, if $\gamma\perm\delta$ then $\gamma$ and $\delta$ are also connected by a sequence of reconfiguration steps over total configurations only.
-\end{proposition}
-
-\begin{proof}
+\end{prop}
+
+\proof
 By the following two observations: firstly, 
@@
 %
-\end{proof}
+\qed
+
+\begin{figure}
+\[
+\begin{array}{ccccccccc}
+	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
+	\\ \\ &&&&&&&& \perm \\ \\
+	\boat9 &\perm& \boat8 &\perm& \boat7 &\perm& \boat6 &\perm& \boat5
+\end{array}
+\]
+\caption{A reconfiguration path requiring two inversions of a single edge}
+\label{fig:boats}
+\end{figure}
+
+\begin{figure}
+\[
+	\boats
+\]
+\caption{Nesting graphs to grow reconfiguration paths exponentially}
+\label{fig:big boat}
+\end{figure}
 
@@
 Thus, the length of a rewiring path may grow exponentially with the size of the graph.
-
-\begin{figure}
-\[
-\begin{array}{ccccccccc}
-	\boat0 &\perm& \boat1 &\perm& \boat2 &\perm& \boat3 &\perm& \boat4
-	\\ \\ &&&&&&&& \perm \\ \\
-	\boat9 &\perm& \boat8 &\perm& \boat7 &\perm& \boat6 &\perm& \boat5
-\end{array}
-\]
-\caption{A reconfiguration path requiring two inversions of a single edge}
-\label{fig:boats}
-\end{figure}
-
-\begin{figure}
-\[
-	\boats
-\]
-\caption{Nesting graphs to grow reconfiguration paths exponentially}
-\label{fig:big boat}
-\end{figure}
 
@@
 That means the weight elements must belong to different edges.
-Note that it is possible to use more than one weight element from the same edge to fill one half of a constraint element; or even weight elements from different edges, but we are interested here only in the \emph{minimum} number of edges needed to inappropriately fill a vertex-gadget.
+Note that it is possible to use more than one weight element from the same edge to fill one half of a constraint element, or even weight elements from different edges, but we are interested here only in the \emph{minimum} number of edges needed to inappropriately fill a vertex-gadget.
 
@@
 
-\begin{definition}
+\begin{defi}
 \label{def:graph encoding}
@@
 
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}
+\begin{defi}
 \label{def:standard linkings}
@@
 \end{enumerate}
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}
+\begin{prop}
 \label{prop:element linkings}
 Standard linkings are proof nets.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{definition}
+\begin{defi}
 \label{def:configuration encoding}
@@
 Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the standard linking on $C,W$; otherwise, extend $\itn\gamma$ by the standard linking on the sequent consisting of $W$ plus the first $3n+4$ free weight absorbers.
-\end{definition}
-
-\begin{proposition}
+\end{defi}
+
+\begin{prop}
 If $\gamma$ is a total configuration for $G$ then $\itn\gamma$ is a proof net for $\itn G$.
-\end{proposition}
-
-\begin{proof}
+\end{prop}
+
+\proof
 Using Proposition~\ref{prop:scoping correctness}, it is sufficient to give a suitable box for each $\pr$. 
@@
 After closing the box of each $W$, each edge-gadget in the box of $\itn v$ becomes a single string of connected vertices, connected to other edge-gadgets only via the indicator target of $\itn v$, thus forming a tree.
-\end{proof}
+\qed
 
@@
 
-\begin{definition}
+\begin{defi}
 %
@@
 \]
-and $\itn\delta'$ is $\itn\delta$ with the first two weight absorbers $a$ and $b$ exchanged: $v\mathbin{\xjump}a$ in $\itn\delta'$ if and only if $v\mathbin{\xjump}b$ in $\itn\delta$, and vice versa.
-\end{definition}
+and $\itn\delta'$ is $\itn\delta$ with the first two weight absorbers $a$ and $b$ exchanged: $v\mathbin{\xjump}a$ in $\itn\delta'$ if and only if $v\mathbin{\xjump}b$ in $\itn\delta$, and vice versa, while $\itn\delta'$ agrees with $\itn\delta$ on any other jump.
+\end{defi}
 
@@
 
-\begin{lemma}
+\begin{lem}
 \label{lem:octopus roll}
@@
 Then there is a net $\links'\perm\links$ in which $W_j$ is well linked to $C$, $W_i$ is linked to $1^n$, and $\links'$ agrees with $\links$ otherwise.
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{proof}
+\proof
 Let $W_i=X\pr Y\pr Z$, $W_j=P\pr Q\pr R$, and $C=A\tn B$.
@@
 \textbf{6.}\quad The jump from $Y$ to $A$ is the one remaining connection between the edge-gadgets $\itn{e_i}$ and $\itn{e_j}$.
-Lemma~\ref{lem:double exchange} allows to swap the targets of the jump from $Y$ to $A$ and the jump from $i$, and simultaneously undo the exchange in the jumps from $P$ to $A$ added in step 4 above.
+Lemma~\ref{lem:double exchange} allows to swap the two targets of the jump from $Y$ to $A$ and the jump from $i$, and simultaneously undo the exchange in the two jumps from $P$ to $A$ added in step 4.
 
@@
 
-\end{proof}
+\qed
 
@@
 
-\begin{lemma}
+\begin{lem}
 \label{lem:permute weight absorbers}
 If $\links$ and $\links'$ are well-linked proof nets for $\itn G$ that are equal up to an even permutation of weight absorbers, then $\links\perm\links'$ if $\links$ and $\links'$ have at least one free edge-gadget $\itn e$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 To reconfigure $\links'$ into $\links$, we will use the double exchange operation of Lemma~\ref{lem:double exchange} to exchange two arbitrary weight absorbers at a time, as well as two chosen jumps in the free edge-gadget $\itn e$.
@@
 %
-\end{proof}
-
-\begin{lemma}
+\qed
+
+\begin{lem}
 \label{lem:completeness}
 If $\gamma\perm\delta$ for total configurations $\gamma$ and $\delta$, then $\itn\gamma\perm\itn\delta_\gamma$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 By Proposition~\ref{prop:partial simulates total reconfiguration} we may assume that $\gamma\perm\delta$ by a sequence of reconfiguration steps over total configurations.
@@
 The resulting proof net is $\itn\delta$ modulo a permutation of weight absorbers; then it is equivalent to either $\itn\delta$ or $\itn\delta'$ by Lemma~\ref{lem:permute weight absorbers}.
-\end{proof}
+\qed
 
@@
 
-\begin{proposition}[{\cite[Proposition 1.i]{Bellin-vandeWiele-1995}}]
+\begin{prop}[{\cite[Proposition 1.i]{Bellin-vandeWiele-1995}}]
 \label{prop:tensor has disjoint subnets}
 In a proof net, if vertices $v$ and $w$ are joined by a tensor, then any two subnets of which they are respective ports are disjoint.
-\end{proposition}
-
-\begin{lemma}
+\end{prop}
+
+\begin{lem}
 In a proof net for $\itn G$, an edge-gadget $\itn e$ belongs to the empire of at most one vertex-gadget $\itn v$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 Since vertex-gadgets are joined by a tensor, the lemma is immediate from Proposition~\ref{prop:tensor has disjoint subnets}.
-\end{proof}
+\qed
 
@@
 
-\begin{lemma}
+\begin{lem}
 \label{lem:appropriate edge weights}
 In a proof net for $\itn G$, for each node $v$ in $G$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 %
@@
 Then to balance $3m$ constraint elements inappropriately requires $m+1$ edge-gadgets.
-
-\end{proof}
+\qed
 
@@
 
-\begin{definition}
+\begin{defi}
 For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where
@@
 
-\begin{proposition}
+\begin{prop}
 \label{prop:retraction}
 $\coitn{\itn\gamma}=\gamma$ and $\coitn{\itn\gamma'}=\gamma$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{lemma}
+\begin{lem}
 \label{lem:soundness}
 If $\links\perm\links'$ are proof nets for $\itn G$ then $\coitn\links\perm\coitn{\links'}$.
-\end{lemma}
-
-\begin{proof}
+\end{lem}
+
+\proof
 The proof will consider the case where $\links\perm*\links'$; the general case follows by transitivity.
@@
 %
-\end{proof}
+\qed
 
@@
 
-\begin{theorem}
+\begin{thm}
 \capsabbrev{mll} proof equivalence is \capsabbrev{pspace}-complete.
-\end{theorem}
-
-\begin{proof}
+\end{thm}
+
+\proof
 \capsabbrev{mll} proof equivalence has at most non-deterministic polynomial space complexity: a proof net may be represented in linear space (with respect to a proof); a single rewiring step is performed without requiring additional space; and a non-deterministic algorithm may guess the correct rewiring sequence.
@@
 The direction $(\Rightarrow)$ is by Lemma~\ref{lem:completeness}; the direction $(\Leftarrow)$ is by Lemma~\ref{lem:soundness} and Proposition \ref{prop:retraction}.
-\end{proof}
-
-\subsection*{Acknowledgements}
-We would like to thank Beniamino Accattoli, Dominic Hughes, and Lutz Stra{\ss}burger for helpful discussions and comments. We would also like to thank the anonymous referees for insightful remarks.
+Encoding an instance of \capsabbrev{ncg}-reconfiguration $(G,\gamma,\delta)$ involves first computing $\itn G$, $\itn\gamma$, and $\itn\delta$, and next computing the parity of $\itn\gamma$ and $\itn\delta$ and adjusting $\itn\delta$ if needed.
+This can be done in polynomial time in the size of $(G,\gamma,\delta)$.
+\qed
+
+\section*{Acknowledgements}
+We would like to thank Beniamino Accattoli, Dominic Hughes, and Lutz Stra{\ss}burger for helpful discussions and comments.
+We would also like to thank the anonymous referees for their insightful remarks.
 
 %===========================
-\bibliographystyle{plain}
+\bibliographystyle{alpha}
 \bibliography{LMCS}
+%\begin{thebibliography}{ladida}
+%\end{thebibliography}
 \end{document}

### 2015-10-16 main/LMCS.tex
Changed lemma
Minor typos

@@
 For intuitionistic \capsabbrev{mll} rewiring may be directed towards the unique conclusion, to yield canonical forms.\footnote{The canonical nets for \capsabbrev{imll} described here appear to be folklore; established proof nets for intuitionistic linear logic, called essential nets \cite{Lamarche-2008,Murawski-Ong-2003}, (non-canonically) attach jumps to the leaves of the formula tree, for easier composition.}
-For classical MLL with units however, there is not an obvious preferred point to attach jumps.
+For classical MLL with units, however, there is not an obvious preferred point to attach jumps.
 And this problem extends to multiplicative--exponential linear logic (\capsabbrev{mell}) without units, where a formula $?A$ may be introduced via a weakening rule with similar permutability to the $\bot$-introduction rule.
@@
 The permutations of sequent proofs are exactly the identifications imposed by the categorical semantics of \capsabbrev{mll}, star-autonomous categories \cite{Barr-1991} (and semi-star-autonomous categories \cite{Houston-2008,Heijltjes-Strassburger} for \capsabbrev{mll} without units).
-Proof equivalence for \capsabbrev{mll} is equivalent to the \emph{word problem} for star-autonomous categories: the problem whether two term representations denote the same morphism in any star-autonomous category.
+Proof equivalence for \capsabbrev{mll} is equivalent to the \emph{word problem} for star-autonomous categories: the problem of deciding whether two term representations denote the same morphism in any star-autonomous category.
 
@@
 By induction on the size of a sequent $\Gamma$.
-The base case is the sequent $\1,\1,\bot\tn\bot$, which has two inequivalent proof nets.
+The base case is the sequent $\1,\1,\1,\bot\tn\bot,\bot\tn\bot$, which has two equivalence classes of proof nets, shown in Figure~\ref{fig:_*_,1,1,1,_*_}.
 For the inductive step, let $\Gamma=\Gamma',A\tn\named a\bot,\named z\1$ where $A\tn\named a\bot$ is a largest $\tn$-formula in $\Gamma$.

### 2015-10-16 main/LMCS.tex
Use “3-partition” rather than “3-Partition” consistently

@@
 
-Both Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994} use a reduction from (a variant of) the 3-Partition problem to show  \capsabbrev{np}-hardness.
+Both Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994} use a reduction from (a variant of) the 3-partition problem to show  \capsabbrev{np}-hardness.
 Such reductions provide a good illustration of how the linearity of \capsabbrev{mll} can be used to encode combinatoric problems.
-In this section we will discuss a similar reduction from 3-Partition.
+In this section we will discuss a similar reduction from 3-partition.
 
@@
 
-An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$.
+An instance of the 3-partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$.
 The decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$.
 It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, so that any partitioning into \emph{subsets} with sum $k$ is a solution, since each subset of sum $k$ necessarily has $3$ elements.
-The 3-Partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.
+The 3-partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.
 
 We will give a simple encoding of 3-partition in MLL proof search, similar to those of Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994}.
-A 3-Partition instance $I$ is encoded by a sequent consisting of:
+A 3-partition instance $I$ is encoded by a sequent consisting of:
 \begin{itemize}

### 2015-10-16 main/LMCS.tex
More typo corrections

@@
 
-The correctness condition ensures that every proof net on a sequent encoding a 3-partition problem gives a solution that problem.
+The correctness condition ensures that every proof net on a sequent encoding a 3-partition problem gives a solution to that problem.
 If two jumps from a formula encoding a number $i$ connect to different formulae $K_j$ and $K_m$, a cycle is created immediately.
@@
 The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
-This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.
+This problem is \capsabbrev{pspace}-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same pair of vertices) can be prohibited, for example.
 
